### 2021-02-11 main.tex
Add statement of theorem

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newtheorem{theorem}{Theorem}

\newcommand{\im}{\mathrm{im}}
\begin{document}
	\begin{theorem}
		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists $U$, an open set containing $V$ such that $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$. Then, $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$ is finitely generated.
	\end{theorem}	
\end{document}

### 2021-02-16 main.tex
Add diagrams for Mayer-Vietoris

@@
-\documentclass{article}
+\documentclass{amsart}
 \usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
+\usepackage{tikz-cd}
 
@@
 \newcommand{\im}{\mathrm{im}}
+\newcommand{\Z}{\mathbb{Z}}
+
 \begin{document}
+	What we want to prove:
 	\begin{theorem}
-		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists $U$, an open set containing $V$ such that $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$.
-Then, $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$ is finitely generated.
+		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
+Then, $\im \big(H_n(Y) \to H_n(X)\big)$ is finitely generated for every $n$.
 	\end{theorem}
+
+	An example to keep in mind:
+	$Z = \left\{\frac{1}{n}\ |\ n \geq 0\right\} \cup \{0\} \subset \mathbb R$ is Hausdorff and compact with infinite 0-homology.
+
+	A diagram to keep in mind
+	\begin{equation}
+	\begin{tikzcd}
+	\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
+	\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
+	\end{tikzcd}
+	\end{equation}
+
+	Consider the following general diagram
+	\begin{equation}
+	\begin{tikzcd}
+	A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
+	X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
+	\end{tikzcd}
+	\end{equation}
 \end{document}

### 2021-02-16 main.tex
Add counterexample

@@
 \usepackage[english]{babel}
-\usepackage{tikz-cd}
+\usepackage{tikz}
 
-\newtheorem{theorem}{Theorem}
+\newtheorem{statement}{Statement}
 
@@
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\R}{\mathbb{R}}
 
 \begin{document}
-	What we want to prove:
-	\begin{theorem}
-		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_n(Y) \to H_n(X)\big)$ is finitely generated for every $n$.
-	\end{theorem}
+	\begin{statement}
+		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
+Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
+	\end{statement}
+	\paragraph{\textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
+Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
+The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
+Furthermore, it is locally simply-connected.
+Taking $Y = X$ gives a counterexample.
 
-	An example to keep in mind:
-	$Z = \left\{\frac{1}{n}\ |\ n \geq 0\right\} \cup \{0\} \subset \mathbb R$ is Hausdorff and compact with infinite 0-homology.
+	\begin{equation*}
+		\begin{tikzpicture}[scale=5]
+		\foreach \i in {0,1,2,...,12}{
+			\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
+		}
+		\end{tikzpicture}
+	\end{equation*}
+\end{document}
 
@@
 \end{equation}
-\end{document}

### 2021-02-16 counterexample.tex
Add beamer of counterexample

--- 2021-02-11 main.tex
@@
-\documentclass{article}
+\documentclass[10pt]{beamer}
 \usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
-
-\newtheorem{theorem}{Theorem}
+\usepackage{tikz}
 
 \newcommand{\im}{\mathrm{im}}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\R}{\mathbb{R}}
+
 \begin{document}
-	\begin{theorem}
-		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists $U$, an open set containing $V$ such that $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$.
-Then, $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$ is finitely generated.
-	\end{theorem}	
+\begin{frame}{Local to global}
+	\begin{block}{Statement}
+		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
+Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
+	\end{block}
+	\pause
+	\begin{block}{Counterexample}
+		Take $X = Y = $ suspension of $\left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
+		\vspace*{.3cm}
+
+		\begin{tikzpicture}[scale=5]
+		\foreach \i in {0,1,2,...,12}{
+			\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
+		}
+		\end{tikzpicture}
+	\end{block}
+	\vspace*{-1cm}
+\end{frame}
 \end{document}

### 2021-02-23 main.tex
Add beamer of counterexample
Add rough proof of the conjecture

@@
 \usepackage[english]{babel}
-\usepackage{tikz}
+\usepackage{amsmath}
+\usepackage{tikz-cd}
 
-\newtheorem{statement}{Statement}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{statement}[theorem]{Statement}
 
-\newcommand{\im}{\mathrm{im}}
 \newcommand{\Z}{\mathbb{Z}}
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\dprime}{{\prime\prime}}
+\DeclareMathOperator{\im}{im}
+\DeclareMathOperator{\interior}{int}
+
+\setlength{\textwidth}{\paperwidth}
+\addtolength{\textwidth}{-1.6in}
+\setlength{\textheight}{\paperheight}
+\addtolength{\textheight}{-1.8in}
+\calclayout
 
@@
 	\end{statement}
-	\paragraph{\textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
+
+	\begin{theorem}
+		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ (compact? check where used).
+		\begin{itemize}
+			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$, then $\im r^n_{\widetilde K, M}$ is finite.
+			\item[$(r^n_\bullet)$] If $V$ is a neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
+		\end{itemize}
+		Then, ($r^{n-1}$) together with ($r^n_\bullet$) imply ($r^n$).
+	\end{theorem}
+
+	\begin{proof}
+		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ of $\interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
+
+		Notice that $\sigma$ contains a compact neighborhood of each $y \in Y$ because of $(r^n_\bullet)$.
+This because locally compact together with Hausdorff imply that for any element $y$ and open $U_y$ there exist $K_y$ compact with $y \in K_y \subseteq U_y$.
+
+		Let $K_1, K_2 \in \sigma$ and let $K_i^\prime$ be a compact neighborhood of $K_i$ such that $\im r^n_{K^\prime_i \cap Y, M}$ is finite.
+Such $K^\prime_i$ since (fill details using compactness of $K_i$ and the above property of locally compact Hausdorff spaces).
+
+		Let $K_i^{\dprime}$ be a compact neighborhood of $K_i$ with $K_i^{\dprime} \subseteq \interior K_i^\prime$. (Fill in the details again.)
+
+		Use $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
+		\begin{equation*}
+		\begin{tikzcd}
+		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
+		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
+		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
+		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
+		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
+		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
+		\end{tikzcd}
+		\end{equation*}
+		The upper right square has a finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is.
+The bottom left square has a finite image using property $(r^n)$ with $K = K_1^\dprime \cap K_2^\dprime$ and $M = \widetilde K_1^\prime \cap \widetilde K_2^\prime$.
+And checking that $\interior(K_i^\prime) \cap Y \subseteq \interior(K_i^\prime \cap Y)$ and $\interior(K_1^\prime) \cap \interior(K_2^\prime) \subseteq \interior(K_1^\prime \cap K_2^\prime)$ (verify this.)
+	\end{proof}
+
+	\begin{lemma}
+		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces, then $(r^0)$ above holds. 
+	\end{lemma}
+
+	\begin{proof}
+		Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$.
+For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite.
+Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
+The beginning of the Mayer-Vietoris sequence gives us
+		\begin{equation*}
+		\begin{tikzcd}
+		\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
+		\bigoplus_i^n H_0(M) \arrow[r] & H_0(M). &
+		\end{tikzcd}
+		\end{equation*}
+	\end{proof}
+\end{document}
+
+\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
 Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
 The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
-Furthermore, it is locally simply-connected.
+Furthermore, locally $H_1 = 0$.
 Taking $Y = X$ gives a counterexample.
@@
 \end{equation*}
-\end{document}
 

### 2021-02-24 main.tex
Version shared with collaborators

@@
 
+	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+
 	\begin{theorem}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ (compact? check where used).
+		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact.
 		\begin{itemize}
 			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$, then $\im r^n_{\widetilde K, M}$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is a neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
+			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
 		\end{itemize}
-		Then, ($r^{n-1}$) together with ($r^n_\bullet$) imply ($r^n$).
+		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
 	\end{theorem}
@@
 	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ of $\interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
+		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
 
-		Notice that $\sigma$ contains a compact neighborhood of each $y \in Y$ because of $(r^n_\bullet)$.
-This because locally compact together with Hausdorff imply that for any element $y$ and open $U_y$ there exist $K_y$ compact with $y \in K_y \subseteq U_y$.
+		Recall the following fact:
+		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
 
-		Let $K_1, K_2 \in \sigma$ and let $K_i^\prime$ be a compact neighborhood of $K_i$ such that $\im r^n_{K^\prime_i \cap Y, M}$ is finite.
-Such $K^\prime_i$ since (fill details using compactness of $K_i$ and the above property of locally compact Hausdorff spaces).
+		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
+		\begin{equation*}
+		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
+		\end{equation*}
+		where $\im r^n_{U_i \cap Y, M}$ is finite. 
+		We can construct such compact neighborhoods using $(\ast)$ as follows:
 
-		Let $K_i^{\dprime}$ be a compact neighborhood of $K_i$ with $K_i^{\dprime} \subseteq \interior K_i^\prime$. (Fill in the details again.)
+		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
+The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$, and a finite union of the corresponding compact neighborhoods form the desired $K_i^\prime, K_i^\dprime$.
 
-		Use $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
+		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior(K_1^\prime \cap K_2^\prime \cap Y)$.
+To see this (if not immediately), take $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$, since by assumption there exist open sets $V_i$ in $X$ such that $p \in V_i \cap K_i^\prime$.
+Letting $V = V_1 \cap V_2$ we have $p \in V \cap (K^\prime_1 \cap K^\prime_2)$ and, since $p \in Y$, $p \in V \cap (K^\prime_1 \cap K^\prime_2 \cap Y)$ implying the claim.
+
+		Using $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
 		\begin{equation*}
@@
 		\end{equation*}
-		The upper right square has a finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is.
-The bottom left square has a finite image using property $(r^n)$ with $K = K_1^\dprime \cap K_2^\dprime$ and $M = \widetilde K_1^\prime \cap \widetilde K_2^\prime$.
-And checking that $\interior(K_i^\prime) \cap Y \subseteq \interior(K_i^\prime \cap Y)$ and $\interior(K_1^\prime) \cap \interior(K_2^\prime) \subseteq \interior(K_1^\prime \cap K_2^\prime)$ (verify this.)
+		The upper right square has finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is finite.
+The bottom left square has a finite image using property $(r^{n-1})$.
+From standard homological algebra using that the middle row is exact we conclude that $K_1 \cup K_2 \in \sigma$.
+
+		Notice that because of $(r_\bullet^n)$ and $(\ast)$, the collection $\sigma$ contains a compact neighborhood of each $y \in Y$.
+
+		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior M$. We can cover $\widetilde{K}$ with finitely many sets in $\sigma$ and conclude that $K$ is itself in $\sigma$.
 	\end{proof}
+\end{document}
 
@@
 Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
-The beginning of the Mayer-Vietoris sequence gives us
+Since
 	\begin{equation*}
@@
 	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
-		\bigoplus_i^n H_0(M) \arrow[r] & H_0(M). &
+	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
 	\end{tikzcd}
 	\end{equation*}
+	commutes, we have the desired conclusion.
+	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
 \end{proof}
-\end{document}
 

### 2021-02-24 main.tex
Cleaned after conversation (still cohomology)

@@
 \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{statement}[theorem]{Statement}
 
@@
 \begin{document}	
-	\begin{statement}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{statement}
-
 	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.
 
-	\begin{theorem}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact.
+	\begin{lemma} \label{l: wilder}
+		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
 		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$, then $\im r^n_{\widetilde K, M}$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
+			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$, then $\im r^n_{\widetilde K, M}$ is finite.
+			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
 		\end{itemize}
 		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
-	\end{theorem}
+	\end{lemma}
 
 	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
+		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
 
@@
 		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
+
+		The collection $\sigma$ is not empty, in fact, it contains a compact neighborhood of any $y \in Y$.
+This follows from taking $V = X$ in $(r_\bullet^n)$ and using $(\ast)$ on the resulting open neighborhood.
+
+		Notice that the collection $\sigma$ is closed under intersections.
+In fact, a stronger statement holds: if $K_1$ is compact and $K_2 \in \sigma$ then $K_1 \cap K_2 \in \sigma$.
+This is a consequence of the fact that the image of a map is finite can be deduced from that property holding for any map that factors it.
+We will next show that $\sigma$ is also closed under finite unions.
 
@@
 		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
-The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$, and a finite union of the corresponding compact neighborhoods form the desired $K_i^\prime, K_i^\dprime$.
+The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$.
+Let $\{p_i^{1}, \dots, p^{n}_i\} \subseteq K_i$ be such that $K_i \subseteq \bigcup_{j=1}^n \interior K^\dprime_i(p^j_i)$.
+Define $K_i^\dag = \bigcup_{j=1}^n K^\dag_i(p^j_i)$ for $i \in \{1,2\}$ and $\dag \in \{\prime, \dprime\}$.
 
-		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior(K_1^\prime \cap K_2^\prime \cap Y)$.
-To see this (if not immediately), take $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$, since by assumption there exist open sets $V_i$ in $X$ such that $p \in V_i \cap K_i^\prime$.
-Letting $V = V_1 \cap V_2$ we have $p \in V \cap (K^\prime_1 \cap K^\prime_2)$ and, since $p \in Y$, $p \in V \cap (K^\prime_1 \cap K^\prime_2 \cap Y)$ implying the claim.
+		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior_Y(K_1^\prime \cap K_2^\prime \cap Y)$.
+To see this consider $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$.
+By construction for $i \in \{1, 2\}$ there exist open sets $V_i \subseteq K_i^\prime$ such that $p \in V_i$.
+Letting $V = V_1 \cap V_2$ we have $p \in V \cap Y \subseteq K^\dprime_1 \cap K^\dprime_2 \cap Y$ implying $p \in \interior_Y(K^\dprime_1 \cap K^\dprime_2 \cap Y)$.
 
@@
 The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra using that the middle row is exact we conclude that $K_1 \cup K_2 \in \sigma$.
+From standard homological algebra using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $\widetilde K_1^\prime \cup \widetilde K_2^\prime$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
 
-		Notice that because of $(r_\bullet^n)$ and $(\ast)$, the collection $\sigma$ contains a compact neighborhood of each $y \in Y$.
+		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
+		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
+Here we are using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
+Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = K \cap C \cup K \cap D$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $D \in \sigma$ trivially.
+	\end{proof}
 
-		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior M$. We can cover $\widetilde{K}$ with finitely many sets in $\sigma$ and conclude that $K$ is itself in $\sigma$.
+	We can now immediately prove the following result.
+
+	\begin{theorem}
+		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
+Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
+	\end{theorem}
+
+	\begin{proof}
+		Using the notation of Lemma \ref{l: wilder}, this would follow from $(r_n)$ applied to the case $K = Y$ and $M = X$.
+To show $(r_n)$ holds for every $n \geq 0$ we proceed by induction noticing that by assumption we have $(r^n_\bullet)$ for every $n$.
 	\end{proof}

### 2021-02-24 main.tex
Replace cohomology by homology

@@
 \begin{document}	
-	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+
+	The following is a modification of a theorem of Wilder.
 
@@
 		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$, then $\im r^n_{\widetilde K, M}$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
+			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $K \cap Y \subset \interior_Y(M \cap Y)$, then $\im H_n\left(K \cap Y \to M\right)$ is finite.
+			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$, then there exist $U$ an open neighborhood of $y$ contained in $V$ such that $\im H_n\left(U \cap Y \to V\right)$ is finite.
 		\end{itemize}
@@
 	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
+		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im H_n\left(U_K \cap Y \to M\right)$ is finite.
 
@@
 		\end{equation*}
-		where $\im r^n_{U_i \cap Y, M}$ is finite. 
+		where $\im H_n\left(U_i \cap Y \to M\right)$ is finite. 
 		We can construct such compact neighborhoods using $(\ast)$ as follows:
@@
 
-		Using $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
 		\begin{equation*}
 		\begin{tikzcd}
-		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
-		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
-		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
-		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
-		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
-		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
+		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
+		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
+		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
+		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
+		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
+		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
 		\end{tikzcd}
 		\end{equation*}
-		The upper right square has finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is finite.
+
+		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$.
 The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $\widetilde K_1^\prime \cup \widetilde K_2^\prime$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
+From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
 
-		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
+		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
 		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
-Here we are using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
-Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = K \cap C \cup K \cap D$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $D \in \sigma$ trivially.
+This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
+Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
 	\end{proof}

### 2021-03-24 main.tex
Add longer diagram
Complete proof of the main lemma

@@
 \newtheorem{lemma}[theorem]{Lemma}
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
 
+\newcommand{\N}{\mathbb{N}}
 \newcommand{\Z}{\mathbb{Z}}
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\HS}{\mathrm{HS}}
 \newcommand{\dprime}{{\prime\prime}}
@@
 \setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
+\addtolength{\textwidth}{-1.4in}
 \setlength{\textheight}{\paperheight}
@@
 
+\newcommand{\p}{\mathrm{p}}
+\newcommand{\q}{\mathrm{q}}
+
+\usepackage{parskip}
 \begin{document}
+
+\begin{definition}
+	For $n \in \N$, a continuous map is said to be \textit{$n$-homologically small}, denoted $\HS_n$, if the image of the map induced by $H_n(-)$ is finitely generated, and we say it is \textit{homologically small}, denoted $\HS$, if it is $\HS_n$ for every $n$.
+\end{definition}
+
+\begin{definition}
+	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
+	\begin{equation*}
+	X_{\leq t} = f^{-1}((-\infty, t]).
+	\end{equation*}
+\end{definition}
+
+\begin{definition}
+	Let $M$ be a metric space. For any $p \in M$ and $\epsilon > 0$, the \textit{$\epsilon$-neighborhood of $p$} is defined by
+	\begin{equation*}
+	B_\epsilon(p) = \{q \in M\ |\ d(p,q) < \epsilon\}.
+	\end{equation*}
+\end{definition}
+
+\begin{definition}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function.
+	The space $M$ is said to be \textit{strongly locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the image of the map induced by $H_n(-)$ on $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $0$.
+\end{definition}
+
+\begin{theorem} \label{t:strong local connectenss implies tameness}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
+\end{theorem}
+
+\begin{lemma} \label{l:commutative algebra}
+	Lemma 17.3 in Bredon.	
+\end{lemma}
+
+\begin{lemma}
+	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies tameness}.
+	For compact sets $K, L \subseteq M$ with $K \subseteq \interior(L)$ and $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
+\end{lemma}
+
+\begin{proof}
+	We will proceed by induction on $n \in \N$. Assume the lemma holds with $\HS$ replaced with $\HS_{(n-1)}$.
+	Given a compact set $L \subseteq M$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $M$ for which there exists $\delta_K > 0$ and an open neighborhood $U_K$ of $K$ such that $U_K \cap M_{s+\delta_K} \to L \cap M_{t}$ is $\HS_n$.
+
+	We start by showing that any point in $\interior(L) \cap M_s$ has a neighborhood in $\Sigma_{s, t}$.
+	Let $x \in \interior(L) \cap M_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
+	By the strong local-$f$-connectivity of $M$, there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ and any $d \geq 0$ the following composition is $\HS$:
+	\begin{equation*}
+	B_\delta(x) \cap M_{s + \delta + d} =
+	B_\delta(x) \cap M_{f(x) + c + \delta + d} \to
+	B_e(x) \cap M_{f(x) + c + e + d} \to
+	L \cap M_{t + d}.
+	\end{equation*}
+
+	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
+	For $i = 1, 2$ let $K_i \in \Sigma_{s,t}$ with chosen $\delta_i > 0$ and open neighborhood $U_i$. Let $K_i^\dprime$ and $K_i^\prime$ be compact sets such that
+	\begin{equation*}
+	K_i \subseteq \interior(K_i^\dprime) \subseteq K_i^\prime \subseteq U_i,
+	\end{equation*}
+	which can be easily constructed using that any neighborhood of a point in a metric space contains a compact neighborhood of that point.
+	Notice that, since $K_i \subseteq U_i$, if $\delta = \min(\delta_i)$ then $K_i^\prime \cap M_{s+\delta} \to L \cap M_t$ is $\HS_n$ and that by induction we have that $K_1^\dprime \cap K_2^\dprime \cap M_s \to K_1^\prime \cap K_2^\prime \cap M_{s+\delta}$ is $\HS_{(n-1)}$.
+
+	We therefore have the following commutative diagram satisfying the assumptions of Lemma \ref{l:commutative algebra}:
+	\begin{equation*}
+	\begin{tikzcd}
+	& H_n(L \cap M_t) & \arrow[l] H_n(L \cap M_t) \oplus H_n(L \cap M_t) \\
+	H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) & 
+	H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[l] \arrow[u] &
+	H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus H_n(K_2^\prime \cap M_{s+\delta}) \arrow[l] \arrow[u] \\
+	H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap M_s) \arrow[u] & 
+	H_{n}((K_1^\dprime \cap M_s) \cup (K_2^\dprime \cap M_s)), \arrow[l] \arrow[u] &
+	\end{tikzcd}
+	\end{equation*}
+	which implies $K_1 \cup K_2 \in \Sigma_{s, t}$ as desired. Since any $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the lemma is proven.
+\end{proof}
+
+\newpage
+
+Assume $X$ is Hausdorff and locally compact.
+
+Let $p_n$ be the proposition: For compact sets $K, L \subseteq X$ with $K \subseteq \interior(L)$, $\forall s < t$, $\exists\, \delta \in (0, t-s)$ s.t.
+$K \cap M_{s+\delta+c} \to L \cap M_{t+c}$ is $n$-fgi for $c \geq 0$.
+
+Assume $(\ast): \forall x \in X$, $\forall e > 0$, $\exists \delta \in (0,e)$ s.t. $\forall c \geq 0$
+\begin{equation*}
+B_\delta(x) \cap M_{f(x)+\delta+c} \to B_e(x) \cap M_{f(x)+e+c}
+\end{equation*} 
+is $n$-fgi for all $n \geq 0$.
+
+Given compact $L \subseteq X$, for $s < t$ let
+\begin{equation*}
+\Sigma_{s,t} = \{K \text{ compact}\ |\ \exists\, \delta \in (0, t-s), \exists\, K \subseteq U \subseteq \interior(L) \text{ open s.t.
+} U \cap M_{s+\delta+c} \to L \cap M_{t+c} \text{ is $n$-fgi for } c\geq 0\}.
+\end{equation*}
+
+1) If $\interior(L) \cap M_s \neq \emptyset$ then $\Sigma_{s, t}$ is not empty:
+
+Let $x \in \interior(L) \cap M_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
+By $(\ast)$ there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ and any $d \geq 0$ the following composition is $n$-fgi for any $n$
+\begin{equation*}
+B_\delta(x) \cap M_{s + \delta + d} =
+B_\delta(x) \cap M_{f(x) + c + \delta + d} \to
+B_e(x) \cap M_{f(x) + c + e + d} \to
+L \cap M_{t + d}.
+\end{equation*}
+
+2) $\Sigma_{s,t}$ is closed under finite unions:
+
+For $i = 1, 2$, let $K_i \in \Sigma_{s,t}$ with associated $\delta_i$ and $U_i$. Let $K_i^\dprime$ and $K_i^\prime$ be compact sets such that
+\begin{equation*}
+K_i \subseteq \interior(K_i^\dprime) \subseteq K_i^\prime \subseteq U_i.
+\end{equation*}
+Notice that if $\delta = \min(\delta_i)$ then $K_i^\prime \cap M_{s+\delta} \to L \cap M_t$ is $n$-fgi.
+
+\begin{equation*}
+\begin{tikzcd}
+& H_n(L \cap M_t) & \arrow[l] H_n(L \cap M_t) \oplus H_n(L \cap M_t) \\
+H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) & 
+H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[l] \arrow[u] &
+H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus H_n(K_2^\prime \cap M_{s+\delta}) \arrow[l] \arrow[u] \\
+H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap M_s) \arrow[u] & 
+H_{n}((K_1^\dprime \cap M_s) \cup (K_2^\dprime \cap M_s)) \arrow[l] \arrow[u]. &
+\end{tikzcd}
+\end{equation*}
+
+\newpage
+
+Assume $X$ is Hausdorff and locally compact.
+
+Let $p_n$ be the proposition: For compact sets $K, L \subseteq X$ with $K \subseteq \interior(L)$, $\forall s < t$, $K \cap Y_{s+c} \to L \cap Y_{t+c}$ is $n$-fgi for $c \geq 0$.
+
+Assume $(\ast): \forall x \in X$, $\forall e > 0$, $\exists \delta \in (0,e)$ s.t. $\forall c \geq 0$
+\begin{equation*}
+B_\delta(x) \cap Y_{f(x)+\delta+c} \to B_e(x) \cap Y_{f(x)+e+c}
+\end{equation*} 
+is $n$-fgi for all $n \geq 0$.
+
+Given compact $L \subseteq X$, for $s < t$ let
+\begin{equation*}
+\Sigma_{s,t} = \{K \text{ compact}\ |\ \exists\ K \subseteq U \subseteq \interior(L) \text{ open s.t. } U \cap Y_{s+c} \to L \cap Y_{t+c} \text{ is $n$-fgi for } c\geq 0\}.
+\end{equation*}
+
+1) If $\interior(L) \cap Y_s \neq \emptyset$ then $\Sigma_{s, t}$ is not empty:
+
+Let $x \in \interior(L) \cap Y_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
+By $(\ast)$ there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ and any $d \geq 0$ the following composition is $n$-fgi for any $n$
+\begin{equation*}
+B_\delta(x) \cap Y_{s + d} \to
+B_\delta(x) \cap Y_{f(x) + c + \delta + d} \to
+B_e(x) \cap Y_{f(x) + c + e + d} \to
+L \cap Y_{t + d}.
+\end{equation*}
+
+2) $\Sigma_{s,t}$ is closed under finite unions:
+
+Let $K_1, K_2 \in \Sigma_{s,t}$ we will construct for $i=1, 2$ compact sets $K_i^\prime$ such that
+\begin{equation*}
+K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime
+\end{equation*}
+and $K_i^\prime \cap Y_{s+\epsilon} \to L \cap Y_t$ is $n$-fgi.
+
+Issue about the fact that $U_i \cap Y_{s+\epsilon} \to L \cap Y_{t+\epsilon}$ is $n$-fgi but not $s+\epsilon \to t$ as needed for the induction.
+
+\newpage
+
+%	Let $f$ be a real-valued function from a metric space $M$ such that for every $s \in \R$ the preimage $M_{\leq s} = f^{-1}(\{r \leq s\})$ is compact and satisfies the following property:\\
+%	
+%	Given values $s < t$, a point $p \in M_{\leq s}$, and any open neighborhood $V$ of $p$ in $M_{\leq t}$ there is an open neighborhood $U \subseteq V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap M_{\leq s}) \to \widetilde H_\bullet(V)\big) = 0$.\\
+%	
+%	Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.\\
+%	
+%	Take $s < t$. If there exists $t_i \in (s, t]$ such that $M_{\leq s} = M_{\leq t_1}$ we are done by Wilder's original theorem.
+%	
+%	Assume the contrary.
+
 	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
 
-	The following is a modification of a theorem of Wilder.
+	\begin{lemma} 
+		Let $Y_t$ a filtration by compact subsets of a locally compact and Hausdorff space $X$. Define the following properties:
+		\begin{itemize}
+			\item[$\p(n)$] Let $s < t$. If $K$ and $L$ are compact subsets of $X$ with $K \cap Y_s \subset \interior(L) \cap Y_t$, then $\im H_n\left(K \cap Y_s \to L \cap Y_t\right)$ is finite.
+			\item[$\q(n)$] Let $s < t$. If $V$ is an open neighborhood of $y \in Y_s$, then there exist an open set $U \subseteq V$ such that $\im H_n\left(U \cap Y_s \to V \cap Y_t\right)$ is finite.
+		\end{itemize}
+		Then, $\p(n-1)$ together with $\q(n)$ imply $\p(n)$.
+	\end{lemma}
+
+	\begin{proof}
+		Recall the following fact:
+		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
+
+		Let $K$ and $L$ as above and choose $r \in (s, t)$.
+Using $\q(n)$ for $r < t$ we can choose for each $y \in Y_r$ an open $U(y)$ such that $U(q) \cap Y_r \to \interior(L) \cap Y_t$ is $H_n$-finite.
+Let $D(y) \subseteq U(y)$ be a compact neighborhood of $y$.
+Using $\q(n)$ for $s < r$ consider for any $x \in Y_s \subseteq Y_r$ an open neighborhood $W(x) \subseteq \interior(D(x))$ such that $W(x) \cap Y_s \to \interior(D(x)) \cap Y_t$ is $H_n$-finite.
+Denote by $C(x) \subseteq W(x)$ a compact neighborhood of $x$.
+Notice that for any $x, x^\prime \in Y_s$ we have $C(x) \cap C(x^\prime) \cap Y_s \subseteq \interior(D(x) \cap D(x^\prime)) \cap Y_r$.
+So, by $\p(n-1)$, the inclusion map $C(x) \cap C(x^\prime) \cap Y_s \to \interior(D(x) \cap D(x^\prime)) \cap Y_r$ is $H_{n-1}$-finite.
+		\begin{equation*}
+		\begin{tikzcd}
+		& H_n(L \cap Y_r) & \arrow[l] H_n(L \cap Y_r) \oplus H_n(L \cap Y_r) \\
+		H_{n-1}(D_1 \cap D_2 \cap Y_t) & 
+		H_n((D_1 \cap Y_t) \cup (D_2 \cap Y_t)) \arrow[l] \arrow[u] &
+		\arrow[l] H_n(D_1 \cap Y_t) \oplus H_n(D_2 \cap Y_t) \arrow[u] \\
+		H_{n-1}(C_1 \cap C_2 \cap Y_s) \arrow[u] & 
+		H_n((C_1 \cap Y_s) \cup (C_2 \cap Y_s)) \arrow[l] \arrow[u]. &
+		\end{tikzcd}
+		\end{equation*}
+
+		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$.
+The bottom left square has a finite image using property $(r^{n-1})$.
+From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
+
+		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
+		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
+This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
+Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
+	\end{proof}
+
+	\newpage
+
+	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
 
@@
 		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
-		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
+		H_{n-1}(K_1^\prime \cap K_2^\prime) & 
+		H_{n}(K_1^\prime \cup K_2^\prime) \arrow[l] \arrow[u] &
+		H_{n}(K_1^\prime) \oplus H_n(K_2^\prime) \arrow[l] \arrow[u] \\
+		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) \arrow[u] & 
 		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
@@
 		\end{equation*}
+
+%		\begin{equation*}
+%		\begin{tikzcd}
+%		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
+%		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
+%		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
+%		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
+%		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
+%		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
+%		\end{tikzcd}
+%		\end{equation*}
 
@@
 
-\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
+Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
 Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.

### 2021-03-25 main.tex
Add previous work

--- 2021-02-24 main.tex
@@
+\immediate\write18{bibtex \jobname}
 \documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
+
+\usepackage{amsmath, amsthm, amssymb}
+\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
+\usepackage[capitalize,noabbrev]{cleveref}
 \usepackage{tikz-cd}
+%\usepackage{newtxtext,newtxmath}
+\usepackage[numbers,sort,compress]{natbib}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
+\usepackage[marginpar]{todo}
+\makeatletter
+\renewcommand{\@tododisplay}[1]{%
+%\marginpar{#1}%
+\textsuperscript{#1}%
+}
+%
+\renewcommand\@displaytodo[2][\todomark]{%
+\@tododisplay{{\todoformat [#1~\ref{todolbl:\thetodo}]}}%
+\footnotetext[\thetodo]{\todoformat #1:~#2}%
+\global\@todotoks\expandafter{\the\@todotoks\todoitem{#1}{#2}}%
+\@todotrue%
+}%
+\renewcommand\todomark{todo}
+\makeatother
 
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\dprime}{{\prime\prime}}
+\theoremstyle{plain}
+\newtheorem{thm}{Theorem}[section]
+\Crefname{thm}{Theorem}{Theorems}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\Crefname{prop}{Proposition}{Propositions}
+\newtheorem{claim}[thm]{Claim}
+\newtheorem{conj}[thm]{Conjecture}
+\Crefname{conj}{Conjecture}{Conjectures}
+
+\theoremstyle{definition}
+\newtheorem{defi}[thm]{Definition}
+\newtheorem{ex}[thm]{Example}
+\newtheorem{rem}[thm]{Remark}
+
 \DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
 
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
+\newcommand\CH{\check{H}}
+
+\title{Persistence in Functional Topology and a Correction to a Theorem by Morse}
+\author{}
+\date{\today}
 
 \begin{document}
-	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+\maketitle
+\begin{abstract}
+With applications to the study of minimal surfaces in mind, Marston Morse wrote a series of papers developing versions of his famous inequalities for a broad class of real-valued functions on metric spaces.
+His work is remarkable in so far as it likely represents the first use of something that can be called persistent homology in the mathematical literature.
+From the modern point of view, it is particularly interesting that he uses Vietoris homology in order to enforce semi-continuity of persistent homology and that he states two topological conditions that supposedly ensure q-tameness.
+However, he is partly incorrect: We present a filtration that satisfies one of his conditions but has non-q-tame persistent homology.
+We also conjecture that his other condition, for which he provides no proof, is correct and discuss possible proof strategies.
+\end{abstract}
 
-	\begin{lemma} \label{l: wilder}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
-		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$, then $\im r^n_{\widetilde K, M}$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
-		\end{itemize}
-		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
-	\end{lemma}
+\section{Introduction}
+Nowadays, when thinking of Marston Morse's work, the first thing that comes to mind is the theory of critical points of his eponymous Morse functions, as presented e.g.\@ in Milnor's famous book \cite{MR0163331}, with a key result being the Morse inequalities for the number of critical points of a function.
+In the 1930s, however, Morse published a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established a much more general theory of critical points and Morse inequalities for not even necessarily continuous functions on metric spaces.
+He termed this general theory Functional Topology because his goal was to use it to study critical points of functionals by topological means.
+In particular, he was interested in existence results for unstable minimal surfaces, i.e., critical points of the area functional for a given boundary curve that are not minimizers of area \cite{Morse.1939,Morse.1941}.
+This work with Tompkins was building on the work of Douglas who solved the general version of Plateau's Problem \cite{Douglas.1931}.
 
-	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im r^n_{U_K \cap Y, M}$ is finite.
+The approach of Morse and Tompkins in \cite{Morse.1939} was to give a topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
+For a more detailed review of their work we refer to \cite{Struwe.1988}.
+In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.g.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation." More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
 
-		Recall the following fact:
-		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
+By now, however, Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in a different context, namely topological data analysis.
+More specifically, Morse studies how the homology of the sublevel sets of a function change as the level changes.
+He defines spaces that encode the same information as the modern persistent homology groups, as well as quantities that correspond to the modern notions of birth and death.
+Eventhough he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
 
-		The collection $\sigma$ is not empty, in fact, it contains a compact neighborhood of any $y \in Y$.
-This follows from taking $V = X$ in $(r_\bullet^n)$ and using $(\ast)$ on the resulting open neighborhood.
+To achieve semi-continuity, Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
+This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
+To achieve q-tameness, Morse wants to use the following condition, given e.g.\@ in \cite{Morse.1940}.
 
-		Notice that the collection $\sigma$ is closed under intersections.
-In fact, a stronger statement holds: if $K_1$ is compact and $K_2 \in \sigma$ then $K_1 \cap K_2 \in \sigma$.
-This is a consequence of the fact that the image of a map is finite can be deduced from that property holding for any map that factors it.
-We will next show that $\sigma$ is also closed under finite unions.
+\begin{defi}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+The space $M$ is called \emph{locally-$f$-connected} if for each $p\in M$, $e>0$ and $d\in\mathbb{N}_0$ there exists $\delta\in(0,e)$ such that the map
+\[
+\tilde{H}_d(f_{\leq f(p)+\delta}\cap B_{\delta}(p)\hookrightarrow f_{\leq f(p)+e}\cap B_e(p);\mathbb{Z})
+\]
+is 0.
+\end{defi}
 
-		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
-		\begin{equation*}
-		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
-		\end{equation*}
-		where $\im r^n_{U_i \cap Y, M}$ is finite. 
-		We can construct such compact neighborhoods using $(\ast)$ as follows:
+Here, $\tilde{H}_{d}$ denotes reduced $d$-dimensional singular homology, $f_{\leq t}$ denotes the sublevel set of $f$ at $t\in\mathbb{R}$, and $B_{\delta}(p)$ denotes the open ball with radius $\delta$ around the point $p$.
+Morse then states the claim below as \cite[Theorem 6.3]{Morse.1940}.
 
-		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
-The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$.
-Let $\{p_i^{1}, \dots, p^{n}_i\} \subseteq K_i$ be such that $K_i \subseteq \bigcup_{j=1}^n \interior K^\dprime_i(p^j_i)$.
-Define $K_i^\dag = \bigcup_{j=1}^n K^\dag_i(p^j_i)$ for $i \in \{1,2\}$ and $\dag \in \{\prime, \dprime\}$.
+\begin{claim}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is locally-$f$-connected and all sublevel sets are compact.
+Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
+\end{claim}
 
-		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior_Y(K_1^\prime \cap K_2^\prime \cap Y)$.
-To see this consider $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$.
-By construction for $i \in \{1, 2\}$ there exist open sets $V_i \subseteq K_i^\prime$ such that $p \in V_i$.
-Letting $V = V_1 \cap V_2$ we have $p \in V \cap Y \subseteq K^\dprime_1 \cap K^\dprime_2 \cap Y$ implying $p \in \interior_Y(K^\dprime_1 \cap K^\dprime_2 \cap Y)$.
+Here, $\CH_{d}$ denotes $d$-dimensional Vietoris or \v{C}ech homology and $f_{\leq\bullet}$ denotes the sublevel set filtration of $f$.
+He does not prove the statement in the above reference, but cites \cite[Theorem 6.1]{Morse.1938}.
+There, Morse presents a supposed proof of the claim by constructing finite bases for the sets $\im \CH_d(f_{\leq s}\hookrightarrow f_{\leq t};\mathbb{F})$.
+As it turns out, the proof is not correct: We present a counterexample to the claim.
 
-		Using $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
-		\begin{equation*}
-		\begin{tikzcd}
-		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
-		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
-		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
-		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
-		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
-		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
-		\end{tikzcd}
-		\end{equation*}
-		The upper right square has finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is finite.
-The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $\widetilde K_1^\prime \cup \widetilde K_2^\prime$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
+\begin{thm}\label{thm:counterexample}
+For any $d$, there exists a funtion $F\colon \mathbb{H}^{d}\to\mathbb{R}$ on the $d$-dimensional Hawaiian earring $\mathbb{H}^{d}$ such that $\mathbb{H}^{d}$ is locally-$F$-connected, all sublevel sets are compact and $\CH_d(F_{\leq\bullet};\mathbb{F})$ is not q-tame for any field $\mathbb{F}$.
+\end{thm}
 
-		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
-		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
-Here we are using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
-Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = K \cap C \cup K \cap D$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $D \in \sigma$ trivially.
+Recall that the $d$-dimensional Hawaiian earring is defined as the subspace
+\[
+\mathbb{H}^{d}=\bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
+\]
+of $d+1$-dimensional Euclidean space.
+
+In \cite{Morse.1937}, Morse gives a slightly stronger definition of local-$f$-connectedness, which we will define under a different name to distinguish it from the weaker notion.
+
+\begin{defi}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+The space $M$ is called \emph{strongly locally-$f$-connected} if for each $p\in M$, $e>0$ and $d\in\mathbb{N}_0$ there exists $\delta\in(0,e)$ such that for all $c\geq f(p)$ the map
+\[
+\tilde{H}_d(f_{\leq c+\delta}\cap B_{\delta}(p)\hookrightarrow f_{\leq c+e}\cap B_e(p);\mathbb{Z})
+\]
+is 0.
+\end{defi}
+
+Clearly, strong local-$f$-connectedness implies local-$f$-connectedness.
+Morse also presents the following claim as \cite[Theorem 9.2]{Morse.1937}, but states immediately thereafter that the proof "while not difficult involves too great detail to be presented here".
+
+\begin{claim}\label{con:q-tame_pers_cech_hom}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is strongly locally-$f$-connected and all sublevel sets are compact.
+Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
+\end{claim}
+
+While we are currently unable to present a proof, we conjecture the claim to be true.
+
+\todo{what does the story look like for cohomology?}
+
+\subsection*{Notation and Conventions}
+For the rest of the paper, we let $\mathbb{F}$ be a field and whenever we write homology without explicit mention of coefficients, we mean homology with coefficients in $\mathbb{F}$.
+
+\section{Proof of the Main Theorem}
+
+\begin{proof}[Proof of \cref{thm:counterexample}]
+Define $F\colon\mathbb{H}^{d}\to\mathbb{R}$ as $0$ at the origin and $1$ everywhere else.
+All sublevel sets are either singletons or the whole space $\mathbb{H}^{d}$ and consequently compact.
+Moreover, $\mathbb{H}^{d}$ is locally-$F$-connected:
+
+Let $e>0$ and $p\in M$. If $p$ is the origin, we choose $\delta$ between 0 and $\min\{e,1\}$. Then $F_{\leq F(p)+\delta}=F_{\leq\delta}=\{p\}$, so we have 
+\[
+\tilde{H}_n(F_{\leq F(p)+\delta}\cap B_{\delta}(p)\hookrightarrow F_{\leq F(p)+e}\cap B_e(p);\mathbb{Z})=\tilde{H}_n(\{p\}\hookrightarrow F_{\leq F(p)+e}\cap B_e(p);\mathbb{Z})=0,
+\]
+where the last map is trivial because $\tilde{H}_{n}(\{p\};\mathbb{Z})$ is trivial for any $n$.
+For $p$ not the origin, there is a unique $d$-sphere in $\mathbb{H}^{d}$ that $p$ lies on.
+Clearly, we may choose $\delta$ so small that $B_{\delta}(p)$ is a disc on this circle, so that $B_{\delta}(p)$ is in particular contractible.
+We have $F_{\leq F(p)+\delta}=F_{\leq F(p)+e}=\mathbb{H}^{d}$, so
+\[
+\tilde{H}_n(F_{\leq F(p)+\delta}\cap B_{\delta}(p)\hookrightarrow F_{\leq F(p)+e}\cap B_e(p);\mathbb{Z})=\tilde{H}_n(B_{\delta}(p)\hookrightarrow B_e(p);\mathbb{Z})=0,
+\]
+where the last map is trivial for any $n$ because we chose $\delta$ such that $B_{\delta}(p)$ is contractible.
+
+What remains to be shown is that $\CH_d(F_{\leq\bullet})$ is not q-tame.
+Note that $\CH_d(F_{\leq\bullet})$ is constant with value $\CH_{d}(\mathbb{H}^{d})$ from some index onward, so it suffices to show that this vector space is infinite dimensional.
+This can be computed by using the fact that \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces:
+
+Define 
+\begin{align*}
+\mathbb{H}^{d}_k&=\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
+&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+\end{align*}
+i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+We have $\lim_{k}\mathbb{H}^{d}_{k}=\bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\mathbb{H}^{d})=\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
+One can easily check that each $\mathbb{H}^{d}_{k}$ satisfies the assumptions for \cref{prop:cech_sing_hom_hlc}, which implies $\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim_{k}H_{d}(\mathbb{H}^{d}_{k})$.
+We compute
+\[
+\lim_{k}H_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+\]
+which is infiite-dimensional over $\mathbb{F}$. This finishes the proof.
 \end{proof}
 
-	We can now immediately prove the following result.
+\begin{rem}
+Note that the singular persistent homology of the sublevel set filtration of $F$ above is also not q-tame because the $d$-dimensional Hawaiian earring has infinite-dimensional $d$-th singular homology \cite{Barratt.1962}.
+\end{rem}
 
-	\begin{theorem}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{theorem}
+\begin{rem}
+The construction above does not yield a counterexample to \cref{con:q-tame_pers_cech_hom} because $\mathbb{H}^{d}$ is not strongly locally-$F$-connected at the origin.
+\end{rem}
 
+\section{Towards a Proof of the Main Conjecture}
+\subsection{Local Connectedness}
+To tackle our conjecture, we want to start by reviewing local connectedness conditions in a broader context.
+
+\begin{defi}\label{defi:local_connectedness}
+Let $\mathcal{C}$ be a category with $0$ object and let $A\colon\mathbf{Top}\to\mathcal{C}$ be a functor.
+We say that a topological space $X$ is \emph{locally connected with respect to $A$} if for each point $p\in X$ and every open neighborhood $V$ of $p$ there is an open neighborhood $U\subseteq V$ of $p$ such that the map $A(U\hookrightarrow V)$ factors through 0.
+
+$X$ is called an \emph{$HLC^{\infty}$-space} if it is locally connected with respect to $\tilde{H}_*(-;\mathbb{Z})$.
+Other choices $G$ of coefficient groups will be denoted by a subscript, i.e., we say that $X$ is an \emph{$HLC^{\infty}_G$-space} if it is locally connected with respect to $\tilde{H}_*(-;G)$.
+\end{defi}
+
+\begin{ex}
+For any $d$, the $d$-dimensional Hawaiian earring is not $HLC^{\infty}$.
+However, if we consider $\mathbb{H}^{d}$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d<d'$, then $\mathbb{H}^{d}$ is $HLC^{\infty}$ in $\mathbb{H}^{d'}$.
+\end{ex}
+
+Local connectedness assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional, see \cite{MR0007094} for early examples.
+For us, the following is relevant.
+
+\begin{prop}[{\cite{MR105677, MR1481706}}]\label{prop:cech_sing_hom_hlc}
+On the category of paracompact $HLC^{\infty}$ Hausdorff spaces, \v{C}ech and singular homology with arbitrary coefficients coincide.
+\end{prop}
+
+We also get a persistent version by applying the above pointwise.
+
+\begin{cor}\label{cor:cech_sing_persistent_iso}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a paracompact $HLC^\infty$-space for each $c\in\mathbb{R}$.
+Then $\CH_d(f_{\leq\bullet})\cong H_d(f_{\leq\bullet})$ for any $d$.
+\end{cor}
+
+For more results of this type, we refer to \cite{MR1481706}.
+There, the above result \cite[Corollary VI.12.6]{MR1481706} and many similar ones are shown using sheaf theoretic methods.
+For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
+Using Bredon's results, we also get the following.
+
+\begin{prop}\label{prop:fin_dim_sing_hom}
+Let $X$ be compact Hausdorff and $HLC^{\infty}$. Then $H_d(X;\mathbb{F})$ is finite-dimensional for all $d$ and any field $\mathbb{F}$.
+\end{prop}
 \begin{proof}
-		Using the notation of Lemma \ref{l: wilder}, this would follow from $(r_n)$ applied to the case $K = Y$ and $M = X$.
-To show $(r_n)$ holds for every $n \geq 0$ we proceed by induction noticing that by assumption we have $(r^n_\bullet)$ for every $n$.
-	\end{proof}
-\end{document}
-
-\begin{lemma}
-	Let $Y \subseteq X$ be a pair of compact Hausdorff spaces, then $(r^0)$ above holds. 
-\end{lemma}
-
-\begin{proof}
-	Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$.
-For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite.
-Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
-Since
-	\begin{equation*}
-	\begin{tikzcd}
-	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
-	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
-	\end{tikzcd}
-	\end{equation*}
-	commutes, we have the desired conclusion.
-	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
+By the universal coefficient theorem for homology, trivial singular homology with integer coefficients also implies trivial singular homology for any other coefficient group.
+In particular, this means that $X$ being $HLC^{\infty}$ also implies that $X$ is $HLC^{\infty}_{\mathbb{F}}$.
+By the universal coefficient theorem for cohomology, the singular cohomology with coefficients in $\mathbb{F}$ is naturally isomorphic to the dual space of the singular homology with coefficients in $\mathbb{F}$.
+This means that being $HLC^{\infty}_{\mathbb{F}}$ implies being locally connected with respect to singular cohomology in all degrees with coefficients in $\mathbb{F}$.
+Since we assume $X$ to be $HLC^{\infty}$, \cite[Theorem III.1.1]{MR1481706} now implies that $X$ is locally connected with respect to sheaf cohomology with coefficients in the locally constant sheaf with value $\mathbb{F}$.
+\cite[Corollary II.17.7]{MR1481706} implies that the sheaf cohomology of the whole space with coefficients in this sheaf is finite-dimensional, so again by \cite[Theorem III.1.1]{MR1481706} the same holds for singular cohomology with coefficients in $\mathbb{F}$.
+Applying the universal coefficient theorem once more proves the claim.
 \end{proof}
 
-\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
-Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
-The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
-Furthermore, locally $H_1 = 0$.
-Taking $Y = X$ gives a counterexample.
+Again, we get a persistent version.
 
-\begin{equation*}
-\begin{tikzpicture}[scale=5]
-\foreach \i in {0,1,2,...,12}{
-	\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
-}
-\end{tikzpicture}
-\end{equation*}
+\begin{cor}
+Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a compact Hausdorff $HLC^\infty$-space for each $c\in\mathbb{R}$.
+Then $H_d(f_{\leq\bullet})$ is p.f.d.
+for any $d$.
+\end{cor}
 
-A diagram to keep in mind
-\begin{equation}
+\subsection{Two Alternative Conjectures}
+In order to relate Morse's conditions to the above, we need a relative version of the $HLC^{\infty}$ condition.
+
+\begin{defi}\label{defi:hlc}
+Let $\mathcal{C}$ be a category with $0$ object and let $A\colon\mathbf{Top}\to\mathcal{C}$ be a functor.
+If $Y\subseteq X$ is a pair of topological spaces, we say that $Y$ is \emph{locally connected with respect to $A$ in $X$} if for each point $p\in Y$ and any open neighborhood $V$ of $p$ in $X$ there is an open neighborhood $U\subseteq V$ of $p$ such that $A(U\cap Y\hookrightarrow V)$ factors through 0.
+
+We say that $Y$ is \emph{$HLC^{\infty}$ in $X$} if it is locally connected with respect to $\tilde{H}_*(-;\mathbb{Z})$ in $X$.
+\end{defi}
+
+We get the following rephrasing of strong local-$f$-connectedness.
+
+\begin{prop}
+Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function. Then $M$ is strongly locally-$f$-connected if and only if $f_{\leq s}$ is $HLC^{\infty}$ in $f_{\leq t}$ whenever $s<t$.
+\end{prop}
+\begin{proof}
+If each sublevel set is $HLC^{\infty}$ in larger sublevel sets, $M$ is clearly strongly locally-$f$-connected.
+For the converse direction, fix $s<t$ and choose some point $p\in f_{\leq s}$ with a neighborhood $V$ of $p$ in $f_{\leq t}$.
+We may choose $e\in(0, t-s)$ such that $B_e(p)\cap f_{\leq t}\subseteq V$.
+By strong local-$f$-connectedness, for each $d$ there is some $\delta\in(0,e)$ such that the map in reduced $d$-dimensional homology induced by $B_{\delta}(p)\cap f_{\leq s}\hookrightarrow B_e(p)\cap f_{\leq t}$ is trivial.
+The map $B_{\delta}(p)\cap f_{\leq s}\hookrightarrow V$ factors through the aforementioned map, so it is trivial in reduced homology, too.
+Thus, $f_{\leq s}$ is $HLC^{\infty}$ in $f_{\leq t}$.
+\end{proof}
+
+Note that the proposition gives a purely topological description of strong local-$f$-connectedness, so we can also use it to define strong local-$f$-connectedness for spaces that are not metrizable.
+It also yields the following corollary.
+
+\begin{cor}
+Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function. If all sublevel sets are $HLC^{\infty}$, then $M$ is strongly locally-$f$-connected.
+\end{cor}
+
+We now propose the following generalization of \cref{prop:fin_dim_sing_hom}.
+
+\begin{conj}\label{conj:q-tame_singular}
+Let $Y\subseteq X$ be compact Hausdorff spaces such that $Y$ is $HLC^{\infty}$ in $X$. Then $\im H_d(Y\hookrightarrow X)$ is finite-dimensional for all $d$.
+\end{conj}
+
+As a persistent version, we have the following obvious consequence.
+
+\begin{prop}\label{prop:q-tame_singular}
+Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that $M$ is strongly locally-$f$-connected, i.e., each sublevel set is $HLC^{\infty}$ in all larger sublevel sets.
+If \cref{conj:q-tame_singular} is true, then $H_{d}(f_{\leq\bullet})$ is q-tame for all $d$.
+\end{prop}
+
+In a similar spirit, we also propose the following conjecture as an analogue to \cref{cor:cech_sing_persistent_iso}.
+
+\begin{conj}\label{con:d_I_0_sing_cech}
+Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that all sublevel sets are paracompact Hausdorff.
+If $M$ is strongly locally-$f$-connected, i.e., each sublevel set is $HLC^{\infty}$ in all larger sublevel sets, then
+\[
+d_I(H_d(f_{\leq\bullet}),\CH_d(f_{\leq\bullet}))=0
+\]
+for all $d$.
+\end{conj}
+
+Here, $d_{I}$ denotes the interleaving distance between persistence modules. The conjecture is relevant because of the following criterion for q-tameness.
+
+\begin{prop}
+Let $M$ and $N$ be persistence modules such that $M$ is q-tame and assume $d_I(M,N)=0$. Then $N$ is q-tame.
+\end{prop}
+\begin{proof}
+Pick indices $s<t$. Because $d_I(M,N)=0$, we may choose a $\delta$-interleaving with $\delta\in\left(0,\frac{t-s}{2}\right)$. Then we have a commutative diagram
+
+\[
 \begin{tikzcd}
-\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
-\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
+N_s\arrow[rrr]\arrow[rd]&&&N_{t}\\
+&M_{s+\delta}\arrow[r]&M_{t-\delta}\arrow[ru]&
 \end{tikzcd}
-\end{equation}
+\]
+so that the rank of $N_s\to N_t$ is bounded above by the rank of $M_{s+\delta}\to M_{t-\delta}$. The rank of $M_{s+\delta}\to M_{t-\delta}$ is finite by assumption, so $N$ is q-tame.
+\end{proof}
 
-Consider the following general diagram
-\begin{equation}
-\begin{tikzcd}
-A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
-X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
+Combining the previous result with \cref{prop:q-tame_singular}, we get the following.
+
+\begin{cor}
+If \cref{conj:q-tame_singular,con:d_I_0_sing_cech} are true, then so is \cref{con:q-tame_pers_cech_hom}.
+\end{cor}
+
+Thus, we have reduced our main conjecture to two smaller ones.
+
+A possible proof strategy for \cref{conj:q-tame_singular} might be to adapt the proof strategy of Wilder's Finiteness Theorem, which is an analogue of \cref{prop:fin_dim_sing_hom} for sheaf cohomology, from \cite[Section II.17]{MR1481706}.
+Essentially the same proof also appears in \cite[Section III.10]{MR842190}.
+
+A possible proof strategy for \cref{con:d_I_0_sing_cech} might be to adapt Bredon's proof of \cref{prop:cech_sing_hom_hlc} using his spectral sequence that relates \v{C}ech and singular homology.
+
+\subsection{Q-Tameness of Persistent \v{C}ech Homology via Cosheaf Homology}\label{sec:cosheaf}
+Note that what follows is rather informal and speculative.
+
+When working with cohomology, the usual modern way to relate the singular and the \v{C}ech theory is via an intermediate step in the form of sheaf cohomology and then use the Leray and Grothendieck spectral sequences \cite[Chapter III]{MR1481706}.
+One might hope to use similar cosheaf theoretic methods, such as a possible theory of cosheaf homology, to obtain similar results for homology.
+So far, treatments of cosheaf homology are sparse.
+Among them are \cite{Andreotti.1973}, \cite{Schneiders.1987} and \cite{prasolov2018cosheaves}, but we are presently unable to determine whether the techniques in these texts can be adapted to our problems.
+Bredon, in \cite{Bredon.1968} and \cite[Chapter VI]{MR1481706}, also defines \v{C}ech homology with coefficients in a precosheaf and compares it to the singular theory for paracompact $HLC^{\infty}$-spaces \cite[Section VI.4 and Theorem VI.12.6]{MR1481706} using cosheaf theoretic methods.
+All of his results are still absolute comparison and finiteness results, i.e., they work for a single space $X$, so another obstacle, besides cosheaf homology being underdeveloped, is our desired generalization to subspaces $Y\subseteq X$ that are only $HLC^{\infty}$ in $X$ but not in themselves.
+That cosheaves might also help in overcoming this problem is suggested by the very nice formulation of the $HLC^{\infty}$ property in terms of precosheaves.
+The following definition appears in \cite{MR1481706}.
+
+\begin{defi}
+Let $\mathfrak{A}$ be a precosheaf on a space $X$ with values in a category with 0 object, i.e., a covariant functor on the poset category of open sets in $X$.
+We call $\mathfrak{A}$ \emph{locally trivial} if for all points $x\in X$ and all open neighborhoods $V$ of $x$ there is another open neighborhood $U\subseteq V$ of $x$ such that $\mathfrak{A}(U)\to\mathfrak{A}(V)$ factors through 0.
+\end{defi}
+
+The following definition is, up to our use of reduced homology, taken from \cite{Curry.2015}.
+
+\begin{defi}
+For any topological space $X$, we define the \emph{reduced Leray precosheaf} $\mathfrak{L}_X$ on $X$ as the precosheaf mapping $U\mapsto \tilde{H}_*(U;\mathbb{Z})$.
+\end{defi}
+
+\begin{defi}
+If $f\colon Y\to X$ is a continuous map between topological spaces and $\mathfrak{A}$ is a precosheaf on $Y$, we define the \emph{pushforward of $\mathfrak{A}$ along $f$} as the precosheaf on $X$ mapping $U\mapsto\mathfrak{A}(f^{-1}(U))$.
+We denote it by $f_*\mathfrak{A}$.
+\end{defi}
+
+Now if $Y\subseteq X$ are topological spaces, we get an obvious morphism $i_*\mathfrak{L}_Y\to\mathfrak{L}_X$ of precosheaves on $X$, where $i\colon Y\hookrightarrow X$ is the inclusion, given by $\tilde{H}_*(U\cap Y\hookrightarrow U;\mathbb{Z})$.
+Note that the category of precosheaves with values in abelian groups is just a functor category from a small category to an abelian category.
+In particular, it has images given "pointwise".
+We get the following rephrasing of the relative $HLC^{\infty}$ property.
+
+\begin{prop}
+Let $Y\subseteq X$ be topological spaces. Then $Y$ is $HLC^{\infty}$ in $X$ if and only if $\im(i_*\mathfrak{L}_Y\to\mathfrak{L}_X)$ is locally trivial.
+\end{prop}
+
+Our hope is that one might be able to use this characterization in the future to prove the previously made conjectures.
+
+\todo{Given $f\colon M\to\mathbb{R}$, is there a way of finding a single space (e.g.
+M itself, disjoint union of sublevel sets, colim of sublevel sets, hocolim of sublevel sets, continuously indexed mapping telescope (how to construct this?) of inclusions of sublevel sets, etc.) and a precosheaf with values in a category of persistence module (maybe the observable category) on that space such that $M$ is locally-$f$-connected iff that precosheaf is locally trivial?}
+
+\section*{Acknowledgements}
+This research has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}, the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
+
+\bibliographystyle{abbrvnaturl}
+\bibliography{biblio}
+
+\todos
+\end{document}

### 2021-03-25 theorem.tex
Add previous work

\documentclass{amsart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{tikz-cd}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\HS}{\mathrm{HS}}
\newcommand{\dprime}{{\prime\prime}}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\interior}{int}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-1.4in}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-1.8in}
\calclayout

\newcommand{\p}{\mathrm{p}}
\newcommand{\q}{\mathrm{q}}

\begin{document}

\begin{definition}
	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ---denoted $\HS_n$--- if the image of the map induced by $H_n(-)$ is finitely generated, and we say it is \textit{homologically small}, denoted $\HS$, if it is $\HS_n$ for every~$n$.
\end{definition}

\begin{definition}
	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
	\begin{equation*}
	X_{\leq t} = f^{-1}((-\infty, t]).
	\end{equation*}
\end{definition}

\begin{definition}
	Let $M$ be a metric space. For any $p \in M$ and $\epsilon \geq 0$ denote
	\begin{equation*}
	B_\epsilon(p) = \{q \in M\ |\ d(p,q) < \epsilon\}, \qquad
	\overline B_\epsilon(p) = \{q \in M\ |\ d(p,q) \leq \epsilon\}.
	\end{equation*}
\end{definition}

\begin{definition}
	Let $M$ be a metric space and $f \colon M \to \R$ a function.
	The space $M$ is said to be \textit{strongly locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the image of the map induced by $H_n(-)$ on $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $0$.
\end{definition}

\begin{theorem} \label{t:strong local connectenss implies q-tameness}
	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
\end{theorem}

\begin{lemma} \label{l:commutative algebra}
	Given a commutative diagram of modules over a principal ideal domain
	\begin{equation*}
	\begin{tikzcd}
	A_{1,1} \arrow[r] & A_{1,2} & \\
	A_{2,1} \arrow[r] \arrow[u] & A_{2,2} \arrow[r] \arrow[u] & A_{2,3} \\
	& A_{3,2} \arrow[r] \arrow[u] & A_{3,3} \arrow[u]
	\end{tikzcd}
	\end{equation*}
	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then $A_{3,2} \to A_{1,2}$ does as well.
\end{lemma}

\begin{lemma} \label{l:neighborhood third}
	Let $M$ be a metric space. For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
	\begin{equation*}
	K \subseteq \interior(K^\prime) \subseteq K^\prime \subseteq U.
	\end{equation*}
\end{lemma}

\begin{proof}
	For any $x \in K$ choose $\epsilon(x)$ such that $B_{\epsilon(x)}(x) \subseteq U$. We have
	\begin{equation*}
	B_{\frac{\epsilon(x)}{3}}(x) \subseteq \overline B_{\frac{\epsilon(x)}{2}}(x) \subseteq B_{\epsilon(x)}(x).
	\end{equation*}
	Since $K$ is compact, there exists a finite set $\{x_\lambda \in K\}_{\Lambda}$ such that $K \subseteq \bigcup_{\Lambda} B_{\frac{\epsilon(x_\lambda)}{3}}(x_\lambda)$. Defining $K^\prime = \bigcup_{\Lambda} \overline B_{\frac{\epsilon(x_\lambda)}{2}}(x_\lambda)$ finishes the proof.
\end{proof}

\begin{lemma} \label{l:key lemma for q-tameness}
	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
	For compact sets $K, L \subseteq M$ with $K \subseteq \interior(L)$ and $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
\end{lemma}

\begin{proof}
	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $H_{n-1}(-)$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.

	Given a compact set $L \subseteq M$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U_K$ of $K$ such that $U_K \cap M_{s+\delta_K} \to L \cap M_{t}$ is $\HS_n$.

	We start by showing that any point in $\interior(L) \cap M_s$ has a neighborhood in $\Sigma_{s, t}$.
	Let $x \in \interior(L) \cap M_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
	By the strong local-$f$-connectivity of $M$, there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ the following composition is $\HS$:
	\begin{equation*}
	\overline B_{\delta/2}(x) \cap M_{s + \delta} \to
	B_\delta(x) \cap M_{s + \delta} =
	B_\delta(x) \cap M_{f(x) + c + \delta} \to
	B_e(x) \cap M_{f(x) + c + e} \to
	L \cap M_{t}.
	\end{equation*}

	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap M_{s+\delta_i} \to L \cap M_{t}$ is $\HS_n$.
	We Use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
	\begin{equation*}
	K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime \subseteq U_i.
	\end{equation*}
	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap M_{s+\delta} \to L \cap M_t$ is $\HS_n$.
	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap M_s \to K_1^\prime \cap K_2^\prime \cap M_{s+\delta}$ is $\HS_{(n-1)}$.
	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:
	\begin{equation*}
	\begin{tikzcd}
	H_n(L \cap M_t) \oplus H_n(L \cap M_t) \arrow[r] &
	H_n(L \cap M_t) & \\
	H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus H_n(K_2^\prime \cap M_{s+\delta}) \arrow[r] \arrow[u] & 
	H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[r] \arrow[u] &
	H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) \\ & 
	H_{n}((K_1 \cup K_2) \cap M_s) \arrow[r] \arrow[u] &
	H_{n-1}(K_1 \cap K_2 \cap M_s). \arrow[u]
	\end{tikzcd}
	\end{equation*}
	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
	Since any $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
\end{proof}

\begin{proof}[Proof of Theorem \ref{t:strong local connectenss implies q-tameness}]
	Given $s < t$ consider the compact metric space $N = M_{\leq t}$ and apply Lemma~\ref{l:key lemma for q-tameness} inside $N$ to $L = N$ and $K = M_{\leq s}$ deducing the desired conclusion.
\end{proof}

\end{document}

### 2021-03-30 theorem.tex
Add corrected proof of the theorem
typo

@@
 	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
-	For compact sets $K, L \subseteq M$ with $K \subseteq \interior(L)$ and $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
+	Consider sets $K, L \subseteq M$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
 \end{lemma}
@@
 	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
-	Since any $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
+	Since any compact $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem \ref{t:strong local connectenss implies q-tameness}]
-	Given $s < t$ consider the compact metric space $N = M_{\leq t}$ and apply Lemma~\ref{l:key lemma for q-tameness} inside $N$ to $L = N$ and $K = M_{\leq s}$ deducing the desired conclusion.
+	 It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = M_{\leq s}$ and $L = M$.
 \end{proof}

### 2021-03-30 connectivity.tex
Split sections

--- 2021-02-24 main.tex
@@
-\documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{tikz-cd}
+\section{Local connectivity}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
+\begin{defi} \label{defi:local_connectedness}
+	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or \textit{trivial}, denoted $\HS_n$ and $\HT_n$ respectively, if the image of the map induced by $\tilde H_n(-)$ is finitely generated or 0, and we say it is \textit{homologically small} or \textit{trivial}, denoted respectively $\HS$ and $\HT$, if it is $\HS_n$ or $\HT_n$ for every~$n$.
 
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\dprime}{{\prime\prime}}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
+	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
+\end{defi}
 
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
+\anibal{Use a different example, $\H$ not yet defined.}
+\begin{ex}
+	For any $d$, the $d$-dimensional Hawaiian earring is not $\HLC$.
+However, if we consider $\H$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d < d'$, then $\H$ is $\HLC$ in $\mathbb{H}^{d'}$.
+\end{ex}
 
-\begin{document}	
-	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+\begin{defi}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function.
+	The space $M$ is said to be \textit{locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the inclusion $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $\HT$.
+\end{defi}
 
-	The following is a modification of a theorem of Wilder.
+Local connectedness assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional, see \cite{MR0007094} for early examples.
+For us, the following is relevant.
 
-	\begin{lemma} \label{l: wilder}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
-		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $K \cap Y \subset \interior_Y(M \cap Y)$, then $\im H_n\left(K \cap Y \to M\right)$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$, then there exist $U$ an open neighborhood of $y$ contained in $V$ such that $\im H_n\left(U \cap Y \to V\right)$ is finite.
-		\end{itemize}
-		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
-	\end{lemma}
+\begin{prop}[{\cite{MR105677, MR1481706}}]\label{prop:cech_sing_hom_hlc}
+	On the category of paracompact Hausdorff $\HLC$ spaces, \v{C}ech and singular homology with arbitrary coefficients coincide.
+\end{prop}
+
+We also get a persistent version by applying the above pointwise.
+
+\begin{cor}\label{cor:cech_sing_persistent_iso}
+	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a paracompact $HLC^\infty$-space for each $c\in\mathbb{R}$.
+Then $\CH_d(f_{\leq\bullet})\cong H_d(f_{\leq\bullet})$ for any $d$.
+\end{cor}
+
+For more results of this type, we refer to \cite{MR1481706}.
+There, the above result \cite[Corollary VI.12.6]{MR1481706} and many similar ones are shown using sheaf theoretic methods.
+For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
+Using Bredon's results, we also get the following.
+
+\begin{prop}\label{prop:fin_dim_sing_hom}
+	Let $X$ be compact Hausdorff and $HLC^{\infty}$. Then $H_d(X;\mathbb{F})$ is finite-dimensional for all $d$ and any field $\mathbb{F}$.
+\end{prop}
 
 \begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im H_n\left(U_K \cap Y \to M\right)$ is finite.
-
-		Recall the following fact:
-		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
-
-		The collection $\sigma$ is not empty, in fact, it contains a compact neighborhood of any $y \in Y$.
-This follows from taking $V = X$ in $(r_\bullet^n)$ and using $(\ast)$ on the resulting open neighborhood.
-
-		Notice that the collection $\sigma$ is closed under intersections.
-In fact, a stronger statement holds: if $K_1$ is compact and $K_2 \in \sigma$ then $K_1 \cap K_2 \in \sigma$.
-This is a consequence of the fact that the image of a map is finite can be deduced from that property holding for any map that factors it.
-We will next show that $\sigma$ is also closed under finite unions.
-
-		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
-		\begin{equation*}
-		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
-		\end{equation*}
-		where $\im H_n\left(U_i \cap Y \to M\right)$ is finite. 
-		We can construct such compact neighborhoods using $(\ast)$ as follows:
-
-		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
-The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$.
-Let $\{p_i^{1}, \dots, p^{n}_i\} \subseteq K_i$ be such that $K_i \subseteq \bigcup_{j=1}^n \interior K^\dprime_i(p^j_i)$.
-Define $K_i^\dag = \bigcup_{j=1}^n K^\dag_i(p^j_i)$ for $i \in \{1,2\}$ and $\dag \in \{\prime, \dprime\}$.
-
-		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior_Y(K_1^\prime \cap K_2^\prime \cap Y)$.
-To see this consider $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$.
-By construction for $i \in \{1, 2\}$ there exist open sets $V_i \subseteq K_i^\prime$ such that $p \in V_i$.
-Letting $V = V_1 \cap V_2$ we have $p \in V \cap Y \subseteq K^\dprime_1 \cap K^\dprime_2 \cap Y$ implying $p \in \interior_Y(K^\dprime_1 \cap K^\dprime_2 \cap Y)$.
-
-		\begin{equation*}
-		\begin{tikzcd}
-		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
-		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
-		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
-		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
-		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
-		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
-		\end{tikzcd}
-		\end{equation*}
-
-		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$.
-The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
-
-		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
-		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
-This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
-Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
+	By the universal coefficient theorem for homology, trivial singular homology with integer coefficients also implies trivial singular homology for any other coefficient group.
+In particular, this means that $X$ being $HLC^{\infty}$ also implies that $X$ is $HLC^{\infty}_{\mathbb{F}}$.
+By the universal coefficient theorem for cohomology, the singular cohomology with coefficients in $\mathbb{F}$ is naturally isomorphic to the dual space of the singular homology with coefficients in $\mathbb{F}$.
+This means that being $HLC^{\infty}_{\mathbb{F}}$ implies being locally connected with respect to singular cohomology in all degrees with coefficients in $\mathbb{F}$.
+Since we assume $X$ to be $HLC^{\infty}$, \cite[Theorem III.1.1]{MR1481706} now implies that $X$ is locally connected with respect to sheaf cohomology with coefficients in the locally constant sheaf with value $\mathbb{F}$.
+\cite[Corollary II.17.7]{MR1481706} implies that the sheaf cohomology of the whole space with coefficients in this sheaf is finite-dimensional, so again by \cite[Theorem III.1.1]{MR1481706} the same holds for singular cohomology with coefficients in $\mathbb{F}$.
+Applying the universal coefficient theorem once more proves the claim.
 \end{proof}
 
-	We can now immediately prove the following result.
+Again, we get a persistent version.
 
-	\begin{theorem}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{theorem}
-
-	\begin{proof}
-		Using the notation of Lemma \ref{l: wilder}, this would follow from $(r_n)$ applied to the case $K = Y$ and $M = X$.
-To show $(r_n)$ holds for every $n \geq 0$ we proceed by induction noticing that by assumption we have $(r^n_\bullet)$ for every $n$.
-	\end{proof}
-\end{document}
-
-\begin{lemma}
-	Let $Y \subseteq X$ be a pair of compact Hausdorff spaces, then $(r^0)$ above holds. 
-\end{lemma}
-
-\begin{proof}
-	Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$.
-For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite.
-Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
-Since
-	\begin{equation*}
-	\begin{tikzcd}
-	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
-	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
-	\end{tikzcd}
-	\end{equation*}
-	commutes, we have the desired conclusion.
-	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
-\end{proof}
-
-\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
-Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
-The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
-Furthermore, locally $H_1 = 0$.
-Taking $Y = X$ gives a counterexample.
-
-\begin{equation*}
-\begin{tikzpicture}[scale=5]
-\foreach \i in {0,1,2,...,12}{
-	\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
-}
-\end{tikzpicture}
-\end{equation*}
-
-A diagram to keep in mind
-\begin{equation}
-\begin{tikzcd}
-\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
-\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
-
-Consider the following general diagram
-\begin{equation}
-\begin{tikzcd}
-A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
-X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
+\begin{cor}
+	Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a compact Hausdorff $HLC^\infty$-space for each $c\in\mathbb{R}$.
+Then $H_d(f_{\leq\bullet})$ is p.f.d.
+for any $d$.
+\end{cor}

### 2021-03-30 counterexample.tex
Split sections

@@
-\documentclass[10pt]{beamer}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{tikz}
+\section{Counterexample}
 
-\newcommand{\im}{\mathrm{im}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=.77\textheight]{hawaiian_earring}
+	\hfill
+	\caption{TBW}
+	\label{fig:earrings}
+\end{figure}
 
-\begin{document}
-\begin{frame}{Local to global}
-	\begin{block}{Statement}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{block}
-	\pause
-	\begin{block}{Counterexample}
-		Take $X = Y = $ suspension of $\left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
-		\vspace*{.3cm}
+In this section we show that weak local-$f$-connectivity is not sufficient to ensure q-tameness and, in the next, that local-$f$-connectivity is.
 
-		\begin{tikzpicture}[scale=5]
-		\foreach \i in {0,1,2,...,12}{
-			\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
-		}
-		\end{tikzpicture}
-	\end{block}
-	\vspace*{-1cm}
-\end{frame}
-\end{document}
+The $d$-dimensional Hawaiian earring is defined as the subspace
+\begin{equation*}
+\H = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
+\end{equation*}
+of $d+1$-dimensional Euclidean space.
+Let $f \colon \mathbb{H}^{d}\to\mathbb{R}$ as $0$ at the origin $\vec{0}$ and $1$ everywhere else.
+All sublevel sets $\H_{\leq t}$ are either the singleton $\{\vec{0}\}$ or the whole space $\H$, and therefore compact.
+Moreover, $\mathbb{H}^{d}$ is locally-$f$-connected as we prove now.
+
+Let $e > 0$ and $p \in \H$.
+If $p$ is the origin, we choose $\delta$ between 0 and $\min\{e,1\}$.
+Then $\H_{\leq f(p) + \delta} = \H_{\leq \delta} = \{p\}$, so the condition is trivially satisfied.
+For $p$ not the origin, there is a unique $d$-sphere that contains it.
+Clearly, we may choose $\delta$ so small that $B_{\delta}(p)$ contained in this sphere, so $B_{\delta}(p)$ is a disk and the condition follows trivially again.
+
+What remains to be shown is that $\H_{\leq \bullet}$ is not q-tame with respect to singular and \v{C}ech homology.
+Note that $\H_{\leq t}$ is constant with value $\H$ for $t \geq 1$, so it suffices to show that the singular and \v{C}ech homology of $\H$ with field coefficients is infinite dimensional.
+The case of singular homology is well know.
+For \v{C}ech homology we use the fact that it commutes with inverse limits for compact Hausdorff spaces.
+Define 
+\begin{align*}
+\mathbb{H}^{d}_k&=\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
+&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+\end{align*}
+i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+We have $\lim_{k}\mathbb{H}^{d}_{k}=\bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\mathbb{H}^{d}) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
+One can easily check that each $\mathbb{H}^{d}_{k}$ satisfies the assumptions for \cref{prop:cech_sing_hom_hlc}, which implies $\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim_{k}H_{d}(\mathbb{H}^{d}_{k})$.
+We compute
+\[
+\lim_{k}H_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+\]
+which is infinite-dimensional over $\mathbb{F}$.
+This finishes the proof.
+
+\begin{rem}
+Note that the singular persistent homology of the sublevel set filtration of $F$ above is also not q-tame because the $d$-dimensional Hawaiian earring has infinite-dimensional $d$-th singular homology \cite{Barratt.1962}.
+\end{rem}
+
+\begin{rem}
+The construction above does not yield a counterexample to \cref{con:q-tame_pers_cech_hom} because $\mathbb{H}^{d}$ is not strongly locally-$F$-connected at the origin.
+\end{rem}

### 2021-03-30 introduction.tex
Split sections

--- 2021-02-24 main.tex
@@
-\documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{tikz-cd}
+\section{Introduction}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
+\begin{itemize}
+	\item Persistence homology, 
+	\item applications in applied topology, application in theoretical topology, 
+	\item barcode, stability, existence of barcode motivates q-tameness. 
+	\item When can we ensure this condition? 
+	\item Morse as a precursor. Geodesic study, natural next context: minimal surfaces, \item proposed condition for q-tameness, it's wrong, 
+	\item a similar condition, assumed equivalent, we prove this implies it.
+	\item We expect this paper to help the ongoing development of persistence methods in geometry.
+\end{itemize}
 
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\dprime}{{\prime\prime}}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
+Nowadays, when thinking of Marston Morse's work, the first thing that comes to mind is the theory of critical points of his eponymous Morse functions, as presented e.g.\@ in Milnor's famous book \cite{MR0163331}, with a key result being the Morse inequalities for the number of critical points of a function.
+In the 1930s, however, Morse published a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established a much more general theory of critical points and Morse inequalities for not even necessarily continuous functions on metric spaces.
+He termed this general theory Functional Topology because his goal was to use it to study critical points of functionals by topological means.
+In particular, he was interested in existence results for unstable minimal surfaces, i.e., critical points of the area functional for a given boundary curve that are not minimizers of area \cite{Morse.1939,Morse.1941}.
+This work with Tompkins was building on the work of Douglas who solved the general version of Plateau's Problem \cite{Douglas.1931}.
 
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
+The approach of Morse and Tompkins in \cite{Morse.1939} was to give a topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
+For a more detailed review of their work we refer to \cite{Struwe.1988}.
+In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.gchoosing.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation." More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
 
-\begin{document}	
-	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
+By now, however, Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in a different context, namely topological data analysis.
+More specifically, Morse studies how the homology of the sublevel sets of a function change as the level changes.
+He defines spaces that encode the same information as the modern persistent homology groups, as well as quantities that correspond to the modern notions of birth and death.
+Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
 
-	The following is a modification of a theorem of Wilder.
+To achieve semi-continuity, Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
+This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
+To achieve q-tameness, Morse wants to use the following condition, given e.g.\@ in \cite{Morse.1940}.
 
-	\begin{lemma} \label{l: wilder}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
-		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $K \cap Y \subset \interior_Y(M \cap Y)$, then $\im H_n\left(K \cap Y \to M\right)$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$, then there exist $U$ an open neighborhood of $y$ contained in $V$ such that $\im H_n\left(U \cap Y \to V\right)$ is finite.
-		\end{itemize}
-		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
-	\end{lemma}
+\begin{defi}
+	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+The space $M$ is called \emph{locally-$f$-connected} if for each $p\in M$, $e>0$ and $d\in\mathbb{N}_0$ there exists $\delta\in(0,e)$ such that the map
+	\[
+	\tilde{H}_d(f_{\leq f(p)+\delta}\cap B_{\delta}(p)\hookrightarrow f_{\leq f(p)+e}\cap B_e(p);\mathbb{Z})
+	\]
+	is 0.
+\end{defi}
 
-	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im H_n\left(U_K \cap Y \to M\right)$ is finite.
+Here, $\tilde{H}_{d}$ denotes reduced $d$-dimensional singular homology, $f_{\leq t}$ denotes the sublevel set of $f$ at $t\in\mathbb{R}$, and $B_{\delta}(p)$ denotes the open ball with radius $\delta$ around the point $p$.
+Morse then states the claim below as \cite[Theorem 6.3]{Morse.1940}.
 
-		Recall the following fact:
-		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
+\begin{claim}
+	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is locally-$f$-connected and all sublevel sets are compact.
+Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
+\end{claim}
 
-		The collection $\sigma$ is not empty, in fact, it contains a compact neighborhood of any $y \in Y$.
-This follows from taking $V = X$ in $(r_\bullet^n)$ and using $(\ast)$ on the resulting open neighborhood.
+Here, $\CH_{d}$ denotes $d$-dimensional Vietoris or \v{C}ech homology and $f_{\leq\bullet}$ denotes the sublevel set filtration of $f$.
+He does not prove the statement in the above reference, but cites \cite[Theorem 6.1]{Morse.1938}.
+There, Morse presents a supposed proof of the claim by constructing finite bases for the sets $\im \CH_d(f_{\leq s}\hookrightarrow f_{\leq t};\mathbb{F})$.
+As it turns out, the proof is not correct: We present a counterexample to the claim.
 
-		Notice that the collection $\sigma$ is closed under intersections.
-In fact, a stronger statement holds: if $K_1$ is compact and $K_2 \in \sigma$ then $K_1 \cap K_2 \in \sigma$.
-This is a consequence of the fact that the image of a map is finite can be deduced from that property holding for any map that factors it.
-We will next show that $\sigma$ is also closed under finite unions.
+\begin{thm}\label{thm:counterexample}
+	For any $d$, there exists a funtion $F\colon \mathbb{H}^{d}\to\mathbb{R}$ on the $d$-dimensional Hawaiian earring $\mathbb{H}^{d}$ such that $\mathbb{H}^{d}$ is locally-$F$-connected, all sublevel sets are compact and $\CH_d(F_{\leq\bullet};\mathbb{F})$ is not q-tame for any field $\mathbb{F}$.
+\end{thm}
 
-		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
-		\begin{equation*}
-		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
-		\end{equation*}
-		where $\im H_n\left(U_i \cap Y \to M\right)$ is finite. 
-		We can construct such compact neighborhoods using $(\ast)$ as follows:
+Recall that the $d$-dimensional Hawaiian earring is defined as the subspace
+\[
+\mathbb{H}^{d}=\bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
+\]
+of $d+1$-dimensional Euclidean space.
 
-		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
-The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$.
-Let $\{p_i^{1}, \dots, p^{n}_i\} \subseteq K_i$ be such that $K_i \subseteq \bigcup_{j=1}^n \interior K^\dprime_i(p^j_i)$.
-Define $K_i^\dag = \bigcup_{j=1}^n K^\dag_i(p^j_i)$ for $i \in \{1,2\}$ and $\dag \in \{\prime, \dprime\}$.
+In \cite{Morse.1937}, Morse gives a slightly stronger definition of local-$f$-connectedness, which we will define under a different name to distinguish it from the weaker notion.
 
-		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior_Y(K_1^\prime \cap K_2^\prime \cap Y)$.
-To see this consider $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$.
-By construction for $i \in \{1, 2\}$ there exist open sets $V_i \subseteq K_i^\prime$ such that $p \in V_i$.
-Letting $V = V_1 \cap V_2$ we have $p \in V \cap Y \subseteq K^\dprime_1 \cap K^\dprime_2 \cap Y$ implying $p \in \interior_Y(K^\dprime_1 \cap K^\dprime_2 \cap Y)$.
+\begin{defi} 
+	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+The space $M$ is called \emph{locally-$f$-connected} if for each $p \in M$, $e > 0$ and $d \in \mathbb{N}_0$ there exists $\delta \in (0,e)$ such that for all $c \geq f(p)$ the map
+	\[
+	\tilde{H}_d(f_{\leq c+\delta} \cap B_{\delta}(p) \hookrightarrow f_{\leq c+e} \cap B_e(p); \mathbb{Z})
+	\]
+	is 0.
+\end{defi}
 
-		\begin{equation*}
-		\begin{tikzcd}
-		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
-		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
-		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
-		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
-		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
-		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
-		\end{tikzcd}
-		\end{equation*}
+Clearly, strong local-$f$-connectedness implies local-$f$-connectedness.
+Morse also presents the following claim as \cite[Theorem 9.2]{Morse.1937}, but states immediately thereafter that the proof "while not difficult involves too great detail to be presented here".
 
-		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$.
-The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
+\begin{claim}\label{con:q-tame_pers_cech_hom}
+	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is strongly locally-$f$-connected and all sublevel sets are compact.
+Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
+\end{claim}
 
-		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
-		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
-This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
-Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
-	\end{proof}
+While we are currently unable to present a proof, we conjecture the claim to be true.
 
-	We can now immediately prove the following result.
+\todo{what does the story look like for cohomology?}
 
-	\begin{theorem}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{theorem}
-
-	\begin{proof}
-		Using the notation of Lemma \ref{l: wilder}, this would follow from $(r_n)$ applied to the case $K = Y$ and $M = X$.
-To show $(r_n)$ holds for every $n \geq 0$ we proceed by induction noticing that by assumption we have $(r^n_\bullet)$ for every $n$.
-	\end{proof}
-\end{document}
-
-\begin{lemma}
-	Let $Y \subseteq X$ be a pair of compact Hausdorff spaces, then $(r^0)$ above holds. 
-\end{lemma}
-
-\begin{proof}
-	Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$.
-For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite.
-Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
-Since
-	\begin{equation*}
-	\begin{tikzcd}
-	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
-	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
-	\end{tikzcd}
-	\end{equation*}
-	commutes, we have the desired conclusion.
-	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
-\end{proof}
-
-\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
-Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
-The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
-Furthermore, locally $H_1 = 0$.
-Taking $Y = X$ gives a counterexample.
-
-\begin{equation*}
-\begin{tikzpicture}[scale=5]
-\foreach \i in {0,1,2,...,12}{
-	\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
-}
-\end{tikzpicture}
-\end{equation*}
-
-A diagram to keep in mind
-\begin{equation}
-\begin{tikzcd}
-\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
-\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
-
-Consider the following general diagram
-\begin{equation}
-\begin{tikzcd}
-A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
-X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
+\subsection*{Notation and Conventions}
+For the rest of the paper, we let $\mathbb{F}$ be a field and whenever we write homology without explicit mention of coefficients, we mean homology with coefficients in $\mathbb{F}$.

### 2021-03-30 main.tex
Split sections

--- 2021-02-24 main.tex
@@
+\immediate\write18{bibtex \jobname}
 \documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
+\usepackage{amsmath, amsthm, amssymb}
+\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
+\usepackage[capitalize,noabbrev]{cleveref}
 \usepackage{tikz-cd}
+%\usepackage{newtxtext,newtxmath}
+\usepackage[numbers,sort,compress]{natbib}
+\usepackage{graphicx}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
+%To-do
+\usepackage[marginpar]{todo}
+\makeatletter
+\renewcommand{\@tododisplay}[1]{%
+%\marginpar{#1}%
+\textsuperscript{#1}%
+}
+%
+\renewcommand\@displaytodo[2][\todomark]{%
+\@tododisplay{{\todoformat [#1~\ref{todolbl:\thetodo}]}}%
+\footnotetext[\thetodo]{\todoformat #1:~#2}%
+\global\@todotoks\expandafter{\the\@todotoks\todoitem{#1}{#2}}%
+\@todotrue%
+}%
+\renewcommand\todomark{todo}
+\makeatother
 
+% theorems
+\theoremstyle{plain}
+\newtheorem{thm}{Theorem}[section]
+\Crefname{thm}{Theorem}{Theorems}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\Crefname{prop}{Proposition}{Propositions}
+\newtheorem{claim}[thm]{Claim}
+\newtheorem{conj}[thm]{Conjecture}
+\Crefname{conj}{Conjecture}{Conjectures}
+\theoremstyle{definition}
+\newtheorem{defi}[thm]{Definition}
+\newtheorem{ex}[thm]{Example}
+\newtheorem{rem}[thm]{Remark}
+
+% commands
+\newcommand{\N}{\mathbb{N}}
 \newcommand{\Z}{\mathbb{Z}}
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\HS}{\mathrm{HS}}
+\newcommand{\HT}{\mathrm{HT}}
+\newcommand{\HLC}{\mathrm{HLC}}
+\renewcommand{\H}{\mathbb{H}^d}
 \newcommand{\dprime}{{\prime\prime}}
+\DeclareMathOperator{\interior}{int}
 \DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
+\newcommand\CH{\check{H}}
 
+% margins
 \setlength{\textwidth}{\paperwidth}
@@
 
+\newcommand{\anibal}[1]{\textcolor{blue}{[Anibal: #1]}}
+
 \begin{document}
-	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.
 
-	The following is a modification of a theorem of Wilder.
+\title{Persistence in functional topology: q-tameness, local-connectivity and a correction to a theorem of Morse}
+\author{}
+\date{\today}
 
-	\begin{lemma} \label{l: wilder}
-		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
-		\begin{itemize}
-			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $K \cap Y \subset \interior_Y(M \cap Y)$, then $\im H_n\left(K \cap Y \to M\right)$ is finite.
-			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$, then there exist $U$ an open neighborhood of $y$ contained in $V$ such that $\im H_n\left(U \cap Y \to V\right)$ is finite.
-		\end{itemize}
-		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
-	\end{lemma}
+\begin{abstract}
+With applications to the study of minimal surfaces in mind, Marston Morse wrote a series of papers developing versions of his famous inequalities for a broad class of real-valued functions on metric spaces.
+His work is remarkable in so far as it likely represents the first use of something that can be called persistent homology in the mathematical literature.
+From the modern point of view, it is particularly interesting that he uses Vietoris homology in order to enforce semi-continuity of persistent homology and that he states two topological conditions that supposedly ensure q-tameness.
+However, he is partly incorrect: We present a filtration that satisfies one of his conditions but has non-q-tame persistent homology.
+We also conjecture that his other condition, for which he provides no proof, is correct and discuss possible proof strategies.
+\end{abstract}
 
-	\begin{proof}
-		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im H_n\left(U_K \cap Y \to M\right)$ is finite.
+\maketitle
 
-		Recall the following fact:
-		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.
+\input{introduction}
+\input{preliminaries}
+\input{connectivity}
+\input{counterexample}
+\input{theorem}
+\input{outlook}
+%\input{other}
 
-		The collection $\sigma$ is not empty, in fact, it contains a compact neighborhood of any $y \in Y$.
-This follows from taking $V = X$ in $(r_\bullet^n)$ and using $(\ast)$ on the resulting open neighborhood.
+\section*{Acknowledgements}
+This research has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}, the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
 
-		Notice that the collection $\sigma$ is closed under intersections.
-In fact, a stronger statement holds: if $K_1$ is compact and $K_2 \in \sigma$ then $K_1 \cap K_2 \in \sigma$.
-This is a consequence of the fact that the image of a map is finite can be deduced from that property holding for any map that factors it.
-We will next show that $\sigma$ is also closed under finite unions.
+\bibliographystyle{abbrvnaturl}
+\bibliography{biblio}
 
-		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
-		\begin{equation*}
-		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
-		\end{equation*}
-		where $\im H_n\left(U_i \cap Y \to M\right)$ is finite. 
-		We can construct such compact neighborhoods using $(\ast)$ as follows:
-
-		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$.
-The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$.
-Let $\{p_i^{1}, \dots, p^{n}_i\} \subseteq K_i$ be such that $K_i \subseteq \bigcup_{j=1}^n \interior K^\dprime_i(p^j_i)$.
-Define $K_i^\dag = \bigcup_{j=1}^n K^\dag_i(p^j_i)$ for $i \in \{1,2\}$ and $\dag \in \{\prime, \dprime\}$.
-
-		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior_Y(K_1^\prime \cap K_2^\prime \cap Y)$.
-To see this consider $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$.
-By construction for $i \in \{1, 2\}$ there exist open sets $V_i \subseteq K_i^\prime$ such that $p \in V_i$.
-Letting $V = V_1 \cap V_2$ we have $p \in V \cap Y \subseteq K^\dprime_1 \cap K^\dprime_2 \cap Y$ implying $p \in \interior_Y(K^\dprime_1 \cap K^\dprime_2 \cap Y)$.
-
-		\begin{equation*}
-		\begin{tikzcd}
-		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
-		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
-		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
-		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
-		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
-		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
-		\end{tikzcd}
-		\end{equation*}
-
-		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$.
-The bottom left square has a finite image using property $(r^{n-1})$.
-From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.
-
-		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
-		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$.
-This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$.
-Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
-	\end{proof}
-
-	We can now immediately prove the following result.
-
-	\begin{theorem}
-		Let $Y \subseteq X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$.
-Then, $\im \big(H_d(Y) \to H_d(X)\big)$ is finitely generated for every $d$.
-	\end{theorem}
-
-	\begin{proof}
-		Using the notation of Lemma \ref{l: wilder}, this would follow from $(r_n)$ applied to the case $K = Y$ and $M = X$.
-To show $(r_n)$ holds for every $n \geq 0$ we proceed by induction noticing that by assumption we have $(r^n_\bullet)$ for every $n$.
-	\end{proof}
+\todos
 \end{document}
-
-\begin{lemma}
-	Let $Y \subseteq X$ be a pair of compact Hausdorff spaces, then $(r^0)$ above holds. 
-\end{lemma}
-
-\begin{proof}
-	Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$.
-For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite.
-Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$.
-Since
-	\begin{equation*}
-	\begin{tikzcd}
-	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
-	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
-	\end{tikzcd}
-	\end{equation*}
-	commutes, we have the desired conclusion.
-	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
-\end{proof}
-
-\paragraph{NOT \textit{Counterexample}} Let $Z = \left\{\left(0, 2^{-n}\right)\ |\ n \geq 0\right\} \cup \{(0, 0)\} \subset \R^2$.
-Let $X$ be a model of the suspension of $Z$ embedded in $\R^2$.
-The space $X$ is path-connected, Hausdorff, compact, and with infinite first homology.
-Furthermore, locally $H_1 = 0$.
-Taking $Y = X$ gives a counterexample.
-
-\begin{equation*}
-\begin{tikzpicture}[scale=5]
-\foreach \i in {0,1,2,...,12}{
-	\draw[line width=0.05mm] (-1,1) .. controls (0,1/2^\i) .. (1,1);
-}
-\end{tikzpicture}
-\end{equation*}
-
-A diagram to keep in mind
-\begin{equation}
-\begin{tikzcd}
-\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
-\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}
-
-Consider the following general diagram
-\begin{equation}
-\begin{tikzcd}
-A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
-X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
-\end{tikzcd}
-\end{equation}

### 2021-03-30 other.tex
Split sections

\subsection{Two Alternative Conjectures}
In order to relate Morse's conditions to the above, we need a relative version of the $HLC^{\infty}$ condition.

\begin{defi}\label{defi:hlc}
Let $\mathcal{C}$ be a category with $0$ object and let $A\colon\mathbf{Top}\to\mathcal{C}$ be a functor. If $Y\subseteq X$ is a pair of topological spaces, we say that $Y$ is \emph{locally connected with respect to $A$ in $X$} if for each point $p\in Y$ and any open neighborhood $V$ of $p$ in $X$ there is an open neighborhood $U\subseteq V$ of $p$ such that $A(U\cap Y\hookrightarrow V)$ factors through 0.

We say that $Y$ is \emph{$HLC^{\infty}$ in $X$} if it is locally connected with respect to $\tilde{H}_*(-;\mathbb{Z})$ in $X$.
\end{defi}

We get the following rephrasing of strong local-$f$-connectedness.

\begin{prop}
Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function. Then $M$ is strongly locally-$f$-connected if and only if $f_{\leq s}$ is $HLC^{\infty}$ in $f_{\leq t}$ whenever $s<t$.
\end{prop}
\begin{proof}
If each sublevel set is $HLC^{\infty}$ in larger sublevel sets, $M$ is clearly strongly locally-$f$-connected. For the converse direction, fix $s<t$ and choose some point $p\in f_{\leq s}$ with a neighborhood $V$ of $p$ in $f_{\leq t}$. We may choose $e\in(0, t-s)$ such that $B_e(p)\cap f_{\leq t}\subseteq V$. By strong local-$f$-connectedness, for each $d$ there is some $\delta\in(0,e)$ such that the map in reduced $d$-dimensional homology induced by $B_{\delta}(p)\cap f_{\leq s}\hookrightarrow B_e(p)\cap f_{\leq t}$ is trivial. The map $B_{\delta}(p)\cap f_{\leq s}\hookrightarrow V$ factors through the aforementioned map, so it is trivial in reduced homology, too. Thus, $f_{\leq s}$ is $HLC^{\infty}$ in $f_{\leq t}$.
\end{proof}

Note that the proposition gives a purely topological description of strong local-$f$-connectedness, so we can also use it to define strong local-$f$-connectedness for spaces that are not metrizable. It also yields the following corollary.

\begin{cor}
Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function. If all sublevel sets are $HLC^{\infty}$, then $M$ is strongly locally-$f$-connected.
\end{cor}

We now propose the following generalization of \cref{prop:fin_dim_sing_hom}.

\begin{conj}\label{conj:q-tame_singular}
Let $Y\subseteq X$ be compact Hausdorff spaces such that $Y$ is $HLC^{\infty}$ in $X$. Then $\im H_d(Y\hookrightarrow X)$ is finite-dimensional for all $d$.
\end{conj}

As a persistent version, we have the following obvious consequence.

\begin{prop}\label{prop:q-tame_singular}
Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that $M$ is strongly locally-$f$-connected, i.e., each sublevel set is $HLC^{\infty}$ in all larger sublevel sets. If \cref{conj:q-tame_singular} is true, then $H_{d}(f_{\leq\bullet})$ is q-tame for all $d$.
\end{prop}

In a similar spirit, we also propose the following conjecture as an analogue to \cref{cor:cech_sing_persistent_iso}.

\begin{conj}\label{con:d_I_0_sing_cech}
Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that all sublevel sets are paracompact Hausdorff. If $M$ is strongly locally-$f$-connected, i.e., each sublevel set is $HLC^{\infty}$ in all larger sublevel sets, then 
\[
d_I(H_d(f_{\leq\bullet}),\CH_d(f_{\leq\bullet}))=0
\]
for all $d$.
\end{conj}

Here, $d_{I}$ denotes the interleaving distance between persistence modules. The conjecture is relevant because of the following criterion for q-tameness.

\begin{prop}
Let $M$ and $N$ be persistence modules such that $M$ is q-tame and assume $d_I(M,N)=0$. Then $N$ is q-tame.
\end{prop}
\begin{proof}
Pick indices $s<t$. Because $d_I(M,N)=0$, we may choose a $\delta$-interleaving with $\delta\in\left(0,\frac{t-s}{2}\right)$. Then we have a commutative diagram

\[
\begin{tikzcd}
N_s\arrow[rrr]\arrow[rd]&&&N_{t}\\
&M_{s+\delta}\arrow[r]&M_{t-\delta}\arrow[ru]&
\end{tikzcd}
\]
so that the rank of $N_s\to N_t$ is bounded above by the rank of $M_{s+\delta}\to M_{t-\delta}$. The rank of $M_{s+\delta}\to M_{t-\delta}$ is finite by assumption, so $N$ is q-tame.
\end{proof}

Combining the previous result with \cref{prop:q-tame_singular}, we get the following.

\begin{cor}
If \cref{conj:q-tame_singular,con:d_I_0_sing_cech} are true, then so is \cref{con:q-tame_pers_cech_hom}.
\end{cor}

Thus, we have reduced our main conjecture to two smaller ones.

A possible proof strategy for \cref{conj:q-tame_singular} might be to adapt the proof strategy of Wilder's Finiteness Theorem, which is an analogue of \cref{prop:fin_dim_sing_hom} for sheaf cohomology, from \cite[Section II.17]{MR1481706}. Essentially the same proof also appears in \cite[Section III.10]{MR842190}.

A possible proof strategy for \cref{con:d_I_0_sing_cech} might be to adapt Bredon's proof of \cref{prop:cech_sing_hom_hlc} using his spectral sequence that relates \v{C}ech and singular homology.

\subsection{Q-Tameness of Persistent \v{C}ech Homology via Cosheaf Homology}\label{sec:cosheaf}
Note that what follows is rather informal and speculative.

When working with cohomology, the usual modern way to relate the singular and the \v{C}ech theory is via an intermediate step in the form of sheaf cohomology and then use the Leray and Grothendieck spectral sequences \cite[Chapter III]{MR1481706}. One might hope to use similar cosheaf theoretic methods, such as a possible theory of cosheaf homology, to obtain similar results for homology. So far, treatments of cosheaf homology are sparse. Among them are \cite{Andreotti.1973}, \cite{Schneiders.1987} and \cite{prasolov2018cosheaves}, but we are presently unable to determine whether the techniques in these texts can be adapted to our problems. Bredon, in \cite{Bredon.1968} and \cite[Chapter VI]{MR1481706}, also defines \v{C}ech homology with coefficients in a precosheaf and compares it to the singular theory for paracompact $HLC^{\infty}$-spaces \cite[Section VI.4 and Theorem VI.12.6]{MR1481706} using cosheaf theoretic methods. All of his results are still absolute comparison and finiteness results, i.e., they work for a single space $X$, so another obstacle, besides cosheaf homology being underdeveloped, is our desired generalization to subspaces $Y\subseteq X$ that are only $HLC^{\infty}$ in $X$ but not in themselves. That cosheaves might also help in overcoming this problem is suggested by the very nice formulation of the $HLC^{\infty}$ property in terms of precosheaves. The following definition appears in \cite{MR1481706}.

\begin{defi}
Let $\mathfrak{A}$ be a precosheaf on a space $X$ with values in a category with 0 object, i.e., a covariant functor on the poset category of open sets in $X$. We call $\mathfrak{A}$ \emph{locally trivial} if for all points $x\in X$ and all open neighborhoods $V$ of $x$ there is another open neighborhood $U\subseteq V$ of $x$ such that $\mathfrak{A}(U)\to\mathfrak{A}(V)$ factors through 0.
\end{defi}

The following definition is, up to our use of reduced homology, taken from \cite{Curry.2015}.

\begin{defi}
For any topological space $X$, we define the \emph{reduced Leray precosheaf} $\mathfrak{L}_X$ on $X$ as the precosheaf mapping $U\mapsto \tilde{H}_*(U;\mathbb{Z})$.
\end{defi}

\begin{defi}
If $f\colon Y\to X$ is a continuous map between topological spaces and $\mathfrak{A}$ is a precosheaf on $Y$, we define the \emph{pushforward of $\mathfrak{A}$ along $f$} as the precosheaf on $X$ mapping $U\mapsto\mathfrak{A}(f^{-1}(U))$. We denote it by $f_*\mathfrak{A}$.
\end{defi}

Now if $Y\subseteq X$ are topological spaces, we get an obvious morphism $i_*\mathfrak{L}_Y\to\mathfrak{L}_X$ of precosheaves on $X$, where $i\colon Y\hookrightarrow X$ is the inclusion, given by $\tilde{H}_*(U\cap Y\hookrightarrow U;\mathbb{Z})$. Note that the category of precosheaves with values in abelian groups is just a functor category from a small category to an abelian category. In particular, it has images given "pointwise". We get the following rephrasing of the relative $HLC^{\infty}$ property.

\begin{prop}
Let $Y\subseteq X$ be topological spaces. Then $Y$ is $HLC^{\infty}$ in $X$ if and only if $\im(i_*\mathfrak{L}_Y\to\mathfrak{L}_X)$ is locally trivial.
\end{prop}

Our hope is that one might be able to use this characterization in the future to prove the previously made conjectures.

\todo{Given $f\colon M\to\mathbb{R}$, is there a way of finding a single space (e.g. M itself, disjoint union of sublevel sets, colim of sublevel sets, hocolim of sublevel sets, continuously indexed mapping telescope (how to construct this?) of inclusions of sublevel sets, etc.) and a precosheaf with values in a category of persistence module (maybe the observable category) on that space such that $M$ is locally-$f$-connected iff that precosheaf is locally trivial?}

### 2021-03-30 preliminaries.tex
Split sections

--- 2021-03-30 theorem.tex
@@
-\documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{tikz-cd}
+\section{Preliminaries}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
+\begin{itemize}
+	\item metric space
+	\item upper semi-continuous function
+	\item Persistence module
+	\item q-tameness
+	\item Barcode
+	\item bottleneck
+	\item stability
+\end{itemize}
 
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\HS}{\mathrm{HS}}
-\newcommand{\dprime}{{\prime\prime}}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.4in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\newcommand{\p}{\mathrm{p}}
-\newcommand{\q}{\mathrm{q}}
-
-\begin{document}
-
-\begin{definition}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ---denoted $\HS_n$--- if the image of the map induced by $H_n(-)$ is finitely generated, and we say it is \textit{homologically small}, denoted $\HS$, if it is $\HS_n$ for every~$n$.
-\end{definition}
-
-\begin{definition}
-	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
-	\begin{equation*}
-	X_{\leq t} = f^{-1}((-\infty, t]).
-	\end{equation*}
-\end{definition}
-
-\begin{definition}
+\begin{defi}
 	Let $M$ be a metric space. For any $p \in M$ and $\epsilon \geq 0$ denote
@@
 	\end{equation*}
-\end{definition}
+\end{defi}
 
-\begin{definition}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function.
-	The space $M$ is said to be \textit{strongly locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the image of the map induced by $H_n(-)$ on $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $0$.
-\end{definition}
-
-\begin{theorem} \label{t:strong local connectenss implies q-tameness}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
-\end{theorem}
-
-\begin{lemma} \label{l:commutative algebra}
-	Given a commutative diagram of modules over a principal ideal domain
+\begin{defi}
+	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
 	\begin{equation*}
-	\begin{tikzcd}
-	A_{1,1} \arrow[r] & A_{1,2} & \\
-	A_{2,1} \arrow[r] \arrow[u] & A_{2,2} \arrow[r] \arrow[u] & A_{2,3} \\
-	& A_{3,2} \arrow[r] \arrow[u] & A_{3,3} \arrow[u]
-	\end{tikzcd}
+	X_{\leq t} = f^{-1}((-\infty, t]).
 	\end{equation*}
-	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then $A_{3,2} \to A_{1,2}$ does as well.
-\end{lemma}
-
-\begin{lemma} \label{l:neighborhood third}
-	Let $M$ be a metric space. For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
-	\begin{equation*}
-	K \subseteq \interior(K^\prime) \subseteq K^\prime \subseteq U.
-	\end{equation*}
-\end{lemma}
-
-\begin{proof}
-	For any $x \in K$ choose $\epsilon(x)$ such that $B_{\epsilon(x)}(x) \subseteq U$. We have
-	\begin{equation*}
-	B_{\frac{\epsilon(x)}{3}}(x) \subseteq \overline B_{\frac{\epsilon(x)}{2}}(x) \subseteq B_{\epsilon(x)}(x).
-	\end{equation*}
-	Since $K$ is compact, there exists a finite set $\{x_\lambda \in K\}_{\Lambda}$ such that $K \subseteq \bigcup_{\Lambda} B_{\frac{\epsilon(x_\lambda)}{3}}(x_\lambda)$.
-Defining $K^\prime = \bigcup_{\Lambda} \overline B_{\frac{\epsilon(x_\lambda)}{2}}(x_\lambda)$ finishes the proof.
-\end{proof}
-
-\begin{lemma} \label{l:key lemma for q-tameness}
-	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
-	Consider sets $K, L \subseteq M$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
-\end{lemma}
-
-\begin{proof}
-	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $H_{n-1}(-)$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
-
-	Given a compact set $L \subseteq M$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U_K$ of $K$ such that $U_K \cap M_{s+\delta_K} \to L \cap M_{t}$ is $\HS_n$.
-
-	We start by showing that any point in $\interior(L) \cap M_s$ has a neighborhood in $\Sigma_{s, t}$.
-	Let $x \in \interior(L) \cap M_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
-	By the strong local-$f$-connectivity of $M$, there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ the following composition is $\HS$:
-	\begin{equation*}
-	\overline B_{\delta/2}(x) \cap M_{s + \delta} \to
-	B_\delta(x) \cap M_{s + \delta} =
-	B_\delta(x) \cap M_{f(x) + c + \delta} \to
-	B_e(x) \cap M_{f(x) + c + e} \to
-	L \cap M_{t}.
-	\end{equation*}
-
-	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
-	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap M_{s+\delta_i} \to L \cap M_{t}$ is $\HS_n$.
-	We Use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
-	\begin{equation*}
-	K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime \subseteq U_i.
-	\end{equation*}
-	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap M_{s+\delta} \to L \cap M_t$ is $\HS_n$.
-	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap M_s \to K_1^\prime \cap K_2^\prime \cap M_{s+\delta}$ is $\HS_{(n-1)}$.
-	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:
-	\begin{equation*}
-	\begin{tikzcd}
-	H_n(L \cap M_t) \oplus H_n(L \cap M_t) \arrow[r] &
-	H_n(L \cap M_t) & \\
-	H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus H_n(K_2^\prime \cap M_{s+\delta}) \arrow[r] \arrow[u] & 
-	H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[r] \arrow[u] &
-	H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) \\ & 
-	H_{n}((K_1 \cup K_2) \cap M_s) \arrow[r] \arrow[u] &
-	H_{n-1}(K_1 \cap K_2 \cap M_s). \arrow[u]
-	\end{tikzcd}
-	\end{equation*}
-	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
-	Since any compact $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{t:strong local connectenss implies q-tameness}]
-	 It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = M_{\leq s}$ and $L = M$.
-\end{proof}
-
-\end{document}
+\end{defi}

### 2021-03-31 connectivity.tex
Changes before meeting

@@
 \begin{ex}
-	For any $d$, the $d$-dimensional Hawaiian earring is not $\HLC$.
+	The $d$-dimensional Hawaiian earring $\H$ is not $\HLC$.
 However, if we consider $\H$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d < d'$, then $\H$ is $\HLC$ in $\mathbb{H}^{d'}$.
@@
 
-\begin{defi}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function.
-	The space $M$ is said to be \textit{locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the inclusion $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $\HT$.
-\end{defi}
-
-Local connectedness assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional, see \cite{MR0007094} for early examples.
+Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional, see \cite{MR0007094} for early examples.
 For us, the following is relevant.
@@
 \begin{cor}\label{cor:cech_sing_persistent_iso}
-	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a paracompact $HLC^\infty$-space for each $c\in\mathbb{R}$.
-Then $\CH_d(f_{\leq\bullet})\cong H_d(f_{\leq\bullet})$ for any $d$.
+	Let $M$ be a metric space and $f \colon M \to \mathbb{R}$ a function such that $M_{\leq c}$ is a paracompact $\HLC$-space for each $c \in \mathbb{R}$.
+	Then $\CH_n(M_{\leq \bullet}) \cong H_n(M_{\leq\bullet})$ for any integer $n$.
 \end{cor}
@@
 
-\begin{prop}\label{prop:fin_dim_sing_hom}
-	Let $X$ be compact Hausdorff and $HLC^{\infty}$. Then $H_d(X;\mathbb{F})$ is finite-dimensional for all $d$ and any field $\mathbb{F}$.
+\anibal{Does this needs field coefficients? (}
+\begin{prop} \label{prop:fin_dim_sing_hom}
+	Let $X$ be compact Hausdorff and $\HLC$.
+	Then $H_n(X; \mathbb{F})$ is finite-dimensional for all $n$ and any field $\mathbb{F}$.
 \end{prop}
@@
 \begin{cor}
-	Let $M$ be a topological space and $f\colon M\to\mathbb{R}$ a function such that $f_{\leq c}$ is a compact Hausdorff $HLC^\infty$-space for each $c\in\mathbb{R}$.
-Then $H_d(f_{\leq\bullet})$ is p.f.d.
-for any $d$.
+	Let $X$ be a topological space and $f \colon X \to \R$ a function such that $f_{\leq c}$ is a compact Hausdorff $\HLC$-space for each $c \in \R$.
+	Then $H_d(f_{\leq\bullet})$ is p.f.d. for any $d$.
 \end{cor}
+
+\begin{defi}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function.
+	The space $M$ is said to be \textit{locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the inclusion $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $\HT$.
+\end{defi}

### 2021-03-31 introduction.tex
Changes before meeting

@@
 \begin{defi}
-	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+	Let $M$ be a metric space and $f \colon M \to \R$ a function.
 The space $M$ is called \emph{locally-$f$-connected} if for each $p\in M$, $e>0$ and $d\in\mathbb{N}_0$ there exists $\delta\in(0,e)$ such that the map
@@
 
-Here, $\tilde{H}_{d}$ denotes reduced $d$-dimensional singular homology, $f_{\leq t}$ denotes the sublevel set of $f$ at $t\in\mathbb{R}$, and $B_{\delta}(p)$ denotes the open ball with radius $\delta$ around the point $p$.
+Here, $\tilde{H}_{d}$ denotes reduced $d$-dimensional singular homology, $f_{\leq t}$ denotes the sublevel set of $f$ at $t\in\R$, and $B_{\delta}(p)$ denotes the open ball with radius $\delta$ around the point $p$.
 Morse then states the claim below as \cite[Theorem 6.3]{Morse.1940}.
@@
 \begin{claim}
-	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is locally-$f$-connected and all sublevel sets are compact.
+	Let $M$ be a metric space and $f\colon M\to\R$ a function such that $M$ is locally-$f$-connected and all sublevel sets are compact.
 Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
@@
 There, Morse presents a supposed proof of the claim by constructing finite bases for the sets $\im \CH_d(f_{\leq s}\hookrightarrow f_{\leq t};\mathbb{F})$.
-As it turns out, the proof is not correct: We present a counterexample to the claim.
-
-\begin{thm}\label{thm:counterexample}
-	For any $d$, there exists a funtion $F\colon \mathbb{H}^{d}\to\mathbb{R}$ on the $d$-dimensional Hawaiian earring $\mathbb{H}^{d}$ such that $\mathbb{H}^{d}$ is locally-$F$-connected, all sublevel sets are compact and $\CH_d(F_{\leq\bullet};\mathbb{F})$ is not q-tame for any field $\mathbb{F}$.
-\end{thm}
-
-Recall that the $d$-dimensional Hawaiian earring is defined as the subspace
-\[
-\mathbb{H}^{d}=\bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
-\]
-of $d+1$-dimensional Euclidean space.
+As it turns out, the proof is not correct: We use the Hawaiian earring to construct a counterexample to this claim in Section \ref{sec:counterexample}.
 
@@
 \begin{defi} 
-	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+	Let $M$ be a metric space and $f\colon M\to\R$ a function.
 The space $M$ is called \emph{locally-$f$-connected} if for each $p \in M$, $e > 0$ and $d \in \mathbb{N}_0$ there exists $\delta \in (0,e)$ such that for all $c \geq f(p)$ the map
@@
 
-\begin{claim}\label{con:q-tame_pers_cech_hom}
-	Let $M$ be a metric space and $f\colon M\to\mathbb{R}$ a function such that $M$ is strongly locally-$f$-connected and all sublevel sets are compact.
+\begin{claim}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function such that $M$ is strongly locally-$f$-connected and all sublevel sets are compact.
 	Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
@@
 
-While we are currently unable to present a proof, we conjecture the claim to be true.
-
-\todo{what does the story look like for cohomology?}
-
-\subsection*{Notation and Conventions}
-For the rest of the paper, we let $\mathbb{F}$ be a field and whenever we write homology without explicit mention of coefficients, we mean homology with coefficients in $\mathbb{F}$.
+We devote Section \ref{sec:theorem} to its proof.

### 2021-03-31 preliminaries.tex
Changes before meeting

@@
 
+\subsection*{Notation and Conventions}
+For the rest of the paper, we let $\mathbb{F}$ be a field and whenever we write homology without explicit mention of coefficients, we mean homology with coefficients in $\mathbb{F}$.
+
+\subsection{Sublevel set filtrations}
+
+Treat in parallel the case of spaces $X$ and the case of sublevel filtrations $(X, f)$. Leads nicely to different connectivities.
 \begin{itemize}
@@
 	\item upper semi-continuous function
-	\item Persistence module
-	\item q-tameness
-	\item Barcode
-	\item bottleneck
-	\item stability
+	\item sublevel set filtrations
 \end{itemize}
@@
 \end{defi}
+
+\subsection{Persistence homology}
+
+\begin{itemize}
+	\item Persistence module
+	\item q-tameness
+	\item Barcode
+	\item bottleneck
+	\item stability
+\end{itemize}

### 2021-03-31 theorem.tex
Changes before meeting

@@
-\documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{tikz-cd}
+\section{Theorem} \label{sec:theorem}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
+\begin{thm} \label{t:strong local connectenss implies q-tameness}
+	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
+\end{thm}
 
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\HS}{\mathrm{HS}}
-\newcommand{\dprime}{{\prime\prime}}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\interior}{int}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.4in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\newcommand{\p}{\mathrm{p}}
-\newcommand{\q}{\mathrm{q}}
-
-\begin{document}
-
-\begin{definition}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ---denoted $\HS_n$--- if the image of the map induced by $H_n(-)$ is finitely generated, and we say it is \textit{homologically small}, denoted $\HS$, if it is $\HS_n$ for every~$n$.
-\end{definition}
-
-\begin{definition}
-	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
-	\begin{equation*}
-	X_{\leq t} = f^{-1}((-\infty, t]).
-	\end{equation*}
-\end{definition}
-
-\begin{definition}
-	Let $M$ be a metric space. For any $p \in M$ and $\epsilon \geq 0$ denote
-	\begin{equation*}
-	B_\epsilon(p) = \{q \in M\ |\ d(p,q) < \epsilon\}, \qquad
-	\overline B_\epsilon(p) = \{q \in M\ |\ d(p,q) \leq \epsilon\}.
-	\end{equation*}
-\end{definition}
-
-\begin{definition}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function.
-	The space $M$ is said to be \textit{strongly locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the image of the map induced by $H_n(-)$ on $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $0$.
-\end{definition}
-
-\begin{theorem} \label{t:strong local connectenss implies q-tameness}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
-\end{theorem}
-
-\begin{lemma} \label{l:commutative algebra}
+\begin{lem} \label{l:commutative algebra}
 	Given a commutative diagram of modules over a principal ideal domain
@@
 	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then $A_{3,2} \to A_{1,2}$ does as well.
-\end{lemma}
+\end{lem}
 
-\begin{lemma} \label{l:neighborhood third}
+\begin{lem} \label{l:neighborhood third}
 	Let $M$ be a metric space. For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
@@
 	\end{equation*}
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{lemma} \label{l:key lemma for q-tameness}
+\begin{lem} \label{l:key lemma for q-tameness}
 	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
 	Consider sets $K, L \subseteq M$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
-\end{lemma}
+\end{lem}
 
@@
 \end{proof}
-
-\end{document}

### 2021-04-01 connectivity.tex
Split preliminaries

@@
 
+Let $\H$ be a fixed homology theory.
+
 \begin{defi} \label{defi:local_connectedness}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or \textit{trivial}, denoted $\HS_n$ and $\HT_n$ respectively, if the image of the map induced by $\tilde H_n(-)$ is finitely generated or 0, and we say it is \textit{homologically small} or \textit{trivial}, denoted respectively $\HS$ and $\HT$, if it is $\HS_n$ or $\HT_n$ for every~$n$.
-
-	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
+	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or \textit{trivial}, denoted $\HS_n$ and $\HT_n$ respectively, if the image of the map induced by $\H_n$ is finitely generated or 0, and we say it is \textit{homologically small} or \textit{trivial}, denoted respectively $\HS$ and $\HT$, if it is $\HS_n$ or $\HT_n$ for every~$n$.
 \end{defi}
 
-\anibal{Use a different example, $\H$ not yet defined.}
-\begin{ex}
-	The $d$-dimensional Hawaiian earring $\H$ is not $\HLC$.
-However, if we consider $\H$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d < d'$, then $\H$ is $\HLC$ in $\mathbb{H}^{d'}$.
-\end{ex}
+\begin{defi}
+	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
+
+	A sublevel filtration $(X,f)$ is said to be $\emph{homologically locally connected}$, denoted $\HLC$, if for each $x \in X$, neighborhood $V$ of $x$ and $\epsilon > 0$ there exists $U$ a neighborhood of $x$ with $U \subseteq V$ and $\delta \in (0, \epsilon)$ such that
+	\begin{equation*}
+	X_{\leq f(x) + \delta} \cap U \to X_{f(x) + \epsilon} \cap V
+	\end{equation*}
+	is $\HT$.
+\end{defi}
+
+%\anibal{Use a different example, $\HE$ not yet defined.}
+%\begin{ex}
+%	The $d$-dimensional Hawaiian earring $\HE$ is not $\HLC$.
+However, if we consider $\HE$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d < d'$, then $\HE$ is $\HLC$ in $\mathbb{H}^{d'}$.
+%\end{ex}
 
@@
 For us, the following is relevant.
+Recall that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
 
@@
 \begin{cor}\label{cor:cech_sing_persistent_iso}
-	Let $M$ be a metric space and $f \colon M \to \mathbb{R}$ a function such that $M_{\leq c}$ is a paracompact $\HLC$-space for each $c \in \mathbb{R}$.
-	Then $\CH_n(M_{\leq \bullet}) \cong H_n(M_{\leq\bullet})$ for any integer $n$.
+	Let $(X, f)$ be a sublevel filtration. If each sublevel set is paracompact and $\HLC$, then its singular and \v{C}ech persistence modules coincide.
 \end{cor}
 
-For more results of this type, we refer to \cite{MR1481706}.
-There, the above result \cite[Corollary VI.12.6]{MR1481706} and many similar ones are shown using sheaf theoretic methods.
+For more results of this type, we refer to \cite{MR1481706}. There, the above proposition \cite[Corollary VI.12.6]{MR1481706} and many similar ones are proven using sheaf theoretic methods.
 For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
@@
 
-\anibal{Does this needs field coefficients? (}
 \begin{prop} \label{prop:fin_dim_sing_hom}
-	Let $X$ be compact Hausdorff and $\HLC$.
-	Then $H_n(X; \mathbb{F})$ is finite-dimensional for all $n$ and any field $\mathbb{F}$.
+	Let $X$ be a compact Hausdorff $\HLC$ space.
+	Then the singular homology of $X$ with field coefficients is finite-dimensional in every degree.
 \end{prop}
-
+\anibal{Does this really needs field coefficients?} 
 \begin{proof}
@@
 \begin{cor}
-	Let $X$ be a topological space and $f \colon X \to \R$ a function such that $f_{\leq c}$ is a compact Hausdorff $\HLC$-space for each $c \in \R$.
-	Then $H_d(f_{\leq\bullet})$ is p.f.d. for any $d$.
+	Let $(X, f)$ be a sublevel filtration. If each sublevel set is compact and $\HLC$
+	Then its singular persistence module is p.f.d. in every degree.
 \end{cor}
-
-\begin{defi}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function.
-	The space $M$ is said to be \textit{locally-$f$-connected} if for each $p \in M$, $e > 0$, and $n \in \N$ there exists $\delta \in (0, e)$ such that for every $c \geq 0$ the inclusion $B_\delta(p) \cap M_{\leq f(p)+\delta+c} \to B_e(p) \cap M_{\leq f(p)+e+c}$ is $\HT$.
-\end{defi}

### 2021-04-01 counterexample.tex
Changes before meeting
Split preliminaries

@@
-\section{Counterexample}
+\section{Counterexample} \label{sec:counterexample}
 
@@
 	\centering
-	\includegraphics[width=.77\textheight]{hawaiian_earring}
-	\hfill
+	\begin{tikzpicture}[scale=88]
+	\draw[thick] (-.1,0) rectangle (.1,.05);
+	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
+	\foreach \i in {1,...,100}{
+		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
+	}
+	\end{tikzpicture}
 	\caption{TBW}
@@
 
-In this section we show that weak local-$f$-connectivity is not sufficient to ensure q-tameness and, in the next, that local-$f$-connectivity is.
+In this section we show that a sublevel filtration can be $\HLC$ and not q-tame.
 
@@
 \begin{equation*}
-\H = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
+\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}
 \end{equation*}
 of $d+1$-dimensional Euclidean space.
-Let $f \colon \mathbb{H}^{d}\to\mathbb{R}$ as $0$ at the origin $\vec{0}$ and $1$ everywhere else.
-All sublevel sets $\H_{\leq t}$ are either the singleton $\{\vec{0}\}$ or the whole space $\H$, and therefore compact.
-Moreover, $\mathbb{H}^{d}$ is locally-$f$-connected as we prove now.
+Let $f \colon \HE\to\R$ as $0$ at the origin $\vec{0}$ and $1$ everywhere else.
+All sublevel sets $\HE_{\leq t}$ are either the singleton $\{\vec{0}\}$ or the whole space $\HE$, and therefore compact.
+Moreover, $\HE$ is locally-$f$-connected as we prove now.
 
-Let $e > 0$ and $p \in \H$.
+Let $e > 0$ and $p \in \HE$.
 If $p$ is the origin, we choose $\delta$ between 0 and $\min\{e,1\}$.
-Then $\H_{\leq f(p) + \delta} = \H_{\leq \delta} = \{p\}$, so the condition is trivially satisfied.
+Then $\HE_{\leq f(p) + \delta} = \HE_{\leq \delta} = \{p\}$, so the condition is trivially satisfied.
 For $p$ not the origin, there is a unique $d$-sphere that contains it.
@@
 
-What remains to be shown is that $\H_{\leq \bullet}$ is not q-tame with respect to singular and \v{C}ech homology.
-Note that $\H_{\leq t}$ is constant with value $\H$ for $t \geq 1$, so it suffices to show that the singular and \v{C}ech homology of $\H$ with field coefficients is infinite dimensional.
+What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame with respect to singular and \v{C}ech homology.
+Note that $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, so it suffices to show that the singular and \v{C}ech homology of $\HE$ with field coefficients is infinite dimensional.
 The case of singular homology is well know.
@@
 \begin{align*}
-\mathbb{H}^{d}_k&=\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
-&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\mathbb{R}^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
+&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
 \end{align*}
 i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-We have $\lim_{k}\mathbb{H}^{d}_{k}=\bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\mathbb{H}^{d}) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
+We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
 One can easily check that each $\mathbb{H}^{d}_{k}$ satisfies the assumptions for \cref{prop:cech_sing_hom_hlc}, which implies $\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim_{k}H_{d}(\mathbb{H}^{d}_{k})$.

### 2021-04-01 filtrations.tex
Split preliminaries

\subsection{Sublevel filtrations}

A \textit{sublevel filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
\begin{equation*}
X_{\leq t} = f^{-1}((-\infty, t]).
\end{equation*}

Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x \in X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every open neighborhood $U$ of $x$ there exists a neighborhood $N$ of $x$ such that $N \subseteq U$.

A sublevel filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.

### 2021-04-01 homology.tex
Split preliminaries

\subsection{Homology theories}

\begin{itemize}
	\item Definition
	\item Examples, main: singular with integer coeff and cech with field 
	\item Mayer-Vietoris
\end{itemize}

### 2021-04-01 theorem.tex
Split preliminaries

@@
 \section{Theorem} \label{sec:theorem}
+
+In this section we introduce a stronger version of $\HLC$ for sublevel filtrations, and we show that Morse filtrations with this property are q-tame.
+
+\begin{defi}
+	A sublevel filtration $(X,f)$ is said to be \textit{strongly} $\HLC$ if for each $x \in X$, neighborhood $V$ of $x$ and $\epsilon > 0$ there exists $U$ a neighborhood of $x$ with $U \subseteq V$ and $\delta \in (0, \epsilon)$ such that
+	\begin{equation*}
+	X_{\leq f(x) + \delta + c} \cap U \to X_{f(x) + \epsilon + c} \cap V
+	\end{equation*}
+	is $\HT$ for every $c \geq 0$.
+\end{defi}
 
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
+	Fix a homology theory. Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
 	Consider sets $K, L \subseteq M$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
@@
 	\begin{tikzcd}
-	H_n(L \cap M_t) \oplus H_n(L \cap M_t) \arrow[r] &
-	H_n(L \cap M_t) & \\
-	H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus H_n(K_2^\prime \cap M_{s+\delta}) \arrow[r] \arrow[u] & 
-	H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[r] \arrow[u] &
-	H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) \\ & 
-	H_{n}((K_1 \cup K_2) \cap M_s) \arrow[r] \arrow[u] &
-	H_{n-1}(K_1 \cap K_2 \cap M_s). \arrow[u]
+	\H_n(L \cap M_t) \oplus \H_n(L \cap M_t) \arrow[r] &
+	\H_n(L \cap M_t) & \\
+	\H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus \H_n(K_2^\prime \cap M_{s+\delta}) \arrow[r] \arrow[u] & 
+	\H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) \\ & 
+	\H_{n}((K_1 \cup K_2) \cap M_s) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1 \cap K_2 \cap M_s). \arrow[u]
 	\end{tikzcd}

### 2021-04-01 filtrations.tex
Change statement and proof of l:neighborhood third

@@
 
-Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x \in X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every open neighborhood $U$ of $x$ there exists a neighborhood $N$ of $x$ such that $N \subseteq U$.
+Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x$ in $X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every $x$ in $X$, every neighborhood of $x$ contains a compact neighborhood of $x$.
 

### 2021-04-01 theorem.tex
Change statement and proof of l:neighborhood third

@@
 \begin{thm} \label{t:strong local connectenss implies q-tameness}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function. If $M$ is strongly locally-$f$-connected and all level sets are compact, then, for any $s < t$ the inclusion $M_s \to M_t$ is $\HS$.
+	Any be a strongly $\HLC$ Morse filtration $(X,f)$ is q-tame, i.e., for every $s < t$ the inclusion $X_s \to X_t$ is $\HS$.
 \end{thm}
@@
 
+\begin{proof}
+	This is proven via a straightforward diagram chase. For complete details see Lemma 17.3 in \cite{Bredon.1968}.
+\end{proof}
+
 \begin{lem} \label{l:neighborhood third}
-	Let $M$ be a metric space. For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
+	Let $X$ be locally compact space.
+	For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
 	\begin{equation*}
@@
 \begin{proof}
-	For any $x \in K$ choose $\epsilon(x)$ such that $B_{\epsilon(x)}(x) \subseteq U$. We have
+	For any $x \in K$ choose a compact neighborhood $C(x) \subseteq U$.
+	We have
 	\begin{equation*}
-	B_{\frac{\epsilon(x)}{3}}(x) \subseteq \overline B_{\frac{\epsilon(x)}{2}}(x) \subseteq B_{\epsilon(x)}(x).
+	K \subseteq \bigcup_K \interior(C(x)) \subseteq \interior\left(\bigcup_K C(x)\right) \subseteq \bigcup_K C(x) \subseteq U
 	\end{equation*}
-	Since $K$ is compact, there exists a finite set $\{x_\lambda \in K\}_{\Lambda}$ such that $K \subseteq \bigcup_{\Lambda} B_{\frac{\epsilon(x_\lambda)}{3}}(x_\lambda)$.
-Defining $K^\prime = \bigcup_{\Lambda} \overline B_{\frac{\epsilon(x_\lambda)}{2}}(x_\lambda)$ finishes the proof.
+	Since $K$ is compact, the first inclusion above is achieved over a finite subset $\{x_1, \dots, x_m\}$ of elements in $K$.
+	Defining $K^\prime = \bigcup_{i=1}^m C(x_i)$ finishes the proof.
 \end{proof}

### 2021-04-01 connectivity.tex
Change theorem: local compactness instead of metric

@@
 
-	A sublevel filtration $(X,f)$ is said to be $\emph{homologically locally connected}$, denoted $\HLC$, if for each $x \in X$, neighborhood $V$ of $x$ and $\epsilon > 0$ there exists $U$ a neighborhood of $x$ with $U \subseteq V$ and $\delta \in (0, \epsilon)$ such that
+	A sublevel filtration $(X,f)$ is said to be $\emph{homologically locally connected}$, denoted $\HLC$, if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
 	\begin{equation*}

### 2021-04-01 theorem.tex
Change theorem: local compactness instead of metric

@@
 \begin{defi}
-	A sublevel filtration $(X,f)$ is said to be \textit{strongly} $\HLC$ if for each $x \in X$, neighborhood $V$ of $x$ and $\epsilon > 0$ there exists $U$ a neighborhood of $x$ with $U \subseteq V$ and $\delta \in (0, \epsilon)$ such that
+	A sublevel filtration $(X,f)$ is said to be \textit{strongly} $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
 	\begin{equation*}
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Fix a homology theory. Let $M$ and $f$ be as in Theorem \ref{t:strong local connectenss implies q-tameness}.
-	Consider sets $K, L \subseteq M$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap M_{s+\delta} \to L \cap M_{t}$ is $\HS$.
+	Fix a homology theory. Let $(X,f)$ be a strongly $\HLC$ Morse filtration.
+	Consider sets $K, L \subseteq X$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap X_{s+\delta} \to L \cap X_{t}$ is $\HS$.
 \end{lem}
@@
 \begin{proof}
-	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $H_{n-1}(-)$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
+	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $\H_{n-1}$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
 
-	Given a compact set $L \subseteq M$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U_K$ of $K$ such that $U_K \cap M_{s+\delta_K} \to L \cap M_{t}$ is $\HS_n$.
+	Given a compact set $L \subseteq X$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U(K)$ of $K$ such that $U(K) \cap X_{s+\delta_K} \to L \cap X_{t}$ is $\HS_n$.
 
-	We start by showing that any point in $\interior(L) \cap M_s$ has a neighborhood in $\Sigma_{s, t}$.
-	Let $x \in \interior(L) \cap M_{s}$ and take $e > 0$ such that $s + e < t$ and $B_e(x) \subseteq \interior(L)$.
-	By the strong local-$f$-connectivity of $M$, there exists $\delta \in (0, e)$ such that for $c = s - f(x)$ the following composition is $\HS$:
+	We start by showing that any element of $\interior(L) \cap X_s$ has a neighborhood in $\Sigma_{s, t}$.
+	Let $x \in \interior(L) \cap X_{s}$.
+	Consider an open neighborhood $U(x)$ of $x$ contained in $\interior(L)$, and take $\epsilon > 0$ such that $s + \epsilon < t$.
+	By the strong $\HLC$ of $(X,f)$ there is a $\delta \in (0, \epsilon)$ and an open neighborhood $W(x) \subseteq U(x)$ such that for $c = s - f(x)$ the following composition is $\HS$:
 	\begin{equation*}
-	\overline B_{\delta/2}(x) \cap M_{s + \delta} \to
-	B_\delta(x) \cap M_{s + \delta} =
-	B_\delta(x) \cap M_{f(x) + c + \delta} \to
-	B_e(x) \cap M_{f(x) + c + e} \to
-	L \cap M_{t}.
+	W(x) \cap X_{f(x) + c + \delta} \to
+	U(x) \cap X_{f(x) + c + e} \to
+	L \cap X_{t}.
 	\end{equation*}
+	By local connectivity we can choose a compact neighborhood of $x$ contained in $W(x)$.
+	This proves the claim.
 
 	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
-	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap M_{s+\delta_i} \to L \cap M_{t}$ is $\HS_n$.
+	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap X_{s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
 	We Use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
@@
 	\end{equation*}
-	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap M_{s+\delta} \to L \cap M_t$ is $\HS_n$.
-	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap M_s \to K_1^\prime \cap K_2^\prime \cap M_{s+\delta}$ is $\HS_{(n-1)}$.
+	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap X_{s+\delta} \to L \cap X_t$ is $\HS_n$.
+	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_s \to K_1^\prime \cap K_2^\prime \cap X_{s+\delta}$ is $\HS_{(n-1)}$.
 	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:
@@
 	\begin{tikzcd}
-	\H_n(L \cap M_t) \oplus \H_n(L \cap M_t) \arrow[r] &
-	\H_n(L \cap M_t) & \\
-	\H_{n}(K_1^\prime \cap M_{s+\delta}) \oplus \H_n(K_2^\prime \cap M_{s+\delta}) \arrow[r] \arrow[u] & 
-	\H_{n}((K_1^\prime \cap M_{s+\delta}) \cup (K_2^\prime \cap M_{s+\delta})) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap M_{s+\delta}) \\ & 
-	\H_{n}((K_1 \cup K_2) \cap M_s) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1 \cap K_2 \cap M_s). \arrow[u]
+	\H_n(L \cap X_t) \oplus \H_n(L \cap X_t) \arrow[r] &
+	\H_n(L \cap X_t) & \\
+	\H_{n}(K_1^\prime \cap X_{s+\delta}) \oplus \H_n(K_2^\prime \cap X_{s+\delta}) \arrow[r] \arrow[u] & 
+	\H_{n}((K_1^\prime \cap X_{s+\delta}) \cup (K_2^\prime \cap X_{s+\delta})) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap X_{s+\delta}) \\ & 
+	\H_{n}((K_1 \cup K_2) \cap X_s) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1 \cap K_2 \cap X_s). \arrow[u]
 	\end{tikzcd}
@@
 \begin{proof}[Proof of Theorem \ref{t:strong local connectenss implies q-tameness}]
-	It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = M_{\leq s}$ and $L = M$.
+	It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = X_{\leq s}$ and $L = X$.
 \end{proof}

### 2021-04-01 counterexample.tex
Change counterexample: statement using conditions on H-theory

@@
 	\end{tikzpicture}
-	\caption{TBW}
+	\caption{A closeup of the Hawaiian hearing $\mathbb{H}^1$.}
 	\label{fig:earrings}
@@
 
-In this section we show that a sublevel filtration can be $\HLC$ and not q-tame.
+In this section we show that a sublevel filtration can be $\HLC$ and not q-tame for most homology theories of interest.
 
-The $d$-dimensional Hawaiian earring is defined as the subspace
+The \textit{$d$-dimensional Hawaiian earring}, see Figure \ref{fig:earrings}, is defined as the subspace
 \begin{equation*}
@@
 of $d+1$-dimensional Euclidean space.
-Let $f \colon \HE\to\R$ as $0$ at the origin $\vec{0}$ and $1$ everywhere else.
-All sublevel sets $\HE_{\leq t}$ are either the singleton $\{\vec{0}\}$ or the whole space $\HE$, and therefore compact.
-Moreover, $\HE$ is locally-$f$-connected as we prove now.
 
-Let $e > 0$ and $p \in \HE$.
-If $p$ is the origin, we choose $\delta$ between 0 and $\min\{e,1\}$.
-Then $\HE_{\leq f(p) + \delta} = \HE_{\leq \delta} = \{p\}$, so the condition is trivially satisfied.
-For $p$ not the origin, there is a unique $d$-sphere that contains it.
-Clearly, we may choose $\delta$ so small that $B_{\delta}(p)$ contained in this sphere, so $B_{\delta}(p)$ is a disk and the condition follows trivially again.
+\begin{thm} \label{thm:counterexample}
+	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
+Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
+\end{thm}
 
-What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame with respect to singular and \v{C}ech homology.
-Note that $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, so it suffices to show that the singular and \v{C}ech homology of $\HE$ with field coefficients is infinite dimensional.
-The case of singular homology is well know.
+\begin{proof}
+	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
+	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	Let us now verify that $\HE$ is $\HLC$.
+	Let $\epsilon > 0$ and $x \in \HE$.
+	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
+	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
+	For $x$ not the origin, there is a unique $d$-sphere that contains it.
+	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
+	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
+	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
+\end{proof}
+
+\begin{prop}
+	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular and \v{Cech} homology.
+\end{prop}
+
+\begin{proof}
+	The case of singular homology is well know and can be found in \cite{Barratt.1962}.
 	For \v{C}ech homology we use the fact that it commutes with inverse limits for compact Hausdorff spaces.
@@
 	We compute
-\[
+	\begin{equation*}
 	\lim_{k}H_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
-\]
+	\end{equation*}
 	which is infinite-dimensional over $\mathbb{F}$.
 	This finishes the proof.
-
-\begin{rem}
-Note that the singular persistent homology of the sublevel set filtration of $F$ above is also not q-tame because the $d$-dimensional Hawaiian earring has infinite-dimensional $d$-th singular homology \cite{Barratt.1962}.
-\end{rem}
-
-\begin{rem}
-The construction above does not yield a counterexample to \cref{con:q-tame_pers_cech_hom} because $\mathbb{H}^{d}$ is not strongly locally-$F$-connected at the origin.
-\end{rem}
+\end{proof}

### 2021-04-01 introduction.tex
Split preliminaries
Change counterexample: statement using conditions on H-theory

@@
 
+\anibal{I would quote the original verbatim}
 \begin{defi}
@@
 
+\anibal{recall that this is not equivalent to Morse's condition.
+	I would not write down the condition below but refer to the definition in the theorem section.
+	Here I think is better to explain in words sating that we were inspired a condition stronger than the one above that is stable under forward translation.}
+
 \begin{defi}

### 2021-04-01 theorem.tex
Change counterexample: statement using conditions on H-theory

@@
 
-In this section we introduce a stronger version of $\HLC$ for sublevel filtrations, and we show that Morse filtrations with this property are q-tame.
+In this section we introduce a stronger version of $\HLC$ for sublevel filtrations and show that Morse filtrations with this property are q-tame.
 
@@
 \begin{thm} \label{t:strong local connectenss implies q-tameness}
-	Any be a strongly $\HLC$ Morse filtration $(X,f)$ is q-tame, i.e., for every $s < t$ the inclusion $X_s \to X_t$ is $\HS$.
+	Strongly $\HLC$ Morse filtrations are q-tame for any homology theory.
 \end{thm}
@@
 	\end{equation*}
-	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then $A_{3,2} \to A_{1,2}$ does as well.
+	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then so does $A_{3,2} \to A_{1,2}$.
 \end{lem}
@@
 \begin{proof}
-	This is proven via a straightforward diagram chase. For complete details see Lemma 17.3 in \cite{Bredon.1968}.
+	This is proven via a straightforward diagram chase. For more details see Lemma 17.3 in \cite{Bredon.1968}.
 \end{proof}
@@
 \begin{proof}
+	We need to prove that the inclusion $X_s \to X_t$ is $\HS$ for every $s < t$.
+
 	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $\H_{n-1}$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.

### 2021-04-01 counterexample.tex
Change counterexample: statement using conditions on H-theory

@@
 	\end{tikzpicture}
-	\caption{A closeup of the Hawaiian hearing $\mathbb{H}^1$.}
+	\caption{TBW}
 	\label{fig:earrings}
@@
 
-In this section we show that a sublevel filtration can be $\HLC$ and not q-tame for most homology theories of interest.
+In this section we show that a sublevel filtration can be $\HLC$ and not q-tame.
 
@@
 \begin{thm} \label{thm:counterexample}
-	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
+	Let $\H$ be a homology theory such that its value at a point is finitely generated for every degree and at $\HE$ is not finitely generated in some degree.
 Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
@@
 	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
-	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	To verify that $(\HE,f)$ is Morse we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
 	Let us now verify that $\HE$ is $\HLC$.

### 2021-04-03 historical.tex
Add section: historical remarks

\section{Historical remarks}

Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}. This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}. To achieve q-tameness, Morse wants to use the following condition, which he refers to as \textit{local $F$-connectivity}. 
\begin{displaycquote}[p.431]{Morse.1940}
	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
\end{displaycquote}
Morse then states that as consequence of bounded compactness and local $F$-connectivity the rank of the persistence Vietoris homology module associated to $(M, F)$ is q-tame.
In the original it reads:
\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
	Let $a$ and $c$ be positive constants such that $a < c < 1$.
	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
\end{displaycquote}
The proof Morse cites, found in \cite[Theorem 6.1]{Morse.1938}, is not correct; neither is the statement.
A stronger notion of local connectivity for the pair $(M, F)$ is needed to prove q-tameness.
Such condition had already appeared in print, introduced by Morse himself, three years earlier.
\begin{displaycquote}[p.421-422]{Morse.1937}
	The space $M$ will be said to be locally $F$-connected for the order $n$ if corresponding to $n$, an arbitrary point $p$ on $M$, and an arbitrary positive constant $e$, there exists a positive constant $\delta$ with the following property. For $c \geq F(p)$ any singular $n$-sphere on $F \leq c$ (the continuous image on $F \leq c$ of an ordinary $n$-sphere) on the $\delta$-neighborhood $p_{\delta}$ of $p$ is the boundary of a singular $(n + 1)$-cell on $F \leq c + e$ and on $p_e$.
\end{displaycquote}
This notion of local-$f$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
Following the introduction of this stronger definition Morse states as \cite[Theorem~9.2, p.422]{Morse.1937} that q-tameness follows from this form of local $F$-connectivity and bounded compactness, adding that the proof ``while not difficult involves too great detail to be presented here".

%From our current viewpoint it is simple to identify an important problem with both of these definitions of local $F$-connectivity, since they seem to assume that all singular homology classes can be represented by spheres, a fact that the fundamental class of a torus disproves.
%Nonetheless, the distinction between the two teach us valuable lessons: q-tameness follows from bounded compactness and a modern interpretation of the second but not the first.\footnote{These are presented as Definitions \ref{defi:local_connectedness} and \ref{defi:strong_local_connectedness}}

### 2021-04-03 introduction.tex
Add section: historical remarks

--- 2021-03-31 introduction.tex
@@
 	\item We expect this paper to help the ongoing development of persistence methods in geometry.
+	\item Floer theory and simplectic geometry.
 \end{itemize}
@@
 Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
-
-To achieve semi-continuity, Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
-This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
-To achieve q-tameness, Morse wants to use the following condition, given e.g.\@ in \cite{Morse.1940}.
-
-\begin{defi}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function.
-The space $M$ is called \emph{locally-$f$-connected} if for each $p\in M$, $e>0$ and $d\in\mathbb{N}_0$ there exists $\delta\in(0,e)$ such that the map
-	\[
-	\tilde{H}_d(f_{\leq f(p)+\delta}\cap B_{\delta}(p)\hookrightarrow f_{\leq f(p)+e}\cap B_e(p);\mathbb{Z})
-	\]
-	is 0.
-\end{defi}
-
-Here, $\tilde{H}_{d}$ denotes reduced $d$-dimensional singular homology, $f_{\leq t}$ denotes the sublevel set of $f$ at $t\in\R$, and $B_{\delta}(p)$ denotes the open ball with radius $\delta$ around the point $p$.
-Morse then states the claim below as \cite[Theorem 6.3]{Morse.1940}.
-
-\begin{claim}
-	Let $M$ be a metric space and $f\colon M\to\R$ a function such that $M$ is locally-$f$-connected and all sublevel sets are compact.
-Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
-\end{claim}
-
-Here, $\CH_{d}$ denotes $d$-dimensional Vietoris or \v{C}ech homology and $f_{\leq\bullet}$ denotes the sublevel set filtration of $f$.
-He does not prove the statement in the above reference, but cites \cite[Theorem 6.1]{Morse.1938}.
-There, Morse presents a supposed proof of the claim by constructing finite bases for the sets $\im \CH_d(f_{\leq s}\hookrightarrow f_{\leq t};\mathbb{F})$.
-As it turns out, the proof is not correct: We use the Hawaiian earring to construct a counterexample to this claim in Section \ref{sec:counterexample}.
-
-In \cite{Morse.1937}, Morse gives a slightly stronger definition of local-$f$-connectedness, which we will define under a different name to distinguish it from the weaker notion.
-
-\begin{defi} 
-	Let $M$ be a metric space and $f\colon M\to\R$ a function.
-The space $M$ is called \emph{locally-$f$-connected} if for each $p \in M$, $e > 0$ and $d \in \mathbb{N}_0$ there exists $\delta \in (0,e)$ such that for all $c \geq f(p)$ the map
-	\[
-	\tilde{H}_d(f_{\leq c+\delta} \cap B_{\delta}(p) \hookrightarrow f_{\leq c+e} \cap B_e(p); \mathbb{Z})
-	\]
-	is 0.
-\end{defi}
-
-Clearly, strong local-$f$-connectedness implies local-$f$-connectedness.
-Morse also presents the following claim as \cite[Theorem 9.2]{Morse.1937}, but states immediately thereafter that the proof "while not difficult involves too great detail to be presented here".
-
-\begin{claim}
-	Let $M$ be a metric space and $f \colon M \to \R$ a function such that $M$ is strongly locally-$f$-connected and all sublevel sets are compact.
-	Then $\CH_d(f_{\leq\bullet};\mathbb{F})$ is q-tame for any $d$ and any field $\mathbb{F}$.
-\end{claim}
-
-We devote Section \ref{sec:theorem} to its proof.

### 2021-04-03 theorem.tex
Add section: historical remarks

@@
 
-\begin{defi}
+\begin{defi} \label{defi:strong_local_connectedness}
 	A sublevel filtration $(X,f)$ is said to be \textit{strongly} $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and

### 2021-04-03 connectivity.tex
Consolidate sections connectivity, counterexample and theorem

--- 2021-04-01 connectivity.tex
@@
-\section{Local connectivity}
+\section{Local connectivity and q-tameness}
 
@@
 	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
-
-	A sublevel filtration $(X,f)$ is said to be $\emph{homologically locally connected}$, denoted $\HLC$, if for each $x \in X$, neighborhood $V$ of $x$ and $\epsilon > 0$ there exists $U$ a neighborhood of $x$ with $U \subseteq V$ and $\delta \in (0, \epsilon)$ such that
-	\begin{equation*}
-	X_{\leq f(x) + \delta} \cap U \to X_{f(x) + \epsilon} \cap V
-	\end{equation*}
-	is $\HT$.
 \end{defi}
-
-%\anibal{Use a different example, $\HE$ not yet defined.}
-%\begin{ex}
-%	The $d$-dimensional Hawaiian earring $\HE$ is not $\HLC$.
-However, if we consider $\HE$ as a subspace of $\mathbb{H}^{d'}$ via the obvious embedding for $d < d'$, then $\HE$ is $\HLC$ in $\mathbb{H}^{d'}$.
-%\end{ex}
 
@@
 
-\begin{prop}[{\cite{MR105677, MR1481706}}]\label{prop:cech_sing_hom_hlc}
+\begin{prop}[{\cite{MR105677, MR1481706}}] \label{prop:cech_sing_hom_hlc}
 	On the category of paracompact Hausdorff $\HLC$ spaces, \v{C}ech and singular homology with arbitrary coefficients coincide.
@@
 
-We also get a persistent version by applying the above pointwise.
+For more results of this type, we refer to \cite{MR1481706}. There, the above proposition \cite[Corollary VI.12.6]{MR1481706} and many similar ones are proven using sheaf theoretic methods.
+For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
+
+For sublevel filtrations we obtain the following persistence version of Proposition~\ref{prop:cech_sing_hom_hlc} obtained by applying it pointwise.
 
@@
 
-For more results of this type, we refer to \cite{MR1481706}. There, the above proposition \cite[Corollary VI.12.6]{MR1481706} and many similar ones are proven using sheaf theoretic methods.
-For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
-Using Bredon's results, we also get the following.
+We are interested in statements that bound the dimension of homology with field coefficients.
+In the non-filtered context one has the following result.
 
@@
 \end{prop}
-\anibal{Does this really needs field coefficients?} 
+
 \begin{proof}
@@
 
-Again, we get a persistent version.
+Again, there is a persistent version for sublevel filtrations.
 
 \begin{cor}
-	Let $(X, f)$ be a sublevel filtration. If each sublevel set is compact and $\HLC$
-	Then its singular persistence module is p.f.d. in every degree.
+	Let $(X, f)$ be a sublevel filtration. If each sublevel set is compact and $\HLC$, then its singular persistence module is p.f.d. in every degree, in particular q-tame.
 \end{cor}
+
+Having each space in a sublevel filtration being $\HLC$ is in many cases too restrictive.
+We would like a relative condition for sublevel filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
+
+\begin{defi} \label{defi:local_connectedness_filtrations}
+	For a fix homology theory $\H$.
+A sublevel filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
+	\begin{equation*}
+	X_{\leq f(x) + \delta + c} \cap U \to X_{f(x) + \epsilon + c} \cap V
+	\end{equation*}
+	is $\HT$ for every $c \geq 0$.
+	We also consider a weaker version, referred to as \textit{weakly} $\HLC$, defined as above with $c = 0$.
+\end{defi}
+
+We remark that if $\H$ is singular homology, both conditions of $\HLC$ for a Morse filtration $(M,f)$ are respectively equivalent to Morse's definitions of locally $f$-connectedness when $M$ is a metric space.
+Please consult the historical recount presented in Section~\ref{sec:historical}.
+
+We will now show that the weak notion does not imply q-tameness in general.
+To do so let us consider the \textit{$d$-dimensional Hawaiian earring}
+\begin{equation*}
+\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
+\end{equation*}
+
+\begin{figure}[t]
+	\centering
+	\begin{tikzpicture}[scale=88]
+	\draw[thick] (-.1,0) rectangle (.1,.05);
+	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
+	\foreach \i in {1,...,100}{
+		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
+	}
+	\end{tikzpicture}
+	\caption{A closeup of the Hawaiian hearing $\mathbb{H}^1$.}
+	\label{fig:earrings}
+\end{figure}
+
+\begin{thm} \label{thm:counterexample}
+	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
+Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
+\end{thm}
+
+\begin{proof}
+	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
+	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	Let us now verify that $\HE$ is $\HLC$.
+	Let $\epsilon > 0$ and $x \in \HE$.
+	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
+	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
+	For $x$ not the origin, there is a unique $d$-sphere that contains it.
+	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
+	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
+	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
+\end{proof}
+
+The theories that we are most interested in do satisfy these conditions.
+
+\begin{prop}
+	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular and \v{Cech} homology.
+\end{prop}
+
+\begin{proof}
+	The case of singular homology is well know and can be found in \cite{Barratt.1962}.
+	For \v{C}ech homology we use the fact that it commutes with inverse limits for compact Hausdorff spaces.
+	Define 
+	\begin{align*}
+	\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
+	&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+	\end{align*}
+	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+	We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
+	One can easily check that each $\mathbb{H}^{d}_{k}$ satisfies the assumptions for \cref{prop:cech_sing_hom_hlc}, which implies $\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim_{k}H_{d}(\mathbb{H}^{d}_{k})$.
+	We compute
+	\begin{equation*}
+	\lim_{k}H_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+	\end{equation*}
+	which is infinite-dimensional over $\mathbb{F}$.
+	This finishes the proof.
+\end{proof}
+
+Now we verify that Morse filtrations which are $\HLC$ are q-tame.
+We will need three lemmas.
+
+\begin{lem} \label{l:commutative algebra}
+	Given a commutative diagram of modules over a principal ideal domain
+	\begin{equation*}
+	\begin{tikzcd}
+	A_{1,1} \arrow[r] & A_{1,2} & \\
+	A_{2,1} \arrow[r] \arrow[u] & A_{2,2} \arrow[r] \arrow[u] & A_{2,3} \\
+	& A_{3,2} \arrow[r] \arrow[u] & A_{3,3} \arrow[u]
+	\end{tikzcd}
+	\end{equation*}
+	where the middle row is exact and both $A_{2,1} \to A_{1,1}$ and $A_{3,3} \to A_{2,3}$ have finitely generated images, then so does $A_{3,2} \to A_{1,2}$.
+\end{lem}
+
+\begin{proof}
+	This is proven via a straightforward diagram chase. For more details see Lemma 17.3 in \cite{Bredon.1968}.
+\end{proof}
+
+\begin{lem} \label{l:neighborhood third}
+	Let $X$ be locally compact space.
+	For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
+	\begin{equation*}
+	K \subseteq \interior(K^\prime) \subseteq K^\prime \subseteq U.
+	\end{equation*}
+\end{lem}
+
+\begin{proof}
+	For any $x \in K$ choose a compact neighborhood $C(x) \subseteq U$.
+	We have
+	\begin{equation*}
+	K \subseteq \bigcup_K \interior(C(x)) \subseteq \interior\left(\bigcup_K C(x)\right) \subseteq \bigcup_K C(x) \subseteq U
+	\end{equation*}
+	Since $K$ is compact, the first inclusion above is achieved over a finite subset $\{x_1, \dots, x_m\}$ of elements in $K$.
+	Defining $K^\prime = \bigcup_{i=1}^m C(x_i)$ finishes the proof.
+\end{proof}
+
+\begin{lem} \label{l:key lemma for q-tameness}
+	Fix a homology theory. Let $(X,f)$ be a $\HLC$ Morse filtration.
+	Consider sets $K, L \subseteq X$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap X_{s+\delta} \to L \cap X_{t}$ is $\HS$.
+\end{lem}
+
+\begin{proof}
+	We need to prove that the inclusion $X_s \to X_t$ is $\HS$ for every $s < t$.
+
+	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $\H_{n-1}$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
+
+	Given a compact set $L \subseteq X$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U(K)$ of $K$ such that $U(K) \cap X_{s+\delta_K} \to L \cap X_{t}$ is $\HS_n$.
+
+	We start by showing that any element of $\interior(L) \cap X_s$ has a neighborhood in $\Sigma_{s, t}$.
+	Let $x \in \interior(L) \cap X_{s}$.
+	Consider an open neighborhood $U(x)$ of $x$ contained in $\interior(L)$, and take $\epsilon > 0$ such that $s + \epsilon < t$.
+	By the strong $\HLC$ of $(X,f)$ there is a $\delta \in (0, \epsilon)$ and an open neighborhood $W(x) \subseteq U(x)$ such that for $c = s - f(x)$ the following composition is $\HS$:
+	\begin{equation*}
+	W(x) \cap X_{f(x) + c + \delta} \to
+	U(x) \cap X_{f(x) + c + e} \to
+	L \cap X_{t}.
+	\end{equation*}
+	By local connectivity we can choose a compact neighborhood of $x$ contained in $W(x)$.
+	This proves the claim.
+
+	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
+	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap X_{s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
+	We Use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
+	\begin{equation*}
+	K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime \subseteq U_i.
+	\end{equation*}
+	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap X_{s+\delta} \to L \cap X_t$ is $\HS_n$.
+	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_s \to K_1^\prime \cap K_2^\prime \cap X_{s+\delta}$ is $\HS_{(n-1)}$.
+	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:
+	\begin{equation*}
+	\begin{tikzcd}
+	\H_n(L \cap X_t) \oplus \H_n(L \cap X_t) \arrow[r] &
+	\H_n(L \cap X_t) & \\
+	\H_{n}(K_1^\prime \cap X_{s+\delta}) \oplus \H_n(K_2^\prime \cap X_{s+\delta}) \arrow[r] \arrow[u] & 
+	\H_{n}((K_1^\prime \cap X_{s+\delta}) \cup (K_2^\prime \cap X_{s+\delta})) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap X_{s+\delta}) \\ & 
+	\H_{n}((K_1 \cup K_2) \cap X_s) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1 \cap K_2 \cap X_s). \arrow[u]
+	\end{tikzcd}
+	\end{equation*}
+	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
+	Since any compact $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
+\end{proof}
+
+\begin{thm} \label{t:strong local connectenss implies q-tameness}
+	Morse filtrations which are $\HLC$ give rise to q-tame persistence modules for any homology theory.
+\end{thm}
+
+\begin{proof}
+	It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = X_{\leq s}$ and $L = X$.
+\end{proof}

### 2021-04-03 historical.tex
Consolidate sections connectivity, counterexample and theorem

@@
-\section{Historical remarks}
+\section{Historical remarks} \label{sec:historical}
 
@@
 \end{displaycquote}
-This notion of local-$f$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
+This notion of local-$F$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
 Following the introduction of this stronger definition Morse states as \cite[Theorem~9.2, p.422]{Morse.1937} that q-tameness follows from this form of local $F$-connectivity and bounded compactness, adding that the proof ``while not difficult involves too great detail to be presented here".

### 2021-04-03 persistence.tex
Split preliminaries
Consolidate sections connectivity, counterexample and theorem

--- 2021-03-30 preliminaries.tex
@@
-\section{Preliminaries}
+\section{Persistence}
 
 \begin{itemize}
-	\item metric space
-	\item upper semi-continuous function
 	\item Persistence module
+	\item p.f.d
 	\item q-tameness
@@
 
-\begin{defi}
-	Let $M$ be a metric space. For any $p \in M$ and $\epsilon \geq 0$ denote
-	\begin{equation*}
-	B_\epsilon(p) = \{q \in M\ |\ d(p,q) < \epsilon\}, \qquad
-	\overline B_\epsilon(p) = \{q \in M\ |\ d(p,q) \leq \epsilon\}.
-	\end{equation*}
-\end{defi}
-
-\begin{defi}
-	Let $X$ be a space and $f \colon X \to \R$ a function. For any $t \in \R$, the \textit{$t$-sublevel set of $f$} is defined by 
+A \textit{sublevel filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
+For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
 \begin{equation*}
@@
 \end{equation*}
-\end{defi}
+
+Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x$ in $X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every $x$ in $X$, every neighborhood of $x$ contains a compact neighborhood of $x$.
+
+A sublevel filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
+Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.

### 2021-04-06 historical.tex
Improve introduction

@@
 \section{Historical remarks} \label{sec:historical}
+
+The approach of Morse and Tompkins in \cite{Morse.1939} was to give a topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
+For a more detailed review of their work we refer to \cite{Struwe.1988}.
+In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.gchoosing.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation." More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
 
@@
 %Nonetheless, the distinction between the two teach us valuable lessons: q-tameness follows from bounded compactness and a modern interpretation of the second but not the first.\footnote{These are presented as Definitions \ref{defi:local_connectedness} and \ref{defi:strong_local_connectedness}}
+
+%By now, however, Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in a different context, namely topological data analysis.
+More specifically, Morse studies how the homology of the sublevel sets of a function change as the level changes.
+He defines spaces that encode the same information as the modern persistent homology groups, as well as quantities that correspond to the modern notions of birth and death.
+Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).

### 2021-04-06 introduction.tex
Improve introduction

@@
 
-\begin{itemize}
-	\item Persistence homology, 
-	\item applications in applied topology, application in theoretical topology, 
-	\item barcode, stability, existence of barcode motivates q-tameness. 
-	\item When can we ensure this condition? 
-	\item Morse as a precursor. Geodesic study, natural next context: minimal surfaces, \item proposed condition for q-tameness, it's wrong, 
-	\item a similar condition, assumed equivalent, we prove this implies it.
-	\item We expect this paper to help the ongoing development of persistence methods in geometry.
-	\item Floer theory and simplectic geometry.
-\end{itemize}
+The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
+When thinking about the work of Morse, a smooth function on a closed differential manifold is possibly our first association, but it should not be our last.
+This finite dimensional context was masterfully summarized in Milnor's famous book on the subject \cite{MR0163331}, where he also developed an application beyond that setting, giving a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Another example of the importance of Morse's insights in infinite dimensional settings is Floer's work on the Arnold conjecture.
+Morse himself worked in a significantly less constraint context, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established a broad theory for functionals on metric spaces which are only semi-continuous, naming it Functional Topology.
+A motivating problem for him came from the study of minimal surfaces.
+In 1931, Jesse Douglas solved Plateau’s Problem \cite{Douglas.1931} for which he received the fields medal in 1936.
+The problem amounts to finding for a given admissible boundary curve $\Gamma$ embedded in euclidean space an area-minimizing embedded surface $\Sigma$ with $\partial \Sigma = \Gamma$.
+In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used Functional Topology to give conditions for the existence of unstable minimal surfaces, i.e., critical points of the area functional that do not locally minimize area.
 
-Nowadays, when thinking of Marston Morse's work, the first thing that comes to mind is the theory of critical points of his eponymous Morse functions, as presented e.g.\@ in Milnor's famous book \cite{MR0163331}, with a key result being the Morse inequalities for the number of critical points of a function.
-In the 1930s, however, Morse published a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established a much more general theory of critical points and Morse inequalities for not even necessarily continuous functions on metric spaces.
-He termed this general theory Functional Topology because his goal was to use it to study critical points of functionals by topological means.
-In particular, he was interested in existence results for unstable minimal surfaces, i.e., critical points of the area functional for a given boundary curve that are not minimizers of area \cite{Morse.1939,Morse.1941}.
-This work with Tompkins was building on the work of Douglas who solved the general version of Plateau's Problem \cite{Douglas.1931}.
+Some of Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in Topological Data Analysis.
+Morse studied the topology of a sublevel filtration and he introduced invariants that encode the same information as the modern persistent homology groups.
+%as well as quantities that correspond to the modern notions of birth and death of a feature.
+Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial for this point of view: The use of homology with field coefficients and the restriction to functionals giving rise to persistence modules with interval decompositions.
 
-The approach of Morse and Tompkins in \cite{Morse.1939} was to give a topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
-For a more detailed review of their work we refer to \cite{Struwe.1988}.
-In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.gchoosing.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation." More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
+In modern applications of the theory of persistence to problems in geometry, the existence of an interval decomposition allows the use of the bottleneck and other metrics on the space of barcodes.
+Rendering a finite metric model on which geometric problems can be recasted.
 
-By now, however, Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in a different context, namely topological data analysis.
-More specifically, Morse studies how the homology of the sublevel sets of a function change as the level changes.
-He defines spaces that encode the same information as the modern persistent homology groups, as well as quantities that correspond to the modern notions of birth and death.
-Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
+Given the semi-continuity of a functional, it was shown in \cite{schmahl2020structure} that the key condition needed for the existence of such decomposition is the q-tameness of the associated persistence module.
+This condition simply states that the inclusion of \textit{distinct} sublevel sets induces a linear map with finite dimensional rank.
+
+The most delicate of the conditions on a sublevel filtration used by Morse and others to obtained q-tameness is a form of local-connectivity.
+In their study of minimal surfaces, Morse and Tompkins stated that the form of local connectivity presented there is enough to imply q-tameness, but neither the proof nor the statement is correct, please see Theorem~\ref{thm:counterexample}.
+In earlier writings, a stronger version was given by Morse and assumed to imply q-tameness.
+This claim is correct and we provide a proof for as Theorem~\ref{t:strong local connectenss implies q-tameness}.
+Please see Section~\ref{sec:historical} for the history of this issue.
+
+The relationship between q-tameness and different forms of local connectivity is the focus of this paper.
+With future applications to geometry in mind, we provide a detailed analysis of q-tameness and two modern versions of Morse's local connectivity assumptions.
+
+In Section 2 ...

### 2021-04-06 connectivity.tex
Improve introduction
Updates from Overleaf

@@
 \begin{equation*}
-\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
+\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
 \end{equation*}
@@
 	\end{tikzpicture}
-	\caption{A closeup of the Hawaiian hearing $\mathbb{H}^1$.}
+	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
 	\label{fig:earrings}
@@
 	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
-Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration that is not q-tame.
+Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration
+	\todo{weakly?}
+	that is not q-tame.
 \end{thm}
@@
 \begin{prop}
-	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular and \v{Cech} homology.
+	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular homology with any coefficients and \v{Cech} homology with field coefficients.
 \end{prop}
@@
 	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+	\todo{inequality?}
 	We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.

### 2021-04-09 connectivity.tex
Add historical stuff from Max thesis

@@
 For more results of this type, we refer to \cite{MR1481706}. There, the above proposition \cite[Corollary VI.12.6]{MR1481706} and many similar ones are proven using sheaf theoretic methods.
-For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel-Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
+For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel--Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
 
@@
 \end{equation*}
+\todo{credit to Milnor}
 
@@
 \begin{thm} \label{thm:counterexample}
-	Let $\H$ be a homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
-Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a $\HLC$ Morse filtration
-	\todo{weakly?}
-	that is not q-tame.
+	Let $\H$ be a (generalized) homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
+Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\HLC$ Morse filtration that is not q-tame.
 \end{thm}
@@
 	\begin{align*}
-	\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{k}\right)^2\right\}\\
+	\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2 \leq \left(\frac{1}{k}\right)^2\right\}\\
 	&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
@@
 	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-	\todo{inequality?}
 	We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
-	One can easily check that each $\mathbb{H}^{d}_{k}$ satisfies the assumptions for \cref{prop:cech_sing_hom_hlc}, which implies $\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim_{k}H_{d}(\mathbb{H}^{d}_{k})$.
-	We compute
+	Clearly, each $\mathbb{H}^{d}_{k}$ is a CW-complex, so we can simply use cellular homology to compute
 	\begin{equation*}
-	\lim_{k}H_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+	\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
 	\end{equation*}
@@
 	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap X_{s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
-	We Use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
+	We use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
 	\begin{equation*}
@@
 	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_s \to K_1^\prime \cap K_2^\prime \cap X_{s+\delta}$ is $\HS_{(n-1)}$.
-	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:
+	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:\todo{check assumptions for mayer-vietoris to apply}
 	\begin{equation*}
@@
 	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
-	Since any compact $K \subseteq \interior(L)$ can be expressed as a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
+	Since any compact $K \subseteq \interior(L)$ can be covered by a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
 \end{proof}

### 2021-04-09 historical.tex
Add historical stuff from Max thesis

@@
 Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
+
+\todo{Max: the following subsections are taken verbatim from my thesis and not adapted to this paper yet} 
+\subsection{Critical Points}
+So far, we have mostly talked about changes in the homology of sublevel sets at certain \emph{values} since this is what is studied in persistent homology.
+The original motivation to study Functional Topology was, however, the study of critical \emph{points}, which we briefly touched upon in section \ref{sec:morse}.
+
+In \cite{Morse.1939}, Morse and Tompkins make the following definition.
+
+\begin{defi}
+Let $(M,d)$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+We say $p\in M$ is a \emph{homotopically ordinary point of $f$} if there is a neighborhood $U$ of $p$ in $f_{\leq f(p)}$ and a continuous map $H\colon U\times[0,1]\to M$ such that
+\begin{itemize}
+\item $H(q,0)=q$ for all $q$,
+\item $H(p,1)\neq p$ and
+\item for any $e>0$ there exists $\delta>0$ with the property that whenever $s<s'$ and $d(H(q,s),H(q,s'))>e$ hold, we have $f(H(q,s))-f(H(q,s'))>\delta$.
+\end{itemize}
+We say that $p$ is a \emph{homotopically critical point of $f$} if it is not homotopically ordinary.
+\end{defi}
+
+Roughly, one can think of homotopically critical points of $f$ as points $p$ that have no neighborhood in $f_{\leq f(p)}$ that can be mapped by a homotopy into $f_{\leq t}$ for some $t<f(p)$.
+
+In the case of isolated critical points, one can then choose a neighborhood $U$ of a homotopically critical point $p$ not containing any other critical point and define the \emph{cap type numbers of $p$} as the cap type numbers of the relative homology lattice associated to the restriction of $f$ to this neighborhood.
+The total cap type numbers are then defined as the sums of all of these cap type numbers.
+Assuming a finite number of critical points, Morse and Tompkins then proceed to state Morse inequalities for these total cap type numbers, referring to \cite{Morse.1940}, which was still in preparation at that time, for proof.
+
+More generally, in the non-isolated case, they consider closed sets of critical points possessing a neighborhood that does not contain any other critical points and call these \emph{critical sets}.
+Again, one can then define the cap type numbers of such sets as the cap type numbers of $f$ restricted to the corresponding neighborhood.
+In order to get Morse inequalities in this setting, without assuming that the critical points are finite in number, Morse and Tompkins additionally assume local-$f$-connectedness and again refer to \cite{Morse.1940} for proof.
+However, the proofs that Morse presents there repeatedly make use of his erroneous claim that local-$f$-connectedness implies q-tameness, so they cannot be seen as valid.
+
+\subsection{The Douglas Functional}
+After the previously described general statements on critical points, Morse and Tompkins then consider the following setting introduced in even greater generality by Douglas: Let $g=(g_i)\colon\mathbb{R}\to\mathbb{R}^n$ be a simple closed curve such that $g$ is differentiable and such that each $g'_i$ is Lipschitz.
+Assume that $g$ is $2\pi$-periodic.
+Let $\tilde{\Omega}$ be the space of continuous functions $\varphi\colon\mathbb{R}\to\mathbb{R}$ with $\varphi((t)+2\pi)=\varphi(t)+2\pi$ for all $t$ and such that there are three distinct points $\alpha_i\in[0,2\pi)$ with $\varphi(\alpha_i)=\alpha_i$.
+We define the \emph{Douglas-functional} associated to the curve $g$ on $\tilde{\Omega}$ by $$A_g(\varphi)=\frac{1}{16}\int_0^{2\pi}\int_0^{2\pi}\sin\left(\frac{\alpha-\beta}{2}\right)^{-2}\lVert g(\varphi(\alpha))-g(\varphi(\beta)) \rVert_2^2\mathrm{d}\alpha\mathrm{d}\beta$$ and set $$\Omega_g=\{\varphi\in\tilde\Omega\mid A_g(\varphi)<\infty\}.$$ Douglas proved that, for even more general $g$ than above, $\Omega_g$ is non-empty and that sublevel sets of $A_g$ on $\Omega_g$ are compact.
+Since $A_g$ is clearly bounded below by $0$, this implies that $A_g$ has a unique global minimizer.
+Douglas then used harmonic analysis to show that this minimizer of $A_g$ corresponds to a solution of Plateau's Problem.
+More generally, each critical point of this functional $A_g$ corresponds to a critical point of the area functional.
+
+Now, Morse and Tompkins first assume that $A_g$ has finitely many homotopically critical points.
+They show that any homotopically critical point of $A_g$ is also a critical point in the classical sense.
+They verify the other assumptions they make for the Morse inequalities and then conclude via these inequalities that if $A_g$ has two distinct minimizers, it must also have a critical point of index 1, i.e.
+with non-zero first cap type number.
+This type of result is often called a Mountain Pass Lemma.
+
+In order to remove the finiteness assumptions, they go on to prove local-$A_g$-connectedness for $\Omega_g$ and require that the two minimizers are contained in disjoint critical sets.
+Again using the Morse inequalities, they infer the existence of an unstable minimal surface.
+As we have mentioned before, Morse's proof in \cite{Morse.1940} of the Morse inequalities in this general case is faulty since local-$A_g$-connectedness is not enough to imply the necessary q-tameness.
+However, the proof of local-$A_g$-connectedness in \cite{Morse.1939} actually shows that $\Omega_g$ is strongly locally-$A_g$-connected.
+In fact, Morse and Tompkins even show that each sublevel set of $A_g$ is locally contractible in all larger sublevel sets.
+So if our previous conjectures are true, the general theory can be applied and their approach still works.

### 2021-04-09 homology.tex
Consolidate sections connectivity, counterexample and theorem
Add historical stuff from Max thesis

@@
-\subsection{Homology theories}
+\section{Homology theories}
 
 \begin{itemize}
-	\item Definition
-	\item Examples, main: singular with integer coeff and cech with field 
+\item Definition (generalized homology theory, without dimension axiom, but with Milnor's additivity axiom)
+\item Examples, main: singular with integer coeff and cech with field \cite{Kelly.1961}
+\item mention Dowker duality
 \item Mayer-Vietoris
 \end{itemize}
+
+\todo{Uli: I saw a discussion about the topological invariance of Vietoris homology for non-compact metric spaces.
+I thought that it suggested that invariance holds only for compact spaces,
+but I can't find it anymore.
+
+What I found was this:
+\url{http://pldml.icm.edu.pl/pldml/element/bwmeta1.element.zamlynska-8f369e96-b1eb-4ec9-99e2-8c366367a5a4} claims invariance also for non-compact.
+\url{https://www.ams.org/journals/tran/1947-062-02/S0002-9947-1947-0024128-6/S0002-9947-1947-0024128-6.pdf} mentions a non-invariant property "null-bounding"
+}

### 2021-04-09 persistence.tex
Add historical stuff from Max thesis

@@
 
-\begin{itemize}
-	\item Persistence module
-	\item p.f.d
-	\item q-tameness
-	\item Barcode
-	\item bottleneck
-	\item stability
-\end{itemize}
+\todo{start with the standard vector space setting, before generalizing?}
+Let $R$ be a ring.
+The category of \emph{persistence $R$-modules} is the functor category  $(\Mod{R})^{\mathbf{R}}$, where $\mathbf{R}$ is the category corresponding to the real numbers $\mathbb{R}$ considered as a poset.
+We will simply say \emph{persistence module} if the coefficient ring is clear from the context.
+
+A persistence module $M$ is called \emph{pointwise finitely generated (p.f.g.)} if $M_{t}$ is a finitely generated module for every $t\in\mathbb{R}$.
+$M$ is called \emph{q-tame} if $\im (M_{s}\to M_{t})$ is finitely generated for all $s<t\in\mathbb{R}$.
+
+The theory of persistence modules is particularly nice if $R=\mathbb{F}$ is a field, which we will assume for the rest of this section.
+In this case, we will say that $M$ is \emph{pointwise finite-dimensional (p.f.d.)} instead of p.f.g.
+
+What makes the field coefficient case nice is that it allows for a combinatorial description of many persistence modules in terms of basic summands.
+Concretely, we say that $M$ has a \emph{barcode} if there is a family of intervals $(I_{\alpha})_{\alpha}$, $I_{\alpha}\subseteq\mathbb{R}$ such that
+\[
+M\cong\bigoplus_{\alpha} C(I_{\alpha}),
+\]
+where the persistence module $C(I)$ for an interval $I$ is defined via
+\[
+C(I)_t=
+\begin{cases}
+    \mathbb{F} & \text{if } t\in I,\\
+    0              & \text{otherwise,}
+\end{cases}
+\qquad
+\text{with structure maps}
+\qquad
+C(I)_{t,u}=
+\begin{cases}
+    \operatorname{id}_{\mathbb{F}} & \text{if } t,u\in I,\\
+    0              & \text{otherwise.}
+\end{cases}
+\]
+
+Interval modules are indecomposable in the category of persistence modules and by the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832}, two direct sums of interval modules can only be isomorphic if the corresponding families of intervals already agree.
+Hence, we can speak of \emph{the} barcode of a persistence module and use it as a complete isomorphism invariant.
+
+Unfortunately, not every persistence module has a barcode, so general existence results are important to have.
+The most widely used of these is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, which asserts that every p.f.d.\ persistence module has a barcode.
+
+As is well-known, Crawley-Boevey's Theorem does not extend to q-tame persistence modules.
+However, there are still ways to get a notion of barcode for q-tame persistence modules, for example by phrasing the definition of barcode in terms of so-called rectangle measures \cite{Chazal.2016a}.
+Other methods include using a slightly weaker notion of isomorphism for the direct sum decomposition into interval modules \cite{Chazal.2016b} or imposing additional algebraic constraints and allowing for the decompositions to be in terms of products instead of sums \cite{schmahl2020structure}.
+For each of these alternative methods, restricting to the p.f.d.\ setting recovers the basic notion of barcode discussed before.
+
+The usefulness of barcodes in applications often rests on their stability.
+To make precise what stability means, we define the \emph{interleaving distance} between two persistence modules $M$ and $N$ as
+\[
+d_{I}(M,N)=\inf\{\delta>0\mid\text{there exists a }\delta\text{-interleaving between }M\text{ and }N\},
+\]
+where a $\delta$-interleaving between $M$ and $N$ is given by a collection of maps $M_{t}\to N_{t+\delta}$ and $N_{t}\to M_{t+\delta}$ for each $t\in\mathbb{R}$ such that the diagrams
+\[
+\begin{tikzcd}
+M_s\arrow[r]\arrow[d] & M_t\arrow[d] \\
+N_{s+\delta}\arrow[r] & N_{t+\delta}
+\end{tikzcd}
+\qquad
+\begin{tikzcd}
+N_s\arrow[r]\arrow[d] & N_t\arrow[d] \\
+M_{s+\delta}\arrow[r] & M_{t+\delta}
+\end{tikzcd}
+\qquad
+\begin{tikzcd}
+M_{t-\delta}\arrow[rd]\arrow[r]& M_{t}\arrow[rd]\arrow[r] & M_{t+\delta} \\
+N_{t-\delta}\arrow[ru]\arrow[r]& N_{t}\arrow[ru]\arrow[r] & N_{t+\delta}
+\end{tikzcd}
+\]
+commute for all $s<t\in\mathbb{R}$.
+
+We also define the \emph{Bottleneck distance} between two barcodes $B=(I_{\alpha})_{\alpha\in A}$ and $B'=(I'_{\alpha'})_{\alpha'\in A'})$ as
+\[
+d_{b}(B,B')=\inf\{\delta>0\mid\text{there exists a }\delta\text{-matching between }M\text{ and }N\},
+\]
+where a $\delta$-matching between $B$ and $B'$ is given by subsets $X\subseteq A$, $X'\subseteq A'$ and a bijection $\sigma\colon X\to X'$ such that
+\[
+\lvert \sup I - \inf I \rvert < 2\delta
+\]
+whenever there is $\alpha\in A\setminus X$ with $I=I_{\alpha}$ or $\alpha'\in A'\setminus X'$ with $I=I'_{\alpha'}$, and
+\begin{align*}
+\lvert \sup I'_{\sigma(\alpha)} - \sup I_{\alpha} \rvert &< \delta \\
+\lvert \inf I'_{\sigma(\alpha)} - \inf I_{\alpha} \rvert &< \delta
+\end{align*}
+for all $\alpha\in X$.
+
+\begin{thm}[\cite{}]\todo{what do we want to cite here?}
+Let $M$ and $M'$ be q-tame persistence modules with barcodes $B$ and $B'$. Then
+\[
+d_{b}(B,B')= d_{I}(M,M').
+\]
+\end{thm}
+
+The most commonly studied example of a persistence module is \emph{persistent homology}, i.e., the persistence module obtained by applying homology to an $\mathbb{R}$-indexed diagram of spaces.
+In what follows, we will study the persistent homology of certain classes of such diagrams, namely filtrations.
 

### 2021-04-09 introduction.tex
Add section by section to intro

@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-When thinking about the work of Morse, a smooth function on a closed differential manifold is possibly our first association, but it should not be our last.
-This finite dimensional context was masterfully summarized in Milnor's famous book on the subject \cite{MR0163331}, where he also developed an application beyond that setting, giving a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
-Another example of the importance of Morse's insights in infinite dimensional settings is Floer's work on the Arnold conjecture.
-Morse himself worked in a significantly less constraint context, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established a broad theory for functionals on metric spaces which are only semi-continuous, naming it Functional Topology.
+Now a days, when thinking about Morse's work a smooth function on a closed differential manifold is possibly our first association, but it need not be our last.
+Morse Theory in this \textit{finite} context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond it to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Another example of the importance of Morse's insights in infinite settings is Floer's work on the Arnold conjecture.
+Morse himself worked in a significantly less constraint context, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context of semi-continuous functionals on metric spaces.
+He name this body of work \textit{functional topology}.
 A motivating problem for him came from the study of minimal surfaces.
 In 1931, Jesse Douglas solved Plateau’s Problem \cite{Douglas.1931} for which he received the fields medal in 1936.
-The problem amounts to finding for a given admissible boundary curve $\Gamma$ embedded in euclidean space an area-minimizing embedded surface $\Sigma$ with $\partial \Sigma = \Gamma$.
-In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used Functional Topology to give conditions for the existence of unstable minimal surfaces, i.e., critical points of the area functional that do not locally minimize area.
+The problem amounts to finding for a given admissible boundary curve $\Gamma$ an area-minimizing embedded surface $\Sigma$ with $\partial \Sigma = \Gamma$.
+In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used functional topology to give conditions for the existence of unstable minimal surfaces, i.e., critical points of the area functional that do not locally minimize area.
 
-Some of Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in Topological Data Analysis.
+Some of Morse's ideas from functional topology, and in particular from \cite{Morse.1940}, have been rediscovered in topological data analysis.
 Morse studied the topology of a sublevel filtration and he introduced invariants that encode the same information as the modern persistent homology groups.
-%as well as quantities that correspond to the modern notions of birth and death of a feature.
-Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial for this point of view: The use of homology with field coefficients and the restriction to functionals giving rise to persistence modules with interval decompositions.
+Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial for this point of view:
+The use of homology with field coefficients and the restriction to functionals giving rise to persistence modules with interval decompositions.
 
@@
 
-Given the semi-continuity of a functional, it was shown in \cite{schmahl2020structure} that the key condition needed for the existence of such decomposition is the q-tameness of the associated persistence module.
-This condition simply states that the inclusion of \textit{distinct} sublevel sets induces a linear map with finite dimensional rank.
+The spaces to which functional topology can be applied to are not necessarily of the homotopy type of CW-complexes, which makes the choice of homology construction an important element of the discussion.
+For many constructions ---including the preferred theory of Morse: \v{C}ech homology--- it was shown in \cite{schmahl2020structure} that the key condition needed for the existence of an interval decomposition of the persistence module associated to a semi-continuous sublevel set filtration is its \textit{q-tameness}.
+This condition simply states that the inclusion of distinct sublevel sets induces a linear map with finite dimensional rank.
 
-The most delicate of the conditions on a sublevel filtration used by Morse and others to obtained q-tameness is a form of local-connectivity.
-In their study of minimal surfaces, Morse and Tompkins stated that the form of local connectivity presented there is enough to imply q-tameness, but neither the proof nor the statement is correct, please see Theorem~\ref{thm:counterexample}.
-In earlier writings, a stronger version was given by Morse and assumed to imply q-tameness.
-This claim is correct and we provide a proof for as Theorem~\ref{t:strong local connectenss implies q-tameness}.
-Please see Section~\ref{sec:historical} for the history of this issue.
+To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel filtration are forms of local-connectivity.
+In their development of functional topology and its applications to minimal surface theory, Morse and Tompkins presented certain forms of local-connectivity claimed to imply q-tameness; unfortunately, neither the proofs nor the statements are correct.
+Please consult Section~\ref{s:historical} for more details on this problem and its history.
 
-The relationship between q-tameness and different forms of local connectivity is the focus of this paper.
-With future applications to geometry in mind, we provide a detailed analysis of q-tameness and two modern versions of Morse's local connectivity assumptions.
+In this paper we analyze in great detail the relationship between different forms of local-connectivity and q-tameness.
+In particular, we show how to strengthen Morse's notion so that the parts of his groundbreaking work depending on q-tameness stand, including the aforementioned critical surface theorem.
 
-In Section 2 ...
+By resurfacing the work of Morse in the novel context of persistence theory, we aim at increasing the number and depth of interactions between this rapidly developing field and geometry, topology, and functional analysis.
+
+An overview of this article follows.
+In Section~\ref{s:homology} we review different constructions of ordinary homology theory including: \v{C}ech, Vietoris and singular.
+In section~\ref{s:persistence} we recall the basics of persistence theory where, for us, the persistence homology of a sublevel set filtration is the key example.
+Section~\ref{s:connectivity} is the core of this work.
+We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply the associated persistence module is q-tame.
+We close with a historical overview of Morse's functional topology in Section~\ref{s:homology}.

### 2021-04-09 connectivity.tex
Add section by section to intro
Improve section, connectivity: remove Bredon.

@@
-\section{Local connectivity and q-tameness}
+\section{Local connectivity and q-tameness} \label{s:connectivity}
 
@@
 
-Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional, see \cite{MR0007094} for early examples.
-For us, the following is relevant.
+Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional.
+We mention the following examples.
+
 Recall that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
-
-\begin{prop}[{\cite{MR105677, MR1481706}}] \label{prop:cech_sing_hom_hlc}
-	On the category of paracompact Hausdorff $\HLC$ spaces, \v{C}ech and singular homology with arbitrary coefficients coincide.
+\begin{prop}[\cite{MR105677}] \label{prop:cech_sing_hom_hlc}
+	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which are $\HLC$ with respect to integral singular homology.
 \end{prop}
 
-For more results of this type, we refer to \cite{MR1481706}. There, the above proposition \cite[Corollary VI.12.6]{MR1481706} and many similar ones are proven using sheaf theoretic methods.
-For example, Bredon also discusses cohomology local connectedness \cite[Section II.17]{MR1481706} and various other comparison results, e.g.\@ between singular and Borel--Moore homology \cite[Corollary V.12.15]{MR1481706} in the presence of homology local connectedness, as well as examples such as spaces that are sheaf cohomology locally connected but not homology locally connected \cite[Example II.17.12]{MR1481706}.
-
-For sublevel filtrations we obtain the following persistence version of Proposition~\ref{prop:cech_sing_hom_hlc} obtained by applying it pointwise.
-
-\begin{cor}\label{cor:cech_sing_persistent_iso}
-	Let $(X, f)$ be a sublevel filtration. If each sublevel set is paracompact and $\HLC$, then its singular and \v{C}ech persistence modules coincide.
-\end{cor}
-
-We are interested in statements that bound the dimension of homology with field coefficients.
-In the non-filtered context one has the following result.
-
 \begin{prop} \label{prop:fin_dim_sing_hom}
-	Let $X$ be a compact Hausdorff $\HLC$ space.
-	Then the singular homology of $X$ with field coefficients is finite-dimensional in every degree.
+	Let $X$ be a compact Hausdorff space.
+	If $X$ is $\HLC$ with respect to integral singular homology, then the singular homology of $X$ with arbitrary coefficients is finite-dimensional in every degree.
 \end{prop}
 
-\begin{proof}
-	By the universal coefficient theorem for homology, trivial singular homology with integer coefficients also implies trivial singular homology for any other coefficient group.
-In particular, this means that $X$ being $HLC^{\infty}$ also implies that $X$ is $HLC^{\infty}_{\mathbb{F}}$.
-By the universal coefficient theorem for cohomology, the singular cohomology with coefficients in $\mathbb{F}$ is naturally isomorphic to the dual space of the singular homology with coefficients in $\mathbb{F}$.
-This means that being $HLC^{\infty}_{\mathbb{F}}$ implies being locally connected with respect to singular cohomology in all degrees with coefficients in $\mathbb{F}$.
-Since we assume $X$ to be $HLC^{\infty}$, \cite[Theorem III.1.1]{MR1481706} now implies that $X$ is locally connected with respect to sheaf cohomology with coefficients in the locally constant sheaf with value $\mathbb{F}$.
-\cite[Corollary II.17.7]{MR1481706} implies that the sheaf cohomology of the whole space with coefficients in this sheaf is finite-dimensional, so again by \cite[Theorem III.1.1]{MR1481706} the same holds for singular cohomology with coefficients in $\mathbb{F}$.
-Applying the universal coefficient theorem once more proves the claim.
-\end{proof}
+We will deduce the previous finiteness result from our main contribution, Theorem~\ref{t:strong local connectenss implies q-tameness}.
+To motivate the statement of our theorem let us record a direct consequence of the previous proposition.
 
-Again, there is a persistent version for sublevel filtrations.
+\begin{prop}
+	Let $(X, f)$ be a sublevel filtration.
+If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d.
+in every degree, in particular q-tame.
+\end{prop}
 
-\begin{cor}
-	Let $(X, f)$ be a sublevel filtration. If each sublevel set is compact and $\HLC$, then its singular persistence module is p.f.d. in every degree, in particular q-tame.
-\end{cor}
-
-Having each space in a sublevel filtration being $\HLC$ is in many cases too restrictive.
+Having each sublevel set being $\HLC$ is in many cases too restrictive.
 We would like a relative condition for sublevel filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
+The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.
 
@@
 	\begin{equation*}
-	X_{\leq f(x) + \delta + c} \cap U \to X_{f(x) + \epsilon + c} \cap V
+	X_{\leq f(x) + \delta + c} \cap U \to X_{\leq f(x) + \epsilon + c} \cap V
 	\end{equation*}
@@
 \end{defi}
-
-We remark that if $\H$ is singular homology, both conditions of $\HLC$ for a Morse filtration $(M,f)$ are respectively equivalent to Morse's definitions of locally $f$-connectedness when $M$ is a metric space.
-Please consult the historical recount presented in Section~\ref{sec:historical}.
 
@@
 \end{equation*}
-\todo{credit to Milnor}
 
@@
 \begin{prop}
-	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular homology with any coefficients and \v{Cech} homology with field coefficients.
+	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular homology with arbitrary coefficients and \v{Cech} homology with field coefficients.
 \end{prop}

### 2021-04-09 introduction.tex
Improve section, connectivity: remove Bredon.

@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Now a days, when thinking about Morse's work a smooth function on a closed differential manifold is possibly our first association, but it need not be our last.
-Morse Theory in this \textit{finite} context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond it to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Now a days, when thinking about the pioneering work of Morse in this interplay, a smooth function on a closed differential manifold is possibly our first association but, as we describe next, it should not be our last.
+Morse Theory in the \textit{finite} context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond it to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
 Another example of the importance of Morse's insights in infinite settings is Floer's work on the Arnold conjecture.
@@
 Some of Morse's ideas from functional topology, and in particular from \cite{Morse.1940}, have been rediscovered in topological data analysis.
-Morse studied the topology of a sublevel filtration and he introduced invariants that encode the same information as the modern persistent homology groups.
-Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial for this point of view:
+Morse studied the topology of a sublevel set filtration introducing invariants that encode the same information as the modern persistent homology groups.
+Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial from point of view:
 The use of homology with field coefficients and the restriction to functionals giving rise to persistence modules with interval decompositions.
@@
 We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply the associated persistence module is q-tame.
-We close with a historical overview of Morse's functional topology in Section~\ref{s:homology}.
+We close with a historical overview of Morse's functional topology in Section~\ref{s:historical}.

### 2021-04-09 introduction.tex
Add new abstract

@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Now a days, when thinking about the pioneering work of Morse in this interplay, a smooth function on a closed differential manifold is possibly our first association but, as we describe next, it should not be our last.
-Morse Theory in the \textit{finite} context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond it to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
-Another example of the importance of Morse's insights in infinite settings is Floer's work on the Arnold conjecture.
-Morse himself worked in a significantly less constraint context, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context of semi-continuous functionals on metric spaces.
+Now a days, when thinking about the pioneering work of Marston Morse in this domain, a smooth function on a closed differential manifold is possibly our first association but, as we describe next, it should not be our last.
+In the \textit{finite} context, Morse theory was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond this setting to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Another example of the importance of Morse's insights in infinite contexts is Floer's work on the Arnold conjecture.
+Morse himself worked in a significantly less constraint setup, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context of semi-continuous functionals on metric spaces.
 He name this body of work \textit{functional topology}.

### 2021-04-09 main.tex
Changes before meeting
Split preliminaries
Add section: historical remarks
Consolidate sections connectivity, counterexample and theorem
Improve introduction
Updates from Overleaf
Add historical stuff from Max thesis
Add new abstract

@@
 \usepackage{graphicx}
+\usepackage{csquotes}
 
@@
 \newcommand{\HLC}{\mathrm{HLC}}
-\renewcommand{\H}{\mathbb{H}^d}
-\newcommand{\dprime}{{\prime\prime}}
+\newcommand{\HE}{\mathbb{H}^d}
+\renewcommand{\H}{\widetilde{H}}
 \DeclareMathOperator{\interior}{int}
@@
 \newcommand\CH{\check{H}}
+\newcommand{\Mod}[1]{#1-\mathbf{Mod}}
 
@@
 
-\title{Persistence in functional topology: q-tameness, local-connectivity and a correction to a theorem of Morse}
+\title[Persistence in functional topology]{Persistence in functional topology: local-connectivity, q-tameness and a correction to a theorem of Morse}
 \author{}
@@
 \begin{abstract}
-With applications to the study of minimal surfaces in mind, Marston Morse wrote a series of papers developing versions of his famous inequalities for a broad class of real-valued functions on metric spaces.
-His work is remarkable in so far as it likely represents the first use of something that can be called persistent homology in the mathematical literature.
-From the modern point of view, it is particularly interesting that he uses Vietoris homology in order to enforce semi-continuity of persistent homology and that he states two topological conditions that supposedly ensure q-tameness.
-However, he is partly incorrect: We present a filtration that satisfies one of his conditions but has non-q-tame persistent homology.
-We also conjecture that his other condition, for which he provides no proof, is correct and discuss possible proof strategies.
+	During the 1930's Morse developed a general theory, which he called functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets, and, in join work with Tompkins, used this theory to study minimal surfaces.
+	Many of the key insights of functional topology have been rediscovered in the study of persistence homology.
+	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
+	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of the most delicate of these conditions: local-connectivity.
+Providing, on passing, a correction to the Critical Surface Theorem of Morse and Tompkins.
 \end{abstract}
@@
 \maketitle
-
+\tableofcontents
 \input{introduction}
-\input{preliminaries}
+\input{homology}
+\input{persistence}
 \input{connectivity}
-\input{counterexample}
-\input{theorem}
-\input{outlook}
+%\input{outlook}
+\input{historical}
 %\input{other}

### 2021-04-15 introduction.tex
Improve abstract

@@
 He name this body of work \textit{functional topology}.
-A motivating problem for him came from the study of minimal surfaces.
-In 1931, Jesse Douglas solved Plateau’s Problem \cite{Douglas.1931} for which he received the fields medal in 1936.
-The problem amounts to finding for a given admissible boundary curve $\Gamma$ an area-minimizing embedded surface $\Sigma$ with $\partial \Sigma = \Gamma$.
-In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used functional topology to give conditions for the existence of unstable minimal surfaces, i.e., critical points of the area functional that do not locally minimize area.
+Motivation for its development came from the study of minimal surfaces.
+Jesse Douglas received the fields medal in 1936 for solving in 1931 \cite{Douglas.1931} Plateau’s Problem: prove the existence of a bounding area-minimizing surface for any given admissible curve.
+In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used functional topology to give conditions for the existence of \textit{unstable} minimal surfaces, i.e., critical points of the Douglas functional that do not locally minimize area.
 

### 2021-04-15 main.tex
Updates from Overleaf

@@
 \begin{abstract}
-	During the 1930's Morse developed a general theory, which he called functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets, and, in join work with Tompkins, used this theory to study minimal surfaces.
+	During the 1930's Morse developed a general theory, which he named functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets; and, in joint work with Tompkins, used this body of work to study minimal surfaces.
 	Many of the key insights of functional topology have been rediscovered in the study of persistence homology.
 	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
-	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of the most delicate of these conditions: local-connectivity.
-Providing, on passing, a correction to the Critical Surface Theorem of Morse and Tompkins.
+	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of local-connectivity for Morse filtrations, the most delicate of these conditions, and provide in passing a correction to the Critical Surface Theorem of Morse and Tompkins.
 \end{abstract}

### 2021-04-15 connectivity.tex
Add remark about spherical classes to historical section

@@
 Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional.
-We mention the following examples.
+We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
 
-Recall that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
 \begin{prop}[\cite{MR105677}] \label{prop:cech_sing_hom_hlc}

### 2021-04-15 historical.tex
Add section by section to intro
Add remark about spherical classes to historical section

@@
-\section{Historical remarks} \label{sec:historical}
+\section{Historical remarks} \label{s:historical}
 
@@
 
-Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
+Morse assumes the spaces under consideration are equipped with a metric -- in particular are locally compact -- and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
 This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
@@
 The proof Morse cites, found in \cite[Theorem 6.1]{Morse.1938}, is not correct; neither is the statement.
-A stronger notion of local connectivity for the pair $(M, F)$ is needed to prove q-tameness.
-Such condition had already appeared in print, introduced by Morse himself, three years earlier.
+A stronger notion of local connectivity for the pair $(M, F)$ appeared in print, introduced by Morse himself three years earlier.
 \begin{displaycquote}[p.421-422]{Morse.1937}
@@
 \end{displaycquote}
-This notion of local-$F$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
+This notion of local-$F$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$, just as in our definition of $\HLC$ and weakly $\HLC$ presented in Definition~\ref{defi:local_connectedness_filtrations}.
 Following the introduction of this stronger definition Morse states as \cite[Theorem~9.2, p.422]{Morse.1937} that q-tameness follows from this form of local $F$-connectivity and bounded compactness, adding that the proof ``while not difficult involves too great detail to be presented here".
+This claim is not true since not all singular homology classes can be represented by the pushing forward the fundamental class of spheres.
+We could use a version of the Hawaiian earring made out of tori instead of spheres to construct a counterexample.
 

### 2021-04-15 connectivity.tex
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

@@
 \begin{prop}
-	Let $(X, f)$ be a sublevel filtration.
+	Let $(X, f)$ be a sublevel set filtration.
 If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d.
@@
 Having each sublevel set being $\HLC$ is in many cases too restrictive.
-We would like a relative condition for sublevel filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
+We would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
 The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.
@@
 	For a fix homology theory $\H$.
-A sublevel filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
+A sublevel set filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
 	\begin{equation*}
@@
 \begin{thm} \label{t:strong local connectenss implies q-tameness}
-	Morse filtrations which are $\HLC$ give rise to q-tame persistence modules for any homology theory.
+	Morse filtrations which are $\HLC$ are q-tame for any homology theory.
 \end{thm}

### 2021-04-15 introduction.tex
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

@@
 
-To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel filtration are forms of local-connectivity.
+To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel set filtration are forms of local-connectivity.
 In their development of functional topology and its applications to minimal surface theory, Morse and Tompkins presented certain forms of local-connectivity claimed to imply q-tameness; unfortunately, neither the proofs nor the statements are correct.

### 2021-04-15 persistence.tex
Add section by section to intro
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

@@
-\section{Persistence}
+\section{Sublevel filtrations and persistence theory} \label{s:persistence}
 
@@
 
-A \textit{sublevel filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
+A \textit{sublevel set filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
 For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
@@
 
-A sublevel filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
+A sublevel set filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
 Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.

### 2021-04-22 homology.tex
Add section by section to intro
Max homology

@@
-\section{Homology theories}
+\section{Homology theories} \label{s:homology}
 
@@
 \end{itemize}
+As special instances of homology theories, we will consider the well-known singular theory, as well as the \v{C}ech and Vietoris theories that we will recall next.
+
+Let $(X_{1},X_{2})$ be a pair of topological spaces. We denote by $\Cov(X_{1},X_{2})$ the set of covers of $(X_{1},X_{2})$ directed by the refinement relation.
+
+If $\alpha=(\alpha_{1},\alpha_{2})$ is a cover of $(X_{1},X_{2})$, we write $\Nrv(\alpha)$ for the simplicial pair $(\Nrv(\alpha_{1}),\Nrv(\alpha_{2}))$, where 
+\[
+\Nrv(\alpha_{i})=\left\{\beta\subseteq\alpha_{i}\mid\beta\text{ is finite and }\bigcap_{U\in\beta} U\neq\emptyset\right\}.
+\]
+denotes the nerve of a cover. The nerve construction defines a functor from $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial pairs.
+
+If $D\subseteq\Cov(X_{1},X_{2})$ is a directed set with respect to refinement and $G$ is an abelian group, we define
+\[
+\CH_{*}^{D}(X_{1},X_{2};G)=\lim_{\alpha\in D}H_{*}(\Nrv(\alpha);G).
+\]
+The \emph{\v{C}ech homology with coefficients in $G$} of $(X_{1},X_{2})$ is defined as
+\[
+\CH_{*}(X_{1},X_{2};G)=\CH_{*}^{\Cov(X_{1},X_{2})}(X_{1},X_{2};G).%=\lim_{\alpha\in\Cov(X_{1},X_{2})}H_{*}(\Nrv(\alpha);G)
+\]
+If $(X_{1},X_{2})$ is a pair of metric spaces, its \emph{metric \v{C}ech homology with coefficients in $G$} is defined as
+\[
+\MCH_{*}(X_{1},X_{2};G)=\CH_{*}^{\Balls(X_{1},X_{2})}(X_{1},X_{2};G),%=\lim_{\alpha\in\Balls(X_{1},X_{2})}H_{*}(\Nrv(\alpha);G).
+\]
+where $\Balls(X_{1},X_{2})=\{((B_{\delta}(x))_{x\in X_{1}},(B_{\delta}(x))_{x\in X_{2}})\mid\delta>0\}\subseteq\Cov(X_{1},X_{2})$.
+
+If $\alpha=(\alpha_{1},\alpha_{2})$ is a cover of $(X_{1},X_{2})$, we write $\Vietoris(\alpha)$ for the simplicial pair $(\Vietoris(\alpha_{1}),\Vietoris(\alpha_{2}))$, where 
+\[
+\Vietoris(\alpha_{i})=\left\{\sigma\subseteq X_{i}\mid\sigma\text{ is finite and there is}U\in\alpha_{i}\text{ with }\sigma\in U\right\}.
+\]
+denotes the Vietoris complex of a cover. The Vietoris complex construction defines a functor from $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial pairs.
+
+If $D\subseteq\Cov(X_{1},X_{2})$ is a directed set with respect to refinement and $G$ is an abelian group, we define
+\[
+\VH_{*}^{D}(X_{1},X_{2};G)=\lim_{\alpha\in D}H_{*}(\Vietoris(\alpha);G).
+\]
+The \emph{Vietoris homology with coefficients in $G$} of $(X_{1},X_{2})$ is defined as
+\[
+\VH_{*}(X_{1},X_{2};G)=\VH_{*}^{\Cov(X_{1},X_{2})}(X_{1},X_{2};G).%=\lim_{\alpha\in\Cov(X_{1},X_{2})}H_{*}(\Vietoris(\alpha);G)
+\]
+If $(X_{1},X_{2})$ is a pair of metric spaces, its \emph{metric Vietoris homology with coefficients in $G$} is defined as
+\[
+\MVH_{*}(X_{1},X_{2};G)=\VH_{*}^{\Balls(X_{1},X_{2})}(X_{1},X_{2};G).%=\lim_{\alpha\in\Balls(X_{1},X_{2})}H_{*}(\Vietoris(\alpha);G).
+\]
+
+\v{C}ech and Vietoris homology, as well as their metric versions, can be made into functors and have boundary operators; we omit the straightforward constructions.
+The metric Vietoris theory is what Morse uses in Functional Topology.
+As we will see, all of the aforementioned theories agree for the spaces we are interested in.
+To see this, we use a special case of Dowker's Theorem.
+
+\begin{thm}[{{\cite{Dowker.1952}}}]
+Let $(X,A)$ be a pair of topological spaces, $\alpha\in\Cov(X_{1},X_{2})$ and $G$ an abelian group. There exists an isomorphism 
+\[
+H_{*}(\Nrv(\alpha);G)\cong H_{*}(\Vietoris(\alpha);G),
+\]
+which is natural with respect to refinement and compatible with the boundary operators.
+\end{thm}
+
+\begin{cor}
+\v{C}ech and Vietoris homology with arbitrary coefficients agree for pairs of topological spaces. Metric \v{C}ech and metric Vietoris homology with arbitrary coefficients agree for metric pairs.
+\end{cor}
+
+Note that when $D_{1},D_{2}\subseteq\Cov(X_{1},X_{2})$ are directed subsets such that one of them is coinital in the other, we have natural isomorphisms $\CH_{*}^{D_{1}}(X_{1},X_{2};G)\cong\CH_{*}^{D_{2}}(X_{1},X_{2};G)$ and $\VH_{*}^{D_{1}}(X_{1},X_{2};G)\cong\VH_{*}^{D_{2}}(X_{1},X_{2};G)$.
+If $X_{1}$ and $X_{2}$ are compact metric spaces, $\Balls(X_{1},X_{2})$ is coinitial in $\Cov(X_{1},X_{2})$.
+This yields the following.
+
+\begin{cor}
+\v{C}ech and metric \v{C}ech homology with arbitrary coefficients, as well as Vietoris and metric Vietoris homology with arbitrary coefficients, agree for compact metric pairs.
+\end{cor}
+
+The previous comparison results justify that from now on, we will use \v{C}ech and Vietoris homology interchangeably.
+
+In full generality, none of of the previously defined functors is an actual homology theory in the sense of the Eilenberg-Steenrod axioms because their long sequences associated to a pair are generally only chain complexes and not necessarily exact.
+We refer to \cite[Section IX--X]{MR0050886} for verifications of the other axioms.
+For vector space coefficients and compact pairs, the long sequences are indeed exact (\cite{Kelly.1961}), so we get the following.
+
+\begin{thm}
+\v{C}ech homology with coefficients in a vector space $V$ over some field $\mathbb{F}$ defines a homology theory for compact pairs.
+\end{thm}
+
+Another important property of \v{C}ech homology, and ultimately the reason why Morse uses it, is its compatibility with inverse limits.
+
+\begin{thm}[{\cite[Chapter VIII, Theorem 3.6.~and Chapter X, Theorem 3.1.]{MR0050886}}]
+\v{C}ech homology commutes with inverse limits of compact Hausdorff pairs, i.e., if $(X_{1,i},X_{2,i})_{i}$ is an inverse system of compact Hausdorff pairs, the inverse limit $\lim_{i}(X_{1,i},X_{2,i})$ taken in the category of pairs of topological spaces is again a compact Hausdorff pair and for any coefficient group $G$ the natural map
+\[
+\CH_{*}(\lim_{i}(X_{1,i},X_{2,i});G)\to\lim_{i}\CH_{*}(X_{1,i},X_{2,i};G)
+\]
+is an isomorphism.
+\end{thm}
 
@@
 \url{https://www.ams.org/journals/tran/1947-062-02/S0002-9947-1947-0024128-6/S0002-9947-1947-0024128-6.pdf} mentions a non-invariant property "null-bounding"
+
+Update: Cech homology (as usually defined) and Vietoris homology (as defined originally) are only isomorphic for compact metric spaces.
+In our setting, this is enough.
+Decide which homology theories are really relevant to us.
+Vietoris (metric),
+Vietoris (topological, i.e. as the limit over all open covers);
+eqivalently (by Dowker duality):
+Cech (metric),
+Cech (topological);
+(Massey also defined Alexander-Spanier homology \url{https://doi.org/10.2307/2321782}. It should be equivalent to the "topological" variants here.)
+Singular;
 }

### 2021-04-22 persistence.tex
Updates from Overleaf
Max homology

@@
 
-\todo{start with the standard vector space setting, before generalizing?}
+%\todo{start with the standard vector space setting, before generalizing?}
 Let $R$ be a ring.
@@
 
-A persistence module $M$ is called \emph{pointwise finitely generated (p.f.g.)} if $M_{t}$ is a finitely generated module for every $t\in\mathbb{R}$.
+A persistence module $M$ is called \emph{pointwise finitely generated ($\PFG$)} if $M_{t}$ is a finitely generated module for every $t\in\mathbb{R}$.
 $M$ is called \emph{q-tame} if $\im (M_{s}\to M_{t})$ is finitely generated for all $s<t\in\mathbb{R}$.
+Recall that for Noetherian rings, being finitely generated is equivalent to being finitely presented, which is a more relevant notion in computational settings.
 
 The theory of persistence modules is particularly nice if $R=\mathbb{F}$ is a field, which we will assume for the rest of this section.
-In this case, we will say that $M$ is \emph{pointwise finite-dimensional (p.f.d.)} instead of p.f.g.
+In this case, we will say that $M$ is \emph{pointwise finite-dimensional ($\PFD$)} instead of $\PFG$.
 
@@
 Unfortunately, not every persistence module has a barcode, so general existence results are important to have.
-The most widely used of these is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, which asserts that every p.f.d.\ persistence module has a barcode.
+The most widely used of these is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, which asserts that every $\PFD$ persistence module has a barcode.
 
@@
 Other methods include using a slightly weaker notion of isomorphism for the direct sum decomposition into interval modules \cite{Chazal.2016b} or imposing additional algebraic constraints and allowing for the decompositions to be in terms of products instead of sums \cite{schmahl2020structure}.
-For each of these alternative methods, restricting to the p.f.d.\ setting recovers the basic notion of barcode discussed before.
+For each of these alternative methods, restricting to the $\PFD$ setting recovers the basic notion of barcode discussed before.
 
@@
 
-\begin{thm}[\cite{}]\todo{what do we want to cite here?}
+\begin{thm}[{{\cite[Theorem 5.14]{Chazal.2016a}}}]
 Let $M$ and $M'$ be q-tame persistence modules with barcodes $B$ and $B'$. Then
@@
 In what follows, we will study the persistent homology of certain classes of such diagrams, namely filtrations.
+If $V$ is a diagram of topological spaces, we call it a \emph{filtration} if $V_s\to V_t$ is an embedding for all $s\leq t\in\mathbb{R}$.
 

### 2021-04-22 historical.tex
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules
Restructure historical remarks

--- 2021-04-06 historical.tex
@@
-\section{Historical remarks} \label{sec:historical}
+\section{Historical remarks} \label{s:historical}
 
-The approach of Morse and Tompkins in \cite{Morse.1939} was to give a topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
-For a more detailed review of their work we refer to \cite{Struwe.1988}.
-In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.gchoosing.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation." More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
+Morse and Tompkins considered the following setting introduced in even greater generality by Douglas:
+Let $g=(g_i)\colon\mathbb{R}\to\mathbb{R}^n$ be a simple closed curve such that $g$ is differentiable and such that each $g'_i$ is Lipschitz.
+Assume that $g$ is $2\pi$-periodic.
+Let $\tilde{\Omega}$ be the space of continuous functions $\varphi \colon \mathbb{R} \to \mathbb{R}$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and such that there are three distinct points $\alpha_i \in [0,2\pi)$ with $\varphi(\alpha_i)=\alpha_i$.
+The \emph{Douglas functional} associated to the curve $g$ on $\tilde{\Omega}$ by \begin{equation*}
+A_g(\varphi)=\frac{1}{16}\int_0^{2\pi}\int_0^{2\pi}\sin\left(\frac{\alpha-\beta}{2}\right)^{-2} \! \lVert g(\varphi(\alpha))-g(\varphi(\beta)) \rVert_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta
+\end{equation*}
+and set
+\begin{equation*}
+\Omega_g=\{\varphi\in\tilde\Omega\mid A_g(\varphi)<\infty\}.
+\end{equation*}
+Douglas proved that, for even more general $g$ than above, $\Omega_g$ is non-empty and that sublevel sets of $A_g$ on $\Omega_g$ are compact.
+Since $A_g$ is clearly bounded below by $0$, this implies that $A_g$ has a unique global minimizer.
+Douglas then used harmonic analysis to show that this minimizer of $A_g$ corresponds to a solution of Plateau's Problem.
+More generally, each critical point of this functional $A_g$ corresponds to a critical point of the area functional.
 
-Morse assumes all spaces in his filtrations to be compact and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
-This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
+In \cite{Morse.1939}, Morse and Tompkins introduce the following topological version of a critical point, which they will use to study the pair $(\Omega_g, A_g)$.
+
+Let $(M,d)$ be a metric space and $f\colon M\to\mathbb{R}$ a function.
+A point $p \in M$ is a \emph{homotopically ordinary point of $f$} if there is a neighborhood $U$ of $p$ in $M_{\leq f(p)}$ and a continuous map $H \colon U \times [0,1] \to M$ such that
+\begin{enumerate}
+	\item $H(q,0) = q$ for all $q$,
+	\item $H(p,1) \neq p$,
+	\item For $e>0$ there is $\delta>0$ such that $s<s'$ and $d(H(q,s), H(q,s')) > e$ imply $f(H(q,s)) - f(H(q,s')) > \delta$.
+\end{enumerate}
+A point $p$ is a \emph{homotopically critical point of $f$} if it is not homotopically ordinary.
+
+Roughly, one can think of homotopically critical points of $f$ as points $p$ that have no neighborhood in $f_{\leq f(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<f(p)$.
+
+In the case of isolated critical points, one can then choose a neighborhood $U$ of a homotopically critical point $p$ not containing any other critical point and define the \emph{cap type numbers of $p$} as the cap type numbers of the relative homology lattice \anibal{Lattice?} associated to the restriction of $f$ to this neighborhood.
+The total cap type numbers are then defined as the sums of all of these cap type numbers. \anibal{intuition for cap type numbers in terms of modern language?}
+Assuming a finite number of critical points, Morse and Tompkins then proceed to state Morse inequalities for these total cap type numbers, referring to \cite{Morse.1940}, which was still in preparation at that time, for proof.
+
+More generally, in the non-isolated case, they consider closed sets of critical points possessing a neighborhood that does not contain any other critical points and call these \emph{critical sets}.
+Again, one can then define the cap type numbers of such sets as the cap type numbers of $f$ restricted to the corresponding neighborhood.
+In order to get Morse inequalities in this setting, without assuming that the critical points are finite in number, \anibal{One needs q-tameness}.
+
 To achieve q-tameness, Morse wants to use the following condition, which he refers to as \textit{local $F$-connectivity}.
@@
 \end{displaycquote}
-This notion of local-$F$-connectedness is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
+This notion of local-$F$-connectivity is stronger than the one first quoted, with the key difference being the freedom granted by the constant $c \geq F(p)$.
+This is precisely the difference between our notions of $\HLC$ and weakly $\HLC$, presented in Definition~\ref{defi:local_connectedness_filtrations}.
 Following the introduction of this stronger definition Morse states as \cite[Theorem~9.2, p.422]{Morse.1937} that q-tameness follows from this form of local $F$-connectivity and bounded compactness, adding that the proof ``while not difficult involves too great detail to be presented here".
 
-%From our current viewpoint it is simple to identify an important problem with both of these definitions of local $F$-connectivity, since they seem to assume that all singular homology classes can be represented by spheres, a fact that the fundamental class of a torus disproves.
-%Nonetheless, the distinction between the two teach us valuable lessons: q-tameness follows from bounded compactness and a modern interpretation of the second but not the first.\footnote{These are presented as Definitions \ref{defi:local_connectedness} and \ref{defi:strong_local_connectedness}}
+%Morse and Tompkins additionally assume local-$f$-connectedness and again refer to \cite{Morse.1940} for proof.
+%However, the proofs that Morse presents there repeatedly make use of his erroneous claim that local-$f$-connectedness implies q-tameness, so they cannot be seen as valid.
 
-%By now, however, Morse's ideas from Functional Topology, and in particular from \cite{Morse.1940}, have been rediscovered in a different context, namely topological data analysis.
-More specifically, Morse studies how the homology of the sublevel sets of a function change as the level changes.
-He defines spaces that encode the same information as the modern persistent homology groups, as well as quantities that correspond to the modern notions of birth and death.
-Even though he did not have a structure theory of persistence modules via barcodes, he emphasized many points that are now known to be connected to this theory: The use of field coefficients, as well as ensuring that the occuring persistence modules are upper semi-continuous and q-tame (which implies the existence of interval decompositions \cite{schmahl2020structure}).
+Let us return now to the Douglas functional on the space $\Omega_g$.
+Morse and Tompkins first assume that $A_g$ has finitely many homotopically critical points. They show that any homotopically critical point of $A_g$ is also a critical point in the classical sense.
+They verify the other assumptions they make for the Morse inequalities and use them to obtain their Critical surface Theorem: if $A_g$ has two distinct minimizers, it must also have a critical point of index 1, i.e.
+with non-zero first cap type number.
+
+In order to remove the finiteness assumptions, they go on to prove local-$A_g$-connectivity for $\Omega_g$ and require that the two minimizers are contained in disjoint critical sets.
+Again using the Morse inequalities, they infer the existence of an unstable minimal surface.
+As we have mentioned before, Morse's proof in \cite{Morse.1940} of the Morse inequalities in this general case is faulty since local-$A_g$-connectedness is not enough to imply the necessary q-tameness.
+However, the proof of local-$A_g$-connectedness in \cite{Morse.1939} actually shows that $\Omega_g$ is strongly locally-$A_g$-connected.
+In fact, Morse and Tompkins even show that each sublevel set of $A_g$ is locally contractible in all larger sublevel sets.
+So if our previous conjectures are true, the general theory can be applied and their approach still works.
+
+%The approach of Morse and Tompkins in \cite{Morse.1939} to minimal surface theory was based on the Douglas functional.
+%topological definition of critical points in the general setting, prove existence of these via Morse inequalities for the so-called Douglas functional, and then to prove that these topological critical points correspond to minimal surfaces.
+%For a more detailed review of their work we refer to \cite{Struwe.1988}.
+In the minimal surface community, these methods do not seem to be deemed very helpful, as is reflected e.gchoosing.\@ in \cite[p.472]{MR2566897}, where the authors state that Morse's "...general Morse-theoretic statements are more or less useless as they are based on topological assumptions which cannot be verified in a concrete situation".
+%More comments on the perceived unsuitability of the theory of Functional Topology for minimal surfaces are made by Struwe in \cite{MR850612}.
+
+%For the development of functional topology, Morse assumes the spaces under consideration are equipped with a metric -- in particular are locally compact -- and uses Vietoris homology, which agrees with \v{C}ech homology by Dowker's Theorem \cite{Dowker.1952}.
+%The functionals he uses are ``bounded compact", that is, all sublevel sets are compact.
+%
+%
+%This implies semi-continuity by a general result stating that, for field coefficients, \v{C}ech homology commutes with inverse limits for compact Hausdorff spaces \cite[Theorem VIII.3.6 and Theorem X.3.1]{MR0050886}.
+%
+%
+%
+%
+%
+%\subsection{Critical Points}
+%So far, we have mostly talked about changes in the homology of sublevel sets at certain \emph{values} since this is what is studied in persistent homology.
+The original motivation to study Functional Topology was, however, the study of critical \emph{points}, which we briefly touched upon in section \ref{sec:morse}.

### 2021-04-22 main.tex
Max homology
Restructure historical remarks

@@
 \usepackage[marginpar]{todo}
-\makeatletter
-\renewcommand{\@tododisplay}[1]{%
-%\marginpar{#1}%
-\textsuperscript{#1}%
-}
-%
-\renewcommand\@displaytodo[2][\todomark]{%
-\@tododisplay{{\todoformat [#1~\ref{todolbl:\thetodo}]}}%
-\footnotetext[\thetodo]{\todoformat #1:~#2}%
-\global\@todotoks\expandafter{\the\@todotoks\todoitem{#1}{#2}}%
-\@todotrue%
-}%
-\renewcommand\todomark{todo}
-\makeatother
+%\makeatletter
+%\renewcommand{\@tododisplay}[1]{%
+%%\marginpar{#1}%
+%\textsuperscript{#1}%
+%}
+%%
+%\renewcommand\@displaytodo[2][\todomark]{%
+%\@tododisplay{{\todoformat [#1~\ref{todolbl:\thetodo}]}}%
+%\footnotetext[\thetodo]{\todoformat #1:~#2}%
+%\global\@todotoks\expandafter{\the\@todotoks\todoitem{#1}{#2}}%
+%\@todotrue%
+%}%
+%\renewcommand\todomark{todo}
+%\makeatother
 
@@
 \newcommand{\Mod}[1]{#1-\mathbf{Mod}}
+\newcommand{\PFD}{\mathrm{PFD}}
+\newcommand{\PFG}{\mathrm{PFG}}
+\DeclareMathOperator{\Nrv}{Nrv}
+\DeclareMathOperator{\Cov}{Cov}
+\DeclareMathOperator{\Vietoris}{Vietoris}
+\DeclareMathOperator{\Balls}{Balls}
+\newcommand\MCH{M\check{H}}
+\newcommand\VH{VH}
+\newcommand\MVH{MVH}
 
@@
 	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
-	With modern applications to geometry in mind, in this article we present a comprehensive and up-to-date study of local-connectivity for Morse filtrations, the most delicate of these conditions, and provide in passing a correction to the Critical Surface Theorem of Morse and Tompkins.
+	With modern applications to geometry in mind, in this article we present an up-to-date study of local-connectivity for Morse filtrations, and provide in passing a correction to the Critical Surface Theorem of Morse and Tompkins.
 \end{abstract}

### 2021-05-14 connectivity.tex
Add homology theories and full proof

@@
 
-Let $\H$ be a fixed homology theory.
+Let $\H$ be a fixed partially exact homology theory.
 
 \begin{defi} \label{defi:local_connectedness}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or \textit{trivial}, denoted $\HS_n$ and $\HT_n$ respectively, if the image of the map induced by $\H_n$ is finitely generated or 0, and we say it is \textit{homologically small} or \textit{trivial}, denoted respectively $\HS$ and $\HT$, if it is $\HS_n$ or $\HT_n$ for every~$n$.
+	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ($\HS_n$) if the image of the map induced $\H_{n}$ is finitely generated.
+	Furthermore, if the image is $0$ then we say it is \textit{$n$-homologically trivial} ($\HT_n$).
+	The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
+	We omit references to $n$ if the conditions hold for all integers.
+	The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
+% 	It is said to be $\piT$/$\HS$/$\HT$ if it is $\piT_{n}$/$\HS_n$/$\HT_n$ for every~$n$. 
 \end{defi}
 
+There are maps that are $\piT$ but not $\HT$ for say ordinary homology, an examples is the collapse of the 1-skeleton of the torus.
+Naturally, $\HT$ does not imply $\piT$ either.
+If the map is $\NH$ then it is $\piT$ and, if the value of $\H$ on a point is 0, $\HT$ as well.
+
 \begin{defi}
-	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
+	A space $X$ is said to be $\HLC$ (resp.
+$\piLC$, $\LC$) if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$ (resp.
+$\piT$, $\NH$).
+	%If the neighborhoods can be chosen so that these inclusion have contractible images we say that the space is \textit{locally contractible} ($\LC$).
 \end{defi}
 
-Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional.
+Local connectivity assumptions like the above ones have a long history of being used to ensure that different homology theories agree and to ensure that homology is finitely generated.
 We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
 
-\begin{prop}[\cite{MR105677}] \label{prop:cech_sing_hom_hlc}
+\begin{prop}[\citet{MR105677}] \label{prop:cech_sing_hom_hlc}
 	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which are $\HLC$ with respect to integral singular homology.
@@
 
-\begin{prop} \label{prop:fin_dim_sing_hom}
-	Let $X$ be a compact Hausdorff space.
-	If $X$ is $\HLC$ with respect to integral singular homology, then the singular homology of $X$ with arbitrary coefficients is finite-dimensional in every degree.
+\begin{prop}[{\citet[p.~109]{MR0007094}}]
+	A compact $\piLC$ Hausdorff space has finite Betti numbers.
 \end{prop}
 
-We will deduce the previous finiteness result from our main contribution, Theorem~\ref{t:strong local connectenss implies q-tameness}.
-To motivate the statement of our theorem let us record a direct consequence of the previous proposition.
+%We will deduce the following similar result from our main contribution, \cref{t:strong local connectedness implies q-tameness}.
 
-\begin{prop}
-	Let $(X, f)$ be a sublevel set filtration.
-If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d.
-in every degree, in particular q-tame.
-\end{prop}
+%\begin{prop} \label{prop:HLC_single_space}
+%	Let $X$ be a compact Hausdorff space.
+%	If $X$ is $\HLC$ then $\H_{n}(X)$ is finitely generated for all $n$.
+%\end{prop}
 
-Having each sublevel set being $\HLC$ is in many cases too restrictive.
+As a direct consequence of the previous proposition, we obtain the following persistence result.
+
+\begin{cor}
+	Let $f \colon X \to \R$ be a function with compact sublevel set filtration. If every sublevel set is $\piLC$ then $\H (X_{\leq \bullet})$ is $\PFG$ in every degree, in particular q-tame.
+\end{cor}
+
+A similar statement with an $\HLC$ condition instead of the $\piLC$ conditions also holds as a consequence of our main theorem.
+Having each sublevel set being locally connected is, however, in many cases too restrictive.
 We would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
-The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.
+% The following definitions are motivated by Morse's work, in particular his local connectivity conditions mentioned in the introduction and reviewed in \cref{s:surfaces}.
 
 \begin{defi} \label{defi:local_connectedness_filtrations}
-	For a fix homology theory $\H$.
-A sublevel set filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\HLC$ (resp.\@ $\piLC$, $\LC$) if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that for every $c \geq 0$ the inclusion
 	\begin{equation*}
-	X_{\leq f(x) + \delta + c} \cap U \to X_{\leq f(x) + \epsilon + c} \cap V
+	X_{\leq f(x) + c + \delta} \cap U \to X_{\leq f(x) + c + \epsilon} \cap V
 	\end{equation*}
-	is $\HT$ for every $c \geq 0$.
-	We also consider a weaker version, referred to as \textit{weakly} $\HLC$, defined as above with $c = 0$.
+	is $\HT$ (resp.\@ $\piT$, $\NH$).
+	We also consider a weaker version, referred to as \textit{weakly} $\HLC$ (resp. $\piLC$ and $\LC$), defined as above but with $c = 0$ fixed.
 \end{defi}
 
-We will now show that the weak notion does not imply q-tameness in general.
+% As for a single space, the $\LC$ notions imply the corresponding $\piLC$ notions and the corresponding $\HLC$ notions if $\H$ evaluated at a point is trivial.
+
+We remark that Morse's 
+% condition of the space $X$ being locally $f$-connected from
+notion of local $f$-connectivity in \cite[p.431]{Morse.1940} that we quoted in the introduction is equivalent to the sublevel set filtration of $f$ being weakly $\piLC$.
+The notion of $\piLC$ was also introduced by Morse, appearing three years earlier in \cite[p.421]{Morse.1937}.
+
+We will now show that not even being weakly $\LC$ is enough to imply q-tameness in general.
 To do so let us consider the \textit{$d$-dimensional Hawaiian earring}
@@
 	\centering
-	\begin{tikzpicture}[scale=88]
+	\begin{tikzpicture}[scale = 76]
 	\draw[thick] (-.1,0) rectangle (.1,.05);
@@
 \begin{thm} \label{thm:counterexample}
-	Let $\H$ be a (generalized) homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
-Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\HLC$ Morse filtration that is not q-tame.
+	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is not finitely generated for some $n$.
 \end{thm}
@@
 \begin{proof}
-	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
-	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
-	Let us now verify that $\HE$ is $\HLC$.
+	The space $\HE$ is Hausdorff and locally compact since $\R^{d+1}$ is.
+	To verify that $f$ has compact sublevel sets we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	Let us now verify that the sublevel set filtration of $f$ is weakly $\LC$.
 	Let $\epsilon > 0$ and $x \in \HE$.
 	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
-	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
-	For $x$ not the origin, there is a unique $d$-sphere that contains it.
-	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
-	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
-	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
+	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the weak $\LC$ condition is trivially satisfied.
+	For $x$ not the origin, there is a unique $d$-sphere in $\HE$ that contains it.
+	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a disk contained in this sphere, so $D_\delta(x)$ can be contracted to $\{x\}$ and the weak $\LC$ condition again follows trivially.
+	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame for $\H$.
+This follows directly from our assumption that $\H_{n}(\HE)$ is not finitely generated for some $n$ because $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
 \end{proof}
 
-The theories that we are most interested in do satisfy these conditions.
+The homology theories that we are most interested in do satisfy the condition in the previous theorem.
 
 \begin{prop}
-	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular homology with arbitrary coefficients and \v{Cech} homology with field coefficients.
+	There is an $n$ such that $\H_{n}(\HE)$ is not finitely generated if $\H$ is singular homology with arbitrary coefficients or \v{C}ech homology with field coefficients.
 \end{prop}
@@
 \begin{proof}
-	The case of singular homology is well know and can be found in \cite{Barratt.1962}.
-	For \v{C}ech homology we use the fact that it commutes with inverse limits for compact Hausdorff spaces.
+	Both assertions are well-known. The case singular homology can be found in \cite{Barratt.1962}. For the reader's convenience, we present the \v{C}ech homology case.
+	One can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{MR0050886}:
 	Define 
 	\begin{align*}
-	\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2 \leq \left(\frac{1}{k}\right)^2\right\}\\
-	&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+	\HE_k &= \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\
+	& \cup \bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right \},
 	\end{align*}
 	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-	We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
-	Clearly, each $\mathbb{H}^{d}_{k}$ is a CW-complex, so we can simply use cellular homology to compute
+	We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \mathbb{F}) = \lim_{k} \CH_{d}(\HE_{k}; \mathbb{F})$.
+	Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
 	\begin{equation*}
@@
 
-Now we verify that Morse filtrations which are $\HLC$ are q-tame.
-We will need three lemmas.
+In particular, this result invalidates the claim in \cite[Theorem 6.3]{Morse.1940} stating that weakly $\piLC$ implies q-tame with respect to \v{C}ech homology with field coefficients.
+
+% After having shown the insufficiency of the weak conditions,
+We will now show that for any homology theory the property of being $\HLC$ implies that of being q-tame for compact sublevel set filtrations.
+Since the Douglas functional induces a filtration which is $\LC$, the following result fixes the gap in the unstable minimal surface theorem of Morse and Tompkins.
+
+\begin{thm} \label{t:strong local connectedness implies q-tameness}
+	Assume that $\H$ is \v{C}ech homology with field coefficients or that $\H$ is a homology theory such that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and $\HLC$, then it is also q-tame.
+\end{thm}
+
+The general proof strategy is inspired by the proof of a result by Wilder as presented by Bredon \cite[Section II.17]{Bredon.1997}.
+We collect the main ideas in three lemmas.
 
@@
 \begin{proof}
-	This is proven via a straightforward diagram chase. For more details see Lemma 17.3 in \cite{Bredon.1968}.
+	This is proven via a straightforward diagram chase. For more details see \cite[Lemma 17.3]{Bredon.1997}.
 \end{proof}
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Fix a homology theory. Let $(X,f)$ be a $\HLC$ Morse filtration.
-	Consider sets $K, L \subseteq X$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap X_{s+\delta} \to L \cap X_{t}$ is $\HS$.
+    Let $\H$ and $f \colon X \to \R$ be as in \cref{t:strong local connectedness implies q-tameness}.
+	Consider sets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	For any $s < t$ the inclusion
+	\[C \cap X_{\leq s} \to L \cap X_{\leq t}\]
+	is $\HS$.
 \end{lem}
@@
 \begin{proof}
-	We need to prove that the inclusion $X_s \to X_t$ is $\HS$ for every $s < t$.
+	We will prove a slightly stronger statement,
+	that there is $\delta \in (0,\, t-s)$ such that the inclusion
+	\[C \cap X_{\leq s+\delta} \to L \cap X_{\leq t}\]
+	is $\HS_n$ for all $n$.
+	The statement holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
+	We will proceed by induction on $n \geq n_0$
+	assuming the statement for $\HS_{n-1}$.
 
-	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $\H_{n-1}$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
+	As the first case, assume that $\H$ is a homology theory. Given an open subset $L \subseteq X$ and $s < t$, let $\Sigma_{s, t}$ be the collection of all 
+% uli/max: simplified %	compact subsets $K \subseteq L$ for which there exists $\delta > 0$ 
+% uli/max: simplified %	and an open neighborhood $U$ of $K$ with $K \subseteq U \subseteq L$ 
+% uli/max: simplified %		such that the inclusion
+% uli/max: simplified %	\[U \cap X_{\leq s+\delta} \to L \cap X_{\leq t}\]
+    open subsets $V$ such that $\overline{V} \subseteq L$ is compact and
+    has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$ 
+    for which there exists $\delta > 0$ such that
+    %such that for $V = \interior(K)$ 
+    the inclusion
+    \[U \cap X_{\leq s+\delta} \to L \cap X_{\leq t}\]
+	is $\HS_n$.
 
-	Given a compact set $L \subseteq X$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U(K)$ of $K$ such that $U(K) \cap X_{s+\delta_K} \to L \cap X_{t}$ is $\HS_n$.
+% 	We start by showing that any point $x \in L \cap X_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+% 	Consider an open neighborhood $U_x \subseteq L$ of $x$, and take $\epsilon > 0$ such that $s + \epsilon < t$.\todo{uli: this seems unnecessary. $U_x = L$ and $s + \epsilon = t$ might work already.}
+% 	By the $\HLC$ of $(X,f)$ there is a $\delta \in (0, \epsilon)$ and an open neighborhood $W_x \subseteq U_x$ such that for $c = s - f(x)$ the following composition is $\HS$:
+% 	\begin{equation*}
+% 	W_x \cap X_{\leq f(x) + c + \delta} \to
+% 	U_x \cap X_{\leq f(x) + c + \epsilon} \to
+% 	L \cap X_{\leq t}.
+% 	\end{equation*}
+% 	By local compactness we can choose a compact neighborhood of $x$ contained in $W_x$.
+% 	This proves the claim.
 
-	We start by showing that any element of $\interior(L) \cap X_s$ has a neighborhood in $\Sigma_{s, t}$.
-	Let $x \in \interior(L) \cap X_{s}$.
-	Consider an open neighborhood $U(x)$ of $x$ contained in $\interior(L)$, and take $\epsilon > 0$ such that $s + \epsilon < t$.
-	By the strong $\HLC$ of $(X,f)$ there is a $\delta \in (0, \epsilon)$ and an open neighborhood $W(x) \subseteq U(x)$ such that for $c = s - f(x)$ the following composition is $\HS$:
+	We start by showing that any point $x \in L \cap X_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	Since the sublevel set filtration of $f$ is $\HLC$, there is a $\delta \in (0, t-s)$ and an open neighborhood $U_x \subseteq L$ such that the inclusion
 	\begin{equation*}
-	W(x) \cap X_{f(x) + c + \delta} \to
-	U(x) \cap X_{f(x) + c + e} \to
-	L \cap X_{t}.
+	U_x \cap X_{\leq s + \delta} \to
+	L \cap X_{\leq t}.
 	\end{equation*}
-	By local connectivity we can choose a compact neighborhood of $x$ contained in $W(x)$.
+	is $\HS$.
+	By local compactness we can choose a compact neighborhood $K_x$ of $x$ contained in $U_x$. Now $V_x = \interior (K_x)$ is an open neighborhood of $x$ that is contained in $\Sigma_{s,t}$.
 	This proves the claim.
 
-	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
-	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap X_{s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
-	We use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
+	Next, we will show that the class $\Sigma_{s,t}$ is closed under finite unions.
+	For $i \in \{1, 2\}$ let $V_i$ be in $\Sigma_{s,t}$ with $U_i$ and $\delta_i \in (0, t-s)$ 
+% uli/max: simplified %		and $U_i$ open with $K_i \subseteq U_i \subseteq L$ 
+% uli/max: simplified %			such that
+% uli/max: simplified %		\[U_{i} \cap X_{\leq s+\delta_i} \to L \cap X_{\leq t}\]
+%    and $V_i = \interior(K_i)$ 
+    such that $\overline{V_i} \subseteq U_i \subseteq L$ and
+	\[U_{i} \cap X_{\leq s+\delta_i} \to L \cap X_{\leq t}\]
+	is $\HS_n$.
+	Writing $K_i = \overline{V_i}$, we use \cref{l:neighborhood third} to construct compact sets $K_i^\prime$ such that
 	\begin{equation*}
@@
 	\end{equation*}
-	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap X_{s+\delta} \to L \cap X_t$ is $\HS_n$.
-	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_s \to K_1^\prime \cap K_2^\prime \cap X_{s+\delta}$ is $\HS_{(n-1)}$.
-	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:\todo{check assumptions for mayer-vietoris to apply}
+	Writing $V_i^\prime = \interior(K_i^\prime)$,
+	we have 
 	\begin{equation*}
-	\begin{tikzcd}
-	\H_n(L \cap X_t) \oplus \H_n(L \cap X_t) \arrow[r] &
-	\H_n(L \cap X_t) & \\
-	\H_{n}(K_1^\prime \cap X_{s+\delta}) \oplus \H_n(K_2^\prime \cap X_{s+\delta}) \arrow[r] \arrow[u] & 
-	\H_{n}((K_1^\prime \cap X_{s+\delta}) \cup (K_2^\prime \cap X_{s+\delta})) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap X_{s+\delta}) \\ & 
-	\H_{n}((K_1 \cup K_2) \cap X_s) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1 \cap K_2 \cap X_s). \arrow[u]
+	V_i \subseteq K_i \subseteq V_i^\prime 
+	%\subseteq K_i^\prime 
+    \subseteq U_i 
+	\subseteq L.
+	\end{equation*}
+	Notice that for $\delta = \min_i\delta_i$ both inclusions
+	\[V_i^\prime \cap X_{\leq s+\delta} \to L \cap X_{\leq t}\]
+	are $\HS_n$.
+	Additionally, the induction hypothesis implies that the inclusion
+	\[
+	K_1 \cap K_2 \cap X_{\leq s} \to V_1^\prime \cap V_2^\prime \cap X_{\leq s+\delta}
+	\]
+	is $\HS_{n-1}$, and thus so is the inclusion
+	\[
+	V_1 \cap V_2 \cap X_{\leq s} 
+% 	\to K_1 \cap K_2 \cap X_{\leq s} 
+	\to V_1^\prime \cap V_2^\prime \cap X_{\leq s+\delta}.
+	\]
+    Because the $V_i$ and $V_i'$ are open and because $\H$ is a homology theory, we can use Mayer-Vietoris sequences to obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\begin{equation*}
+	\begin{tikzcd}[column sep=small]
+	\H_n(L \cap X_{\leq t}) \oplus \H_n(L \cap X_{\leq t}) \arrow[r] &
+	\H_n(L \cap X_{\leq t}) & \\
+	\H_{n}(V_1^\prime \cap X_{\leq s+\delta}) \oplus \H_n(V_2^\prime \cap X_{\leq s+\delta}) \arrow[r] \arrow[u] & 
+	\H_{n}((V_1^\prime \cup V_2^\prime) \cap X_{\leq s+\delta}) \arrow[r] \arrow[u] &
+	\H_{n-1}(V_1^\prime \cap V_2^\prime \cap X_{\leq s+\delta}) \\ & 
+	\H_{n}((V_1 \cup V_2) \cap X_{\leq s}) \arrow[r] \arrow[u] &
+	\H_{n-1}(V_1 \cap V_2 \cap X_{\leq s}). \arrow[u]
+	\end{tikzcd}
+	\end{equation*}
+	We conclude that $V_1 \cup V_2 \in \Sigma_{s, t}$.
+
+	In the second case where $\H$ is \v{C}ech homology with field coefficients, the conditions for Mayer-Vietoris are different, so we also want a different definition of $\Sigma_{s,t}$.
+Concretely, in this case, let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $L$ for which there exists $\delta_K > 0$ and an open neighborhood $U(K) \subseteq L$ of $K$ such that the inclusion $U(K) \cap X_{\leq s+\delta_K} \to L \cap X_{\leq t}$ is $\HS_n$.
+
+	Again, we show that any point $x \in L \cap X_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	Take $\epsilon > 0$ such that $s + \epsilon < t$.
+ 	Since $L$ is open and the sublevel set filtration of $f$ is $\HLC$ is a $\delta \in (0, \epsilon)$ and an open neighborhood $W_x \subseteq L$ such that for $c = s - f(x)$ the inclusion 
+ 	\begin{equation*}
+ 	W_x \cap X_{\leq f(x) + c + \delta} \to
+ 	L \cap X_{\leq t}
+ 	\end{equation*}
+ 	is $\HS$.
+ 	By local compactness of $X$ we can choose a compact neighborhood of $x$ contained in $W_x$.
+ 	This proves the claim.
+
+ 	Next, we will show that also in the \v{C}ech case, $\Sigma_{s,t}$ is closed under finite unions.
+ 	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $U_i \supseteq K_i$ open such that $U_{i} \cap X_{\leq s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
+	We use \cref{l:neighborhood third} to construct sets $K_i^\prime$ such that
+	\begin{equation*}
+	K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime \subseteq U_i.
+	\end{equation*}
+	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap X_{\leq s+\delta} \to L \cap X_t$ is $\HS_n$.
+	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_{\leq s} \to K_1^\prime \cap K_2^\prime \cap X_{\leq s+\delta}$ is $\HS_{(n-1)}$.
+	Because the $K_i$, $K_i'$ and the sublevel sets of $f$ are conpact Hausdorff, we can use Mayer-Vietoris sequences to obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\begin{equation*}
+	\begin{tikzcd}[column sep=small]
+	\H_n(L \cap X_{\leq t}) \oplus \H_n(L \cap X_{\leq t}) \arrow[r] &
+	\H_n(L \cap X_{\leq t}) & \\
+	\H_{n}(K_1^\prime \cap X_{\leq s+\delta}) \oplus \H_n(K_2^\prime \cap X_{\leq s+\delta}) \arrow[r] \arrow[u] & 
+	\H_{n}((K_1^\prime \cup K_2^\prime) \cap X_{\leq s+\delta})) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap X_{\leq s+\delta}) \\ & 
+	\H_{n}((K_1 \cup K_2) \cap X_{\leq s}) \arrow[r] \arrow[u] &
+	\H_{n-1}(K_1 \cap K_2 \cap X_{\leq s}). \arrow[u]
 	\end{tikzcd}
@@
 	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
-	Since any compact $K \subseteq \interior(L)$ can be covered by a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
+
+	We can now finish in both cases simultaneously: Since any point in $L$ has a neighborhood in $\Sigma_{s,t}$, the set $C \subseteq L$ can be covered by sets in $\Sigma_{s,t}$.
+As $C$ is compact, this cover can be chosen finite.
+This implies the induction step because $\Sigma_{s,t}$ is closed under finite unions, so the lemma is proven.
 \end{proof}
 
-\begin{thm} \label{t:strong local connectenss implies q-tameness}
-	Morse filtrations which are $\HLC$ are q-tame for any homology theory.
-\end{thm}
-
-\begin{proof}
-	It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = X_{\leq s}$ and $L = X$.
+We can now complete the proof of the claim stating that for compact sublevel set filtrations, $\HLC$ implies q-tameness. 
+\begin{proof}[Proof of \cref{t:strong local connectedness implies q-tameness}]
+	This follows from applying \cref{l:key lemma for q-tameness} with $C = X_{\leq s}$ and $L = X$.
 \end{proof}

### 2021-05-14 homology.tex
Add homology theories and full proof

--- 2021-04-01 homology.tex
@@
-\subsection{Homology theories}
+\section{Homology theories} \label{s:homology}
 
+Let $R$ be a ring and let $\H = \big\{ \H_{n} \big\}_{n \in \Z}$ be a collection of homotopy invariant functors from pairs of topological spaces to $R$-modules.
+Consider the following two properties known respectively as \textit{excision} and \textit{exactness}:
 \begin{itemize}
-	\item Definition
-	\item Examples, main: singular with integer coeff and cech with field 
-	\item Mayer-Vietoris
+	\item If $(X,A)$ is a pair and $U \subseteq X$ is an open subspace whose closure in $X$ is contained in $A$, then the inclusion $(X \setminus U, A \setminus U) \to (X, A)$ is sent to an isomorphism by $\H_{n}$ for all $n$.
+	\item For each pair $(X,A)$ there exists a natural long exact sequence
+	\begin{equation*}
+    \begin{tikzcd}[column sep = small]
+	\cdots \arrow[r] & \H_{n+1}(X,A) \arrow[r] & \H_{n}(A, \emptyset) \arrow[r] & \H_{n}(X, \emptyset) \arrow[r] & \H_{n}(X,A) \arrow[r] & \cdots
+	\end{tikzcd}
+	\end{equation*}
 \end{itemize}
+
+If $\H$ satisfies these properties, we call it a \emph{homology theory}.
+Nowadays, it is common to also ask of a homology theory to satisfy some form of additivity, but this property, suggested by Milnor \cite{MR159327}, was not part of Eilenberg-Steenrod axioms as presented in \cite[Chapter I]{MR0050886} and,
+since it does not play a role in this work, we do not demand it.
+
+Similarly, point axiom ....
+
+Ulrich: uniqueness theorems.
+
+For us, a weaker version of exactness will be important.
+We say $\H$ satisfies \textit{partial exactness} if pairs of spaces give rise to long sequences satisfying the chain complex property but not needing to be exact, i.e., satisfying a condition of the form ``$\im \subseteq \ker$" instead of ``$\im = \ker$".
+We say that $\H$ is a \emph{partially exact homology theory} if it satisfies excision and partial exactness.
+
+Let us now review the Mayer-Vietories long exact sequence.
+We say that a triple of spaces $X_{1}, X_{2} \subseteq X$ is \emph{excisive} with respect to $\H$ if the inclusion of $(X_{1}, X_{1} \cap X_{2})$ into $(X, X_{2})$ is sent to an isomorphism by $\H_{n}$ for all $n$.
+Note that if $\H$ satisfies excision then a triple $X_{1}, X_{2} \subseteq X$ is excisive if $X = X_{1} \cup X_{2}$ and $X_{1}$, $X_{2}$ are open in $X$.
+
+If $X_{1}, X_{2} \subseteq X$ are excisive with respect to $\H$ and the long sequences associated to $(X_{1}, X_{1} \cap X_{2})$ and $(X, X_{2})$ are exact, then there is a natural long exact sequence
+\[
+\begin{tikzcd}[column sep = small]
+\cdots \arrow[r] & \H_{n}(X_{1} \cap X_{2}) \arrow[r] & \H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] & \H_{n}(X) \arrow[r] & \H_{n-1}(X_{1} \cap X_{2}) \arrow[r] & \cdots
+\end{tikzcd}
+\]
+referred to as the \emph{Mayer-Vietoris sequence} of $X_{1}, X_{2} \subseteq X$.
+
+In particular, for any homology theory there is an exact Mayer-Vietoris sequence for any triple of spaces $X_{1}, X_{2} \subseteq X$ if $X = X_{1} \cup X_{2}$ and $X_{1}$, $X_{2}$ are open in $X$.
+
+An example of a homology theory consider in this work is the well-known singular theory of Eilenberg \cite{Eilenberg.1944}, whereas an example of a partially exact homology theory, reviewed next, is the \v{C}ech theory, for which a historical account can be found in \cite{Edwards.1980}.
+
+Let $(X_{1},X_{2})$ be a pair of topological spaces.
+We say that $\alpha = (\alpha_1, \alpha_2)$ is an \emph{open cover} of $(X_1, X_2)$ if $\alpha_1$ is an open cover of $X_1$ and $\alpha_2 \subseteq \alpha_1$ is a subcover such that $X_1 \subseteq \bigcup_{U \in \alpha_2} U$.
+We denote by $\Cov(X_{1}, X_{2})$ the set of open covers of $(X_{1}, X_{2})$ directed by the refinement relation.
+
+If $\alpha = (\alpha_{1}, \alpha_{2})$ is a cover of $(X_{1}, X_{2})$, we write $\Nrv(\alpha)$ for the simplicial pair $(\Nrv(\alpha_{1}),\Nrv(\alpha_{2}))$, where 
+\[
+\Nrv(\alpha_{i}) =
+\big\{ \beta \subseteq \alpha_{i} \mid \beta \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}
+\]
+denotes the nerve of a cover. The nerve construction defines a functor from $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial pairs.
+
+The \emph{\v{C}ech homology with coefficients in $G$} of $(X_{1},X_{2})$ is defined as
+\[
+\CH_{*}(X_{1}, X_{2}; G) \ =
+\lim_{\alpha \in \Cov(X_{1}, X_{2})} H_{*}(\Nrv(\alpha); G).
+\]
+
+\v{C}ech homology can be made into a functor and satisfies the axioms of a partially exact homology theory; we refer to \cite[Section IX--X]{MR0050886} for the constructions and verifications of the axioms.
+For arbitrary coefficients it is not in general a homology theory, but for vector space coefficients and compact Hausdorff pairs, the associated long sequences are exact \cite{Kelly.1961}.
+If $X_{1}, X_{2} \subseteq X = X_{1} \cup X_2$ are all compact Hausdorff, they are also excisive for \v{C}ech homology \cite[Sections X.1, X.5]{MR0050886}, so such triples have exact Mayer-Vietoris sequences for \v{C}ech homology with field coefficients.
+
+Another important property of \v{C}ech homology is its compatibility with cofiltered limits \cite[Theorems VIII.3.6.\@ and X.3.1.]{MR0050886}.
+More specifically, if $(X_i, Y_i)_i$ is a totally ordered diagram of compact Hausdorff spaces, its limit $(X, Y) = \lim_i (X_i, Y_i)$ in the category of pairs of spaces is again a compact Hausdorff pair and the natural map $\CH_*(X, Y; G) \to \lim_i \CH_*(X_i, Y_i; G)$ is an isomorphism.
+
+%\todo{Uli: I saw a discussion about the topological invariance of Vietoris homology for non-compact metric spaces.
+%I thought that it suggested that invariance holds only for compact spaces,
+%but I can't find it anymore.
+
+%What I found was this:
+%\url{http://pldml.icm.edu.pl/pldml/element/bwmeta1.element.zamlynska-8f369e96-b1eb-4ec9-99e2-8c366367a5a4} claims invariance also for non-compact.
+%\url{https://www.ams.org/journals/tran/1947-062-02/S0002-9947-1947-0024128-6/S0002-9947-1947-0024128-6.pdf} mentions a non-invariant property "null-bounding"
+
+%Update: Cech homology (as usually defined) and Vietoris homology (as defined originally) are only isomorphic for compact metric spaces.
+In our setting, this is enough.
+Decide which homology theories are really relevant to us.
+%Vietoris (metric),
+%Vietoris (topological, i.e. as the limit over all open covers);
+%eqivalently (by Dowker duality):
+%Cech (metric),
+%Cech (topological);
+%(Massey also defined Alexander-Spanier homology \url{https://doi.org/10.2307/2321782}. It should be equivalent to the "topological" variants here.)
+%Singular;
+%}

### 2021-05-14 inequalities.tex
Add homology theories and full proof

\section{Morse Inequalities} \label{s:inequalities}

We now present a description of Morse inequalities from the viewpoint of persistence theory which, when applied in the context of Functional Topology, agrees with Morse's original definitions.

Let $M$ be a graded q-tame persistence module, and let $\mathfrak{m}_d$ be the multiplicity function of the barcode of the $d$-dimensional part of $M$, having values in the extended natural numbers.

To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$, Morse defined the $(d, t, e)$-\textit{cap numbers}, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
Explicitly,
\[
    m_{d}^{> e}(t) =
    \sum_{\substack{p \in \R \\ t-p>e}} \mathfrak{m}_{d-1}(p, t) +
    \sum_{\substack{q \in \R \\ q-t>e}} \mathfrak{m}_d(t, q).
\]

If $m_{d}^{> e}(t)$ is non-zero for only finitely many $t$, we obtain the $(d,e)$-cap numbers 
\[
m_{d}^{> e } = \sum_{t} m_{d}^{> e}(t) = \sum_{\substack{(p,q)\\q-p>e\\q\neq\infty}}\mathfrak{m}_{d-1}(p,q)+\sum_{\substack{(p,q)\\q-p>e\\p\neq-\infty}}\mathfrak{m}_d(p,q).
\] 
One can show that this finiteness assumption is satisfied if $M$ is initially and eventually constant, i.e., if there exist $t_0$ and $t_1$ with $M_s = M_{t_0}$ for all $s \leq t_0$ and $M_u = M_{t_1}$ for all $u \geq t_1$. In particular, this is the case for the persistent homology of the sublevel set filtration of a bounded function.

If $X$ is a closed manifold and $F$ is a Morse function, then the cap numbers $m_{d}^{> e}(F)$ associated to the persistent homology of the sublevel set filtration of $F$ agree with the number of critical points of $F$ with index $d$ for all sufficiently small $e > 0$. As an analogue to the Betti numbers of $X$ appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$, which, under the same assumptions as before, can be expressed in the language of persistence as
\[
p_{d} = \sum_{p} \mathfrak{m}_d(p,\infty).
\]

Provided that $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, an easy calculation shows that in this language we have Morse inequalities for any graded q-tame persistence module given by
\begin{equation*}
    \sum_{i=1}^d (-1)^i (m^{>e}_{d-i} - p_{d-i}) \ \geq\  0
\end{equation*}
for any dimension $d$. As a special case, this yields Morse inequalities for any bounded real-valued function $F$ whose sublevel set filtration has q-tame and upper semi-continuous persistent homology. As we have discussed previously, these algebraic conditions are satisfied in the setting of Functional Topology, where \v{C}ech homology is used and the sublevel set filtration is assumed to be compact and $\HLC$.

% \[
% (m^{>e}_d - p_d) + (-1)^1 (m^{>e}_{d-1} - p_{d-1}) + \dots + (-1)^n (m^{>e}_0 - p_0) \geq 0
% \]

% \begin{thm}
% With notation as above, assume that $\tilde H_{d}(X_{\leq \bullet})$ is q-tame and upper-semicontinuous for all $d$ with multiplicity function $\mathfrak{m}_{d}$. Assume that $\tilde H_{d}(X_{\leq \bullet})$ is eventually constant for all $d$ and that $\mathfrak{m}_{d}(-\infty, q) = 0$ for all $q$ and $d$. Then the following hold.
% \begin{enumerate}
% 	\item The numbers $m_{d}^{> e}(F, t)$ are finite for all $t \in \R$ and non-zero for only finitely many $t \in \R$.
% 	\item The numbers $p_{d}(F)$ are finite.
% 	\item We have 
% 	\[
% 	m_{d}^{> e}(F) = \sum_{\substack{(p,q)\\q-p>e\\q\neq\infty}}\mathfrak{m}_{d-1}(p,q)+\sum_{\substack{(p,q)\\q-p>e\\p\neq-\infty}}\mathfrak{m}_d(p,q).
% 	\]
% 	\item The Morse inequalities 
% 	\[
% 	(m^{>e}_n-p_n)+(-1)^1 (m^{>e}_{n-1}-p_{n-1})+\dots+(-1)^n (m^{>e}_0-p_0)\geq 0
% 	\]
% 	hold for all $n$.
% \end{enumerate}
% \end{thm}

%For semi-continuity: \cref{thm:cech_cont} and the fact that $\lim_{\varepsilon > 0} X_{\leq t + \varepsilon} = X_{\leq t}$.
%For q-tameness: \cref{t:strong local connectedness implies q-tameness}.
%For the rest: Boundedness of $F$.

### 2021-05-14 introduction.tex
Add homology theories and full proof

--- 2021-04-15 introduction.tex
@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Now a days, when thinking about the pioneering work of Marston Morse in this domain, a smooth function on a closed differential manifold is possibly our first association but, as we describe next, it should not be our last.
-In the \textit{finite} context, Morse theory was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}; where he also move beyond this setting to give a new proof of Bott's periodicity, applying Morse theory to the energy functional of paths in a Riemannian manifold.
-Another example of the importance of Morse's insights in infinite contexts is Floer's work on the Arnold conjecture.
-Morse himself worked in a significantly less constraint setup, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context of semi-continuous functionals on metric spaces.
-He name this body of work \textit{functional topology}.
-Motivation for its development came from the study of minimal surfaces.
-Jesse Douglas received the fields medal in 1936 for solving in 1931 \cite{Douglas.1931} Plateau’s Problem: prove the existence of a bounding area-minimizing surface for any given admissible curve.
-In \cite{Morse.1939, Morse.1941}, Morse and Tompkins used functional topology to give conditions for the existence of \textit{unstable} minimal surfaces, i.e., critical points of the Douglas functional that do not locally minimize area.
+Nowadays, when thinking about the pioneering work of Marston Morse, our first association is possibly with a smooth function on a closed differential manifold, but, as we describe next, that should not be our the last.
+Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also focused on applications beyond this restricted setting;
+giving a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Another important example of the use of Morse's insights in an infinite setting is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
+Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
+He named this body of work functional topology and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
+In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their unstable minimal surface theorem which gives conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
 
-Some of Morse's ideas from functional topology, and in particular from \cite{Morse.1940}, have been rediscovered in topological data analysis.
-Morse studied the topology of a sublevel set filtration introducing invariants that encode the same information as the modern persistent homology groups.
-Even though Morse did not have a structure theory of persistence modules via barcodes, he emphasized many points that are crucial from point of view:
-The use of homology with field coefficients and the restriction to functionals giving rise to persistence modules with interval decompositions.
+While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have been rediscovered in the study of persistent homology, a method originated in applied topology ---based on the functoriality of the homology construction--- providing robust and effectively computable invariants of filtered spaces.
+The successes of this technique have motivated the development of an abstract and rich theory of persistence, lying in the intersection of representation theory, geometry, and topology, and whose influence goes beyond applied topology.
 
-In modern applications of the theory of persistence to problems in geometry, the existence of an interval decomposition allows the use of the bottleneck and other metrics on the space of barcodes.
-Rendering a finite metric model on which geometric problems can be recasted.
+One of the cornerstones of persistence theory comes from the fact that its basic invariants, known as barcodes, can be organized into a metric space, and that passing from filtrations to barcodes is $1$-Lipschitz.
+This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
 
-The spaces to which functional topology can be applied to are not necessarily of the homotopy type of CW-complexes, which makes the choice of homology construction an important element of the discussion.
-For many constructions ---including the preferred theory of Morse: \v{C}ech homology--- it was shown in \cite{schmahl2020structure} that the key condition needed for the existence of an interval decomposition of the persistence module associated to a semi-continuous sublevel set filtration is its \textit{q-tameness}.
-This condition simply states that the inclusion of distinct sublevel sets induces a linear map with finite dimensional rank.
+Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations, a property that simply states that the inclusion of distinct sublevel sets induces a linear map with finite dimensional rank.
+The q-tame property is key for the existence of barcodes, and for Morse, it is useful to provide a version of his famous inequalities in functional topology, which we review in terms of barcodes in \cref{s:inequalities}.
 
-To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel filtration are forms of local-connectivity.
-In their development of functional topology and its applications to minimal surface theory, Morse and Tompkins presented certain forms of local-connectivity claimed to imply q-tameness; unfortunately, neither the proofs nor the statements are correct.
-Please consult Section~\ref{s:historical} for more details on this problem and its history.
+The spaces that functional topology deals with are not necessarily of the homotopy type of CW-complexes, making the choice of homology construction an important element of the discussion.
+Morse worked with a metric version of \v{C}ech homology which we review in \cref{s:vietoris}.
+This choice ensures that the homology functor is well behaved with respect to certain limits, a property which in conjunction with q-tameness has been shown to ensure the existence of barcodes in general \cite{schmahl2020structure}.
 
-In this paper we analyze in great detail the relationship between different forms of local-connectivity and q-tameness.
-In particular, we show how to strengthen Morse's notion so that the parts of his groundbreaking work depending on q-tameness stand, including the aforementioned critical surface theorem.
+Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
+In particular, Morse and Tompkins use in their applications to minimal surface theory the following version:
+\begin{displaycquote}[p.431]{Morse.1940}
+	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
+\end{displaycquote}
+Here, $M$ is a metric space and $F$ a real-valued function on $M$ whose sublevel sets $F_{t}$ are all compact.
+Morse then states that as consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
+In the original it reads:
+\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
+	Let $a$ and $c$ be positive constants such that $a < c < 1$.
+	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
+\end{displaycquote}
+Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem 6.1]{Morse.1938}.
+Unfortunately, the claim as stated is not correct and in this work we provide a counterexample as a consequence of \cref{thm:counterexample}.
 
-By resurfacing the work of Morse in the novel context of persistence theory, we aim at increasing the number and depth of interactions between this rapidly developing field and geometry, topology, and functional analysis.
+We introduce a stronger version of local-connectivity and obtain the statement above, using this notion, as a consequence of \cref{t:strong local connectedness implies q-tameness}.
+Since the Douglas functional defines a sublevel set filtration satisfying our version of local-connectivity, the work of Morse and Tompkins depending on q-tameness stand, including the Morse inequalities and the aforementioned unstable minimal surface theorem.
+
+By reinterpreting the work of Morse in the modern context of persistence theory, we aim at increasing the number and depth of interactions occurring between this rapidly developing field on one side, and geometry, topology, and functional analysis on the other.
 
 An overview of this article follows.
-In Section~\ref{s:homology} we review different constructions of ordinary homology theory including: \v{C}ech, Vietoris and singular.
-In section~\ref{s:persistence} we recall the basics of persistence theory where, for us, the persistence homology of a sublevel set filtration is the key example.
-Section~\ref{s:connectivity} is the core of this work.
-We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply the associated persistence module is q-tame.
-We close with a historical overview of Morse's functional topology in Section~\ref{s:historical}.
+In \cref{s:homology} we review some basic constructions of homology theory paying special attention to \v{C}ech homology.
+In \cref{s:persistence} we recall the foundations of persistence theory where, for us, the persistent homology of a sublevel set filtration is the key example.
+In \cref{s:inequalities}, we present a persistence-theoretic point of view on Morse inequalities, relating to Morse's version of these inequalities in functional topology.
+\cref{s:connectivity} is the core of this work.
+We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply that the associated persistence module is q-tame.
+We close with a historical overview of Morse's functional topology and its relation to our previous results in \cref{s:surfaces}.

### 2021-05-14 main.tex
Add homology theories and full proof

@@
 \usepackage{amsmath, amsthm, amssymb}
-\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
-\usepackage[capitalize,noabbrev]{cleveref}
 \usepackage{tikz-cd}
-%\usepackage{newtxtext,newtxmath}
 \usepackage[numbers,sort,compress]{natbib}
@@
 \usepackage{csquotes}
-
-%To-do
-\usepackage[marginpar]{todo}
-%\makeatletter
-%\renewcommand{\@tododisplay}[1]{%
-%%\marginpar{#1}%
-%\textsuperscript{#1}%
-%}
-%%
-%\renewcommand\@displaytodo[2][\todomark]{%
-%\@tododisplay{{\todoformat [#1~\ref{todolbl:\thetodo}]}}%
-%\footnotetext[\thetodo]{\todoformat #1:~#2}%
-%\global\@todotoks\expandafter{\the\@todotoks\todoitem{#1}{#2}}%
-%\@todotrue%
-%}%
-%\renewcommand\todomark{todo}
-%\makeatother
+\usepackage[bookmarks=true,
+bookmarksnumbered=true, breaklinks=true,
+pdfstartview=FitH, hyperfigures=true,
+plainpages=false, naturalnames=true,
+colorlinks=true, pagebackref=true,
+pdfpagelabels]{hyperref}
+\hypersetup{
+	linktocpage,
+	colorlinks,
+	citecolor=blue,
+	linkcolor=blue,
+	urlcolor=blue}
+\usepackage[capitalize, noabbrev]{cleveref}
 
@@
 \newcommand{\HLC}{\mathrm{HLC}}
+\newcommand{\piT}{\pi\mathrm{T}}
+\newcommand{\LC}{\mathrm{LC}}
+\newcommand{\NH}{\mathrm{NH}}
+\newcommand{\piLC}{\pi\mathrm{LC}}
 \newcommand{\HE}{\mathbb{H}^d}
@@
 \DeclareMathOperator{\Cov}{Cov}
-\DeclareMathOperator{\Vietoris}{Vietoris}
+\DeclareMathOperator{\Vietoris}{Vtr}
 \DeclareMathOperator{\Balls}{Balls}
+\DeclareMathOperator*{\colim}{colim}
+\DeclareMathOperator{\crit}{crit}
 \newcommand\MCH{M\check{H}}
@@
 \setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
+\addtolength{\textwidth}{-2.5in}
 \setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
+\addtolength{\textheight}{-2.5in}
 \calclayout
-
-\newcommand{\anibal}[1]{\textcolor{blue}{[Anibal: #1]}}
 
@@
 \title[Persistence in functional topology]{Persistence in functional topology: local-connectivity, q-tameness and a correction to a theorem of Morse}
-\author{}
+
+% % Anibal
+% \author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
+% \address{Max Planck Institute for Mathematics, Bonn, Germany}
+% \email{ammedmar@mpim-bonn.mpg.de}
+% \address{Department of Mathematics, University of Notre, Notre Dame, IN, USA}
+% \email{amedinam@nd.edu}
+
 \date{\today}
@@
 \begin{abstract}
-	During the 1930's Morse developed a general theory, which he named functional topology, relating the critical set of a semi-continuous functional and the topology of its sublevel sets; and, in joint work with Tompkins, used this body of work to study minimal surfaces.
-	Many of the key insights of functional topology have been rediscovered in the study of persistence homology.
-	In particular, conditions enforcing the existence of an interval decomposition are as central to functional topology as they are to persistence theory.
-	With modern applications to geometry in mind, in this article we present an up-to-date study of local-connectivity for Morse filtrations, and provide in passing a correction to the Critical Surface Theorem of Morse and Tompkins.
+	During the 1930's Morse developed the theory of functional topology relating the critical set of a semi-continuous functional and the topology of its sublevel sets.
+	Morse and Tompkins applied this body of work in the setting defined by Douglas' solution to Plateau's Problem, and proved with it their Unstable Minimal Surface Theorem.
+	Many of the key insights of functional topology have been rediscovered in the study of persistent homology, with the notion of q-tameness being as central to functional topology as it is to persistence theory.
+	With applications to geometry in mind, in this article we present a modern treatment of the relationship between local-connectivity properties of sublevel set filtrations, Morse inequalities, and the q-tameness of their associated persistence modules.
+	As a consequence of our analysis we identify a gap in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins and provide a correction.
 \end{abstract}
@@
 \input{persistence}
+\input{inequalities}
 \input{connectivity}
-%\input{outlook}
-\input{historical}
-%\input{other}
+\input{surfaces}
+\appendix
+\input{vietoris}
 
@@
 
+A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL where part of this work developed.
+
 \bibliographystyle{abbrvnaturl}
@@
 
-\todos
 \end{document}

### 2021-05-14 persistence.tex
Add homology theories and full proof

@@
-\section{Sublevel filtrations and persistence theory} \label{s:persistence}
+\section{Sublevel set filtrations and persistence theory} \label{s:persistence}
 
-%\todo{start with the standard vector space setting, before generalizing?}
 Let $R$ be a ring.
-The category of \emph{persistence $R$-modules} is the functor category  $(\Mod{R})^{\mathbf{R}}$, where $\mathbf{R}$ is the category corresponding to the real numbers $\mathbb{R}$ considered as a poset.
-We will simply say \emph{persistence module} if the coefficient ring is clear from the context.
+The category of \emph{persistence $R$-modules} is the category of functors from the poset $\R$ to the category of $R$-modules.
+We will simply call its objects \emph{persistence modules} if the coefficient ring is clear from the context.
 
-A persistence module $M$ is called \emph{pointwise finitely generated ($\PFG$)} if $M_{t}$ is a finitely generated module for every $t\in\mathbb{R}$.
-$M$ is called \emph{q-tame} if $\im (M_{s}\to M_{t})$ is finitely generated for all $s<t\in\mathbb{R}$.
-Recall that for Noetherian rings, being finitely generated is equivalent to being finitely presented, which is a more relevant notion in computational settings.
+A persistence module $M$ is said to be \emph{pointwise finitely generated} ($\PFG$) if $M_{t}$ is a finitely generated module for every $t \in \mathbb{R}$.
+A persistence module $M$ is \emph{q-tame} if $\im (M_{s} \to M_{t})$ is finitely generated for all $s < t$.
+Recall that for Noetherian rings being finitely generated is equivalent to being finitely presented, a notion which is more relevant in computational settings.
 
-The theory of persistence modules is particularly nice if $R=\mathbb{F}$ is a field, which we will assume for the rest of this section.
-In this case, we will say that $M$ is \emph{pointwise finite-dimensional ($\PFD$)} instead of $\PFG$.
+The theory of persistence modules is particularly well-behaved if the coefficient ring is a field $\mathbb{F}$, which we will assume for the rest of this section.
+In this case, we will say that $M$ is \emph{pointwise finite-dimensional} ($\PFD$) instead of $\PFG$.
+A key property allowed by restricting persistence modules to field coefficient is the existence of a complete combinatorial invariant which we now review.
 
-What makes the field coefficient case nice is that it allows for a combinatorial description of many persistence modules in terms of basic summands.
-Concretely, we say that $M$ has a \emph{barcode} if there is a family of intervals $(I_{\alpha})_{\alpha}$, $I_{\alpha}\subseteq\mathbb{R}$ such that
+We say that $M$ has a \emph{barcode} if there is a family $(I_{\alpha})_{\alpha}$ of intervals $I_{\alpha}\subseteq\mathbb{R}$ such that
 \[
-M\cong\bigoplus_{\alpha} C(I_{\alpha}),
+M \cong \bigoplus_{\alpha} C(I_{\alpha}),
 \]
-where the persistence module $C(I)$ for an interval $I$ is defined via
-\[
-C(I)_t=
+where the interval persistence module $C(I)$ is defined by
+\begin{equation} \label{e:interval module}
+    C(I)_t =
     \begin{cases}
-    \mathbb{F} & \text{if } t\in I,\\
-    0              & \text{otherwise,}
+        \mathbb{F} & \text{if } t\in I, \\
+        0          & \text{otherwise},
     \end{cases}
     \qquad
-\text{with structure maps}
     \qquad
-C(I)_{t,u}=
+    C(I)_{s, t} =
     \begin{cases}
-    \operatorname{id}_{\mathbb{F}} & \text{if } t,u\in I,\\
-    0              & \text{otherwise.}
+        \operatorname{id}_{\mathbb{F}} & \text{if } s, t \in I,\\
+        0 & \text{otherwise}.
     \end{cases}    
-\]
+\end{equation}
 
 Interval modules are indecomposable in the category of persistence modules and by the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832}, two direct sums of interval modules can only be isomorphic if the corresponding families of intervals already agree.
-Hence, we can speak of \emph{the} barcode of a persistence module and use it as a complete isomorphism invariant.
+Hence, the barcode of a persistence module is well defined and is a complete isomorphism invariant.
 
@@
 
-As is well-known, Crawley-Boevey's Theorem does not extend to q-tame persistence modules.
-However, there are still ways to get a notion of barcode for q-tame persistence modules, for example by phrasing the definition of barcode in terms of so-called rectangle measures \cite{Chazal.2016a}.
+It is well known that the Crawley-Boevey Theorem does not extend to q-tame persistence modules, see \cite{Chazal.2016a} for counterexamples.
+However, there are alternative methods to define a notion of barcode for q-tame persistence modules, for example by phrasing the definition of barcode in terms of so-called rectangle measures \cite{Chazal.2016a}.
 Other methods include using a slightly weaker notion of isomorphism for the direct sum decomposition into interval modules \cite{Chazal.2016b} or imposing additional algebraic constraints and allowing for the decompositions to be in terms of products instead of sums \cite{schmahl2020structure}.
@@
 The usefulness of barcodes in applications often rests on their stability.
-To make precise what stability means, we define the \emph{interleaving distance} between two persistence modules $M$ and $N$ as
-\[
-d_{I}(M,N)=\inf\{\delta>0\mid\text{there exists a }\delta\text{-interleaving between }M\text{ and }N\},
-\]
-where a $\delta$-interleaving between $M$ and $N$ is given by a collection of maps $M_{t}\to N_{t+\delta}$ and $N_{t}\to M_{t+\delta}$ for each $t\in\mathbb{R}$ such that the diagrams
+A precise formulations of this property use the interleaving and bottleneck distances which we review next.
+For $\delta > 0$, a $\delta$-interleaving between persistence modules $M$ and $N$ is given by maps $M_{t} \to N_{t+\delta}$ and $N_{t}\to M_{t+\delta}$ for each $t \in \R$ such that the diagrams
 \[
@@
 \]
-commute for all $s<t\in\mathbb{R}$.
+commute for all $s < t \in \R$.
 
-We also define the \emph{Bottleneck distance} between two barcodes $B=(I_{\alpha})_{\alpha\in A}$ and $B'=(I'_{\alpha'})_{\alpha'\in A'})$ as
-\[
-d_{b}(B,B')=\inf\{\delta>0\mid\text{there exists a }\delta\text{-matching between }M\text{ and }N\},
-\]
-where a $\delta$-matching between $B$ and $B'$ is given by subsets $X\subseteq A$, $X'\subseteq A'$ and a bijection $\sigma\colon X\to X'$ such that
+The \textit{interleaving distance} $d_{I}(M,N)$ is defined as the infimum over all $\delta > 0$ for which there exists a $\delta$-interleaving between $M$ and $N$.
+We also define the \emph{bottleneck distance} $d_{b}(B,B')$ between two barcodes $B = (I_{\alpha})_{\alpha\in A}$ and $B' = (I'_{\alpha'})_{\alpha'\in A'}$ as the infimum over all $\delta > 0$ for which there exists a $\delta$-matching between $B$ and $B'$, where a $\delta$-matching between $B$ and $B'$ is given by subsets $X\subseteq A$, $X'\subseteq A'$ and a bijection $\sigma\colon X\to X'$ such that
 \[
@@
 whenever there is $\alpha\in A\setminus X$ with $I=I_{\alpha}$ or $\alpha'\in A'\setminus X'$ with $I=I'_{\alpha'}$, and
-\begin{align*}
-\lvert \sup I'_{\sigma(\alpha)} - \sup I_{\alpha} \rvert &< \delta \\
-\lvert \inf I'_{\sigma(\alpha)} - \inf I_{\alpha} \rvert &< \delta
-\end{align*}
+\begin{equation*}
+\lvert \sup I'_{\sigma(\alpha)} - \sup I_{\alpha} \rvert < \delta, \qquad
+\lvert \inf I'_{\sigma(\alpha)} - \inf I_{\alpha} \rvert < \delta
+\end{equation*}
 for all $\alpha\in X$.
 
-\begin{thm}[{{\cite[Theorem 5.14]{Chazal.2016a}}}]
+\begin{thm}[{{\citet[Theorem 5.14]{Chazal.2016a}}}]
 Let $M$ and $M'$ be q-tame persistence modules with barcodes $B$ and $B'$. Then
@@
 
-The most commonly studied example of a persistence module is \emph{persistent homology}, i.e., the persistence module obtained by applying homology to an $\mathbb{R}$-indexed diagram of spaces.
-In what follows, we will study the persistent homology of certain classes of such diagrams, namely filtrations.
-If $V$ is a diagram of topological spaces, we call it a \emph{filtration} if $V_s\to V_t$ is an embedding for all $s\leq t\in\mathbb{R}$.
+The most commonly studied example of a persistence module is \emph{persistent homology}, i.e., the persistence module obtained by applying a homology theory to a filtered space $X = \bigcup_{t \in \R} X_{\leq t}$.
 
-A \textit{sublevel set filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
-For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
+\begin{defi}
+Given a space $X$ and a function $f \colon X \to \R$, the \textit{sublevel set filtration} of $X$ induced by $f$ is defined by
 \begin{equation*}
-X_{\leq t} = f^{-1}((-\infty, t]).
+X_{\leq t} = f^{-1}(-\infty, t].
 \end{equation*}
+% We refer to $X_{\leq t}$ as the the \textit{$t$-sublevel set},
+We say this filtration is \textit{compact} if $X$ is a locally compact Hausdorff space and all sublevel sets are compact.
+We say that the filtration is \emph{q-tame} with respect to a homology theory $\H$ if $\H (X_{\bullet})$ is a q-tame persistence module.
+\end{defi}
 
-Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x$ in $X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every $x$ in $X$, every neighborhood of $x$ contains a compact neighborhood of $x$.
+% \begin{defi}
+% If $V$ is an $\mathbb{R}$-indexed diagram of topological spaces, we call it a \emph{filtration} if $V_s\to V_t$ is an inclusion for all $s\leq t\in\mathbb{R}$.
+If $X$ is a space and $f\colon X\to\mathbb{R}$ is a function, we obtain a \textit{sublevel set filtration} $X_{\leq\bullet}$, where for any $t \in \R$, the \textit{$t$-sublevel set} is defined by
+% \begin{equation*}
+% X_{\leq t} = f^{-1}(-\infty, t].
+% \end{equation*}
+% We say that the sublevel set filtration is \emph{compact} if $X$ is a locally compact Hausdorff space and all sublevet sets $X_{\leq t}$ are compact.
+% \end{defi}
 
-A sublevel set filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
-Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.
+%Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x$ in $X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every $x$ in $X$, every neighborhood of $x$ contains a compact neighborhood of $x$.
+
+%A sublevel set filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
+%Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.

### 2021-05-14 surfaces.tex
Add homology theories and full proof

\section{Minimal surfaces and functional topology} \label{s:surfaces}

Morse and Tompkins considered the following setting introduced by Douglas.
Let $g \colon \R \to \R^n$ be $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and such that there are three distinct points $\alpha_i \in [0,2\pi)$ with $\varphi(\alpha_i)=\alpha_i$.
The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined by
\begin{equation*}
A_g(\varphi)=\frac{1}{16}\int_0^{2\pi}\int_0^{2\pi}\sin\left(\frac{\alpha-\beta}{2}\right)^{-2} \! \lVert g(\varphi(\alpha))-g(\varphi(\beta)) \rVert_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta.
\end{equation*}
Let $\Omega_g=\{\varphi\in\widetilde\Omega\mid A_g(\varphi)<\infty\}$.
Douglas proved that, for a large class of curves $g$ the set $\Omega_g$ is non-empty with compact sublevel sets of $A_g$.
Since $A_g$ is bounded below by $0$, this implies that $A_g$ has a unique global minimizer.
Douglas then used harmonic analysis to show that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem.

In \cite[p.445]{Morse.1939}, Morse and Tompkins introduce for any metric space $M$ and $F \colon M \to \R$ a homotopical version of critical point.
Intuitively, a point $p$ is \textit{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.

Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, i.e., a minimal surface.
They then use a form of Morse inequalities for homotopically critical points
% , or, more generally, critical sets
to infer their unstable minimal surface theorem:
\begin{itemize}
    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of index 1.
\end{itemize}

In \cref{s:inequalities} we review Morse's topological inequalities using the language of barcodes.
In order to apply these inequalities and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$. 
For this they want to use that $(\Omega_g, A_g)$ is weakly $\piLC$ \cite[p.431]{Morse.1940}. This property is not sufficient to ensure q-tameness as \cref{thm:counterexample} demonstrates.
However, the proof given in \cite[p.464]{Morse.1939} establishes that $(\Omega_g, A_g)$ is $\LC$, implying that it is also $\HLC$ for any homology theory.
Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is q-tame as claimed.
This implies that Morse inequalities hold as does the unstable minimal surfaces theorem of Morse.

% We also mention that in \cite[p.421]{Morse.1937} appearing three years before the work of Morse-Tompkins on minimal surfaces, Morse considered the notion of $\piLC$ and claiming it to be sufficient to ensure q-tameness of compact sublevel set filtrations.

% We anticipate that the stronger version of local $F$-connectivity introduced by Morse, and inspiring our $\HLC$ notion, is also sufficient to obtain q-tameness, but we do not provide a proof.

% A stronger notion of local connectivity for the pair $(M, F)$ appeared in print, introduced by Morse himself three years earlier, and claimed sufficient for q-tameness although no proof was given.
% \begin{displaycquote}[p.421]{Morse.1937}
% 	The space $M$ will be said to be locally $F$-connected for the order $n$ if corresponding to $n$, an arbitrary point $p$ on $M$, and an arbitrary positive constant $e$, there exists a positive constant $\delta$ with the following property. For $c \geq F(p)$ any singular $n$-sphere on $F \leq c$ (the continuous image on $F \leq c$ of an ordinary $n$-sphere) on the $\delta$-neighborhood $p_{\delta}$ of $p$ is the boundary of a singular $(n + 1)$-cell on $F \leq c + e$ and on $p_e$.
% \end{displaycquote}
% This is precisely the notions of $\piLC$ \cref{defi:local_connectedness_filtrations}.

% As is, the argument given by Morse and Tompkins to establish $(\ast)$ is not strictly valid, however, the proof of the local $A_g$-connectivity of $\Omega_g$ given in \cite[p.?]{Morse.1939} establishes th stronger statement implying, in our terminology, that $(\Omega_g, A_g)$ is $\HLC$ for any homology theory, and \cref{t:strong local connectedness implies q-tameness} fixes this gap.
% We anticipate that the stronger version of local $F$-connectivity introduced by Morse, and inspiring our $\HLC$ notion, is also sufficient to obtain q-tameness, but we do not provide a proof.

### 2021-05-14 vietoris.tex
Add homology theories and full proof

\section{Vietoris homology} \label{s:vietoris}

In his work on functional topology, Morse uses the Vietoris homology for metric spaces as introduced in \cite{MR1512371}. So far, we have considered \v{C}ech homology instead, applying a topological rather than metric construction.
We will recall the definition of Vietoris homology and recall that these two constructions yield the same result for compact metric spaces.

\v{C}ech homology of a pair of spaces $(X_{1}, X_{2})$ was defined as the inverse limit over the homology of nerves of covers of $(X_{1}, X_{2})$.
As an alternative to the nerve construction, for a cover $\alpha = (\alpha_{1}, \alpha_{2})$ one can define $\Vietoris(\alpha)$ as the simplicial pair $\big(\Vietoris (\alpha_{1}), \Vietoris (\alpha_{2})\big)$, where 
\[
\Vietoris (\alpha_{i}) = \left\{ \sigma \subseteq X_{i} \mid \sigma \text{ is finite and there is } U \in \alpha_{i} \text{ with } \sigma \in U \right\}.
\]
This construction is dual in the sense of Dowker's Theorem \cite{Dowker.1952} to the nerve construction.
As a consequence, we have that
$
H_{*} (\Nrv (\alpha); G) \cong H_{*} (\Vietoris (\alpha); G)
$
for any coefficient group $G$.
This isomorphism is natural with respect to refinement and compatible with the boundary operators, so that we get an alternative description of \v{C}ech homology as 
%the inverse limit over the homology of Vietoris complexes of covers.
\[
\lim_{\alpha \in \Cov (X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \, \cong\, \CH (X_{1}, X_{2}; G)
\]
This is still not exactly the construction of Vietoris homology of a pair of metric spaces $(X_{1}, X_{2})$ as presented in \cite{MR1512371}, which in modern notation is the limit
\begin{equation*}
    \lim_{\alpha \in \Balls(X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G),
\end{equation*}
where 
\[
\Balls (X_{1}, X_{2}) = \left\{ \big( ( B_{\delta} (x) )_{x \in X_{1}} , ( B_{\delta} (x) )_{x \in X_{2}} \big) \mid \delta > 0 \right\}
%\left\{ \big(B_{\delta}(x),\ B_{\delta}(y) \big) \right\}_{(x,y) \in X_{1} \times X_2} 
\subseteq \Cov (X_{1}, X_{2}).
\]
But if the metric pair $(X_{1}, X_{2})$ is compact, then $\Balls (X_{1}, X_{2})$ is coinitial in $\Cov (X_{1}, X_{2})$, that is to say, they define the same limit.
Thus, we have natural isomorphisms
\[
\lim_{\alpha \in \Balls(X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \ \cong \,
%\lim_{\alpha \in \Cov (X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \, \cong\, 
\CH (X_{1}, X_{2}; G),
\]
so in Morse's setting the metric Vietoris homology theory he uses is indeed the same as the \v{C}ech homology we considered earlier on.

### 2021-05-14 connectivity.tex
Change introduction: more general viewpoint moving Morse original back

@@
 We will now show that for any homology theory the property of being $\HLC$ implies that of being q-tame for compact sublevel set filtrations.
-Since the Douglas functional induces a filtration which is $\LC$, the following result fixes the gap in the unstable minimal surface theorem of Morse and Tompkins.
+Since the Douglas functional induces a filtration which is $\LC$, the following result fixes the gap in the Unstable Minimal Surface Theorem of Morse and Tompkins.
 

### 2021-05-14 surfaces.tex
Change introduction: more general viewpoint moving Morse original back

@@
+Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
+In particular, Morse and Tompkins use in their applications to minimal surface theory the following version:
+\begin{displaycquote}[p.431]{Morse.1940}
+	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
+\end{displaycquote}
+Here, $M$ is a metric space and $F$ a real-valued function on $M$ whose sublevel sets $F_{t}$ are all compact.
+Morse then states that as consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
+In the original it reads:
+\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
+	Let $a$ and $c$ be positive constants such that $a < c < 1$.
+	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
+\end{displaycquote}
+Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem 6.1]{Morse.1938}.
+Unfortunately, the claim as stated is not correct and in this work we provide a counterexample as a consequence of \cref{thm:counterexample}.
+
 \section{Minimal surfaces and functional topology} \label{s:surfaces}
@@
 % , or, more generally, critical sets
-to infer their unstable minimal surface theorem:
+to infer their Unstable Minimal Surface Theorem:
 \begin{itemize}

### 2021-05-14 introduction.tex
Updates from Overleaf

@@
 He named this body of work functional topology and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their unstable minimal surface theorem which gives conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
+In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their Unstable Minimal Surface Theorem which gives conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
 
-While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have been rediscovered in the study of persistent homology, a method originated in applied topology ---based on the functoriality of the homology construction--- providing robust and effectively computable invariants of filtered spaces.
-The successes of this technique have motivated the development of an abstract and rich theory of persistence, lying in the intersection of representation theory, geometry, and topology, and whose influence goes beyond applied topology.
+While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have been rediscovered in the study of persistent homology.
+A method originated in applied topology and based on the functoriality of the homology construction, that provides robust and effectively computable invariants of filtered spaces.
+The successes of this technique have motivated the development of an abstract and rich theory of persistence, lying in the intersection of representation theory, geometry, and topology, and whose influence extends beyond it original domain.
 
-One of the cornerstones of persistence theory comes from the fact that its basic invariants, known as barcodes, can be organized into a metric space, and that passing from filtrations to barcodes is $1$-Lipschitz.
+One of the primary reasons for the use of persistence theory in geometry is the fact that its basic invariants, known as barcodes, can be organized into a metric space, and that passing from filtrations to barcodes is $1$-Lipschitz.
 This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
 
-Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations, a property that simply states that the inclusion of distinct sublevel sets induces a linear map with finite dimensional rank.
-The q-tame property is key for the existence of barcodes, and for Morse, it is useful to provide a version of his famous inequalities in functional topology, which we review in terms of barcodes in \cref{s:inequalities}.
+For the existence of barcodes some form of finite-dimensionality must be assumed of the  filtered space being considered.
+The most general condition associated to this problem is known as quadrant-tameness or q-tameness for short \cite{bibid}.
+It simply states that the inclusion of distinct sublevel sets induces in homology with field coefficients a linear map with finite dimensional rank.
 
-The spaces that functional topology deals with are not necessarily of the homotopy type of CW-complexes, making the choice of homology construction an important element of the discussion.
-Morse worked with a metric version of \v{C}ech homology which we review in \cref{s:vietoris}.
-This choice ensures that the homology functor is well behaved with respect to certain limits, a property which in conjunction with q-tameness has been shown to ensure the existence of barcodes in general \cite{schmahl2020structure}.
+Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations.
+These allowed him to state and prove a version his famous inequalities for general filtered spaces using homotopical critical points.
+These inequalities are crucial for applications and we reinterpret them in the modern language of barcodes in \cref{s:inequalities}.
 
-Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins use in their applications to minimal surface theory the following version:
-\begin{displaycquote}[p.431]{Morse.1940}
-	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
-\end{displaycquote}
-Here, $M$ is a metric space and $F$ a real-valued function on $M$ whose sublevel sets $F_{t}$ are all compact.
-Morse then states that as consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
-In the original it reads:
-\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
-	Let $a$ and $c$ be positive constants such that $a < c < 1$.
-	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
-\end{displaycquote}
-Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem 6.1]{Morse.1938}.
-Unfortunately, the claim as stated is not correct and in this work we provide a counterexample as a consequence of \cref{thm:counterexample}.
+Since general applications may take us away from spaces with the homotopy type of CW-complexes, the choice of homology construction is an important element of the discussion.
+Two types of properties of these constructions are important for the existence of barcodes.
+On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietories exact sequences.
+On the other, those ensuring that q-tame persistence modules admit a multiplicative interval decomposition, which was shown in \cite{schmahl2020structure} to follow from the preservation of certain categorical limits.
 
-We introduce a stronger version of local-connectivity and obtain the statement above, using this notion, as a consequence of \cref{t:strong local connectedness implies q-tameness}.
-Since the Douglas functional defines a sublevel set filtration satisfying our version of local-connectivity, the work of Morse and Tompkins depending on q-tameness stand, including the Morse inequalities and the aforementioned unstable minimal surface theorem.
+Our analysis allows us to show the insufficiency of the local-connectivity assumption used by Morse and Tompkins to state that the filtration defined by Douglas's functional is q-tame.
+This is because it falls into the class ruled out by \cref{thm:counterexample}.
+The existence of Morse inequalities requires q-tameness and, hence, so does the Unstable Minimal Surface Theorem of Morse and Tompkins.
+Nonetheless, this filtration satisfies a stronger condition which \cref{t:strong local connectedness implies q-tameness} ensures to be sufficient
 
-By reinterpreting the work of Morse in the modern context of persistence theory, we aim at increasing the number and depth of interactions occurring between this rapidly developing field on one side, and geometry, topology, and functional analysis on the other.
+By reinterpreting the work of Morse in the modern context of persistence theory, and clarifying the conditions needed to prove the existence of barcodes for a broad class of sublevel set filtrations, we aim to increase the number and depth of interactions occurring between persistence theory on one side, and geometry, topology, and functional analysis on the other.
 

### 2021-05-14 surfaces.tex
Updates from Overleaf
Modify Section: surfaces, bring Morse discussion there

@@
-Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins use in their applications to minimal surface theory the following version:
-\begin{displaycquote}[p.431]{Morse.1940}
-	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
-\end{displaycquote}
-Here, $M$ is a metric space and $F$ a real-valued function on $M$ whose sublevel sets $F_{t}$ are all compact.
-Morse then states that as consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
-In the original it reads:
-\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
-	Let $a$ and $c$ be positive constants such that $a < c < 1$.
-	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
-\end{displaycquote}
-Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem 6.1]{Morse.1938}.
-Unfortunately, the claim as stated is not correct and in this work we provide a counterexample as a consequence of \cref{thm:counterexample}.
-
 \section{Minimal surfaces and functional topology} \label{s:surfaces}
@@
 Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, i.e., a minimal surface.
-They then use a form of Morse inequalities for homotopically critical points
-% , or, more generally, critical sets
-to infer their Unstable Minimal Surface Theorem:
+They then use a form of Morse inequalities for homotopically critical points to infer their Unstable Minimal Surface Theorem:
 \begin{itemize}
@@
 
-In \cref{s:inequalities} we review Morse's topological inequalities using the language of barcodes.
 In order to apply these inequalities and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
-For this they want to use that $(\Omega_g, A_g)$ is weakly $\piLC$ \cite[p.431]{Morse.1940}. This property is not sufficient to ensure q-tameness as \cref{thm:counterexample} demonstrates.
+Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
+In particular, Morse and Tompkins use in their applications to minimal surface theory the following version equivalent to $\piLC$:
+\begin{displaycquote}[p.431]{Morse.1940}
+	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
+\end{displaycquote}
+They then state that as a consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
+In the original it reads:
+\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
+	Let $a$ and $c$ be positive constants such that $a < c < 1$.
+	The $k^{\mathrm{th}}$ connectivity $R^k(a,c)$ of $F_a$ on $F_c$ is finite.
+\end{displaycquote}
+Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
+Unfortunately, this argument is not in general sound as \cref{thm:counterexample} shows.
 However, the proof given in \cite[p.464]{Morse.1939} establishes that $(\Omega_g, A_g)$ is $\LC$, implying that it is also $\HLC$ for any homology theory.
 Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is q-tame as claimed.
-This implies that Morse inequalities hold as does the unstable minimal surfaces theorem of Morse.
-
-% We also mention that in \cite[p.421]{Morse.1937} appearing three years before the work of Morse-Tompkins on minimal surfaces, Morse considered the notion of $\piLC$ and claiming it to be sufficient to ensure q-tameness of compact sublevel set filtrations.
-
-% We anticipate that the stronger version of local $F$-connectivity introduced by Morse, and inspiring our $\HLC$ notion, is also sufficient to obtain q-tameness, but we do not provide a proof.
-
-% A stronger notion of local connectivity for the pair $(M, F)$ appeared in print, introduced by Morse himself three years earlier, and claimed sufficient for q-tameness although no proof was given.
-% \begin{displaycquote}[p.421]{Morse.1937}
-% 	The space $M$ will be said to be locally $F$-connected for the order $n$ if corresponding to $n$, an arbitrary point $p$ on $M$, and an arbitrary positive constant $e$, there exists a positive constant $\delta$ with the following property.
-For $c \geq F(p)$ any singular $n$-sphere on $F \leq c$ (the continuous image on $F \leq c$ of an ordinary $n$-sphere) on the $\delta$-neighborhood $p_{\delta}$ of $p$ is the boundary of a singular $(n + 1)$-cell on $F \leq c + e$ and on $p_e$.
-% \end{displaycquote}
-% This is precisely the notions of $\piLC$ \cref{defi:local_connectedness_filtrations}.
-
-% As is, the argument given by Morse and Tompkins to establish $(\ast)$ is not strictly valid, however, the proof of the local $A_g$-connectivity of $\Omega_g$ given in \cite[p.?]{Morse.1939} establishes th stronger statement implying, in our terminology, that $(\Omega_g, A_g)$ is $\HLC$ for any homology theory, and \cref{t:strong local connectedness implies q-tameness} fixes this gap.
-% We anticipate that the stronger version of local $F$-connectivity introduced by Morse, and inspiring our $\HLC$ notion, is also sufficient to obtain q-tameness, but we do not provide a proof.
+This implies that Morse inequalities hold, and hence so does the unstable minimal surfaces theorem of Morse.

### 2021-06-15 connectivity.tex
version with stability

--- 2021-04-15 connectivity.tex
@@
-\section{Local connectivity and q-tameness} \label{s:connectivity}
+\section{Persistence diagrams from local connectivity} \label{s:connectivity}
 
-Let $\H$ be a fixed homology theory.
+We have seen that q-tame functions admit persistence diagrams, which can be used to formulate Morse inequalities.
+With q-tameness being a rather abstract condition, we would now like to establish more concrete topological conditions that ensure the q-tameness of a function.
+Our definitions are motivated by similar conditions that Morse considered in his work on functional topology.
+We will present a historical account in \cref{s:surfaces}.
+
+Whether a function is q-tame or not depends on the functor that is used to pass from the sublevel set filtration of the function to a persistence module.
+The general idea that we want to employ is to deduce global finiteness properties like q-tameness from local ones.
+Thus, the functors we consider should have some property that allows us to do so.
+
+Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call \emph{homology}.
+A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps fit in a long exact sequence
+ \[
+\begin{tikzcd}[column sep = small]
+\cdots \arrow[r] & \H_{n}(X_{1} \cap X_{2}) \arrow[r] & \H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] & \H_{n}(X) \arrow[r] & \H_{n-1}(X_{1} \cap X_{2}) \arrow[r] & \cdots \ .
+\end{tikzcd}
+\]
+We say that $\H$ has the \emph{open} (resp.\@ \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@ compact Hausdorff).
+
+For the rest of this section, we will assume that $\H$ has the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$. 
+Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.
 
 \begin{defi} \label{defi:local_connectedness}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or \textit{trivial}, denoted $\HS_n$ and $\HT_n$ respectively, if the image of the map induced by $\H_n$ is finitely generated or 0, and we say it is \textit{homologically small} or \textit{trivial}, denoted respectively $\HS$ and $\HT$, if it is $\HS_n$ or $\HT_n$ for every~$n$.
+	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ($\HS_n$) if the image of the map induced by $\H_{n}$ is finite dimensional.
+	Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
+	%The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
+	We omit references to $n$ if the conditions hold for all integers.
+	%The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
 \end{defi}
 
-\begin{defi}
-	A space $X$ is said to be \emph{homologically locally connected}, denoted $\HLC$, if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$.
+%There are maps that are $\piT$ but not $\HT$ for singular or \v{C}ech homology. Consider for example the map from a torus to a sphere given by the collapse of its 1-skeleton.
+
+%Naturally, $\HT$ for singular or \v{C}ech homology does not imply $\piT$ either.
+%If the map is $\NH$ then it is $\piT$ and, if the value of $\H$ on a point is 0, $\HT$ as well.
+
+%\begin{defi}
+%	A space $X$ is said to be $\HLC$ (resp.
+$\piLC$, $\LC$) if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$ (resp.
+$\piT$, $\NH$).
+	%If the neighborhoods can be chosen so that these inclusion have contractible images we say that the space is \textit{locally contractible} ($\LC$).
+%\end{defi}
+
+%Local connectivity assumptions like the above ones have a long history of being used to ensure that different homology theories agree, e.g.
+in \cite{MR105677}, and to ensure that homology is finitely generated, where we mention the following example.
+%\begin{prop}[{\citet[p.~109]{MR0007094}}]
+%	A compact $\piLC$ Hausdorff space has finite Betti numbers.
+%\end{prop}
+
+%We will deduce the following similar result from our main contribution, \cref{t:strong local connectedness implies q-tameness}.
+
+%\begin{prop} \label{prop:HLC_single_space}
+%	Let $X$ be a compact Hausdorff space.
+%	If $X$ is $\HLC$ then $\H_{n}(X)$ is finitely generated for all $n$.
+%\end{prop}
+
+%We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
+
+%\begin{prop}[\citet{MR105677}] \label{prop:cech_sing_hom_hlc}
+%	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which %are $\HLC$ with respect to integral singular homology.
+%\end{prop}
+
+%As a direct consequence of the previous proposition, we obtain the following first persistence result.
+
+%\begin{cor}
+%	Let $f \colon X \to \R$ be a function with compact sublevel set filtration. If every sublevel set is $\piLC$ then $\H (X_{\leq \bullet})$ is $\PFD$ in every degree, in particular q-tame.
+%\end{cor}
+%
+%A similar statement with an $\HLC$ condition instead of the $\piLC$ conditions also holds as a consequence of our main theorem.
+Having each sublevel set being locally connected is, however, in many cases too restrictive.
+Moreover, the weaker finiteness property of being q-tame is sufficient to obtain a notion of barcode and formulate Morse inequalities.
+%Hence, we would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
+% The following definitions are motivated by Morse's work, in particular his local connectivity conditions mentioned in the introduction and reviewed in \cref{s:surfaces}.
+
+\begin{defi} \label{defi:local_connectedness_filtrations}
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\HLC$ 
+	%(resp.\@ $\piLC$, $\LC$) 
+	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+	\begin{equation*}
+	f_{\leq s} \cap U \to f_{\leq t} \cap V
+	\end{equation*}
+	is $\HT$.
+	%(resp.\@ $\piT$, $\NH$).
+    %
+	Similarly, the sublevel set filtration is called \emph{strongly $\HLC$} if for any $x \in X$, $V$ a neighborhood of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+	\begin{equation*}
+	f_{\leq s} \cap U \to f_{\leq t} \cap V
+	\end{equation*}
+	is $\HT$.
 \end{defi}
 
-Local connectivity assumptions have a long history of being used to ensure that different homology theories agree and to ensure that homology is finite dimensional.
-We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
+Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$. If the filtration is induced by a continuous function, the converse also holds, as the following theorem shows.
 
-\begin{prop}[\cite{MR105677}] \label{prop:cech_sing_hom_hlc}
-	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which are $\HLC$ with respect to integral singular homology.
-\end{prop}
+\begin{thm}\label{thm:hlc_to_strong_hlc}
+    If the sublevel set filtration of a continuous function $f \colon X \to \R$ is $\HLC$, then it is also strongly $\HLC$.
+\end{thm}
+\begin{proof}
+    Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
+We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HT$.
 
-\begin{prop} \label{prop:fin_dim_sing_hom}
-	Let $X$ be a compact Hausdorff space.
-	If $X$ is $\HLC$ with respect to integral singular homology, then the singular homology of $X$ with arbitrary coefficients is finite-dimensional in every degree.
-\end{prop}
+    To do so, we start by using the $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HT$.
+    Now, if $s = f(x)$, we choose $U = U'$. 
+    If $s > f(x)$, we choose $U = U' \cap f_{< s'}$, where $f_{< s'} = f^{-1} (-\infty, s')$.
+    %is the open sublevel set of $f$ at $s'$. 
+    Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of $X$.
 
-We will deduce the previous finiteness result from our main contribution, Theorem~\ref{t:strong local connectenss implies q-tameness}.
-To motivate the statement of our theorem let us record a direct consequence of the previous proposition.
+    In both cases, we obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
+This second map is $\HT$ by construction.
+Any map that factors through an $\HT$ map is also $\HT$, so the proof is finished.
+\end{proof}
 
-\begin{prop}
-	Let $(X, f)$ be a sublevel set filtration.
-If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d.
-in every degree, in particular q-tame.
-\end{prop}
+% As for a single space, the $\LC$ notions imply the corresponding $\piLC$ notions and the corresponding $\HLC$ notions if $\H$ evaluated at a point is trivial.
 
-Having each sublevel set being $\HLC$ is in many cases too restrictive.
-We would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
-The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.
+As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies q-tameness, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.
 
-\begin{defi} \label{defi:local_connectedness_filtrations}
-	For a fix homology theory $\H$.
-A sublevel set filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
-	\begin{equation*}
-	X_{\leq f(x) + \delta + c} \cap U \to X_{\leq f(x) + \epsilon + c} \cap V
-	\end{equation*}
-	is $\HT$ for every $c \geq 0$.
-	We also consider a weaker version, referred to as \textit{weakly} $\HLC$, defined as above with $c = 0$.
-\end{defi}
-
-We will now show that the weak notion does not imply q-tameness in general.
-To do so let us consider the \textit{$d$-dimensional Hawaiian earring}
-\begin{equation*}
-\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
-\end{equation*}
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale=88]
-	\draw[thick] (-.1,0) rectangle (.1,.05);
-	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
-	\foreach \i in {1,...,100}{
-		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
-	}
-	\end{tikzpicture}
-	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
-	\label{fig:earrings}
-\end{figure}
-
-\begin{thm} \label{thm:counterexample}
-	Let $\H$ be a (generalized) homology theory such that its value on a point is finitely generated for every degree and on $\HE$ is not finitely generated for some degree.
-Then, the function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\HLC$ Morse filtration that is not q-tame.
+\begin{thm} \label{t:strong local connectedness implies q-tameness}
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and strongly $\HLC$, then it is also q-tame.
 \end{thm}
 
-\begin{proof}
-	The space $\HE$ is Hausdorff and locally compact since $R^{d+1}$ is.
-	To verify that $(\HE,f)$ is a Morse filtration we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
-	Let us now verify that $\HE$ is $\HLC$.
-	Let $\epsilon > 0$ and $x \in \HE$.
-	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
-	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the desired condition follows from the first assumption on the homology theory.
-	For $x$ not the origin, there is a unique $d$-sphere that contains it.
-	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is contained in this sphere, so $D_\delta(x)$ is homotopy equivalent to a $x$ and the condition again follows trivially.
-	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame.
-	Since $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$, the second assumption on the homology theory finishes the proof.
-\end{proof}
-
-The theories that we are most interested in do satisfy these conditions.
-
-\begin{prop}
-	The assumptions of Theorem~\ref{thm:counterexample} are satisfied by singular homology with arbitrary coefficients and \v{Cech} homology with field coefficients.
-\end{prop}
-
-\begin{proof}
-	The case of singular homology is well know and can be found in \cite{Barratt.1962}.
-	For \v{C}ech homology we use the fact that it commutes with inverse limits for compact Hausdorff spaces.
-	Define 
-	\begin{align*}
-	\HE_k &= \left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{k}\right)^2+x_1^2+\dots+x_d^2 \leq \left(\frac{1}{k}\right)^2\right\}\\
-	&\cup\bigcup_{n=1}^{k-1}\left\{(x_0,\dots,x_d)\in\R^{d+1}\mid \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
-	\end{align*}
-	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-	We have $\lim_{k}\HE_{k} = \bigcap_{k}\mathbb{H}^{d}_{k}=\mathbb{H}^{d}$, and hence $\CH_{d}(\HE) = \lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})$.
-	Clearly, each $\mathbb{H}^{d}_{k}$ is a CW-complex, so we can simply use cellular homology to compute
-	\begin{equation*}
-	\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
-	\end{equation*}
-	which is infinite-dimensional over $\mathbb{F}$.
-	This finishes the proof.
-\end{proof}
-
-Now we verify that Morse filtrations which are $\HLC$ are q-tame.
-We will need three lemmas.
+The general proof strategy is inspired by the proof of a result attributed to Wilder as presented by Bredon \cite[Section II.17]{Bredon.1997}.
+We collect the main ideas in three lemmas.
 
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Fix a homology theory. Let $(X,f)$ be a $\HLC$ Morse filtration.
-	Consider sets $K, L \subseteq X$ with $K$ compact and $K \subseteq \interior(L)$. For any $s < t$ there is $\delta \in (0,\, t-s)$ such that $K \cap X_{s+\delta} \to L \cap X_{t}$ is $\HS$.
+    With the assumptions of \cref{t:strong local connectedness implies q-tameness},
+	consider sets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	For any $s < t$ the inclusion
+	\[
+	C \cap f_{\leq s} \to L \cap f_{\leq t}
+	\]
+	is $\HS$.
 \end{lem}
@@
 \begin{proof}
-	We need to prove that the inclusion $X_s \to X_t$ is $\HS$ for every $s < t$.
+    The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
+    We will proceed by induction on $n \geq n_0$ assuming the statement for $\HS_{n-1}$.
 
-	The lemma holds for $\HS$ replaced by $\HS_{(n-1)}$ for any $n \leq 0$ since $\H_{n-1}$ induces the zero map. We will proceed by induction on $n$ assuming the lemma for $\HS_{(n-1)}$.
+    We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with 
+	$\overline{V} \subseteq U \subseteq L$
+	for which there exists $s' \in (s,\, t)$ such that the inclusion
+    $U \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	is $\HS_n$.
 
-	Given a compact set $L \subseteq X$ and $s < t$ let $\Sigma_{s, t}$ be the collection of all compact subsets $K$ of $\interior(L)$ for which there exists $\delta_K > 0$ and an open neighborhood $U(K)$ of $K$ such that $U(K) \cap X_{s+\delta_K} \to L \cap X_{t}$ is $\HS_n$.
+	We will show that $\Sigma_{s, t}$ has following three properties:
+	\begin{enumerate}
+	    \item Any point $x \in L \cap f_{\leq s}$ has a neighborhood $V_x \in \Sigma_{s,t}$.
+	    \item If $V_1,\, V_2 \in \Sigma_{s,t}$, then $V_1 \cup V_2 \in \Sigma_{s,t}$.
+	    \item For each $V \in \Sigma_{s,t}$ the inclusion 
+	    $V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
+	    is $\HS_n$.
+	\end{enumerate}
 
-	We start by showing that any element of $\interior(L) \cap X_s$ has a neighborhood in $\Sigma_{s, t}$.
-	Let $x \in \interior(L) \cap X_{s}$.
-	Consider an open neighborhood $U(x)$ of $x$ contained in $\interior(L)$, and take $\epsilon > 0$ such that $s + \epsilon < t$.
-	By the strong $\HLC$ of $(X,f)$ there is a $\delta \in (0, \epsilon)$ and an open neighborhood $W(x) \subseteq U(x)$ such that for $c = s - f(x)$ the following composition is $\HS$:
-	\begin{equation*}
-	W(x) \cap X_{f(x) + c + \delta} \to
-	U(x) \cap X_{f(x) + c + e} \to
-	L \cap X_{t}.
-	\end{equation*}
-	By local connectivity we can choose a compact neighborhood of $x$ contained in $W(x)$.
-	This proves the claim.
+	The first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$. 
+	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$. 
+	By the second property, we have $V = \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}$.
+	Using the third property, the inclusion 
+	$V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
+	is $\HS_n$, so the inclusion 
+	$C \cap f_{\leq s} \to L \cap f_{\leq t}$ 
+	is also $\HS_n$ because this map factors through the aforementioned one.
 
-	We will now show that the class $\Sigma_{s,t}$ is closed under finite unions.
-	For $i \in \{1, 2\}$ let $K_i$ be in $\Sigma_{s,t}$ with $\delta_i > 0$ and $K_i \subseteq U_i$ open such that $U_{i} \cap X_{s+\delta_i} \to L \cap X_{t}$ is $\HS_n$.
-	We use Lemma \ref{l:neighborhood third} to construct sets $K_i^\prime$ such that
-	\begin{equation*}
-	K_i \subseteq \interior(K_i^\prime) \subseteq K_i^\prime \subseteq U_i.
-	\end{equation*}
-	Notice that for $\delta = \min(\delta_i)$ we have $K_i^\prime \cap X_{s+\delta} \to L \cap X_t$ is $\HS_n$.
-	Additionally, the induction hypothesis implies that $K_1 \cap K_2 \cap X_s \to K_1^\prime \cap K_2^\prime \cap X_{s+\delta}$ is $\HS_{(n-1)}$.
-	We therefore have the following commutative diagram satisfying the assumptions of Lemma~\ref{l:commutative algebra}:\todo{check assumptions for mayer-vietoris to apply}
-	\begin{equation*}
-	\begin{tikzcd}
-	\H_n(L \cap X_t) \oplus \H_n(L \cap X_t) \arrow[r] &
-	\H_n(L \cap X_t) & \\
-	\H_{n}(K_1^\prime \cap X_{s+\delta}) \oplus \H_n(K_2^\prime \cap X_{s+\delta}) \arrow[r] \arrow[u] & 
-	\H_{n}((K_1^\prime \cap X_{s+\delta}) \cup (K_2^\prime \cap X_{s+\delta})) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1^\prime \cap K_2^\prime \cap X_{s+\delta}) \\ & 
-	\H_{n}((K_1 \cup K_2) \cap X_s) \arrow[r] \arrow[u] &
-	\H_{n-1}(K_1 \cap K_2 \cap X_s). \arrow[u]
+	What is left to do is to show that $\Sigma_{s,t}$ has the properties we want.
+
+	For the third property, let $V \in \Sigma_{s,t}$ with $U$ an open neighborhood of $\overline{V}$ in $L$ and $s' \in (s,\, t)$ such that 
+	$U \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	is $\HS_n$. 
+	The inclusion
+	$V \cap f_{\leq s} \to L \cap f_{\leq t}$
+	factors through the previous one %because we have 
+	%$V \cap f_{\leq s} \subseteq U \cap f_{\leq s'}$, 
+	so it is $\HS_n$ as well. Thus, $\Sigma_{s, t}$ has the third property we want.
+
+	Next, we will show using the strong $\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	Choose an arbitrary $s' \in (s,\, t)$.
+	Since the sublevel set filtration of $f$ is strongly $\HLC$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
+	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	is $\HT$, so in particular $\HS_n$.
+	By local compactness of $X$ we can choose a compact neighborhood $K_x$ of $x$ contained in $U_x$. 
+	Now $V_x = \interior (K_x)$ is a neighborhood of $x$ with $V_x \in \Sigma_{s,t}$.
+
+	Finally, we will show using Mayer-Vietoris and the induction hypothesis that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions. 
+	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that 
+	$\overline{V_i} \subseteq U_i \subseteq L$ 
+	and
+	$U_{i} \cap f_{\leq s'_i} \to L \cap f_{\leq t}$
+	is $\HS_n$.
+	Writing $K_i = \overline{V_i}$, we use \cref{l:neighborhood third} to construct compact sets $K'_i$ such that
+	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq U_i \subseteq L\]
+	where $V'_i = \interior(K'_i)$.
+	We have that the union $V_1 \cup V_2 \subseteq L$ is open, its closure $\overline{V_1 \cup V_2}$ is compact, and we have $\overline{V_1 \cup V_2} \subseteq V'_1 \cup V'_2 \subseteq L$. 
+	Thus, we obtain $V_1 \cup V_2 \in \Sigma_{s,t}$ if we can show that there is an $s' \in (s,\, t)$ such that the inclusion 
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	is $\HS_n$. 
+	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$. 
+	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer-Vietoris property.
+
+	In the open case, notice that for both choices of $i$ the inclusions
+	$U_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
+	are $\HS_n$.
+	Additionally, the inclusion
+	$V'_1 \cap V'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$
+	is $\HS_{n-1}$ because it factors through the inclusion
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$,
+	which is $\HS_{n-1}$ by the induction hypothesis.
+    Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\[
+	\begin{tikzcd}[column sep=small]
+	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
+	\H_n(L \cap f_{\leq t}) & \\
+	\H_{n}(U_1 \cap f_{\leq s''}) \oplus \H_n(U_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
+	\H_{n}((U_1 \cup U_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
+	\H_{n-1}(U_1 \cap U_2 \cap f_{\leq s''}) \\ & 
+	\H_{n}((V'_1 \cup V'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
+	\H_{n-1}(V'_1 \cap V'_2 \cap f_{\leq s'}). \arrow[u]
 	\end{tikzcd}
-	\end{equation*}
-	We conclude that $K_1 \cup K_2 \in \Sigma_{s, t}$.
-	Since any compact $K \subseteq \interior(L)$ can be covered by a finite union of sets in $\Sigma_{s,t}$ the induction step and the lemma are proven.
+	\]
+	We conclude that the inclusion 
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
+	is $\HS_n$, which finishes this part of the proof.
+
+	In the compact case, we apply \cref{l:neighborhood third} again to obtain compact sets $K''_i$ such that
+	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq V''_i \subseteq K''_i \subseteq U_i \subseteq L\]
+	where $V''_i = \interior(K''_i)$. The rest of the proof is then analogous to the previous case:
+	We have that for both choices of $i$ the inclusions
+	$K''_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
+	are $\HS_n$ because this is true for the corresponding inclusions with $K''_i$ replaced by $U_i$.
+	Moreover, the inclusion
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \to K''_1 \cap K''_2 \cap f_{\leq s''}$
+	is $\HS_{n-1}$ because it factors through the inclusion
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \to V''_1 \cap V''_2 \cap f_{\leq s''}$,
+	which is $\HS_{n-1}$ by the induction hypothesis.
+	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\[
+	\begin{tikzcd}[column sep=small]
+	\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
+	\H_n(L \cap f_{\leq t}) & \\
+	\H_{n}(K''_1 \cap f_{\leq s''}) \oplus \H_n(K''_2 \cap f_{\leq s''}) \arrow[r] \arrow[u] & 
+	\H_{n}((K''_1 \cup K''_2) \cap f_{\leq s''}) \arrow[r] \arrow[u] &
+	\H_{n-1}(K''_1 \cap K''_2 \cap f_{\leq s''}) \\ & 
+	\H_{n}((K'_1 \cup K'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
+	\H_{n-1}(K'_1 \cap K'_2 \cap f_{\leq s'}). \arrow[u]
+	\end{tikzcd}
+	\]
+	We conclude that the inclusion 
+	$\left(K'_1 \cup K'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	is $\HS_n$, so the same is true for the inclusion
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
+	because it factors through the previous one. This finishes the proof of the lemma.
 \end{proof}
 
-\begin{thm} \label{t:strong local connectenss implies q-tameness}
-	Morse filtrations which are $\HLC$ are q-tame for any homology theory.
-\end{thm}
+We can now complete the proof of the claim stating that for compact sublevel set filtrations, strong $\HLC$ implies q-tameness.
 
-\begin{proof}
-	It follows from applying Lemma~\ref{l:key lemma for q-tameness} to $K = X_{\leq s}$ and $L = X$.
+\begin{proof}[Proof of \cref{t:strong local connectedness implies q-tameness}]
+	This follows from applying \cref{l:key lemma for q-tameness} with $C = f_{\leq s}$ and $L = X$.
 \end{proof}
+
+Combining \cref{thm:hlc_to_strong_hlc} with \cref{t:strong local connectedness implies q-tameness} also yields the following result for continuous functions.
+
+\begin{cor}
+    If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and $\HLC$, then it is also q-tame.
+\end{cor}

### 2021-06-15 inequalities.tex
version with stability

@@
-\section{Morse Inequalities} \label{s:inequalities}
+\section{Generalized Morse inequalities from persistence diagrams} \label{s:inequalities}
 
-We now present a description of Morse inequalities from the viewpoint of persistence theory which, when applied in the context of Functional Topology, agrees with Morse's original definitions.
+In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse--Tompkins to prove their Unstable Minimal Surface Theorem, see \cref{s:surfaces} for more details on this result.
+We deduce this general version from the existence of persistence diagrams, \cref{thm:q-tame modules have barcodes}.
 
-Let $M$ be a graded q-tame persistence module, and let $\mathfrak{m}_d$ be the multiplicity function of the barcode of the $d$-dimensional part of $M$, having values in the extended natural numbers.
+Fix a $\Z$-graded q-tame persistence module $M$.
+For simplicity, the reader may think of $M$ as the persistent homology of a q-tame filtration.
+By \cref{thm:q-tame modules have barcodes} $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
 
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$, Morse defined the $(d, t, e)$-\textit{cap numbers}, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
-Explicitly,
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
+
+In analogy, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \[
 m_{d}^{> e}(t) =
-    \sum_{\substack{p \in \R \\ t-p>e}} \mathfrak{m}_{d-1}(p, t) +
-    \sum_{\substack{q \in \R \\ q-t>e}} \mathfrak{m}_d(t, q).
+\sum_{\substack{p \in \R \\ t - p > e}} \mathfrak{m}_{d-1}(p, t) +
+\sum_{\substack{q \in \R \\ q - t > e}} \mathfrak{m}_d(t, q).
+\]
+Note that finiteness of these quantities is ensured by the q-tameness of $M$.
+% which are well-defined natural numbers because of the q-tameness of $M$.
+
+Whenever the sums below are well-defined, we also consider the \emph{$(d,e)$-cap numbers} 
+\[
+m_{d}^{> e } 
+= \sum_{t} m_{d}^{> e}(t) 
+=
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
++
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q).
+\] 
+They are well-defined for example if $M$ is the persistent homology of the sublevel set filtration of a bounded function. This can be deduced from the following general result.
+
+\begin{thm}
+    Assume that $N$ is a q-tame persistence module that is initially and eventually constant, i.e., that there exist $t_0$ and $t_1$ with $N_s = N_{t_0}$ for all $s \leq t_0$ and $N_u = N_{t_1}$ for all $u \geq t_1$, and let $\mathfrak{n}$ be the multiplicity function of the persistence diagram of $N$.
+Then for each $e>0$ we have
+    \[
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q) < \infty.
+    \]
+\end{thm}
+
+\begin{proof}
+    We split the sum whose finiteness we want to show in two parts
+    \[
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q)
+    =
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
+    +
+    \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
+    \]
+    and show for each summand separately that it is finite. 
+    Here, $T$ denotes the triangle
+    \[
+    T = \{(p,q) \in \multiplicityDomain \mid t_0 \leq p < q \leq t_1\}.
     \]
 
-If $m_{d}^{> e}(t)$ is non-zero for only finitely many $t$, we obtain the $(d,e)$-cap numbers 
+    For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\mathfrak{n}(p,q) = 0$ whenever one of $-\infty < p < t_0$, $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
+    This implies 
     \[
-m_{d}^{> e } = \sum_{t} m_{d}^{> e}(t) = \sum_{\substack{(p,q)\\q-p>e\\q\neq\infty}}\mathfrak{m}_{d-1}(p,q)+\sum_{\substack{(p,q)\\q-p>e\\p\neq-\infty}}\mathfrak{m}_d(p,q).
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
+    =
+    \sum_{t_0 < q < t_1} \mathfrak{n} (-\infty,q)
+    +
+    \sum_{t_0 < p < t_1} \mathfrak{n} (p, \infty)
     \]
-One can show that this finiteness assumption is satisfied if $M$ is initially and eventually constant, i.e., if there exist $t_0$ and $t_1$ with $M_s = M_{t_0}$ for all $s \leq t_0$ and $M_u = M_{t_1}$ for all $u \geq t_1$.
-In particular, this is the case for the persistent homology of the sublevel set filtration of a bounded function.
+    which is clearly finite because $N$ is q-tame.
 
-If $X$ is a closed manifold and $F$ is a Morse function, then the cap numbers $m_{d}^{> e}(F)$ associated to the persistent homology of the sublevel set filtration of $F$ agree with the number of critical points of $F$ with index $d$ for all sufficiently small $e > 0$.
-As an analogue to the Betti numbers of $X$ appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$, which, under the same assumptions as before, can be expressed in the language of persistence as
+    For the second summand, note that  
     \[
-p_{d} = \sum_{p} \mathfrak{m}_d(p,\infty).
+    \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
+    \leq
+    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q),
     \]
+    where $T^{\geq e}$ is the smaller triangle 
+    \[
+    T^{\geq e} = \{(p,q) \in T \mid q-p \geq e\}.
+    \]
+    Thus, in order to prove the theorem, it suffices to show that we have 
+    \[
+    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
+    < 
+    \infty.
+    \]
+    To do this, we consider open quadrants 
+    \[
+    Q(x, y) = \{ (p, q) \in \R^2 \mid p < x \text{ and } y < q \}.
+    \]
+    Covering the compact set $T^{\geq e}$ by the open quadrants $Q \left(x, x + \frac{e}{2} \right)$ for $x \in \R$, we may choose a finite subcover given by, say, $x_1,\dots, x_n$. We obtain
+    \[
+    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
+    \ \leq \
+    \sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{e}{2})}} \mathfrak{n}(p,q). 
+    \]
+    Each of sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{e}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{e}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from), see \cite[Section 3.8]{Chazal.2016a}.
+This finishes the proof.
+\end{proof}
 
-Provided that $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, an easy calculation shows that in this language we have Morse inequalities for any graded q-tame persistence module given by
-\begin{equation*}
-    \sum_{i=1}^d (-1)^i (m^{>e}_{d-i} - p_{d-i}) \ \geq\  0
-\end{equation*}
-for any dimension $d$.
-As a special case, this yields Morse inequalities for any bounded real-valued function $F$ whose sublevel set filtration has q-tame and upper semi-continuous persistent homology.
-As we have discussed previously, these algebraic conditions are satisfied in the setting of Functional Topology, where \v{C}ech homology is used and the sublevel set filtration is assumed to be compact and $\HLC$.
+%If $X$ is a closed manifold and $F$ is a Morse function, then the cap numbers $m_{d}^{> e}(F)$ associated to the persistent homology of the sublevel set filtration of $F$ agree with the number of critical points of $F$ with index $d$ for all sufficiently small $e > 0$.
+
+Comparing to the usual Morse inequalities, the cap numbers in dimension $d$ act like the number of critical points with index $d$.
+As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$, which, under the same assumptions as before, can be expressed in the language of persistence as
+\[
+p_{d} \ = \!\! \sum_{p \in \R \cup \{-\infty\}} \mathfrak{m}_d(p,\infty),
+\]
+which is also the dimension of the colimit of the degree $d$ part of $M$.
+%Because $M$ is 0-interleaved with $\bigoplus_(p,q) \bigoplus_{\mathfrak{m}(p,q)} C((p,q))$ and colimits commute with direct sums and are invariant up to finite interleaving distance.
+
+\begin{thm}
+    Let $M$ be a graded q-tame persistence module with $m_{d}^{> e }$ and $p_{d}$ finite for all $d$ and $e$.
+If $\mathfrak{m}_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
+    \begin{equation} \label{e:morse inequalities}
+        \sum_{d=0}^n \ (-1)^{n-d} (m^{>e}_{d} - p_{d}) \ \geq\  0
+    \end{equation}
+    for any dimension $d$ and any $e > 0$.
+\end{thm}
+
+\begin{proof}
+    Using a simple argument carried out for example in \cite[Section 11]{Morse.1940}, the claimed inequalities are equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
+
+    Since we assume $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, we have
+    \begin{align*}
+    m^{>e}_{d}
+    \ &=
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
+    \ +
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    \\
+    &=
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    \ +
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    \end{align*}
+    and
+    \[
+    p_{d}
+    \ = \!\!
+    \sum_{p \in \R \cup \{-\infty\}} \mathfrak{m}_d(p,\infty)
+    \ = \
+    \sum_{p \in \R} \mathfrak{m}_d(p,\infty),
+    \]
+    which yields
+    \begin{align*}
+    m^{>e}_{d} - p_{d}
+    &= 
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    +
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    -
+    \sum_{p \in \R} \mathfrak{m}_d(p,\infty)
+    \\
+    &=
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    +
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q),
+    \end{align*}
+    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q)$ satisfies $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$. This finishes the proof.
+\end{proof}
+As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology.
+This includes classical Morse functions on closed manifolds, for which the inequalities in our theorem agree with the classical Morse inequalities if $e > 0$ is chosen sufficiently small.
+
+Our inequalities, as presented in \eqref{e:morse inequalities}, also agree with Morse's historical version from functional topology if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if we use \v{C}ech homology.
 

### 2021-06-15 introduction.tex
version with stability

@@
 He named this body of work functional topology and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their Unstable Minimal Surface Theorem which gives conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
+In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their Unstable Minimal Surface Theorem giving conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
 
-While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have been rediscovered in the study of persistent homology.
-A method originated in applied topology and based on the functoriality of the homology construction, that provides robust and effectively computable invariants of filtered spaces.
-The successes of this technique have motivated the development of an abstract and rich theory of persistence, lying in the intersection of representation theory, geometry, and topology, and whose influence extends beyond it original domain.
-
-One of the primary reasons for the use of persistence theory in geometry is the fact that its basic invariants, known as barcodes, can be organized into a metric space, and that passing from filtrations to barcodes is $1$-Lipschitz.
+While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have flourished in other domains.
+% Many of his ideas, specially when applied to the finite dimensional case, have been rediscovered in the study of persistent homology.
+% , a method originated in applied topology and based on applying a homology functor to a filtered space,
+We now review one such area.
+The technique known as persistence homology provides robust and effectively computable invariants of filtered spaces through the application of a homology functor.
+Its successes in applied topology have motivated the development of a refined abstract theory of persistence, lying in the intersection of representation theory, geometry, and topology.
+The influence of this theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that
+% has been growing and the and whose influence extends beyond finite dimensional settings.
+% One of the primary reasons being that
+its basic invariants, known as barcodes, can be organized into a metric space, and that, when they exists, the passage from filtrations to barcodes is Lipschitz.
 This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
 
-For the existence of barcodes some form of finite-dimensionality must be assumed of the  filtered space being considered.
-The most general condition associated to this problem is known as quadrant-tameness or q-tameness for short \cite{bibid}.
-It simply states that the inclusion of distinct sublevel sets induces in homology with field coefficients a linear map with finite dimensional rank.
+In this work we focus on the existence of barcode decompositions for a broad class of filtered spaces arising from the sublevel sets of real valued functions.
+One important consequence we present is the existence of Morse inequalities when such decompositions are available.
 
-Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations.
-These allowed him to state and prove a version his famous inequalities for general filtered spaces using homotopical critical points.
-These inequalities are crucial for applications and we reinterpret them in the modern language of barcodes in \cref{s:inequalities}.
+For general persistence modules, a well studied condition for the existence of a barcode decomposition is q-tameness \cite{Chazal.2016a,Chazal.2016b}.
+It simply states that all non-identity linear maps in the persistence module have finite dimensional rank.
+In order to obtain the q-tameness of the persistence module associated to a sublevel set filtration, we study different notions of local-connectivity.
+Showing their sufficiency and limitations in different context.
 
-Since general applications may take us away from spaces with the homotopy type of CW-complexes, the choice of homology construction is an important element of the discussion.
-Two types of properties of these constructions are important for the existence of barcodes.
-On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietories exact sequences.
-On the other, those ensuring that q-tame persistence modules admit a multiplicative interval decomposition, which was shown in \cite{schmahl2020structure} to follow from the preservation of certain categorical limits.
+Having conditions for general sublevel set filtration that ensure the existence of barcodes and Morse inequalities is important to extend the influence of persistence methods into infinite dimensional geometrical settings, like the one originally considered by Morse and Topmkins.
+As a consequence of our analysis we identify and fill a gap in the proof the Unstable Minimal Surface Theorem.
 
-Our analysis allows us to show the insufficiency of the local-connectivity assumption used by Morse and Tompkins to state that the filtration defined by Douglas's functional is q-tame.
-This is because it falls into the class ruled out by \cref{thm:counterexample}.
-The existence of Morse inequalities requires q-tameness and, hence, so does the Unstable Minimal Surface Theorem of Morse and Tompkins.
-Nonetheless, this filtration satisfies a stronger condition which \cref{t:strong local connectedness implies q-tameness} ensures to be sufficient
+% Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations.
+% These allowed him to state and prove a version his famous inequalities for general filtered spaces using homotopical critical points.
+% These inequalities are crucial for applications and we reinterpret them in the modern language of barcodes in \cref{s:inequalities}.
 
-By reinterpreting the work of Morse in the modern context of persistence theory, and clarifying the conditions needed to prove the existence of barcodes for a broad class of sublevel set filtrations, we aim to increase the number and depth of interactions occurring between persistence theory on one side, and geometry, topology, and functional analysis on the other.
+% Since general applications may take us away from spaces with the homotopy type of CW-complexes, the choice of homology construction is an important element of the discussion.
+% Two types of properties of these constructions are important for the existence of barcodes.
+% On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietories exact sequences.
+% On the other, those ensuring that q-tame persistence modules admit a multiplicative interval decomposition, which was shown in \cite{schmahl2020structure} to follow from the preservation of certain categorical limits.
+
+% Our analysis allows us to show the insufficiency of the local-connectivity assumption used by Morse and Tompkins to state that the filtration defined by Douglas's functional is q-tame.
+% This is because it falls into the class ruled out by \cref{thm:counterexample}.
+% The existence of Morse inequalities requires q-tameness and, hence, so does the Unstable Minimal Surface Theorem of Morse and Tompkins.
+% Nonetheless, this filtration satisfies a stronger condition which \cref{t:strong local connectedness implies q-tameness} ensures to be sufficient
+
+% By reinterpreting the work of Morse in the modern context of persistence theory, and clarifying the conditions needed to prove the existence of barcodes for a broad class of sublevel set filtrations, we aim to increase the number and depth of interactions occurring between persistence theory on one side, and geometry, topology, and functional analysis on the other.
 

### 2021-06-15 main.tex
version with stability

@@
 \usepackage[capitalize, noabbrev]{cleveref}
+\usepackage{todo}
 
@@
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\F}{\mathbb{F}}
 \newcommand{\R}{\mathbb{R}}
@@
 \DeclareMathOperator{\im}{im}
+\DeclareMathOperator{\coker}{coker}
+\DeclareMathOperator{\rad}{rad}
 \newcommand\CH{\check{H}}
@@
 \newcommand\MVH{MVH}
+\newcommand{\obs}{\dashrightarrow}
+\newcommand{\multiplicityDomain}{\mathcal{E}}
+\newcommand{\Top}{\mathsf{Top}}
+\newcommand{\Vect}{\mathsf{Vect}}
+\newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}
 
@@
 \setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-2.5in}
+\addtolength{\textwidth}{-2.3in}
 \setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-2.5in}
+\addtolength{\textheight}{-2.3in}
 \calclayout
@@
 
-\title[Persistence in functional topology]{Persistence in functional topology: local-connectivity, q-tameness and a correction to a theorem of Morse}
+\title[Persistence in functional analysis]{Persistence in functional analysis and a correction to a theorem of Morse}
 
@@
 	Many of the key insights of functional topology have been rediscovered in the study of persistent homology, with the notion of q-tameness being as central to functional topology as it is to persistence theory.
-	With applications to geometry in mind, in this article we present a modern treatment of the relationship between local-connectivity properties of sublevel set filtrations, Morse inequalities, and the q-tameness of their associated persistence modules.
-	As a consequence of our analysis we identify a gap in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins and provide a correction.
+	With applications to geometry in mind, we present a modern treatment of local-connectivity of sublevel set filtrations, q-tameness of their associated persistence homology, and Morse inequalities.
+	As a consequence of our analysis we identify and correct a gap in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
 \end{abstract}
@@
 \input{introduction}
-\input{homology}
 \input{persistence}

### 2021-06-15 persistence.tex
version with stability

--- 2021-04-15 persistence.tex
@@
-\section{Sublevel filtrations and persistence theory} \label{s:persistence}
+\section{Filtered spaces and persistence theory} \label{s:persistence}
 
-\todo{start with the standard vector space setting, before generalizing?}
-Let $R$ be a ring.
-The category of \emph{persistence $R$-modules} is the functor category  $(\Mod{R})^{\mathbf{R}}$, where $\mathbf{R}$ is the category corresponding to the real numbers $\mathbb{R}$ considered as a poset.
-We will simply say \emph{persistence module} if the coefficient ring is clear from the context.
+In this section we present the theory of persistence as is used in connection with geometric questions.
+A bridge build through filtrations by sublevel sets of real-valued functions.
+For a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
+An example of interest to us is given by volume functionals on moduli spaces of Riemannian manifolds.
+For more examples please consult \cite{polterovich2020topological}.
 
-A persistence module $M$ is called \emph{pointwise finitely generated (p.f.g.)} if $M_{t}$ is a finitely generated module for every $t\in\mathbb{R}$.
-$M$ is called \emph{q-tame} if $\im (M_{s}\to M_{t})$ is finitely generated for all $s<t\in\mathbb{R}$.
+The so called \textit{persistence pipeline} relates geometry, algebra and discrete mathematics as follows:
+Given a space $X$ filtered by a function $f$, the application of the $n^{\mathrm{th}}$ degree part of a homology theory or, more generally, a functor from topological to vector spaces, produces a \textit{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \textit{persistence diagram}.
 
-The theory of persistence modules is particularly nice if $R=\mathbb{F}$ is a field, which we will assume for the rest of this section.
-In this case, we will say that $M$ is \emph{pointwise finite-dimensional (p.f.d.)} instead of p.f.g.
+These invariants are key for applications.
+For example, in the next section we will see how they lead to a generalization of Morse inequalities.
+Much of their usefulness comes from a remarkable geometric fact known as stability, stating that the set of all persistence diagrams is a metric space and the map from functions on $X$ with the $L^\infty$ norm to it is 1-Lipschitz.
 
-What makes the field coefficient case nice is that it allows for a combinatorial description of many persistence modules in terms of basic summands.
-Concretely, we say that $M$ has a \emph{barcode} if there is a family of intervals $(I_{\alpha})_{\alpha}$, $I_{\alpha}\subseteq\mathbb{R}$ such that
-\[
-M\cong\bigoplus_{\alpha} C(I_{\alpha}),
-\]
-where the persistence module $C(I)$ for an interval $I$ is defined via
-\[
-C(I)_t=
+Let us now explain in detail all the terms used above.
+Consider a space $X$ and a function $f \colon X \to \R$.
+Unless otherwise noted, the functions we consider need not be continuous.
+We pass to filtered spaces by considering the \textit{sublevel set filtration $f_{\leq \bullet}$ of $X$ induced by $f$}, which is defined by
+\begin{equation*}
+f_{\leq t} = f^{-1}(-\infty, t].
+\end{equation*}
+We say this filtration is \textit{compact} if $X$ is a locally compact Hausdorff space and all sublevel sets are compact.
+
+For the next step in the persistence pipeline, we will need a coherent assignment of a vector space to any topological space.
+More precisely, a functor from $\Top$ to $\Vect$, with key examples coming from \emph{homology theories}, which for now are simply assumed to be $\Z$-graded families $\H = (\H_d)_{d \in Z}$ of \emph{homotopy invariant functors}, which are functors assigning the same morphism to homotopic maps.
+Particularly important for us are \v{C}ech homology \cite[Section IX-X]{MR0050886} with field coefficients, and vector-space-valued homology theories in the sense of Eilenberg-Steenrod \cite[Section I]{MR0050886}, such as singular homology with field coefficients \cite{Eilenberg.1944}.
+
+By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$, yields for every $t \in \R$ a vector space $M_t$ and for any pair $s, t \in \R$ with $s \leq t$ a linear map $M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity, and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
+
+In other words, we obtain a functor from the real numbers considered as a category via its linear order structure to the category of vector spaces.
+Such functors will be called \emph{persistence modules}.
+A morphism of persistence modules $\varphi \colon M \to N$ is a natural transformations, i.e., an assignment of a linear map $\varphi_t \colon M_t \to N_t$ for every $t \in \R$ making the diagram
+\begin{equation*}
+    \begin{tikzcd}
+    M_{s} \arrow[r, "M_{s,t}"] \arrow[d] & M_{t} \arrow[d] \\
+    N_{s} \arrow[r, "N_{s,t}"] & N_{t}
+    \end{tikzcd}
+\end{equation*}
+commute for all pairs $s \leq t$.
+
+Usual constructions that work in the category of vector spaces can be transported to the category of persistence modules by performing them pointwise.
+For example, the kernel and cokernel of a morphism, as well as the direct sum of persistence modules are well-defined.
+Persistence modules that are \emph{indecomposable}, i.e., those that have only trivial direct sum decompositions, play an important role in persistence theory.
+A rich family of indecomposable persistence modules is given by \emph{interval modules}, which for an interval $I \subseteq \R$ are defined by
+\begin{equation} \label{e:interval module}
+    C(I)_t =
     \begin{cases}
-    \mathbb{F} & \text{if } t\in I,\\
-    0              & \text{otherwise,}
+        \mathbb{F} & \text{if } t \in I, \\
+        0          & \text{otherwise},
     \end{cases}
     \qquad
-\text{with structure maps}
     \qquad
-C(I)_{t,u}=
+    C(I)_{s, t} =
     \begin{cases}
-    \operatorname{id}_{\mathbb{F}} & \text{if } t,u\in I,\\
-    0              & \text{otherwise.}
+        \operatorname{id}_{\mathbb{F}} & \text{if } s, t \in I,\\
+        0 & \text{otherwise}.
     \end{cases}    
+\end{equation}
+These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of them.
+% \[
+% \bigoplus_{\lambda \in \Lambda} C(I_{\lambda}).
+% \]
+The multiset of intervals $\{I_{\lambda}\}_{\lambda \in \Lambda}$ associated to a barcode module is known as its \textit{barcode}.
+By a version of the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832} (see also \cite[Theorem 2.7]{Chazal.2016a} for a specialization to barcode modules), two isomorphic barcode modules have the same barcodes up to a choice of the index set $\Lambda$.
+Thus, if a persistence module $M$ is isomorphic to a barcode module, the associated barcode is a complete invariant of $M$, and the (non-unique) isomorphism to the barcode module is called a \emph{barcode decomposition}.
+
+We want to use the passage from persistence modules to invariants obtained from decompositions as the last step in our pipeline, so we have to study which persistence modules admit barcode decompositions.
+The most commonly used existence result is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, stating that every persistence module $M$ for which $M_t$ is a finite dimensional vector space for all $t \in \R$ admits a barcode decomposition.
+Such persistence modules are called \emph{pointwise finite dimensional ($\PFD$)}.
+
+Unfortunately, the $\PFD$ condition is too restrictive for our purposes.
+In particular, it is not necessarily satisfied in the historical setup of Morse's work on minimal surfaces.
+In this context, the persistence modules $M$ only have the slightly weaker property of being \emph{q-tame}, which is defined by the rank of the maps $M_{s,t} \colon M_s \to M_t$ being finite for all $s < t$.
+
+Not every q-tame persistence module admits a barcode decomposition in the above sense, as exemplified by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$, but there are multiple ways of working around this to still get discrete invariants in the spirit of barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
+We briefly recall the approach from \citet{Chazal.2016b}.
+
+A persistence module $K$ is called \emph{ephemeral} if the maps $K_{s,t} \colon K_s \to K_t$ are $0$ for all $s < t$.
+The \emph{radical} $\rad M$ of a persistence module $M$ is defined as the unique maximal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
+If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Theorem ?]{Chazal.2016b},
+with the associated barcode describing the isomorphism type of $M$ ``up-to-ephemerals".
+
+This can be formalized by constructing the \emph{observable category of persistence modules}, which is equivalent to the quotient of the category of persistence modules by the full sub-category of ephemeral persistence modules.
+Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
+The barcode of the radical of a q-tame persistence module $M$ is then a complete invariant of $M$ in the observable category.
+
+Instead of talking about the barcode of the radical of a q-tame persistence module, it will be more convenient for our treatment of Morse inequalities to talk about the \emph{(undecorated) persistence diagram} associated to a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which is the multiset defined by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
+\[
+\multiplicityDomain =
+\big\{ (p,q) \mid p \in \R \cup \{-\infty\}, \ q \in \R \cup \{+\infty\}, \ p < q \big\}
 \]
+the cardinality of the set $\{ \alpha \in A \mid \inf I_{\alpha} = p,\ \sup I_{\alpha} = q\}$.
 
-Interval modules are indecomposable in the category of persistence modules and by the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832}, two direct sums of interval modules can only be isomorphic if the corresponding families of intervals already agree.
-Hence, we can speak of \emph{the} barcode of a persistence module and use it as a complete isomorphism invariant.
+Two q-tame barcode modules are observably isomorphic if and only if their persistence diagrams agree, so the persistence diagram associated to the barcode of $\rad M$ is still a complete invariant of the q-tame persistence module $M$ in the observable category.
+We summarize:
 
-Unfortunately, not every persistence module has a barcode, so general existence results are important to have.
-The most widely used of these is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, which asserts that every p.f.d.\ persistence module has a barcode.
-
-As is well-known, Crawley-Boevey's Theorem does not extend to q-tame persistence modules.
-However, there are still ways to get a notion of barcode for q-tame persistence modules, for example by phrasing the definition of barcode in terms of so-called rectangle measures \cite{Chazal.2016a}.
-Other methods include using a slightly weaker notion of isomorphism for the direct sum decomposition into interval modules \cite{Chazal.2016b} or imposing additional algebraic constraints and allowing for the decompositions to be in terms of products instead of sums \cite{schmahl2020structure}.
-For each of these alternative methods, restricting to the p.f.d.\ setting recovers the basic notion of barcode discussed before.
-
-The usefulness of barcodes in applications often rests on their stability.
-To make precise what stability means, we define the \emph{interleaving distance} between two persistence modules $M$ and $N$ as
-\[
-d_{I}(M,N)=\inf\{\delta>0\mid\text{there exists a }\delta\text{-interleaving between }M\text{ and }N\},
-\]
-where a $\delta$-interleaving between $M$ and $N$ is given by a collection of maps $M_{t}\to N_{t+\delta}$ and $N_{t}\to M_{t+\delta}$ for each $t\in\mathbb{R}$ such that the diagrams
-\[
-\begin{tikzcd}
-M_s\arrow[r]\arrow[d] & M_t\arrow[d] \\
-N_{s+\delta}\arrow[r] & N_{t+\delta}
-\end{tikzcd}
-\qquad
-\begin{tikzcd}
-N_s\arrow[r]\arrow[d] & N_t\arrow[d] \\
-M_{s+\delta}\arrow[r] & M_{t+\delta}
-\end{tikzcd}
-\qquad
-\begin{tikzcd}
-M_{t-\delta}\arrow[rd]\arrow[r]& M_{t}\arrow[rd]\arrow[r] & M_{t+\delta} \\
-N_{t-\delta}\arrow[ru]\arrow[r]& N_{t}\arrow[ru]\arrow[r] & N_{t+\delta}
-\end{tikzcd}
-\]
-commute for all $s<t\in\mathbb{R}$.
-
-We also define the \emph{Bottleneck distance} between two barcodes $B=(I_{\alpha})_{\alpha\in A}$ and $B'=(I'_{\alpha'})_{\alpha'\in A'})$ as
-\[
-d_{b}(B,B')=\inf\{\delta>0\mid\text{there exists a }\delta\text{-matching between }M\text{ and }N\},
-\]
-where a $\delta$-matching between $B$ and $B'$ is given by subsets $X\subseteq A$, $X'\subseteq A'$ and a bijection $\sigma\colon X\to X'$ such that
-\[
-\lvert \sup I - \inf I \rvert < 2\delta
-\]
-whenever there is $\alpha\in A\setminus X$ with $I=I_{\alpha}$ or $\alpha'\in A'\setminus X'$ with $I=I'_{\alpha'}$, and
-\begin{align*}
-\lvert \sup I'_{\sigma(\alpha)} - \sup I_{\alpha} \rvert &< \delta \\
-\lvert \inf I'_{\sigma(\alpha)} - \inf I_{\alpha} \rvert &< \delta
-\end{align*}
-for all $\alpha\in X$.
-
-\begin{thm}[\cite{}]\todo{what do we want to cite here?}
-Let $M$ and $M'$ be q-tame persistence modules with barcodes $B$ and $B'$. Then
-\[
-d_{b}(B,B')= d_{I}(M,M').
-\]
+\begin{thm}[{{\citet{Chazal.2016a,Chazal.2016b}}}] \label{thm:q-tame modules have barcodes}
+Every q-tame persistence module has a unique persistence diagram that completely describes its isomorphism type in the observable category.
 \end{thm}
 
-The most commonly studied example of a persistence module is \emph{persistent homology}, i.e., the persistence module obtained by applying homology to an $\mathbb{R}$-indexed diagram of spaces.
-In what follows, we will study the persistent homology of certain classes of such diagrams, namely filtrations.
+In total, we have seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
+If this is the case, we will call the function \emph{q-tame} with respect to $\H$.
+If $\H$ is some kind of homology, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
 
-A \textit{sublevel set filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
-For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
-\begin{equation*}
-X_{\leq t} = f^{-1}((-\infty, t]).
-\end{equation*}
+As we have mentioned, the whole process is 1-Lipschitz for appropriate metrics \cite{MR3333456}.
+The metric of choice to start with on the space of $\R$-valued functions on $X$ is the $L^{\infty}$ distance.
+The metric of choice on the space of persistence diagrams is the \emph{bottleneck distance}, which measures...
 
-Recall that a subset $N$ of a space $X$ is said to be a \textit{neighborhood} of $x$ in $X$ if there is an open set $U$ with $x \in U \subseteq N$, and that a Hausdorff space is \textit{locally compact} if for every $x$ in $X$, every neighborhood of $x$ contains a compact neighborhood of $x$.
-
-A sublevel set filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
-Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.
+One strategy to prove this is to also define the so-called \emph{interleaving distance} for filtrations and persistence modules \cite{MR2279866}, which measures how much one needs to shift two such objects along the index set $\R$ to obtain an isomorphism between them, and show that each individual step in the pipeline is 1-Lipschitz.
+With this approach, by far the most difficult step is showing that passing from persistence moduels to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3348168}.

### 2021-06-15 surfaces.tex
version with stability

@@
 In \cite[p.445]{Morse.1939}, Morse and Tompkins introduce for any metric space $M$ and $F \colon M \to \R$ a homotopical version of critical point.
-Intuitively, a point $p$ is \textit{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
+Roughly, a point $p$ is \textit{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
 
@@
 
-In order to apply these inequalities and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
+They infer the Morse inequalities for homotopicaly critical points by relating these points to cap numbers and then applying Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities} and as Morse considered them in \cite{Morse.1940}.
+
+We have seen that these inequalities require q-tameness, so in order to apply them and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
 Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins use in their applications to minimal surface theory the following version equivalent to $\piLC$:
+In particular, Morse and Tompkins use in their applications to minimal surface theory the following condition:
 \begin{displaycquote}[p.431]{Morse.1940}
@@
 \end{displaycquote}
+Here, $c = F(p)$.
 They then state that as a consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
@@
 Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
-Unfortunately, this argument is not in general sound as \cref{thm:counterexample} shows.
-However, the proof given in \cite[p.464]{Morse.1939} establishes that $(\Omega_g, A_g)$ is $\LC$, implying that it is also $\HLC$ for any homology theory.
+Unfortunately, this argument is not in general sound as we will show next.
+
+\begin{defi}
+The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ 
+if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+\begin{equation*}
+f_{\leq s} \cap U \to f_{\leq t} \cap V
+\end{equation*}
+is homtopic to a constant map.
+\end{defi}
+
+Clearly, if the homology $\H$ takes trivial values on one point spaces, being $\LC$ implies being $\HLC$.
+Moreover, if the sublevel set filtration of a function $F \colon M \to \R$ on a metric space $M$ is $\LC$, then $M$ is locally $F$-connected in the sense of Morse's definition above.
+
+We will now show that neither our $\HLC$ condition nor Morse's condition above are sufficient in general to imply q-tameness for compact sublevel set filtrations induced by non-continuous functions by producing an $\LC$ filtration which is not q-tame.
+In particular, this invalidates Morse's claim we have quoted above.
+
+To do this, we consider the \textit{$d$-dimensional Hawaiian earring}
+\begin{equation*}
+\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
+\end{equation*}
+
+\begin{figure}[t]
+	\centering
+	\begin{tikzpicture}[scale = 76]
+	\draw[thick] (-.1,0) rectangle (.1,.05);
+	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
+	\foreach \i in {1,...,100}{
+		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
+	}
+	\end{tikzpicture}
+	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
+	\label{fig:earrings}
+\end{figure}
+
+\begin{thm} \label{thm:counterexample}
+	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is not finite dimensional for some $n$.
+\end{thm}
+
+\begin{proof}
+	The space $\HE$ is Hausdorff and locally compact since $\R^{d+1}$ is.
+	To verify that $f$ has compact sublevel sets we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	Let us now verify that the sublevel set filtration of $f$ is weakly $\LC$.
+	Let $\epsilon > 0$ and $x \in \HE$.
+	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
+	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the weak $\LC$ condition is trivially satisfied.
+	For $x$ not the origin, there is a unique $d$-sphere in $\HE$ that contains it.
+	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a disk contained in this sphere, so $D_\delta(x)$ can be contracted to $\{x\}$ and the weak $\LC$ condition again follows trivially.
+	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame for $\H$.
+This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$ because $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+\end{proof}
+
+Both singular and \v{C}ech homology of the Hawaiian earring are infinite dimensional in some degree, so they satisfy the assumptions of \cref{thm:counterexample}.
+The singular case is treated in \cite{Barratt.1962}, and for \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{MR0050886}:
+	Define 
+	\begin{align*}
+	\HE_k &= \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\
+	& \cup \bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right \},
+	\end{align*}
+	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+	We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \mathbb{F}) = \lim_{k} \CH_{d}(\HE_{k}; \mathbb{F})$.
+	Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
+	\begin{equation*}
+	\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+	\end{equation*}
+	which is infinite-dimensional over $\mathbb{F}$.
+
+\begin{cor}
+    The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.
+\end{cor}
+
+The gap in the argument of Morse and Tompkins that we have highlighted can be fixed by applying \cref{t:strong local connectedness implies q-tameness} because the proof given in \cite[p.464]{Morse.1939} for local connectivity of $(\Omega_g, A_g)$ actually establishes that the sublevel set filtration of $A_g$ is \emph{strongly} $\LC$, which can be defined analogously to our strong $\HLC$ property.
+This implies that the filtration is also $\HLC$ for any homology theory that takes trivial values on one point spaces, so in particular for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
 Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is q-tame as claimed.
-This implies that Morse inequalities hold, and hence so does the unstable minimal surfaces theorem of Morse.
+This implies that Morse inequalities hold, and hence so does the unstable minimal surfaces theorem of Morse--Tompkins.

### 2021-06-15 vietoris.tex
version with stability

@@
 
-In his work on functional topology, Morse uses the Vietoris homology for metric spaces as introduced in \cite{MR1512371}.
-So far, we have considered \v{C}ech homology instead, applying a topological rather than metric construction.
-We will recall the definition of Vietoris homology and recall that these two constructions yield the same result for compact metric spaces.
+Let $(X_{1},X_{2})$ be a pair of topological spaces.
+We say that $\alpha = (\alpha_1, \alpha_2)$ is an \emph{open cover} of $(X_1, X_2)$ if $\alpha_1$ is an open cover of $X_1$ and $\alpha_2 \subseteq \alpha_1$ is a subcover such that $X_1 \subseteq \bigcup_{U \in \alpha_2} U$.
+We denote by $\Cov(X_{1}, X_{2})$ the set of open covers of $(X_{1}, X_{2})$ directed by the refinement relation.
+
+If $\alpha = (\alpha_{1}, \alpha_{2})$ is a cover of $(X_{1}, X_{2})$, we write $\Nrv(\alpha)$ for the simplicial pair $(\Nrv(\alpha_{1}),\Nrv(\alpha_{2}))$, where 
+\[
+\Nrv(\alpha_{i}) =
+\big\{ \beta \subseteq \alpha_{i} \mid \beta \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}
+\]
+denotes the nerve of a cover $\alpha_{i}$.
+The nerve construction defines a functor from $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial pairs.
+
+The \emph{\v{C}ech homology with coefficients in $\mathbb{F}$} of $(X_{1},X_{2})$ is defined as
+\[
+\CH_{*}(X_{1}, X_{2}; \mathbb{F}) \ =
+\lim_{\alpha \in \Cov(X_{1}, X_{2})} H_{*}(\Nrv(\alpha); \mathbb{F}).
+\]
+
+In his work on functional topology, Morse uses Vietoris homology for metric spaces as introduced in \cite{MR1512371}.
+So far, we have considered \v{C}ech homology instead, applying a topological rather than a metric construction.
+We will review the definition of Vietoris homology and recall that these two constructions yield the same result for compact metric spaces.
 
@@
 \[
-\Vietoris (\alpha_{i}) = \left\{ \sigma \subseteq X_{i} \mid \sigma \text{ is finite and there is } U \in \alpha_{i} \text{ with } \sigma \in U \right\}.
+\Vietoris (\alpha_{i}) = \left\{ \sigma \subseteq X_{i} \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha_{i}  \right\}.
 \]
@@
 \]
-This is still not exactly the construction of Vietoris homology of a pair of metric spaces $(X_{1}, X_{2})$ as presented in \cite{MR1512371}, which in modern notation is the limit
+This is still not exactly the same as the construction of Vietoris homology of a pair of metric spaces $(X_{1}, X_{2})$ as presented in \cite{MR1512371}, which in modern notation is the limit
 \begin{equation*}
@@
 \]
-But if the metric pair $(X_{1}, X_{2})$ is compact, then $\Balls (X_{1}, X_{2})$ is coinitial in $\Cov (X_{1}, X_{2})$, that is to say, they define the same limit.
+However, if the metric pair $(X_{1}, X_{2})$ is compact, then $\Balls (X_{1}, X_{2})$ is coinitial in $\Cov (X_{1}, X_{2})$, that is to say, they define the same limit.
 Thus, we have natural isomorphisms
@@
 \]
-so in Morse's setting the metric Vietoris homology theory he uses is indeed the same as the \v{C}ech homology we considered earlier on.
+and so the metric Vietoris homology theory employed in Morse's setting is indeed canonically isomorphic to the \v{C}ech homology we considered earlier on.

### 2021-06-15 main.tex
Change doc-class to springer and modify abstract

@@
-\immediate\write18{bibtex \jobname}
-\documentclass{amsart}
+%\immediate\write18{bibtex \jobname}
+\documentclass[nospthms, a4paper, final]{svjour3}
+\setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}
+\setlength{\textheight}{\dimexpr\pdfpageheight-2in}
+\usepackage{mathptmx}
 \usepackage{amsmath, amsthm, amssymb}
@@
 
-% margins
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-2.3in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-2.3in}
-\calclayout
-
 \begin{document}
 
-\title[Persistence in functional analysis]{Persistence in functional analysis and a correction to a theorem of Morse}
+\title{Persistence in functional analysis and a correction to a theorem of Morse}
 
-% % Anibal
-% \author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-% \address{Max Planck Institute for Mathematics, Bonn, Germany}
-% \email{ammedmar@mpim-bonn.mpg.de}
-% \address{Department of Mathematics, University of Notre, Notre Dame, IN, USA}
-% \email{amedinam@nd.edu}
+\author{author1 \and author2 \and author3}
 
-\date{\today}
+\institute{author1 \at where \\ \email{@} \and
+	author2 \at where \\ \email{@} \and
+	author3 \at where \\ \email{@} \and
+}
+
+\authorrunning{author1, author2, author3}
+
+\maketitle
 
@@
 	During the 1930's Morse developed the theory of functional topology relating the critical set of a semi-continuous functional and the topology of its sublevel sets.
-	Morse and Tompkins applied this body of work in the setting defined by Douglas' solution to Plateau's Problem, and proved with it their Unstable Minimal Surface Theorem.
-	Many of the key insights of functional topology have been rediscovered in the study of persistent homology, with the notion of q-tameness being as central to functional topology as it is to persistence theory.
-	With applications to geometry in mind, we present a modern treatment of local-connectivity of sublevel set filtrations, q-tameness of their associated persistence homology, and Morse inequalities.
-	As a consequence of our analysis we identify and correct a gap in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
+	Morse and Tompkins applied this body of work to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
+	In recent years, persistence homology has led to fast passed developments in both mathematical theory and practice within several fields including simplectic geometry, WHAT ELSE?
+and neuroscience.
+In this article, we present a modern account of Morse's functional topology from the point of view of persistence theory.
+	We do so to allow for future applications of persistence techniques in functional analysis, as well as to correct a gap we identified in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
 \end{abstract}
 
-\maketitle
 \tableofcontents

### 2021-06-15 persistence.tex
Change doc-class to springer and modify abstract

@@
 In this section we present the theory of persistence as is used in connection with geometric questions.
-A bridge build through filtrations by sublevel sets of real-valued functions.
-For a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
-An example of interest to us is given by volume functionals on moduli spaces of Riemannian manifolds.
-For more examples please consult \cite{polterovich2020topological}.
+A bridge built through filtrations by sublevel sets of real-valued functions.
+A class of examples directly related to the origin of this connection is that of functionals defined on the moduli spaces of Riemannian metrics on a manifold.
+For more examples please consult \cite{polterovich2020topological} and for a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
 

### 2021-07-15 inequalities.tex
Before meeting on Friday mid July

@@
 In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse--Tompkins to prove their Unstable Minimal Surface Theorem, see \cref{s:surfaces} for more details on this result.
-We deduce this general version from the existence of persistence diagrams, \cref{thm:q-tame modules have barcodes}.
+We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{thm:q-tame modules have barcodes}.
 
-Fix a $\Z$-graded q-tame persistence module $M$.
-For simplicity, the reader may think of $M$ as the persistent homology of a q-tame filtration.
-By \cref{thm:q-tame modules have barcodes} $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
+Recall that for a Morse function $f$ on a closed manifold $X$, the usual Morse inequalities state that for any $n$ we have
+\begin{equation}\label{equ:morse_inequalities}
+    \sum_{d=0}^n \ (-1)^{n-d} ( \# \crit_{d}(f) - \beta_{d}(X) ) \ \geq\  0,  
+\end{equation}
+where $\crit_{d}(f)$ is the set of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d$th Betti number of $X$.
 
+Now if no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing the barcode of $H_*(f_{\leq \bullet})$.
+
+More precisely, an index $d$ critical point may either kill an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
+
+The Betti numbers of $X$ may also be expressed in terms of barcodes because they agree with the number of intervals that extend to $+\infty$. 
+Thus, the Morse inequalities above can be expressed entirely in terms of the barcode or persistence diagram of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
+
+This approach of counting homological changes instead of critical points is also what Morse used in his non-smooth setting of functional topology.
 To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
-In analogy, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
+Working entirely in the algebraic setting, we will now fix a $\Z$-graded q-tame persistence module $M$.
+Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
+
+By \cref{thm:q-tame modules have barcodes} $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
+In analogy to Morse's definitions, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \[
@@
 Note that finiteness of these quantities is ensured by the q-tameness of $M$. 
-% which are well-defined natural numbers because of the q-tameness of $M$.
+Moreover, note that the condition on the counted features to have persistence greater than $e$ is necessary for finiteness of the cap numbers in the q-tame setting. 
+One may omit the lower persistence bound $e$ in the definition if one restricts to $\PFD$ persistence modules.
 
@@
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q)
-    =
+    \ = \!\!
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
-    +
+    \ \ +
     \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
@@
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
-    =
+    \ = \!
     \sum_{t_0 < q < t_1} \mathfrak{n} (-\infty,q)
-    +
+    \ + \!
     \sum_{t_0 < p < t_1} \mathfrak{n} (p, \infty)
@@
     \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
-    \leq
+    \ \, \leq \!\!
     \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q),
@@
     \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
-    < 
+    \ < \ 
     \infty.
@@
     \end{equation}
-    for any dimension $d$ and any $e > 0$.
+    for any dimension $n$ and any $e > 0$.
 \end{thm}
@@
     \begin{align*}
-    m^{>e}_{d} - p_{d}
+    m^{>e}_{d} - p_{d} \
     &= 
     \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
-    +
+    \ +
     \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
-    -
+    \ - \
     \sum_{p \in \R} \mathfrak{m}_d(p,\infty)
@@
     \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
-    +
+    \ + \!
     \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q),
@@
 \end{proof}
-As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology.
-This includes classical Morse functions on closed manifolds, for which the inequalities in our theorem agree with the classical Morse inequalities if $e > 0$ is chosen sufficiently small.
+As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions on closed manifolds, as well as the functionals that Morse considered in his work on functional topology.
 
-Our inequalities, as presented in \eqref{e:morse inequalities}, also agree with Morse's historical version from functional topology if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if we use \v{C}ech homology.
+As we have outlined while motivating the definition for the cap numbers above, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} for Morse functions $f$ on closed manifolds $X$ because in this setting, we have $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
+Our inequalities also agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
+Note, however, that in contrast to Morse's version, our inequalities also work without the upper semi-continuity assumption, removing the need for this unusual choice of homology theory.
 
+\begin{rem}
+In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical and which formalizes the idea of a point being critical if it produces topological changes in the sublevel set filtration.
+This notion is employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
+The usefulness of this notion might be limited though, because for example in the context of Floer theory, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.
+In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable, because while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology, to which our inequalities may also be applied.
+\end{rem}
+
+%\anibal{Is there a theorem worth mentioning relating homotopical critical points and the algebraic Morse inequalities.}
 % \[

### 2021-07-15 main.tex
Before meeting on Friday mid July

@@
 \newcommand{\HT}{\mathrm{HT}}
-\newcommand{\HLC}{\mathrm{HLC}}
+\newcommand{\HLC}{\mathrm{LHS}}
 \newcommand{\piT}{\pi\mathrm{T}}
@@
 \newcommand{\HE}{\mathbb{H}^d}
-\renewcommand{\H}{\widetilde{H}}
+\renewcommand{\H}{H}
 \DeclareMathOperator{\interior}{int}
@@
 
-\title{Persistence in functional analysis and a correction to a theorem of Morse}
+\title{Persistence in functional topology and a correction to a theorem of Morse}
 
-\author{author1 \and author2 \and author3}
+\author{Ulrich Bauer \and Anibal M.~Medina-Mardones \and Maximilian Schmahl}
 
-\institute{author1 \at where \\ \email{@} \and
-	author2 \at where \\ \email{@} \and
-	author3 \at where \\ \email{@} \and
+\institute{
+    Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
+	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics, Bonn \\ \email{ammedmar@mpim-bonn.mpg.de} 
+	\and
+	Maximilian Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg}
 }
 
-\authorrunning{author1, author2, author3}
+\authorrunning{U.~Bauer, A.~M.~Medina-Mardones, M.~Schmahl}
 
@@
 \begin{abstract}
-	During the 1930's Morse developed the theory of functional topology relating the critical set of a semi-continuous functional and the topology of its sublevel sets.
-	Morse and Tompkins applied this body of work to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
-	In recent years, persistence homology has led to fast passed developments in both mathematical theory and practice within several fields including simplectic geometry, WHAT ELSE?
-and neuroscience.
-In this article, we present a modern account of Morse's functional topology from the point of view of persistence theory.
-	We do so to allow for future applications of persistence techniques in functional analysis, as well as to correct a gap we identified in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
+	During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
+	Morse and Tompkins applied this body of work, referred to as functional topology, to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
+	Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics with applications to a wide range of topics, including neuroscience, genomics, and symplectic geometry.
+	In this article, we provide a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
+	We adjust several key definitions and prove stronger statements in order to allow for future applications of persistence techniques in functional analysis, as well as to correct a mistake in the proof by Morse and Tompkins of the Unstable Minimal Surface Theorem.
 \end{abstract}
@@
 
-A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL where part of this work developed.
+A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL, where part of this work developed.
 

### 2021-07-15 persistence.tex
Before meeting on Friday mid July

--- 2021-06-15 persistence.tex
@@
 
-In this section we present the theory of persistence as is used in connection with geometric questions.
-A bridge build through filtrations by sublevel sets of real-valued functions.
-For a more complete treatment of persistence theory we refer to \cite{Chazal.2016a, MR3408277}.
-An example of interest to us is given by volume functionals on moduli spaces of Riemannian manifolds.
-For more examples please consult \cite{polterovich2020topological}.
+In this section we present an overview of the theory of persistence as it is used in geometric contexts, through filtrations by sublevel sets of real-valued functions.
+For a detailed exposition we refer to \cite{polterovich2020topological} and \cite{Chazal.2016a, MR3408277}.
 
-The so called \textit{persistence pipeline} relates geometry, algebra and discrete mathematics as follows:
-Given a space $X$ filtered by a function $f$, the application of the $n^{\mathrm{th}}$ degree part of a homology theory or, more generally, a functor from topological to vector spaces, produces a \textit{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \textit{persistence diagram}.
+The ``pipeline'' of topological persistence traverses through geometry, algebra and discrete mathematics as follows:
+Given a space $X$ filtered by the sublevel sets of a function $f$, the application of some homology theory in degree $n$ with coefficients in a field,  or, more generally, a functor from topological spaces to vector spaces, produces a \textit{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \textit{persistence diagram}.
 
-These invariants are key for applications.
-For example, in the next section we will see how they lead to a generalization of Morse inequalities.
-Much of their usefulness comes from a remarkable geometric fact known as stability, stating that the set of all persistence diagrams is a metric space and the map from functions on $X$ with the $L^\infty$ norm to it is 1-Lipschitz.
+These invariants are key to applications.
+For example, in the next section we will see how they lead to a generalization of the classical Morse inequalities.
+Much of their usefulness comes from a remarkable geometric fact known as stability, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric, called the \emph{bottleneck distance}.
 
-Let us now explain in detail all the terms used above.
-Consider a space $X$ and a function $f \colon X \to \R$.
-Unless otherwise noted, the functions we consider need not be continuous.
+To explain the meaning of the above terms in detail, we consider a space $X$ and a function $f \colon X \to \R$.
+Unless noted otherwise, the functions we consider need not be continuous.
 We pass to filtered spaces by considering the \textit{sublevel set filtration $f_{\leq \bullet}$ of $X$ induced by $f$}, which is defined by
@@
 \end{equation*}
-We say this filtration is \textit{compact} if $X$ is a locally compact Hausdorff space and all sublevel sets are compact.
+We say that this filtration is \textit{compact} if $X$ is a locally compact Hausdorff space and all sublevel sets are compact.
 
-For the next step in the persistence pipeline, we will need a coherent assignment of a vector space to any topological space.
-More precisely, a functor from $\Top$ to $\Vect$, with key examples coming from \emph{homology theories}, which for now are simply assumed to be $\Z$-graded families $\H = (\H_d)_{d \in Z}$ of \emph{homotopy invariant functors}, which are functors assigning the same morphism to homotopic maps.
-Particularly important for us are \v{C}ech homology \cite[Section IX-X]{MR0050886} with field coefficients, and vector-space-valued homology theories in the sense of Eilenberg-Steenrod \cite[Section I]{MR0050886}, such as singular homology with field coefficients \cite{Eilenberg.1944}.
+For the next step in the persistence pipeline, we will need a coherent assignment of a vector space to any topological space, more precisely, a functor from $\Top$ to $\Vect$.
+The key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
+Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{MR0050886} with coefficients in some fixed field $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{MR0050886}, such as singular homology, again with coefficients in some field $\F$ \cite{Eilenberg.1944}.
 
-By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$, yields for every $t \in \R$ a vector space $M_t$ and for any pair $s, t \in \R$ with $s \leq t$ a linear map $M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity, and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
-
-In other words, we obtain a functor from the real numbers considered as a category via its linear order structure to the category of vector spaces.
+By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$ yields for every $t \in \R$ a vector space~$M_t$ and for any pair~$s, t \in \R$ with~$s \leq t$ a linear map~$M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
+In other words, we obtain a functor from the real numbers, considered as a poset category, to the category of vector spaces.
 Such functors will be called \emph{persistence modules}.
-A morphism of persistence modules $\varphi \colon M \to N$ is a natural transformations, i.e., an assignment of a linear map $\varphi_t \colon M_t \to N_t$ for every $t \in \R$ making the diagram
+A morphism of persistence modules $\varphi \colon M \to N$ is a natural transformation, i.e., an assignment of a linear map $\varphi_t \colon M_t \to N_t$ for every $t \in \R$ making the diagram
 \begin{equation*}
@@
 
-Usual constructions that work in the category of vector spaces can be transported to the category of persistence modules by performing them pointwise.
+Usual constructions that work in the category of vector spaces over the field $\F$ can be transferred to the category of persistence modules by applying them pointwise.
 For example, the kernel and cokernel of a morphism, as well as the direct sum of persistence modules are well-defined.
@@
 \end{equation}
-These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of them.
+These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of interval modules.
 % \[
@@
 
-We want to use the passage from persistence modules to invariants obtained from decompositions as the last step in our pipeline, so we have to study which persistence modules admit barcode decompositions.
-The most commonly used existence result is Crawley-Boevey's Theorem \cite{Crawley-Boevey.2015}, stating that every persistence module $M$ for which $M_t$ is a finite dimensional vector space for all $t \in \R$ admits a barcode decomposition.
-Such persistence modules are called \emph{pointwise finite dimensional ($\PFD$)}.
+We want to use the passage from persistence modules to invariants obtained from decompositions as the last step in our pipeline, so we have to understand which persistence modules admit barcode decompositions.
+The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's theorem \cite{Crawley-Boevey.2015}.
+It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional ($\PFD$)} persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all $t \in \R$.
 
 Unfortunately, the $\PFD$ condition is too restrictive for our purposes.
-In particular, it is not necessarily satisfied in the historical setup of Morse's work on minimal surfaces.
-In this context, the persistence modules $M$ only have the slightly weaker property of being \emph{q-tame}, which is defined by the rank of the maps $M_{s,t} \colon M_s \to M_t$ being finite for all $s < t$.
-
-Not every q-tame persistence module admits a barcode decomposition in the above sense, as exemplified by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$, but there are multiple ways of working around this to still get discrete invariants in the spirit of barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
+In particular, it is not necessarily satisfied in the historical setup of Morse and Tompkins' work on minimal surfaces.
+In this context, the persistence modules $M$ only have the slightly weaker property of being \emph{q-tame}, which is defined by the rank of the maps $M_{s,t} \colon M_s \to M_t$ being finite for all $s < t$  \cite{Chazal.2016a}.
+Not every q-tame persistence module admits a barcode decomposition in the above sense, as exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$.
+Yet, there are multiple ways of working around this to still get discrete invariants in the spirit of barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
 We briefly recall the approach from \citet{Chazal.2016b}.
@@
 A persistence module $K$ is called \emph{ephemeral} if the maps $K_{s,t} \colon K_s \to K_t$ are $0$ for all $s < t$.
-The \emph{radical} $\rad M$ of a persistence module $M$ is defined as the unique maximal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
-If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Theorem ?]{Chazal.2016b},
-with the associated barcode describing the isomorphism type of $M$ ``up-to-ephemerals".
-
+The \emph{radical} $\rad M$ of a persistence module $M$ is defined as the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
+Specifically, $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
+If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Corollary~3.6]{Chazal.2016b},
+with the associated barcode describing the isomorphism type of~$M$ ``up to ephemerals".
 This can be formalized by constructing the \emph{observable category of persistence modules}, which is equivalent to the quotient of the category of persistence modules by the full sub-category of ephemeral persistence modules.
@@
 
-In total, we have seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
-If this is the case, we will call the function \emph{q-tame} with respect to $\H$.
-If $\H$ is some kind of homology, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
+We have thus seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
+If this is the case, we will call the function \emph{q-tame} with respect to the functor $\H$.
+If $\H$ is some kind of homology theory, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
 
-As we have mentioned, the whole process is 1-Lipschitz for appropriate metrics \cite{MR3333456}.
-The metric of choice to start with on the space of $\R$-valued functions on $X$ is the $L^{\infty}$ distance.
-The metric of choice on the space of persistence diagrams is the \emph{bottleneck distance}, which measures...
+As mentioned earlier, the passage from functions to persistence diagrams is 1-Lipschitz for appropriate metrics \cite{MR3333456}.
+The metric of choice to consider on the space of $\R$-valued functions on $X$ is the distance induced by the supremum norm.
+The metric of choice on the space of persistence diagrams is the \emph{bottleneck distance}, which expresses the distance between persistence diagrams by an optimal matching of the intervals in the corresponding barcodes: two diagrams are within distance $\delta$ if any two matched intervals are within Hausdorff distance $\delta$, and any unmatched interval has length at most $2\delta$.
 
-One strategy to prove this is to also define the so-called \emph{interleaving distance} for filtrations and persistence modules \cite{MR2279866}, which measures how much one needs to shift two such objects along the index set $\R$ to obtain an isomorphism between them, and show that each individual step in the pipeline is 1-Lipschitz.
-With this approach, by far the most difficult step is showing that passing from persistence moduels to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3348168}.
+The most general stability result is shown by considering as an intermediate step the \emph{interleaving distance} for filtrations and persistence modules \cite{MR2279866}, which measures how far two $\R$-indexed diagrams $M,N$ are from being isomorphic.
+A $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t, (N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the internal structure maps $(M_t \to M_{t+2\delta})_t, (N_t \to N_{t+2\delta})_t$.
+Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ admitting a $\delta$-interleaving is the interleaving distance between the two diagrams.
+As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance on diagrams of topological spaces), to persistent homology (with interleaving distance on persistence modules), and finally to persistence diagrams (with the bottleneck distance).
+In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456}.

### 2021-07-15 surfaces.tex
Before meeting on Friday mid July

@@
 
-They infer the Morse inequalities for homotopicaly critical points by relating these points to cap numbers and then applying Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities} and as Morse considered them in \cite{Morse.1940}.
+They infer Morse inequalities for homotopically critical points by relating these points to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities} and as Morse considered them in \cite{Morse.1940}.
 
@@
 Here, $c = F(p)$.
-They then state that as a consequence of these assumptions the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
+Using similar language to the one used in \cref{s:connectivity}, this property is equivalent to the following notion applicable to general topological spaces.
+
+\begin{defi}
+    The sublevel set filtration of a function $F \colon M \to \R$ is said to be $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+	\begin{equation*}
+	f_{\leq s} \cap U \to f_{\leq t} \cap V
+	\end{equation*}
+	induces the zero map on homotopy groups.
+\end{defi}
+
+It is then stated that as a consequence of local $F$-connectivity the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
 In the original it reads:
+
 \begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
@@
 \begin{defi}
-The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ 
-if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+    The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
     \begin{equation*}
@@
     \end{equation*}
-is homtopic to a constant map.
+    is homotopic to a constant map.
 \end{defi}
 
-Clearly, if the homology $\H$ takes trivial values on one point spaces, being $\LC$ implies being $\HLC$.
-Moreover, if the sublevel set filtration of a function $F \colon M \to \R$ on a metric space $M$ is $\LC$, then $M$ is locally $F$-connected in the sense of Morse's definition above.
+Clearly, being $\LC$ implies being $\piLC$ and, if the homology $\H$ takes finite dimensional values on one point spaces, also $\HLC$.
+% Moreover, if the sublevel set filtration of a function $F \colon M \to \R$ on a metric space $M$ is $\LC$, then $M$ is locally $F$-connected in the sense of Morse's definition above.
+We will now show that not even $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations.
+% neither our $\HLC$ condition nor Morse's condition above are sufficient in general to imply q-tameness for compact sublevel set filtrations induced by non-continuous functions by producing an $\LC$ filtration which is not q-tame.
+In particular, our construction will be used to invalidate Morse's claim quoted above.
 
-We will now show that neither our $\HLC$ condition nor Morse's condition above are sufficient in general to imply q-tameness for compact sublevel set filtrations induced by non-continuous functions by producing an $\LC$ filtration which is not q-tame.
-In particular, this invalidates Morse's claim we have quoted above.
-
-To do this, we consider the \textit{$d$-dimensional Hawaiian earring}
+Consider the \textit{$d$-dimensional Hawaiian earring}
 \begin{equation*}
@@
 	\begin{tikzpicture}[scale = 76]
-	\draw[thick] (-.1,0) rectangle (.1,.05);
+	\draw[thick] (-.1,-.001) rectangle (.1,.05);
 	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
@@
 	i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-	We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \mathbb{F}) = \lim_{k} \CH_{d}(\HE_{k}; \mathbb{F})$.
+	We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \mathbb{F}) = \lim_{k} \CH_{d}(\HE_{k}; \mathbb{F})$, where $\CH$ denotes \v{C}ech homology.
 	Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
 	\begin{equation*}
-	\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+	\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \mathbb{F})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
 	\end{equation*}
@@
 The gap in the argument of Morse and Tompkins that we have highlighted can be fixed by applying \cref{t:strong local connectedness implies q-tameness} because the proof given in \cite[p.464]{Morse.1939} for local connectivity of $(\Omega_g, A_g)$ actually establishes that the sublevel set filtration of $A_g$ is \emph{strongly} $\LC$,  which can be defined analogously to our strong $\HLC$ property.
-This implies that the filtration is also $\HLC$ for any homology theory that takes trivial values on one point spaces, so in particular for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
+Explicitly, the sublevel set filtration defined by a function $f \colon X \to \R$ is said to be \emph{strongly $\LC$} if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+Clearly, the filtration being strongly $\LC$ implies that the filtration is also strongly $\HLC$ 
+%for any homology theory that takes trivial values on one point spaces, so in particular
+for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
 Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is q-tame as claimed.
-This implies that Morse inequalities hold, and hence so does the unstable minimal surfaces theorem of Morse--Tompkins.
+This implies that Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem by Morse and Tompkins.
+
+We also mention that Morse introduced another condition that he also called local $F$-connectivity three years earlier. 
+It roughly corresponds to being \emph{strongly} $\piLC$ with a certain added uniformity property.
+In the original it reads:
+\begin{displaycquote}[p.421-422]{Morse.1937}
+	The space $M$ will be said to be locally $F$-connected for the order $n$ if corresponding to $n$, an arbitrary point $p$ on $M$, and an arbitrary positive constant $e$, there exists a positive constant $\delta$ with the following property.
+For $c \geq F(p)$ any singular $n$-sphere on $F \leq c$ (the continuous image on $F \leq c$ of an ordinary $n$-sphere) on the $\delta$-neighborhood $p_{\delta}$ of $p$ is the boundary of a singular $(n + 1)$-cell on $F \leq c + e$ and on $p_e$.
+\end{displaycquote}
+Morse also claims in the given reference that this condition is sufficient for q-tameness, but without providing proof. 
+We expect this statement to be true, but do not investigate it further.

### 2021-07-15 vietoris.tex
Before meeting on Friday mid July

--- 2021-05-14 vietoris.tex
@@
-\section{Vietoris homology} \label{s:vietoris}
+\section{Vietoris and \v{C}ech homology} \label{s:vietoris}
 
-In his work on functional topology, Morse uses the Vietoris homology for metric spaces as introduced in \cite{MR1512371}.
-So far, we have considered \v{C}ech homology instead, applying a topological rather than metric construction.
-We will recall the definition of Vietoris homology and recall that these two constructions yield the same result for compact metric spaces.
+As we have mentioned before, Morse's original treatment of functional topology relied on him studying the Vietoris homology \cite{MR1512371} of the sublevel set filtration induced by a function on a metric space.
+For ease of reference, we have instead talked about \v{C}ech homology, which will now be justified by recalling that these two homology constructions agree for compact metric spaces.
 
-\v{C}ech homology of a pair of spaces $(X_{1}, X_{2})$ was defined as the inverse limit over the homology of nerves of covers of $(X_{1}, X_{2})$.
-As an alternative to the nerve construction, for a cover $\alpha = (\alpha_{1}, \alpha_{2})$ one can define $\Vietoris(\alpha)$ as the simplicial pair $\big(\Vietoris (\alpha_{1}), \Vietoris (\alpha_{2})\big)$, where
+First, we recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{MR0050886}.
+Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation. 
+Recall that for an open cover $\alpha \in \Cov(X)$ its \emph{nerve} $\Nrv(\alpha)$ is defined as the simplicial complex
 \[
-\Vietoris (\alpha_{i}) = \left\{ \sigma \subseteq X_{i} \mid \sigma \text{ is finite and there is } U \in \alpha_{i} \text{ with } \sigma \in U \right\}.
+\Nrv(\alpha) =
+\big\{ \beta \subseteq \alpha \mid \beta \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}.
 \]
+The nerve construction defines a functor from the poset $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial complexes. 
+The \emph{\v{C}ech homology with coefficients in $\mathbb{F}$} of $X$ is defined as
+\[
+\CH_{*}(X; \mathbb{F}) \ =
+\lim_{\alpha \in \Cov(X)} H_{*}(\Nrv(\alpha); \mathbb{F}),
+\]
+which extends to a homotopy invariant functor and which admits boundary operators in a natural way.
+
+As an alternative to the nerve construction, for a cover $\alpha \in \Cov(X)$ one can define $\Vietoris(\alpha)$ as the simplicial complex
+\[
+\Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha  \right\},
+\]
+which again yields a functor from $\Cov(X)$ to simplicial complexes.
 This construction is dual in the sense of Dowker's Theorem \cite{Dowker.1952} to the nerve construction.
@@
 $
-H_{*} (\Nrv (\alpha); G) \cong H_{*} (\Vietoris (\alpha); G)
+H_{*} (\Nrv (\alpha); \mathbb{F}) \cong H_{*} (\Vietoris (\alpha); \mathbb{F}).
 $
-for any coefficient group $G$.
 This isomorphism is natural with respect to refinement and compatible with the boundary operators, so that we get an alternative description of \v{C}ech homology as 
@@
 \[
-\lim_{\alpha \in \Cov (X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \, \cong\, \CH (X_{1}, X_{2}; G)
+\CH (X; \mathbb{F}) \ =
+\lim_{\alpha \in \Cov (X)} H_{*} (\Vietoris (\alpha); \mathbb{F}).
 \]
-This is still not exactly the construction of Vietoris homology of a pair of metric spaces $(X_{1}, X_{2})$ as presented in \cite{MR1512371}, which in modern notation is the limit
+
+If $X$ is a metric space, this is still not exactly the same as the construction of Vietoris homology as presented in \cite{MR1512371} and as used by Morse, which in modern notation is the limit
 \begin{equation*}
-    \lim_{\alpha \in \Balls(X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G),
+    \lim_{\alpha \in \Balls(X)} H_{*} (\Vietoris (\alpha); \mathbb{F}),
 \end{equation*}
@@
 \[
-\Balls (X_{1}, X_{2}) = \left\{ \big( ( B_{\delta} (x) )_{x \in X_{1}} , ( B_{\delta} (x) )_{x \in X_{2}} \big) \mid \delta > 0 \right\}
-%\left\{ \big(B_{\delta}(x),\ B_{\delta}(y) \big) \right\}_{(x,y) \in X_{1} \times X_2} 
-\subseteq \Cov (X_{1}, X_{2}).
+\Balls (X) = \left\{ ( B_{\delta} (x) )_{x \in X} \mid \delta > 0 \right\}
+\subseteq \Cov (X).
 \]
-But if the metric pair $(X_{1}, X_{2})$ is compact, then $\Balls (X_{1}, X_{2})$ is coinitial in $\Cov (X_{1}, X_{2})$, that is to say, they define the same limit.
-Thus, we have natural isomorphisms
+However, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they define the same limit.
+Thus, we have a natural isomorphism
 \[
-\lim_{\alpha \in \Balls(X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \ \cong \,
-%\lim_{\alpha \in \Cov (X_{1}, X_{2})} H_{*} (\Vietoris (\alpha); G) \, \cong\, 
-\CH (X_{1}, X_{2}; G),
+\CH_{*} (X; \mathbb{F}) \ \cong \,
+\lim_{\alpha \in \Balls(X)} H_{*} (\Vietoris (\alpha); \mathbb{F})
 \]
-so in Morse's setting the metric Vietoris homology theory he uses is indeed the same as the \v{C}ech homology we considered earlier on.
+for a compact metric space $X$ and so the metric Vietoris homology theory employed in Morse's setting is indeed canonically isomorphic to the \v{C}ech homology we considered earlier on.

### 2021-07-15 connectivity.tex

@@
 We have seen that q-tame functions admit persistence diagrams, which can be used to formulate Morse inequalities.
-With q-tameness being a rather abstract condition, we would now like to establish more concrete topological conditions that ensure the q-tameness of a function.
+With q-tameness being a rather abstract condition, we now establish more concrete topological conditions that ensure the q-tameness of a function.
 Our definitions are motivated by similar conditions that Morse considered in his work on functional topology.
@@
 \]
-We say that $\H$ has the \emph{open} (resp.\@ \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@ compact Hausdorff).
+We say that $\H$ has the \emph{open} (resp.\@\  \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
 
-For the rest of this section, we will assume that $\H$ has the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$. 
+For the rest of this section, we will assume that $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$. 
 Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.
+%We prioritize the reduced versions of these theories, which motivates our notation for a generic homology $\H$.
 
@@
 	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ($\HS_n$) if the image of the map induced by $\H_{n}$ is finite dimensional.
-	Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
+	%Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
 	%The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
-	We omit references to $n$ if the conditions hold for all integers.
+	We omit references to $n$ if the condition holds for all integers.
 	%The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
@@
 \begin{defi} \label{defi:local_connectedness_filtrations}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\HLC$ 
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ 
 	%(resp.\@ $\piLC$, $\LC$) 
-	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+	if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
 	\begin{equation*}
@@
 	\end{equation*}
-	is $\HT$.
+	is $\HS$.
 	%(resp.\@ $\piT$, $\NH$).
     %
-	Similarly, the sublevel set filtration is called \emph{strongly $\HLC$} if for any $x \in X$, $V$ a neighborhood of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
+	Similarly, the sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
 	\begin{equation*}
@@
 	\end{equation*}
-	is $\HT$.
+	is $\HS$.
 \end{defi}
@@
     Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
-We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HT$.
+We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 
-    To do so, we start by using the $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HT$.
-    Now, if $s = f(x)$, we choose $U = U'$. 
-    If $s > f(x)$, we choose $U = U' \cap f_{< s'}$, where $f_{< s'} = f^{-1} (-\infty, s')$.
+    To do so, we start by using the $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
+    Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
     %is the open sublevel set of $f$ at $s'$. 
@@
 
-    In both cases, we obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
-This second map is $\HT$ by construction.
-Any map that factors through an $\HT$ map is also $\HT$, so the proof is finished.
+    We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
+This second map is $\HS$ by construction.
+Any map that factors through an $\HS$ map is also $\HS$, so the proof is finished.
 \end{proof}
@@
 \begin{proof}
-	This is proven via a straightforward diagram chase. For more details see \cite[Lemma 17.3]{Bredon.1997}.
+	This is proven via a straightforward diagram chase. For more details see \cite[Lemma II.17.3]{Bredon.1997}.
 \end{proof}
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-    With the assumptions of \cref{t:strong local connectedness implies q-tameness},
-	consider sets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+    %With the assumptions of \cref{t:strong local connectedness implies q-tameness},
+    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and
+    %
+	consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
 	For any $s < t$ the inclusion
@@
 
-	We will show that $\Sigma_{s, t}$ has following three properties:
+	We will show that $\Sigma_{s, t}$ has the following three properties:
 	\begin{enumerate}
@@
 	is also $\HS_n$ because this map factors through the aforementioned one.
-
 	What is left to do is to show that $\Sigma_{s,t}$ has the properties we want.
@@
 	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
-	is $\HT$, so in particular $\HS_n$.
+	is $\HS$, so in particular $\HS_n$.
 	By local compactness of $X$ we can choose a compact neighborhood $K_x$ of $x$ contained in $U_x$. 
@@
 \begin{proof}[Proof of \cref{t:strong local connectedness implies q-tameness}]
-	This follows from applying \cref{l:key lemma for q-tameness} with $C = f_{\leq s}$ and $L = X$.
+    By definition, the sublevel set filtration of $f$ is q-tame if and only if the inclusion $f_{\leq s} \to f_{\leq t}$ is $\HS$ for all pairs $s < t$.
+    Thus, the theorem follows by applying \cref{l:key lemma for q-tameness} with $C = f_{\leq s}$, which is compact by assumption, and $L = X$.
 \end{proof}

### 2021-07-15 introduction.tex

@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Nowadays, when thinking about the pioneering work of Marston Morse, our first association is possibly with a smooth function on a closed differential manifold, but, as we describe next, that should not be our the last.
-Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also focused on applications beyond this restricted setting;
-giving a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
-Another important example of the use of Morse's insights in an infinite setting is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
+Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also come to mind.
+Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
 Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
-He named this body of work functional topology and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove their Unstable Minimal Surface Theorem giving conditions for the existence of critical points of the Douglas functional that do not locally minimize area.
+He named this body of work \emph{functional topology} and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
+In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove the Unstable Minimal Surface Theorem, a result providing conditions for the existence of critical points of the Douglas functional that are not local minima.
 
-While Morse's work on functional topology did not have a long lasting impact in minimal surface theory, many of his ideas have flourished in other domains.
-% Many of his ideas, specially when applied to the finite dimensional case, have been rediscovered in the study of persistent homology.
-% , a method originated in applied topology and based on applying a homology functor to a filtered space,
-We now review one such area.
-The technique known as persistence homology provides robust and effectively computable invariants of filtered spaces through the application of a homology functor.
-Its successes in applied topology have motivated the development of a refined abstract theory of persistence, lying in the intersection of representation theory, geometry, and topology.
-The influence of this theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that
-% has been growing and the and whose influence extends beyond finite dimensional settings.
-% One of the primary reasons being that
-its basic invariants, known as barcodes, can be organized into a metric space, and that, when they exists, the passage from filtrations to barcodes is Lipschitz.
+While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general, many of his ideas have resurfaced and flourished in other domains.
+In particular, in applied topology, specifically in \emph{topological data analysis}, several key insights of Morse were rediscovered independently as part of the development of persistent homology, which is
+a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
+Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.
+The homology of a filtered space is a diagram of vector spaces indexed over the real numbers (considered as a poset category), also called a \emph{persistence module}.
+In many important cases, persistence module admit an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as the \emph{persistence barcodes}.
+The influence of persistence theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that persistence barcodes can be organized into a metric space, and that the passage to barcodes from filtrations -- or more specifically, real valued-functions with the $L^\infty$ metric -- is Lipschitz.
 This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
 
-In this work we focus on the existence of barcode decompositions for a broad class of filtered spaces arising from the sublevel sets of real valued functions.
-One important consequence we present is the existence of Morse inequalities when such decompositions are available.
+Going into more detail, one interesting aspect of Morse's work from the modern point of view is his use of Vietoris homology with coefficients in a field (or, equivalently, \v{C}ech homology, see \cref{s:vietoris}), which connects closely to the use of filtered Vietoris-Rips and \v{C}ech complexes and the computation of their persistent homology in the context of topological data analysis.
+The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he develops the theory of \emph{caps} and their \emph{spans}, which capture much of the same information as the modern notion of a persistence barcode does, including concepts such as the persistence or the birth and the death of a topological feature.
+As mentioned, Morse's intended use for his theory of caps was to study functionals by analyzing the evolution of the topology of their sublevel sets, which relied on him defining so-called cap numbers and proving that they satisfy a version of his eponymous inequalities.
+In this work, we generalize the definition of these cap numbers in terms of barcode decompositions of persistence modules and show that Morse inequalities are also satisfied in this setting.
+This approach overcomes a limitation of Morse's functional topology setting, which enforced the use of Vietoris homology.
+With our generalization, the analogous results now hold for singular homology as well.
+Furthermore, the generalized Morse inequalities now become applicable in settings beyond sublevel set persistence, such as Floer homology.
 
-For general persistence modules, a well studied condition for the existence of a barcode decomposition is q-tameness \cite{Chazal.2016a,Chazal.2016b}.
-It simply states that all non-identity linear maps in the persistence module have finite dimensional rank.
-In order to obtain the q-tameness of the persistence module associated to a sublevel set filtration, we study different notions of local-connectivity.
-Showing their sufficiency and limitations in different context.
-
-Having conditions for general sublevel set filtration that ensure the existence of barcodes and Morse inequalities is important to extend the influence of persistence methods into infinite dimensional geometrical settings, like the one originally considered by Morse and Topmkins.
-As a consequence of our analysis we identify and fill a gap in the proof the Unstable Minimal Surface Theorem.
+Building on these generalized Morse inequalities, our focus will be on the existence of barcode decompositions for a broad class of filtered spaces arising from the sublevel sets of real valued functions.
+For general persistence modules, a well studied condition for the existence of a barcode decomposition is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different indices in the persistence module have finite dimensional rank.
+Even though none of the structure theory of persistence modules existed at the time, this condition is also already emphasized by Morse in his work on functional topology, where he considered different local connectivity conditions for filtered metric spaces that he claimed to be sufficient for q-tameness.
+Contrary to his claims, one of Morse's conditions is actually insufficient, leaving a gap in the proof the Unstable Minimal Surface Theorem.
+To correct this mistake, we will consider similar, but more natural and more widely applicable local connectivity conditions,
+showing their sufficiency and limitations for guaranteeing q-tameness in different contexts.
+Establishing these general conditions for sublevel set filtrations that ensure the existence of barcodes and Morse inequalities is important to extend the applicability of persistence methods in infinite dimensional geometric settings, such as the one originally considered by Morse and Tompkins.
 
@@
 % Two types of properties of these constructions are important for the existence of barcodes.
-% On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietories exact sequences.
+% On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietoris exact sequences.
 % On the other, those ensuring that q-tame persistence modules admit a multiplicative interval decomposition, which was shown in \cite{schmahl2020structure} to follow from the preservation of certain categorical limits.
@@
 
-An overview of this article follows.
-In \cref{s:homology} we review some basic constructions of homology theory paying special attention to \v{C}ech homology.
+\subsection*{Outline}
 In \cref{s:persistence} we recall the foundations of persistence theory where, for us, the persistent homology of a sublevel set filtration is the key example.
@@
 We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply that the associated persistence module is q-tame.
-We close with a historical overview of Morse's functional topology and its relation to our previous results in \cref{s:surfaces}.
+We close with a historical overview of Morse's functional topology and its relation to our results in \cref{s:surfaces}.
+\cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and a comparison between them based on Dowker's Theorem.

### 2021-07-15 persistence.tex
Improve sect 2

@@
 By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$ yields for every $t \in \R$ a vector space~$M_t$ and for any pair~$s, t \in \R$ with~$s \leq t$ a linear map~$M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
-In other words, we obtain a functor from the real numbers, considered as a poset category, to the category of vector spaces.
-Such functors will be called \emph{persistence modules}.
+In other words, a functor from the real numbers considered as a category via its poset structure to the category of vector spaces.
+Such functors are referred to as \emph{persistence modules}.
 A morphism of persistence modules $\varphi \colon M \to N$ is a natural transformation, i.e., an assignment of a linear map $\varphi_t \colon M_t \to N_t$ for every $t \in \R$ making the diagram
@@
 These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of interval modules.
-% \[
-% \bigoplus_{\lambda \in \Lambda} C(I_{\lambda}).
-% \]
-The multiset of intervals $\{I_{\lambda}\}_{\lambda \in \Lambda}$ associated to a barcode module is known as its \textit{barcode}.
+Given a barcode module $\bigoplus_{\lambda \in \Lambda} C(I_{\lambda})$, the associated multiset of intervals $\{I_{\lambda}\}_{\lambda \in \Lambda}$ is known as its \textit{barcode}.
 By a version of the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832} (see also \cite[Theorem 2.7]{Chazal.2016a} for a specialization to barcode modules), two isomorphic barcode modules have the same barcodes up to a choice of the index set $\Lambda$.
-Thus, if a persistence module $M$ is isomorphic to a barcode module, the associated barcode is a complete invariant of $M$, and the (non-unique) isomorphism to the barcode module is called a \emph{barcode decomposition}.
+Thus, if a persistence module $M$ is provided with an isomorphism to a barcode module, referred to as a \emph{barcode decomposition}, the associated barcode is a complete invariant of $M$.
 
-We want to use the passage from persistence modules to invariants obtained from decompositions as the last step in our pipeline, so we have to understand which persistence modules admit barcode decompositions.
+Since the passage from persistence modules to these discrete invariants is the last step in the persistence pipeline, understanding which persistence modules admit barcode decompositions is key.
 The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's theorem \cite{Crawley-Boevey.2015}.
@@
 
-Unfortunately, the $\PFD$ condition is too restrictive for our purposes.
-In particular, it is not necessarily satisfied in the historical setup of Morse and Tompkins' work on minimal surfaces.
-In this context, the persistence modules $M$ only have the slightly weaker property of being \emph{q-tame}, which is defined by the rank of the maps $M_{s,t} \colon M_s \to M_t$ being finite for all $s < t$  \cite{Chazal.2016a}.
-Not every q-tame persistence module admits a barcode decomposition in the above sense, as exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$.
+Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
+In particular, it is unsuited for the the applications of Morse and Tompkins in minimal surfaces theory.
+An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tame}.
+A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite dimensional for all $s < t$  \cite{Chazal.2016a}.
+As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
 Yet, there are multiple ways of working around this to still get discrete invariants in the spirit of barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
@@
 
-The most general stability result is shown by considering as an intermediate step the \emph{interleaving distance} for filtrations and persistence modules \cite{MR2279866}, which measures how far two $\R$-indexed diagrams $M,N$ are from being isomorphic.
-A $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t, (N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the internal structure maps $(M_t \to M_{t+2\delta})_t, (N_t \to N_{t+2\delta})_t$.
-Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ admitting a $\delta$-interleaving is the interleaving distance between the two diagrams.
+The most general stability result is shown by considering as an intermediate step the metric space of filtrations and persistence modules equipped with the \emph{interleaving distance} \cite{MR2279866}.
+Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
+Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
 As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance on diagrams of topological spaces), to persistent homology (with interleaving distance on persistence modules), and finally to persistence diagrams (with the bottleneck distance).

### 2021-07-16 inequalities.tex
Improve sect 3

@@
 
-In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse--Tompkins to prove their Unstable Minimal Surface Theorem, see \cref{s:surfaces} for more details on this result.
+In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse and Tompkins to prove their Unstable Minimal Surface Theorem.
 We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{thm:q-tame modules have barcodes}.
 
-Recall that for a Morse function $f$ on a closed manifold $X$, the usual Morse inequalities state that for any $n$ we have
-\begin{equation}\label{equ:morse_inequalities}
+Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any $n$ we have
+\begin{equation} \label{equ:morse_inequalities}
 \sum_{d=0}^n \ (-1)^{n-d} ( \# \crit_{d}(f) - \beta_{d}(X) ) \ \geq\  0,  
 \end{equation}
-where $\crit_{d}(f)$ is the set of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d$th Betti number of $X$.
+where $\crit_{d}(f)$ is the set of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d\th$ Betti number of $X$.
 
-Now if no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing the barcode of $H_*(f_{\leq \bullet})$.
-
+If no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing in the barcode of the persistence homology of $f_{\leq \bullet}$.
 More precisely, an index $d$ critical point may either kill an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
@@
 The Betti numbers of $X$ may also be expressed in terms of barcodes because they agree with the number of intervals that extend to $+\infty$.
-Thus, the Morse inequalities above can be expressed entirely in terms of the barcode or persistence diagram of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
+Thus, the Morse inequalities above can be expressed entirely in terms of the barcode (or persistence diagram) of the persistence homology of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
 
-This approach of counting homological changes instead of critical points is also what Morse used in his non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
+This approach counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
-Working entirely in the algebraic setting, we will now fix a $\Z$-graded q-tame persistence module $M$.
+Working entirely in the algebraic setting, we will now fix a graded q-tame persistence module $M$.
 Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
-
-By \cref{thm:q-tame modules have barcodes} $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
+By \cref{thm:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
 In analogy to Morse's definitions, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
-\[
+\begin{equation*}
 m_{d}^{> e}(t) =
@@
 \sum_{\substack{q \in \R \\ q - t > e}} \mathfrak{m}_d(t, q).
-\]
-Note that finiteness of these quantities is ensured by the q-tameness of $M$. 
-Moreover, note that the condition on the counted features to have persistence greater than $e$ is necessary for finiteness of the cap numbers in the q-tame setting. 
-One may omit the lower persistence bound $e$ in the definition if one restricts to $\PFD$ persistence modules.
+\end{equation*}
+Note that finiteness of these quantities is ensured by the q-tameness of $M$ and the use of a non-zero $e$ bounding below the persistence of the considered features.
+To see the necessity of this second condition, consider the q-tame persistence module given by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$.
 
 Whenever the sums below are well-defined, we also consider the \emph{$(d,e)$-cap numbers} 
-\[
-m_{d}^{> e } 
-= \sum_{t} m_{d}^{> e}(t) 
-=
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
-+
+\begin{equation} \label{e:cap numbers}
+m_{d}^{> e } =
+\sum_{t} m_{d}^{> e}(t) \ =
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q) \ +
 \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q).
-\] 
-They are well-defined for example if $M$ is the persistent homology of the sublevel set filtration of a bounded function. This can be deduced from the following general result.
+\end{equation} 
+They are well-defined for example if $M$ is the persistent homology of the sublevel set filtration of a bounded function.
+This can be deduced from the following general result.
 
@@
     Then for each $e>0$ we have 
-    \[
+    \begin{equation*}
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q) < \infty.
-    \]
+    \end{equation*}
 \end{thm}
@@
     We split the sum whose finiteness we want to show in two parts
-    \[
+    \begin{equation*}
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q)
@@
     \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
-    \]
+    \end{equation*}
     and show for each summand separately that it is finite.
     Here, $T$ denotes the triangle
-    \[
+    \begin{equation*}
     T = \{(p,q) \in \multiplicityDomain \mid t_0 \leq p < q \leq t_1\}.
-    \]
+    \end{equation*}
 
-    For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\mathfrak{n}(p,q) = 0$ whenever one of $-\infty < p < t_0$, $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
+    For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\mathfrak{n}(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
     This implies 
-    \[
+    \begin{equation*}
     \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
@@
     \sum_{t_0 < p < t_1} \mathfrak{n} (p, \infty)
-    \]
+    \end{equation*}
     which is clearly finite because $N$ is q-tame.
@@
     For the second summand, note that  
-    \[
+    \begin{equation*}
     \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
@@
     \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q),
-    \]
+    \end{equation*}
     where $T^{\geq e}$ is the smaller triangle 
-    \[
+    \begin{equation*}
     T^{\geq e} = \{(p,q) \in T \mid q-p \geq e\}.
-    \]
+    \end{equation*}
     Thus, in order to prove the theorem, it suffices to show that we have 
-    \[
+    \begin{equation*}
     \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
@@
     \infty.
-    \]
+    \end{equation*}
     To do this, we consider open quadrants 
-    \[
+    \begin{equation*}
     Q(x, y) = \{ (p, q) \in \R^2 \mid p < x \text{ and } y < q \}.
-    \]
-    Covering the compact set $T^{\geq e}$ by the open quadrants $Q \left(x, x + \frac{e}{2} \right)$ for $x \in \R$, we may choose a finite subcover given by, say, $x_1,\dots, x_n$. We obtain
-    \[
+    \end{equation*}
+    Covering the compact set $T^{\geq e}$ by the open quadrants $Q \left(x, x + \frac{e}{2} \right)$ for $x \in \R$, we may choose a finite subcover given by, say, $x_1,\dots, x_n$.
+	We obtain
+    \begin{equation*}
     \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
@@
     \sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{e}{2})}} \mathfrak{n}(p,q).
-    \]
-    Each of sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{e}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{e}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from), see \cite[Section 3.8]{Chazal.2016a}.
-This finishes the proof.
+    \end{equation*}
+    Each of sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{e}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{e}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
 \end{proof}
 
-%If $X$ is a closed manifold and $F$ is a Morse function, then the cap numbers $m_{d}^{> e}(F)$ associated to the persistent homology of the sublevel set filtration of $F$ agree with the number of critical points of $F$ with index $d$ for all sufficiently small $e > 0$.
-
 Comparing to the usual Morse inequalities, the cap numbers in dimension $d$ act like the number of critical points with index $d$.
-As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$, which, under the same assumptions as before, can be expressed in the language of persistence as
-\[
+As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$ referred to as \emph{essential dimensions}, which, under the same assumptions as before, can be expressed in the language of persistence diagrams as
+\begin{equation} \label{e:essential dimension}
 p_{d} \ = \!\! \sum_{p \in \R \cup \{-\infty\}} \mathfrak{m}_d(p,\infty),
-\]
+\end{equation}
 which is also the dimension of the colimit of the degree $d$ part of $M$.
-%Because $M$ is 0-interleaved with $\bigoplus_(p,q) \bigoplus_{\mathfrak{m}(p,q)} C((p,q))$ and colimits commute with direct sums and are invariant up to finite interleaving distance.
 
 \begin{thm}
-    Let $M$ be a graded q-tame persistence module with $m_{d}^{> e }$ and $p_{d}$ finite for all $d$ and $e$.
+	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{> e }$ and essential dimensions $p_{d}$ finite for all $d$ and $e$.
 	If $\mathfrak{m}_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
@@
 \begin{proof}
-    Using a simple argument carried out for example in \cite[Section 11]{Morse.1940}, the claimed inequalities are equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
-
+    The claimed inequalities are equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
     Since we assume $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, we have
@@
     and
-    \[
+    \begin{equation*}
     p_{d}
@@
     \sum_{p \in \R} \mathfrak{m}_d(p,\infty),
-    \]
+    \end{equation*}
     which yields
@@
     \end{align*}
-    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q)$ satisfies $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$. This finishes the proof.
+    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q)$ satisfies $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
-As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions on closed manifolds, as well as the functionals that Morse considered in his work on functional topology.
 
-As we have outlined while motivating the definition for the cap numbers above, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} for Morse functions $f$ on closed manifolds $X$ because in this setting, we have $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
+As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions on closed smooth manifolds, as well as the functionals that Morse considered in his work on functional topology.
+As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} for a Morse function $f$ on a closed smooth manifold $X$ because, in this setting, $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
 Our inequalities also agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
@@
 \end{rem}
-
-%\anibal{Is there a theorem worth mentioning relating homotopical critical points and the algebraic Morse inequalities.}
-% \[
-% (m^{>e}_d - p_d) + (-1)^1 (m^{>e}_{d-1} - p_{d-1}) + \dots + (-1)^n (m^{>e}_0 - p_0) \geq 0
-% \]
-
-% \begin{thm}
-% With notation as above, assume that $\tilde H_{d}(X_{\leq \bullet})$ is q-tame and upper-semicontinuous for all $d$ with multiplicity function $\mathfrak{m}_{d}$.
-Assume that $\tilde H_{d}(X_{\leq \bullet})$ is eventually constant for all $d$ and that $\mathfrak{m}_{d}(-\infty, q) = 0$ for all $q$ and $d$.
-Then the following hold.
-% \begin{enumerate}
-% 	\item The numbers $m_{d}^{> e}(F, t)$ are finite for all $t \in \R$ and non-zero for only finitely many $t \in \R$.
-% 	\item The numbers $p_{d}(F)$ are finite.
-% 	\item We have 
-% 	\[
-% 	m_{d}^{> e}(F) = \sum_{\substack{(p,q)\\q-p>e\\q\neq\infty}}\mathfrak{m}_{d-1}(p,q)+\sum_{\substack{(p,q)\\q-p>e\\p\neq-\infty}}\mathfrak{m}_d(p,q).
-% 	\]
-% 	\item The Morse inequalities 
-% 	\[
-% 	(m^{>e}_n-p_n)+(-1)^1 (m^{>e}_{n-1}-p_{n-1})+\dots+(-1)^n (m^{>e}_0-p_0)\geq 0
-% 	\]
-% 	hold for all $n$.
-% \end{enumerate}
-% \end{thm}
-
-%For semi-continuity: \cref{thm:cech_cont} and the fact that $\lim_{\varepsilon > 0} X_{\leq t + \varepsilon} = X_{\leq t}$.
-%For q-tameness: \cref{t:strong local connectedness implies q-tameness}.
-%For the rest: Boundedness of $F$.

### 2021-07-16 introduction.tex
Improve sect 3

@@
 The homology of a filtered space is a diagram of vector spaces indexed over the real numbers (considered as a poset category), also called a \emph{persistence module}.
-In many important cases, persistence module admit an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as the \emph{persistence barcodes}.
-The influence of persistence theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that persistence barcodes can be organized into a metric space, and that the passage to barcodes from filtrations -- or more specifically, real valued-functions with the $L^\infty$ metric -- is Lipschitz.
+In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields its basic invariant known as its \emph{persistence diagram}.
+The influence of persistence theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that persistence diagrams can be organized into a metric space, and that the passage to barcodes from filtrations -- or more specifically, real valued-functions with the $L^\infty$ metric -- is Lipschitz.
 This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
@@
 Going into more detail, one interesting aspect of Morse's work from the modern point of view is his use of Vietoris homology with coefficients in a field (or, equivalently, \v{C}ech homology, see \cref{s:vietoris}), which connects closely to the use of filtered Vietoris-Rips and \v{C}ech complexes and the computation of their persistent homology in the context of topological data analysis.
-The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he develops the theory of \emph{caps} and their \emph{spans}, which capture much of the same information as the modern notion of a persistence barcode does, including concepts such as the persistence or the birth and the death of a topological feature.
+The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he develops the theory of \emph{caps} and their \emph{spans}, which capture much of the same information as the modern notion of a persistence diagram does, including concepts such as the persistence or the birth and the death of a topological feature.
 As mentioned, Morse's intended use for his theory of caps was to study functionals by analyzing the evolution of the topology of their sublevel sets, which relied on him defining so-called cap numbers and proving that they satisfy a version of his eponymous inequalities.
@@
 
-% Even though Morse did not have a structural description of the homology of a filtration like the one provided by barcodes, he emphasized many aspects that are crucial for their existence, including the use of field coefficients and the restriction to q-tame filtrations.
-% These allowed him to state and prove a version his famous inequalities for general filtered spaces using homotopical critical points.
-% These inequalities are crucial for applications and we reinterpret them in the modern language of barcodes in \cref{s:inequalities}.
-
-% Since general applications may take us away from spaces with the homotopy type of CW-complexes, the choice of homology construction is an important element of the discussion.
-% Two types of properties of these constructions are important for the existence of barcodes.
-% On one hand, those ensuring that local-connectivity properties of sublevel set filtrations are sufficient for q-tameness which, thanks to our analysis, boil down to the existence of Mayer-Vietoris exact sequences.
-% On the other, those ensuring that q-tame persistence modules admit a multiplicative interval decomposition, which was shown in \cite{schmahl2020structure} to follow from the preservation of certain categorical limits.
-
-% Our analysis allows us to show the insufficiency of the local-connectivity assumption used by Morse and Tompkins to state that the filtration defined by Douglas's functional is q-tame.
-% This is because it falls into the class ruled out by \cref{thm:counterexample}.
-% The existence of Morse inequalities requires q-tameness and, hence, so does the Unstable Minimal Surface Theorem of Morse and Tompkins.
-% Nonetheless, this filtration satisfies a stronger condition which \cref{t:strong local connectedness implies q-tameness} ensures to be sufficient
-
-% By reinterpreting the work of Morse in the modern context of persistence theory, and clarifying the conditions needed to prove the existence of barcodes for a broad class of sublevel set filtrations, we aim to increase the number and depth of interactions occurring between persistence theory on one side, and geometry, topology, and functional analysis on the other.
-
 \subsection*{Outline}

### 2021-07-16 persistence.tex
Improve sect 3

@@
 For example, in the next section we will see how they lead to a generalization of the classical Morse inequalities.
-Much of their usefulness comes from a remarkable geometric fact known as stability, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric, called the \emph{bottleneck distance}.
+Much of their usefulness comes from a remarkable geometric fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance}.
 
@@
 
-For the next step in the persistence pipeline, we will need a coherent assignment of a vector space to any topological space, more precisely, a functor from $\Top$ to $\Vect$.
-The key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
+For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, more precisely, a functor from $\Top$ to $\Vect$.
+Key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
 Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{MR0050886} with coefficients in some fixed field $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{MR0050886}, such as singular homology, again with coefficients in some field $\F$ \cite{Eilenberg.1944}.
@@
 In other words, a functor from the real numbers considered as a category via its poset structure to the category of vector spaces.
-Such functors are referred to as \emph{persistence modules}.
+Such functors are called \emph{persistence modules}.
 A morphism of persistence modules $\varphi \colon M \to N$ is a natural transformation, i.e., an assignment of a linear map $\varphi_t \colon M_t \to N_t$ for every $t \in \R$ making the diagram
@@
 commute for all pairs $s \leq t$.
+Since most examples of interest arise from applying a homology theory to a filtered space, we also consider \emph{graded persistence modules}, which are collections of persistence modules indexed by the integers.
+To ease the reading, in what follows we study persistence modules omitting the straightforward generalization of the developed concepts to graded persistence modules.
 
@@
 By a version of the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832} (see also \cite[Theorem 2.7]{Chazal.2016a} for a specialization to barcode modules), two isomorphic barcode modules have the same barcodes up to a choice of the index set $\Lambda$.
-Thus, if a persistence module $M$ is provided with an isomorphism to a barcode module, referred to as a \emph{barcode decomposition}, the associated barcode is a complete invariant of $M$.
-
-Since the passage from persistence modules to these discrete invariants is the last step in the persistence pipeline, understanding which persistence modules admit barcode decompositions is key.
-The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's theorem \cite{Crawley-Boevey.2015}.
-It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional ($\PFD$)} persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all $t \in \R$.
-
+Thus, if a persistence module $M$ is provided with an isomorphism to a barcode module, referred to as a \emph{barcode decomposition}, the associated barcode is a complete isomorphism invariant of $M$.
+So understanding which persistence modules admit barcode decompositions is key.
+The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's \cite{Crawley-Boevey.2015}.
+It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all $t \in \R$.
 Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
@@
 A persistence module $K$ is called \emph{ephemeral} if the maps $K_{s,t} \colon K_s \to K_t$ are $0$ for all $s < t$.
-The \emph{radical} $\rad M$ of a persistence module $M$ is defined as the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
+The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
 Specifically, $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
+For example, the radical of the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ is the direct sum $\bigoplus_{n \in \N_{> 0}} C([0,1/n))$.
 If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Corollary~3.6]{Chazal.2016b},
@@
 
-We have thus seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
+We have thus seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration, and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
 If this is the case, we will call the function \emph{q-tame} with respect to the functor $\H$.
@@
 
-As mentioned earlier, the passage from functions to persistence diagrams is 1-Lipschitz for appropriate metrics \cite{MR3333456}.
-The metric of choice to consider on the space of $\R$-valued functions on $X$ is the distance induced by the supremum norm.
-The metric of choice on the space of persistence diagrams is the \emph{bottleneck distance}, which expresses the distance between persistence diagrams by an optimal matching of the intervals in the corresponding barcodes: two diagrams are within distance $\delta$ if any two matched intervals are within Hausdorff distance $\delta$, and any unmatched interval has length at most $2\delta$.
+As mentioned earlier and reviewed below, the passage from real-valued functions on a topological space to persistence diagrams is 1-Lipschitz for appropriate metrics.
+On the space of real-valued functions one considered the metric induced by the supremum norm, and for the space of persistence diagrams the \emph{bottleneck distance}.
+This metric expresses the distance between persistence diagrams by an optimal matching of the intervals in the corresponding barcodes: two diagrams are within distance $\delta$ if any two matched intervals are within Hausdorff distance $\delta$, and any unmatched interval has length at most $2\delta$.
+\anibal{This is not really flowing for me. Can one describe the bottleneck distance in terms of the persistence diagram only and not use Hausdorff distance?}
 
-The most general stability result is shown by considering as an intermediate step the metric space of filtrations and persistence modules equipped with the \emph{interleaving distance} \cite{MR2279866}.
+The most general stability result is shown by considering as an intermediate step the metric spaces of filtrations and persistence modules equipped with the \emph{interleaving distance}.
 Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
 Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
-As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance on diagrams of topological spaces), to persistent homology (with interleaving distance on persistence modules), and finally to persistence diagrams (with the bottleneck distance).
-In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456}.
+As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistent modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).
+In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456, MR2279866}.

### 2021-07-16 connectivity.tex
Improve sect 4

@@
 
-Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call \emph{homology}.
+Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
 A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps fit in a long exact sequence
- \[
+\begin{equation*}
 \begin{tikzcd}[column sep = small]
@@
 \end{tikzcd}
-\]
+\end{equation*}
 We say that $\H$ has the \emph{open} (resp.\@\  \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
 
-For the rest of this section, we will assume that $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$. 
+For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
 Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.
-%We prioritize the reduced versions of these theories, which motivates our notation for a generic homology $\H$.
 
 \begin{defi} \label{defi:local_connectedness}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} ($\HS_n$) if the image of the map induced by $\H_{n}$ is finite dimensional.
+	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
 	%Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
@@
 
-%There are maps that are $\piT$ but not $\HT$ for singular or \v{C}ech homology. Consider for example the map from a torus to a sphere given by the collapse of its 1-skeleton.
-
-%Naturally, $\HT$ for singular or \v{C}ech homology does not imply $\piT$ either.
-%If the map is $\NH$ then it is $\piT$ and, if the value of $\H$ on a point is 0, $\HT$ as well.
-
-%\begin{defi}
-%	A space $X$ is said to be $\HLC$ (resp.
-$\piLC$, $\LC$) if for each $x \in X$ any neighborhood $V$ of $x$ contains a neighborhood $U$ of $x$ such that the inclusion $U \to V$ is $\HT$ (resp.
-$\piT$, $\NH$).
-	%If the neighborhoods can be chosen so that these inclusion have contractible images we say that the space is \textit{locally contractible} ($\LC$).
-%\end{defi}
-
-%Local connectivity assumptions like the above ones have a long history of being used to ensure that different homology theories agree, e.g.
-in \cite{MR105677}, and to ensure that homology is finitely generated, where we mention the following example.
-%\begin{prop}[{\citet[p.~109]{MR0007094}}]
-%	A compact $\piLC$ Hausdorff space has finite Betti numbers.
-%\end{prop}
-
-%We will deduce the following similar result from our main contribution, \cref{t:strong local connectedness implies q-tameness}.
-
-%\begin{prop} \label{prop:HLC_single_space}
-%	Let $X$ be a compact Hausdorff space.
-%	If $X$ is $\HLC$ then $\H_{n}(X)$ is finitely generated for all $n$.
-%\end{prop}
-
-%We mention the following examples of these two uses, recalling that a space is said to be \textit{paracompact} if every open cover has a locally finite open refinement, i.e., every point has a neighborhood intersecting finitely many sets in the refinement.
-
-%\begin{prop}[\citet{MR105677}] \label{prop:cech_sing_hom_hlc}
-%	\v{C}ech and singular homology with arbitrary coefficients coincide on the category of paracompact Hausdorff spaces which %are $\HLC$ with respect to integral singular homology.
-%\end{prop}
-
-%As a direct consequence of the previous proposition, we obtain the following first persistence result.
-
-%\begin{cor}
-%	Let $f \colon X \to \R$ be a function with compact sublevel set filtration. If every sublevel set is $\piLC$ then $\H (X_{\leq \bullet})$ is $\PFD$ in every degree, in particular q-tame.
-%\end{cor}
-%
-%A similar statement with an $\HLC$ condition instead of the $\piLC$ conditions also holds as a consequence of our main theorem.
-Having each sublevel set being locally connected is, however, in many cases too restrictive.
-Moreover, the weaker finiteness property of being q-tame is sufficient to obtain a notion of barcode and formulate Morse inequalities.
-%Hence, we would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
-% The following definitions are motivated by Morse's work, in particular his local connectivity conditions mentioned in the introduction and reviewed in \cref{s:surfaces}.
-
 \begin{defi} \label{defi:local_connectedness_filtrations}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ 
-	%(resp.\@ $\piLC$, $\LC$) 
-	if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
-	\begin{equation*}
-	f_{\leq s} \cap U \to f_{\leq t} \cap V
-	\end{equation*}
-	is $\HS$.
-	%(resp.\@ $\piT$, $\NH$).
-    %
-	Similarly, the sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
-	\begin{equation*}
-	f_{\leq s} \cap U \to f_{\leq t} \cap V
-	\end{equation*}
-	is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+\end{defi}
+Similarly, we have the following stronger version of this property.
+\begin{defi}
+	The sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
 
-Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$. If the filtration is induced by a continuous function, the converse also holds, as the following theorem shows.
+Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$.
+If the filtration is induced by a continuous function, the converse also holds, as the following theorem shows.
 
@@
 
-As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies q-tameness, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.
+As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies \mbox{q-tameness}, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.
 
@@
 \begin{proof}
-	This is proven via a straightforward diagram chase. For more details see \cite[Lemma II.17.3]{Bredon.1997}.
+	This is proven via a straightforward diagram chase.
+For more details see \cite[Lemma II.17.3]{Bredon.1997}.
 \end{proof}
@@
 	For any $s < t$ the inclusion
-	\[
+	\begin{equation*}
 	C \cap f_{\leq s} \to L \cap f_{\leq t}
-	\]
+	\end{equation*}
 	is $\HS$.
@@
 \begin{proof}
+	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
     The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
@@
 	is $\HS_n$.
-
 	We will show that $\Sigma_{s, t}$ has the following three properties:
@@
 
-	The first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$. 
+	Assuming them for the moment, the first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$.
 	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$.
@@
 	%$V \cap f_{\leq s} \subseteq U \cap f_{\leq s'}$, 
-	so it is $\HS_n$ as well. Thus, $\Sigma_{s, t}$ has the third property we want.
+	so it is $\HS_n$ as well.
+	Thus, $\Sigma_{s, t}$ has the third property we want.
 
@@
 
-	Finally, we will show using Mayer-Vietoris and the induction hypothesis that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions. 
+	Finally, using Mayer-Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
 	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that 
@@
 	Writing $K_i = \overline{V_i}$, we use \cref{l:neighborhood third} to construct compact sets $K'_i$ such that
-	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq U_i \subseteq L\]
+	\begin{equation*}
+	V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq U_i \subseteq L
+	\end{equation*}
 	where $V'_i = \interior(K'_i)$.
@@
     Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\[
+	\begin{equation*}
 	\begin{tikzcd}[column sep=small]
@@
 	\end{tikzcd}
-	\]
+	\end{equation*}
 	We conclude that the inclusion 
@@
 	In the compact case, we apply \cref{l:neighborhood third} again to obtain compact sets $K''_i$ such that
-	\[V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq V''_i \subseteq K''_i \subseteq U_i \subseteq L\]
-	where $V''_i = \interior(K''_i)$. The rest of the proof is then analogous to the previous case:
+	\begin{equation*}
+	V_i \subseteq K_i \subseteq V'_i \subseteq K'_i \subseteq V''_i \subseteq K''_i \subseteq U_i \subseteq L
+	\end{equation*}
+	where $V''_i = \interior(K''_i)$.
+	The rest of the proof is then analogous to the previous case:
 	We have that for both choices of $i$ the inclusions
@@
 	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\[
+	\begin{equation*}
 	\begin{tikzcd}[column sep=small]
@@
 	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ 
-	because it factors through the previous one. This finishes the proof of the lemma.
+	because it factors through the previous one.
 \end{proof}

### 2021-07-16 introduction.tex
Improve sect 4

@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also come to mind.
+Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also be regarded.
 Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.

### 2021-07-16 main.tex
Improve sect 3
Improve sect 4

@@
 \newcommand{\Vect}{\mathsf{Vect}}
+\renewcommand{\th}{^{\mathrm{th}}}
 \newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}
@@
     Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics, Bonn \\ \email{ammedmar@mpim-bonn.mpg.de} 
+	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics in Bonn \at Department of Mathematics, University of Notre Dame \\ \email{ammedmar@mpim-bonn.mpg.de} 
 	\and
@@
 
-\authorrunning{U.~Bauer, A.~M.~Medina-Mardones, M.~Schmahl}
+\authorrunning{U.~Bauer, A.~Medina-Mardones, M.~Schmahl}
 

### 2021-07-16 surfaces.tex
Improve sect 4

@@
 \begin{itemize}
-    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of index 1.
+    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of of $A_g$ of index 1.
 \end{itemize}
 
-They infer Morse inequalities for homotopically critical points by relating these points to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities} and as Morse considered them in \cite{Morse.1940}.
+They infer Morse inequalities for homotopically critical points by relating these points to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
 
 We have seen that these inequalities require q-tameness, so in order to apply them and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
-Throughout his work on functional topology, to obtain q-tameness Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
+Throughout his work on functional topology, to obtain \mbox{q-tameness} Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
 In particular, Morse and Tompkins use in their applications to minimal surface theory the following condition:
@@
 \begin{defi}
-    The sublevel set filtration of a function $F \colon M \to \R$ is said to be $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
-	\begin{equation*}
-	f_{\leq s} \cap U \to f_{\leq t} \cap V
-	\end{equation*}
-	induces the zero map on homotopy groups.
+    The sublevel set filtration of a function $F \colon M \to \R$ is said to be $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces the zero map on homotopy groups.
 \end{defi}
@@
 \begin{defi}
-    The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion
-    \begin{equation*}
-    f_{\leq s} \cap U \to f_{\leq t} \cap V
-    \end{equation*}
-    is homotopic to a constant map.
+    The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 
-The gap in the argument of Morse and Tompkins that we have highlighted can be fixed by applying \cref{t:strong local connectedness implies q-tameness} because the proof given in \cite[p.464]{Morse.1939} for local connectivity of $(\Omega_g, A_g)$ actually establishes that the sublevel set filtration of $A_g$ is \emph{strongly} $\LC$,  which can be defined analogously to our strong $\HLC$ property.
-Explicitly, the sublevel set filtration defined by a function $f \colon X \to \R$ is said to be \emph{strongly $\LC$} if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
-Clearly, the filtration being strongly $\LC$ implies that the filtration is also strongly $\HLC$ 
-%for any homology theory that takes trivial values on one point spaces, so in particular
-for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
-Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is q-tame as claimed.
-This implies that Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem by Morse and Tompkins.
+The gap we have highlighted in the argument of Morse and Tompkins can be fixed by applying \cref{t:strong local connectedness implies q-tameness} because the proof given in \cite[p.464]{Morse.1939} for local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property for the sublevel set filtration of $A_g$, which we now formalize.
 
-We also mention that Morse introduced another condition that he also called local $F$-connectivity three years earlier. 
+\begin{defi}
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{strongly} $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+\end{defi}
+
+Clearly, the filtration being strongly $\LC$ implies that the filtration is also strongly $\HLC$ for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
+Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is \mbox{q-tame} as claimed.
+This implies that Morse inequalities hold, and hence so does the Morse-Tompkins' Unstable Minimal Surfaces Theorem.
+
+We have also mentioned that Morse introduced another condition that he also called local $F$-connectivity three years earlier.
 It roughly corresponds to being \emph{strongly} $\piLC$ with a certain added uniformity property.
@@
 \end{displaycquote}
-Morse also claims in the given reference that this condition is sufficient for q-tameness, but without providing proof. 
+Morse also claims in the given reference that this condition is sufficient for q-tameness, but without providing a proof.
 We expect this statement to be true, but do not investigate it further.

### 2021-07-16 vietoris.tex
Improve sect 4

@@
 
-As we have mentioned before, Morse's original treatment of functional topology relied on him studying the Vietoris homology \cite{MR1512371} of the sublevel set filtration induced by a function on a metric space.
-For ease of reference, we have instead talked about \v{C}ech homology, which will now be justified by recalling that these two homology constructions agree for compact metric spaces.
+As we have mentioned, Morse's original treatment of functional topology used metric Vietoris homology \cite{MR1512371} of filtered metric spaces. 
+For greater generality we have instead considered \v{C}ech homology.
+We now justify this choice showing that these two homology constructions agree on compact metric spaces.
 
-First, we recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{MR0050886}.
+First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{MR0050886}.
 Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation. 
 Recall that for an open cover $\alpha \in \Cov(X)$ its \emph{nerve} $\Nrv(\alpha)$ is defined as the simplicial complex
-\[
+\begin{equation*}
 \Nrv(\alpha) =
 \big\{ \beta \subseteq \alpha \mid \beta \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}.
-\]
-The nerve construction defines a functor from the poset $\Cov(X_{1},X_{2})$ regarded as a category to the category of simplicial complexes. 
+\end{equation*}
+The nerve construction defines a functor from the poset $\Cov(X)$ regarded as a category to that of simplicial complexes. 
 The \emph{\v{C}ech homology with coefficients in $\mathbb{F}$} of $X$ is defined as
-\[
-\CH_{*}(X; \mathbb{F}) \ =
-\lim_{\alpha \in \Cov(X)} H_{*}(\Nrv(\alpha); \mathbb{F}),
-\]
-which extends to a homotopy invariant functor and which admits boundary operators in a natural way.
-
+\begin{equation*}
+\CH(X; \mathbb{F}) \ =
+\lim_{\alpha \in \Cov(X)} H(\Nrv(\alpha); \mathbb{F}).
+\end{equation*}
 As an alternative to the nerve construction, for a cover $\alpha \in \Cov(X)$ one can define $\Vietoris(\alpha)$ as the simplicial complex
-\[
+\begin{equation*}
 \Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha  \right\},
-\]
+\end{equation*}
 which again yields a functor from $\Cov(X)$ to simplicial complexes.
 This construction is dual in the sense of Dowker's Theorem \cite{Dowker.1952} to the nerve construction.
-As a consequence, we have that
-$
-H_{*} (\Nrv (\alpha); \mathbb{F}) \cong H_{*} (\Vietoris (\alpha); \mathbb{F}).
-$
-This isomorphism is natural with respect to refinement and compatible with the boundary operators, so that we get an alternative description of \v{C}ech homology as 
-%the inverse limit over the homology of Vietoris complexes of covers.
-\[
-\CH (X; \mathbb{F}) \ =
-\lim_{\alpha \in \Cov (X)} H_{*} (\Vietoris (\alpha); \mathbb{F}).
-\]
+As a consequence, we have that $H (\Nrv (\alpha); \mathbb{F}) \cong H (\Vietoris (\alpha); \mathbb{F})$.
+This isomorphism is natural with respect to refinement so we get an alternative description of \v{C}ech homology as 
+\begin{equation*}
+\CH (X; \mathbb{F}) \ \cong
+\lim_{\alpha \in \Cov (X)} H (\Vietoris (\alpha); \mathbb{F}).
+\end{equation*}
 
-If $X$ is a metric space, this is still not exactly the same as the construction of Vietoris homology as presented in \cite{MR1512371} and as used by Morse, which in modern notation is the limit
+If $X$ is a metric space, this is still not exactly the same as the construction of metric Vietoris homology presented in \cite{MR1512371} and used by Morse, which in modern notation is the limit
 \begin{equation*}
-    \lim_{\alpha \in \Balls(X)} H_{*} (\Vietoris (\alpha); \mathbb{F}),
+\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \mathbb{F}),
 \end{equation*}
 where 
-\[
+\begin{equation*}
 \Balls (X) = \left\{ ( B_{\delta} (x) )_{x \in X} \mid \delta > 0 \right\}
 \subseteq \Cov (X).
-\]
-However, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they define the same limit.
+\end{equation*}
+However, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they both define the same limit.
 Thus, we have a natural isomorphism
-\[
-\CH_{*} (X; \mathbb{F}) \ \cong \,
-\lim_{\alpha \in \Balls(X)} H_{*} (\Vietoris (\alpha); \mathbb{F})
-\]
-for a compact metric space $X$ and so the metric Vietoris homology theory employed in Morse's setting is indeed canonically isomorphic to the \v{C}ech homology we considered earlier on.
+\begin{equation*}
+\CH (X; \mathbb{F}) \ \cong \,
+\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \mathbb{F})
+\end{equation*}
+for a compact metric space $X$.
+In other words, the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we considered.

### 2021-07-16 connectivity.tex
Version after overall read

@@
 	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
-	%Furthermore, if that image is $0$ then we say that the map is \textit{$n$-homologically trivial} ($\HT_n$).
-	%The map is said to be \textit{$n$-homotopically trivial} $(\piT_{n})$ if the map induced by $\pi_{n}$ is 0.
 	We omit references to $n$ if the condition holds for all integers.
-	%The map is said to be \emph{null-homotopic} ($\NH$) if it is homotopic to a constant map.
 \end{defi}
@@
 Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$.
-If the filtration is induced by a continuous function, the converse also holds, as the following theorem shows.
+If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
 
@@
     Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
-    %is the open sublevel set of $f$ at $s'$.
     Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of $X$.
@@
 
-% As for a single space, the $\LC$ notions imply the corresponding $\piLC$ notions and the corresponding $\HLC$ notions if $\H$ evaluated at a point is trivial.
-
-As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies \mbox{q-tameness}, and consequently also implies the existence of a persistence diagram, yielding persistent Morse inequalities.
+As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies \mbox{q-tameness}, and consequently also implies the existence of a persistence diagram which yields persistent Morse inequalities.
 
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-    %With the assumptions of \cref{t:strong local connectedness implies q-tameness},
-    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and
-    %
-	consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
 	For any $s < t$ the inclusion
@@
 	$V \cap f_{\leq s} \to L \cap f_{\leq t}$
-	factors through the previous one %because we have 
-	%$V \cap f_{\leq s} \subseteq U \cap f_{\leq s'}$, 
-	so it is $\HS_n$ as well.
+	factors through the previous one so it is $\HS_n$ as well.
 	Thus, $\Sigma_{s, t}$ has the third property we want.

### 2021-07-16 inequalities.tex
Version after overall read

@@
 \begin{proof}
-    The claimed inequalities are equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
+    Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
     Since we assume $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, we have

### 2021-07-16 inequalities.tex
Changes during meeting

--- 2021-07-15 inequalities.tex
@@
 
-In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse--Tompkins to prove their Unstable Minimal Surface Theorem, see \cref{s:surfaces} for more details on this result.
+In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse--Tompkins in their proof of the Unstable Minimal Surface Theorem (see \cref{s:surfaces} for more details on this result).
 We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{thm:q-tame modules have barcodes}.
 
-Recall that for a Morse function $f$ on a closed manifold $X$, the usual Morse inequalities state that for any $n$ we have
+Recall that the usual Morse inequalities state that for a Morse function $f$ on a closed manifold $X$ and for any $n \in \mathbb N$ we have
 \begin{equation}\label{equ:morse_inequalities}
@@
 
-Now if no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing the barcode of $H_*(f_{\leq \bullet})$.
-
-More precisely, an index $d$ critical point may either kill an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
-
-The Betti numbers of $X$ may also be expressed in terms of barcodes because they agree with the number of intervals that extend to $+\infty$. 
+Now if $f$ is a \emph{excellent} Morse function, meaning that no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing the barcode of $H_*(f_{\leq \bullet})$.
+More precisely, an index $d$ critical point may either kill an existing homology class in degree $d-1$, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class in degree $d$, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
+The Betti numbers of $X$ may also be expressed in terms of barcodes, as they agree with the number of intervals that extend to $+\infty$. 
 Thus, the Morse inequalities above can be expressed entirely in terms of the barcode or persistence diagram of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
@@
 This approach of counting homological changes instead of critical points is also what Morse used in his non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which can be described in terms of persistent homology as follows.
+Assuming that the associated persistence module $M$ has a barcode and is \emph{upper semi-continuous}, meaning that $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$, the $(d, t, e)$-cap number correspond to the number of finite bars with length greater than $e$ in the $d$-dimensional barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)$-dimensional barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
 Working entirely in the algebraic setting, we will now fix a $\Z$-graded q-tame persistence module $M$.
-Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
+Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could also arise, for example, as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
 
-By \cref{thm:q-tame modules have barcodes} $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
+By \cref{thm:q-tame modules have barcodes}, the persistence module $M$ has a persistence diagram in every degree $d$, with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
 In analogy to Morse's definitions, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as

### 2021-07-16 persistence.tex
Improve sect 4
Changes during meeting

--- 2021-07-15 persistence.tex
@@
 
-In this section we present an overview of the theory of persistence as it is used in geometric contexts, through filtrations by sublevel sets of real-valued functions.
+In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions, applicable to functionals defined on a function or moduli space.
 For a detailed exposition we refer to \cite{polterovich2020topological} and \cite{Chazal.2016a, MR3408277}.
@@
 An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tame}.
-A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite dimensional for all $s < t$  \cite{Chazal.2016a}.
+A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite for all $s < t$ \cite{Chazal.2016a}.
 As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
@@
 A persistence module $K$ is called \emph{ephemeral} if the maps $K_{s,t} \colon K_s \to K_t$ are $0$ for all $s < t$.
-The \emph{radical} $\rad M$ of a persistence module $M$ is defined as the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
+The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
 Specifically, $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
@@
 
-Instead of talking about the barcode of the radical of a q-tame persistence module, it will be more convenient for our treatment of Morse inequalities to talk about the \emph{(undecorated) persistence diagram} associated to a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which is the multiset defined by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
+Instead of talking about the barcode of the radical of a q-tame persistence module, it will be more convenient for our treatment of Morse inequalities to talk about the \emph{(undecorated) persistence diagram} associated to a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which is the multiset defined by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in the set $\multiplicityDomain$ of pairs of interval endpoints,
 \[
 \multiplicityDomain =
-\big\{ (p,q) \mid p \in \R \cup \{-\infty\}, \ q \in \R \cup \{+\infty\}, \ p < q \big\}
+\big\{ (p,q) \mid p \in \R \cup \{-\infty\}, \ q \in \R \cup \{+\infty\}, \ p < q \big\},
 \]
@@
 
-The most general stability result is shown by considering as an intermediate step the metric space of filtrations and persistence modules equipped with the \emph{interleaving distance} \cite{MR2279866}.
+The most general stability result is shown by considering as an intermediate step the metric spaces of filtrations and persistence modules equipped with the \emph{interleaving distance} \cite{MR2279866}.
 Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
-Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
-As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance on diagrams of topological spaces), to persistent homology (with interleaving distance on persistence modules), and finally to persistence diagrams (with the bottleneck distance).
+Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the \emph{interleaving distance} between them.
+As it turns out, the stability of persistence barcodes can then be described as a sequence of several 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance on diagrams of topological spaces), to persistent homology (with interleaving distance on persistence modules), and finally to persistence diagrams (with the bottleneck distance).
 In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem  \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456}.

### 2021-07-16 persistence.tex

--- 2021-07-16 persistence.tex
@@
 Instead of talking about the barcode of the radical of a q-tame persistence module, it will be more convenient for our treatment of Morse inequalities to talk about the \emph{(undecorated) persistence diagram} associated to a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which is the multiset defined by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
-\[
+\begin{equation*}
 \multiplicityDomain =
 \big\{ (p,q) \mid p \in \R \cup \{-\infty\}, \ q \in \R \cup \{+\infty\}, \ p < q \big\}
-\]
+\end{equation*}
 the cardinality of the set $\{ \alpha \in A \mid \inf I_{\alpha} = p,\ \sup I_{\alpha} = q\}$.

### 2021-07-22 connectivity.tex
Version before meeting

@@
 \begin{defi}
-	The sublevel set filtration is called \emph{strongly locally homologically small $\HLC$} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{strongly locally homologically small} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 The general proof strategy is inspired by the proof of a result attributed to Wilder as presented by Bredon \cite[Section II.17]{Bredon.1997}.
-We collect the main ideas in three lemmas.
+We collect the main ideas in several lemmas.
 
@@
 \begin{lem} \label{l:neighborhood third}
-	Let $X$ be locally compact space.
+	Let $X$ be a locally compact space.
 	For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
@@
 	\begin{equation*}
-	K \subseteq \bigcup_K \interior(C(x)) \subseteq \interior\left(\bigcup_K C(x)\right) \subseteq \bigcup_K C(x) \subseteq U
+	K \subseteq \bigcup_{x \in K} \interior(C(x)) \subseteq \interior\left(\bigcup_{x \in K} C(x)\right) \subseteq \bigcup_{x \in K} C(x) \subseteq U
 	\end{equation*}
@@
 
+We want to use \cref{l:neighborhood third} on the domain of the function whose sublevel set filtration we consider.
+However, we do not want to assume the domain to be locally compact for \cref{t:strong local connectedness implies q-tameness}.
+To circumvent this, we will work in one of the sublevel sets, which are assumed to be compact Hausdorff and hence locally compact.
+This requires the use of a slight weakening of the strong $\HLC$ condition.
+
+\begin{defi}
+	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{strongly $\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+\end{defi}
+
+\begin{lem}\label{l: restriction of LHS filtration}
+    Let $f \colon X \to \R$ be a function whose sublevel set filtration is strongly $\HLC$.
+    Fix $u \in \R$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y = f_{\leq u}$.
+    Then, the sublevel set filtration defined by $g$ is strongly $\HLC$ below $u$.
+\end{lem}
+
+\begin{proof}
+    Let $x \in Y$, $V$ a neighborhood of $x$ in $Y$ and consider indices $s,t$ with $g(x) < s < t < u$. 
+    We need to find a neighborhood $U \subseteq V$ of $x$ such that the inclusion $g_{\leq s} \cap U \to g_{\leq t} \cap V$ is $\HS$.
+
+    Since $Y \subseteq X$ carries the subspace topology, we may choose a neighborhood $V'$ of $x$ in $X$ such that $V = V' \cap Y$. 
+    The sublevel set filtration of $f$ is assumed to be strongly $\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
+    We set $U = U' \cap Y$, which defines a neighborhood of $x$ in $Y$.
+
+    Now, $s < t < u$ implies that we have $g_{\leq s} = f_{\leq s}$ and $g_{\leq t} = f_{\leq t}$. 
+    Moreover, we have $f_{\leq s} \cap Y = f_{\leq s} \cap f_{\leq u} = f_{\leq s}$ and $f_{\leq t} \cap Y = f_{\leq t} \cap f_{\leq u} = f_{\leq t}$. 
+    Thus, we obtain $g_{\leq s} \cap U = f_{\leq s} \cap Y \cap U' = f_{\leq s} \cap U'$ and $g_{\leq t} \cap V = f_{\leq t} \cap Y \cap V' = f_{\leq t} \cap V'$.
+    This implies that the inclusion $g_{\leq s} \cap U \to g_{\leq t} \cap V$ is $\HS$ because it agrees with the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$, which is $\HS$ by construction.
+This finishes the proof.
+\end{proof}
+
 \begin{lem} \label{l:key lemma for q-tameness}
-    Let $f \colon X \to \R$ be a function whose sublevel set filtration is compact and strongly $\HLC$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
-	For any $s < t$ the inclusion
-	\begin{equation*}
-	C \cap f_{\leq s} \to L \cap f_{\leq t}
-	\end{equation*}
-	is $\HS$.
+    Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and strongly $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
 \end{lem}
@@
 	Choose an arbitrary $s' \in (s,\, t)$.
-	Since the sublevel set filtration of $f$ is strongly $\HLC$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
+	Since the sublevel set filtration of $f$ is strongly $\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
 	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
@@
 	The rest of the proof is then analogous to the previous case:
-	We have that for both choices of $i$ the inclusions
+	We have that for both choices of~$i$ the inclusions
 	$K''_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
@@
     By definition, the sublevel set filtration of $f$ is q-tame if and only if the inclusion $f_{\leq s} \to f_{\leq t}$ is $\HS$ for all pairs $s < t$. 
-    Thus, the theorem follows by applying \cref{l:key lemma for q-tameness} with $C = f_{\leq s}$, which is compact by assumption, and $L = X$.
+    Choose $u \in \R$ with $u > t$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y=f_{\leq u}$. 
+    Since we assume $f$ to induce a strongly $\HLC$ sublevel set filtration, by \cref{l: restriction of LHS filtration} the sublevel set filtration of $g$ is strongly $\HLC$ below $u$. 
+    Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.
+    Thus, we can apply \cref{l:key lemma for q-tameness} to the filtration $g_{\leq \bullet}$ with $C = f_{\leq s}$ and $L = Y$ to obtain that the inclusion $f_{\leq s} = C \cap g_{\leq s} \to L \cap g_{\leq t} = f_{\leq t}$ is $\HS$.
 \end{proof}
@@
 
-\begin{cor}
+\begin{cor}\label{c: q-tameness for continuous functions}
     If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and $\HLC$, then it is also q-tame.

### 2021-07-22 inequalities.tex
Version before meeting

--- 2021-07-16 inequalities.tex
@@
 
-Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any $n$ we have
+Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any non-negative integer $n$ the following holds:
 \begin{equation} \label{equ:morse_inequalities}
@@
 
-If no two critical points of $f$ have the same value, the critical points are in one-to-one correspondence with the critical values, which in turn are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing in the barcode of the persistence homology of $f_{\leq \bullet}$.
+If no two critical points of $f$ have the same value, the sets of critical points and values are naturally in one-to-one correspondence, which, in turn, are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing in the barcode of the persistent homology of $f_{\leq \bullet}$.
 More precisely, an index $d$ critical point may either kill an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
@@
 The Betti numbers of $X$ may also be expressed in terms of barcodes because they agree with the number of intervals that extend to $+\infty$.
-Thus, the Morse inequalities above can be expressed entirely in terms of the barcode (or persistence diagram) of the persistence homology of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
+Thus, the Morse inequalities above can be expressed entirely in terms of the barcode (or persistence diagram) of the persistent homology of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
 
-This approach counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
+This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
 To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
@@
 
-\begin{thm}
+\begin{thm}\label{t:inequalities}
 	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{> e }$ and essential dimensions $p_{d}$ finite for all $d$ and $e$.
@@
 
-As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions on closed smooth manifolds, as well as the functionals that Morse considered in his work on functional topology.
-As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} for a Morse function $f$ on a closed smooth manifold $X$ because, in this setting, $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
-Our inequalities also agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
+As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions $f$ on closed smooth manifolds $X$.
+As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
+
+The finiteness conditions of our theorem are also satisfied for the functionals that Morse considered in his work on functional topology, with q-tameness being guaranteed by \cref{t:strong local connectedness implies q-tameness} instead of the insufficient condition Morse proposed.
+As we have also mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
 Note, however, that in contrast to Morse's version, our inequalities also work without the upper semi-continuity assumption, removing the need for this unusual choice of homology theory.

### 2021-07-22 introduction.tex
Version before meeting

@@
 Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also be regarded.
-Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold.
+Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold, which notably goes beyond the compact setting.
 Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
 Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
-He named this body of work \emph{functional topology} and used it to study minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
+He named this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
 In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove the Unstable Minimal Surface Theorem, a result providing conditions for the existence of critical points of the Douglas functional that are not local minima.
@@
 While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general, many of his ideas have resurfaced and flourished in other domains.
-In particular, in applied topology, specifically in \emph{topological data analysis}, several key insights of Morse were rediscovered independently as part of the development of persistent homology, which is
-a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
+In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \textit{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
 Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.
-The homology of a filtered space is a diagram of vector spaces indexed over the real numbers (considered as a poset category), also called a \emph{persistence module}.
-In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields its basic invariant known as its \emph{persistence diagram}.
-The influence of persistence theory and its sophistication have seen rapid growth in recent years, motivated in part by the fact that persistence diagrams can be organized into a metric space, and that the passage to barcodes from filtrations -- or more specifically, real valued-functions with the $L^\infty$ metric -- is Lipschitz.
-This often allows to recast geometric questions about general filtered spaces into a combinatorial and typically finite metric model.
 
-Going into more detail, one interesting aspect of Morse's work from the modern point of view is his use of Vietoris homology with coefficients in a field (or, equivalently, \v{C}ech homology, see \cref{s:vietoris}), which connects closely to the use of filtered Vietoris-Rips and \v{C}ech complexes and the computation of their persistent homology in the context of topological data analysis.
-The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he develops the theory of \emph{caps} and their \emph{spans}, which capture much of the same information as the modern notion of a persistence diagram does, including concepts such as the persistence or the birth and the death of a topological feature.
-As mentioned, Morse's intended use for his theory of caps was to study functionals by analyzing the evolution of the topology of their sublevel sets, which relied on him defining so-called cap numbers and proving that they satisfy a version of his eponymous inequalities.
-In this work, we generalize the definition of these cap numbers in terms of barcode decompositions of persistence modules and show that Morse inequalities are also satisfied in this setting.
-This approach overcomes a limitation of Morse's functional topology setting, which enforced the use of Vietoris homology.
-With our generalization, the analogous results now hold for singular homology as well.
-Furthermore, the generalized Morse inequalities now become applicable in settings beyond sublevel set persistence, such as Floer homology.
+The homology of a filtered space is an example of what is called a \textit{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
+In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as its \textit{persistence diagram}.
 
-Building on these generalized Morse inequalities, our focus will be on the existence of barcode decompositions for a broad class of filtered spaces arising from the sublevel sets of real valued functions.
-For general persistence modules, a well studied condition for the existence of a barcode decomposition is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different indices in the persistence module have finite dimensional rank.
-Even though none of the structure theory of persistence modules existed at the time, this condition is also already emphasized by Morse in his work on functional topology, where he considered different local connectivity conditions for filtered metric spaces that he claimed to be sufficient for q-tameness.
-Contrary to his claims, one of Morse's conditions is actually insufficient, leaving a gap in the proof the Unstable Minimal Surface Theorem.
-To correct this mistake, we will consider similar, but more natural and more widely applicable local connectivity conditions,
-showing their sufficiency and limitations for guaranteeing q-tameness in different contexts.
-Establishing these general conditions for sublevel set filtrations that ensure the existence of barcodes and Morse inequalities is important to extend the applicability of persistence methods in infinite dimensional geometric settings, such as the one originally considered by Morse and Tompkins.
+The influence of persistence theory and its sophistication have seen rapid growth in recent years.
+One of the primary reasons for this is the fact that persistence diagrams can be organized into a metric space, often allowing to recast geometric questions about general filtered spaces in a combinatorial metric model.
+This is because the passage via the homology construction to this metric space is Lipschitz, a statement commonly known as the \textit{stability} of persistence diagrams.
+
+The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he developed the theory of \textit{caps} and their \textit{spans}, capturing much of the same information as the modern notion of persistence diagram, including concepts such as the persistence or birth-death of a topological feature.
+Morse used his theory of caps to study functionals on a metric space by analyzing the evolution of the topology of their sublevel sets.
+A key tool for this end is a version of his eponymous inequalities for cap numbers, which expands their usual version in the compact and smooth setting.
+In this work, using persistence diagrams, we generalize  the definition of these cap numbers to persistence modules and prove the existence of Morse inequalities for a large class of them (\cref{t:inequalities}).
+Our approach makes these inequalities accessible in new contexts beyond those originally covered by functional topology, including, for example, symplectic geometry.
+
+Given the importance of persistence diagrams for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
+For general persistence modules, a well studied condition for the existence of persistence diagrams is \textit{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite dimensional rank.
+The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
+In fact, the problem of finding such conditions was already considered by Morse, who studied certain local connectivity properties of a filtered metric space and claimed them to suffice for the q-tameness of the associated persistent homology.
+Contrary to these claims, we show that the local connectivity condition used by Morse and Tompkins in the proof of the Unstable Minimal Surface Theorem is insufficient (\cref{c: counterexample}).
+We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c: q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:strong local connectedness implies q-tameness}).
+Since Douglas' functional has compact sublevel sets but is not continuous in the $C^0$ topology, which Morse and Tompkins considered, we use this second condition to correct their proof.
+
+\subsection*{Summary}
+
+The primary contribution of this work consists in the introduction of topological conditions for a broad class of filtered spaces ensuring their associated persistence homology modules satisfy Morse inequalities.
+As an application, we identify and fix with our conditions a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins.
 
 \subsection*{Outline}
+
 In \cref{s:persistence} we recall the foundations of persistence theory where, for us, the persistent homology of a sublevel set filtration is the key example.
-In \cref{s:inequalities}, we present a persistence-theoretic point of view on Morse inequalities, relating to Morse's version of these inequalities in functional topology.
-\cref{s:connectivity} is the core of this work.
-We define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply that the associated persistence module is q-tame.
+We present a persistence-theoretic point of view on Morse inequalities in \cref{s:inequalities}.
+It generalizes both their version in the smooth and compact setting as well as the one used in functional topology.
+The core of this work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness for its associated persistence module.
 We close with a historical overview of Morse's functional topology and its relation to our results in \cref{s:surfaces}.

### 2021-07-22 main.tex
Version after overall read
Version before meeting

@@
-%\immediate\write18{bibtex \jobname}
 \documentclass[nospthms, a4paper, final]{svjour3}
 \setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}
-\setlength{\textheight}{\dimexpr\pdfpageheight-2in}
+\setlength{\textheight}{\dimexpr\pdfpageheight-2.4in}
 \usepackage{mathptmx}
@@
 
-\author{Ulrich Bauer \and Anibal M.~Medina-Mardones \and Maximilian Schmahl}
+\author{Ulrich Bauer \and Anibal M.~Medina-Mardones \and Maximilian~Schmahl}
 
@@
     Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics in Bonn \at Department of Mathematics, University of Notre Dame \\ \email{ammedmar@mpim-bonn.mpg.de} 
+	Anibal M.~Medina-Mardones \at University of Notre Dame du Lac \at Max Planck Institute for Mathematics in Bonn \\ \email{ammedmar@mpim-bonn.mpg.de} 
 	\and
-	Maximilian Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg}
+	Maximilian~Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg.de}
 }
@@
 	Morse and Tompkins applied this body of work, referred to as functional topology, to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
-	Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics with applications to a wide range of topics, including neuroscience, genomics, and symplectic geometry.
+	Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics.
 	In this article, we provide a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
-	We adjust several key definitions and prove stronger statements in order to allow for future applications of persistence techniques in functional analysis, as well as to correct a mistake in the proof by Morse and Tompkins of the Unstable Minimal Surface Theorem.
+	We adjust several key definitions and prove stronger statements, including a generalized version of Morse inequalities, in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
+	As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
 \end{abstract}

### 2021-07-22 persistence.tex
Version before meeting

@@
 For example, in the next section we will see how they lead to a generalization of the classical Morse inequalities.
-Much of their usefulness comes from a remarkable geometric fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance}.
+Much of their usefulness comes from a remarkable fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance}.
 
@@
 \end{equation*}
-We say that this filtration is \textit{compact} if $X$ is a locally compact Hausdorff space and all sublevel sets are compact.
+We say that this filtration is \textit{compact} if all sublevel sets are compact Hausdorff spaces.
 
-For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, more precisely, a functor from $\Top$ to $\Vect$.
+For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, or, more precisely, a functor from the category $\Top$ of topological spaces to the category $\Vect$ of vector spaces over a fixed field $\mathbb{F}$.
 Key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
-Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{MR0050886} with coefficients in some fixed field $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{MR0050886}, such as singular homology, again with coefficients in some field $\F$ \cite{Eilenberg.1944}.
+Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{MR0050886} with coefficients in $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{MR0050886}, such as singular homology, again with coefficients in $\F$ \cite{Eilenberg.1944}.
 
 By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$ yields for every $t \in \R$ a vector space~$M_t$ and for any pair~$s, t \in \R$ with~$s \leq t$ a linear map~$M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
-In other words, a functor from the real numbers considered as a category via its poset structure to the category of vector spaces.
+In other words, we obtain a functor $M$ from the real numbers considered as a category via its poset structure to the category of vector spaces.
 Such functors are called \emph{persistence modules}.
@@
 Persistence modules that are \emph{indecomposable}, i.e., those that have only trivial direct sum decompositions, play an important role in persistence theory.
-A rich family of indecomposable persistence modules is given by \emph{interval modules}, which for an interval $I \subseteq \R$ are defined by
+A rich family of indecomposable persistence modules is given by \emph{interval modules}, which for intervals $I \subseteq \R$ are defined by
 \begin{equation} \label{e:interval module}
@@
 Thus, if a persistence module $M$ is provided with an isomorphism to a barcode module, referred to as a \emph{barcode decomposition}, the associated barcode is a complete isomorphism invariant of $M$.
-So understanding which persistence modules admit barcode decompositions is key.
+Hence, understanding which persistence modules admit barcode decompositions is key.
 The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's \cite{Crawley-Boevey.2015}.
@@
 Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
-In particular, it is unsuited for the the applications of Morse and Tompkins in minimal surfaces theory.
-An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tame}.
+In particular, it is unsuited for the applications of Morse and Tompkins in minimal surfaces theory.
+An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tameness}.
 A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite for all $s < t$ \cite{Chazal.2016a}.
 As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
-Yet, there are multiple ways of working around this to still get discrete invariants in the spirit of barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
+Yet, there are multiple ways to regularize q-tame persistence modules to obtain discrete invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
 We briefly recall the approach from \citet{Chazal.2016b}.
@@
 Specifically, $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
-For example, the radical of the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ is the direct sum $\bigoplus_{n \in \N_{> 0}} C([0,1/n))$.
+For example, the radical of the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ is the direct sum $\bigoplus_{n \in \N_{> 0}} C((0,1/n))$.
 If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Corollary~3.6]{Chazal.2016b},
@@
 \end{equation*}
-the cardinality of the set $\{ \alpha \in A \mid \inf I_{\alpha} = p,\ \sup I_{\alpha} = q\}$.
+the cardinality of the set $\{ \lambda \in \Lambda \mid \inf I_{\lambda} = p,\ \sup I_{\lambda} = q\}$.
 
@@
 
-As mentioned earlier and reviewed below, the passage from real-valued functions on a topological space to persistence diagrams is 1-Lipschitz for appropriate metrics.
-On the space of real-valued functions one considered the metric induced by the supremum norm, and for the space of persistence diagrams the \emph{bottleneck distance}.
-This metric expresses the distance between persistence diagrams by an optimal matching of the intervals in the corresponding barcodes: two diagrams are within distance $\delta$ if any two matched intervals are within Hausdorff distance $\delta$, and any unmatched interval has length at most $2\delta$.
-\anibal{This is not really flowing for me. Can one describe the bottleneck distance in terms of the persistence diagram only and not use Hausdorff distance?}
+As mentioned earlier, the passage from real-valued functions on a topological space to persistence diagrams is 1-Lipschitz for appropriate metrics.
+On the space of real-valued functions one considers the metric induced by the supremum norm, and for the space of persistence diagrams the \emph{bottleneck distance}.
+This metric expresses the distance between persistence diagrams by a matching of their points, counted with multiplicities, which is optimal with respect to the $L^{\infty}$-distance on $\multiplicityDomain$: two diagrams are within distance $\delta$ if any two matched points are within $L^{\infty}$-distance $\delta$, and any unmatched point has $L^{\infty}$-distance at most $2\delta$ to the diagonal $\{(p,q) \in \R^2 \mid p = q\}$.
 
 The most general stability result is shown by considering as an intermediate step the metric spaces of filtrations and persistence modules equipped with the \emph{interleaving distance}.
-Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
+Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving between $M$ and $N$ consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
 Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
-As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: from functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistent modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).
+As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: From functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistence modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).
 In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456, MR2279866}.

### 2021-07-22 surfaces.tex
Version after overall read
Version before meeting

@@
 Morse and Tompkins considered the following setting introduced by Douglas.
-Let $g \colon \R \to \R^n$ be $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
+Let $g \colon \R \to \R^n$ be a $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
 Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and such that there are three distinct points $\alpha_i \in [0,2\pi)$ with $\varphi(\alpha_i)=\alpha_i$.
@@
 \begin{itemize}
-    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of of $A_g$ of index 1.
+    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of $A_g$ of index 1.
 \end{itemize}
@@
 We have seen that these inequalities require q-tameness, so in order to apply them and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
-Throughout his work on functional topology, to obtain \mbox{q-tameness} Morse assumed slightly varying forms of local-connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins use in their applications to minimal surface theory the following condition:
-\begin{displaycquote}[p.431]{Morse.1940}
+Throughout his work on functional topology, in order to obtain \mbox{q-tameness}, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations.
+In particular, in their applications to minimal surface theory, Morse and Tompkins use the following condition:
+\begin{displaycquote}[p.~431]{Morse.1940}
 	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
@@
 \begin{defi}
-    The sublevel set filtration of a function $F \colon M \to \R$ is said to be $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces the zero map on homotopy groups.
+    The sublevel set filtration of a function $F \colon M \to \R$ is said to be \emph{homotopically locally connected} or $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
 \end{defi}
@@
 
-\begin{displaycquote}[Theorem 6.3, p.432]{Morse.1940}
+\begin{displaycquote}[Theorem 6.3, p.~432]{Morse.1940}
 	Let $a$ and $c$ be positive constants such that $a < c < 1$.
@@
 Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
-Unfortunately, this argument is not in general sound as we will show next.
+Unfortunately, this claim does not hold in general, as we will show next by providing an explicit counterexample.
 
 \begin{defi}
-    The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+    The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally connected} or $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 Clearly, being $\LC$ implies being $\piLC$ and, if the homology $\H$ takes finite dimensional values on one point spaces, also $\HLC$.
-% Moreover, if the sublevel set filtration of a function $F \colon M \to \R$ on a metric space $M$ is $\LC$, then $M$ is locally $F$-connected in the sense of Morse's definition above.
-We will now show that not even $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations.
-% neither our $\HLC$ condition nor Morse's condition above are sufficient in general to imply q-tameness for compact sublevel set filtrations induced by non-continuous functions by producing an $\LC$ filtration which is not q-tame.
+We will now show that not even $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
 In particular, our construction will be used to invalidate Morse's claim quoted above.
@@
 \begin{proof}
-	The space $\HE$ is Hausdorff and locally compact since $\R^{d+1}$ is.
-	To verify that $f$ has compact sublevel sets we notice that all level sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
-	Let us now verify that the sublevel set filtration of $f$ is weakly $\LC$.
+    \todo{needs to be rewritten with the new s, t notation instead of the epsilon, delta notation}
+	The space $\HE$ is Hausdorff %and locally compact
+	since $\R^{d+1}$ is.
+	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
+	Let us now verify that the sublevel set filtration of $f$ is $\LC$.
 	Let $\epsilon > 0$ and $x \in \HE$.
@@
 
-\begin{cor}
+\begin{cor}\label{c: counterexample}
     The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.

### 2021-07-22 vietoris.tex
Version before meeting

@@
 
-As we have mentioned, Morse's original treatment of functional topology used metric Vietoris homology \cite{MR1512371} of filtered metric spaces. 
-For greater generality we have instead considered \v{C}ech homology.
+An interesting aspect of Morse's work from the modern point of view is his use of metric Vietoris homology with coefficients in a field, which closely relates to the use of filtered Vietoris-Rips and \v{C}ech complexes in topological data analysis.
+
+For greater generality, instead of metric Vietoris homology we have instead considered \v{C}ech homology in the previous section.
 We now justify this choice showing that these two homology constructions agree on compact metric spaces.

### 2021-07-26 connectivity.tex
Pre-release version

@@
 For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the closed Mayer-Vietoris property.
+Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
 
@@
 
-Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$.
+Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$:
+while the $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the \emph{strong} $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
 If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.

### 2021-07-26 inequalities.tex
Pre-release version

@@
 This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $e$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, e)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is upper semi-continuous\footnote{A persistence module $M$ is \emph{upper semi-continuous} if $M_{t} \to \lim_{u > t} M_{u}$ is an isomorphism for all~$t$.}, correspond to the number of finite bars with length greater than $e$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $e$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, \epsilon)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
@@
 By \cref{thm:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
-In analogy to Morse's definitions, we may define the $(d, t, e)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
+In analogy to Morse's definitions, we may define the $(d, t, \epsilon)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \begin{equation*}
-m_{d}^{> e}(t) =
-\sum_{\substack{p \in \R \\ t - p > e}} \mathfrak{m}_{d-1}(p, t) +
-\sum_{\substack{q \in \R \\ q - t > e}} \mathfrak{m}_d(t, q).
+m_{d}^{\epsilon}(t) =
+\sum_{\substack{p \in \R \\ t - p > \epsilon}} \mathfrak{m}_{d-1}(p, t) +
+\sum_{\substack{q \in \R \\ q - t > \epsilon}} \mathfrak{m}_d(t, q).
 \end{equation*}
@@
 
-Whenever the sums below are well-defined, we also consider the \emph{$(d,e)$-cap numbers} 
+Whenever the sums below are well-defined, we also consider the \emph{$(d,\epsilon)$-cap numbers} 
 \begin{equation} \label{e:cap numbers}
-m_{d}^{> e } =
-\sum_{t} m_{d}^{> e}(t) \ =
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q) \ +
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q).
+m_{d}^{\epsilon} =
+\sum_{t} m_{d}^{\epsilon}(t) \ =
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q) \ +
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q).
 \end{equation} 
-They are well-defined for example if $M$ is the persistent homology of the sublevel set filtration of a bounded function.
+They are well-defined, for example, if $M$ is the persistent homology of the sublevel set filtration of a bounded function.
 This can be deduced from the following general result.
@@
     Assume that $N$ is a q-tame persistence module that is initially and eventually constant, i.e., that there exist $t_0$ and $t_1$ with $N_s = N_{t_0}$ for all $s \leq t_0$ and $N_u = N_{t_1}$ for all $u \geq t_1$, and let $\mathfrak{n}$ be the multiplicity function of the persistence diagram of $N$.
-    Then for each $e>0$ we have 
+    Then for each $\epsilon > 0$ we have 
     \begin{equation*}
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q) < \infty.
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \mathfrak{n} (p,q) < \infty.
     \end{equation*}
@@
     \begin{equation*}
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > e } } \mathfrak{n} (p,q)
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \mathfrak{n} (p,q)
     \ = \!\!
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
-    \ \ +
-    \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
+    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
+    \ +
+    \sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
     \end{equation*}
@@
     \begin{equation*}
-    \sum_{ \substack{ (p,q) \in T \\ q-p > e } } \mathfrak{n} (p,q)
+    \sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
     \ \, \leq \!\!
@@
     \end{equation*}
-    where $T^{\geq e}$ is the smaller triangle 
+    where $T^{\geq \epsilon}$ is the smaller triangle 
     \begin{equation*}
-    T^{\geq e} = \{(p,q) \in T \mid q-p \geq e\}.
+    T^{\epsilon} = \{(p,q) \in T \mid q-p \geq \epsilon\}.
     \end{equation*}
@@
     \begin{equation*}
-    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
+    \sum_{(p,q) \in T^{e}} \mathfrak{n} (p,q) 
     \ < \ 
@@
     \end{equation*}
-    Covering the compact set $T^{\geq e}$ by the open quadrants $Q \left(x, x + \frac{e}{2} \right)$ for $x \in \R$, we may choose a finite subcover given by, say, $x_1,\dots, x_n$.
+    Covering the compact set $T^{\epsilon}$ by the open quadrants $Q \left(x, x + \frac{\epsilon}{2} \right)$ for $x \in \R$, we may choose a finite subcover given by, say, $x_1,\dots, x_n$.
 	We obtain
@@
     \ \leq \
-    \sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{e}{2})}} \mathfrak{n}(p,q).
+    \sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{\epsilon}{2})}} \mathfrak{n}(p,q).
     \end{equation*}
-    Each of sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{e}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{e}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
+    Each of the sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{\epsilon}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{\epsilon}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
 \end{proof}
@@
 \begin{thm}\label{t:inequalities}
-	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{> e }$ and essential dimensions $p_{d}$ finite for all $d$ and $e$.
+	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{\epsilon}$ and essential dimensions $p_{d}$ finite for all $d$ and $\epsilon$.
 	If $\mathfrak{m}_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
     \begin{equation} \label{e:morse inequalities}
-    \sum_{d=0}^n \ (-1)^{n-d} (m^{>e}_{d} - p_{d}) \ \geq\  0
+    \sum_{d=0}^n \ (-1)^{n-d} (m^{\epsilon}_{d} - p_{d}) \ \geq\  0
     \end{equation}
-    for any dimension $n$ and any $e > 0$.
+    for any dimension $n$ and any $\epsilon > 0$.
 \end{thm}
@@
 \begin{proof}
-    Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
+    Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
     Since we assume $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, we have
     \begin{align*}
-    m^{>e}_{d}
+    m^{\epsilon}_{d}
     \ &=
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
     \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
     \\
     &=
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
     \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
     \end{align*}
@@
     \begin{align*}
-    m^{>e}_{d} - p_{d} \
+    m^{\epsilon}_{d} - p_{d} \
     &= 
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
     \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > e \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
     \ - \
@@
     &=
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }} \mathfrak{m}_{d-1}(p,q)
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
     \ + \!
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q),
+    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }}\mathfrak{m}_d(p,q),
     \end{align*}
-    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > e }}\mathfrak{m}_d(p,q)$ satisfies $m^{>e}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }}\mathfrak{m}_d(p,q)$ satisfies $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
@@
 As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions $f$ on closed smooth manifolds $X$.
-As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{>e} = \crit_d(f)$ for $e > 0$ smaller than the minimal difference between any two critical values of $f$.
+As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of $f$.
 
 The finiteness conditions of our theorem are also satisfied for the functionals that Morse considered in his work on functional topology, with q-tameness being guaranteed by \cref{t:strong local connectedness implies q-tameness} instead of the insufficient condition Morse proposed.
-As we have also mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also upper semi-continuous, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
-Note, however, that in contrast to Morse's version, our inequalities also work without the upper semi-continuity assumption, removing the need for this unusual choice of homology theory.
+As we have also mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
+Note, however, that in contrast to Morse's version, our inequalities also work without the assumption of continuity from above, expanding their use beyond \v{C}ech type theories.
 
@@
 	The usefulness of this notion might be limited though, because for example in the context of Floer theory, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.
-	In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable, because while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology, to which our inequalities may also be applied.
+	In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable, because while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology.
 \end{rem}

### 2021-07-26 introduction.tex
Pre-release version

@@
 Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
-Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940, MR9102} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
+Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
 He named this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
@@
 
-While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general, many of his ideas have resurfaced and flourished in other domains.
+While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly because, as Hildebrandt [4, p.
+324] puts it, ``Morse--Tompkins' original paper [is] unreadable and inaccessible for the non-specialist''---
+many of his ideas have resurfaced and flourished in other domains.
 In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \textit{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
@@
 
-The primary contribution of this work consists in the introduction of topological conditions for a broad class of filtered spaces ensuring their associated persistence homology modules satisfy Morse inequalities.
-As an application, we identify and fix with our conditions a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins.
+The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules satisfy Morse inequalities.
+As an application, we identify a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins and fix it with our results.
 

### 2021-07-26 main.tex
Pre-release version

@@
     Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at University of Notre Dame du Lac \at Max Planck Institute for Mathematics in Bonn \\ \email{ammedmar@mpim-bonn.mpg.de} 
+	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics \at University of Notre Dame du Lac \\ \email{ammedmar@mpim-bonn.mpg.de} 
 	\and

### 2021-07-26 persistence.tex
Pre-release version

@@
 
-In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions, applicable to functionals defined on a function or moduli space.
+In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions on general topological spaces.
 For a detailed exposition we refer to \cite{polterovich2020topological} and \cite{Chazal.2016a, MR3408277}.
@@
 commute for all pairs $s \leq t$.
+
 Since most examples of interest arise from applying a homology theory to a filtered space, we also consider \emph{graded persistence modules}, which are collections of persistence modules indexed by the integers.
-To ease the reading, in what follows we study persistence modules omitting the straightforward generalization of the developed concepts to graded persistence modules.
+To lighten the presentation of the theory of persistence, in what follows we will solely focus on persistence modules omitting straightforward generalizations to their graded counterparts.
 
@@
 Hence, understanding which persistence modules admit barcode decompositions is key.
+
 The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's \cite{Crawley-Boevey.2015}.
@@
 This can be formalized by constructing the \emph{observable category of persistence modules}, which is equivalent to the quotient of the category of persistence modules by the full sub-category of ephemeral persistence modules.
-Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
 The barcode of the radical of a q-tame persistence module $M$ is then a complete invariant of $M$ in the observable category.
 
-Instead of talking about the barcode of the radical of a q-tame persistence module, it will be more convenient for our treatment of Morse inequalities to talk about the \emph{(undecorated) persistence diagram} associated to a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which is the multiset defined by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
+Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
+One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{schmahl2020structure}, which is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology.
+In terms of barcodes, continuity from above amounts to only admitting intervals that are closed on the left and open on the right.
+One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities later on.
+% When forgetting the endpoints of the intervals in the barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$ of a persistence module with an interval decomposition, i.e., when disregarding the distinction between open, closed and half-open intervals, we obtain a discrete invariant that is more convenient in many regards, including the formulation of generalized Morse inequalities.
+Defined precisely, this invariant known as the \textit{persistence diagram} is the multiset given by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
 \begin{equation*}
@@
 the cardinality of the set $\{ \lambda \in \Lambda \mid \inf I_{\lambda} = p,\ \sup I_{\lambda} = q\}$.
-
-Two q-tame barcode modules are observably isomorphic if and only if their persistence diagrams agree, so the persistence diagram associated to the barcode of $\rad M$ is still a complete invariant of the q-tame persistence module $M$ in the observable category.
-We summarize:
+Because information about the endpoints of intervals is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete for q-tame modules in the observable category.
+% and suffices to recover the barcode in many cases of interest.
+Stated explicitly, we have the following.
 

### 2021-07-26 surfaces.tex
Pre-release version

@@
 \section{Minimal surfaces and functional topology} \label{s:surfaces}
+
+After having presented Morse inequalities in terms of persistence diagrams and having developed topological conditions for existence of persistence diagrams associated to filtrations, we will now connect these previous results to the work of Morse and Tompkins on minimal surfaces from \cite{Morse.1939}.
+We will focus on the homological aspects of their approach.
+For a general exposition we refer to \cite[Sections 4.3-5]{Bott.1980}, and for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}.
 
@@
 
-In \cite[p.445]{Morse.1939}, Morse and Tompkins introduce for any metric space $M$ and $F \colon M \to \R$ a homotopical version of critical point.
+In \cite[p.~445]{Morse.1939}, Morse and Tompkins introduce a homotopical notion of critical point for any metric space $M$ and $F \colon M \to \R$.
 Roughly, a point $p$ is \textit{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
 
-Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, i.e., a minimal surface.
-They then use a form of Morse inequalities for homotopically critical points to infer their Unstable Minimal Surface Theorem:
-\begin{itemize}
-    \item[($\ast$)] If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely a critical point of $A_g$ of index 1.
-\end{itemize}
+Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, i.e., a minimal surface, and use this correspondence to prove the following result \cite[p.~447]{Morse.1939}, also reviewed as Theorem 6.10 in \cite{Struwe.1988}.
 
-They infer Morse inequalities for homotopically critical points by relating these points to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
+\begin{thm}[Unstable Minimal Surface Theorem]
+    If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely, a critical point of $A_g$ of index 1.
+\end{thm}
+
+Their proof relies on Morse inequalities for homotopically critical points which they infer by relating them to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
 
@@
 Throughout his work on functional topology, in order to obtain \mbox{q-tameness}, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations.
-In particular, in their applications to minimal surface theory, Morse and Tompkins use the following condition:
+In particular, in their applications to minimal surface theory, Morse and Tompkins used the following condition:
 \begin{displaycquote}[p.~431]{Morse.1940}
@@
 \begin{defi}
-    The sublevel set filtration of a function $F \colon M \to \R$ is said to be \emph{homotopically locally connected} or $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
+    The sublevel set filtration of a function $f \colon M \to \R$ is said to be \emph{homotopically locally connected} or $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with  $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
 \end{defi}
 
-It is then stated that as a consequence of local $F$-connectivity the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
+Morse then goes on to state that as a consequence of local $F$-connectivity the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
 In the original it reads:
-
 \begin{displaycquote}[Theorem 6.3, p.~432]{Morse.1940}
@@
 Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
-Unfortunately, this claim does not hold in general, as we will show next by providing an explicit counterexample.
+Unfortunately, the above claim does not hold in general, as we will show next by providing an explicit counterexample.
 
@@
 
-Consider the \textit{$d$-dimensional Hawaiian earring}
+We will consider the \textit{$d$-dimensional Hawaiian earring}
 \begin{equation*}
-\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\}.
+\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
 \end{equation*}
+which is a compact subspace of $\R^{d+1}$.
 
@@
 \begin{proof}
-    \todo{needs to be rewritten with the new s, t notation instead of the epsilon, delta notation}
-	The space $\HE$ is Hausdorff %and locally compact
-	since $\R^{d+1}$ is.
-	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact spaces.
-	Let us now verify that the sublevel set filtration of $f$ is $\LC$.
-	Let $\epsilon > 0$ and $x \in \HE$.
-	If $x$ is the origin, we choose $\delta$ between $0$ and the minimum of $\epsilon$ and $1$.
-	Then $\HE_{\leq f(x) + \delta} = \HE_{\leq \delta} = \{x\}$, so the weak $\LC$ condition is trivially satisfied.
-	For $x$ not the origin, there is a unique $d$-sphere in $\HE$ that contains it.
-	Clearly, we may choose $\delta > 0$ so small that $D_\delta(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a disk contained in this sphere, so $D_\delta(x)$ can be contracted to $\{x\}$ and the weak $\LC$ condition again follows trivially.
-	What remains to be shown is that $\HE_{\leq \bullet}$ is not q-tame for $\H$.
-This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$ because $\HE_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
+
+	Let us now verify that the sublevel set filtration of $f$ is $\LC$, so
+	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
+We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+
+	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
+	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\LC$ condition is trivially satisfied.
+
+	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$. 
+	Note that because $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains it.
+	Clearly, we may choose $\delta > 0$ so small that $D_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a disk contained in this sphere and contained in $V$. 
+	The disk $D_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = D_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+
+	What remains to be shown is that $f_{\leq \bullet}$ is not q-tame for $\H$.
+    This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$ because $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
 \end{proof}
@@
 Morse also claims in the given reference that this condition is sufficient for q-tameness, but without providing a proof.
-We expect this statement to be true, but do not investigate it further.
+Whether this statement is true or not is not covered by our analysis, because the $\piLC$ and $\HLC$ conditions generally do not imply each other.
+We expect the quoted claim to be true, but do not investigate it further.

### 2021-07-26 connectivity.tex
Improve code

@@
 For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{MR0050886}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
+Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
 
-\begin{defi} \label{defi:local_connectedness}
-	For $n \in \Z$ a continuous map is said to be \textit{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
+\begin{defi}
+	For $n \in \Z$ a continuous map is said to be \emph{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
 	We omit references to $n$ if the condition holds for all integers.
@@
 
-\begin{defi} \label{defi:local_connectedness_filtrations}
+\begin{defi}
 	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
+
 Similarly, we have the following stronger version of this property.
+
 \begin{defi}
@@
 
-\begin{thm}\label{thm:hlc_to_strong_hlc}
+\begin{thm} \label{t:hlc to strong hlc}
 	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is $\HLC$, then it is also strongly $\HLC$.
 \end{thm}
+
 \begin{proof}
@@
 
-\begin{lem}\label{l: restriction of LHS filtration}
+\begin{lem} \label{l:restriction of LHS filtration}
 	Let $f \colon X \to \R$ be a function whose sublevel set filtration is strongly $\HLC$.
@@
 
-    We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with 
-	$\overline{V} \subseteq U \subseteq L$
-	for which there exists $s' \in (s,\, t)$ such that the inclusion
-    $U \cap f_{\leq s'} \to L \cap f_{\leq t}$
-	is $\HS_n$.
+	We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$	for which there exists $s' \in (s,\, t)$ such that the inclusion $U \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$.
 	We will show that $\Sigma_{s, t}$ has the following three properties:
@@
 		 \item Any point $x \in L \cap f_{\leq s}$ has a neighborhood $V_x \in \Sigma_{s,t}$.
-	    \item If $V_1,\, V_2 \in \Sigma_{s,t}$, then $V_1 \cup V_2 \in \Sigma_{s,t}$.
+		 \item If $V_1,\, V_2 \in \Sigma_{s,t}$ then $V_1 \cup V_2 \in \Sigma_{s,t}$.
 		 \item For each $V \in \Sigma_{s,t}$ the inclusion 
-	    $V \cap f_{\leq s} \to L \cap f_{\leq t}$ 
-	    is $\HS_n$.
+		 $V \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS_n$.
 	\end{enumerate}
@@
 	Choose $u \in \R$ with $u > t$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y=f_{\leq u}$. 
-    Since we assume $f$ to induce a strongly $\HLC$ sublevel set filtration, by \cref{l: restriction of LHS filtration} the sublevel set filtration of $g$ is strongly $\HLC$ below $u$. 
+	Since we assume $f$ to induce a strongly $\HLC$ sublevel set filtration, by \cref{l:restriction of LHS filtration} the sublevel set filtration of $g$ is strongly $\HLC$ below $u$. 
 	Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.
@@
 
-Combining \cref{thm:hlc_to_strong_hlc} with \cref{t:strong local connectedness implies q-tameness} also yields the following result for continuous functions.
+Combining \cref{t:hlc to strong hlc} with \cref{t:strong local connectedness implies q-tameness} also yields the following result for continuous functions.
 
-\begin{cor}\label{c: q-tameness for continuous functions}
+\begin{cor} \label{c:q-tameness for continuous functions}
 	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and $\HLC$, then it is also q-tame.

### 2021-07-26 inequalities.tex
Improve code

@@
 In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse and Tompkins to prove their Unstable Minimal Surface Theorem.
-We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{thm:q-tame modules have barcodes}.
+We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{t:q-tame modules have barcodes}.
 
 Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any non-negative integer $n$ the following holds:
-\begin{equation} \label{equ:morse_inequalities}
-\sum_{d=0}^n \ (-1)^{n-d} ( \# \crit_{d}(f) - \beta_{d}(X) ) \ \geq\  0,  
+\begin{equation} \label{e:morse_inequalities}
+\sum_{d=0}^n \ (-1)^{n-d} \big( \# \crit_{d}(f) - \beta_{d}(X) \big) \ \geq \ 0,
 \end{equation}
@@
 This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, \epsilon)$-\textit{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
@@
 Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
-By \cref{thm:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\mathfrak{m}_d \colon \multiplicityDomain \to \N$.
-In analogy to Morse's definitions, we may define the $(d, t, \epsilon)$-\textit{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
+By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\m_d \colon \multiplicityDomain \to \N$.
+In analogy to Morse's definitions, we may define the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \begin{equation*}
 m_{d}^{\epsilon}(t) =
-\sum_{\substack{p \in \R \\ t - p > \epsilon}} \mathfrak{m}_{d-1}(p, t) +
-\sum_{\substack{q \in \R \\ q - t > \epsilon}} \mathfrak{m}_d(t, q).
+\sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) +
+\sum_{\substack{q \in \R \\ q - t > \epsilon}} \m_d(t, q).
 \end{equation*}
@@
 \sum_{t} m_{d}^{\epsilon}(t) \ =
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q) \ +
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q).
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
+\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q).
 \end{equation} 
@@
 \begin{thm}
-    Assume that $N$ is a q-tame persistence module that is initially and eventually constant, i.e., that there exist $t_0$ and $t_1$ with $N_s = N_{t_0}$ for all $s \leq t_0$ and $N_u = N_{t_1}$ for all $u \geq t_1$, and let $\mathfrak{n}$ be the multiplicity function of the persistence diagram of $N$.
+	Assume that $N$ is a q-tame persistence module that is initially and eventually constant, i.e., that there exist $t_0$ and $t_1$ with $N_s = N_{t_0}$ for all $s \leq t_0$ and $N_u = N_{t_1}$ for all $u \geq t_1$, and let $\n$ be the multiplicity function of the persistence diagram of $N$.
 	Then for each $\epsilon > 0$ we have 
 	\begin{equation*}
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \mathfrak{n} (p,q) < \infty.
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q) < \infty.
 	\end{equation*}
@@
 	\begin{equation*}
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \mathfrak{n} (p,q)
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q)
 	\ = \!\!
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \n (p,q)
 	\ +
-    \sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
+	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \n (p,q)
 	\end{equation*}
@@
 
-    For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\mathfrak{n}(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
+	For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
 	This implies 
 	\begin{equation*}
-    \sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \mathfrak{n} (p,q)
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \n (p,q)
 	\ = \!
-    \sum_{t_0 < q < t_1} \mathfrak{n} (-\infty,q)
+	\sum_{t_0 < q < t_1} \n (-\infty,q)
 	\ + \!
-    \sum_{t_0 < p < t_1} \mathfrak{n} (p, \infty)
+	\sum_{t_0 < p < t_1} \n (p, \infty)
 	\end{equation*}
@@
 	\begin{equation*}
-    \sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \mathfrak{n} (p,q)
+	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \n (p,q)
 	\ \, \leq \!\!
-    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q),
+	\sum_{(p,q) \in T^{\geq e}} \n (p,q),
 	\end{equation*}
@@
 	\begin{equation*}
-    \sum_{(p,q) \in T^{e}} \mathfrak{n} (p,q) 
+	\sum_{(p,q) \in T^{e}} \n (p,q) 
 	\ < \ 
@@
 	\begin{equation*}
-    \sum_{(p,q) \in T^{\geq e}} \mathfrak{n} (p,q) 
+	\sum_{(p,q) \in T^{\geq e}} \n (p,q) 
 	\ \leq \
-    \sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{\epsilon}{2})}} \mathfrak{n}(p,q).
+	\sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{\epsilon}{2})}} \n(p,q).
 	\end{equation*}
-    Each of the sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{\epsilon}{2} \right)} \mathfrak{n}(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{\epsilon}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
+	Each of the sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{\epsilon}{2} \right)} \n(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{\epsilon}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
 \end{proof}
@@
 \begin{equation} \label{e:essential dimension}
-p_{d} \ = \!\! \sum_{p \in \R \cup \{-\infty\}} \mathfrak{m}_d(p,\infty),
+p_{d} \ = \!\! \sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty),
 \end{equation}
@@
 
-\begin{thm}\label{t:inequalities}
+\begin{thm} \label{t:inequalities}
 	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{\epsilon}$ and essential dimensions $p_{d}$ finite for all $d$ and $\epsilon$.
-	If $\mathfrak{m}_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
+	If $\m_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
 	\begin{equation} \label{e:morse inequalities}
@@
 	Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
-    Since we assume $\mathfrak{m}_d(-\infty, p) = 0$ for all $p$, we have
+	Since we assume $\m_d(-\infty, p) = 0$ for all $p$, we have
 	\begin{align*}
-    m^{\epsilon}_{d}
-    \ &=
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \mathfrak{m}_{d-1}(p,q)
-    \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
-    \\
-    &=
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
-    \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
+	m^{\epsilon}_{d}\ &=
+	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
+	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \\ &=
+	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon }} \m_{d-1}(p,q) \ +
+	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)
 	\end{align*}
@@
 	\begin{equation*}
-    p_{d}
-    \ = \!\!
-    \sum_{p \in \R \cup \{-\infty\}} \mathfrak{m}_d(p,\infty)
-    \ = \
-    \sum_{p \in \R} \mathfrak{m}_d(p,\infty),
+	p_{d} \ = \!\!
+	\sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty) \ = \
+	\sum_{p \in \R} \m_d(p,\infty),
 	\end{equation*}
@@
 	\begin{align*}
-    m^{\epsilon}_{d} - p_{d} \
-    &= 
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
-    \ +
-    \sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\mathfrak{m}_d(p,q)
-    \ - \
-    \sum_{p \in \R} \mathfrak{m}_d(p,\infty)
-    \\
-    &=
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }} \mathfrak{m}_{d-1}(p,q)
+	m^{\epsilon}_{d} - p_{d} \ &= 
+	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q) \ +
+	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)	\ - \
+	\sum_{p \in \R} \m_d(p,\infty) \\	&=
+	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q)
 	\ + \!
-    \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }}\mathfrak{m}_d(p,q),
+	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q),
 	\end{align*}
-    so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q - p > \epsilon }}\mathfrak{m}_d(p,q)$ satisfies $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
@@
 As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions $f$ on closed smooth manifolds $X$.
-As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{equ:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of $f$.
+As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of $f$.
 

### 2021-07-26 introduction.tex
Improve code

@@
 Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also be regarded.
-Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{MR0163331}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold, which notably goes beyond the compact setting.
-Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{MR1702944}.
+Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{Milnor.1963}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold, which notably goes beyond the compact setting.
+Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{Salamon.1999}.
 Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
@@
 many of his ideas have resurfaced and flourished in other domains.
-In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \textit{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
+In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
 Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.
 
-The homology of a filtered space is an example of what is called a \textit{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
-In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as its \textit{persistence diagram}.
+The homology of a filtered space is an example of what is called a \emph{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
+In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as its \emph{persistence diagram}.
 
@@
 One of the primary reasons for this is the fact that persistence diagrams can be organized into a metric space, often allowing to recast geometric questions about general filtered spaces in a combinatorial metric model.
-This is because the passage via the homology construction to this metric space is Lipschitz, a statement commonly known as the \textit{stability} of persistence diagrams.
+This is because the passage via the homology construction to this metric space is Lipschitz, a statement commonly known as the \emph{stability} of persistence diagrams.
 
-The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he developed the theory of \textit{caps} and their \textit{spans}, capturing much of the same information as the modern notion of persistence diagram, including concepts such as the persistence or birth-death of a topological feature.
+The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he developed the theory of \emph{caps} and their \emph{spans}, capturing much of the same information as the modern notion of persistence diagram, including concepts such as the persistence or birth-death of a topological feature.
 Morse used his theory of caps to study functionals on a metric space by analyzing the evolution of the topology of their sublevel sets.
@@
 Given the importance of persistence diagrams for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
-For general persistence modules, a well studied condition for the existence of persistence diagrams is \textit{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite dimensional rank.
+For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite dimensional rank.
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
@@
 Contrary to these claims, we show that the local connectivity condition used by Morse and Tompkins in the proof of the Unstable Minimal Surface Theorem is insufficient (\cref{c: counterexample}).
-We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c: q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:strong local connectedness implies q-tameness}).
+We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:strong local connectedness implies q-tameness}).
 Since Douglas' functional has compact sublevel sets but is not continuous in the $C^0$ topology, which Morse and Tompkins considered, we use this second condition to correct their proof.

### 2021-07-26 main.tex
Improve code

@@
 \renewcommand{\th}{^{\mathrm{th}}}
+\newcommand{\m}{\mathfrak{m}}
+\newcommand{\n}{\mathfrak{n}}
 \newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}
@@
 	Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics \at University of Notre Dame du Lac \\ \email{ammedmar@mpim-bonn.mpg.de} 
-	\and
+	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics \at University of Notre Dame du Lac \\ \email{ammedmar@mpim-bonn.mpg.de} \and
 	Maximilian~Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg.de}

### 2021-07-26 persistence.tex
Improve code

@@
 In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions on general topological spaces.
-For a detailed exposition we refer to \cite{polterovich2020topological} and \cite{Chazal.2016a, MR3408277}.
+For a detailed exposition we refer to \cite{Polterovich.2020} and \cite{Chazal.2016a, Oudot.2015}.
 
 The ``pipeline'' of topological persistence traverses through geometry, algebra and discrete mathematics as follows:
-Given a space $X$ filtered by the sublevel sets of a function $f$, the application of some homology theory in degree $n$ with coefficients in a field,  or, more generally, a functor from topological spaces to vector spaces, produces a \textit{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \textit{persistence diagram}.
+Given a space $X$ filtered by the sublevel sets of a function $f$, the application of some homology theory in degree $n$ with coefficients in a field, or, more generally, a functor from topological spaces to vector spaces, produces a \emph{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \emph{persistence diagram}.
 
@@
 Unless noted otherwise, the functions we consider need not be continuous.
-We pass to filtered spaces by considering the \textit{sublevel set filtration $f_{\leq \bullet}$ of $X$ induced by $f$}, which is defined by
+We pass to filtered spaces by considering the \emph{sublevel set filtration $f_{\leq \bullet}$ of $X$ induced by $f$}, which is defined by
 \begin{equation*}
@@
 \end{equation*}
-We say that this filtration is \textit{compact} if all sublevel sets are compact Hausdorff spaces.
+We say that this filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
 
@@
 Key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
-Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{MR0050886} with coefficients in $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{MR0050886}, such as singular homology, again with coefficients in $\F$ \cite{Eilenberg.1944}.
+Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{Eilenberg.1952} with coefficients in $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{Eilenberg.1952}, such as singular homology, again with coefficients in $\F$ \cite{Eilenberg.1944}.
 
@@
 \end{cases}
-    \qquad
-    \qquad
+\qquad \qquad
 C(I)_{s, t} =
 \begin{cases}
-    \operatorname{id}_{\mathbb{F}} & \text{if } s, t \in I,\\
+\operatorname{id}_{\mathbb{F}} & \text{if } s, t \in I, \\
 0 & \text{otherwise}.
@@
 These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of interval modules.
-Given a barcode module $\bigoplus_{\lambda \in \Lambda} C(I_{\lambda})$, the associated multiset of intervals $\{I_{\lambda}\}_{\lambda \in \Lambda}$ is known as its \textit{barcode}.
-By a version of the Krull--Remak--Schmidt--Azumaya Theorem \cite{MR37832} (see also \cite[Theorem 2.7]{Chazal.2016a} for a specialization to barcode modules), two isomorphic barcode modules have the same barcodes up to a choice of the index set $\Lambda$.
+Given a barcode module $\bigoplus_{\lambda \in \Lambda} C(I_{\lambda})$, the associated multiset of intervals $\{I_{\lambda}\}_{\lambda \in \Lambda}$ is known as its \emph{barcode}.
+By a version of the Krull--Remak--Schmidt--Azumaya Theorem \cite{Azumaya.1950} (see also \cite[Theorem 2.7]{Chazal.2016a} for a specialization to barcode modules), two isomorphic barcode modules have the same barcodes up to a choice of the index set $\Lambda$.
 Thus, if a persistence module $M$ is provided with an isomorphism to a barcode module, referred to as a \emph{barcode decomposition}, the associated barcode is a complete isomorphism invariant of $M$.
@@
 As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
-Yet, there are multiple ways to regularize q-tame persistence modules to obtain discrete invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, schmahl2020structure}.
+Yet, there are multiple ways to regularize q-tame persistence modules to obtain discrete invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
 We briefly recall the approach from \citet{Chazal.2016b}.
@@
 Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
-One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{schmahl2020structure}, which is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology.
+One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}, which is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology.
 In terms of barcodes, continuity from above amounts to only admitting intervals that are closed on the left and open on the right.
@@
 % When forgetting the endpoints of the intervals in the barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$ of a persistence module with an interval decomposition, i.e., when disregarding the distinction between open, closed and half-open intervals, we obtain a discrete invariant that is more convenient in many regards, including the formulation of generalized Morse inequalities.
-Defined precisely, this invariant known as the \textit{persistence diagram} is the multiset given by the \emph{multiplicity function} $\mathfrak{m} \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
+Defined precisely, this invariant known as the \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
 \begin{equation*}
@@
 
-\begin{thm}[{{\citet{Chazal.2016a,Chazal.2016b}}}] \label{thm:q-tame modules have barcodes}
+\begin{thm}[\citet{Chazal.2016a, Chazal.2016b}] \label{t:q-tame modules have barcodes}
 	Every q-tame persistence module has a unique persistence diagram that completely describes its isomorphism type in the observable category.
@@
 As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: From functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistence modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).
-In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{10.1145/1542362.1542407,Chazal.2016a,MR3333456, MR2279866}.
+In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{Chazal.2009, Chazal.2016a, Bauer.2015, Cohen-Steiner.2007}.

### 2021-07-26 surfaces.tex
Improve code

@@
 In \cite[p.~445]{Morse.1939}, Morse and Tompkins introduce a homotopical notion of critical point for any metric space $M$ and $F \colon M \to \R$.
-Roughly, a point $p$ is \textit{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
+Roughly, a point $p$ is \emph{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
 
@@
 \begin{displaycquote}[p.~431]{Morse.1940}
-	The space $M$ is said to be \textit{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
+	The space $M$ is said to be \emph{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
 \end{displaycquote}
@@
 
-We will consider the \textit{$d$-dimensional Hawaiian earring}
+We will consider the \emph{$d$-dimensional Hawaiian earring}
 \begin{equation*}
@@
 	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
-	\label{fig:earrings}
 \end{figure}
 
-\begin{thm} \label{thm:counterexample}
+\begin{thm} \label{t:counterexample}
 	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is not finite dimensional for some $n$.
@@
 
-Both singular and \v{C}ech homology of the Hawaiian earring are infinite dimensional in some degree, so they satisfy the assumptions of \cref{thm:counterexample}.
-The singular case is treated in \cite{Barratt.1962}, and for \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{MR0050886}:
+Both singular and \v{C}ech homology of the Hawaiian earring are infinite dimensional in some degree, so they satisfy the assumptions of \cref{t:counterexample}.
+The singular case is treated in \cite{Barratt.1962}, and for \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{Eilenberg.1952}:
 Define 
 \begin{align*}
-\HE_k &= \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\
-& \cup \bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle|\  \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right \},
+\HE_k &=
+\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\cup
+\bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
 \end{align*}
@@
 
-\begin{cor}\label{c: counterexample}
+\begin{cor} \label{c: counterexample}
 	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.

### 2021-07-26 vietoris.tex
Improve code

@@
 
-First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{MR0050886}.
+First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{Eilenberg.1952}.
 Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation. 
@@
 
-If $X$ is a metric space, this is still not exactly the same as the construction of metric Vietoris homology presented in \cite{MR1512371} and used by Morse, which in modern notation is the limit
+If $X$ is a metric space, this is still not exactly the same as the construction of metric Vietoris homology presented in \cite{Vietoris.1927} and used by Morse, which in modern notation is the limit
 \begin{equation*}

### 2021-07-26 abstract.tex
Split off the abstract

--- 2021-07-26 main.tex
@@
-\documentclass[nospthms, a4paper, final]{svjour3}
-\setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}
-\setlength{\textheight}{\dimexpr\pdfpageheight-2.4in}
-\usepackage{mathptmx}
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{tikz-cd}
-\usepackage[numbers,sort,compress]{natbib}
-\usepackage{graphicx}
-\usepackage{csquotes}
-\usepackage[bookmarks=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=true,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	linktocpage,
-	colorlinks,
-	citecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue}
-\usepackage[capitalize, noabbrev]{cleveref}
-\usepackage{todo}
-
-% theorems
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\Crefname{thm}{Theorem}{Theorems}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\Crefname{prop}{Proposition}{Propositions}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{conj}[thm]{Conjecture}
-\Crefname{conj}{Conjecture}{Conjectures}
-\theoremstyle{definition}
-\newtheorem{defi}[thm]{Definition}
-\newtheorem{ex}[thm]{Example}
-\newtheorem{rem}[thm]{Remark}
-
-% commands
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\F}{\mathbb{F}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\HS}{\mathrm{HS}}
-\newcommand{\HT}{\mathrm{HT}}
-\newcommand{\HLC}{\mathrm{LHS}}
-\newcommand{\piT}{\pi\mathrm{T}}
-\newcommand{\LC}{\mathrm{LC}}
-\newcommand{\NH}{\mathrm{NH}}
-\newcommand{\piLC}{\pi\mathrm{LC}}
-\newcommand{\HE}{\mathbb{H}^d}
-\renewcommand{\H}{H}
-\DeclareMathOperator{\interior}{int}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\coker}{coker}
-\DeclareMathOperator{\rad}{rad}
-\newcommand\CH{\check{H}}
-\newcommand{\Mod}[1]{#1-\mathbf{Mod}}
-\newcommand{\PFD}{\mathrm{PFD}}
-\newcommand{\PFG}{\mathrm{PFG}}
-\DeclareMathOperator{\Nrv}{Nrv}
-\DeclareMathOperator{\Cov}{Cov}
-\DeclareMathOperator{\Vietoris}{Vtr}
-\DeclareMathOperator{\Balls}{Balls}
-\DeclareMathOperator*{\colim}{colim}
-\DeclareMathOperator{\crit}{crit}
-\newcommand\MCH{M\check{H}}
-\newcommand\VH{VH}
-\newcommand\MVH{MVH}
-\newcommand{\obs}{\dashrightarrow}
-\newcommand{\multiplicityDomain}{\mathcal{E}}
-\newcommand{\Top}{\mathsf{Top}}
-\newcommand{\Vect}{\mathsf{Vect}}
-\renewcommand{\th}{^{\mathrm{th}}}
-\newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}
-
-\begin{document}
-
-\title{Persistence in functional topology and a correction to a theorem of Morse}
-
-\author{Ulrich Bauer \and Anibal M.~Medina-Mardones \and Maximilian~Schmahl}
-
-\institute{
-    Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics \at University of Notre Dame du Lac \\ \email{ammedmar@mpim-bonn.mpg.de} 
-	\and
-	Maximilian~Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg.de}
-}
-
-\authorrunning{U.~Bauer, A.~Medina-Mardones, M.~Schmahl}
-
-\maketitle
-
-\begin{abstract}
 During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
@@
 As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
-\end{abstract}
-
-\tableofcontents
-\input{introduction}
-\input{persistence}
-\input{inequalities}
-\input{connectivity}
-\input{surfaces}
-\appendix
-\input{vietoris}
-
-\section*{Acknowledgements}
-This research has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}, the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
-
-A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL, where part of this work developed.
-
-\bibliographystyle{abbrvnaturl}
-\bibliography{biblio}
-
-\end{document}

### 2021-07-26 main.tex
Split off the abstract

@@
 \usepackage[capitalize, noabbrev]{cleveref}
-\usepackage{todo}
 
@@
 \begin{abstract}
-	During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
-	Morse and Tompkins applied this body of work, referred to as functional topology, to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem.
-	Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics.
-	In this article, we provide a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
-	We adjust several key definitions and prove stronger statements, including a generalized version of Morse inequalities, in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
-	As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
+	\input{abstract}
 \end{abstract}

### 2021-07-26 introduction.tex
Remove unused commands

@@
 
-While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly because, as Hildebrandt [4, p.
+While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly in part because, as Hildebrandt [4, p.
 324] puts it, ``Morse--Tompkins' original paper [is] unreadable and inaccessible for the non-specialist''---

### 2021-07-29 abstract.tex
Overleaf version to post

@@
 In this article, we provide a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
-We adjust several key definitions and prove stronger statements, including a generalized version of Morse inequalities, in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
-As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem of Morse and Tompkins.
+We adjust several key definitions and prove stronger statements, including a generalized version of the Morse inequalities, in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
+As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem by Morse and Tompkins.

### 2021-07-29 connectivity.tex
Overleaf version to post

@@
-\section{Persistence diagrams from local connectivity} \label{s:connectivity}
+% \section{Sufficient conditions for the existence of persistence diagrams} \label{s:connectivity}
+
+\section{Existence of persistence diagrams} \label{s:connectivity}
 
 We have seen that q-tame functions admit persistence diagrams, which can be used to formulate Morse inequalities.
-With q-tameness being a rather abstract condition, we now establish more concrete topological conditions that ensure the q-tameness of a function.
+With q-tameness being a rather abstract condition, we now establish concrete topological requirements that ensure the q-tameness of a function.
 Our definitions are motivated by similar conditions that Morse considered in his work on functional topology.
@@
 Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
-A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps fit in a long exact sequence
+A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
 \begin{equation*}
@@
 For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which, like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}, has the open Mayer-Vietoris property, and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
+Note that this includes singular homology with field coefficients, which has the open Mayer-Vietoris property (like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
 
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally homologically small} or $\HLC$ if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{%strongly
+	locally homologically small} or \emph{%strongly
+	$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
 
-Similarly, we have the following stronger version of this property.
+Similarly, we have the following weaker version of this property.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{strongly locally homologically small} or \emph{strongly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
 
-Clearly, any strongly $\HLC$ sublevel set filtration is also $\HLC$:
-while the $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the \emph{strong} $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
+Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
+while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the %\emph{strong} 
+$\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
 If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
 
-\begin{thm} \label{t:hlc to strong hlc}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is $\HLC$, then it is also strongly $\HLC$.
+\begin{thm} \label{t:weak hlc to hlc}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also %strongly 
+	$\HLC$.
 \end{thm}
@@
 
-	To do so, we start by using the $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
+	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
 	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
@@
 
-As our main result, we will now show that for compact sublevel set filtrations the strong $\HLC$ condition implies \mbox{q-tameness}, and consequently also implies the existence of a persistence diagram which yields persistent Morse inequalities.
+As our main result we will show now that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
 
-\begin{thm} \label{t:strong local connectedness implies q-tameness}
-	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and strongly $\HLC$, then it is also q-tame.
+\begin{thm} \label{t:local connectedness implies q-tameness}
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
 \end{thm}
 
-The general proof strategy is inspired by the proof of a result attributed to Wilder as presented by Bredon \cite[Section II.17]{Bredon.1997}.
+The general proof strategy is inspired by the proof of a result attributed to Wilder \cite[p.~325]{Wilder.1949}, as presented by Bredon \cite[Section II.17]{Bredon.1997}.
 We collect the main ideas in several lemmas.
@@
 We want to use \cref{l:neighborhood third} on the domain of the function whose sublevel set filtration we consider.
-However, we do not want to assume the domain to be locally compact for \cref{t:strong local connectedness implies q-tameness}.
+However, we do not want to assume the domain to be locally compact for \cref{t:local connectedness implies q-tameness}.
 To circumvent this, we will work in one of the sublevel sets, which are assumed to be compact Hausdorff and hence locally compact.
-This requires the use of a slight weakening of the strong $\HLC$ condition.
+This requires the use of a slight weakening of the $\HLC$ condition.
 
 \begin{defi}
-	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{strongly $\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{%strongly
+	$\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 \begin{lem} \label{l:restriction of LHS filtration}
-	Let $f \colon X \to \R$ be a function whose sublevel set filtration is strongly $\HLC$.
+	Let $f \colon X \to \R$ be a function whose sublevel set filtration is %strongly 
+	$\HLC$.
 	Fix $u \in \R$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y = f_{\leq u}$.
-	Then, the sublevel set filtration defined by $g$ is strongly $\HLC$ below $u$.
+	Then the sublevel set filtration defined by $g$ is %strongly 
+	$\HLC$ below $u$.
 \end{lem}
@@
 	Since $Y \subseteq X$ carries the subspace topology, we may choose a neighborhood $V'$ of $x$ in $X$ such that $V = V' \cap Y$. 
-	The sublevel set filtration of $f$ is assumed to be strongly $\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
+	The sublevel set filtration of $f$ is assumed to be %strongly 
+	$\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
 	We set $U = U' \cap Y$, which defines a neighborhood of $x$ in $Y$.
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and strongly $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and %strongly 
+	$\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
 	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
@@
 
-	Next, we will show using the strong $\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	Next, we will show using the %strong 
+	$\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
 	Choose an arbitrary $s' \in (s,\, t)$.
-	Since the sublevel set filtration of $f$ is strongly $\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
+	Since the sublevel set filtration of $f$ is %strongly
+	$\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
 	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
@@
 
-We can now complete the proof of the claim stating that for compact sublevel set filtrations, strong $\HLC$ implies q-tameness.
+We can now complete the proof of the claim stating that for compact sublevel set filtrations, %strong 
+$\HLC$ implies q-tameness.
 
-\begin{proof}[Proof of \cref{t:strong local connectedness implies q-tameness}]
+\begin{proof}[Proof of \cref{t:local connectedness implies q-tameness}]
 	By definition, the sublevel set filtration of $f$ is q-tame if and only if the inclusion $f_{\leq s} \to f_{\leq t}$ is $\HS$ for all pairs $s < t$. 
 	Choose $u \in \R$ with $u > t$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y=f_{\leq u}$. 
-	Since we assume $f$ to induce a strongly $\HLC$ sublevel set filtration, by \cref{l:restriction of LHS filtration} the sublevel set filtration of $g$ is strongly $\HLC$ below $u$. 
+	Since we assume $f$ to induce a %strongly 
+	$\HLC$ sublevel set filtration, by \cref{l:restriction of LHS filtration} the sublevel set filtration of $g$ is %strongly 
+	$\HLC$ below $u$. 
 	Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.
@@
 
-Combining \cref{t:hlc to strong hlc} with \cref{t:strong local connectedness implies q-tameness} also yields the following result for continuous functions.
+Combining \cref{t:weak hlc to hlc} with \cref{t:local connectedness implies q-tameness} also yields the following result for continuous functions.
 
 \begin{cor} \label{c:q-tameness for continuous functions}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and $\HLC$, then it is also q-tame.
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
 \end{cor}

### 2021-07-29 inequalities.tex
Overleaf version to post

@@
-\section{Generalized Morse inequalities from persistence diagrams} \label{s:inequalities}
+\section{Generalized Morse inequalities} \label{s:inequalities}
 
@@
 \end{equation}
-They are well-defined, for example, if $M$ is the persistent homology of the sublevel set filtration of a bounded function.
-This can be deduced from the following general result.
+An important setting where all cap numbers are well-defined is when $M$ is the persistent homology of the sublevel set filtration of a bounded function.
+A more general statement can be made using the following notion.
 
-\begin{thm}
-	Assume that $N$ is a q-tame persistence module that is initially and eventually constant, i.e., that there exist $t_0$ and $t_1$ with $N_s = N_{t_0}$ for all $s \leq t_0$ and $N_u = N_{t_1}$ for all $u \geq t_1$, and let $\n$ be the multiplicity function of the persistence diagram of $N$.
-	Then for each $\epsilon > 0$ we have 
+\begin{defi} \label{d:initially and eventually constant}
+    A persistence module $N$ is said to be \emph{initially constant} if there is $t_0 \in \R$ such that $N_{u,t_0}$ is an isomorphism for all $u \leq t_0$.
+    Similarly, it is said to be \emph{eventually constant} if there is $t_1 \in \R$
+    such that $N_{t_1,u}$ is an isomorphism for all $u \geq t_1$.
+\end{defi}
+
+\begin{thm} \label{t:cap numbers well defined}
+	Let $N$ be a q-tame persistence module that is both initially and eventually constant.
+	If $\n$ is the multiplicity function of the persistence diagram of $N$,
+	then 
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q) < \infty.
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q) < \infty
 	\end{equation*}
+	for each $\epsilon > 0$.
 \end{thm}
@@
 \begin{proof}
+    Let $t_0, t_1 \in \R$ be as in \cref{d:initially and eventually constant}.
 	We split the sum whose finiteness we want to show in two parts
@@
 
-	For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$, $p > t_1$ or $t_1 < q < \infty$ holds.
+	For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$ or $p > t_1$ or $t_1 < q < \infty$ holds.
 	This implies 
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > e } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \n (p,q)
 	\ = \!
@@
 	\ \, \leq \!\!
-	\sum_{(p,q) \in T^{\geq e}} \n (p,q),
+	\sum_{(p,q) \in T^{\epsilon}} \n (p,q),
 	\end{equation*}
-	where $T^{\geq \epsilon}$ is the smaller triangle 
+	where $T^{\epsilon}$ is the smaller triangle 
 	\begin{equation*}
@@
 	\begin{equation*}
-	\sum_{(p,q) \in T^{e}} \n (p,q) 
+	\sum_{(p,q) \in T^{\epsilon}} \n (p,q) 
 	\ < \ 
@@
 \begin{thm} \label{t:inequalities}
-	Let $M$ be a graded q-tame persistence module with cap numbers $m_{d}^{\epsilon}$ and essential dimensions $p_{d}$ finite for all $d$ and $\epsilon$.
+	Let $M$ be a graded q-tame persistence module with finite cap numbers $m_{d}^{\epsilon}$ and essential dimensions $p_{d}$ for all $d$ and $\epsilon$.
 	If $\m_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
@@
 	\begin{align*}
-	m^{\epsilon}_{d}\ &=
+	m^{\epsilon}_{d} \ &=
 	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \\ &=
+	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ =
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon }} \m_{d-1}(p,q) \ +
@@
 	\begin{equation*}
-	p_{d} \ = \!\!
+	p_{d} \ = \!\!\!
 	\sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty) \ = \
@@
 	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
-	\sum_{p \in \R} \m_d(p,\infty) \\	&=
+	\sum_{p \in \R} \m_d(p,\infty) \ =
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q)
@@
 	\end{align*}
-	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies the equation $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
 
-As we have remarked, the finiteness assumptions are satisfied if $M$ is initially and eventually constant, so as a special case, the theorem yields Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, which includes classical Morse functions $f$ on closed smooth manifolds $X$.
-As we have outlined while motivating the definition of the cap numbers, our inequalities as presented in \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:morse_inequalities} because, in this setting, $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of $f$.
+As mentioned above, the finiteness assumptions are satisfied if $M$ is initially and eventually constant.
+Hence, as a special case, the theorem yields generalized Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, including classical Morse functions $f$ on closed smooth manifolds $X$.
+As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:morse_inequalities}, as $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
 
-The finiteness conditions of our theorem are also satisfied for the functionals that Morse considered in his work on functional topology, with q-tameness being guaranteed by \cref{t:strong local connectedness implies q-tameness} instead of the insufficient condition Morse proposed.
-As we have also mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
-Note, however, that in contrast to Morse's version, our inequalities also work without the assumption of continuity from above, expanding their use beyond \v{C}ech type theories.
+The finiteness conditions of our theorem are also satisfied for the functionals considered by Morse in his work on functional topology.
+While the condition proposed by Morse turns out to be insufficient as shown in \cref{s:surfaces}, q-tameness is still guaranteed by \cref{t:local connectedness implies q-tameness} established in \cref{s:connectivity}.
+As mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
+Note however that, in contrast to Morse's version, our inequalities also hold without the assumption of continuity from above, expanding their use beyond \v{C}ech type theories.
 
-\begin{rem}
-	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical and which formalizes the idea of a point being critical if it produces topological changes in the sublevel set filtration.
+\begin{rem} \label{r:homotopically critial points}
+	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical, and which formalizes the idea of a point being critical if it causes a topological change in the sublevel set filtration.
 	This notion is employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.

### 2021-07-29 introduction.tex
Overleaf version to post

--- 2021-07-26 introduction.tex
@@
 The interplay between the critical set of a function and the topology of its domain is a cornerstone of modern mathematics.
-Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably considers a differentiable function on a closed smooth manifold, but more general settings should also be regarded.
+Nowadays, when thinking about the pioneering work of Marston Morse, our first thought probably involves a differentiable function on a closed smooth manifold, but more general settings should also be considered.
 Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{Milnor.1963}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold, which notably goes beyond the compact setting.
 Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{Salamon.1999}.
-Morse himself worked in a very general setting, publishing in the 1930s a series of papers \cite{Morse.1937, Morse.1938, Morse.1940} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
-He named this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove the Unstable Minimal Surface Theorem, a result providing conditions for the existence of critical points of the Douglas functional that are not local minima.
+Morse himself worked in a very general setting, publishing in the 1930s a pair of papers \cite{Morse.1937, Morse.1940} and a monograph \cite{Morse.1938} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
+He called the theory set forth in this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
+In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove a general form of \emph{Mountain Pass Theorem} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous.
+From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima.
 
-While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly because, as Hildebrandt [4, p.
-324] puts it, ``Morse--Tompkins' original paper [is] unreadable and inaccessible for the non-specialist''---
-many of his ideas have resurfaced and flourished in other domains.
+Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general; possibly in part because, as expressed by Struwe:
+\begin{displaycquote}[p.~82]{Struwe.1988}
+    The technical complexity and the use of a sophisticated topological machinery [...] tend to make Morse--Tompkins' original paper unreadable and inaccessible for the non-specialist.
+\end{displaycquote}
+A similar assessment was given by Raoul Bott, who writes in \cite[p.~934]{Bott.1980} that the papers \cite{Morse.1937, Morse.1940} ``are not easy reading'' and constitute a ``tour de force'' by Morse.
+
+The intricacies of Morse's development notwithstanding, many of his ideas have resurfaced in the intervening years and flourished in other domains.
 In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
-Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.
+Its success in applied topology has motivated a refined abstract theory of persistence that lies in the intersection of geometry, topology, and representation theory.
 
 The homology of a filtered space is an example of what is called a \emph{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
-In many important cases, a persistence module admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields the basic invariant known as its \emph{persistence diagram}.
+In many important cases, a persistence module $M$ admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields a complete discrete invariant of $M$ known as its \emph{persistence diagram}.
+The set of all persistence diagrams can be organized into a metric space.
+This often allows to recast geometric questions about general filtered spaces in a combinatorial metric model, since the passage via the homology construction to this metric space is Lipschitz, a statement commonly known as the \emph{stability} of persistence diagrams.
 
-The influence of persistence theory and its sophistication have seen rapid growth in recent years.
-One of the primary reasons for this is the fact that persistence diagrams can be organized into a metric space, often allowing to recast geometric questions about general filtered spaces in a combinatorial metric model.
-This is because the passage via the homology construction to this metric space is Lipschitz, a statement commonly known as the \emph{stability} of persistence diagrams.
-
-The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he developed the theory of \emph{caps} and their \emph{spans}, capturing much of the same information as the modern notion of persistence diagram, including concepts such as the persistence or birth-death of a topological feature.
+The most remarkable connections between functional topology and persistence theory come from Morse's paper \cite{Morse.1940}, where he developed the theory of \emph{caps} and their \emph{spans}.
+They capture much of the same information as the modern notion of persistence diagram, including concepts such as the persistence or birth and death of a homology class, although Morse's results still fall short of yielding global decompositions of persistence modules.
 Morse used his theory of caps to study functionals on a metric space by analyzing the evolution of the topology of their sublevel sets.
@@
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-In fact, the problem of finding such conditions was already considered by Morse, who studied certain local connectivity properties of a filtered metric space and claimed them to suffice for the q-tameness of the associated persistent homology.
-Contrary to these claims, we show that the local connectivity condition used by Morse and Tompkins in the proof of the Unstable Minimal Surface Theorem is insufficient (\cref{c: counterexample}).
-We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:strong local connectedness implies q-tameness}).
-Since Douglas' functional has compact sublevel sets but is not continuous in the $C^0$ topology, which Morse and Tompkins considered, we use this second condition to correct their proof.
+In fact, the problem of finding such conditions was already considered by Morse, who studied certain local connectivity properties of a filtered metric space and claimed them to suffice for the q-tameness of the associated persistent \v{C}ech homology.
+Contrary to these claims, we show that the local connectivity condition used by Morse and Tompkins in the proof of the Unstable Minimal Surface Theorem is insufficient (\cref{c:counterexample}).
+We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
+Since Douglas' functional has compact sublevel sets but is not continuous in the $C^0$ topology considered by Morse and Tompkins, we use this second condition to correct their proof.
 
@@
 The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules satisfy Morse inequalities.
-As an application, we identify a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins and fix it with our results.
+As an application of our results, we identify and fix a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins.
 
@@
 We present a persistence-theoretic point of view on Morse inequalities in \cref{s:inequalities}.
-It generalizes both their version in the smooth and compact setting as well as the one used in functional topology.
+It generalizes both their versions in the smooth and compact setting as well as the one used in functional topology.
 The core of this work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness for its associated persistence module.
-We close with a historical overview of Morse's functional topology and its relation to our results in \cref{s:surfaces}.
+We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.
 \cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and a comparison between them based on Dowker's Theorem.

### 2021-07-29 main.tex
Remove unused commands
Overleaf version to post

@@
-\documentclass[nospthms, a4paper, final]{svjour3}
-\setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}
-\setlength{\textheight}{\dimexpr\pdfpageheight-2.4in}
+\documentclass{amsart}
 \usepackage{mathptmx}
@@
 
+% layout
+\setlength{\textwidth}{\paperwidth}
+\addtolength{\textwidth}{-1.85in}
+\setlength{\textheight}{\paperheight}
+\addtolength{\textheight}{-2in}
+\calclayout
+
+% updating to MSC2020
+\makeatletter
+\@namedef{subjclassname@2020}{%
+	\textup{2020} Mathematics Subject Classification}
+\makeatother
+
 % theorems
@@
 \Crefname{prop}{Proposition}{Propositions}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{conj}[thm]{Conjecture}
-\Crefname{conj}{Conjecture}{Conjectures}
 \theoremstyle{definition}
 \newtheorem{defi}[thm]{Definition}
-\newtheorem{ex}[thm]{Example}
 \newtheorem{rem}[thm]{Remark}
@@
 \DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\coker}{coker}
 \DeclareMathOperator{\rad}{rad}
-\newcommand\CH{\check{H}}
-\newcommand{\Mod}[1]{#1-\mathbf{Mod}}
+\newcommand{\CH}{\check{H}}
 \newcommand{\PFD}{\mathrm{PFD}}
-\newcommand{\PFG}{\mathrm{PFG}}
 \DeclareMathOperator{\Nrv}{Nrv}
@@
 \DeclareMathOperator{\crit}{crit}
-\newcommand\MCH{M\check{H}}
-\newcommand\VH{VH}
-\newcommand\MVH{MVH}
-\newcommand{\obs}{\dashrightarrow}
 \newcommand{\multiplicityDomain}{\mathcal{E}}
@@
 \newcommand{\n}{\mathfrak{n}}
-\newcommand{\anibal}[1]{\textcolor{blue}{\underline{Anibal}: #1}}
 
@@
 
-\title{Persistence in functional topology and a correction to a theorem of Morse}
+	\title[Persistence in functional topology]{Persistence in functional topology and a correction to a theorem of Morse}
 
-\author{Ulrich Bauer \and Anibal M.~Medina-Mardones \and Maximilian~Schmahl}
+	\author[U. Bauer]{Ulrich Bauer}
+	\address{U.~Bauer, Technical University of Munich}
+	\email{\href{mailto:mail@ulrich-bauer.org}{mail@ulrich-bauer.org}}
 
-\institute{
-	Ulrich Bauer \at Technical University of Munich \\ \email{mail@ulrich-bauer.org} \and
-	Anibal M.~Medina-Mardones \at Max Planck Institute for Mathematics \at University of Notre Dame du Lac \\ \email{ammedmar@mpim-bonn.mpg.de} \and
-	Maximilian~Schmahl \at Heidelberg University \\ \email{mschmahl@mathi.uni-heidelberg.de}
-}
+	\author[A. Medina-Mardones]{Anibal M.~Medina-Mardones}
+	\address{A.~Medina-Mardones, Max Planck Institute for Mathematics \and University of Notre Dame}
+	\email{\href{mailto:ammedmar@mpim-bonn.mpg.de}{ammedmar@mpim-bonn.mpg.de}}
 
-\authorrunning{U.~Bauer, A.~Medina-Mardones, M.~Schmahl}
+	\author[M. Schmahl]{Maximilian~Schmahl}
+	\address{M.~Schmahl, Heidelberg University}
+	\email{\href{mailto:mschmahl@mathi.uni-heidelberg.de}{mschmahl@mathi.uni-heidelberg.de}}
 
-\maketitle
+	\subjclass[2020]{Primary: 55N31, 58E05. Secondary: 58E12, 54D05, 55N05.}
+
+	\date{\today}
 
@@
 
-\tableofcontents
+	\maketitle
 	\input{introduction}
@@
 	\section*{Acknowledgements}
-This research has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}, the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
+	U.B. has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.
 
-A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL, where part of this work developed.
+	A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.
+
+	M.S. has been supported by German Research Foundation (DFG) through %the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, 
+	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
 

### 2021-07-29 persistence.tex
Overleaf version to post

@@
 Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
-In particular, it is unsuited for the applications of Morse and Tompkins in minimal surfaces theory.
+In particular, it is unsuited for the applications of Morse and Tompkins in minimal surface theory.
 An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tameness}.
@@
 The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
-Specifically, $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
-For example, the radical of the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ is the direct sum $\bigoplus_{n \in \N_{> 0}} C((0,1/n))$.
+More explicitly, we have $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
+As an example, the radical of the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ is the direct sum $\bigoplus_{n \in \N_{> 0}} C((0,1/n))$.
 If $M$ is q-tame, then its radical admits a barcode decomposition \cite[Corollary~3.6]{Chazal.2016b},
@@
 One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities later on.
-% When forgetting the endpoints of the intervals in the barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$ of a persistence module with an interval decomposition, i.e., when disregarding the distinction between open, closed and half-open intervals, we obtain a discrete invariant that is more convenient in many regards, including the formulation of generalized Morse inequalities.
 Defined precisely, this invariant known as the \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
@@
 Because information about the endpoints of intervals is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete for q-tame modules in the observable category.
-% and suffices to recover the barcode in many cases of interest.
 Stated explicitly, we have the following.

### 2021-07-29 surfaces.tex
Overleaf version to post

@@
-\section{Minimal surfaces and functional topology} \label{s:surfaces}
+\section{Minimal surfaces and persistent homology} \label{s:surfaces}
 
-After having presented Morse inequalities in terms of persistence diagrams and having developed topological conditions for existence of persistence diagrams associated to filtrations, we will now connect these previous results to the work of Morse and Tompkins on minimal surfaces from \cite{Morse.1939}.
+Having established Morse inequalities in terms of persistence diagrams and topological conditions for existence of persistence diagrams associated to filtrations, we now connect these results to the work of Morse and Tompkins on minimal surfaces from \cite{Morse.1939}.
 We will focus on the homological aspects of their approach.
-For a general exposition we refer to \cite[Sections 4.3-5]{Bott.1980}, and for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}.
+For a general exposition we refer to \cite[Sections 4.3--5]{Bott.1980}, and for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}.
 
@@
 \begin{equation*}
-A_g(\varphi)=\frac{1}{16}\int_0^{2\pi}\int_0^{2\pi}\sin\left(\frac{\alpha-\beta}{2}\right)^{-2} \! \lVert g(\varphi(\alpha))-g(\varphi(\beta)) \rVert_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta.
+A_g(\varphi) = \frac{1}{16} \int_0^{2\pi} \int_0^{2\pi} \sin \left( \frac{\alpha-\beta}{2} \right)^{-2} \!
+\lVert g(\varphi(\alpha)) - g(\varphi(\beta)) \rVert_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta.
 \end{equation*}
-Let $\Omega_g=\{\varphi\in\widetilde\Omega\mid A_g(\varphi)<\infty\}$.
-Douglas proved that, for a large class of curves $g$ the set $\Omega_g$ is non-empty with compact sublevel sets of $A_g$.
+Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$.
+Douglas proved that, for a large class of curves $g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
 Since $A_g$ is bounded below by $0$, this implies that $A_g$ has a unique global minimizer.
-Douglas then used harmonic analysis to show that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem.
+Using methods from harmonic analysis, Douglas then showed that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem.
 
-In \cite[p.~445]{Morse.1939}, Morse and Tompkins introduce a homotopical notion of critical point for any metric space $M$ and $F \colon M \to \R$.
+As alluded to in \cref{r:homotopically critial points}, Morse and Tompkins consider a homotopical notion of critical point for a general function $F \colon M \to \R$ on a metric space \cite[p.~445]{Morse.1939}, see also \cite{Morse.1943}.
 Roughly, a point $p$ is \emph{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
 
-Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, i.e., a minimal surface, and use this correspondence to prove the following result \cite[p.~447]{Morse.1939}, also reviewed as Theorem 6.10 in \cite{Struwe.1988}.
+Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, called a minimal surface, and use this correspondence to prove the following result \cite[p.~447]{Morse.1939}, also reviewed as Theorem II.6.10 in \cite{Struwe.1988}.
 
@@
 
-Their proof relies on Morse inequalities for homotopically critical points which they infer by relating them to cap numbers and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
+Their proof relies on Morse inequalities for homotopically critical points, which they infer by relating these critical points to the cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration of the function, and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
 
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon M \to \R$ is said to be \emph{homotopically locally connected} or $\piLC$	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
+	The sublevel set filtration of a function $f \colon M \to \R$ is said to be \emph{weakly homotopically locally connected} or \emph{weakly $\piLC$}	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
 \end{defi}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally connected} or $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
 
-Clearly, being $\LC$ implies being $\piLC$ and, if the homology $\H$ takes finite dimensional values on one point spaces, also $\HLC$.
-We will now show that not even $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
+Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one point spaces, also weakly $\HLC$.
+We will now show that not even weakly $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
 In particular, our construction will be used to invalidate Morse's claim quoted above.
@@
 \begin{thm} \label{t:counterexample}
-	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is not finite dimensional for some $n$.
+	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
 \end{thm}
@@
 
-	Let us now verify that the sublevel set filtration of $f$ is $\LC$, so
+	In order to verify that the sublevel set filtration of $f$ is weakly $\LC$, we
 	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
@@
 	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$. 
-	Note that because $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains it.
-	Clearly, we may choose $\delta > 0$ so small that $D_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a disk contained in this sphere and contained in $V$. 
+	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
+	Clearly, we may choose $\delta > 0$ so small that $D_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological disk contained in this sphere and contained in $V$. 
 	The disk $D_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = D_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
 
-	What remains to be shown is that $f_{\leq \bullet}$ is not q-tame for $\H$.
-	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$ because $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
+	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
 \end{proof}
@@
 \HE_k &=
-\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\cup
+\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\, \cup
 \bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
@@
 
-\begin{cor} \label{c: counterexample}
+\begin{cor} \label{c:counterexample}
 	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.
@@
 
-The gap we have highlighted in the argument of Morse and Tompkins can be fixed by applying \cref{t:strong local connectedness implies q-tameness} because the proof given in \cite[p.464]{Morse.1939} for local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property for the sublevel set filtration of $A_g$, which we now formalize.
+The gap we have highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
+This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property, which we now formalize.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{strongly} $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
 
-Clearly, the filtration being strongly $\LC$ implies that the filtration is also strongly $\HLC$ for \v{C}ech homology with field coefficients, which is what Morse and Tompkins use.
-Therefore, from \cref{t:strong local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is \mbox{q-tame} as claimed.
-This implies that Morse inequalities hold, and hence so does the Morse-Tompkins' Unstable Minimal Surfaces Theorem.
+Clearly, the filtration being $\LC$ implies that the filtration is also $\HLC$ for \v{C}ech homology with field coefficients, which is the homology theory Morse and Tompkins use.
+Therefore, from \cref{t:local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is indeed \mbox{q-tame} as needed.
+This implies that the generalized Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem.
 
 We have also mentioned that Morse introduced another condition that he also called local $F$-connectivity three years earlier.
-It roughly corresponds to being \emph{strongly} $\piLC$ with a certain added uniformity property.
+It roughly corresponds to being $\piLC$ with a certain added uniformity property.
 In the original it reads:
-\begin{displaycquote}[p.421-422]{Morse.1937}
+\begin{displaycquote}[p.421--422]{Morse.1937}
 	The space $M$ will be said to be locally $F$-connected for the order $n$ if corresponding to $n$, an arbitrary point $p$ on $M$, and an arbitrary positive constant $e$, there exists a positive constant $\delta$ with the following property.

### 2021-07-29 vietoris.tex
Overleaf version to post

@@
-\section{Vietoris and \v{C}ech homology} \label{s:vietoris}
+\section{Vietoris and \texorpdfstring{\v{C}}{}ech homology} \label{s:vietoris}  % command preventing a hyperref warning
 
@@
 
-For greater generality, instead of metric Vietoris homology we have instead considered \v{C}ech homology in the previous section.
-We now justify this choice showing that these two homology constructions agree on compact metric spaces.
+For greater generality, instead of metric Vietoris homology in this paper we consider \v{C}ech homology instead.
+We now justify this choice by showing that these two constructions for homology agree on compact metric spaces.
 
@@
 which again yields a functor from $\Cov(X)$ to simplicial complexes.
-This construction is dual in the sense of Dowker's Theorem \cite{Dowker.1952} to the nerve construction.
+This construction is dual to the nerve construction in the sense of Dowker's Theorem \cite{Dowker.1952}, which asserts that the two complexes $\Nrv (\alpha)$ and $\Vietoris (\alpha)$ are homotopy equivalent.
 As a consequence, we have that $H (\Nrv (\alpha); \mathbb{F}) \cong H (\Vietoris (\alpha); \mathbb{F})$.
-This isomorphism is natural with respect to refinement so we get an alternative description of \v{C}ech homology as 
+This isomorphism is natural with respect to refinement of covers, so we get an alternative description of \v{C}ech homology as 
 \begin{equation*}
@@
 for a compact metric space $X$.
-In other words, the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we considered.
+In other words, the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we consider in this paper.

### 2021-07-29 main.tex
Version to post to the arXiv

@@
 \newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\Crefname{prop}{Proposition}{Propositions}
 \theoremstyle{definition}
@@
 \DeclareMathOperator{\crit}{crit}
-\newcommand{\multiplicityDomain}{\mathcal{E}}
+\newcommand{\mulDom}{\mathcal{E}}
 \newcommand{\Top}{\mathsf{Top}}
@@
 
-	\begin{abstract}
 	\input{abstract}
-	\end{abstract}
 
 	\maketitle
+
 	\input{introduction}
@@
 
-	\section*{Acknowledgements}
-	U.B. has been supported by German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.
-
-	A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.
-
-	M.S. has been supported by German Research Foundation (DFG) through %the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, 
-	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
+	\input{acknowledgment}
 

### 2021-07-29 vietoris.tex
Version to post to the arXiv

@@
-\section{Vietoris and \texorpdfstring{\v{C}}{}ech homology} \label{s:vietoris}  % command preventing a hyperref warning
+\section{Vietoris and \texorpdfstring{\v{C}}{}ech homology} \label{s:vietoris}
 
-An interesting aspect of Morse's work from the modern point of view is his use of metric Vietoris homology with coefficients in a field, which closely relates to the use of filtered Vietoris-Rips and \v{C}ech complexes in topological data analysis.
+For greater generality, in this paper we considered \v{C}ech homology instead of the homology construction used by Morse in functional topology: metric Vietoris homology.
+We now justify this choice by showing that these two constructions agree on compact metric spaces.
 
-For greater generality, instead of metric Vietoris homology in this paper we consider \v{C}ech homology instead.
-We now justify this choice by showing that these two constructions for homology agree on compact metric spaces.
-
-First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section IX--X]{Eilenberg.1952}.
+First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section~IX--X]{Eilenberg.1952}.
 Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation. 
@@
 The nerve construction defines a functor from the poset $\Cov(X)$ regarded as a category to that of simplicial complexes. 
-The \emph{\v{C}ech homology with coefficients in $\mathbb{F}$} of $X$ is defined as
+The \emph{\v{C}ech homology with coefficients in $\F$} of $X$ is defined as
 \begin{equation*}
-\CH(X; \mathbb{F}) \ =
-\lim_{\alpha \in \Cov(X)} H(\Nrv(\alpha); \mathbb{F}).
+\CH(X; \F) \ =
+\lim_{\alpha \in \Cov(X)} H(\Nrv(\alpha); \F).
 \end{equation*}
@@
 This construction is dual to the nerve construction in the sense of Dowker's Theorem \cite{Dowker.1952}, which asserts that the two complexes $\Nrv (\alpha)$ and $\Vietoris (\alpha)$ are homotopy equivalent.
-As a consequence, we have that $H (\Nrv (\alpha); \mathbb{F}) \cong H (\Vietoris (\alpha); \mathbb{F})$.
+As a consequence, we have that $H (\Nrv (\alpha); \F) \cong H (\Vietoris (\alpha); \F)$.
 This isomorphism is natural with respect to refinement of covers, so we get an alternative description of \v{C}ech homology as 
 \begin{equation*}
-\CH (X; \mathbb{F}) \ \cong
-\lim_{\alpha \in \Cov (X)} H (\Vietoris (\alpha); \mathbb{F}).
+\CH (X; \F) \ \cong
+\lim_{\alpha \in \Cov (X)} H (\Vietoris (\alpha); \F).
 \end{equation*}
@@
 \begin{equation*}
-\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \mathbb{F}),
+\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \F),
 \end{equation*}
@@
 \begin{equation*}
-\CH (X; \mathbb{F}) \ \cong \,
-\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \mathbb{F})
+\CH (X; \F) \ \cong \,
+\lim_{\alpha \in \Balls(X)} H (\Vietoris (\alpha); \F)
 \end{equation*}

### 2021-07-29 main.tex
Updates from Overleaf

@@
 \newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\Crefname{prop}{Proposition}{Propositions}
 \theoremstyle{definition}
@@
 \DeclareMathOperator{\crit}{crit}
-\newcommand{\mulDom}{\mathcal{E}}
+\newcommand{\multiplicityDomain}{\mathcal{E}}
 \newcommand{\Top}{\mathsf{Top}}
@@
 
+	\begin{abstract}
 		\input{abstract}
+	\end{abstract}
 
 	\maketitle
-
 	\input{introduction}
@@
 
-	\input{acknowledgment}
+	\section*{Acknowledgements}
+	U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.
+
+	A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.
+
+	M.S. has been supported by the German Research Foundation (DFG) through %the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics}, 
+	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
 

### 2021-07-29 abstract.tex

@@
+\begin{abstract}
 	During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
@@
 	As an application, we identify and correct a mistake in the proof of the Unstable Minimal Surface Theorem by Morse and Tompkins.
+\end{abstract}

### 2021-07-29 connectivity.tex

@@
-% \section{Sufficient conditions for the existence of persistence diagrams} \label{s:connectivity}
-
 \section{Existence of persistence diagrams} \label{s:connectivity}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{%strongly
-	locally homologically small} or \emph{%strongly
-	$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
-while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the %\emph{strong} 
-$\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
+while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
 If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
@@
 \begin{thm} \label{t:weak hlc to hlc}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also %strongly 
-	$\HLC$.
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also $\HLC$.
 \end{thm}
@@
 \begin{defi}
-	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{%strongly
-	$\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{$\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 \begin{lem} \label{l:restriction of LHS filtration}
-	Let $f \colon X \to \R$ be a function whose sublevel set filtration is %strongly 
-	$\HLC$.
+	Let $f \colon X \to \R$ be a function whose sublevel set filtration is $\HLC$.
 	Fix $u \in \R$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y = f_{\leq u}$.
-	Then the sublevel set filtration defined by $g$ is %strongly 
-	$\HLC$ below $u$.
+	Then the sublevel set filtration defined by $g$ is $\HLC$ below $u$.
 \end{lem}
@@
 	Since $Y \subseteq X$ carries the subspace topology, we may choose a neighborhood $V'$ of $x$ in $X$ such that $V = V' \cap Y$.
-	The sublevel set filtration of $f$ is assumed to be %strongly 
-	$\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
+	The sublevel set filtration of $f$ is assumed to be $\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
 	We set $U = U' \cap Y$, which defines a neighborhood of $x$ in $Y$.
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and %strongly 
-	$\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
 	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
@@
 
-	Next, we will show using the %strong 
-	$\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	Next, we will show using the $\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
 	Choose an arbitrary $s' \in (s,\, t)$.
-	Since the sublevel set filtration of $f$ is %strongly
-	$\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
+	Since the sublevel set filtration of $f$ is $\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
 	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
@@
 	\H_{n}((V'_1 \cup V'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
-	\H_{n-1}(V'_1 \cap V'_2 \cap f_{\leq s'}). \arrow[u]
+	\H_{n-1}(V'_1 \cap V'_2 \cap f_{\leq s'}) \arrow[u].
 	\end{tikzcd}
@@
 	\H_{n}((K'_1 \cup K'_2) \cap f_{\leq s'}) \arrow[r] \arrow[u] &
-	\H_{n-1}(K'_1 \cap K'_2 \cap f_{\leq s'}). \arrow[u]
+	\H_{n-1}(K'_1 \cap K'_2 \cap f_{\leq s'}) \arrow[u].
 	\end{tikzcd}
@@
 
-We can now complete the proof of the claim stating that for compact sublevel set filtrations, %strong 
-$\HLC$ implies q-tameness.
+We can now complete the proof of the claim stating that for compact sublevel set filtrations, $\HLC$ implies q-tameness.
 
@@
 	Choose $u \in \R$ with $u > t$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y=f_{\leq u}$.
-	Since we assume $f$ to induce a %strongly 
-	$\HLC$ sublevel set filtration, by \cref{l:restriction of LHS filtration} the sublevel set filtration of $g$ is %strongly 
-	$\HLC$ below $u$. 
+	Since we assume $f$ to induce a $\HLC$ sublevel set filtration, by \cref{l:restriction of LHS filtration} the sublevel set filtration of $g$ is $\HLC$ below $u$.
 	Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.

### 2021-07-29 inequalities.tex

@@
 Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
-By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\m_d \colon \multiplicityDomain \to \N$.
+By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\m_d \colon \mulDom \to \N$.
 In analogy to Morse's definitions, we may define the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \begin{equation*}
-m_{d}^{\epsilon}(t) =
+m_{d}^{\epsilon}(t) \ =
 \sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) +
@@
 \sum_{t} m_{d}^{\epsilon}(t) \ =
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
-\sum_{\substack{(p,q) \in \multiplicityDomain \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q).
+\sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
+\sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q).
 \end{equation}
@@
 	A persistence module $N$ is said to be \emph{initially constant} if there is $t_0 \in \R$ such that $N_{u,t_0}$ is an isomorphism for all $u \leq t_0$.
-    Similarly, it is said to be \emph{eventually constant} if there is $t_1 \in \R$
-    such that $N_{t_1,u}$ is an isomorphism for all $u \geq t_1$.
+	Similarly, it is said to be \emph{eventually constant} if there is $t_1 \in \R$ such that $N_{t_1,u}$ is an isomorphism for all $u \geq t_1$.
 \end{defi}
@@
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q) < \infty
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) < \infty
 	\end{equation*}
@@
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q)
 	\ = \!\!
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q)
 	\ +
@@
 	\begin{equation*}
-	T = \{(p,q) \in \multiplicityDomain \mid t_0 \leq p < q \leq t_1\}.
+	T = \{(p,q) \in \mulDom \mid t_0 \leq p < q \leq t_1\}.
 	\end{equation*}
@@
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \multiplicityDomain \setminus T \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q)
 	\ = \!
@@
 	m^{\epsilon}_{d} \ &=
-	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ =
+	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
+	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ =
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon }} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)
+	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)
 	\end{align*}
@@
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \multiplicityDomain \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
+	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
 	\sum_{p \in \R} \m_d(p,\infty) \ =

### 2021-07-29 persistence.tex

@@
 
-For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, or, more precisely, a functor from the category $\Top$ of topological spaces to the category $\Vect$ of vector spaces over a fixed field $\mathbb{F}$.
+For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, or, more precisely, a functor from the category $\Top$ of topological spaces to the category $\Vect$ of vector spaces over a fixed field $\F$.
 Key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
@@
 \begin{cases}
-\mathbb{F} & \text{if } t \in I, \\
+\F & \text{if } t \in I, \\
 0 & \text{otherwise},
@@
 \begin{cases}
-\operatorname{id}_{\mathbb{F}} & \text{if } s, t \in I, \\
+\operatorname{id}_{\F} & \text{if } s, t \in I, \\
 0 & \text{otherwise}.
@@
 One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities later on.
-Defined precisely, this invariant known as the \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \multiplicityDomain \to \mathbb{N}$ that associates to an element in
+Defined precisely, this invariant known as the \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \mulDom \to \N$ that associates to an element in
 \begin{equation*}
-\multiplicityDomain =
+\mulDom =
 \big\{ (p,q) \mid p \in \R \cup \{-\infty\}, \ q \in \R \cup \{+\infty\}, \ p < q \big\}
@@
 On the space of real-valued functions one considers the metric induced by the supremum norm, and for the space of persistence diagrams the \emph{bottleneck distance}.
-This metric expresses the distance between persistence diagrams by a matching of their points, counted with multiplicities, which is optimal with respect to the $L^{\infty}$-distance on $\multiplicityDomain$: two diagrams are within distance $\delta$ if any two matched points are within $L^{\infty}$-distance $\delta$, and any unmatched point has $L^{\infty}$-distance at most $2\delta$ to the diagonal $\{(p,q) \in \R^2 \mid p = q\}$.
+This metric expresses the distance between persistence diagrams by a matching of their points, counted with multiplicities, which is optimal with respect to the $L^{\infty}$-distance on $\mulDom$: two diagrams are within distance $\delta$ if any two matched points are within $L^{\infty}$-distance $\delta$, and any unmatched point has $L^{\infty}$-distance at most $2\delta$ to the diagonal $\{(p,q) \in \R^2 \mid p = q\}$.
 

### 2021-09-01 aux/acknowledgment.tex
Improve structure of files

\section*{Acknowledgements}

U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.

A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.

M.S. has been supported by the German Research Foundation (DFG) through	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.

### 2021-09-01 sec/connectivity.tex
Improve structure of files

--- 2021-07-29 connectivity.tex
@@
 Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
-A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
+A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer---Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
 \begin{equation*}
@@
 \end{equation*}
-We say that $\H$ has the \emph{open} (resp.\@\ \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
+We say that $\H$ has the \emph{open} (resp.\@\ \emph{compact}) \emph{Mayer---Vietoris property} if there are natural Mayer---Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
 
-For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which has the open Mayer-Vietoris property (like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
+For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer---Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+Note that this includes singular homology with field coefficients, which has the open Mayer---Vietoris property (like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer---Vietoris property.
 
@@
 \begin{proof}
-	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer---Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
 	The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
@@
 
-	Finally, using Mayer-Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
+	Finally, using Mayer---Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
 	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that 
@@
 	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$.
-	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer-Vietoris property.
+	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer---Vietoris property.
 
@@
 	which is $\HS_{n-1}$ by the induction hypothesis.
-	Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer---Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
 	\begin{equation*}
@@
 	which is $\HS_{n-1}$ by the induction hypothesis.
-	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer---Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
 	\begin{equation*}

### 2021-09-01 sec/inequalities.tex
Improve structure of files

--- 2021-07-29 inequalities.tex
@@
 m_{d}^{\epsilon}(t) \ =
-\sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) +
+\sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) \ +
 \sum_{\substack{q \in \R \\ q - t > \epsilon}} \m_d(t, q).
@@
 \begin{defi} \label{d:initially and eventually constant}
-	A persistence module $N$ is said to be \emph{initially constant} if there is $t_0 \in \R$ such that $N_{u,t_0}$ is an isomorphism for all $u \leq t_0$.
-	Similarly, it is said to be \emph{eventually constant} if there is $t_1 \in \R$ such that $N_{t_1,u}$ is an isomorphism for all $u \geq t_1$.
+	A persistence module $N$ is said to be \emph{initially constant} if there is $s \in \R$ such that $N_{r,s}$ is an isomorphism for all $r \leq s$.
+	Similarly, it is said to be \emph{eventually constant} if there is $u \in \R$
+	such that $N_{u,v}$ is an isomorphism for all $u \leq v$.
 \end{defi}
@@
 \begin{proof}
-	Let $t_0, t_1 \in \R$ be as in \cref{d:initially and eventually constant}.
+	Let $s, u \in \R$ be as in \cref{d:initially and eventually constant}.
 	We split the sum whose finiteness we want to show in two parts
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q)
-	\ = \!\!
-	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q)
-	\ +
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) \ = \!\!
+	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q) \ +
 	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \n (p,q)
 	\end{equation*}
-	and show for each summand separately that it is finite.
-	Here, $T$ denotes the triangle
+	where $T$ denotes the triangle
 	\begin{equation*}
@@
 
-	For the first summand, observe that because $N$ is constant below $t_0$ and constant above $t_1$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < t_0$ or $q < t_0$ or $p > t_1$ or $t_1 < q < \infty$ holds.
+	For the first summand, observe that because $N$ is constant below $s$ and constant above $u$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
 	This implies 
@@
 	\ = \!
-	\sum_{t_0 < q < t_1} \n (-\infty,q)
+	\sum_{s < q < u} \n (-\infty,q)
 	\ + \!
-	\sum_{t_0 < p < t_1} \n (p, \infty)
+	\sum_{s < p < u} \n (p, \infty)
 	\end{equation*}

### 2021-09-01 sec/introduction.tex
Improve structure of files

--- 2021-07-29 introduction.tex
@@
 
-The homology of a filtered space is an example of what is called a \emph{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
+The homology of a filtered space is an example of what is referred to as a \emph{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
 In many important cases, a persistence module $M$ admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields a complete discrete invariant of $M$ known as its \emph{persistence diagram}.

### 2021-09-01 sec/persistence.tex
Improve structure of files

--- 2021-07-29 persistence.tex
@@
 
-To explain the meaning of the above terms in detail, we consider a space $X$ and a function $f \colon X \to \R$.
+In more detail, consider a space $X$ and a function $f \colon X \to \R$.
 Unless noted otherwise, the functions we consider need not be continuous.
@@
 Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
-One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}, which is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology.
+One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}, which is satisfied in Morse's setting of compact sublevel set filtrations and \v{C}ech homology.
 In terms of barcodes, continuity from above amounts to only admitting intervals that are closed on the left and open on the right.
-One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities later on.
-Defined precisely, this invariant known as the \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \mulDom \to \N$ that associates to an element in
+One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities.
+Defined precisely, this invariant known as \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \mulDom \to \N$ that associates to an element in
 \begin{equation*}
@@
 the cardinality of the set $\{ \lambda \in \Lambda \mid \inf I_{\lambda} = p,\ \sup I_{\lambda} = q\}$.
-Because information about the endpoints of intervals is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete for q-tame modules in the observable category.
+Because information about the endpoints of intervals is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete invariant for q-tame modules in the observable category.
 Stated explicitly, we have the following.
@@
 \begin{thm}[\citet{Chazal.2016a, Chazal.2016b}] \label{t:q-tame modules have barcodes}
-	Every q-tame persistence module has a unique persistence diagram that completely describes its isomorphism type in the observable category.
+	Every q-tame persistence module has a unique persistence diagram that completely determines its isomorphism type in the observable category.
 \end{thm}
@@
 If this is the case, we will call the function \emph{q-tame} with respect to the functor $\H$.
-If $\H$ is some kind of homology theory, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
+If $\H$ is a homology theory, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
 

### 2021-09-01 sec/surfaces.tex
Improve structure of files

--- 2021-07-29 surfaces.tex
@@
 \begin{equation*}
-\HE = \bigcup_{n\in\mathbb{N}}\left\{(x_0,\dots,x_d)\in\R^{d+1} \ \middle | \ \left(x_0-\frac{1}{n}\right)^2+x_1^2+\dots+x_d^2=\left(\frac{1}{n}\right)^2\right\},
+\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
 \end{equation*}
@@
 	\draw[thick] (-.1,-.001) rectangle (.1,.05);
-	\clip (-.1,0) rectangle (.1,.05); % remove for all circles
+	\clip (-.1,0) rectangle (.1,.05);
 	\foreach \i in {1,...,100}{
@@
 \end{proof}
-
-Both singular and \v{C}ech homology of the Hawaiian earring are infinite dimensional in some degree, so they satisfy the assumptions of \cref{t:counterexample}.
-The singular case is treated in \cite{Barratt.1962}, and for \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{Eilenberg.1952}:
+\newpage
+Both singular and \v{C}ech homology of the $d$-dimensional Hawaiian earring is infinite dimensional in degree $d$, so they satisfy the assumptions of \cref{t:counterexample}.
+For singular homology this is proven in \cite{Barratt.1962}.
+For \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{Eilenberg.1952} as follows.
 Define 
@@
 i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \mathbb{F}) = \lim_{k} \CH_{d}(\HE_{k}; \mathbb{F})$, where $\CH$ denotes \v{C}ech homology.
+We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \F) = \lim_{k} \CH_{d}(\HE_{k}; \F)$, where $\CH$ denotes \v{C}ech homology.
 Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
 \begin{equation*}
-\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \mathbb{F})=\lim\left(\dots\to \prod_{n=1}^2\mathbb{F}\to \prod_{n=1}^1\mathbb{F}\to \prod_{n=1}^0\mathbb{F}\right)=\prod_{n\in\mathbb{N}}\mathbb{F},
+\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \F)=\lim\left(\dots\to \prod_{n=1}^2\F\to \prod_{n=1}^1\F\to \prod_{n=1}^0\F\right)=\prod_{n\in\N}\F,
 \end{equation*}
-which is infinite-dimensional over $\mathbb{F}$.
+which is infinite-dimensional over $\F$.
 
@@
 The gap we have highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
-This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property, which we now formalize.
+This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property described next.
 

### 2021-09-01 func_top.tex
Improve structure of files
Return to original paper size and use biblatex for references

--- 2021-07-29 main.tex
@@
 \documentclass{amsart}
-\usepackage{mathptmx}
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{tikz-cd}
-\usepackage[numbers,sort,compress]{natbib}
-\usepackage{graphicx}
-\usepackage{csquotes}
-\usepackage[bookmarks=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=true,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	linktocpage,
-	colorlinks,
-	citecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue}
-\usepackage[capitalize, noabbrev]{cleveref}
-
-% layout
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.85in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-2in}
-\calclayout
-
-% updating to MSC2020
-\makeatletter
-\@namedef{subjclassname@2020}{%
-	\textup{2020} Mathematics Subject Classification}
-\makeatother
-
-% theorems
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\Crefname{thm}{Theorem}{Theorems}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lem}[thm]{Lemma}
-\theoremstyle{definition}
-\newtheorem{defi}[thm]{Definition}
-\newtheorem{rem}[thm]{Remark}
-
-% commands
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\F}{\mathbb{F}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\HS}{\mathrm{HS}}
-\newcommand{\HT}{\mathrm{HT}}
-\newcommand{\HLC}{\mathrm{LHS}}
-\newcommand{\piT}{\pi\mathrm{T}}
-\newcommand{\LC}{\mathrm{LC}}
-\newcommand{\NH}{\mathrm{NH}}
-\newcommand{\piLC}{\pi\mathrm{LC}}
-\newcommand{\HE}{\mathbb{H}^d}
-\renewcommand{\H}{H}
-\DeclareMathOperator{\interior}{int}
-\DeclareMathOperator{\im}{im}
-\DeclareMathOperator{\rad}{rad}
-\newcommand{\CH}{\check{H}}
-\newcommand{\PFD}{\mathrm{PFD}}
-\DeclareMathOperator{\Nrv}{Nrv}
-\DeclareMathOperator{\Cov}{Cov}
-\DeclareMathOperator{\Vietoris}{Vtr}
-\DeclareMathOperator{\Balls}{Balls}
-\DeclareMathOperator*{\colim}{colim}
-\DeclareMathOperator{\crit}{crit}
-\newcommand{\mulDom}{\mathcal{E}}
-\newcommand{\Top}{\mathsf{Top}}
-\newcommand{\Vect}{\mathsf{Vect}}
-\renewcommand{\th}{^{\mathrm{th}}}
-\newcommand{\m}{\mathfrak{m}}
-\newcommand{\n}{\mathfrak{n}}
-
-\begin{document}
+\input{aux/style}
+\input{aux/commands}
 
@@
 
-	\author[U. Bauer]{Ulrich Bauer}
-	\address{U.~Bauer, Technical University of Munich}
+\author[U.~Bauer]{Ulrich Bauer}
+\address{U.B., Technical University of Munich}
 \email{\href{mailto:mail@ulrich-bauer.org}{mail@ulrich-bauer.org}}
 
-	\author[A. Medina-Mardones]{Anibal M.~Medina-Mardones}
-	\address{A.~Medina-Mardones, Max Planck Institute for Mathematics \and University of Notre Dame}
+\author[A.~Medina-Mardones]{Anibal M. Medina-Mardones}
+\address{A.M-M., Max Planck Institute for Mathematics \and University of Notre Dame}
 \email{\href{mailto:ammedmar@mpim-bonn.mpg.de}{ammedmar@mpim-bonn.mpg.de}}
 
-	\author[M. Schmahl]{Maximilian~Schmahl}
-	\address{M.~Schmahl, Heidelberg University}
+\author[M.~Schmahl]{Maximilian Schmahl}
+\address{M.S., Heidelberg University}
 \email{\href{mailto:mschmahl@mathi.uni-heidelberg.de}{mschmahl@mathi.uni-heidelberg.de}}
 
-	\subjclass[2020]{Primary: 55N31, 58E05. Secondary: 58E12, 54D05, 55N05.}
+\subjclass[2020]{55N31, 58E05, 58E12, 54D05, 55N05.}
 
@@
 
-	\input{abstract}
-
+\begin{document}
+	\input{aux/abstract}
 	\maketitle
-
-	\input{introduction}
-	\input{persistence}
-	\input{inequalities}
-	\input{connectivity}
-	\input{surfaces}
+	\input{sec/introduction}
+	\input{sec/persistence}
+	\input{sec/inequalities}
+	\input{sec/connectivity}
+	\input{sec/surfaces}
 	\appendix
-	\input{vietoris}
-
-	\input{acknowledgment}
-
-	\bibliographystyle{abbrvnaturl}
-	\bibliography{biblio}
-
+	\input{sec/vietoris}
+	\input{aux/acknowledgment}
+	\printbibliography
 \end{document}

### 2021-09-01 sec/connectivity.tex
Return to original paper size and use biblatex for references

--- 2021-07-29 connectivity.tex
@@
 Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
-A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer-Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
+A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer--Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
 \begin{equation*}
 \begin{tikzcd}[column sep = small]
-\cdots \arrow[r] & \H_{n}(X_{1} \cap X_{2}) \arrow[r] & \H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] & \H_{n}(X) \arrow[r] & \H_{n-1}(X_{1} \cap X_{2}) \arrow[r] & \cdots \ .
+\cdots \arrow[r] &[-10pt] \H_{n+1}(X) \arrow[d] & &[-20pt] & \\
+& \H_{n}(X_{1} \cap X_{2}) \arrow[r] &
+\H_{n}(X_{1}) \oplus \H_{n}(X_{2}) \arrow[r] &
+\H_{n}(X) \arrow[d] \\ & & &
+\H_{n-1}(X_{1} \cap X_{2}) \arrow[r] &
+\cdots \ .
 \end{tikzcd}
 \end{equation*}
-We say that $\H$ has the \emph{open} (resp.\@\ \emph{compact}) \emph{Mayer-Vietories property} if there are natural Mayer-Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
+We say that $\H$ has the \emph{open} (resp.\@\ \emph{compact}) \emph{Mayer--Vietoris property} if there are natural Mayer--Vietoris sequences for all triples $X_{1}, X_{2} \subseteq X$ with $X = X_1 \cup X_2$ and $X_i \subseteq X$ open (resp.\@\ compact Hausdorff).
 
-For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer-Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which has the open Mayer-Vietoris property (like any homology theory in the sense of the Eilenberg-Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer-Vietoris property.
+For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer--Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
 
@@
 \begin{proof}
-	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer-Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer--Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
 	The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
@@
 
-	Finally, using Mayer-Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
+	Finally, using Mayer--Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
 	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that
@@
 	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$.
-	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer-Vietoris property.
+	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer--Vietoris property.
 
@@
 	which is $\HS_{n-1}$ by the induction hypothesis.
-	Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\begin{equation*}
+	Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer--Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\begin{center}
+		\adjustbox{scale=.92}{
 			\begin{tikzcd}[column sep=small]
@@
 			\end{tikzcd}
-	\end{equation*}
+		}
+	\end{center}
 	We conclude that the inclusion
@@
 	which is $\HS_{n-1}$ by the induction hypothesis.
-	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer-Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\begin{equation*}
+	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer--Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
+	\begin{center}
+		\adjustbox{scale=.885}{
 			\begin{tikzcd}[column sep=small]

### 2021-09-01 sec/inequalities.tex
Return to original paper size and use biblatex for references

@@
 Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any non-negative integer $n$ the following holds:
-\begin{equation} \label{e:morse_inequalities}
+\begin{equation} \label{e:classical morse inequalities}
 \sum_{d=0}^n \ (-1)^{n-d} \big( \# \crit_{d}(f) - \beta_{d}(X) \big) \ \geq \ 0,
@@
 This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \citet{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
@@
 Whenever the sums below are well-defined, we also consider the \emph{$(d,\epsilon)$-cap numbers}
-\begin{equation} \label{e:cap numbers}
+\[
 m_{d}^{\epsilon} =
@@
 \sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q).
-\end{equation}
+\]
 An important setting where all cap numbers are well-defined is when $M$ is the persistent homology of the sublevel set filtration of a bounded function.
@@
 As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$ referred to as \emph{essential dimensions}, which, under the same assumptions as before, can be expressed in the language of persistence diagrams as
-\begin{equation} \label{e:essential dimension}
+\[
 p_{d} \ = \!\! \sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty),
-\end{equation}
+\]
 which is also the dimension of the colimit of the degree $d$ part of $M$.
@@
 	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
-	\sum_{p \in \R} \m_d(p,\infty) \ =
+	\sum_{p \in \R} \m_d(p,\infty) \\ &=
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q)
@@
 Hence, as a special case, the theorem yields generalized Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, including classical Morse functions $f$ on closed smooth manifolds $X$.
-As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:morse_inequalities}, as $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
+As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:classical morse inequalities}, as $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
 

### 2021-09-01 sec/persistence.tex
Return to original paper size and use biblatex for references

@@
 A rich family of indecomposable persistence modules is given by \emph{interval modules}, which for intervals $I \subseteq \R$ are defined by
-\begin{equation} \label{e:interval module}
+\begin{equation*}
 C(I)_t =
@@
 \end{cases}
-\end{equation}
+\end{equation*}
 These indecomposable interval modules can be used as building blocks for \emph{barcode modules}, which are direct sums of interval modules.
@@
 Yet, there are multiple ways to regularize q-tame persistence modules to obtain discrete invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
-We briefly recall the approach from \citet{Chazal.2016b}.
+We briefly recall the approach from \cite{Chazal.2016b}.
 
@@
 
-\begin{thm}[\citet{Chazal.2016a, Chazal.2016b}] \label{t:q-tame modules have barcodes}
+\begin{thm}[\cite{Chazal.2016a, Chazal.2016b}] \label{t:q-tame modules have barcodes}
 	Every q-tame persistence module has a unique persistence diagram that completely determines its isomorphism type in the observable category.

### 2021-09-01 sec/surfaces.tex
Return to original paper size and use biblatex for references

@@
 	\centering
-	\begin{tikzpicture}[scale = 76]
+	\begin{tikzpicture}[scale = 60]
 	\draw[thick] (-.1,-.001) rectangle (.1,.05);
@@
 \end{proof}
-\newpage
+
 Both singular and \v{C}ech homology of the $d$-dimensional Hawaiian earring is infinite dimensional in degree $d$, so they satisfy the assumptions of \cref{t:counterexample}.

### 2021-09-13 sec/connectivity.tex
Sent to CCM

@@
+%!TEX root = ../func_top.tex
+
 \section{Existence of persistence diagrams} \label{s:connectivity}
@@
 Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
-A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer--Vietoris sequence} for $\H$ if the inclusion-induced maps assemble to a long exact sequence
+A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer--Vietoris sequence} for $\H$ if the inclusion-induced maps can be completed to a long exact sequence
 \begin{equation*}
@@
 For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer--Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
-Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}) , and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
+Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}), and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
 
@@
 	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
-	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of $X$.
+	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of~$X$.
 
@@
 
-The general proof strategy is inspired by the proof of a result attributed to Wilder \cite[p.~325]{Wilder.1949}, as presented by Bredon \cite[Section II.17]{Bredon.1997}.
+The general proof strategy is inspired by the proof of a result by Wilder \cite[p.~325]{Wilder.1949}, as presented by Bredon \cite[Section II.17]{Bredon.1997}.
 We collect the main ideas in several lemmas.
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $f \colon X \to \R$ be a function on a locally compact space $X$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq X$ with $C$ compact and $L$ open.
+	Let $f \colon Y \to \R$ be a function on a locally compact space $Y$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq Y$ with $C$ compact and $L$ open.
 	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
@@
 
-	We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq X$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$	for which there exists $s' \in (s,\, t)$ such that the inclusion $U \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$.
+	We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq Y$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$	for which there exists $s' \in (s,\, t)$ such that the inclusion $U \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$.
 	We will show that $\Sigma_{s, t}$ has the following three properties:
@@
 	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$.
-	By the second property, we have $V = \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}$.
+	By the second property, we have
+	\[V \defeq \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}.\]
 	Using the third property, the inclusion
@@
 	is $\HS$, so in particular $\HS_n$.
-	By local compactness of $X$ we can choose a compact neighborhood $K_x$ of $x$ contained in $U_x$.
+	By local compactness of $Y$ we can choose a compact neighborhood $K_x$ of $x$ contained in $U_x$.
 	Now $V_x = \interior (K_x)$ is a neighborhood of $x$ with $V_x \in \Sigma_{s,t}$.
@@
 	Because the $V_i$ and $V'_i$ are open and because $\H$ has the open Mayer--Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\begin{center}
-		\adjustbox{scale=.92}{
-			\begin{tikzcd}[column sep=small]
+	\[
+			\begin{tikzcd}[column sep=small,every matrix/.append style={nodes={font=\small}}]
 			\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
@@
 			\end{tikzcd}
-		}
-	\end{center}
+	\]
 	We conclude that the inclusion
@@
 
-	In the compact case, we apply \cref{l:neighborhood third} again to obtain compact sets $K''_i$ such that
+	In the compact case, we apply \cref{l:neighborhood third} once more to obtain compact sets $K''_i$ such that
 	\begin{equation*}
@@
 	Because the $K'_i$ and $K''_i$ as well as the sublevel sets of $f$ are all compact and because $\H$ has the compact Mayer--Vietoris property, we obtain the following commutative diagram satisfying the assumptions of \cref{l:commutative algebra}:
-	\begin{center}
-		\adjustbox{scale=.885}{
-			\begin{tikzcd}[column sep=small]
+	\[
+			\begin{tikzcd}[column sep=tiny,every matrix/.append style={nodes={font=\small}}]
 			\H_n(L \cap f_{\leq t}) \oplus \H_n(L \cap f_{\leq t}) \arrow[r] &
@@
 	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
-	because it factors through the previous one.
+	as it factors through the previous one.
 \end{proof}
@@
 	Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.
-	Thus, we can apply \cref{l:key lemma for q-tameness} to the filtration $g_{\leq \bullet}$ with $C = f_{\leq s}$ and $L = Y$ to obtain that the inclusion $f_{\leq s} = C \cap g_{\leq s} \to L \cap g_{\leq t} = f_{\leq t}$ is $\HS$.
+	Thus, we can apply \cref{l:key lemma for q-tameness} to the filtration $g_{\leq \bullet}$ with $C = L = Y$ to obtain that the inclusion $f_{\leq s} = C \cap g_{\leq s} \to L \cap g_{\leq t} = f_{\leq t}$ is $\HS$.
 \end{proof}

### 2021-09-13 sec/inequalities.tex
Sent to CCM

@@
+%!TEX root = ../func_top.tex
+
 \section{Generalized Morse inequalities} \label{s:inequalities}
@@
 \begin{equation*}
-m_{d}^{\epsilon}(t) \ =
+c_{d}^{\epsilon}(t) \ =
 \sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) \ +
@@
 \[
-m_{d}^{\epsilon} =
-\sum_{t} m_{d}^{\epsilon}(t) \ =
+c_{d}^{\epsilon} =
+\sum_{t} c_{d}^{\epsilon}(t) \ =
 \sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
@@
 	If $\n$ is the multiplicity function of the persistence diagram of $N$,
-	then
+	then for each $\epsilon > 0$,
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) < \infty
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) < \infty.
 	\end{equation*}
-	for each $\epsilon > 0$.
 \end{thm}
@@
 
-	For the first summand, observe that because $N$ is constant below $s$ and constant above $u$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
+	For the first summand, observe that, because $N$ is constant below $s$ and constant above $u$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
 	This implies
@@
 \begin{thm} \label{t:inequalities}
-	Let $M$ be a graded q-tame persistence module with finite cap numbers $m_{d}^{\epsilon}$ and essential dimensions $p_{d}$ for all $d$ and $\epsilon$.
+	Let $M$ be a graded q-tame persistence module with finite cap numbers $c_{d}^{\epsilon}$ and finite essential dimensions $p_{d}$ for all $d$ and $\epsilon$.
 	If $\m_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
 	\begin{equation} \label{e:morse inequalities}
-	\sum_{d=0}^n \ (-1)^{n-d} (m^{\epsilon}_{d} - p_{d}) \ \geq\ 0
+	\sum_{d=0}^n \ (-1)^{n-d} (c_{d}^{\epsilon} - p_{d}) \ \geq\ 0
 	\end{equation}
@@
 \begin{proof}
-	Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$.
+	Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$.
 	Since we assume $\m_d(-\infty, p) = 0$ for all $p$, we have
 	\begin{align*}
-	m^{\epsilon}_{d} \ &=
+	c_{d}^{\epsilon} \ &=
 	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
@@
 	\begin{align*}
-	m^{\epsilon}_{d} - p_{d} \ &=
+	c_{d}^{\epsilon} - p_{d} \ &=
 	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q) \ +
@@
 	\end{align*}
-	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies the equation $m^{\epsilon}_{d} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
 
-As mentioned above, the finiteness assumptions are satisfied if $M$ is initially and eventually constant.
+As shown in \cref{t:cap numbers well defined}, the finiteness assumptions are satisfied if $M$ is initially and eventually constant.
 Hence, as a special case, the theorem yields generalized Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, including classical Morse functions $f$ on closed smooth manifolds $X$.
-As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:classical morse inequalities}, as $\beta_d(X) = p_d$ and $m_d^{\epsilon} = \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
+As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:classical morse inequalities}, as $\beta_d(X) = p_d$ and $c_d^{\epsilon} = \# \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
+Morse inequalities for unbounded functions can still be obtained by restricting the function to an arbitrary sublevel set.
 
-The finiteness conditions of our theorem are also satisfied for the functionals considered by Morse in his work on functional topology.
+The finiteness conditions of our theorem are also satisfied for the Douglas functional considered by Morse and Tompkins as an application of Morse' theory of functional topology.
 While the condition proposed by Morse turns out to be insufficient as shown in \cref{s:surfaces}, q-tameness is still guaranteed by \cref{t:local connectedness implies q-tameness} established in \cref{s:connectivity}.
@@
 \begin{rem} \label{r:homotopically critial points}
-	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical, and which formalizes the idea of a point being critical if it causes a topological change in the sublevel set filtration.
+	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical, and which formalizes the idea of criticality of a point in terms of topological changes in the sublevel set filtration.
 	This notion is employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
-	The usefulness of this notion might be limited though, because for example in the context of Floer theory, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.
+	The usefulness of this notion is might limited in many cases of interest.
+	In Floer theory, for example, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.
 	In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable, because while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology.

### 2021-09-13 sec/introduction.tex
Sent to CCM

@@
+%!TEX root = ../func_top.tex
+
 \section{Introduction}
@@
 The intricacies of Morse's development notwithstanding, many of his ideas have resurfaced in the intervening years and flourished in other domains.
-In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
-Its success in applied topology has motivated a refined abstract theory of persistence that lies in the intersection of geometry, topology, and representation theory.
+In particular, in applied topology and symplectic geometry, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
+Its success in these fields has motivated a refined abstract theory of persistence that lies in the intersection of geometry, topology, and representation theory.
 
 The homology of a filtered space is an example of what is referred to as a \emph{persistence module}, a functor to vector spaces from the real numbers considered as a poset category.
-In many important cases, a persistence module $M$ admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields a complete discrete invariant of $M$ known as its \emph{persistence diagram}.
+In many important cases, a persistence module $M$ admits an essentially unique decomposition into indecomposable direct summands, and the structure of this decomposition yields a complete invariant of $M$ known as its \emph{persistence diagram}.
 The set of all persistence diagrams can be organized into a metric space.
@@
 We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
-Since Douglas' functional has compact sublevel sets but is not continuous in the $C^0$ topology considered by Morse and Tompkins, we use this second condition to correct their proof.
+Since the Douglas functional has compact sublevel sets but is not continuous in the $C^0$ topology considered by Morse and Tompkins, we use this second condition to correct their proof.
 
@@
 
-The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules satisfy Morse inequalities.
+The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules have persistence diagrams and satisfy generalized Morse inequalities.
 As an application of our results, we identify and fix a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins.
@@
 We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.
-\cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and a comparison between them based on Dowker's Theorem.
+\cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and their equivalence for compact metric spaces.

### 2021-09-13 sec/persistence.tex
Sent to CCM

@@
+%!TEX root = ../func_top.tex
+
 \section{Filtered spaces and persistence theory} \label{s:persistence}
@@
 In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions on general topological spaces.
-For a detailed exposition we refer to \cite{Polterovich.2020} and \cite{Chazal.2016a, Oudot.2015}.
+For a detailed exposition we refer to either of \cite{Chazal.2016a, Oudot.2015, Polterovich.2020}, and for applications of this theory in symplectic geometry to 
+\cite{Polterovich.2016, Usher.2016, LeRoux.2018, Shelukhin.2019}.
 
 The ``pipeline'' of topological persistence traverses through geometry, algebra and discrete mathematics as follows:
-Given a space $X$ filtered by the sublevel sets of a function $f$, the application of some homology theory in degree $n$ with coefficients in a field, or, more generally, a functor from topological spaces to vector spaces, produces a \emph{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful discrete invariant called \emph{persistence diagram}.
+Given a space $X$ filtered by the sublevel sets of a function $f$, the application of some homology theory in degree $n$ with coefficients in a field, or, more generally, a functor from topological spaces to vector spaces, produces a \emph{persistence module}, an algebraic object equipped with a structure theory leading in favorable cases to a powerful invariant called \emph{persistence diagram}.
 
@@
 We say that this filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
+In this case, the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
 
@@
 As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
-Yet, there are multiple ways to regularize q-tame persistence modules to obtain discrete invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
+Yet, there are multiple ways to regularize q-tame persistence modules to obtain invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
 We briefly recall the approach from \cite{Chazal.2016b}.
@@
 Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
-One can avoid losing any information in this process, for example by requiring all persistence modules $M$ to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}, which is satisfied in Morse's setting of compact sublevel set filtrations and \v{C}ech homology.
+In certain situations, no information is lost in this process, for example if the persistence module $M$ can be assumed to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}.
+This assumption is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology; in this setting, both the filtration as well as the resulting persistence module are continuous from above.
 In terms of barcodes, continuity from above amounts to only admitting intervals that are closed on the left and open on the right.
-One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another discrete invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities.
-Defined precisely, this invariant known as \emph{persistence diagram} is the multiset given by the \emph{multiplicity function} $\m \colon \mulDom \to \N$ that associates to an element in
+One can also simply disregard the distinction between open, closed and half-open intervals in a barcode $\{I_{\lambda}\}_{\lambda \in \Lambda}$, which leads to another invariant that is more convenient in many settings, including our formulation of generalized Morse inequalities.
+This invariant, known as the \emph{persistence diagram}, is defined as the multiset given by the \emph{multiplicity function} $\m \colon \mulDom \to \N$ that associates to an element in
 \begin{equation*}
@@
 Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
+$M$ and $N$ are isomorphic in the observable category if and only if they have interleaving distance $0$.
 As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: From functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistence modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).

### 2021-09-13 sec/surfaces.tex
Sent to CCM

@@
-\section{Minimal surfaces and persistent homology} \label{s:surfaces}
+%!TEX root = ../func_top.tex
+
+\section{Persistent homology and the minimal surface problem} \label{s:surfaces}
 
@@
 Let $g \colon \R \to \R^n$ be a $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
-Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and such that there are three distinct points $\alpha_i \in [0,2\pi)$ with $\varphi(\alpha_i)=\alpha_i$.
+Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
 The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined by
 \begin{equation*}
-A_g(\varphi) = \frac{1}{16} \int_0^{2\pi} \int_0^{2\pi} \sin \left( \frac{\alpha-\beta}{2} \right)^{-2} \!
-\lVert g(\varphi(\alpha)) - g(\varphi(\beta)) \rVert_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta.
+A_g(\varphi) = \frac{1}{16 \pi} \int_0^{2\pi} \int_0^{2\pi}  \left\| \frac{g(\varphi(\alpha)) - g(\varphi(\beta))}{\sin \frac{\alpha-\beta}{2}} \right\|_2^2 \ \mathrm{d}\alpha \ \mathrm{d}\beta.
 \end{equation*}
@@
 Douglas proved that, for a large class of curves $g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
-Since $A_g$ is bounded below by $0$, this implies that $A_g$ has a unique global minimizer.
-Using methods from harmonic analysis, Douglas then showed that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem.
+Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimimum.
+Douglas then showed that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem, a surface homeomorphic to a disk with boundary $g$ and minimum area.
 
@@
 
-Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, called a minimal surface, and use this correspondence to prove the following result \cite[p.~447]{Morse.1939}, also reviewed as Theorem II.6.10 in \cite{Struwe.1988}.
+Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, called a minimal surface \cite[p.~464]{Morse.1939}, and use this correspondence to prove the following result \cite[p.~472]{Morse.1939}, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
 
 \begin{thm}[Unstable Minimal Surface Theorem]
-	If $\Omega_g$ contains two distinct solutions to Plateau's Problem then it also contains an unstable minimal surface, more precisely, a critical point of $A_g$ of index 1.
+	If $\Omega_g$ contains two distinct solutions of Plateau's Problem contained in disjoint critical sets of $A_g$, then it also contains an unstable minimal surface, more precisely, a homotopically critical point of $A_g$ of non-minimum type.
 \end{thm}
+Moreover, they give an explicit example of a curve $g$ satisfying these assumptions, proving the existence of an unstable minimal surface.
 
@@
 \begin{displaycquote}[p.~431]{Morse.1940}
-	The space $M$ is said to be \emph{locally $F$-connected} of order $r$ at $p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
+	Let $p$ be a point of $M$ at which $F(p)=c$.
+	The space $M$ is said to be \emph{locally $F$-connected} of order $r$ at~$p$ if corresponding to each positive constant $e$ there exists a positive constant $\delta$ such that each singular $r$-sphere on the $\delta$-neighborhood of $p$ and on $F_{c+\delta}$ bounds an $(r+1)$-cell of norm $e$ on $F_{c+e}$.
 \end{displaycquote}
-Here, $c = F(p)$.
-Using similar language to the one used in \cref{s:connectivity}, this property is equivalent to the following notion applicable to general topological spaces.
+Using similar language to the one used in \cref{s:connectivity}, the property of local $F$-connectedness of all orders is equivalent to the following notion applicable to general topological spaces.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon M \to \R$ is said to be \emph{weakly homotopically locally connected} or \emph{weakly $\piLC$}	if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly homotopically locally connected}, or \emph{weakly $\piLC$}, if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
 \end{defi}
 
-Morse then goes on to state that as a consequence of local $F$-connectivity the persistent \v{C}ech homology of this sublevel set filtration is q-tame.
-In the original it reads:
+Morse then goes on to claim that the persistent \v{C}ech homology of this sublevel set filtration is q-tame, provided that $F$ is bounded from below and satisfies the assumptions of local $F$-connectivity and compactness of sublevel sets.
+%, and a further condition called $F$-regularity, which is trivially satisfied if the domain of $F$ is compact.
+In the original (where the function is assumed to take values in $[0,1)$ the claim reads:
 \begin{displaycquote}[Theorem 6.3, p.~432]{Morse.1940}
@@
 Unfortunately, the above claim does not hold in general, as we will show next by providing an explicit counterexample.
+We start by introducing a stronger version of weak local connectedness, which will still be satisfied by our counterexample.
 
@@
 
-Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one point spaces, also weakly $\HLC$.
-We will now show that not even weakly $\LC$ is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
+Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one-point spaces, also weakly $\HLC$.
+We will now show that not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
 In particular, our construction will be used to invalidate Morse's claim quoted above.
@@
 	\foreach \i in {1,...,100}{
-		\draw[line width=0.1/\i mm] (0, 1/\i^2) circle (1/\i^2);
+		\draw[line width=0.4/\i^0.5 pt] (0, 1/\i^2) circle (1/\i^2);
 	}
@@
 	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
-	Clearly, we may choose $\delta > 0$ so small that $D_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological disk contained in this sphere and contained in $V$.
-	The disk $D_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = D_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$. 
+	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
 
@@
 For singular homology this is proven in \cite{Barratt.1962}.
-For \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6.\@ and X.3.1.]{Eilenberg.1952} as follows.
+For \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
 Define
@@
 \begin{cor} \label{c:counterexample}
-	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.
+	The function $f \colon \HE \to \R$ with value~$0$ at the origin and $1$ elsewhere defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.
 \end{cor}

### 2021-09-13 sec/vietoris.tex
Return to original paper size and use biblatex for references
Sent to CCM

--- 2021-07-29 vietoris.tex
@@
+%!TEX root = ../func_top.tex
+
 \section{Vietoris and \texorpdfstring{\v{C}}{}ech homology} \label{s:vietoris}
@@
 
-First, let us recall the definition of \v{C}ech homology as presented for example by \citet[Section~IX--X]{Eilenberg.1952}.
-Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation. 
+First, let us recall the definition of \v{C}ech homology as presented for example by \cite[Section~IX--X]{Eilenberg.1952}.
+Let $X$ be a topological space and let $\Cov(X)$ be the set of all open covers of $X$ ordered by the refinement relation, which we implicitly regard as a poset category.
 Recall that for an open cover $\alpha \in \Cov(X)$ its \emph{nerve} $\Nrv(\alpha)$ is defined as the simplicial complex
@@
 \end{equation*}
-The nerve construction defines a functor from the poset $\Cov(X)$ regarded as a category to that of simplicial complexes. 
+For any field $\F$, the nerve construction composed with the functor of simplicial homology with coefficients in $\F$ define a functor from $\Cov(X)$ to the category of graded $\F$-vector spaces.
 The \emph{\v{C}ech homology with coefficients in $\F$} of $X$ is defined as
@@
 \begin{equation*}
-\Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha \right\},
+\Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha \right\}.
 \end{equation*}
-which again yields a functor from $\Cov(X)$ to simplicial complexes.
-This construction is dual to the nerve construction in the sense of Dowker's Theorem \cite{Dowker.1952}, which asserts that the two complexes $\Nrv (\alpha)$ and $\Vietoris (\alpha)$ are homotopy equivalent.
+This construction is dual to the nerve construction in the sense of Dowker's Theorem \cite{Dowker.1952}, which asserts that the two complexes $\Nrv (\alpha)$ and $\Vietoris (\alpha)$ are homotopy equivalent after geometric realization.
 As a consequence, we have that $H (\Nrv (\alpha); \F) \cong H (\Vietoris (\alpha); \F)$.
@@
 
-If $X$ is a metric space, this is still not exactly the same as the construction of metric Vietoris homology presented in \cite{Vietoris.1927} and used by Morse, which in modern notation is the limit
+If $X$ is an arbitrary metric space, this is still not exactly the same as the construction of \emph{metric} Vietoris homology, as originally defined by Vietoris \cite{Vietoris.1927} and used by Morse, which in modern notation is the limit over all covers of $X$ by metric $\delta$-balls,
 \begin{equation*}
@@
 However, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they both define the same limit.
-Thus, we have a natural isomorphism
+Thus, in this case we have a natural isomorphism
 \begin{equation*}
@@
 \end{equation*}
-for a compact metric space $X$.
-In other words, the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we consider in this paper.
+In other words, for compact metric spaces the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we consider in this paper.

### 2021-10-12 aux/abstract.tex
After interchanging summary and abstract

\begin{abstract}
The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules admit persistence diagrams, which, in particular, imply that they satisfy generalized Morse inequalities.
We illustrate the applicability of this result by recasting the original proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins in a modern and rigorous framework.
\end{abstract}

### 2021-10-12 sec/inequalities.tex
After interchanging summary and abstract

@@
-%!TEX root = ../func_top.tex
+% !TEX root = ../func_top.tex
 
@@
 	\end{align*}
-	so the sequence given by $\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)$ satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+	so the sequence given by
+	\[\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)\]
+	satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
 \end{proof}
@@
 While the condition proposed by Morse turns out to be insufficient as shown in \cref{s:surfaces}, q-tameness is still guaranteed by \cref{t:local connectedness implies q-tameness} established in \cref{s:connectivity}.
-As mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
+As mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite[Corollary~12.3]{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
 Note however that, in contrast to Morse's version, our inequalities also hold without the assumption of continuity from above, expanding their use beyond \v{C}ech type theories.

### 2021-10-12 sec/introduction.tex
After interchanging summary and abstract

@@
 From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima.
+A result that in the intervening years has been proven again and generalized in several directions using various techniques \cite{1,2,3,4}.
 
@@
 
-Given the importance of persistence diagrams for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
+Given the importance of persistence diagrams, in particular for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
 For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite dimensional rank.
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-In fact, the problem of finding such conditions was already considered by Morse, who studied certain local connectivity properties of a filtered metric space and claimed them to suffice for the q-tameness of the associated persistent \v{C}ech homology.
-Contrary to these claims, we show that the local connectivity condition used by Morse and Tompkins in the proof of the Unstable Minimal Surface Theorem is insufficient (\cref{c:counterexample}).
-We introduce two similar but more widely applicable conditions, and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
-Since the Douglas functional has compact sublevel sets but is not continuous in the $C^0$ topology considered by Morse and Tompkins, we use this second condition to correct their proof.
+We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
+
+To illustrate the applicability of these results we return to the original setting that motivated the development of functional topology considering the Douglas functional.
+It satisfies the hypothesis of our second result above, so its associated persistent \v{C}ech homology is q-tame and satisfies the Morse inequalities assumed by Morse and Tompkins under certain local-connectivity assumptions that are not sufficient for this conclusion (\cref{c:counterexample}).
 
 \subsection*{Summary}
+%During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
+%Morse and Tompkins applied this body of work, referred to as functional topology, to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem, a result later re-proven and generalized by minimal surface theorists using other techniques.
+%Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics.
 
-The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules have persistence diagrams and satisfy generalized Morse inequalities.
-As an application of our results, we identify and fix a mistake in the proof the Unstable Minimal Surface Theorem of Morse and Tompkins.
+The primary contribution of this work consists in 
+%In this article, we provide 
+a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
+We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
+More specifically, we provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
+With the goal of illustrating the applicability of this result, we use it to correct an inaccuracy in a central result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
 

### 2021-10-12 sec/connectivity.tex
After including counterexample into section 4

@@
 Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}), and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
+
+\subsection{Local connectivity and q-tameness}
 
@@
 
-As our main result we will show now that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+As our main result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
 
@@
 \end{thm}
+
+Combining \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} we have the following consequence.
+
+\begin{cor} \label{c:q-tameness for continuous functions}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
+\end{cor}
+
+As the following example illustrates, the continuity assumption in the above corollary is crucial.
+Consider the \emph{$d$-dimensional Hawaiian earring}
+\begin{equation*}
+\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
+\end{equation*}
+which is a compact subspace of $\R^{d+1}$.
+
+\begin{figure}[t]
+	\centering
+	\begin{tikzpicture}[scale = 60]
+	\draw[thick] (-.1,-.001) rectangle (.1,.05);
+	\clip (-.1,0) rectangle (.1,.05);
+	\foreach \i in {1,...,100}{
+		\draw[line width=0.4/\i^0.25 pt] (0, 1/\i^2) circle (1/\i^2);
+	}
+	\end{tikzpicture}
+	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
+\end{figure}
+
+\begin{thm} \label{t:counterexample}
+	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\HLC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
+\end{thm}
+
+\begin{proof}
+	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
+
+	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we
+	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
+We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+
+	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
+	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\HLC$ condition is trivially satisfied.
+
+	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
+	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
+	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
+	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+
+	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
+	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+\end{proof}
+
+\subsection{Proof of \cref{t:local connectedness implies q-tameness}}
 
@@
 \end{proof}
-
-Combining \cref{t:weak hlc to hlc} with \cref{t:local connectedness implies q-tameness} also yields the following result for continuous functions.
-
-\begin{cor} \label{c:q-tameness for continuous functions}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
-\end{cor}

### 2021-10-12 sec/surfaces.tex
Arxiv2
After including counterexample into section 4

@@
 
-We will consider the \emph{$d$-dimensional Hawaiian earring}
-\begin{equation*}
-\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
-\end{equation*}
-which is a compact subspace of $\R^{d+1}$.
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale = 60]
-	\draw[thick] (-.1,-.001) rectangle (.1,.05);
-	\clip (-.1,0) rectangle (.1,.05);
-	\foreach \i in {1,...,100}{
-		\draw[line width=0.4/\i^0.5 pt] (0, 1/\i^2) circle (1/\i^2);
-	}
-	\end{tikzpicture}
-	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
-\end{figure}
-
-\begin{thm} \label{t:counterexample}
-	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
-\end{thm}
-
-\begin{proof}
-	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
-
-	In order to verify that the sublevel set filtration of $f$ is weakly $\LC$, we
-	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
+%We will consider the \emph{$d$-dimensional Hawaiian earring}
+%\begin{equation*}
+%\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
+%\end{equation*}
+%which is a compact subspace of $\R^{d+1}$.
+%
+%\begin{figure}[t]
+%	\centering
+%	\begin{tikzpicture}[scale = 60]
+%	\draw[thick] (-.1,-.001) rectangle (.1,.05);
+%	\clip (-.1,0) rectangle (.1,.05);
+%	\foreach \i in {1,...,100}{
+%		\draw[line width=0.4/\i^0.25 pt] (0, 1/\i^2) circle (1/\i^2);
+%	}
+%	\end{tikzpicture}
+%	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
+%\end{figure}
+%
+%\begin{thm} \label{t:counterexample}
+%	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\LC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
+%\end{thm}
+%
+%\begin{proof}
+%	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
+%
+%	In order to verify that the sublevel set filtration of $f$ is weakly $\LC$, we
+%	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
 We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
-
-	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
-	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\LC$ condition is trivially satisfied.
-
-	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
-	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
-	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$. 
-	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
-
-	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
-	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
-\end{proof}
+%
+%	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
+%	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\LC$ condition is trivially satisfied.
+%
+%	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
+%	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
+%	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
+%	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+%
+%	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
+%	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+%\end{proof}
 

### 2021-10-14 sec/abstract.tex
After including counterexample into section 4
After spliting into ss Sect 5

--- 2021-10-12 aux/abstract.tex
@@
+%!TEX root = ../func_top.tex
+
 \begin{abstract}
-The primary contribution of this work consists in the introduction of topological conditions on a broad class of filtered spaces ensuring their associated persistent homology modules admit persistence diagrams, which, in particular, imply that they satisfy generalized Morse inequalities.
-We illustrate the applicability of this result by recasting the original proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins in a modern and rigorous framework.
+We introduce topological conditions on a broad class of filtered spaces ensuring that their associated persistent homology modules admit persistence diagrams, which, in particular, implies that they satisfy generalized Morse inequalities.
+We illustrate the applicability of these results by recasting the original proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins in a modern and rigorous framework.
 \end{abstract}

### 2021-10-14 sec/connectivity.tex
After spliting into ss Sect 5

@@
 The general idea that we want to employ is to deduce global finiteness properties like q-tameness from local ones.
-Thus, the functors we consider should have some property that allows us to do so.
+Thus, the functors we consider should have a certain property allowing us to do so.
 
@@
 For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer--Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+We will also assume that $\H_{n}$ takes finite dimensional values on one-point spaces.
 Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}), and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
@@
 
-As our main result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+Our main result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
 
@@
 
-Combining \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} we have the following consequence.
+Combining \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} we have the following consequence;
+the existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
 
@@
 	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
-We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+Since we assume that $\H_{n}$ is homotopy invariant and takes singletons to finite dimensional spaces, it suffices to find $U$ as above such that $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 

### 2021-10-14 sec/introduction.tex
After spliting into ss Sect 5

@@
 From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima.
-A result that in the intervening years has been proven again and generalized in several directions using various techniques \cite{1,2,3,4}.
+In the intervening years, this result has been reproven and generalized in several directions using various techniques, and the problem class is still an active area of research \cite{Struwe.1984,Jost.1990,Jost.1991,Montezuma.2020,Marques.2021}.
 
@@
 To illustrate the applicability of these results we return to the original setting that motivated the development of functional topology considering the Douglas functional.
-It satisfies the hypothesis of our second result above, so its associated persistent \v{C}ech homology is q-tame and satisfies the Morse inequalities assumed by Morse and Tompkins under certain local-connectivity assumptions that are not sufficient for this conclusion (\cref{c:counterexample}).
+It satisfies the hypothesis of \cref{t:local connectedness implies q-tameness}, so its associated persistent \v{C}ech homology is indeed q-tame and satisfies the Morse inequalities assumed by Morse and Tompkins, eventhough the other local-connectivity assumptions they wanted to employ are not sufficient for this conclusion (\cref{c:counterexample}).
 
@@
 a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
-We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in functional analysis and symplectic geometry.
+We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in functional analysis.
+% and symplectic geometry.
 More specifically, we provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
-With the goal of illustrating the applicability of this result, we use it to correct an inaccuracy in a central result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
+With the goal of illustrating the applicability of this result, we use it to correct an inaccuracy in a result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
 
@@
 We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.
+\todo{update this to reflect the restructuring}
 \cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and their equivalence for compact metric spaces.

### 2021-10-14 sec/surfaces.tex
After spliting into ss Sect 5

@@
 
-\section{Persistent homology and the minimal surface problem} \label{s:surfaces}
+\section{Persistent homology and functional topology} \label{s:surfaces}
 
-Having established Morse inequalities in terms of persistence diagrams and topological conditions for existence of persistence diagrams associated to filtrations, we now connect these results to the work of Morse and Tompkins on minimal surfaces from \cite{Morse.1939}.
+Having established topological conditions for the existence of persistence diagrams associated to filtrations and corresponding generalized Morse inequalities, we now illustrate how these results relate to Morse and Tompkins' work on minimal surfaces from \cite{Morse.1939}.
 We will focus on the homological aspects of their approach.
-For a general exposition we refer to \cite[Sections 4.3--5]{Bott.1980}, and for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}.
+For a general exposition we refer to \cite[Sections 4.3--5]{Bott.1980}, for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6.7]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
+
+\subsection{The unstable minimal surface problem}
 
@@
 Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
-The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined by
+The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined as
 \begin{equation*}
@@
 \end{equation*}
-Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$.
-Douglas proved that, for a large class of curves $g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
-Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimimum.
+Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$, equipped with the $C^0$ metric.
+Douglas proved that, for a large class of curves~$g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
+Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimum.
 Douglas then showed that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem, a surface homeomorphic to a disk with boundary $g$ and minimum area.
@@
 
-Morse and Tompkins prove that each homotopically critical point of the functional $A_g$ corresponds to a critical point of the area functional, called a minimal surface \cite[p.~464]{Morse.1939}, and use this correspondence to prove the following result \cite[p.~472]{Morse.1939}, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
+Morse and Tompkins prove \cite[p.~464]{Morse.1939} that each homotopically critical point of the functional $A_g$ indeed corresponds to 
+%
+%a critical point of the area functional,
+%called 
+a \emph{minimal surface} -- a surface with vanishing mean curvature -- and use this correspondence to prove the following result, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
 
-\begin{thm}[Unstable Minimal Surface Theorem]
-	If $\Omega_g$ contains two distinct solutions of Plateau's Problem contained in disjoint critical sets of $A_g$, then it also contains an unstable minimal surface, more precisely, a homotopically critical point of $A_g$ of non-minimum type.
+\begin{thm}[{Unstable Minimal Surface Theorem \cite[p.~472]{Morse.1939}}]
+	If the space $\Omega_g$ contains two distinct solutions of Plateau's Problem contained in disjoint critical sets of the functional $A_g$, then it also contains a critical set not of minimum type.
+	%, more precisely, a homotopically critical point of $A_g$ of non-minimum type.
 \end{thm}
-Moreover, they give an explicit example of a curve $g$ satisfying these assumptions, proving the existence of an unstable minimal surface.
+Here, a \emph{critical set} $S$ is a closed and open subspace of the set of all critical points with a given function value.
+It is said to be of \emph{minimum type} if for every neighborhood $N$ of $S$, the function value on the complement $N \setminus S$ exceeds the function value on $S$. 
+%it corresponds to a homotopically critical point of $A_g$ of non-minimum type?
+In addition to the general theorem above, Morse and Tompkins also give an explicit example of a curve $g$ satisfying the assumptions, thus proving the existence of an unstable minimal surface.
 
-Their proof relies on Morse inequalities for homotopically critical points, which they infer by relating these critical points to the cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration of the function, and then applying the Morse inequalities for cap numbers as we have considered them in \cref{s:inequalities}, and as Morse considered them in \cite{Morse.1940}.
+While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, the original approach of Morse and Tompkins is notable for its connection to persistent homology.
+
+\subsection{Morse's local connectivity conditions}
+
+Morse and Tompkins' proof of the existence of unstable minimal surfaces is revisited in \cite{Morse.1940} using an argument that relies on Morse inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
 
@@
 Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
-Unfortunately, the above claim does not hold in general, as we will show next by providing an explicit counterexample.
-We start by introducing a stronger version of weak local connectedness, which will still be satisfied by our counterexample.
+Unfortunately, the above claim does not hold in general, as exemplified by the sublevel set filtration from \cref{t:counterexample}.
+To elaborate on this, we consider a stronger version of weak local connectedness.
 
@@
 Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one-point spaces, also weakly $\HLC$.
-We will now show that not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions.
-In particular, our construction will be used to invalidate Morse's claim quoted above.
+Observe that the proof of \cref{t:counterexample} actually establishes that the filtration given there is weakly $\LC$, so not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions in general.
+In particular, our construction invalidates Morse's claim quoted above because \v{C}ech homology satisfies the assumptions on the homology theory made in \cref{t:counterexample}.
+
+Specifically, \v{C}ech homology is infinite dimensional in degree $d$ for the $d$-dimensional Hawaiian earring. 
+To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
+Define
+\begin{align*}
+\HE_k &=
+\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\, \cup
+\bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
+\end{align*}
+i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \F) = \lim_{k} \CH_{d}(\HE_{k}; \F)$, where $\CH$ denotes \v{C}ech homology.
+Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
+\begin{equation*}
+\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \F)=\lim\left(\dots\to \prod_{n=1}^2\F\to \prod_{n=1}^1\F\to \prod_{n=1}^0\F\right)=\prod_{n\in\N}\F,
+\end{equation*}
+which is infinite-dimensional over $\F$.
 
@@
 
-Both singular and \v{C}ech homology of the $d$-dimensional Hawaiian earring is infinite dimensional in degree $d$, so they satisfy the assumptions of \cref{t:counterexample}.
-For singular homology this is proven in \cite{Barratt.1962}.
-For \v{C}ech homology, one can use the fact that it commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
-Define
-\begin{align*}
-\HE_k &=
-\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\, \cup
-\bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
-\end{align*}
-i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \F) = \lim_{k} \CH_{d}(\HE_{k}; \F)$, where $\CH$ denotes \v{C}ech homology.
-Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
-\begin{equation*}
-\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \F)=\lim\left(\dots\to \prod_{n=1}^2\F\to \prod_{n=1}^1\F\to \prod_{n=1}^0\F\right)=\prod_{n\in\N}\F,
-\end{equation*}
-which is infinite-dimensional over $\F$.
+As proven in \cite{Barratt.1962}, the singular homology of the Hawaiian earrings is also infinite dimensional. In summary, we have the following.
 
@@
 
-The gap we have highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
+The gap we have thus highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
 This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property described next.

### 2021-10-14 sec/connectivity.tex
Reorder section 4

@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-\end{defi}
-
-Similarly, we have the following weaker version of this property.
-
-\begin{defi}
 	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
@@
 
-Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
-while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
-If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
+The following result is deduced directly from \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} below.
+The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
 
-\begin{thm} \label{t:weak hlc to hlc}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also $\HLC$.
+\begin{thm} \label{t:q-tameness for continuous functions}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
 \end{thm}
-
-\begin{proof}
-	Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
-	We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-
-	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
-	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
-	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of~$X$.
-
-	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
-	This second map is $\HS$ by construction.
-	Any map that factors through an $\HS$ map is also $\HS$, so the proof is finished.
-\end{proof}
-
-Our main result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
-
-\begin{thm} \label{t:local connectedness implies q-tameness}
-	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
-\end{thm}
-
-Combining \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} we have the following consequence;
-the existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
-
-\begin{cor} \label{c:q-tameness for continuous functions}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
-\end{cor}
 
@@
 \end{proof}
+
+We consider the following stronger local connectivity condition of sublevel set filtrations.
+
+\begin{defi}
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+\end{defi}
+
+Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
+while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
+If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
+
+\begin{thm} \label{t:weak hlc to hlc}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also $\HLC$.
+\end{thm}
+
+\begin{proof}
+	Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
+	We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+
+	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
+	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
+	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of~$X$.
+
+	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
+	This second map is $\HS$ by construction.
+	Any map that factors through an $\HS$ map is also $\HS$, so the proof is finished.
+\end{proof}
+
+Our main technical result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+
+\begin{thm} \label{t:local connectedness implies q-tameness}
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
+\end{thm}
 

### 2022-03-28 sec/connectivity.tex
Before addressing reviewer

@@
 
-\subsection{Local connectivity and q-tameness}
+\subsection{Weak local connectivity and q-tameness}
 
@@
 
-As the following example illustrates, the continuity assumption in the above corollary is crucial.
+As the following example illustrates, the continuity assumption in the above theorem is crucial.
 Consider the \emph{$d$-dimensional Hawaiian earring}
@@
 	\begin{tikzpicture}[scale = 60]
-	\draw[thick] (-.1,-.001) rectangle (.1,.05);
+	\draw[thick,lightgray] (-.1,-.001) rectangle (.1,.05);
 	\clip (-.1,0) rectangle (.1,.05);
@@
 
-	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we
-	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
+	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
 	We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
@@
 
-We consider the following stronger local connectivity condition of sublevel set filtrations.
+\subsection{Local connectivity and q-tameness}
+
+Motivated by the example above, we introduce a stronger local connectivity condition for sublevel set filtrations that ensures its q-tameness without the strict continuity assumption.
 
@@
 	This second map is $\HS$ by construction.
-	Any map that factors through an $\HS$ map is also $\HS$, so the proof is finished.
+	Any map that factors through an $\HS$ map is also $\HS$, so the proof is complete.
 \end{proof}
 
-Our main technical result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+Our main technical result, proven in the remainder of this subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
 
@@
 	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
+	In particular, $f$ has a persistence diagram.
 \end{thm}
-
-\subsection{Proof of \cref{t:local connectedness implies q-tameness}}
 

### 2022-03-28 sec/introduction.tex
Before addressing reviewer

@@
 He called the theory set forth in this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939, Morse.1941} used these techniques to prove a general form of \emph{Mountain Pass Theorem} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous.
+In particular, Morse and Tompkins \cite{Morse.1939} used these techniques to prove a general form of \emph{Mountain Pass Theorem} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous.
 From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima.
@@
 In this work, using persistence diagrams, we generalize the definition of these cap numbers to persistence modules and prove the existence of Morse inequalities for a large class of them (\cref{t:inequalities}).
-Our approach makes these inequalities accessible in new contexts beyond those originally covered by functional topology, including, for example, symplectic geometry.
+Our approach makes these inequalities accessible in new contexts beyond those originally covered by functional topology. %including, for example, symplectic geometry.
 
@@
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
+We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{t:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
 
-To illustrate the applicability of these results we return to the original setting that motivated the development of functional topology considering the Douglas functional.
-It satisfies the hypothesis of \cref{t:local connectedness implies q-tameness}, so its associated persistent \v{C}ech homology is indeed q-tame and satisfies the Morse inequalities assumed by Morse and Tompkins, eventhough the other local-connectivity assumptions they wanted to employ are not sufficient for this conclusion (\cref{c:counterexample}).
+To illustrate the applicability of these results we return to the original setting of the Douglas functional that motivated the development of functional topology.
+This functional satisfies the hypotheses of \cref{t:local connectedness implies q-tameness}, so its associated persistent \v{C}ech homology is indeed q-tame and admits a persistence diagram.
+From this, one can easily deduce the existence of an unstable minimal surface for certain explicit examples.
+As it turns out, the local connectivity conditions proposed by Morse \cite{Morse.1937} are not sufficient for this purpose, which we illustrate by a counterexample (\cref{c:counterexample}).
 
 \subsection*{Summary}
-%During the 1930s, Marston Morse developed a vast generalization of what is commonly known as Morse theory relating the critical points of a semi-continuous functional with the topology of its sublevel sets.
-%Morse and Tompkins applied this body of work, referred to as functional topology, to prove the Unstable Minimal Surface Theorem in the setting defined by Douglas' solution to Plateau's Problem, a result later re-proven and generalized by minimal surface theorists using other techniques.
-%Several concepts introduced by Morse in this context can be seen as early precursors to the theory of persistent homology, which by now has established itself as a popular tool in applied and theoretical mathematics.
 
-The primary contribution of this work consists in 
-%In this article, we provide 
-a modern redevelopment of the homological aspects of Morse's functional topology from the perspective of persistence theory.
+The primary contribution of this work consists in a modern development of the homological aspects of Morse's functional topology from the perspective of persistence theory.
 We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in functional analysis.
-% and symplectic geometry.
-More specifically, we provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
-With the goal of illustrating the applicability of this result, we use it to correct an inaccuracy in a result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
+We provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
+As an application of these result, we correct an inaccuracy in a result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
 
@@
 We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.
-\todo{update this to reflect the restructuring}
 \cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and their equivalence for compact metric spaces.

### 2022-03-28 sec/persistence.tex
Before addressing reviewer

@@
 For example, in the next section we will see how they lead to a generalization of the classical Morse inequalities.
-Much of their usefulness comes from a remarkable fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance}.
+Much of their usefulness comes from a remarkable fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance} \cite{Cohen-Steiner.2007}.
 
@@
 For the next step in the persistence pipeline, one needs a coherent assignment of a vector space to any topological space, or, more precisely, a functor from the category $\Top$ of topological spaces to the category $\Vect$ of vector spaces over a fixed field $\F$.
-Key examples are provided by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
+The typical choices are given by \emph{homology theories}, which for now are only assumed to be $\Z$-graded families $\H = (\H_d)_{d \in \Z}$ of \emph{homotopy invariant functors}, meaning that they assign the same morphism to homotopic maps.
 Of particular importance to us are \v{C}ech homology \cite[Section IX--X]{Eilenberg.1952} with coefficients in $\F$, and homology theories in the sense of Eilenberg--Steenrod \cite[Section I]{Eilenberg.1952}, such as singular homology, again with coefficients in $\F$ \cite{Eilenberg.1944}.
@@
 As it turns out, the stability of persistence barcodes can then be described as a sequence of 1-Lipschitz transformations: From functions (with the supremum norm) to filtrations by sublevel sets (with the interleaving distance), to persistence modules (with the interleaving distance), and finally to persistence diagrams (with the bottleneck distance).
-In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{Chazal.2009, Chazal.2016a, Bauer.2015, Cohen-Steiner.2007}.
+In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{Chazal.2009, Bauer.2015, Chazal.2016a}.

### 2022-03-28 sec/surfaces.tex
Before addressing reviewer

@@
 
-Having established topological conditions for the existence of persistence diagrams associated to filtrations and corresponding generalized Morse inequalities, we now illustrate how these results relate to Morse and Tompkins' work on minimal surfaces from \cite{Morse.1939}.
-We will focus on the homological aspects of their approach.
-For a general exposition we refer to \cite[Sections 4.3--5]{Bott.1980}, for a more detailed exposition including the analytical details see \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6.7]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
+Having established topological conditions for the existence of persistence diagrams associated to filtrations and corresponding generalized Morse inequalities, we now describe how these results relate to Morse's general theory of functional topology \cite{Morse.1937, Morse.1938, Morse.1940}, and to its application in Morse and Tompkins' work on unstable minimal surfaces from \cite{Morse.1939}.
+We will focus on the homological aspects of this approach referring to \cite[Sections 4.3--5]{Bott.1980} for a general exposition.
+For a more thorough presentation of the unstable minimal surface problem, including the analytical details, please consult \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
 
@@
 \end{equation*}
+It coincides with the Dirichlet energy of the unique harmonic extension of the reparametrized curve $g \circ \phi$ to a parametrized surface.
+The Dirichlet energy is an upper bound for the area, with equality if the parametrization is conformal.
 Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$, equipped with the $C^0$ metric.
@@
 Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimum.
-Douglas then showed that this minimizing critical point of $A_g$ corresponds to a solution of Plateau's Problem, a surface homeomorphic to a disk with boundary $g$ and minimum area.
+The corresponding surface is then a solution of \emph{Plateau's Problem}, which asks for a surface homeomorphic to a disk with boundary $g$ and minimum area.
 
@@
 %it corresponds to a homotopically critical point of $A_g$ of non-minimum type?
-In addition to the general theorem above, Morse and Tompkins also give an explicit example of a curve $g$ satisfying the assumptions, thus proving the existence of an unstable minimal surface.
+In addition to the general theorem above, Morse and Tompkins also give an explicit example of a curve $g$ satisfying the assumptions, thus proving the existence of an unstable minimal surface in the above sense.
 
-While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, the original approach of Morse and Tompkins is notable for its connection to persistent homology.
+%sci-hub.se/10.1215/S0012-7094-41-00828-1
+%
+%A point q of M will be termed non-minimizing if in every neighborhood of q there is a point p such thatF(p)<F(q).
+A homotopic critical set which is not a minimizing set contains at least one non-minimizing point of F.
+
+While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable for its close connection to persistent homology.
 
@@
 
-Morse and Tompkins' proof of the existence of unstable minimal surfaces is revisited in \cite{Morse.1940} using an argument that relies on Morse inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
+Parts of the framework of functional topology that Morse and Tompkins use is developed by Morse in \cite{Morse.1940} in a very general setting. 
+In particular, he proves inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
+From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical set of minimum type.
 
-We have seen that these inequalities require q-tameness, so in order to apply them and deduce their theorem, Morse and Tompkins need to prove the \mbox{q-tameness} of $(\Omega_g, A_g)$.
+We have seen that these inequalities require q-tameness, so in order to apply them in the minimal surface setting % and deduce their theorem,
+one needs to prove the \mbox{q-tameness} of the sublevel set filtration of the Douglas functional $A_g$.
 Throughout his work on functional topology, in order to obtain \mbox{q-tameness}, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations.
-In particular, in their applications to minimal surface theory, Morse and Tompkins used the following condition:
+In particular, Morse and Tompkins used the following condition in their applications to minimal surface theory (see also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain typographical errors):
 \begin{displaycquote}[p.~431]{Morse.1940}
+%\cite[p.~ 25]{Morse.1938}
 	Let $p$ be a point of $M$ at which $F(p)=c$.
@@
 
-Specifically, \v{C}ech homology is infinite dimensional in degree $d$ for the $d$-dimensional Hawaiian earring. 
-To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
-Define
-\begin{align*}
-\HE_k &=
-\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\, \cup
-\bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
-\end{align*}
-i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
-We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \F) = \lim_{k} \CH_{d}(\HE_{k}; \F)$, where $\CH$ denotes \v{C}ech homology.
-Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
-\begin{equation*}
-\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \F)=\lim\left(\dots\to \prod_{n=1}^2\F\to \prod_{n=1}^1\F\to \prod_{n=1}^0\F\right)=\prod_{n\in\N}\F,
-\end{equation*}
-which is infinite-dimensional over $\F$.
-
+Specifically, using the the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ for the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
+%To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
+%Define
+%\begin{align*}
+%\HE_k &=
+%\left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle| \ \left( x_0 - \frac{1}{k} \right)^2 + x_1^2 + \dots + x_d^2 \leq \left( \frac{1}{k} \right)^2 \right\} \\ &\, \cup
+%\bigcup_{n=1}^{k-1} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle |\ \left( x_0 - \frac{1}{n} \right)^2 + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
+%\end{align*}
+%i.e., the $d$-dimensional Hawaiian earring but with the $k$-th largest $d$-sphere filled.
+%We have $\lim_{k} \HE_{k} = \bigcap_{k} \HE_{k} = \HE$, and hence $\CH_{d}(\HE; \F) = \lim_{k} \CH_{d}(\HE_{k}; \F)$, where $\CH$ denotes \v{C}ech homology.
+%Clearly, each $\HE_{k}$ is a CW-complex, so we can simply use cellular homology to compute
+%\begin{equation*}
+%\lim_{k}\CH_{d}(\mathbb{H}^{d}_{k}; \F)=\lim\left(\dots\to \prod_{n=1}^2\F\to \prod_{n=1}^1\F\to \prod_{n=1}^0\F\right)=\prod_{n\in\N}\F,
+%\end{equation*}
+%which is infinite-dimensional over $\F$.
 %We will consider the \emph{$d$-dimensional Hawaiian earring}
@@
 %\end{proof}
-
-As proven in \cite{Barratt.1962}, the singular homology of the Hawaiian earrings is also infinite dimensional. In summary, we have the following.
+Moreover, the singular homology of the $d$-dimensional Hawaiian earring is also infinite dimensional, as proven in \cite{Barratt.1962}. In summary, we have the following.
 
@@
 The gap we have thus highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
-This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of $(\Omega_g, A_g)$ actually establishes a stronger property described next.
+This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of the sublevel set filtration induced by $A_g$ can actually be seen to establish a stronger property described next.
 
@@
 Clearly, the filtration being $\LC$ implies that the filtration is also $\HLC$ for \v{C}ech homology with field coefficients, which is the homology theory Morse and Tompkins use.
-Therefore, from \cref{t:local connectedness implies q-tameness} we can conclude that $(\Omega_g, A_g)$ is indeed \mbox{q-tame} as needed.
+Therefore, from \cref{t:local connectedness implies q-tameness} we can conclude that the sublevel set filtration of $A_g$ is indeed \mbox{q-tame} as needed.
 This implies that the generalized Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem.

### 2022-03-28 referee_reply.tex
Add referee_reply file and first fixes

\documentclass{article}
\usepackage{csquotes}
\title{Author's reply to the referee report of \\
\textsc{``PERSISTENCE IN FUNCTIONAL TOPOLOGY: EXISTENCE OF PERSISTENCE DIAGRAMS AND MORSE INEQUALITIES''}
}
\begin{document}
	\maketitle
	\section{First point.} TBW

	\section{Second point.} TBW

	\section{Third point.} TBW

	\section{Additional suggestion.} TBW

	\section{List of typos, minor remarks and suggestions.}
	\begin{enumerate}
		\item Replaced as suggested (RAS), thank you.
		\item RAS, thank you.
		\item We did mean to ``functional analysis''. Thank you for the question.
		\item RAS, thank you.
		\item RAS, thank you.
		\item Before discussing more details of the stability result, including the concepts related to the metric theory of persistence modules we added the sentence:
		\begin{quote}
			We now provide more details regarding this result although they are not used in the present work.
		\end{quote}
		\item Definition moved as suggested.
		\item RAS, thank you.
		\item RAS, thank you.
		\item RAS, thank you.
		\item RAS, thank you. (ULI, PLEASE CHECK THIS CHANGE)
		\item RAS, thank you.
		\item (MAX, PLEASE ADDRESS THIS ONE)
		\item RAS, thank you.
		\item Replaced the preceding paragraph with:
		\begin{quote}
			In analogy to Morse's definitions, we may define, for an integer $d$ and real numbers $t$ and $\epsilon > 0$, the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as:
		\end{quote}
		(MAX, PLEASE CHECK THIS CHANGE)
		\item MAX, I REMEMBER ASKING YOU ABOUT THIS. WHAT WAS YOUR ANSWER? COULD YOU TAKE CARE OF THIS POINT?
		\item RAS, thank you.
		\item RAS, thank you.
		\item RAS, thank you.
		\item TBW
		\item RAS, thank you.
		\item (I THINK WE ARE ASSUMING HAUSDORFF, RIGHT? IS THIS NOT MENTIONED?)
		\item TBW
		\item TBW
		\item RAS, thank you.
		\item (I DO NOT KNOW)
		\item RAS, thank you.
		\item RAS, thank you.
		\item (I DO NOT KNOW)
		\item TO BE ADDRESS AFTER DISCUSSING WHAT ``homotopically critical point'' ARE.
		\item (I DO NOT KNOW)
		\item RAS, thank you.
		\item RAS, thank you.
		\item RAS, thank you.
		\item RAS, thank you.
		\item (I DO NOT KNOW)
		\item TBW
		\item (I DO NOT KNOW)
		\item RAS, thank you.
		\item TBW
	\end{enumerate}
\end{document}

### 2022-03-28 sec/connectivity.tex
Add referee_reply file and first fixes

@@
 	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+\end{defi}
+
+\begin{defi}
+	We say that a sublevel set filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
+	In this case, the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
 \end{defi}
@@
 
-Motivated by the example above, we introduce a stronger local connectivity condition for sublevel set filtrations that ensures its q-tameness without the strict continuity assumption.
+Motivated by the example above, we introduce a stronger local connectivity condition for sublevel set filtrations that ensures its q-tameness without the continuity assumption.
 
@@
 
-	Finally, using Mayer--Vietoris and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
+	Finally, using the Mayer--Vietoris property and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
 	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that

### 2022-03-28 sec/inequalities.tex
After spliting into ss Sect 5
Before addressing reviewer
Add referee_reply file and first fixes

@@
 By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\m_d \colon \mulDom \to \N$.
-In analogy to Morse's definitions, we may define the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
+In analogy to Morse's definitions, we may define, for an integer $d$ and real numbers $t$ and $\epsilon > 0$, the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
 \begin{equation*}
@@
 \end{equation*}
-Note that finiteness of these quantities is ensured by the q-tameness of $M$ and the use of a non-zero $e$ bounding below the persistence of the considered features.
+Note that finiteness of these quantities is ensured by the q-tameness of $M$ and the use of a non-zero $\epsilon$ bounding below the persistence of the considered features.
 To see the necessity of this second condition, consider the q-tame persistence module given by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$.
@@
 	\begin{equation*}
-	T = \{(p,q) \in \mulDom \mid t_0 \leq p < q \leq t_1\}.
+	T = \{(p,q) \in \mulDom \mid s \leq p < q \leq u\}.
 	\end{equation*}
@@
 	\begin{equation*}
-	\sum_{(p,q) \in T^{\geq e}} \n (p,q)
+	\sum_{(p,q) \in T^{\epsilon}} \n (p,q)
 	\ \leq \
@@
 	so the sequence given by
-	\[\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q)\]
+	\[\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q) \geq 0\]
 	satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
@@
 
-The finiteness conditions of our theorem are also satisfied for the Douglas functional considered by Morse and Tompkins as an application of Morse' theory of functional topology.
+The finiteness conditions of our theorem are also satisfied for the Douglas functional considered by Morse and Tompkins as an application of Morse's theory of functional topology.
 While the condition proposed by Morse turns out to be insufficient as shown in \cref{s:surfaces}, q-tameness is still guaranteed by \cref{t:local connectedness implies q-tameness} established in \cref{s:connectivity}.
@@
 	This notion is employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
-	The usefulness of this notion is might limited in many cases of interest.
+	The usefulness of this notion might however be limited in many cases of interest.
 	In Floer theory, for example, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.

### 2022-03-28 sec/introduction.tex
Add referee_reply file and first fixes

@@
 Morse used his theory of caps to study functionals on a metric space by analyzing the evolution of the topology of their sublevel sets.
-A key tool for this end is a version of his eponymous inequalities for cap numbers, which expands their usual version in the compact and smooth setting.
+A key tool to this end is a version of his eponymous inequalities for cap numbers, which expands their usual version in the compact and smooth setting.
 In this work, using persistence diagrams, we generalize the definition of these cap numbers to persistence modules and prove the existence of Morse inequalities for a large class of them (\cref{t:inequalities}).
@@
 Given the importance of persistence diagrams, in particular for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
-For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite dimensional rank.
+For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
@@
 We provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
-As an application of these result, we correct an inaccuracy in a result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
+As an application of these results, we correct an inaccuracy in a result by Morse, which was employed in the proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins.
 
@@
 It generalizes both their versions in the smooth and compact setting as well as the one used in functional topology.
-The core of this work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness for its associated persistence module.
+The core of this work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness of its associated persistence module.
 We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.

### 2022-03-28 sec/persistence.tex
Add referee_reply file and first fixes

@@
 \end{equation*}
-We say that this filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
-In this case, the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
 
@@
 
-The most commonly used existence result for barcode decompositions is due to Crawley-Boevey's \cite{Crawley-Boevey.2015}.
+The most commonly used existence result for barcode decompositions is due to Crawley-Boevey \cite{Crawley-Boevey.2015}.
 It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all $t \in \R$.
@@
 
-A persistence module $K$ is called \emph{ephemeral} if the maps $K_{s,t} \colon K_s \to K_t$ are $0$ for all $s < t$.
+A persistence module $M$ is called \emph{ephemeral} if the maps $M_{s,t} \colon M_s \to M_t$ are $0$ for all $s < t$.
 The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
@@
 As mentioned earlier, the passage from real-valued functions on a topological space to persistence diagrams is 1-Lipschitz for appropriate metrics.
-On the space of real-valued functions one considers the metric induced by the supremum norm, and for the space of persistence diagrams the \emph{bottleneck distance}.
-This metric expresses the distance between persistence diagrams by a matching of their points, counted with multiplicities, which is optimal with respect to the $L^{\infty}$-distance on $\mulDom$: two diagrams are within distance $\delta$ if any two matched points are within $L^{\infty}$-distance $\delta$, and any unmatched point has $L^{\infty}$-distance at most $2\delta$ to the diagonal $\{(p,q) \in \R^2 \mid p = q\}$.
+We now provide more details regarding this result although they are not used in the present work.
+On the space of real-valued functions one considers the metric induced by the supremum norm, and on the space of persistence diagrams the \emph{bottleneck distance}.
+This metric expresses the distance between persistence diagrams by a matching of their points, counted with multiplicities, which is optimal with respect to the $L^{\infty}$-distance on $\mulDom$: two diagrams are within distance $\delta$ if any two matched points are within $L^{\infty}$-distance $\delta$, and any unmatched point has $L^{\infty}$-distance at most $\delta$ to the diagonal $\{(p,q) \in \R^2 \mid p = q\}$.
 
@@
 Given two functors $M,N \colon \R \to \mathsf C$, where $\mathsf C$ is typically $\Top$ or $\Vect$, a $\delta$-interleaving between $M$ and $N$ consists of a pair of natural transformations $(M_t \to N_{t+\delta})_t$ and $(N_t \to M_{t+\delta})_t$ from one diagram to a shifted version of the other and vice versa, which compose to the structure maps $(M_t \to M_{t+2\delta})_t$ and $(N_t \to N_{t+2\delta})_t$.
-Clearly, the case $\delta=0$ describes an isomorphism, and the infimum $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
+Clearly, the case $\delta=0$ describes an isomorphism, and the infimum of $\delta$ for which $M$ and $N$ admit a $\delta$-interleaving is defined as the interleaving distance between them.
 $M$ and $N$ are isomorphic in the observable category if and only if they have interleaving distance $0$.

### 2022-03-28 sec/surfaces.tex
Add referee_reply file and first fixes

@@
 Let $g \colon \R \to \R^n$ be a $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
-Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi((t)+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
+Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi(t+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
 The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined as
@@
 \end{equation*}
-It coincides with the Dirichlet energy of the unique harmonic extension of the reparametrized curve $g \circ \phi$ to a parametrized surface.
+It coincides with the Dirichlet energy of the unique harmonic extension of the reparametrized curve $g \circ \varphi$ to a parametrized surface.
 The Dirichlet energy is an upper bound for the area, with equality if the parametrization is conformal.
@@
 In particular, he proves inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
-From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical set of minimum type.
+From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical sets of minimum type.
 
@@
 %, and a further condition called $F$-regularity, which is trivially satisfied if the domain of $F$ is compact.
-In the original (where the function is assumed to take values in $[0,1)$ the claim reads:
+In the original (where the function is assumed to take values in $[0,1)$) the claim reads:
 \begin{displaycquote}[Theorem 6.3, p.~432]{Morse.1940}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or weakly $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 
-Specifically, using the the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ for the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
+Specifically, using the the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
 %To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.

### 2022-03-28 sec/vietoris.tex
Add referee_reply file and first fixes

@@
 \end{equation*}
-For any field $\F$, the nerve construction composed with the functor of simplicial homology with coefficients in $\F$ define a functor from $\Cov(X)$ to the category of graded $\F$-vector spaces.
+For any field $\F$, the nerve construction composed with the functor of simplicial homology with coefficients in $\F$ defines a functor from $\Cov(X)$ to the category of graded $\F$-vector spaces.
 The \emph{\v{C}ech homology with coefficients in $\F$} of $X$ is defined as

### 2022-03-28 referee_reply.tex
Max addressing basic referee requests

@@
 \usepackage{csquotes}
-\title{Author's reply to the referee report of \\
-\textsc{``PERSISTENCE IN FUNCTIONAL TOPOLOGY: EXISTENCE OF PERSISTENCE DIAGRAMS AND MORSE INEQUALITIES''}
+\usepackage{hyperref}
+\usepackage[margin=1in]{geometry}
+
+\title{Author's reply to the referee report of \\ \textsc{
+    ``PERSISTENCE IN FUNCTIONAL TOPOLOGY: EXISTENCE OF PERSISTENCE DIAGRAMS AND MORSE INEQUALITIES''
     }
+}
+\author{Bauer \and Medina-Mardones \and Schmahl}
 \begin{document}
@@
 		\item Replaced as suggested (RAS), thank you.
-		\item RAS, thank you.
-		\item We did mean to ``functional analysis''. Thank you for the question.
-		\item RAS, thank you.
-		\item RAS, thank you.
+		\item RAS.
+		\item We did mean ``functional analysis''. Thank you for the question.
+		\item RAS.
+		\item RAS.
 		\item Before discussing more details of the stability result, including the concepts related to the metric theory of persistence modules we added the sentence:
@@
 		\item Definition moved as suggested.
-		\item RAS, thank you.
-		\item RAS, thank you.
-		\item RAS, thank you.
+		\item RAS.
+		\item RAS.
+		\item RAS.
 		\item RAS, thank you. (ULI, PLEASE CHECK THIS CHANGE)
-		\item RAS, thank you.
-		\item (MAX, PLEASE ADDRESS THIS ONE)
-		\item RAS, thank you.
+		\item RAS.
+		\item Removed ``finite'' from the informal description and changed the definition of $c_d^{\epsilon}(t)$ as suggested.
+		\item RAS.
 		\item Replaced the preceding paragraph with:
@@
 		\end{quote}
-		(MAX, PLEASE CHECK THIS CHANGE)
-		\item MAX, I REMEMBER ASKING YOU ABOUT THIS. WHAT WAS YOUR ANSWER? COULD YOU TAKE CARE OF THIS POINT?
-		\item RAS, thank you.
-		\item RAS, thank you.
-		\item RAS, thank you.
+		\item Replaced $N$ by $M$.
+		\item RAS.
+		\item RAS.
+		\item RAS.
 		\item TBW
-		\item RAS, thank you.
+		\item RAS.
 		\item (I THINK WE ARE ASSUMING HAUSDORFF, RIGHT? IS THIS NOT MENTIONED?)
+		Max: I guess not in general.
+Here, we want the version 3' of local compactness from \url{https://en.wikipedia.org/wiki/Locally_compact_space}, which is only equivalent to weaker versions for Hausdorff spaces.
+We apply the lemma only to Hausdorff spaces, so it's fine to add the assumption.
+
+		Added Hausdorff assumption as suggested, also added the assumption for the domain $Y$ to be compact in the main lemma. 
 		\item TBW
-		\item TBW
-		\item RAS, thank you.
-		\item (I DO NOT KNOW)
-		\item RAS, thank you.
-		\item RAS, thank you.
+		\item RAS.
+		\item RAS.
+		\item Assumption that $\varphi$ should be non-decreasing was indeed missing and has been added, thank you.
+		\item RAS.
+		\item RAS.
 		\item (I DO NOT KNOW)
@@
 		\item (I DO NOT KNOW)
-		\item RAS, thank you.
-		\item RAS, thank you.
-		\item RAS, thank you.
-		\item RAS, thank you.
-		\item (I DO NOT KNOW)
-		\item TBW
-		\item (I DO NOT KNOW)
-		\item RAS, thank you.
-		\item TBW
+		Max: Not making a change, yet, but i think the referee is correct.
+As stated right now "minimum type" would only refer to global minima, but it should probably also refer to local minima.
+Please check this, Uli.
+		\item RAS.
+		\item RAS.
+		\item RAS.
+		\item RAS.
+		\item RAS.
+		\item Made it clearer that the results in the appendix are not original and added suggested references in the first paragraph.
+		\item Added a remark as suggested at the end.
+		\item RAS.
+		\item Explained that this indeed follows from Lebesgue's number lemma.
 	\end{enumerate}

### 2022-03-28 sec/connectivity.tex
Max addressing basic referee requests

@@
 \begin{lem} \label{l:neighborhood third}
-	Let $X$ be a locally compact space.
+	Let $X$ be a locally compact Hausdorff space.
 	For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $f \colon Y \to \R$ be a function on a locally compact space $Y$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq Y$ with $C$ compact and $L$ open.
+	Let $f \colon Y \to \R$ be a function on a locally compact Hausdorff space $Y$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq Y$ with $C$ compact and $L$ open.
 	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
@@
 
-	Assuming them for the moment, the first property allows us to cover $C$ by sets $V_x \in \Sigma_{s,t}$, $x \in C$.
-	Because $C$ is compact, this cover can be chosen finite, represented by say $x_1,\dots, x_m$.
+	Assuming them for the moment, the first property allows us to cover $C \cap f_{\leq s}$ by sets $V_x \in \Sigma_{s,t}$, $x \in C \cap f_{\leq s}$.
+	Because both $C$ and $f_{\leq s}$ are compact, $C \cap f_{\leq s}$ is again compact, and hence the cover can be chosen finite, represented by say $x_1,\dots, x_m$.
 	By the second property, we have

### 2022-03-28 sec/inequalities.tex
Max addressing basic referee requests

@@
 This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of finite bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of finite bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
 
@@
 c_{d}^{\epsilon}(t) \ =
-\sum_{\substack{p \in \R \\ t - p > \epsilon}} \m_{d-1}(p, t) \ +
-\sum_{\substack{q \in \R \\ q - t > \epsilon}} \m_d(t, q).
+\sum_{\substack{p \in \R \cup \{-\infty\} \\ t - p > \epsilon}} \m_{d-1}(p, t) \ +
+\sum_{\substack{q \in \R \cup \{\infty\} \\ q - t > \epsilon}} \m_d(t, q).
 \end{equation*}
@@
 \begin{defi} \label{d:initially and eventually constant}
-	A persistence module $N$ is said to be \emph{initially constant} if there is $s \in \R$ such that $N_{r,s}$ is an isomorphism for all $r \leq s$.
+	A persistence module $M$ is said to be \emph{initially constant} if there is $s \in \R$ such that $M_{r,s}$ is an isomorphism for all $r \leq s$.
 	Similarly, it is said to be \emph{eventually constant} if there is $u \in \R$
-	such that $N_{u,v}$ is an isomorphism for all $u \leq v$.
+	such that $M_{u,v}$ is an isomorphism for all $u \leq v$.
 \end{defi}
@@
 \begin{thm} \label{t:cap numbers well defined}
-	Let $N$ be a q-tame persistence module that is both initially and eventually constant.
-	If $\n$ is the multiplicity function of the persistence diagram of $N$,
+	Let $M$ be a q-tame persistence module that is both initially and eventually constant.
+	If $\m$ is the multiplicity function of the persistence diagram of $N$,
 	then for each $\epsilon > 0$,
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) < \infty.
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \m (p,q) < \infty.
 	\end{equation*}
@@
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \n (p,q) \ = \!\!
-	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q) \ +
-	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \mulDom \\ q-p > \epsilon } } \m (p,q) \ = \!\!
+	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \m (p,q) \ +
+	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \m (p,q)
 	\end{equation*}
@@
 
-	For the first summand, observe that, because $N$ is constant below $s$ and constant above $u$, we have $\n(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
+	For the first summand, observe that, because $M$ is constant below $s$ and constant above $u$, we have $\m(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
 	This implies
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in \mulDom \setminus T \\ q-p > \epsilon } } \m (p,q)
 	\ = \!
-	\sum_{s < q < u} \n (-\infty,q)
+	\sum_{s < q < u} \m (-\infty,q)
 	\ + \!
-	\sum_{s < p < u} \n (p, \infty)
+	\sum_{s < p < u} \m (p, \infty)
 	\end{equation*}
-	which is clearly finite because $N$ is q-tame.
+	which is clearly finite because $M$ is q-tame.
 
@@
 	\begin{equation*}
-	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \n (p,q)
+	\sum_{ \substack{ (p,q) \in T \\ q-p > \epsilon } } \m (p,q)
 	\ \, \leq \!\!
-	\sum_{(p,q) \in T^{\epsilon}} \n (p,q),
+	\sum_{(p,q) \in T^{\epsilon}} \m (p,q),
 	\end{equation*}
@@
 	\begin{equation*}
-	\sum_{(p,q) \in T^{\epsilon}} \n (p,q)
+	\sum_{(p,q) \in T^{\epsilon}} \m (p,q)
 	\ < \
@@
 	\begin{equation*}
-	\sum_{(p,q) \in T^{\epsilon}} \n (p,q)
+	\sum_{(p,q) \in T^{\epsilon}} \m (p,q)
 	\ \leq \
-	\sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{\epsilon}{2})}} \n(p,q).
+	\sum_{i=1}^n \sum_{\substack{(p, q) \in \\ Q (x_i, x_i + \frac{\epsilon}{2})}} \m(p,q).
 	\end{equation*}
-	Each of the sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{\epsilon}{2} \right)} \n(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{\epsilon}{2} \right)$ is finite since $N$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
+	Each of the sums $\sum_{(p,q) \in Q \left(x_i, x_i + \frac{\epsilon}{2} \right)} \m(p,q)$ over the quadrants $Q \left(x_i, x_i + \frac{\epsilon}{2} \right)$ is finite since $M$ is q-tame (which is where the name q-tame or \emph{quadrant}-tame comes from, see \cite[Section 3.8]{Chazal.2016a}).
 \end{proof}

### 2022-03-28 sec/surfaces.tex
Max addressing basic referee requests

@@
 Let $g \colon \R \to \R^n$ be a $2\pi$-periodic function representing a simple closed curve such that $g$ is differentiable with Lipschitz derivative.
-Let $\widetilde{\Omega}$ be the space of continuous functions $\varphi \colon \R \to \R$ with $\varphi(t+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
+Let $\widetilde{\Omega}$ be the space of continuous non-decreasing functions $\varphi \colon \R \to \R$ with $\varphi(t+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
 The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined as
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or weakly $\LC$ if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or \emph{weakly $\LC$} if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally connected} $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}

### 2022-03-28 sec/vietoris.tex
Max addressing basic referee requests

@@
 For greater generality, in this paper we considered \v{C}ech homology instead of the homology construction used by Morse in functional topology: metric Vietoris homology.
-We now justify this choice by showing that these two constructions agree on compact metric spaces.
+We now justify this choice by reminding the reader that these two constructions agree on compact metric spaces following \cite{Dowker.1952}.
+For an earlier approach, the reader may also wish to consult \cite[Section VII.6]{Lefschetz.1942}.
 
@@
 \end{equation*}
-However, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they both define the same limit.
+If the metric space $X$ is compact, then for each cover $\alpha$ there exists $\lambda > 0$ by Lebesgue's number lemma such that $(B_{\lambda}(x))_{x \in X}$ refines $\alpha$.
+In other words, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they yield the same limit.
 Thus, in this case we have a natural isomorphism
@@
 \end{equation*}
-In other words, for compact metric spaces the metric Vietoris homology theory employed in Morse's setting is canonically isomorphic to the \v{C}ech homology we consider in this paper.
+In other words, for compact metric spaces the metric Vietoris homology theory employed in Morse's setting is isomorphic to the \v{C}ech homology we consider in this paper.
+Note that the relevant isomorphisms above can all be seen to be natural with respect to continuous maps (see in particular \cite[Lemma 7a]{Dowker.1952}), so that in particular both homology constructions yield the same persistence modules when applied to sublevel set filtrations.

### 2022-03-28 sec/introduction.tex
Reorder to address point 2 of the reviewer

@@
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{t:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
+We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
 

### 2022-03-29 referee_reply.tex
Add description of changes to point 1 and 2 in reply
Updates from Overleaf

@@
 	\maketitle
-	\section{First point.} TBW
+	\section{First point.} We have added a complete and self-contained formulation of our main result (Theorem 4.7 in the reviewers copy) to the introduction.
 
-	\section{Second point.} TBW
+	A: What should we do about THM 5.1?
+
+	\section{Second point.} Thank you for the suggestions.
+	We have implemented them all as requested.
 
@@
 We apply the lemma only to Hausdorff spaces, so it's fine to add the assumption.
+		Added Hausdorff assumption as suggested, also added the assumption for the domain $Y$ to be Hausdorff in the main lemma.
 
-		Added Hausdorff assumption as suggested, also added the assumption for the domain $Y$ to be compact in the main lemma. 
 		\item TBW

### 2022-03-29 sec/connectivity.tex

@@
 
-\subsection{Weak local connectivity and q-tameness}
+\subsection{Local connectivity and q-tameness}
 
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 	We say that a sublevel set filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
-	In this case, the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
 \end{defi}
 
-The following result is deduced directly from \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} below.
-The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
+If $f_{\leq t}$ is compact then the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
 
-\begin{thm} \label{t:q-tameness for continuous functions}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
-\end{thm}
-
-As the following example illustrates, the continuity assumption in the above theorem is crucial.
-Consider the \emph{$d$-dimensional Hawaiian earring}
-\begin{equation*}
-\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
-\end{equation*}
-which is a compact subspace of $\R^{d+1}$.
-
-\begin{figure}[t]
-	\centering
-	\begin{tikzpicture}[scale = 60]
-	\draw[thick,lightgray] (-.1,-.001) rectangle (.1,.05);
-	\clip (-.1,0) rectangle (.1,.05);
-	\foreach \i in {1,...,100}{
-		\draw[line width=0.4/\i^0.25 pt] (0, 1/\i^2) circle (1/\i^2);
-	}
-	\end{tikzpicture}
-	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
-\end{figure}
-
-\begin{thm} \label{t:counterexample}
-	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\HLC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
-\end{thm}
-
-\begin{proof}
-	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
-
-	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
-	We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-	Since we assume that $\H_{n}$ is homotopy invariant and takes singletons to finite dimensional spaces, it suffices to find $U$ as above such that $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
-
-	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
-	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\HLC$ condition is trivially satisfied.
-
-	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
-	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
-	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
-	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
-
-	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
-	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
-\end{proof}
-
-\subsection{Local connectivity and q-tameness}
-
-Motivated by the example above, we introduce a stronger local connectivity condition for sublevel set filtrations that ensures its q-tameness without the continuity assumption.
-
-\begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-\end{defi}
-
-Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
-while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
-If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
-
-\begin{thm} \label{t:weak hlc to hlc}
-	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also $\HLC$.
-\end{thm}
-
-\begin{proof}
-	Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
-	We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-
-	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
-	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
-	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of~$X$.
-
-	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
-	This second map is $\HS$ by construction.
-	Any map that factors through an $\HS$ map is also $\HS$, so the proof is complete.
-\end{proof}
-
-Our main technical result, proven in the remainder of this subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+Our main result, proven in the remainder of this subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
 
@@
 \end{proof}
+
+\subsection{Continuity}
+
+We now describe a weaker version of local connectivity of sublevel set filtrations that implies q-tameness when continuity is assumed.
+
+\begin{defi}
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+\end{defi}
+
+Clearly, any $\HLC$ sublevel set filtration is also weakly $\HLC$:
+while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
+If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
+
+\begin{lem} \label{l:weak hlc to hlc}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is weakly $\HLC$, then it is also $\HLC$.
+\end{lem}
+
+\begin{proof}
+	Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
+	We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+
+	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
+	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
+	Note that this choice of $U$ still defines a neighborhood of $x$ because $f$ is assumed to be continuous, so that $f_{< s'}$ is an open subset of~$X$.
+
+	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
+	This second map is $\HS$ by construction.
+	Any map that factors through an $\HS$ map is also $\HS$, so the proof is complete.
+\end{proof}
+
+The following result is deduced directly from \cref{l:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness}.
+The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
+
+\begin{cor} \label{c:q-tameness for continuous functions}
+	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
+\end{cor}
+
+As the following example illustrates, the continuity assumption in the above theorem is crucial.
+
+\begin{figure}[t]
+	\centering
+	\begin{tikzpicture}[scale = 60]
+		\draw[thick,lightgray] (-.1,-.001) rectangle (.1,.05);
+		\clip (-.1,0) rectangle (.1,.05);
+		\foreach \i in {1,...,100}{
+			\draw[line width=0.4/\i^0.25 pt] (0, 1/\i^2) circle (1/\i^2);
+		}
+	\end{tikzpicture}
+	\caption{A closeup of the Hawaiian earring $\mathbb{H}^1$.}
+\end{figure}
+
+\begin{example} \label{e:counterexample}
+	Consider the \emph{$d$-dimensional Hawaiian earring}
+	\begin{equation*}
+		\HE = \bigcup_{n \in \N} \left\{ (x_0, \dots, x_d) \in \R^{d+1} \ \middle | \ \left( x_0 - \frac{1}{n} \right)^2 \!\! + x_1^2 + \dots + x_d^2 = \left( \frac{1}{n} \right)^2 \right\},
+	\end{equation*}
+	which is a compact subspace of $\R^{d+1}$.
+	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\HLC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
+
+	To verify that $f$ has compact sublevel sets we notice that all sublevel sets are either the empty set, the singleton containing the origin, or $\HE$ itself, all compact Hausdorff spaces.
+
+	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
+	We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	Since we assume that $\H_{n}$ is homotopy invariant and takes singletons to finite dimensional spaces, it suffices to find $U$ as above such that $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+
+	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
+	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\HLC$ condition is trivially satisfied.
+
+	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
+	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
+	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
+	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+
+	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
+	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+\end{example}

### 2022-03-29 sec/introduction.tex

@@
 For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
-The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
+The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology.
+We now present the answers provided in this work.
 
-To illustrate the applicability of these results we return to the original setting of the Douglas functional that motivated the development of functional topology.
+The persistence module associated to a filtration depends on the homology construction used, which even agreeing on cellular spaces, need not coincide for general topological spaces.
+We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open of closed sets, for example singular or \v{C}ech homology respectively
+
+The sublevel set filtration $f_{\leq t} = f^{-1}(-\infty, t]$ of a real valued function $f$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is \emph{homologically small}; that is to say, for a given homology theory the induced map has finite rank in every degree.
+We say that a sublevel set filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
+We can now state our main result (\cref{t:local connectedness implies q-tameness}):
+
+\begin{thm*}
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
+\end{thm*}
+
+\noindent We also introduce a weaker local-connectivity condition that can be used instead of $\HLC$ in the statement above if the filtration is defined by a continuous functional (\cref{c:q-tameness for continuous functions}).
+
+To illustrate the applicability of our results we return to the original setting of the Douglas functional that motivated the development of functional topology.
 This functional satisfies the hypotheses of \cref{t:local connectedness implies q-tameness}, so its associated persistent \v{C}ech homology is indeed q-tame and admits a persistence diagram.

### 2022-03-29 sec/surfaces.tex

@@
 Morse does not prove this statement in the given reference, but rather refers to \cite[Theorem~6.1]{Morse.1938}.
-Unfortunately, the above claim does not hold in general, as exemplified by the sublevel set filtration from \cref{t:counterexample}.
+Unfortunately, the above claim does not hold in general, as exemplified by the sublevel set filtration from \cref{e:counterexample}.
 To elaborate on this, we consider a stronger version of weak local connectedness.
@@
 Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one-point spaces, also weakly $\HLC$.
-Observe that the proof of \cref{t:counterexample} actually establishes that the filtration given there is weakly $\LC$, so not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions in general.
-In particular, our construction invalidates Morse's claim quoted above because \v{C}ech homology satisfies the assumptions on the homology theory made in \cref{t:counterexample}.
+Observe that \cref{e:counterexample} actually establishes that the filtration given there is weakly $\LC$, so not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions in general.
+In particular, our construction invalidates Morse's claim quoted above because \v{C}ech homology satisfies the assumptions on the homology theory made in \cref{e:counterexample}.
 

### 2022-03-29 sec/vietoris.tex

@@
 \end{equation*}
-If the metric space $X$ is compact, then for each cover $\alpha$ there exists $\lambda > 0$ by Lebesgue's number lemma such that $(B_{\lambda}(x))_{x \in X}$ refines $\alpha$.
+If the metric space $X$ is compact, then for each cover $\alpha$ there exists $\lambda > 0$ by Lebesgue's number lemma \cite[Lemma 27.5]{Munkres.2000} such that $(B_{\lambda}(x))_{x \in X}$ refines $\alpha$.
 In other words, if the metric space $X$ is compact, then $\Balls (X)$ is coinitial in $\Cov (X)$, that is to say, they yield the same limit.

### 2022-04-25 referee_reply.tex
Add proof of UMST

@@
 
-	\section{Third point.} TBW
+	\section{Third point.} Thank you for the suggestions. 
+	We have included a proof of the Unstable Minimal Surface Theorem and a formal definition of the notion of homotopically critical point in Section 5.1, mostly following the general outline that was suggested.
+	The proof is broken down into some intermediate lemmas and cites Morse--Tompkins and Struwe as necessary.
+	We have also added the notions of \emph{number of births} and \emph{number of deaths} in the section on persistence and gave some basic formulas to compute them, which was necessary to make the later proofs work.
 
-	\section{Additional suggestion.} TBW
+	\section{Additional suggestion.} We have implemented the conceptually easier proof of the Morse inequalities as suggested, thank you.
 
@@
 		\item RAS.
-		\item RAS, thank you. (ULI, PLEASE CHECK THIS CHANGE)
+		\item RAS. (@Uli, please check this change.)
 		\item RAS.
@@
 		\item RAS.
-		\item TBW
+		\item Paragraph has been reformulated.
 		\item RAS.
-		\item (I THINK WE ARE ASSUMING HAUSDORFF, RIGHT? IS THIS NOT MENTIONED?)
-		Max: I guess not in general.
-Here, we want the version 3' of local compactness from \url{https://en.wikipedia.org/wiki/Locally_compact_space}, which is only equivalent to weaker versions for Hausdorff spaces.
-We apply the lemma only to Hausdorff spaces, so it's fine to add the assumption.
-		Added Hausdorff assumption as suggested, also added the assumption for the domain $Y$ to be Hausdorff in the main lemma.
-
-		\item TBW
+		\item Clarified as suggested by adding the Hausdorff assumption explicitly.
+		\item RAS.
 		\item RAS.
@@
 		\item RAS.
-		\item (I DO NOT KNOW)
-		\item TO BE ADDRESS AFTER DISCUSSING WHAT ``homotopically critical point'' ARE.
-		\item (I DO NOT KNOW)
-		Max: Not making a change, yet, but i think the referee is correct.
-As stated right now "minimum type" would only refer to global minima, but it should probably also refer to local minima.
-Please check this, Uli.
+		\item The sentence ``for a large class of curves'' seems to have been a remnant of a previous version where we did not make the assumptions on the curve explicit.
+We have removed this part and included a precise reference to the relevant part in Morse--Tompkins' paper.
+		\item RAS.
+		\item It should have indeed said ``there exists a neighborhood'' instead of ``for every neighborhood''.
+We also realised there was another assumption missing: The neighborhood should not only contain the critical set but in fact its closure -- in general a critical set will only be closed in its level set, but not necessarily in the whole space.
 		\item RAS.
@@
 	\end{enumerate}
+
+	\section{Other changes}
+	The notion that was formerly called 'homotopically locally connected' is now simply called 'locally connected of all orders' and the notion that was formerly called 'locally connected' is now called 'locally contractible', which seems to be more in line with the existing literature.
 \end{document}

### 2022-04-25 sec/inequalities.tex
Add proof of UMST

@@
 \begin{equation} \label{e:classical morse inequalities}
-\sum_{d=0}^n \ (-1)^{n-d} \big( \# \crit_{d}(f) - \beta_{d}(X) \big) \ \geq \ 0,
+\sum_{d=0}^n \ (-1)^{n-d} \big( c_{d}(f) - \beta_{d}(X) \big) \ \geq \ 0,
 \end{equation}
-where $\crit_{d}(f)$ is the set of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d\th$ Betti number of $X$.
+where $c(f)$ is the number of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d\th$ Betti number of $X$.
 
@@
 To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
+In the compact smooth setting, for sufficiently small $\epsilon$, the $(d, t, \epsilon)$-cap number equals the number of critical points of index $d$ and value $t$.
 
@@
 \begin{thm} \label{t:inequalities}
-	Let $M$ be a graded q-tame persistence module with finite cap numbers $c_{d}^{\epsilon}$ and finite essential dimensions $p_{d}$ for all $d$ and $\epsilon$.
+	Let $\epsilon > 0$, and let $M$ be a graded q-tame persistence module
+	with finite cap numbers $c_{d}^{\epsilon}$ and finite essential dimensions $p_{d}$ for all $d$.
 	If $\m_d(-\infty, p) = 0$ for all $p \in \R \cup \{\infty\}$ and all $d$, then we have Morse inequalities
@@
 	\end{equation}
-	for any dimension $n$ and any $\epsilon > 0$.
+	for any dimension $n$.
 \end{thm}
@@
 \begin{proof}
-	Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$.
+The $d$th $\epsilon$-cap number is
+\[c_{d}^{\epsilon} = \alpha_{d}^{\epsilon} + \omega_{d-1}^{\epsilon},\] 
+where
+\begin{align*}
+\alpha_{d}^{\epsilon} \ &=
+\sum_{\substack{(p,q) \in \mulDom \\ p\neq\infty, q - p > \epsilon}} \m_d(p, q),
+&
+\omega_{d}^{\epsilon} \ &=
+\sum_{\substack{(p,q) \in \mulDom \\ q\neq-\infty, q - p > \epsilon}} \m_{d}(p, q)
+\end{align*}
+count the multiplicity of left endpoints $p$ and right endpoints $q$, respectively, in elements $(p,q) \in \mulDom$ in the persistence diagram for $M$ that have degree $d$ and persistence $q-p > \epsilon$.
 Since we assume $\m_d(-\infty, p) = 0$ for all $p$, we have
-	\begin{align*}
-	c_{d}^{\epsilon} \ &=
-	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ =
-	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon }} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)
-	\end{align*}
-	and
 	\begin{equation*}
-	p_{d} \ = \!\!\!
-	\sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty) \ = \
-	\sum_{p \in \R} \m_d(p,\infty),
+	p_{d} \ = \alpha_{d}^{\epsilon} - \omega_{d}^{\epsilon}
 	\end{equation*}
-	which yields
-	\begin{align*}
-	c_{d}^{\epsilon} - p_{d} \ &=
-	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q) \ +
-	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
-	\sum_{p \in \R} \m_d(p,\infty) \\ &=
-	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q)
-	\ + \!
-	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q),
-	\end{align*}
-	so the sequence given by
-	\[\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q) \geq 0\]
-	satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+The difference of the two numbers, which appears in the Morse inequalities to be shown, is thus
+\[
+c_{d}^{\epsilon} - p_{d} = \omega_{d-1}^{\epsilon} + \omega_{d}^{\epsilon},
+\]
+and their sum is
+\[
+\sum_{d=0}^n \ (-1)^{n-d} (c_{d}^{\epsilon} - p_{d}) = \omega_{n}^{\epsilon} \geq\ 0
+\]
+as claimed.
 \end{proof}
+
+In other words, given the assertion that the persistence module $M$ has a persistence diagram, the Morse inequalities simply express the fact that the number of right endpoints in nonnegative.
+% This observation emphasizes the role of persistence in interpreting fundamental facts in Morse theory.
+This observation illustrates the usefulness of interpreting fundamental facts in Morse theory through the lens of persistence theory.
+
+%\begin{proof}
+%	Using a telescopic sum argument, the claimed inequalities can be seen to be equivalent to the existence of a sequence $(\nu_d)_d$ of non-negative integers with $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$.
+%	Since we assume $\m_d(-\infty, p) = 0$ for all $p$, we have
+%	\begin{align*}
+%	c_{d}^{\epsilon} \ &=
+%	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
+%	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ =
+%	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon }} \m_{d-1}(p,q) \ +
+%	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q)
+%	\end{align*}
+%	and
+%	\begin{equation*}
+%	p_{d} \ = \!\!\!
+%	\sum_{p \in \R \cup \{-\infty\}} \m_d(p,\infty) \ = \
+%	\sum_{p \in \R} \m_d(p,\infty),
+%	\end{equation*}
+%	which yields
+%	\begin{align*}
+%	c_{d}^{\epsilon} - p_{d} \ &=
+%	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q) \ +
+%	\sum_{\substack{(p,q) \in \mulDom \\ q-p > \epsilon \\ p \neq -\infty}} \m_d(p,q) \ - \
+%	\sum_{p \in \R} \m_d(p,\infty) \\ &=
+%	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_{d-1}(p,q)
+%	\ + \!
+%	\sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q),
+%	\end{align*}
+%	so the sequence given by
+%	\[\nu_d = \sum_{\substack{(p,q) \in \R^2 \\ q-p > \epsilon}} \m_d(p,q) \geq 0\]
+%	satisfies the equation $c_{d}^{\epsilon} - p_{d} = \nu_{d-1} + \nu_{d}$ as desired.
+%\end{proof}
 
@@
 
-The finiteness conditions of our theorem are also satisfied for the Douglas functional considered by Morse and Tompkins as an application of Morse's theory of functional topology.
-While the condition proposed by Morse turns out to be insufficient as shown in \cref{s:surfaces}, q-tameness is still guaranteed by \cref{t:local connectedness implies q-tameness} established in \cref{s:connectivity}.
-As mentioned before, our inequalities then agree with Morse's historical version from functional topology as presented in \cite[Corollary~12.3]{Morse.1940} if the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, which is satisfied for compact sublevel set filtrations if one uses \v{C}ech homology, as is the case in Morse's work.
-Note however that, in contrast to Morse's version, our inequalities also hold without the assumption of continuity from above, expanding their use beyond \v{C}ech type theories.
+The finiteness conditions of our theorem are also satisfied by the Douglas functional considered by Morse and Tompkins as an application of Morse's theory of functional topology.
+The details in \cite{Morse.1939} are incomplete, with some crucial theorems being stated without proof, and with a citation to a paper in preparation that has never been published under the same name (we suppose that this paper is \cite{Morse.1940}).
+Nevertheless, Morse and Tompkins establish the conditions required for \cref{t:local connectedness implies q-tameness}, from which we can deduce q-tameness and obtain Morse inequalities by \cref{t:inequalities}.
+While Morse's approach is restricted to \v{C}ech homology, and singular homology is explicitly excluded due to a lack of continuity, our approach is more flexible and applies to any setting where persistent homology is q-tame.
+If the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, our inequalities agree with Morse's historical version from functional topology as presented in \cite[Corollary~12.3]{Morse.1940}.
 
 \begin{rem} \label{r:homotopically critial points}
-	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposes a generalized version of critical points, which he calls homotopically critical, and which formalizes the idea of criticality of a point in terms of topological changes in the sublevel set filtration.
-	This notion is employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
+	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposed a generalized version of critical points, which he called homotopically critical, and which formalizes the idea of criticality of a point in terms of topological changes in the sublevel set filtration.
+	This notion was employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
 	The usefulness of this notion might however be limited in many cases of interest.

### 2022-04-25 sec/introduction.tex
Add proof of UMST

@@
 For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
-The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology.
+The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
 We now present the answers provided in this work.
@@
 The persistence module associated to a filtration depends on the homology construction used, which even agreeing on cellular spaces, need not coincide for general topological spaces.
-We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open of closed sets, for example singular or \v{C}ech homology respectively
+We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open of closed sets, for example singular or \v{C}ech homology, respectively.
 

### 2022-04-25 sec/persistence.tex
Add proof of UMST

@@
 Intuitively, one may think of the observable category as forgetting all information in persistence modules that does not persist over a non-zero amount of time.
-In certain situations, no information is lost in this process, for example if the persistence module $M$ can be assumed to be \emph{continuous from above}, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}.
-This assumption is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology; in this setting, both the filtration as well as the resulting persistence module are continuous from above.
+In certain situations, no information is lost in this process, for example if the persistence module $M$ can be assumed to be \emph{continuous from above at $s$} for all~$s \in \R$, i.e., $M_{s} \to \lim_{s < t} M_{t}$ is an isomorphism for all~$s \in \R$ \cite{Schmahl.2021}.
+Alternatively, one may also impose the condition that $M$ be \emph{continuous from below at $t$} for all~$t \in \R$, i.e., $\colim_{s < t} M_{s} \to M_{t}$ is an isomorphism for all~$t \in \R$.
+Continuity from above is satisfied in Morse's setting of studying compact sublevel set filtrations with \v{C}ech homology; in this setting, both the filtration as well as the resulting persistence module are continuous from above.
 In terms of barcodes, continuity from above amounts to only admitting intervals that are closed on the left and open on the right.
@@
 In this approach, by far the most difficult step is showing that passing from persistence modules to persistence diagrams is stable, a result which is known as the Algebraic Stability Theorem \cite{Chazal.2009, Bauer.2015, Chazal.2016a}.
+
+We will now finish this section by recording some helpful facts about the \emph{number of births at $t$}
+\[
+	\alpha(t) = \sum_{q \in (t, \infty]} \m(t,q)
+\]
+and the \emph{number of deaths at $t$}
+\[
+	\omega(t) = \sum_{p \in [-\infty, t)} \m(p,t)
+\]
+for a q-tame persistence module $M$ with persistence diagram given by $\m$.
+%\begin{defi}
+%	Let $M$ be a q-tame persistence module with persistence diagram given by $\m$. 
+%	For $t \in \R$ we define the \emph{number of births at $t$} as
+%	\[
+%		\alpha(t) = \sum_{q \in (t, \infty]} \m(t,q)
+%	\]
+%	and the \emph{number of deaths at $t$} as 
+%	\[
+%		\omega(t) = \sum_{p \in [-\infty, t)} \m(p,t).
+%	\]
+%\end{defi}
+
+\todo{should we somehow unify definitions of $\alpha$, $\omega$, $c$ etc. in a single place? compare also the use of $\alpha^{\epsilon}$ and $\omega^{\epsilon}$ in the proof of \cref{t:inequalities}}
+
+\begin{lem}
+\label{lem:birth_death_formulas}
+	Let $M$ be a q-tame persistence module.
+	For each $t \in \R$ we either have 
+	\[
+		\alpha(t) = \dim \coker (\colim_{s < t} M_{s} \to \lim_{u > t} M_{u})
+	\]
+	or both quantities are infinite.
+	Similarly, we either have 
+	\[
+		\omega(t) = \dim \ker (\colim_{s < t} M_{s} \to \lim_{u > t} M_{u})
+	\]
+	or both quantities are infinite.
+\end{lem}
+\begin{proof}
+	None of the quantities appearing in the statement change if we replace $M$ by its radical.
+	This radical admits a barcode decomposition and the claims easily follow from an explicit computation on the corresponding barcode module.
+\end{proof}
+
+If $M$ is continuous from below or above, then the colimits and limits appearing in the formulas above may simply be replaced by constituent vector spaces of $M$. 
+As a special case, this yields the following corollary.
+
+\begin{cor}
+\label{cor:regular_value_no_endpoint}
+	Let $M$ be a q-tame persistence module.
+	If $M$ is continuous from above and below at $t$ we have
+	\[
+		\alpha(t) = \omega(t) = 0.
+	\]
+\end{cor}

### 2022-04-25 sec/surfaces.tex
Add proof of UMST

@@
 Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$, equipped with the $C^0$ metric.
-Douglas proved that, for a large class of curves~$g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
+The set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact \cite[p.~448]{Morse.1939}.
 Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimum.
@@
 As alluded to in \cref{r:homotopically critial points}, Morse and Tompkins consider a homotopical notion of critical point for a general function $F \colon M \to \R$ on a metric space \cite[p.~445]{Morse.1939}, see also \cite{Morse.1943}.
-Roughly, a point $p$ is \emph{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
+%Roughly, a point $p$ is \emph{homotopically critical} if it has no neighborhood in $F_{\leq F(p)}$ that can be mapped by a homotopy into $F_{\leq t}$ for some $t<F(p)$.
 
-Morse and Tompkins prove \cite[p.~464]{Morse.1939} that each homotopically critical point of the functional $A_g$ indeed corresponds to
+\begin{defi}[{{\cite[Definition II.6.1-II.6.2]{Struwe.1988},\cite[p.~445, 472]{Morse.1939}}}]
+	Consider a real-valued function $F$ on a metric space $(M,d)$.
+	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$ satisfying $\varphi(p,1) \neq p$ such that for every compact subset $V \subseteq U$ there exists a function $\delta \colon \R_{\geq 0} \to \R_{\geq 0}$ with
+	$\delta(e) = 0$ if and only if $e = 0$, and
+	\[
+	F(\varphi(x,s)) - F(\varphi(x,t)) > \delta(d(\varphi(x,s),\varphi(x,t)))
+	\]
+	for all $x \in V$ and $0 \leq s \leq t \leq 1$.
+% 	\begin{itemize}
+% 		\item $\delta(e) = 0$ if and only if $e = 0$, and
+% 		\item $F(\varphi(x,s)) - F(\varphi(x,t)) > \delta(d(\varphi(x,s),\varphi(x,t)))$ for all $x \in V$ and $0 \leq s \leq t \leq 1$.
+% 	\end{itemize}
+	A point that is not homotopically regular is called \emph{homotopically critical}.
+	Function values of  homotopically critical points will be called \emph{critical values} and all other values will be called \emph{regular values}.
+	A \emph{critical set} $S$ is a closed and open subset of the subspace of all homotopically critical points with a given function value.
+	It is said to be of \emph{minimum type} if there exists a neighborhood $N$ of the closure $\overline{S}$ of $S$, taken in $M$, such that the function values on $N \setminus S$ strictly exceed the function value on $S$.
+\end{defi}
+
+Note that, in particular, an isolated local minimum constitutes a critical set of minimum type.
+Morse and Tompkins state the following result with slightly different assumptions, as a general Mountain Pass Lemma for critical sets.
+
+% \begin{thm}[{\cite[Corollary 7.1, p.~472]{Morse.1939}}]
+% \label{thm:mountain_pass}
+% 	Let $M$ be a metric space and $F \colon M \to \R$ a function. 
+% 	Assume that $F$ is bounded below, that the sublevel set filtration of $F$ is compact, and let $\H$ be an additive homology theory taking non-zero values on non-empty sets in dimension 0, and such that $\H(F_{\leq \bullet})$ is q-tame, continuous from above and has essential dimension $p_{0} = 1$.
+% 	If $M$ contains two distinct critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.\todo{sort of difficult to parse, assumptions too long.
+maybe only formulate for \v{C}ech homology to get rid of some text?}
+% \end{thm}
+
+\begin{thm}[{\cite[Corollary 7.1, p.~472]{Morse.1939}}]
+\label{thm:mountain_pass}
+	Let $M$ be a metric space and $F \colon M \to \R$ a function. 
+	Assume that $F$ is bounded below, that the sublevel set filtration of $F$ is compact, and that $\CH(F_{\leq \bullet})$ is q-tame with essential dimension $\cp_{0} = 1$, where $\CH$ denotes \v{C}ech homology.
+	If $M$ contains two distinct critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.
+\end{thm}
+
+\begin{rem}
+    We mention that more general homology theories can be considered in this theorem.
+    The precise hypothesis on the homology theory $H$ are that it is additive, taking non-zero values on non-empty sets in dimension $0$, and such that $\H(F_{\leq \bullet})$ is continuous from above.
+\todo{Where is continuous from above introduced?
+Maybe put a reference here.}
+    % Recall that $\H$ is called \emph{additive} if $\H (A \sqcup B) \cong \H(A) \oplus \H(B)$ for all $A$ and $B$.
+\end{rem}
+
+An important case where the hypotheses of \cref{thm:mountain_pass} are satisfied is when $M$ is contractible (which ensures that $\check{p}_0 = 1$ by \cref{lem:essential_cech_dim}), and the sublevel set filtration is $\HLC$ with respect to $\CH$ (which ensures the q-tameness hypothesis by \cref{t:local connectedness implies q-tameness}).
+
+Morse and Tompkins aim to prove that the Douglas functional satisfies the assumptions of the \cref{thm:mountain_pass} (we will elaborate on this at the end of this section and in \cref{subsec:historic_hlc}) and they show \cite[Theorem 6.2]{Morse.1939} that each homotopically critical point of the Douglas functional $A_g$ indeed corresponds to
 %
@@
 %called
-a \emph{minimal surface} -- a surface with vanishing mean curvature -- and use this correspondence to prove the following result, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
+a \emph{minimal surface} -- a surface with vanishing mean curvature -- and use this correspondence to deduce the following result, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
 
-\begin{thm}[{Unstable Minimal Surface Theorem \cite[p.~472]{Morse.1939}}]
-	If the space $\Omega_g$ contains two distinct solutions of Plateau's Problem contained in disjoint critical sets of the functional $A_g$, then it also contains a critical set not of minimum type.
-	%, more precisely, a homotopically critical point of $A_g$ of non-minimum type.
-\end{thm}
-Here, a \emph{critical set} $S$ is a closed and open subspace of the set of all critical points with a given function value.
-It is said to be of \emph{minimum type} if for every neighborhood $N$ of $S$, the function value on the complement $N \setminus S$ exceeds the function value on $S$.
-%it corresponds to a homotopically critical point of $A_g$ of non-minimum type?
-In addition to the general theorem above, Morse and Tompkins also give an explicit example of a curve $g$ satisfying the assumptions, thus proving the existence of an unstable minimal surface in the above sense.
+\begin{cor}[{Unstable Minimal Surface Theorem \cite[Corollary 7.1, p.~472]{Morse.1939}}]
+\label{thm:unstable_minimial_surface}
+	If the space~$\Omega_g$ contains two minimal surfaces contained in distinct critical sets of minimum type of the functional $A_g$, then it also contains an \emph{unstable} minimal surface, i.e., a minimal surface contained in a critical set that is not of minimum type.
+\end{cor}
 
-%sci-hub.se/10.1215/S0012-7094-41-00828-1
-%
-%A point q of M will be termed non-minimizing if in every neighborhood of q there is a point p such thatF(p)<F(q).
-A homotopic critical set which is not a minimizing set contains at least one non-minimizing point of F.
+In \cite[Section 8]{Morse.1939}, Morse and Tompkins provide an example of a curve $g$ for which $\Omega_{g}$ indeed contains two distinct critical sets of minimum type, so that $g$ then also spans an unstable minimal surface.
 
-While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable for its close connection to persistent homology.
+\begin{rem}
+	In their definition of a critical set $S$ of \emph{minimum type} \cite[p.~472]{Morse.1939}, Morse and Tompkins do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
+	However, without this additional assumption, \cref{thm:mountain_pass} does not hold, as the example given by $f \colon [0,1] \to \R$ with $f(0) = f(1) = 0$ and $f(t) = 1$ for $0 < t < 1$ shows:
+	$f$ has the four critical sets $\{0\}$, $\{1\}$, $\{0\} \cup \{1\}$ and $(0,1)$, which all satisfy the minimum type condition if the neighborhood $N$ need not contain their closure, but then there is no critical set that is not of minimum type.
+\end{rem}
 
-\subsection{Morse's local connectivity conditions}
+While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable
+% for its close connection to persistent homology. 
+for its connections to other areas of mathematics.
+As an illustration, we will now sketch a proof of \cref{thm:mountain_pass} using the previously developed machinery, starting with some intermediate results.
 
-Parts of the framework of functional topology that Morse and Tompkins use is developed by Morse in \cite{Morse.1940} in a very general setting.
-In particular, he proves inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
-From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical sets of minimum type.
+\begin{lem}
+\label{lem:endpoint_implies_crit_pt}
+	Let $F \colon M \to \R$ be a function on a metric space with compact sublevel set filtration. 
+	Assume that $\H(F_{\leq \bullet})$ is q-tame and continuous from above and consider $t \in \R$ and its cap numbers $c^{\epsilon}(t)$.
+	If there exists $\epsilon > 0$ such that $c^{\epsilon}(t) > 0$, then $t$ is a critical value.
+\end{lem}
+\begin{proof}
+	Following \cite[Remark II.6.3]{Struwe.1988}, we know that if $t$ is a regular value, there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \to F_{\leq t}$ is a homotopy equivalence for all $s \in [t - \epsilon, t]$.
+\todo{not quite what struwe says, check whether this is actually true}
+	Thus, $\H(F_{\leq \bullet})$ is continuous from below at every regular value.
+	However, we assume $\H(F_{\leq \bullet})$ to be also continuous from above at every value, and in particular at regular values. 
+	Hence, \cref{cor:regular_value_no_endpoint} implies that $\alpha(t) = \omega(t) = 0$ whenever $t$ is regular, which proves the claim.
+\end{proof}
 
-We have seen that these inequalities require q-tameness, so in order to apply them in the minimal surface setting % and deduce their theorem,
-one needs to prove the \mbox{q-tameness} of the sublevel set filtration of the Douglas functional $A_g$.
+%\begin{lem}
+%\label{lem:minimum_type_implies_summand}
+%	Let $F \colon M \to \R$ be a function on a metric space and let $S$ be a critical set with value $t$. 
+%	If $S$ is of minimum type, then it is a topological summand of $F_{\leq t}$ in the sense that $F_{\leq t}$ is homeomorphic to the disjoint union $S \sqcup (F_{\leq t} \setminus S)$.
+%\end{lem}
+%\begin{proof}
+%	By definition, there exists a neighborhood $N$ of $\overline{S}$ in $M$ such that the function values of $F$ on $N \setminus S$ exceed $t$. 
+%	In particular, we have $F_{\leq t} \cap N = S$, showing that $S$ is open in $F_{\leq t}$. 
+%	Because $N$ contains $\overline{S}$, we also obtain $F_{\leq t} \cap \overline{S} = S$, showing that $S$ is closed in $F_{\leq t}$.
+%	This proves the claim.
+%\end{proof}
+
+%In particular, \cref{lem:minimum_type_implies_summand} implies that a critical set of minimum type can only give birth to new features in the persistence diagram and not kill existing ones, provided that the homology theory being used is additive.
+
+\begin{lem}
+\label{lem:minimum_type_implies_some_birth_and_no_death}
+	Let $F \colon M \to \R$ be a function on a metric space with compact sublevel set filtration and let $S$ be a critical set of minimum type with value $t$. 
+	Assume that $\H$ is additive and that $\H(F_{\leq \bullet})$ is q-tame and continuous from above.
+	\begin{enumerate}
+		\item We have $\alpha(t) \geq \dim \H(S)$ for the number of births at $t$.
+		\item If there are not homotopically critical points with value $t$ outside $S$, then we have $\omega(t) = 0$ for the number of deaths at $t$.
+	\end{enumerate}
+\end{lem}
+\begin{proof}
+	We start by showing that $S$ is a topological summand of $F_{\leq t}$ in the sense that $F_{\leq t}$ is homeomorphic to the disjoint union $S \sqcup (F_{\leq t} \setminus S)$.
+	It suffices to show that $S$ is open and closed in $F_{\leq t}$.
+	By definition, there exists a neighborhood $N$ of $\overline{S}$ in $M$ such that the function values of $F$ on $N \setminus S$ exceed $t$. 
+	In particular, we have $F_{\leq t} \cap N = S$, showing that $S$ is open in $F_{\leq t}$. 
+	Because $N$ contains $\overline{S}$, we also obtain $F_{\leq t} \cap \overline{S} = S$, showing that $S$ is closed in $F_{\leq t}$.
+
+	Using additivity of $\H$ and \cref{lem:birth_death_formulas}, we now obtain
+	\begin{align*}
+		\alpha(t) &= \dim \coker \big( \colim_{s < t} \H(F_{\leq s}) \to \lim_{u > t} \H(F_{\leq u}) \big) \\
+			      &= \dim \coker \big( \colim_{s < t} \H(F_{\leq s}) \to \H(F_{\leq t}) \big) \\
+			      &= \dim \coker \big( \colim_{s < t} \H(F_{\leq s}) \to \H(F_{\leq t} \setminus S) \oplus \H(S) \big) \\
+			      &\geq \dim \H(S),
+	\end{align*}
+	where we have used the assumption that $\H(F_{\leq \bullet})$ is continuous from above for the second equality and the fact that $F_{\leq s} \subseteq (F_{\leq t} \setminus S)$ for all $s < t$ for the final inequality.
+
+	Now, assuming that $S$ is the set of all homotopically critical points with value $t$ implies that the inclusion $F_{\leq s} \to (F_{\leq t} \setminus S)$ is in fact a homotopy equivalence for $s < t$, again following \cite[Remark II.6.3]{Struwe.1988}.\todo{again, needs to be reviewed whether this actually follows from what struwe says}
+	Hence, again using additivity of $\H$, continuity from above, and \cref{lem:birth_death_formulas}, we obtain that 
+	\begin{align*}
+		\omega(t) &= \dim \ker \big( \colim_{s < t} \H(F_{\leq s}) \to \lim_{u > t} \H(F_{\leq u}) \big) \\
+				&= \dim \ker \big( \colim_{s < t} \H(F_{\leq s}) \to \H(F_{\leq t}) \big) \\
+				&= \dim \ker \big( \colim_{s < t} \H(F_{\leq s}) \to \colim_{s < t} H(F_{\leq s}) \oplus \H(S) \big) \\
+				&= 0
+	\end{align*}
+	as claimed.
+\end{proof}
+
+We are now ready to give a proof of the Mountain Pass Lemma.
+\begin{proof}[Proof of \cref{thm:mountain_pass}]
+    We write $\cc_d$, $\calpha_d$, $\comega_d$, and $\cp_d$ for the cap numbers, births, deaths, and essential dimensions of $\CH_d(F_{\leq \bullet})$, respectively. 
+	Assume that $F$ has two distinct critical sets $S_{1}$ and $S_{2}$ of minimum type with values $t_{1}$ and $t_{2}$, respectively.
+	Since both critical sets are non-empty, we have $\CH_{0}(S_{i}) \neq 0$, and thus the first assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death} implies $\calpha_{0}(t_{i}) \geq \dim \CH_0(S_{i}) \geq 1$ for $i = 1,2$.
+	This implies that there exists $\epsilon > 0$ with $\cc_{0}^{\epsilon} \geq \calpha_{0}(t_{1}) + \calpha_{0}(t_{2}) \geq 1 + 1 = 2$.
+	However, we assume $\cp_{0} = 1$, so with notation as in the proof of \cref{t:inequalities}, we obtain $\comega_{0}^{\epsilon} = \cc_{0}^{\epsilon} - \cp_{0} \geq 2 - 1 = 1$.
+	Thus, there must be some $t \in \R$ with $\comega_{0}(t) > 0$, so that in particular $\cc_{0}^{\epsilon}(t) > 0$.
+	Next, we apply \cref{lem:endpoint_implies_crit_pt} and obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
+	If $S$ were of minimum type, then we would have $\comega_{0}(t) = 0$ by the second assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death}, contradicting the choice of $t$.
+	Hence, $S$ cannot be of minimum type, which finishes the proof.
+\end{proof}
+
+\todo{should we remark on the fact that the morse inequalities only yield $c_{1}^{\epsilon} \geq 1$, but that this is not enough to conclude existence of something that is not of minimum type?
+$\omega(t) \geq 1$ is needed}
+
+What remains to be discussed in order to obtain the Unstable Minimal Surface Theorem of Morse and Tompkins (\cref{thm:unstable_minimial_surface}) as a consequence of their Mountain Pass Lemma, is why the Douglas functional $A_{g}$ satisfies the hypothesis of \cref{thm:mountain_pass}.
+We have already mentioned that $A_{g} \colon \Omega_{g} \to \R$ is bounded below and has compact sublevel sets.
+% One can use \v{C}ech homology
+% , which satisfies the assumptions on the homology theory in \cref{thm:mountain_pass} (see \cite{Milnor.1962} for additivity),
+% to obtain a sublevel set persistence module that is continuous from above.
+We can also check that the essential dimension $\check{p}_{0}$ is $1$ using the following lemma, because $\Omega_{g}$ is contractible by \cite[Theorem 4.3]{Morse.1939}.
+
+\begin{lem}
+\label{lem:essential_cech_dim}
+	Let $F \colon M \to \R$ be a function on a non-empty metric space with compact sublevel set filtration and let $\cp_{d}$ be the essential dimensions of its q-tame persistent \v{C}ech homology. 
+	If $M$ is contractible, then $\cp_{0} = 1$.
+\end{lem}
+\begin{proof}
+	Let $\H$ denote singular homology, let $p_{d}$ denote the essential dimensions of the persistent singular homology of $F_{\leq \bullet}$, and let $\CH$ denote \v{C}ech homology. 
+	Since $M$ is contractible, we have $\dim H_{0}(M) = 1$.
+	We also have $p_{d} = \dim \colim_{t \to \infty} H_{d}(F_{\leq t}) = \dim H_{d}(M)$, where the second equality holds because all the sublevel sets of $F$ are compact \cite[Proposition 3.33]{Hatcher.2002}.
+	Now, the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so $\cp_{0} \leq p_{0}$.
+	Moreover, we clearly have $\cp_{0} \geq 1$ because $M$ is non-empty.
+%Map from some non-empty sublevel set to $M$ has to have at least rank 1 and has ti factor through colimit, so $\cp_{0} = \dim \colim \geq 1$.
+	In total, we obtain $1 \leq \cp_{0} \leq p_{0} = \dim H_{0}(M) = 1$, which proves the claim.
+\end{proof}
+
+The only assumption left to verify is q-tameness.
+
+\subsection{Morse's local connectivity conditions}\label{subsec:historic_hlc}
+%Parts of the framework of functional topology that Morse and Tompkins use is developed by Morse in \cite{Morse.1940} in a very general setting.
+%In particular, he proves inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
+%From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical sets of minimum type.
+
+%We have seen that these inequalities require q-tameness, so in order to apply them in the minimal surface setting % and deduce their theorem,
+%one needs to prove the \mbox{q-tameness} of the sublevel set filtration of the Douglas functional $A_g$.
+
+% What remains to be discussed is why the Douglas functional $A_{g} \colon \Omega_{g} \to \R$ satisfies the assumptions of \cref{thm:mountain_pass} so that the Unstable Minimal Surface Theorem follows as a corollary.
+
 Throughout his work on functional topology, in order to obtain \mbox{q-tameness}, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins used the following condition in their applications to minimal surface theory (see also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain typographical errors):
+In particular, Morse and Tompkins used the following condition in their applications to minimal surface theory:
 \begin{displaycquote}[p.~431]{Morse.1940}
@@
 \end{displaycquote}
+See also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain typographical errors.
 Using similar language to the one used in \cref{s:connectivity}, the property of local $F$-connectedness of all orders is equivalent to the following notion applicable to general topological spaces.
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly homotopically locally connected}, or \emph{weakly $\piLC$}, if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected of all orders}, or \emph{weakly $\piLC$}\todo{check whether $\piLC$ is still appropriate}, if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
 \end{defi}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or \emph{weakly $\LC$} if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally contractible}, or \emph{weakly $\LC$}\todo{check whether $\LC$ is still appropriate}, if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 
-Specifically, using the the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
+Specifically, using the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
 %To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally connected} $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally contractible} or \emph{$\LC$} if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 Therefore, from \cref{t:local connectedness implies q-tameness} we can conclude that the sublevel set filtration of $A_g$ is indeed \mbox{q-tame} as needed.
-This implies that the generalized Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem.
+This implies that \cref{thm:mountain_pass} indeed applies to the Douglas functional, and hence the Unstable Minimal Surface Theorem holds.
 

### 2022-04-25 sec/introduction.tex
Update Mountain Pass Lemma terminology

@@
 He called the theory set forth in this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939} used these techniques to prove a general form of \emph{Mountain Pass Theorem} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous.
-From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima.
+In particular, Morse and Tompkins \cite{Morse.1939} used these techniques to prove a general \emph{Mountain Pass Lemma} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous (\cref{thm:mountain_pass}).
+From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima (\cref{thm:unstable_minimial_surface}).
 In the intervening years, this result has been reproven and generalized in several directions using various techniques, and the problem class is still an active area of research \cite{Struwe.1984,Jost.1990,Jost.1991,Montezuma.2020,Marques.2021}.

### 2022-07-13 referee_reply.tex
after second ref

@@
 	\section{First point.} We have added a complete and self-contained formulation of our main result (Theorem 4.7 in the reviewers copy) to the introduction.
-
-	A: What should we do about THM 5.1?
+    We have also introduced in section 5 the necessary definitions in order to state the Unstable Minimal Surface Theorem (5.1 in the reviewer's copy), now referenced in the introduction.
+    (Please see point 3 below.)
 
@@
 	The proof is broken down into some intermediate lemmas and cites Morse--Tompkins and Struwe as necessary.
-	We have also added the notions of \emph{number of births} and \emph{number of deaths} in the section on persistence and gave some basic formulas to compute them, which was necessary to make the later proofs work.
+	We have also added the notions of \emph{number of births} and \emph{number of deaths} and gave some basic formulas to compute them, which was necessary to make the later proofs work.
+	Notably, another slight correction to a definition used by Morse--Tompkins was necessary: the notion of a \emph{critical set of minimum type} is not accurately captured by the original definition, as discussed in Remark 5.3.
 
@@
 		\item RAS.
-		\item We did mean ``functional analysis''. Thank you for the question.
+		\item We did mean ``functional analysis''. To make clearer what exactly we were referring to, we changed the wording to ``calculus of variations". Thank you for the question.
 		\item RAS.
@@
 		\item RAS.
-		\item RAS. (@Uli, please check this change.)
+		\item RAS.
 		\item RAS.
@@
 	The notion that was formerly called 'homotopically locally connected' is now simply called 'locally connected of all orders' and the notion that was formerly called 'locally connected' is now called 'locally contractible', which seems to be more in line with the existing literature.
+
+	We have also added a reference to a paper by Cagliari and Landi where a multiparameter version of Corollary 4.12 in the current version has been established for slightly stronger assumptions on the domain of the function.
+
+	Considering the changes suggested by the reviewer and feedback gathered from other mathematicians while presenting this work, we have settled on a new title: ``Persistent homology for functionals.''
+
+	We have also made several small changes to the expository parts of the paper, expanded the discussion on the historical assumptions for the Mountain Pass Theorem by Morse and Tompkins, and fixed typos throughout.
 \end{document}

### 2022-07-13 ref_reply2.tex
after second ref

\documentclass{article}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\title{Author's second reply to the referee report of \\ \textsc{
    ``PERSISTENCE IN FUNCTIONAL TOPOLOGY: EXISTENCE OF PERSISTENCE DIAGRAMS AND MORSE INEQUALITIES''
    }
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for his careful reading of our revised article, again providing very helpful commentary and uncovering many of our inaccuracies.

	\section{First point.}
	After revisiting Struwe's argument for the homotopy equivalence of the sublevel sets more carefully, we were also unable to determine why Struwe supposes the level set to be compact, and we could also not establish a different argument for the necessary homotopy equivalence without returning to Morse's concept of weak upper-reducibility (WUR). 
	Hence, we have added this assumption to the Mountain Pass Theorem and we have added a lemma stating that the needed homotopy equivalence holds given that the function is WUR.
	This lemma can be proven by a very similar argument to the (imprecise) one by Struwe, and very similar arguments also appear in Morse's monograph on functional topology, where he, however, uses a slightly stronger version of upper-reducibility, making these results not directly citable for us.
	As a compromise between readability and precision, we have decided to just state the lemma at first without proof and with references to these similar arguments, and then to sketch a proof in a new section in the appendix.
	There, we now also comment on the differences between Morse's notion of cap numbers and our corresponding notion.
	The preparatory lemmas now also include the WUR assumption where necessary.

	\section{Second point.}
	The referee is correct in that the proposition cited from Hatcher does not actually apply in the setting as stated; in fact our lemma is not true as it was stated.
	We have consequently added the assumption that $\colim \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
	We also include an example in a remark after the Mountain Pass Theorem showing that if this assumption is removed it may happen that $\check{p}_0 > 1$.
	Moreover, we added a reference in the proof of the Unstable Minimal Surface Theorem for the fact that this new assumption is satisfied for the Douglas functional, which is due to Morse's "regularity at infinity" condition.

	\section{List of typos, minor remarks and suggestions.}
	\begin{enumerate}
		\item Removed as suggested (A.S.).
		\item Changed A.S.
		\item Removed A.S.
		\item Changed A.S.
		\item We have added a reference to the original paper by Douglas, where it is explained that his functional takes finite values for rectifiable curves, and we have added a very brief explanation why this applies in our setting.
		\item Changed A.S.
		\item Changed A.S.
		\item We now address this point in a remark after the Mountain Pass Theorem.
		\item We have replaced ``the following result [...] can be deduced from the Mountain Pass Theorem'' right above the Unstable Minimal Surface Theorem with ``the following result [...] can be deduced from the Mountain Pass Theorem as further explained in \S 5.2.''
		\item We have included a reference for the fact that $M$ may be replaced by its radical and have added the explicit calculations showing that the lemma holds for the radical.
		\item Removed A.S.
		\item Changed A.S.
		\item Replaced A.S.
	\end{enumerate}

	\section{Other changes}
	We fixed a typo in the proof of the Mountain Pass Theorem: It needs to be "... , so that in particular $\cc_{1}^{\epsilon}(t) > 0$" instead of "... , so that in particular $\cc_{0}^{\epsilon}(t) > 0$".

	We also slightly streamlined the proof of Lemma 4.9: The third requirement on $\Sigma_{s,t}$ was unnecessary and has been removed.

	We also fixed a typo in the definition of the Vietoris complex in the appendix: It should say "$\sigma \subseteq U$" instead of "$\sigma \in U$".
\end{document}

### 2022-07-13 sec/abstract.tex
after second ref

@@
 
+% \begin{abstract}
+% We introduce topological conditions on a broad class of filtered spaces ensuring that their associated persistent homology modules admit persistence diagrams, which, in particular, implies that they satisfy generalized Morse inequalities.
+% We illustrate the applicability of these results by recasting the original proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins in a modern and rigorous framework.
+% \end{abstract}
+
+%% If title is "PH for functionals", I would suggest a rewrite of the abstract above along the following lines:
+
 \begin{abstract}
-We introduce topological conditions on a broad class of filtered spaces ensuring that their associated persistent homology modules admit persistence diagrams, which, in particular, implies that they satisfy generalized Morse inequalities.
+    We introduce topological conditions on a broad class of functionals that ensure that the persistent homology modules of their associated sublevel set filtration admit persistence diagrams, which, in particular, implies that they satisfy generalized Morse inequalities.
     We illustrate the applicability of these results by recasting the original proof of the Unstable Minimal Surface Theorem given by Morse and Tompkins in a modern and rigorous framework.

### 2022-07-13 sec/caps.tex
after second ref

%!TEX root = ../func_top.tex

\section{Regular values and cap numbers} \label{s:caps}
We will now discuss the equivalence of our definition of cap numbers and the one used by Morse.
Futhermore, we provide a proof of \cref{lem:sublevel_set_homotopy} establishing a homotopy equivalence of sublevel sets at a regular value.
As a starting point, we observe that the basic use of \cref{lem:sublevel_set_homotopy} is to show that if $t$ is an endpoint of a feature in the persistence diagram associated to our function $F$, i.e., if $c(t) > 0$, then there must be a homotopically critical point with value $t$.
To achieve this, we assume that $F$ is weakly upper-reducible and its sublevel set filtration is compact.
A very similar statement appears in \cite[Theorem 8.1]{Morse.1938}, which says that if $t$ is a \emph{cap limit}, then there must be a homotopically critical point with value $t$.
There are two slight differences to our approach: 
First, in \cite[Theorem 8.1]{Morse.1938} it is assumed that $F$ is not only weakly upper-reducible but upper-reducible.
Second, $t$ is not required to satisfy $c(t) > 0$, but required to be a \emph{cap limit}, meaning that $\colim_{s: s < t} \CH_*(F_{\leq t}, F_{\leq s}) \neq 0$ \cite[p.~12]{Morse.1938}.
Regarding the second point, it turns out that the two requirements are equivalent.

\begin{prop}\label{prop:cap_limits}
	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration.
	Assume that $\H$ has long exact sequences for pairs of compact spaces, and that $\H_*(F_{\leq \bullet})$ is q-tame and continuous from above.
	Then $\dim \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) = c_d(t)$ or both quantities are infinite.
\end{prop}
\begin{proof}
	First, note that we have a splitting 
	\begin{align*}
	\colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) 
	&\cong \im \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_*(F_{\leq t}, F_{\leq s}) \right) \\
	&\oplus \coker \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right).
	\end{align*}
    Computing with the long exact sequences of pairs in homology, we have
    \begin{align*}
        \alpha_d(t)
        &= \dim \coker \left( \colim_{s: s < t} \H_d(F_{\leq s} \hookrightarrow F_{\leq t}) \right) \\
        &= \dim \colim_{s: s < t} \coker \left( \H_d(F_{\leq s} \hookrightarrow F_{\leq t}) \right) \\
        &= \dim \colim_{s: s < t} \im \left( \H_d(F_{\leq t}) \to \H_d(F_{\leq t}, F_{\leq s}) \right) \\
        &= \dim \im \left( \H_*(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right), \\
    \end{align*}
    and
    \begin{align*}
    	\omega_{d-1}(t)
        &= \dim \ker \left( \colim_{s: s < t} \H_{d-1}(F_{\leq s} \hookrightarrow F_{\leq t}) \right) \\
        &= \dim \colim_{s: s < t} \ker \left( \H_{d-1}(F_{\leq s} \hookrightarrow F_{\leq t}) \right) \\
        &= \dim \colim_{s: s < t} \coker \left( \H_d(F_{\leq t}) \to \H_d(F_{\leq t}, F_{\leq s}) \right) \\
        &= \dim \coker \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right), \\
    \end{align*}
    where we have in both cases used the fact that taking filtered colimits of vector spaces is exact, and where the first equalities hold in case both sides of the equation are finite because of \cref{lem:birth_death_formulas} and the fact that $\H_*(F_{\leq \bullet})$ is continuous from above.
	Since $c_d(t) = \alpha_d(t) + \omega_{d-1}(t)$, this finishes the proof.
\end{proof}

\begin{rem}
	\cref{prop:cap_limits} only references cap limits, i.e., levels $t$ for which the \emph{cap space} $\colim_{s: s < t} \H_*(F_{\leq t}, F_{\leq s})$ is non-zero.
	However, Morse not only considers these cap spaces on their own, but he also defines the \emph{span} of a cap, and considers the space of caps with span greater than some $\epsilon > 0$, see for example \cite[Section 11]{Morse.1940}. 
	Using slight generalizations of the arguments proving \cref{prop:cap_limits,lem:birth_death_formulas}, one can show that the dimensions of these spaces agree with $c^{\epsilon}(t)$.
	We already mentioned this when talking about Morse inequalities, which Morse originally formulated for dimensions of such cap spaces.	
\end{rem}

Note that the assumptions of \cref{prop:cap_limits} are in particular satisfied for \v{C}ech homology with field coefficients and a function $F$ whose sublevel set filtration is $\HLC$ with respect to this homology theory.
Regarding the first difference we mentioned between our approach and the one from \cite[Theorem 8.1]{Morse.1938} with respect to upper-reducibility, we will now sketch that this is not an issue.
That is, we will give an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988}.
\begin{proof}[Proof of \cref{lem:sublevel_set_homotopy}]
	Let $t \in \R$ be a regular value of $F$.
	For each $p \in F_{\leq t}$ we can find a number $\delta_{p} > 0$ and a continuous map $\varphi_{p} \colon B_{\delta_{p}}(p) \times [0,1] \to M$, where $B_{\delta_{p}}(p)$ is the open metric ball around $p$ in $F_{\leq t}$ with radius $\delta_{p}$, such that 
	\begin{enumerate}
		\item $\varphi_{p}(\cdot,0) = \operatorname{id}$,
		\item for all $V \subseteq B_{\delta_{p}}(p)$ compact there exists $\epsilon(p,V) > 0$ with 
		\begin{enumerate}
			%\item $F(\varphi_{p}(x,r))$ is non-increasing in $r$ for all $x \in B_{\delta_{p}}(p)$, and
			\item $\varphi_{p}(V \cap F_{\leq s}\times [0,1]) \subseteq F_{\leq s}$ for all $s \in (t - \epsilon(p,V), t]$, and
			\item $\varphi(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$.
		\end{enumerate}
	\end{enumerate}
	For $p$ with $F(p) = t$ the existence of such $\delta_{p}$ and $\varphi_{p}$ is guaranteed by the assumption that $t$ is a regular value and hence $p$ is homotopically regular,
	and for $p$ with $F(p) < t$ it is guaranteed by the assumption that $F$ is weakly upper-reducible.
	Because $F_{\leq t}$ is compact, we can now choose finitely many points $p_{1}, \dots, p_{n}$ such that $F_{\leq t}$ is covered by $( B_{\frac{\delta_{p_{i}}}{3}}(p_{i}))_{i}$, and we set 
	\[
		\epsilon \defeq \max_{i = 1,\dots,n} \epsilon \left( p_{i}, \overline{B}_{\frac{\delta_{p_{i}}}{3}}(p_{i}) \right).
	\]
	We extend the corresponding homotopies $\varphi_{p_{i}}$ from $B_{\delta_{p_{i}}}(p_{i})$ to all of $F_{\leq t}$, not changing them on $B_{\frac{\delta_{p_{i}}}{3}}(p_{i})$, and being the identity on $F_{\leq t} \setminus B_{\delta_{p_{i}}}(p_{i})$:
	Let $\psi \colon [0,1] \to [0,1]$ be the continous map given by 
	\[
		\psi(x) = 
		\begin{cases}
			1  & \text{if } x \in [0,\frac{1}{3}), \\
			-3x + 2 & \text{if } x \in [\frac{1}{3}, \frac{2}{3}), \\
			0 & \text{if } x \in [\frac{2}{3},1].
		\end{cases}
	\]
	We define $\tilde{\varphi}_{i} \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ by 
	\[
		\tilde{\varphi}_{i}(x,r) = 
		\begin{cases}
			\varphi_{p_{i}} \left( x, \psi \left( \frac{d(x,p_{i})}{\delta_{p_{i}}} \right) \cdot r \right)  & \text{if } x \in B_{\delta_{p_{i}}}(p_{i}), \\
			x & \text{otherwise}.
		\end{cases}
	\]
	Finally, we define $\varphi \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ as the concatenation of the maps $\tilde{\varphi}_{i}$, i.e., $\varphi(x,0) = x$ and $\varphi(x,r) = \varphi_{i} \left( x, n \cdot r - i \right)$ for $r \in \left( \frac{i}{n}, \frac{i+1}{n} \right]$.
	From the properties of the maps $\varphi_{p_{i}}$ chosen in the beginning and the construction of the maps $\tilde{\varphi}_{i}$, we obtain that 
	\begin{enumerate}
		\item $\varphi(\cdot, 0) = \operatorname{id}$, 
		\item $\varphi(F_{\leq s} \times [0,1]) \subseteq F_{\leq s}$ for all $s \in (t - \epsilon, t]$, and 
		\item $\varphi(F_{\leq t}, 1) \subseteq F_{\leq t - \epsilon}$.
	\end{enumerate}
	This shows that, indeed, the inclusions $F_{\leq s} \hookrightarrow F_{\leq t}$ are homotopy equivalences for $s \in (t - \epsilon, t]$, with homotopy inverses given by $\varphi$.
\end{proof}

### 2022-07-13 sec/connectivity.tex
Add proof of UMST
after second ref

@@
 We have seen that q-tame functions admit persistence diagrams, which can be used to formulate Morse inequalities.
-With q-tameness being a rather abstract condition, we now establish concrete topological requirements that ensure the q-tameness of a function.
-Our definitions are motivated by similar conditions that Morse considered in his work on functional topology.
+With q-tameness being a rather abstract algebraic property, we now establish concrete topological conditions that ensure the q-tameness of a function.
+Our definitions are motivated by similar conditions considered by Morse in his work on functional topology.
 We will present a historical account in \cref{s:surfaces}.
@@
 Whether a function is q-tame or not depends on the functor that is used to pass from the sublevel set filtration of the function to a persistence module.
-The general idea that we want to employ is to deduce global finiteness properties like q-tameness from local ones.
+The general strategy is to deduce global finiteness properties like q-tameness from local ones.
 Thus, the functors we consider should have a certain property allowing us to do so.
 
-Concretely, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
+Specifically, let $\H = (\H_d)_{d \in \Z} \colon \Top \to \Vect$ be a fixed graded homotopy invariant functor, which we call a \emph{homology theory}.
 A triple of spaces $X_{1}, X_{2} \subseteq X$ is said to have a \emph{Mayer--Vietoris sequence} for $\H$ if the inclusion-induced maps can be completed to a long exact sequence
@@
 
-For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer--Vietoris property and for which there is $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+For the rest of this section, we will assume that $\H$ is a homology theory that has either the open or the compact Mayer--Vietoris property and for which there is $n_0$ such that $\H_{n}$ is zero for all $n \leq n_0$.
 We will also assume that $\H_{n}$ takes finite dimensional values on one-point spaces.
-Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Section I]{Eilenberg.1952}), and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property.
+Note that this includes singular homology with field coefficients, which has the open Mayer--Vietoris property (like any homology theory in the sense of the Eilenberg--Steenrod axioms \cite[Chapter I]{Eilenberg.1952}), and it also includes \v{C}ech homology with field coefficients, which has the compact Mayer--Vietoris property by \cite[Theorem 10.7.2]{tomDieck.2008} as a consequence of the strong excision property of \v{C}ech homology \cite[Theorem X.5.4]{Eilenberg.1952}.
 
@@
 \begin{defi}
-	For $n \in \Z$ a continuous map is said to be \emph{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
+	For $n \in \Z$, a continuous map is said to be \emph{$n$-homologically small} or $\HS_n$ if the image of the map induced by $\H_{n}$ is finite dimensional.
 	We omit references to $n$ if the condition holds for all integers.
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 
-If $f_{\leq t}$ is compact then the function $f$ is necessarily lower-semicontinuous and bounded from below, see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}.
+If $f_{\leq t}$ is compact for all $t$, then the function $f$ is necessarily lower-semicontinuous and bounded from below (see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}).
 
-Our main result, proven in the remainder of this subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
+Our main result, proven in the remainder of this subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness}, and consequently also the existence of a persistence diagram:
 
 \begin{thm} \label{t:local connectedness implies q-tameness}
-	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then its persistent homology is also q-tame.
 	In particular, $f$ has a persistence diagram.
@@
 
-The general proof strategy is inspired by the proof of a result by Wilder \cite[p.~325]{Wilder.1949}, as presented by Bredon \cite[Section II.17]{Bredon.1997}.
+The general proof strategy is inspired by the proof of Wilder's Finiteness Theorem \cite[p.~325]{Wilder.1949} as presented by Bredon \cite[Section II.17]{Bredon.1997}.
 We collect the main ideas in several lemmas.
@@
 	Let $X$ be a locally compact Hausdorff space.
-	For any compact subset $K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
+	For any compact subset~$K$ and open set $U$ with $K \subseteq U$ there exists a compact set $K^\prime$ such that
 	\begin{equation*}
@@
 	\begin{equation*}
-	K \subseteq \bigcup_{x \in K} \interior(C(x)) \subseteq \interior\left(\bigcup_{x \in K} C(x)\right) \subseteq \bigcup_{x \in K} C(x) \subseteq U
+	K \subseteq \bigcup_{x \in K} \interior(C(x)).
 	\end{equation*}
-	Since $K$ is compact, the first inclusion above is achieved over a finite subset $\{x_1, \dots, x_m\}$ of elements in $K$.
+	Since $K$ is compact, there is a finite subset $\{x_1, \dots, x_m\}$ of elements in $K$ so that
+	\begin{equation*}
+	K \subseteq \bigcup_{i=1}^m \interior(C(x_i)) \subseteq \interior\left(\bigcup_{i=1}^m C(x_i)\right) \subseteq \bigcup_{i=1}^m C(x_i) \subseteq U
+	\end{equation*}
 	Defining $K^\prime = \bigcup_{i=1}^m C(x_i)$ finishes the proof.
@@
 \begin{defi}
-	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{$\HLC$ below $u$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	For $u \in \R$, the sublevel set filtration of a function $f \colon X \to \R$ is called \emph{$\HLC$ below $u$} if, for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t < u$, there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 \begin{proof}
-	Let $x \in Y$, $V$ a neighborhood of $x$ in $Y$ and consider indices $s,t$ with $g(x) < s < t < u$.
-	We need to find a neighborhood $U \subseteq V$ of $x$ such that the inclusion $g_{\leq s} \cap U \to g_{\leq t} \cap V$ is $\HS$.
+	Let $x \in Y$, let $V$ be a neighborhood of $x$ in $Y$, and consider indices $s,t$ with $g(x) < s < t < u$.
+	We need to find a neighborhood $U \subseteq V$ of $x$ such that the inclusion $g_{\leq s} \cap U \hookrightarrow g_{\leq t} \cap V$ is $\HS$.
 
 	Since $Y \subseteq X$ carries the subspace topology, we may choose a neighborhood $V'$ of $x$ in $X$ such that $V = V' \cap Y$.
-	The sublevel set filtration of $f$ is assumed to be $\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$ is $\HS$.
+	The sublevel set filtration of $f$ is assumed to be $\HLC$, so there is a neighborhood $U' \subseteq V'$ of $x$ in $X$ such that the inclusion $f_{\leq s} \cap U' \hookrightarrow f_{\leq t} \cap V'$ is $\HS$.
 	We set $U = U' \cap Y$, which defines a neighborhood of $x$ in $Y$.
 
-	Now, $s < t < u$ implies that we have $g_{\leq s} = f_{\leq s}$ and $g_{\leq t} = f_{\leq t}$.
+	Now $s < t < u$ implies that $g_{\leq s} = f_{\leq s}$ and $g_{\leq t} = f_{\leq t}$.
 	Moreover, we have $f_{\leq s} \cap Y = f_{\leq s} \cap f_{\leq u} = f_{\leq s}$ and $f_{\leq t} \cap Y = f_{\leq t} \cap f_{\leq u} = f_{\leq t}$.
 	Thus, we obtain $g_{\leq s} \cap U = f_{\leq s} \cap Y \cap U' = f_{\leq s} \cap U'$ and $g_{\leq t} \cap V = f_{\leq t} \cap Y \cap V' = f_{\leq t} \cap V'$.
-	This implies that the inclusion $g_{\leq s} \cap U \to g_{\leq t} \cap V$ is $\HS$ because it agrees with the inclusion $f_{\leq s} \cap U' \to f_{\leq t} \cap V'$, which is $\HS$ by construction.
+	This implies that the inclusion $g_{\leq s} \cap U \hookrightarrow g_{\leq t} \cap V$ is $\HS$ because it agrees with the inclusion $f_{\leq s} \cap U' \hookrightarrow f_{\leq t} \cap V'$, which is $\HS$ by assumption.
 	This finishes the proof.
@@
 \begin{lem} \label{l:key lemma for q-tameness}
-	Let $f \colon Y \to \R$ be a function on a locally compact Hausdorff space $Y$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq Y$ with $C$ compact and $L$ open.
-	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS$.
+	Let $f \colon Y \to \R$ be a function on a locally compact Hausdorff space~$Y$ whose sublevel set filtration is compact and $\HLC$ below $u \in \R$, and consider subsets $C \subseteq L \subseteq Y$ with $C$ compact and $L$ open.
+	For any $s < t < u$ the inclusion $C \cap f_{\leq s} \hookrightarrow L \cap f_{\leq t}$ is $\HS$.
 \end{lem}
@@
 \begin{proof}
-	Recall that we are assuming that the underlying homology theory $\H$ has either the open or the compact Mayer--Vietoris property and that there is some $n_0$ such that $\H_{n}$ is 0 for all $n \leq n_0$.
+	Recall our assumption that the underlying homology theory $\H$ has either the open or the compact Mayer--Vietoris property and that there is some $n_0$ such that $\H_{n}$ is zero for all $n \leq n_0$.
 	The statement of the lemma holds for $\HS_{n}$ in place of $\HS$ for any $n \leq n_0$ since $\H_{n}$ induces the zero map.
@@
 
-	We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq Y$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$	for which there exists $s' \in (s,\, t)$ such that the inclusion $U \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$.
-	We will show that $\Sigma_{s, t}$ has the following three properties:
+	We define $\Sigma_{s, t}$ to be the collection of all open subsets $V \subseteq Y$ whose closure $\overline{V}$ is compact, contained in $L$, and has an open neighborhood $U$ with $\overline{V} \subseteq U \subseteq L$	for which there exists $s' \in (s,\, t)$ such that the inclusion $U \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$ is $\HS_n$.
+	We will show that $\Sigma_{s, t}$ has the following two properties:
 	\begin{enumerate}
@@
 		\item If $V_1,\, V_2 \in \Sigma_{s,t}$ then $V_1 \cup V_2 \in \Sigma_{s,t}$.
-		\item For each $V \in \Sigma_{s,t}$ the inclusion
-		$V \cap f_{\leq s} \to L \cap f_{\leq t}$ is $\HS_n$.
+%		\item For each $V \in \Sigma_{s,t}$ the inclusion
+%		$V \cap f_{\leq s} \hookrightarrow L \cap f_{\leq t}$ is $\HS_n$.
 	\end{enumerate}
@@
 	\[V \defeq \bigcup_{i = 1}^m V_{x_i} \in \Sigma_{s,t}.\]
-	Using the third property, the inclusion
-	$V \cap f_{\leq s} \to L \cap f_{\leq t}$
-	is $\HS_n$, so the inclusion
-	$C \cap f_{\leq s} \to L \cap f_{\leq t}$
-	is also $\HS_n$ because this map factors through the aforementioned one.
-	What is left to do is to show that $\Sigma_{s,t}$ has the properties we want.
-
-	For the third property, let $V \in \Sigma_{s,t}$ with $U$ an open neighborhood of $\overline{V}$ in $L$ and $s' \in (s,\, t)$ such that
-	$U \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	Thus, there exists an open neighborhood $U$ of $\overline{V}$ in $L$ and $s' \in (s,\, t)$ such that the inclusion
+	$U \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
 	is $\HS_n$.
 	The inclusion
-	$V \cap f_{\leq s} \to L \cap f_{\leq t}$
-	factors through the previous one so it is $\HS_n$ as well.
-	Thus, $\Sigma_{s, t}$ has the third property we want.
+	$C \cap f_{\leq s} \hookrightarrow L \cap f_{\leq t}$
+	factors through the previous one, so it is $\HS_n$ as well.
+	What is left to do is to show that $\Sigma_{s,t}$ has the two claimed properties.
 
@@
 	Choose an arbitrary $s' \in (s,\, t)$.
-	Since the sublevel set filtration of $f$ is $\HLC$ below $u$ and we have $s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
-	$U_x \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	Since the sublevel set filtration of $f$ is $\HLC$ below $u$ and we have $f(x) \leq s < s' < t < u$, there is an open neighborhood $U_x \subseteq L$ such that the inclusion
+	$U_x \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
 	is $\HS$, so in particular $\HS_n$.
@@
 	and
-	$U_{i} \cap f_{\leq s'_i} \to L \cap f_{\leq t}$
+	$U_{i} \cap f_{\leq s'_i} \hookrightarrow L \cap f_{\leq t}$
 	is $\HS_n$.
@@
 	where $V'_i = \interior(K'_i)$.
-	We have that the union $V_1 \cup V_2 \subseteq L$ is open, its closure $\overline{V_1 \cup V_2}$ is compact, and we have $\overline{V_1 \cup V_2} \subseteq V'_1 \cup V'_2 \subseteq L$.
+	The union $V_1 \cup V_2 \subseteq L$ is open, its closure $\overline{V_1 \cup V_2}$ is compact, and $\overline{V_1 \cup V_2} \subseteq V'_1 \cup V'_2 \subseteq L$.
 	Thus, we obtain $V_1 \cup V_2 \in \Sigma_{s,t}$ if we can show that there is an $s' \in (s,\, t)$ such that the inclusion
-	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
 	is $\HS_n$.
 	To do so, we set $s'' = \min_i s'_i$ and choose $s' \in (s,\, s'')$.
-	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer--Vietoris property.
+	For proving that $\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$ is $\HS_n$ we now distinguish the two cases where $\H$ has either the open or the compact Mayer--Vietoris property.
 
-	In the open case, notice that for both choices of $i$ the inclusions
-	$U_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
+	For the open Mayer--Vietoris property, note that for both $i \in \{1, 2\}$ the inclusions
+	$U_i \cap f_{\leq s''} \hookrightarrow L \cap f_{\leq t}$
 	are $\HS_n$.
-	Additionally, the inclusion
-	$V'_1 \cap V'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$
+	Moreover, the inclusion
+	$V'_1 \cap V'_2 \cap f_{\leq s'} \hookrightarrow U_1 \cap U_2 \cap f_{\leq s''}$
 	is $\HS_{n-1}$ because it factors through the inclusion
-	$K'_1 \cap K'_2 \cap f_{\leq s'} \to U_1 \cap U_2 \cap f_{\leq s''}$,
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \hookrightarrow U_1 \cap U_2 \cap f_{\leq s''}$,
 	which is $\HS_{n-1}$ by the induction hypothesis.
@@
 	We conclude that the inclusion
-	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
 	is $\HS_n$, which finishes this part of the proof.
 
-	In the compact case, we apply \cref{l:neighborhood third} once more to obtain compact sets $K''_i$ such that
+	For the compact Mayer--Vietoris property, we apply \cref{l:neighborhood third} once more to obtain compact sets $K''_i$ such that
 	\begin{equation*}
@@
 	The rest of the proof is then analogous to the previous case:
-	We have that for both choices of~$i$ the inclusions
-	$K''_i \cap f_{\leq s''} \to L \cap f_{\leq t}$
-	are $\HS_n$ because this is true for the corresponding inclusions with $K''_i$ replaced by $U_i$.
+	We have that for both $i \in \{1, 2\}$ the inclusion
+	$K''_i \cap f_{\leq s''} \hookrightarrow L \cap f_{\leq t}$
+	is $\HS_n$ because it factors through $U_i \cap f_{\leq s''} \hookrightarrow L \cap f_{\leq t}$.
 	Moreover, the inclusion
-	$K'_1 \cap K'_2 \cap f_{\leq s'} \to K''_1 \cap K''_2 \cap f_{\leq s''}$
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \hookrightarrow K''_1 \cap K''_2 \cap f_{\leq s''}$
 	is $\HS_{n-1}$ because it factors through the inclusion
-	$K'_1 \cap K'_2 \cap f_{\leq s'} \to V''_1 \cap V''_2 \cap f_{\leq s''}$,
+	$K'_1 \cap K'_2 \cap f_{\leq s'} \hookrightarrow V''_1 \cap V''_2 \cap f_{\leq s''}$,
 	which is $\HS_{n-1}$ by the induction hypothesis.
@@
 	We conclude that the inclusion
-	$\left(K'_1 \cup K'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
-	is $\HS_n$, so the same is true for the inclusion
-	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \to L \cap f_{\leq t}$
+	$\left(K'_1 \cup K'_2 \right) \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
+	is $\HS_n$, and so the same is true for the inclusion
+	$\left(V'_1 \cup V'_2 \right) \cap f_{\leq s'} \hookrightarrow L \cap f_{\leq t}$
 	as it factors through the previous one.
@@
 \begin{proof}[Proof of \cref{t:local connectedness implies q-tameness}]
-	By definition, the sublevel set filtration of $f$ is q-tame if and only if the inclusion $f_{\leq s} \to f_{\leq t}$ is $\HS$ for all pairs $s < t$.
+	By definition, the sublevel set filtration of $f$ is q-tame if and only if the inclusion $f_{\leq s} \hookrightarrow f_{\leq t}$ is $\HS$ for all pairs $s < t$.
 	Choose $u \in \R$ with $u > t$ and let $g \colon Y \to \R$ be the restriction of $f$ to the sublevel set $Y=f_{\leq u}$.
@@
 	Clearly, the sublevel set filtration of $g$ is also compact, and its domain $Y$ is locally compact being a compact Hausdorff space by assumption.
-	Thus, we can apply \cref{l:key lemma for q-tameness} to the filtration $g_{\leq \bullet}$ with $C = L = Y$ to obtain that the inclusion $f_{\leq s} = C \cap g_{\leq s} \to L \cap g_{\leq t} = f_{\leq t}$ is $\HS$.
+	Thus, we can apply \cref{l:key lemma for q-tameness} to the filtration $g_{\leq \bullet}$ with $C = L = Y$ to obtain that the inclusion $f_{\leq s} = C \cap g_{\leq s} \hookrightarrow L \cap g_{\leq t} = f_{\leq t}$ is $\HS$.
 \end{proof}
@@
 
-We now describe a weaker version of local connectivity of sublevel set filtrations that implies q-tameness when continuity is assumed.
+We now describe a weaker version of local connectivity of sublevel set filtrations, which implies q-tameness when continuity is assumed.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally homologically small} or \emph{weakly $\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
 \end{defi}
@@
 while the weak $\HLC$ property merely requires the existence of an index $s \in (f(x),t)$ satisfying the $\HS$ condition, the $\HLC$ property requires the $\HS$ condition to hold for any $s \in (f(x),t)$.
-If the filtration is induced by a continuous function, the converse also holds as the following theorem shows.
+If the filtration is induced by a continuous function, the converse also holds, as the following theorem shows.
 
@@
 \begin{proof}
-	Fix $x \in X$, a neighborhood $V$ of $x$ and indices $f(x) < s < t$.
-	We need to show that there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
+	Fix $x \in X$, a neighborhood $V$ of $x$, and indices $f(x) < s < t$.
+	We need to show that there exists a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
 
-	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$ is $\HS$.
+	To do so, we start by using the weak $\HLC$ property to choose a neighborhood $U' \subseteq V$ of $x$ and an index $s' \in (f(x),\, t)$ such that the inclusion $f_{\leq s'} \cap U' \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
 	Now, we choose $U = f_{< s'} \cap U'$, where $f_{< s'} = f^{-1} (-\infty, s')$.
@@
 
-	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ factors through the inclusion $f_{\leq s'} \cap U' \to f_{\leq t} \cap V$.
-	This second map is $\HS$ by construction.
-	Any map that factors through an $\HS$ map is also $\HS$, so the proof is complete.
+	We obtain that $f_{\leq s} \cap U \subseteq f_{\leq s'} \cap U'$, so that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$  as it factors through the inclusion $f_{\leq s'} \cap U' \hookrightarrow f_{\leq t} \cap V$, which is $\HS$.
 \end{proof}
@@
 The following result is deduced directly from \cref{l:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness}.
-The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.
+The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}, and a multiparameter version with slightly stronger assumptions on the domain of the function has been shown by Cagliari and Landi \cite{Cagliari.2011} .
 
@@
 
-As the following example illustrates, the continuity assumption in the above theorem is crucial.
+As the following example illustrates, the continuity assumption in the above corollary is crucial.
 
@@
 	which is a compact subspace of $\R^{d+1}$.
-	The function $f \colon \HE \to \R$ whose value at the origin is $0$ and is $1$ everywhere else defines a compact and weakly $\HLC$ sublevel set filtration that is not q-tame with respect to $\H$ if $\H_{n}(\HE)$ is infinite dimensional for some $n$.
+	The function $f \colon \HE \to \R$ whose value is $0$ at the origin and is $1$ everywhere else defines a compact and weakly $\HLC$ sublevel set filtration that is not q-tame with respect to any homology theory $\H$ for which $\H_{d}(\HE)$ is infinite dimensional, as is the case for both singular and \v Cech homology.
+	Specifically, using the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring $\HE$ is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
+	Moreover, the singular homology of $\HE$ is also infinite dimensional, as proven in \cite{Barratt.1962}.
 
@@
 
-	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
-	We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is $\HS$.
-	Since we assume that $\H_{n}$ is homotopy invariant and takes singletons to finite dimensional spaces, it suffices to find $U$ as above such that $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	In order to verify that the sublevel set filtration of $f$ is weakly $\HLC$, we consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$, and $t > f(x)$.
+	We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
+	Since we assume that $\H_{n}$ is homotopy invariant and takes singletons to finite dimensional spaces, it suffices to find $U$ as above such that $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to a constant map.
 
 	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
-	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\HLC$ condition is trivially satisfied.
+	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\HLC$ condition is trivially satisfied.
 
-	For $x$ not the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
+	For $x$ different from the origin we have $f(x) = 1$ and choose $s \in (1,t)$ arbitrarily, so that $f_{\leq s} = f_{\leq t} = \HE$.
 	Note that since $x$ is not the origin, there is a unique $d$-sphere in $\HE$ that contains $x$.
 	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
-	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
 
 	It remains to be shown that $f_{\leq \bullet}$ is not q-tame for $\H$.
-	This follows directly from our assumption that $\H_{n}(\HE)$ is not finite dimensional for some $n$, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
+	This follows directly from our assumption that $\H_{d}(\HE)$ is not finite dimensional, as $f_{\leq t}$ is constant with value $\HE$ for $t \geq 1$.
 \end{example}

### 2022-07-13 sec/inequalities.tex
after second ref

@@
 
-In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities that specializes to the usual Morse inequalities in the smooth context, as well as to the version used by Morse and Tompkins to prove their Unstable Minimal Surface Theorem.
+In this section we prove that $q$-tame persistence modules satisfy a general version of Morse inequalities, specializing to the usual Morse inequalities in the smooth context as well as to the version used by Morse and Tompkins to prove their Unstable Minimal Surface Theorem.
 We deduce these general inequalities from the existence of persistence diagrams as reviewed in \cref{t:q-tame modules have barcodes}.
 
-Recall that for a Morse function $f$ on a closed smooth manifold $X$, the usual Morse inequalities state that for any non-negative integer $n$ the following holds:
+First recall that for a Morse function $f$ on a closed smooth manifold $X$, the classical Morse inequalities \cite{Morse.1925} state that for any non-negative integer~$n$ the following inequality holds:
 \begin{equation} \label{e:classical morse inequalities}
@@
 \end{equation}
-where $c(f)$ is the number of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d\th$ Betti number of $X$.
+where $c_d(f)$ is the number of critical points of $f$ with index $d$ and $\beta_{d}(X)$ is the $d\th$ Betti number of $X$.
 
-If no two critical points of $f$ have the same value, the sets of critical points and values are naturally in one-to-one correspondence, which, in turn, are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing in the barcode of the persistent homology of $f_{\leq \bullet}$.
-More precisely, an index $d$ critical point may either kill an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it may give rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
+If no two critical points of $f$ have the same value, the critical points are in natural one-to-one correspondence with the critical values, which, in turn, are in one-to-one correspondence with the homological changes in the sublevel set filtration of $f$, i.e., the endpoints of the intervals appearing in the barcode of the persistent homology of $f_{\leq \bullet}$.
+More precisely, an index $d$ critical point either kills an existing homology class, in which case it corresponds to the right endpoint of an interval in the barcode of $H_{d-1}(f_{\leq \bullet})$, or it gives rise to a new homology class, in which case it corresponds to the left endpoint of an interval in the barcode of $H_d(f_{\leq \bullet})$.
 
-The Betti numbers of $X$ may also be expressed in terms of barcodes because they agree with the number of intervals that extend to $+\infty$.
-Thus, the Morse inequalities above can be expressed entirely in terms of the barcode (or persistence diagram) of the persistent homology of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
+The Betti numbers of $X$ may also be expressed in terms of barcodes, as they agree with the number of intervals that extend to $+\infty$.
+Thus, the above Morse inequalities can be expressed entirely in terms of the barcode (or persistence diagram) of the persistent homology of the sublevel set filtration of the function, which encodes the homological changes in the filtration.
 
 This approach of counting homological changes instead of critical points is also what Morse used in the non-smooth setting of functional topology.
-To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$ but not indefinitely, \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration, which, when the associated persistence module has a barcode and is continuous from above, correspond to the number of bars with length greater than $\epsilon$ in the $d\th$ barcode with left endpoint $t$, plus the number of bars with length greater than $\epsilon$ in the $(d-1)\th$ barcode with right endpoint $t$ (killed by something $d$-dimensional).
-In the compact smooth setting, for sufficiently small $\epsilon$, the $(d, t, \epsilon)$-cap number equals the number of critical points of index $d$ and value $t$.
+To keep track of the number of $d$-dimensional homological events at filtration value $t$ that persist for at least time $\epsilon > 0$, Morse \cite{Morse.1940} defined the $(d, t, \epsilon)$-\emph{cap numbers} of a filtration.
+The definition given by Morse is specific to Vietoris homology and implicitly relies on the fact that the resulting persistence module is continuous from above.
+Expressed in terms of persistence barcodes, the $(d, t, \epsilon)$-cap number correspond to the number of bars in the $d\th$ barcode with left endpoint~$t$ and length greater than $\epsilon$, plus the number of bars in the $(d-1)\th$ barcode with right endpoint~$t$ and length greater than $\epsilon$.
+In the compact smooth setting, for sufficiently small~$\epsilon$, the $(d, t, \epsilon)$-cap number equals the number of critical points of index~$d$ and value~$t$, which either create homology in degree $d$ or destroy homology in degree $(d-1)$.
+In \cite[Corollary~12.3]{Morse.1940}, Morse proves a version of his eponymous inequalities using cap numbers as a replacement for numbers of critical points, with the stated goal of making the inequalities applicable in settings where the function may not be smooth or the number of critical points may not be finite.
 
-Working entirely in the algebraic setting, we will now fix a graded q-tame persistence module $M$.
-Of course, one may think of $M$ as the persistent homology of a q-tame filtration, but $M$ could for example also arise as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
-By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$ with multiplicity function denoted $\m_d \colon \mulDom \to \N$.
+We now take a more general persistence-based approach that allows us to go beyond the setting of Vietoris homology.
+Working entirely in the algebraic setting, we will fix a graded q-tame persistence module $M$.
+Of course, one may think of $M$ as the persistent homology of a q-tame filtration for any choice of homology theory, but $M$ could also arise, for example, as the filtered Floer homology of some Hamiltonian on a symplectic manifold.
+By \cref{t:q-tame modules have barcodes}, $M$ has a persistence diagram in every degree $d$, with multiplicity function denoted $\m_d \colon \mulDom \to \N$.
 In analogy to Morse's definitions, we may define, for an integer $d$ and real numbers $t$ and $\epsilon > 0$, the $(d, t, \epsilon)$-\emph{cap number} of our graded q-tame persistence module $M$ in terms of its persistence diagram as
@@
 c_{d}^{\epsilon}(t) \ =
-\sum_{\substack{p \in \R \cup \{-\infty\} \\ t - p > \epsilon}} \m_{d-1}(p, t) \ +
-\sum_{\substack{q \in \R \cup \{\infty\} \\ q - t > \epsilon}} \m_d(t, q).
+\alpha_{d}^{\epsilon}(t) + \omega_{d-1}^{\epsilon}(t),
 \end{equation*}
-Note that finiteness of these quantities is ensured by the q-tameness of $M$ and the use of a non-zero $\epsilon$ bounding below the persistence of the considered features.
-To see the necessity of this second condition, consider the q-tame persistence module given by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$.
+where 
+\begin{align*}
+\alpha_{d}^{\epsilon}(t) &= \sum_{\substack{q \in \R \cup \{\infty\} \\ q - t > \epsilon}} \m_d(t, q),
+%\\
+%\intertext{and}
+&
+\omega_{d}^{\epsilon}(t) &= \sum_{\substack{p \in \R \cup \{-\infty\} \\ t - p > \epsilon}} \m_{d}(p, t) 
+\end{align*}
+are the \emph{number of births} and the \emph{number of deaths}, respectively, in degree $d$, at parameter $t$, and with persistence greater than~$\epsilon$.
+We will comment on the connection between our definition and the original one by Morse in \cref{s:caps}.
+Note that finiteness of the quantities above is ensured by the q-tameness of $M$ and the use of a non-zero $\epsilon$ bounding below the persistence of the considered features.
+To see the necessity of this second condition, consider the q-tame persistence module given by the infinite product $\prod_{n \in \N_{> 0}} C([0,1/n))$ whose cap numbers $c^{\epsilon}(0)$ tend to $\infty$ as $\epsilon$ tends to 0.
 
@@
 \[
-c_{d}^{\epsilon} =
-\sum_{t} c_{d}^{\epsilon}(t) \ =
-\sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ q \neq \infty}} \m_{d-1}(p,q) \ +
-\sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q).
+c_{d}^{\epsilon} = \sum_{t \in \R} c_{d}^{\epsilon}(t)  = \alpha_{d}^{\epsilon} + \omega_{d-1}^{\epsilon},
 \]
+where
+\begin{align*}
+\alpha_{d}^{\epsilon} &= \sum_{t \in \R} \alpha_{d}^{\epsilon}(t) = \sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ p \neq -\infty}}\m_d(p,q),
+&
+\omega_{d}^{\epsilon} &= \sum_{t \in \R} \omega_{d}^{\epsilon}(t) = \sum_{\substack{(p,q) \in \mulDom \\ q - p > \epsilon \\ q \neq \infty}} \m_{d}(p,q)
+\end{align*}
+are the \emph{total number of births} and the \emph{total number of deaths}, respectively, in degree~$d$ and with persistence greater than~$\epsilon$.
+
 An important setting where all cap numbers are well-defined is when $M$ is the persistent homology of the sublevel set filtration of a bounded function.
@@
 	Let $M$ be a q-tame persistence module that is both initially and eventually constant.
-	If $\m$ is the multiplicity function of the persistence diagram of $N$,
+	If $\m$ is the multiplicity function of the persistence diagram of~$M$,
 	then for each $\epsilon > 0$,
@@
 
-	For the first summand, observe that, because $M$ is constant below $s$ and constant above $u$, we have $\m(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
+	For the first summand, observe that since $M$ is constant below $s$ and constant above $u$, we have $\m(p,q) = 0$ whenever one of $-\infty < p < s$ or $q < s$ or $p > u$ or $u < q < \infty$ holds.
 	This implies
@@
 
-Comparing to the usual Morse inequalities, the cap numbers in dimension $d$ act like the number of critical points with index $d$.
-As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$ referred to as \emph{essential dimensions}, which, under the same assumptions as before, can be expressed in the language of persistence diagrams as
+Comparing to the classical Morse inequalities, the cap numbers in dimension $d$ play the role of the number of critical points with index $d$.
+As an analogue to the Betti numbers of the manifold appearing in the usual Morse inequalities, Morse defines quantities $p_{d}$, which we refer to as \emph{essential dimensions}.
+For a graded q-tame persistence module $M$, these can be expressed in the language of persistence diagrams as
 \[
@@
 \]
-which is also the dimension of the colimit of the degree $d$ part of $M$.
+which agrees with the dimension of the colimit of the degree $d$ part of $M$.
 
@@
 \begin{proof}
-The $d$th $\epsilon$-cap number is
-\[c_{d}^{\epsilon} = \alpha_{d}^{\epsilon} + \omega_{d-1}^{\epsilon},\] 
-where
-\begin{align*}
-\alpha_{d}^{\epsilon} \ &=
-\sum_{\substack{(p,q) \in \mulDom \\ p\neq\infty, q - p > \epsilon}} \m_d(p, q),
-&
-\omega_{d}^{\epsilon} \ &=
-\sum_{\substack{(p,q) \in \mulDom \\ q\neq-\infty, q - p > \epsilon}} \m_{d}(p, q)
-\end{align*}
-count the multiplicity of left endpoints $p$ and right endpoints $q$, respectively, in elements $(p,q) \in \mulDom$ in the persistence diagram for $M$ that have degree $d$ and persistence $q-p > \epsilon$.
+Recall that the $d$th $\epsilon$-cap number is defined as
+\[c_{d}^{\epsilon} = \alpha_{d}^{\epsilon} + \omega_{d-1}^{\epsilon}.\] 
+%where
+%\begin{align*}
+%\alpha_{d}^{\epsilon} \ &=
+%\sum_{\substack{(p,q) \in \mulDom \\ p\neq\infty, q - p > \epsilon}} \m_d(p, q),
+%&
+%\omega_{d}^{\epsilon} \ &=
+%\sum_{\substack{(p,q) \in \mulDom \\ q\neq-\infty, q - p > \epsilon}} \m_{d}(p, q)
+%\end{align*}
+%count the total number of births $p$ and deaths $q$, respectively, over all elements $(p,q) \in \mulDom$ in the persistence diagram for $M$ that have degree $d$ and persistence $q-p > \epsilon$.
 Since we assume $\m_d(-\infty, p) = 0$ for all $p$, we have
 	\begin{equation*}
-	p_{d} \ = \alpha_{d}^{\epsilon} - \omega_{d}^{\epsilon}
+	p_{d} \ = \alpha_{d}^{\epsilon} - \omega_{d}^{\epsilon}.
 	\end{equation*}
-The difference of the two numbers, which appears in the Morse inequalities to be shown, is thus
+The difference of the two numbers is thus
 \[
@@
 \]
-and their sum is
+and so their sum is
 \[
@@
 
-In other words, given the assertion that the persistence module $M$ has a persistence diagram, the Morse inequalities simply express the fact that the number of right endpoints in nonnegative.
+In other words, given the assertion that the persistence module $M$ has a persistence diagram, the Morse inequalities simply express the fact that the total number of deaths of features with persistence greater than $\epsilon$ is nonnegative.
 % This observation emphasizes the role of persistence in interpreting fundamental facts in Morse theory.
@@
 As shown in \cref{t:cap numbers well defined}, the finiteness assumptions are satisfied if $M$ is initially and eventually constant.
-Hence, as a special case, the theorem yields generalized Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, including classical Morse functions $f$ on closed smooth manifolds $X$.
-As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:classical morse inequalities}, as $\beta_d(X) = p_d$ and $c_d^{\epsilon} = \# \crit_d(f)$ for $\epsilon > 0$ smaller than the minimal difference between any two critical values of~$f$.
+Hence, as a special case, the theorem yields generalized Morse inequalities for any bounded real-valued function whose sublevel set filtration has q-tame persistent homology, including smooth Morse functions $f$ on closed smooth manifolds $X$.
+As outlined in our motivation for the definition of cap numbers, in this setting our inequalities \eqref{e:morse inequalities} agree with the classical inequalities \eqref{e:classical morse inequalities}, as $\beta_d(X) = p_d$ and $c_d^{\epsilon} = \# \crit_d(f)$ for any $\epsilon > 0$ smaller than the minimum difference between any two critical values of~$f$.
 Morse inequalities for unbounded functions can still be obtained by restricting the function to an arbitrary sublevel set.
+Using \v{C}ech homology and considering bounded q-tame functions, our cap numbers and essential dimensions agree with the corresponding historical notions from \cite{Morse.1940}, so in this case our inequalities \eqref{e:morse inequalities} also agree with the inequalities \cite[Corollary~12.3]{Morse.1940}.
 
-The finiteness conditions of our theorem are also satisfied by the Douglas functional considered by Morse and Tompkins as an application of Morse's theory of functional topology.
-The details in \cite{Morse.1939} are incomplete, with some crucial theorems being stated without proof, and with a citation to a paper in preparation that has never been published under the same name (we suppose that this paper is \cite{Morse.1940}).
-Nevertheless, Morse and Tompkins establish the conditions required for \cref{t:local connectedness implies q-tameness}, from which we can deduce q-tameness and obtain Morse inequalities by \cref{t:inequalities}.
-While Morse's approach is restricted to \v{C}ech homology, and singular homology is explicitly excluded due to a lack of continuity, our approach is more flexible and applies to any setting where persistent homology is q-tame.
-If the persistent homology of the sublevel set filtration is not only q-tame but also continuous from above, our inequalities agree with Morse's historical version from functional topology as presented in \cite[Corollary~12.3]{Morse.1940}.
+To apply our inequalities, one needs q-tameness, and our next goal will be to give topological conditions that ensure q-tameness (\cref{t:local connectedness implies q-tameness}).
+These conditions are in particular satisfied by the Douglas functional (\cref{prop:douglas_hlc}), as shown by Morse and Tompkins in their work on unstable minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces}, and which motivated the developments in \cite{Morse.1940}.
 
@@
 	In addition to the formulation of the inequalities in terms of cap numbers, Morse also proposed a generalized version of critical points, which he called homotopically critical, and which formalizes the idea of criticality of a point in terms of topological changes in the sublevel set filtration.
-	This notion was employed by Morse and Tompkins in their study of minimal surfaces \cite{Morse.1939}, which we will partly review in \cref{s:surfaces} and for which a thorough historical account may be found in \cite[Section II.6]{Struwe.1988}.
-	The usefulness of this notion might however be limited in many cases of interest.
-	In Floer theory, for example, critical points of the action functional corresponding to a Hamiltonian usually have infinite index and thus do not produce changes in the topology.
-	In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable, because while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology.
+	This notion was employed in the above mentioned work on minimal surfaces by Morse and Tompkins \cite{Morse.1939}.
+
+	The usefulness of this notion might however be limited in some cases of interest.
+	In Floer theory, for example, critical points of the action functional corresponding to a Hamiltonian usually do not have a finite index and thus do not lead to a change in the homotopy type of sublevel sets.
+	In this setting, our approach of formulating the inequalities purely in algebraic terms might be more suitable: while these critical points are not topologically visible, they do correspond to features in the persistence diagram of the filtered Floer homology.
 \end{rem}

### 2022-07-13 sec/introduction.tex
after second ref

@@
 Morse theory in the smooth context was masterfully presented in Milnor's famous book on the subject \cite{Milnor.1963}, where he also gave a new proof of Bott's periodicity by applying Morse theory to the energy functional of paths in a Riemannian manifold, which notably goes beyond the compact setting.
-Another important example of the use of Morse's insights in an infinite context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{Salamon.1999}.
+Another important example of the use of Morse's insights in an infinite-dimensional context is Floer's work on the Arnold conjecture and its many ramifications in symplectic topology, as surveyed for example in \cite{Salamon.1999}.
 Morse himself worked in a very general setting, publishing in the 1930s a pair of papers \cite{Morse.1937, Morse.1940} and a monograph \cite{Morse.1938} in which he established the key results of Morse theory in the broad context defined by semi-continuous functionals on metric spaces.
 He called the theory set forth in this body of work \emph{functional topology} and used it to study questions about minimal surfaces motivated by Douglas' solution to Plateau’s Problem \cite{Douglas.1931}.
-In particular, Morse and Tompkins \cite{Morse.1939} used these techniques to prove a general \emph{Mountain Pass Lemma} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous (\cref{thm:mountain_pass}).
+In particular, Morse and Tompkins \cite{Morse.1939} used these techniques to prove a general \emph{Mountain Pass Theorem} --~an existence result for saddle points~-- applying to functions that are not necessarily continuous (\cref{thm:mountain_pass}).
 From this, they deduce their \emph{Unstable Minimal Surface Theorem}, showing the existence of critical points of the Douglas functional that are not local minima (\cref{thm:unstable_minimial_surface}).
@@
 \end{displaycquote}
-A similar assessment was given by Raoul Bott, who writes in \cite[p.~934]{Bott.1980} that the papers \cite{Morse.1937, Morse.1940} ``are not easy reading'' and constitute a ``tour de force'' by Morse.
+A similar assessment was given by Bott, who writes in \cite[p.~934]{Bott.1980} that the papers \cite{Morse.1937, Morse.1940} ``are not easy reading'' and constitute a ``tour de force'' by Morse.
 
-The intricacies of Morse's development notwithstanding, many of his ideas have resurfaced in the intervening years and flourished in other domains.
+The intricacies of Morse's development notwithstanding, many of his ideas have subsequently resurfaced and flourished in other domains.
 In particular, in applied topology and symplectic geometry, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
@@
 In this work, using persistence diagrams, we generalize the definition of these cap numbers to persistence modules and prove the existence of Morse inequalities for a large class of them (\cref{t:inequalities}).
-Our approach makes these inequalities accessible in new contexts beyond those originally covered by functional topology. %including, for example, symplectic geometry.
+Our approach makes these inequalities accessible in new contexts beyond those originally covered by functional topology.
 
@@
 For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
+This condition is satisfied by a large class of important constructions; for example, the Vietoris--Rips or \v Cech persistent homology of a totally bounded metric space is q-tame \cite{Chazal.2014}.
 The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
-We now present the answers provided in this work.
+We now present the answers provided in the present work.
 
-The persistence module associated to a filtration depends on the homology construction used, which even agreeing on cellular spaces, need not coincide for general topological spaces.
-We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open of closed sets, for example singular or \v{C}ech homology, respectively.
+The persistence module associated to a filtration depends on the homology construction used, which, even when agreeing on cellular spaces, need not coincide for general topological spaces.
+We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open or closed sets, the primary examples being singular homology or \v{C}ech homology, respectively.
 
-The sublevel set filtration $f_{\leq t} = f^{-1}(-\infty, t]$ of a real valued function $f$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is \emph{homologically small}; that is to say, for a given homology theory the induced map has finite rank in every degree.
+The sublevel set filtration $f_{\leq t} = f^{-1}(-\infty, t]$ of a real valued function $f$ is called \emph{locally homologically small} or \emph{$\HLC$} for a given homology theory if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$, there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is \emph{homologically small}; that is to say, the induced map in homology has finite rank in every degree.
 We say that a sublevel set filtration is \emph{compact} if all sublevel sets are compact Hausdorff spaces.
@@
 \begin{thm*}
-	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then it is also q-tame.
+	If the sublevel set filtration of a function $f \colon X \to \R$ is compact and	$\HLC$, then its persistent homology is q-tame.
 \end{thm*}
@@
 This functional satisfies the hypotheses of \cref{t:local connectedness implies q-tameness}, so its associated persistent \v{C}ech homology is indeed q-tame and admits a persistence diagram.
-From this, one can easily deduce the existence of an unstable minimal surface for certain explicit examples.
-As it turns out, the local connectivity conditions proposed by Morse \cite{Morse.1937} are not sufficient for this purpose, which we illustrate by a counterexample (\cref{c:counterexample}).
+From this, one can easily deduce the existence of an unstable minimal surface.
+As it turns out, the local connectivity conditions proposed by Morse \cite{Morse.1938,Morse.1939,Morse.1940} are not sufficient for this purpose, which we illustrate by a counterexample (\cref{c:counterexample}).
 
@@
 The primary contribution of this work consists in a modern development of the homological aspects of Morse's functional topology from the perspective of persistence theory.
-We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in functional analysis.
+We adjust several key definitions and prove stronger statements -- including a generalized version of the Morse inequalities -- in order to allow for novel uses of persistence techniques in the calculus of variations.
 We provide sufficient conditions for a lower semicontinuous function to have q-tame persistent sublevel set homology, and hence to admit a persistence diagram.
@@
 
-In \cref{s:persistence} we recall the foundations of persistence theory where, for us, the persistent homology of a sublevel set filtration is the key example.
+In \cref{s:persistence} we recall the foundations of persistence theory, considering the persistent homology of a sublevel set filtration as the key example.
 We present a persistence-theoretic point of view on Morse inequalities in \cref{s:inequalities}.
 It generalizes both their versions in the smooth and compact setting as well as the one used in functional topology.
-The core of this work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness of its associated persistence module.
-We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' use of functional topology in minimal surface theory, and explore its relation to our results.
+The main result of the present work is presented in \cref{s:connectivity}, where we define two natural notions of local-connectivity for a sublevel set filtration and show under what circumstances they imply q-tameness of its associated persistence module.
+We close in \cref{s:surfaces} with a historical overview of Morse--Tompkins' application of functional topology to minimal surface theory, and we explore its relation to our results.
 \cref{s:vietoris} contains a brief discussion on the definitions of Vietoris and \v{C}ech homology and their equivalence for compact metric spaces.

### 2022-07-13 sec/persistence.tex
Enforce basic code conventions
after second ref

@@
 In this section we present an overview of the theory of persistence through filtrations by sublevel sets of real-valued functions on general topological spaces.
-For a detailed exposition we refer to either of \cite{Chazal.2016a, Oudot.2015, Polterovich.2020}, and for applications of this theory in symplectic geometry to
+For a detailed exposition we refer to \cite{Chazal.2016a, Oudot.2015, Polterovich.2020} and for applications of this theory in symplectic geometry to
 \cite{Polterovich.2016, Usher.2016, LeRoux.2018, Shelukhin.2019}.
@@
 For example, in the next section we will see how they lead to a generalization of the classical Morse inequalities.
-Much of their usefulness comes from a remarkable fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance} \cite{Cohen-Steiner.2007}.
+Much of their usefulness results from a remarkable fact known as \emph{stability}, stating that the map from functions on $X$ with the supremum norm to the set of all persistence diagrams is 1-Lipschitz with respect to a certain natural metric called \emph{bottleneck distance} \cite{Cohen-Steiner.2007}.
 
 In more detail, consider a space $X$ and a function $f \colon X \to \R$.
-Unless noted otherwise, the functions we consider need not be continuous.
+Unless stated otherwise, the functions we consider need not be continuous.
 We pass to filtered spaces by considering the \emph{sublevel set filtration $f_{\leq \bullet}$ of $X$ induced by $f$}, which is defined by
@@
 
-By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$ yields for every $t \in \R$ a vector space~$M_t$ and for any pair~$s, t \in \R$ with~$s \leq t$ a linear map~$M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
-In other words, we obtain a functor $M$ from the real numbers considered as a category via its poset structure to the category of vector spaces.
+By definition, applying to a filtered space $\{X_t\}_{t \in \R}$ a functor from $\Top$ to $\Vect$ yields, for every $t \in \R$ a vector space~$M_t$ and for any pair~$s, t \in \R$ with~$s \leq t$, a linear map~$M_{s,t} \colon M_s \to M_t$ such that $M_{t,t}$ is the identity and the composition $M_{s,t} \circ M_{r,s}$ is equal to $M_{r,t}$ for any triple $r \leq s \leq t$.
+In other words, we obtain a functor $M$ from the real numbers, considered as a poset category, to the category of vector spaces.
 Such functors are called \emph{persistence modules}.
@@
 \end{equation*}
-commute for all pairs $s \leq t$.
+commute for every pair $s \leq t$.
 
 Since most examples of interest arise from applying a homology theory to a filtered space, we also consider \emph{graded persistence modules}, which are collections of persistence modules indexed by the integers.
-To lighten the presentation of the theory of persistence, in what follows we will solely focus on persistence modules omitting straightforward generalizations to their graded counterparts.
+To lighten the presentation of the theory of persistence, in what follows we will solely focus on persistence modules, omitting straightforward generalizations to their graded counterparts.
 
-Usual constructions that work in the category of vector spaces over the field $\F$ can be transferred to the category of persistence modules by applying them pointwise.
-For example, the kernel and cokernel of a morphism, as well as the direct sum of persistence modules are well-defined.
+Functorial constructions defined on the category of vector spaces over the field~$\F$ can be transferred to the category of persistence modules by applying them pointwise.
+For example, the kernel and cokernel of a morphism as well as the direct sum of persistence modules are well-defined.
 Persistence modules that are \emph{indecomposable}, i.e., those that have only trivial direct sum decompositions, play an important role in persistence theory.
@@
 The most commonly used existence result for barcode decompositions is due to Crawley-Boevey \cite{Crawley-Boevey.2015}.
-It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all $t \in \R$.
+It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all~$t \in \R$.
 Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
@@
 As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
-Yet, there are multiple ways to regularize q-tame persistence modules to obtain invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
+Yet, there are multiple ways to regularize q-tame persistence modules in order to obtain invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
 We briefly recall the approach from \cite{Chazal.2016b}.
 
-A persistence module $M$ is called \emph{ephemeral} if the maps $M_{s,t} \colon M_s \to M_t$ are $0$ for all $s < t$.
-The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \to M$ is an ephemeral persistence module.
+A persistence module $M$ is called \emph{ephemeral} if the maps $M_{s,t} \colon M_s \to M_t$ are zero for all $s < t$.
+The \emph{radical} $\rad M$ of a persistence module $M$ is the unique minimal submodule of $M$ such that the cokernel of the inclusion $\rad M \hookrightarrow M$ is an ephemeral persistence module.
 More explicitly, we have $(\rad M)_t = \sum_{s<t}\im M_{s,t}$.
@@
 with the associated barcode describing the isomorphism type of~$M$ ``up to ephemerals".
-This can be formalized by constructing the \emph{observable category of persistence modules}, which is equivalent to the quotient of the category of persistence modules by the full sub-category of ephemeral persistence modules.
+This can be formalized by constructing the \emph{observable category of persistence modules}, which is equivalent to the quotient of the category of persistence modules by the full subcategory of ephemeral persistence modules.
 The barcode of the radical of a q-tame persistence module $M$ is then a complete invariant of $M$ in the observable category.
@@
 \end{equation*}
-the cardinality of the set $\{ \lambda \in \Lambda \mid \inf I_{\lambda} = p,\ \sup I_{\lambda} = q\}$.
-Because information about the endpoints of intervals is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete invariant for q-tame modules in the observable category.
+the cardinality of the set of intervals with lower bound $p$ and upper bound $q$, $\{ \lambda \in \Lambda \mid \inf I_{\lambda} = p,\ \sup I_{\lambda} = q\}$.
+Since the type of interval is irrelevant in the observable category, the persistence diagram associated to the barcode of the radical is still a complete invariant for q-tame modules in the observable category.
 Stated explicitly, we have the following.
@@
 
-We have thus seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration, and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
-If this is the case, we will call the function \emph{q-tame} with respect to the functor $\H$.
-If $\H$ is a homology theory, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration $f_{\leq \bullet}$.
+We have thus seen how to obtain a persistence diagram from a real-valued function $f$ by applying a functor $\H \colon \Top \to \Vect$ to its sublevel set filtration and considering the persistence diagram of the resulting persistence module $\H(f_{\leq \bullet})$, which is well-defined provided that $\H(f_{\leq \bullet})$ is q-tame.
+In this case, we will also call the function $f$ and the filtration $f_{\leq \bullet}$ \emph{q-tame} with respect to the functor~$\H$.
+If $\H$ is a homology theory, we will call $\H(f_{\leq \bullet})$ the \emph{persistent homology} of the filtration~$f_{\leq \bullet}$.
 
 As mentioned earlier, the passage from real-valued functions on a topological space to persistence diagrams is 1-Lipschitz for appropriate metrics.
-We now provide more details regarding this result although they are not used in the present work.
+We now provide some more details regarding this result for context, noting that they are not used in the present work.
 On the space of real-valued functions one considers the metric induced by the supremum norm, and on the space of persistence diagrams the \emph{bottleneck distance}.
@@
 
-We will now finish this section by recording some helpful facts about the \emph{number of births at $t$}
-\[
-	\alpha(t) = \sum_{q \in (t, \infty]} \m(t,q)
-\]
-and the \emph{number of deaths at $t$}
-\[
-	\omega(t) = \sum_{p \in [-\infty, t)} \m(p,t)
-\]
-for a q-tame persistence module $M$ with persistence diagram given by $\m$.
+%We will now finish this section by recording some helpful facts about the \emph{number of births at $t$}	\todo{move this}
+
+%\[
+%	\alpha(t) = \sum_{q \in (t, \infty]} \m(t,q)
+%\]
+%and the \emph{number of deaths at $t$}
+%\[
+%	\omega(t) = \sum_{p \in [-\infty, t)} \m(p,t)
+%\]
+%for a q-tame persistence module $M$ with persistence diagram given by $\m$.
 %\begin{defi}
@@
 
-\todo{should we somehow unify definitions of $\alpha$, $\omega$, $c$ etc. in a single place? compare also the use of $\alpha^{\epsilon}$ and $\omega^{\epsilon}$ in the proof of \cref{t:inequalities}}
-
-\begin{lem}
-\label{lem:birth_death_formulas}
-	Let $M$ be a q-tame persistence module.
-	For each $t \in \R$ we either have 
-	\[
-		\alpha(t) = \dim \coker (\colim_{s < t} M_{s} \to \lim_{u > t} M_{u})
-	\]
-	or both quantities are infinite.
-	Similarly, we either have 
-	\[
-		\omega(t) = \dim \ker (\colim_{s < t} M_{s} \to \lim_{u > t} M_{u})
-	\]
-	or both quantities are infinite.
-\end{lem}
-\begin{proof}
-	None of the quantities appearing in the statement change if we replace $M$ by its radical.
-	This radical admits a barcode decomposition and the claims easily follow from an explicit computation on the corresponding barcode module.
-\end{proof}
-
-If $M$ is continuous from below or above, then the colimits and limits appearing in the formulas above may simply be replaced by constituent vector spaces of $M$. 
-As a special case, this yields the following corollary.
-
-\begin{cor}
-\label{cor:regular_value_no_endpoint}
-	Let $M$ be a q-tame persistence module.
-	If $M$ is continuous from above and below at $t$ we have
-	\[
-		\alpha(t) = \omega(t) = 0.
-	\]
-\end{cor}
+%\todo{should we somehow unify definitions of $\alpha$, $\omega$, $c$ etc. in a single place? compare also the use of $\alpha^{\epsilon}$ and $\omega^{\epsilon}$ in the proof of \cref{t:inequalities}}

### 2022-07-13 sec/surfaces.tex
Enforce basic code conventions
Update Mountain Pass Lemma terminology
after second ref

--- 2022-03-29 sec/surfaces.tex
@@
 Having established topological conditions for the existence of persistence diagrams associated to filtrations and corresponding generalized Morse inequalities, we now describe how these results relate to Morse's general theory of functional topology \cite{Morse.1937, Morse.1938, Morse.1940}, and to its application in Morse and Tompkins' work on unstable minimal surfaces from \cite{Morse.1939}.
-We will focus on the homological aspects of this approach referring to \cite[Sections 4.3--5]{Bott.1980} for a general exposition.
-For a more thorough presentation of the unstable minimal surface problem, including the analytical details, please consult \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
+We will focus on the homological aspects of this approach, referring to \cite[Sections 4.3--5]{Bott.1980} for a general exposition.
+For a more thorough presentation of the unstable minimal surface problem, including the analytical details see \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
 
 \subsection{The unstable minimal surface problem}
+\label{subsec:unstable}
 
@@
 Let $\widetilde{\Omega}$ be the space of continuous non-decreasing functions $\varphi \colon \R \to \R$ with $\varphi(t+2\pi) = \varphi(t) + 2\pi$ for all $t$ and $\varphi(\alpha_i)=\alpha_i$ for three fixed distinct points $\alpha_i \in [0,2\pi)$.
-The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined as
+The \emph{Douglas functional} on $\widetilde \Omega$ associated to the curve $g$ is defined \cite{Douglas.1931} as
 \begin{equation*}
@@
 Let $\Omega_g = \{\varphi \in \widetilde\Omega \mid A_g(\varphi) < \infty\}$, equipped with the $C^0$ metric.
-Douglas proved that, for a large class of curves~$g$, the set $\Omega_g$ is non-empty and the sublevel sets of $A_g$ are compact.
+The set $\Omega_g$ is non-empty because $g$ is continuously differentiable and hence rectifiable, which implies $A_g(\operatorname{id}_{\R}) < \infty$ \cite[p.~267-268]{Douglas.1931}.
+Moreover, the sublevel sets of $A_g$ are compact \cite[p.~448]{Morse.1939}.
 Since $A_g$ is bounded below by $0$, this implies that $A_g$ attains a global minimum.
@@
 As alluded to in \cref{r:homotopically critial points}, Morse and Tompkins consider a homotopical notion of critical point for a general function $F \colon M \to \R$ on a metric space \cite[p.~445]{Morse.1939}, see also \cite{Morse.1943}.
-Roughly, a point $p$ is \emph{homotopically critical} if it has no neighborhood in $M_{\leq F(p)}$ that can be mapped by a homotopy into $M_{\leq t}$ for some $t<F(p)$.
 
-Morse and Tompkins prove \cite[p.~464]{Morse.1939} that each homotopically critical point of the functional $A_g$ indeed corresponds to
+\begin{defi}[{{\cite[Definition II.6.1-II.6.2]{Struwe.1988}, \cite[p.~445, 466]{Morse.1939}}}]
+\label{def:critical_set}
+	Consider a real-valued function $F$ on a metric space $(M,d)$.
+	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(p,1) \neq p$, such that for every compact subset $V \subseteq U$ there exists a \emph{displacement function} $\delta \colon \R_{\geq 0} \to \R_{\geq 0}$ with
+	$\delta(e) = 0$ if and only if $e = 0$, and
+	\[
+	F(\varphi(x,s)) - F(\varphi(x,t)) \geq \delta(d(\varphi(x,s),\varphi(x,t)))
+	\]
+	for all $x \in V$ and $0 \leq s \leq t \leq 1$.
+% 	\begin{itemize}
+% 		\item $\delta(e) = 0$ if and only if $e = 0$, and
+% 		\item $F(\varphi(x,s)) - F(\varphi(x,t)) > \delta(d(\varphi(x,s),\varphi(x,t)))$ for all $x \in V$ and $0 \leq s \leq t \leq 1$.
+% 	\end{itemize}
+	A point that is not homotopically regular is called \emph{homotopically critical}.
+	Function values of homotopically critical points will be called \emph{critical values} and all other values will be called \emph{regular values}.
+	A \emph{critical set} $S$ is a closed and open subset of the subspace of all homotopically critical points with a given function value.
+	It is said to be of \emph{minimum type} if there exists a neighborhood $N$ of the closure $\overline{S}$ of $S$, taken in $M$, such that the function values on $N \setminus S$ strictly exceed the function value on $S$.
+\end{defi}
+
+Note that, in particular, an isolated local minimum constitutes a critical set of minimum type.
+Similarly, a critical submanifold of a Morse-Bott function on which the function values are locally minimized is also a critical set of minimum type.
+
+\begin{defi}[{{\cite[p.~445]{Morse.1939}}}]
+\label{def:upper_reducible}
+    Let $F \colon M \to \R$ be a function on a metric space. 
+    We say that $F$ is \emph{weakly upper-reducible} if for all $p \in M$ and all $c > F(p)$ there exists a neighborhood $U$ of $p$ in $F_{\leq c}$, a positive constant $\eta > 0$, and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(U,1) \subseteq F_{\leq c-\eta}$, such that on every compact subset $V \subseteq U \cap F_{\geq c - \eta}$ there exists a displacement function for $\varphi$ as in \cref{def:critical_set}.
+\end{defi}
+
+In \cite[p.~36]{Morse.1938}, the stronger notion of \emph{upper-reducibility}, without the prefix \emph{weakly}, is defined analogously to \cref{def:upper_reducible} with the slight difference that the existence of a displacement function is not only demanded for compact $V \subseteq U \cap F_{\geq c - \eta}$, but for all compact $V \subseteq U$.
+Morse and Tompkins state the following Mountain Pass Theorem under slightly different assumptions, and with a slightly different conclusion.
+
+% \begin{thm}[{\cite[Corollary 7.1, p.~472]{Morse.1939}}]
+% \label{thm:mountain_pass}
+% 	Let $M$ be a metric space and $F \colon M \to \R$ a function.
+% 	Assume that $F$ is bounded below, that the sublevel set filtration of $F$ is compact, and let $\H$ be an additive homology theory taking non-zero values on non-empty sets in dimension 0, and such that $\H(F_{\leq \bullet})$ is q-tame, continuous from above and has essential dimension $p_{0} = 1$.
+% 	If $M$ contains two distinct critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.\todo{sort of difficult to parse, assumptions too long.
+%	maybe only formulate for \v{C}ech homology to get rid of some text?}
+% \end{thm}
+
+\begin{thm}[Mountain Pass Theorem, {\cite[Corollary 7.1]{Morse.1939}}]
+\label{thm:mountain_pass}
+	Let $F \colon M \to \R$ be a weakly upper-reducible function on a non-empty connected metric space with compact sublevel set filtration.
+	Assume that the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism, and that the sublevel set filtration of $F$ is $\HLC$ with respect to \v Cech homology.
+	If $M$ contains two distinct critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.
+\end{thm}
+
+It is worth noting, however, that the details in \cite{Morse.1939} are incomplete, with some crucial theorems such as \cite[Theorems 7.3 and 7.4, Corollary 7.1]{Morse.1939} being stated without proof, and with a citation to a paper in preparation that has never been published under the given name (we suppose that this paper is \cite{Morse.1940}).
+Moreover, there is a gap in \cite{Morse.1940}, because \cite[Theorem 6.3]{Morse.1940}, which establishes q-tameness, is incorrect as we will show in \cref{c:counterexample}.
+The assumptions we choose for our version of the Mountain Pass Theorem are adapted from the original assumptions to the modern language of persistence theory, and they fix the problem with q-tameness.
+Still, our assumptions can be established for the Douglas functional from the results of Morse and Tompkins \cite{Morse.1939}.
+We provide more detailed comments regarding the differences between these assumptions in \cref{rem:critical_set,rem:mountain_pass_assumptions,subsec:historic_hlc}, and regarding the differences in the conclusions of the Mountain Pass Theorem in \cref{rem:mountain_pass_conclusion}.
+
+\begin{rem}\label{rem:critical_set}
+	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
+	Without this additional assumption, however, \cref{thm:mountain_pass} does not hold, as shown by the example $F \colon [0,1] \to \R$ with $F(0) = F(1) = 0$ and $F(t) = 1$ for $0 < t < 1$:
+	$F$ has the four critical sets $\{0\}$, $\{1\}$, $\{0\} \cup \{1\}$ and $(0,1)$, which all satisfy the minimum type condition if the neighborhood $N$ need not contain their closure, but then there is no critical set that is not of minimum type.
+\end{rem}
+
+\begin{rem}\label{rem:mountain_pass_assumptions}
+    In \cite[Corollary 7.1]{Morse.1939}, the assumptions that Morse and Tompkins use for $F$ and $M$ are that the sublevel set filtration is compact,  weakly upper-reducible, ``regular at infinity'', and that $M$ is ``locally $F$-connected''.
+    Compactness is also required for our version, as is weak upper-reducibility. 
+    Local $F$-connectedness is replaced by the $\HLC$ condition.
+    (This point will be discussed in more detail in \cref{subsec:historic_hlc}).
+    Regularity at infinity roughly corresponds to our assumption that $M$ is connected and the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism (see \cite[p.~444]{Morse.1939} and our proof of \cref{thm:unstable_minimial_surface}).
+    This assumption may also replaced by the assumption that $\cp_0 = 1$, which we deduce from our assumptions in \cref{lem:essential_cech_dim}.
+\end{rem}
+
+\begin{rem}\label{rem:mountain_pass_conclusion}
+    The precise statement of \cite[Corollary 7.1]{Morse.1939} postulates the existence of a homotopic critical point such that every critical set containing it has a positive first \emph{type number}.
+    This corresponds to our statement in so far as the existence of a critical set not of minimum type implies that there are $\epsilon$ and $t$ such that $c_{1}^{\epsilon}(t) > 0$ (see \cref{lem:endpoint_implies_crit_pt} and the proof of \cref{thm:mountain_pass}).
+    Note, however, that the existence of a positive cap number $c_{1}^{\epsilon}(t) > 0$ does not conversely imply the existence of a critical set not of minimum type:
+    Consider the parabola $P = \{(x,x^2) \in \R^2 \mid x \in \R\}$, let $M = S^1 \times P$ and let $F \colon M \to \R$ be the Morse--Bott function given by the projection to the second coordinate in $P$.
+    There is a single critical set $C = S^1 \times \{(0,0)\}$, which is of minimum type, but we still have $c_{1}^{\epsilon}(0) > 0$ for any $\epsilon > 0$ if $H$ is a homology theory such that $H_1(C) \neq 0$, e.g.\ singular or \v{C}ech homology.
+    To establish the existence of a critical set not of minimum type in the proof of \cref{thm:mountain_pass}, we will show that not only $c_{1}^{\epsilon}(t) > 0$, but that we indeed have $\omega_1^{\epsilon}(t) > 0$, i.e., that the positive cap number is created by the death of a feature.
+\end{rem}
+
+\begin{rem}
+	We mention that more general homology theories can be considered in \cref{thm:mountain_pass}.
+	The precise hypotheses on the homology theory $\H$ are that it is additive, taking non-zero values on non-empty sets in dimension $0$, and such that $\H(F_{\leq \bullet})$ is continuous from above, i.e., $\H(F_{\leq s}) \to \lim_{s < t} \H(F_{\leq t})$ is an isomorphism for all~$s \in \R$.
+	One may also replace the topological conditions of $M$ being connected, the natural map $\colim \H_0(F_{\leq \bullet}) \to \H_0(M)$ being an isomorphism, and $F$ being $\HLC$ by the algebraic conditions that $p_0 = 1$ and $\H(F_{\leq \bullet})$ be q-tame.
+	% Recall that $\H$ is called \emph{additive} if $\H (A \sqcup B) \cong \H(A) \oplus \H(B)$ for all $A$ and $B$.
+\end{rem}
+
+Morse and Tompkins show \cite[Theorem 6.2]{Morse.1939} that each homotopically critical point of the Douglas functional $A_g$ indeed corresponds to
 %
@@
 %called
-a \emph{minimal surface} -- a surface with vanishing mean curvature -- and use this correspondence to prove the following result, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}.
+a \emph{minimal surface} -- a surface with vanishing mean curvature -- and using this correspondence the following result, also reviewed in \cite[Theorem II.6.10]{Struwe.1988}, can be deduced from the Mountain Pass Theorem as further explained in \cref{subsec:historic_hlc}.
 
 \begin{thm}[{Unstable Minimal Surface Theorem \cite[p.~472]{Morse.1939}}]
-	If the space $\Omega_g$ contains two distinct solutions of Plateau's Problem contained in disjoint critical sets of the functional $A_g$, then it also contains a critical set not of minimum type.
-	%, more precisely, a homotopically critical point of $A_g$ of non-minimum type.
+\label{thm:unstable_minimial_surface}
+	If the space~$\Omega_g$ contains two minimal surfaces contained in distinct critical sets of minimum type of the functional $A_g$, then it also contains an \emph{unstable} minimal surface, i.e., a minimal surface contained in a critical set that is not of minimum type.
 \end{thm}
-Here, a \emph{critical set} $S$ is a closed and open subspace of the set of all critical points with a given function value.
-It is said to be of \emph{minimum type} if for every neighborhood $N$ of $S$, the function value on the complement $N \setminus S$ exceeds the function value on $S$.
-%it corresponds to a homotopically critical point of $A_g$ of non-minimum type?
-In addition to the general theorem above, Morse and Tompkins also give an explicit example of a curve $g$ satisfying the assumptions, thus proving the existence of an unstable minimal surface in the above sense.
 
-%sci-hub.se/10.1215/S0012-7094-41-00828-1
-%
-%A point q of M will be termed non-minimizing if in every neighborhood of q there is a point p such thatF(p)<F(q).
-A homotopic critical set which is not a minimizing set contains at least one non-minimizing point of F.
+In \cite[Section 8]{Morse.1939}, Morse and Tompkins provide an example of a curve $g$ for which $\Omega_{g}$ indeed contains two distinct critical sets of minimum type, so that $g$ then also spans an unstable minimal surface.
 
-While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable for its close connection to persistent homology.
+While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable
+% for its close connection to persistent homology.
+for its connections to other areas of mathematics.
+As an illustration, we will now sketch a proof of \cref{thm:mountain_pass} using the previously developed machinery, starting with some intermediate results.
+As a first step, we will give general formulas for \emph{numbers of births} $\alpha(t) = \sum_{q \in (t, \infty]} \m(t,q)$ and \emph{numbers of deaths} $\omega(t) = \sum_{p \in [-\infty, t)} \m(p,t)$ in q-tame persistence modules.
 
-\subsection{Morse's local connectivity conditions}
+\begin{lem}
+\label{lem:birth_death_formulas}
+	Let $M$ be a q-tame persistence module.
+	For each $t \in \R$ we either have
+	\[
+		\alpha(t) = \dim \coker \left( \colim_{s < t} M_{s} \to \lim_{u > t} M_{u} \right)
+	\]
+	or both quantities are infinite.
+	Similarly, we either have
+	\[
+		\omega(t) = \dim \ker \left( \colim_{s < t} M_{s} \to \lim_{u > t} M_{u} \right)
+	\]
+	or both quantities are infinite.
+\end{lem}
+\begin{proof}
+    The internal colimits $\colim_{s < t} M_{s}$ and limits $\lim_{u > t} M_{u}$ are invariant under weak isomorphisms by \cite[Lemmas 3.5 and 3.6]{Schmahl.2021}, and the same is true for the numbers of births and deaths $\alpha(t)$ and $\omega(t)$ because they are defined through persistence diagrams, which themselves are invariant under weak isomorphisms.
+	Hence, using the fact that the inclusion $\rad M \hookrightarrow M$ is a weak isomorphism, we conclude that none of the quantities appearing in the statement change if we replace $M$ by its radical.
+	This radical admits a barcode decomposition and the claims follow from an explicit computation on the corresponding barcode module $M' = \bigoplus_{\lambda \in \Lambda} C(I_\lambda)$:
 
-Parts of the framework of functional topology that Morse and Tompkins use is developed by Morse in \cite{Morse.1940} in a very general setting.
-In particular, he proves inequalities for cap numbers associated to the persistent \v{C}ech homology of the sublevel set filtration, as also considered in \cref{s:inequalities}.
-From these generalized Morse inequalities, the existence of an unstable minimal surface can easily be deduced in the presence of two distinct critical sets of minimum type.
+	First, note that we have 
+	\[
+	    \dim \lim_{u > t} M'_{u} 
+	    = \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} \leq t,\ \sup I_{\lambda} > t \right\} 
+	    %= \sharp \{ \lambda \in \Lambda \mid \inf I_{\lambda} = t,\ \sup I_{\lambda} > t\}
+	    %+ \sharp \{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} > t\}
+	\]
+	if one side of the equation is finite, and we also have
+	\[
+	    \dim \colim_{s < t} M'_{s} 
+	    = \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} \geq t \right\}, 
+	    %= \sharp \{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} = t\}
+	    %+ \sharp \{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} > t\}
+	\]
+	as well as
+	\[
+	    \dim \im \left( \colim_{s < t} M'_{s} \to \lim_{u > t} M'_{u} \right)
+	    = \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} > t \right\}.
+	\]
+	From this, if again one side of the equation is finite, we obtain
+	\begin{align*}
+	    \alpha(t) &= \sum_{q \in (t, \infty]} \m(t,q) \\
+	              &= \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} = t,\ \sup I_{\lambda} > t \right\} \\
+	              &= \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} \leq t,\ \sup I_{\lambda} > t \right\}
+	              -  \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} > t \right\} \\
+	              &= \dim \lim_{u > t} M'_{u} - \dim \im \left( \colim_{s < t} M'_{s} \to \lim_{u > t} M'_{u} \right) \\
+	              &= \dim \coker \left( \colim_{s < t} M'_{s} \to \lim_{u > t} M'_{u} \right)
+	\end{align*}
+	and we also obtain
+	\begin{align*}
+	    \omega(t) &= \sum_{p \in [-\infty, t)} \m(p,t) \\
+	              &= \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} = t \right\} \\
+	              &= \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} \geq t \right\}
+	              -  \sharp \left\{ \lambda \in \Lambda \mid \inf I_{\lambda} < t,\ \sup I_{\lambda} > t \right\} \\
+	              &= \dim \colim_{s < t} M'_{s} - \dim \im \left( \colim_{s < t} M'_{s} \to \lim_{u > t} M'_{u} \right) \\
+	              &= \dim \ker \left( \colim_{s < t} M'_{s} \to \lim_{u > t} M'_{u} \right).
+	              \qedhere
+	\end{align*}
+\end{proof}
 
-We have seen that these inequalities require q-tameness, so in order to apply them in the minimal surface setting % and deduce their theorem,
-one needs to prove the \mbox{q-tameness} of the sublevel set filtration of the Douglas functional $A_g$.
-Throughout his work on functional topology, in order to obtain \mbox{q-tameness}, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations.
-In particular, Morse and Tompkins used the following condition in their applications to minimal surface theory (see also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain typographical errors):
+If $M$ is continuous from below or above, then the colimits and limits appearing in the formulas above may simply be replaced by the constituent vector spaces of~$M$.
+As a special case, this yields the following corollary.
+
+\begin{cor}
+\label{cor:regular_value_no_endpoint}
+	Let $M$ be a q-tame persistence module.
+	If $M$ is continuous from above and below at $t$, we have
+	\[
+		\alpha(t) = \omega(t) = 0.
+	\]
+\end{cor}
+
+We now return to the setting of functions $F$ on metric spaces and prove some more lemmas.
+To emphasize which persistence-theoretic notions are relevant, we will work with a general homology theory $\H$ such that $\H(F_{\leq \bullet})$ has certain properties, stated in the lemmas. 
+In all cases, \v{C}ech homology as used in \cref{thm:mountain_pass} satisfies the necessary conditions.
+We start with a first result stating that, as in the case of smooth Morse theory, the homotopy type of sublevel sets does not change leading up to regular values.
+
+\begin{lem}\label{lem:sublevel_set_homotopy}
+	Let $F \colon M \to \R$ be a weakly upper-reducible function a metric space with compact sublevel set filtration.
+	If $t \in \R$ is a regular value of $F$, then there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
+\end{lem}
+
+%\cref{lem:sublevel_set_homotopy} can be shown analogously to the argument in \cite[Remark II.6.3]{Struwe.1988}, where level sets of $F$ are assumed to be compact, but $F$ is not assumed to be weakly upper-reducible.
+A weaker version of \cref{lem:sublevel_set_homotopy} is stated in \cite[Lemma 8.1]{Morse.1938}, under the slightly stronger assumption of upper-reducibility.
+In \cite{Morse.1939}, Morse and Tompkins introduce and use \emph{weak} upper-reducibility, noting that the results and arguments from \cite[Sections 7 and 8]{Morse.1938} still apply.
+For convenience, we revisit the arguments using this setting in \cref{s:caps}, loosely following the exposition by Struwe \cite[Remark II.6.3]{Struwe.1988}.
+
+We proceed by showing that function values with non-vanishing \emph{cap numbers} $c_d(t) \defeq \alpha_d(t) + \omega_{d-1}(t)$, for any $d$, are indeed critical values.
+This corresponds to \cite[Theorem 8.1]{Morse.1938}.
+Note that the definition of cap numbers used by Morse is phrased in terms of relative homology, differing from our definition in terms of absolute homology.
+The equivalence of both definition is shown in \cref{prop:cap_limits}.
+
+\begin{lem}
+\label{lem:endpoint_implies_crit_pt}
+	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration.
+	Assume that $\H(F_{\leq \bullet})$ is q-tame and continuous from above, and consider $t \in \R$ and its birth and death numbers $\alpha_d(t)$ and $\omega_{d-1}(t)$.
+	If $\alpha_d(t) > 0$ or $\omega_{d-1}(t) > 0$, then $t$ is a critical value of $F$.
+\end{lem}
+\begin{proof}
+	Following \cref{lem:sublevel_set_homotopy}, we know that if $t$ is a regular value, there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
+	Thus, $\H(F_{\leq \bullet})$ is continuous from below at every regular value.
+	However, we assume $\H(F_{\leq \bullet})$ to be also continuous from above at every value, and in particular at regular values.
+	Hence, \cref{cor:regular_value_no_endpoint} implies that $\alpha_d(t) = \omega_{d-1}(t) = 0$ whenever $t$ is regular, which proves the claim.
+\end{proof}
+
+%\begin{lem}
+%\label{lem:minimum_type_implies_summand}
+%	Let $F \colon M \to \R$ be a function on a metric space and let $S$ be a critical set with value $t$.
+%	If $S$ is of minimum type, then it is a topological summand of $F_{\leq t}$ in the sense that $F_{\leq t}$ is homeomorphic to the disjoint union $S \sqcup (F_{\leq t} \setminus S)$.
+%\end{lem}
+%\begin{proof}
+%	By definition, there exists a neighborhood $N$ of $\overline{S}$ in $M$ such that the function values of $F$ on $N \setminus S$ exceed $t$.
+%	In particular, we have $F_{\leq t} \cap N = S$, showing that $S$ is open in $F_{\leq t}$.
+%	Because $N$ contains $\overline{S}$, we also obtain $F_{\leq t} \cap \overline{S} = S$, showing that $S$ is closed in $F_{\leq t}$.
+%	This proves the claim.
+%\end{proof}
+
+%In particular, \cref{lem:minimum_type_implies_summand} implies that a critical set of minimum type can only give birth to new features in the persistence diagram and not kill existing ones, provided that the homology theory being used is additive.
+
+Next, we will analyze how the homology of sublevel sets changes at function values of critical sets of minimum type.
+
+\begin{lem}
+\label{lem:minimum_type_implies_some_birth_and_no_death}
+	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration and let $S$ be a critical set of minimum type with value $t$.
+	Assume that~$\H$~is additive and that $\H(F_{\leq \bullet})$ is q-tame and continuous from above.
+	\begin{enumerate}
+		\item The number of births at $t$ satisfies $\alpha_d(t) \geq \dim \H_d(S)$.
+		\item If there are no homotopically critical points with value $t$ outside $S$, then the number of deaths at $t$ satisfies $\omega_d(t) = 0$ for all $d$.
+	\end{enumerate}
+\end{lem}
+\begin{proof}
+	We start by showing that $S$ is a topological summand of $F_{\leq t}$ in the sense that $F_{\leq t}$ is homeomorphic to the disjoint union $S \sqcup (F_{\leq t} \setminus S)$.
+	It suffices to show that $S$ is open and closed in $F_{\leq t}$.
+	By definition, there exists a neighborhood $N$ of $\overline{S}$ in $M$ such that the function values of $F$ on $N \setminus S$ exceed $t$.
+	In particular, we have $F_{\leq t} \cap N = S$, showing that $S$ is open in $F_{\leq t}$.
+	Because $N$ contains $\overline{S}$, we also obtain $F_{\leq t} \cap \overline{S} = S$, showing that $S$ is closed in $F_{\leq t}$.
+
+	Using additivity of $\H$ and \cref{lem:birth_death_formulas}, we now obtain
+	\begin{align*}
+		\alpha_d(t) &= \dim \coker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \lim_{u > t} \H_d(F_{\leq u}) \big) \\
+			&= \dim \coker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \H_d(F_{\leq t}) \big) \\
+			&= \dim \coker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \H_d(F_{\leq t} \setminus S) \oplus \H_d(S) \big) \\
+			&\geq \dim \H_d(S),
+	\end{align*}
+	where we have used the assumption that $\H(F_{\leq \bullet})$ is continuous from above for the second equality and the fact that $F_{\leq s} \subseteq (F_{\leq t} \setminus S)$ for all $s < t$ for the final inequality.
+
+	Now, assume that $S$ is the set of all homotopically critical points of $F$ with value~$t$ and consider the restriction of $F$ to $F_{\leq t} \setminus S$, denoted by $G$.
+	The set $F_{\leq t} \setminus S$ is compact because $F_{\leq t}$ is compact and $S$ is open in $F_{\leq t}$, so the sublevel set filtration of $G$ is compact.
+	$G$ is also weakly upper-reducible because the same is true for $F$.
+	Moreover, any homotopically critical point of $G$ is a homotopically critical point of $F$, so our assumption that $S$ is the set of all homotopically critical points with value $t$ of $F$ implies that $t$ is a regular value for $G$.
+	By \cref{lem:sublevel_set_homotopy},  this implies that there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} = G_{\leq s} \hookrightarrow G_{\leq t} = (F_{\leq t} \setminus S)$ is a homotopy equivalence for for all $s \in (t - \epsilon, t]$
+	Hence, again using additivity of $\H$, continuity from above, and \cref{lem:birth_death_formulas}, we obtain that
+	\begin{align*}
+		\omega_d(t) &= \dim \ker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \lim_{u > t} \H_d(F_{\leq u}) \big) \\
+				&= \dim \ker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \H_d(F_{\leq t}) \big) \\
+				&= \dim \ker \big( \colim_{s < t} \H_d(F_{\leq s}) \to \colim_{s < t} H_d(F_{\leq s}) \oplus \H_d(S) \big) \\
+				&= 0
+	\end{align*}
+	as claimed.
+\end{proof}
+
+As the last preparatory result, we will show that connectedness of $M$ together with the condition on the colimit of the persistent homology of $F$ in the setting of \cref{thm:mountain_pass} imply that the $0$-th essential dimension is trivial for \v{C}ech homology.
+
+\begin{lem}
+\label{lem:essential_cech_dim}
+	Let $F \colon M \to \R$ be a function on a connected non-empty metric space with compact sublevel set filtration such that the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism and $\CH_0(F_{\leq \bullet})$ is q-tame.
+	Then the essential dimension of $\CH_0(F_{\leq \bullet})$ satisfies $\cp_{0} = 1$.
+\end{lem}
+\begin{proof}
+	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
+	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so $\dim \CH_0(M) = 1$.
+	Together with our assumption on the colimit, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
+\end{proof}
+
+\begin{rem}
+%    \todo{should we move the rest of this remark to after \cref{lem:essential_cech_dim}?}
+    Note that $\cp_0 = 1$ does not already follow from just $M$ being connected, i.e., the assumption $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is non-vacuous:
+	For the lower semi-continuous function $F \colon [0,1] \to \R$ defined as $F(0) = 0$ and $F(t) = \frac1t$ for $t > 0$, we have for $t > 0$ that $F_{\leq t} = \{0\} \cup [\frac1t, 1]$.
+	%where $\frac1t$ goes monotonically to 0 as $t \to \infty$.
+	Hence, we get $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = 2$ despite $M$ being contractible and the sublevel sets of $F$ being compact. %\todo{Is $F$ weakly upper-reducible?}
+%	\todo{maybe make it more clear what the function values at the endpoints of the intervals are}
+%	\begin{figure}
+%    \centering
+%    \begin{tikzpicture}[scale = 10]
+%		\clip (-.005,-.005) rectangle (1.1,.501);
+%		\draw[lightgray] (0,0) -- (0,.5);
+%		\draw[lightgray] (0,0) -- (1,0);
+%		\foreach \i in {0,...,10}{
+%			 \draw[line width=.5pt] (1/2^\i, \i/20) -- (2/2^\i, \i/20);
+%		}
+%		\draw[fill] (0,0) circle (0.003);
+%	\end{tikzpicture}
+%    \caption{Caption\todo{Needs a caption}}
+%    \label{fig:step_function}
+%    \end{figure}
+
+    %The weak upper-reducibility condition does not have an analogue in the assumptions of \cref{thm:mountain_pass}. 
+    %This is interesting insofar as establishing that the Douglas functional satisfies this condition takes up a large part of \cite{Morse.1939}, and Courant \cite{Courant.1941} emphasizes that establishing weak upper-reducibility is one of the key difficulties in the proof of Morse and Tompkins, requiring ``a rather deep explicit analysis of the functional''.
+
+    %One can check that the example given in \cref{rem:critical_set} also satisfies the conditions that Morse and Tompkins impose for their Mountain Pass Theorem.
+
+    %Weak upper-reducibility (WUR) is not used in our paper. Is it really unnecessary or do we miss something?
+
+    %In the functional topology monograph, Morse states that WUR implies that every cap limit is assumed by a homotopically critical point.
+We do this without WUR in Lemma 5.8, but assume that the persistence module is continuous from above.
+
+    %WUR is not used in rank and span paper.
+Morse says that this paper is not concerned with critical points.
+Morse states in the same paper that the map $H(f_{\leq t}) \to lim_{u > t} H(f_{\leq u})$ is injective, but in fact it is also surjective, so that we have continuity from above.
+Maybe he is unaware that this is a general fact and wants to use WUR to circumvent this.
+
+    %Note that Courant says WUR is key in https://www.pnas.org/doi/pdf/10.1073/pnas.27.1.51 and establishing WUR makes up a large part of the Morse-Tompkins paper, so getting rid of this assumption actually simplifies things quite a bit.
+
+    %WUR also seems to be satisfied in our example that establishes the necessity of modifying the definition of minimum type, so WUR also does not seem to rectify this issue.
+
+    %Apparently we did indeed miss something! Our argument without WUR relies on an argument by Struwe that seems to be incomplete and only works in general if WUR is also assumed.
+\end{rem}
+
+We are now ready to give a proof of the Mountain Pass Theorem.
+
+\begin{proof}[Proof of \cref{thm:mountain_pass}]
+    First, we observe that $\CH_*(F_{\leq \bullet})$ is q-tame by \cref{t:local connectedness implies q-tameness} because we assume that $F_{\leq \bullet}$ is $\HLC$ for \v{C}ech homology.
+    As a consequence, $\CH_*(F_{\leq \bullet})$ has a well-defined persistence diagram by \cref{t:q-tame modules have barcodes}, and thus we can consider cap numbers, births, deaths, etc.
+    We write $\cc_d$, $\calpha_d$, $\comega_d$, and $\cp_d$ for the cap numbers, births, deaths, and essential dimensions of $\CH_d(F_{\leq \bullet})$, respectively.
+    The sublevel set filtration of $F_{\leq \bullet}$ is also assumed to be compact, $M$ is assumed to be connected and non-empty, $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is assumed to be an isomorphism, and $F$ is assumed to be weakly upper-reducible, so the previous lemmas are all applicable.
+
+	Now assume that $F$ has two distinct critical sets $S_{1}$ and $S_{2}$ of minimum type with values $t_{1}$ and $t_{2}$, respectively.
+	Since both critical sets are non-empty, we have $\CH_{0}(S_{i}) \neq 0$, and thus the first assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death} implies $\calpha_{0}(t_{i}) \geq \dim \CH_0(S_{i}) \geq 1$ for $i = 1,2$,
+	indicating the existence of at least one feature for each $i = 1,2$ with birth $t_{i}$ and some positive persistence $\epsilon_i > 0$ in the persistence diagram of $\CH_0(F_{\leq \bullet})$.
+	Choosing $0 < \epsilon < \min_i \epsilon_i$, this implies that
+	$\calpha_{0}^{\epsilon}(t_{i}) \geq 1$ for $i = 1,2$,
+	and thus
+	$\cc_{0}^{\epsilon} \geq \calpha_{0}^{\epsilon}(t_{1}) + \calpha_{0}^{\epsilon}(t_{2}) \geq 1 + 1 = 2$.
+	Now, from \cref{lem:essential_cech_dim} we obtain that $\cp_{0} = 1$, which yields $\comega_{0}^{\epsilon} = \cc_{0}^{\epsilon} - \cp_{0} \geq 2 - 1 = 1$.
+	Thus, there must be some $t \in \R$ with $\comega_{0}(t) > 0$, so that we may apply \cref{lem:endpoint_implies_crit_pt} to obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
+	If $S$ were of minimum type, then we would have $\comega_{0}(t) = 0$ by the second assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death}, contradicting the choice of $t$.
+	Hence, $S$ cannot be of minimum type, which finishes the proof.
+\end{proof}
+
+\subsection{Morse's local connectivity conditions}\label{subsec:historic_hlc}
+In order to complete the proof of the Unstable Minimal Surface Theorem, we explain why the Douglas functional is q-tame for \v{C}ech homology (\cref{prop:douglas_hlc}), and we discuss the issue with Morse's approach to q-tameness in \cite[Theorem 6.3]{Morse.1940}.
+
+Throughout his work on functional topology, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations in order to obtain \mbox{q-tameness}.
+In particular, Morse and Tompkins used the following condition from \cite{Morse.1938,Morse.1940} in their application to minimal surface theory:
 \begin{displaycquote}[p.~431]{Morse.1940}
@@
 \end{displaycquote}
-Using similar language to the one used in \cref{s:connectivity}, the property of local $F$-connectedness of all orders is equivalent to the following notion applicable to general topological spaces.
+See also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain evident typographical errors.
+Expressed in similar language as \cref{s:connectivity}, the property of local $F$-connectedness of all orders is equivalent to the following notion, applicable to general topological spaces.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly homotopically locally connected}, or \emph{weakly $\piLC$}, if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ induces trivial maps on homotopy groups.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected of all orders}, or \emph{weakly $\piLC$}, if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ induces trivial maps on all homotopy groups.
 \end{defi}
@@
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally connected} or \emph{weakly $\LC$} if for any $x \in X$, $V$ a neighborhood of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{weakly locally contractible}, or \emph{weakly $\LC$}, if for any $x \in X$, any neighborhood $V$ of $x$, and any index $t > f(x)$, there is an index $s$ with $f(x) < s < t$ and a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
@@
 Clearly, being weakly $\LC$ implies being weakly $\piLC$ and, if the homology $\H$ takes finite dimensional values on one-point spaces, also weakly $\HLC$.
-Observe that \cref{e:counterexample} actually establishes that the filtration given there is weakly $\LC$, so not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions in general.
-In particular, our construction invalidates Morse's claim quoted above because \v{C}ech homology satisfies the assumptions on the homology theory made in \cref{e:counterexample}.
-
-Specifically, using the the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
+Observe that our discussion in \cref{e:counterexample} actually establishes that the filtration given there is weakly $\LC$, so not even the weak $\LC$ condition is sufficient to ensure the q-tameness of compact sublevel set filtrations that are induced by non-continuous functions in general.
+In particular, our construction invalidates Morse's claim quoted above:
+% because \v{C}ech homology satisfies the assumptions on the homology theory made in \cref{e:counterexample}. %mentioned beofre already
+%
+%Specifically, using the fact that \v{C}ech homology of compact Hausdorff spaces commutes with inverse limits, it is straightforward to verify that the \v{C}ech homology in degree $d$ of the $d$-dimensional Hawaiian earring $\HE$ is isomorphic to $\prod_{n\in\N}\F$, which is infinite dimensional over $\F$.
 %To see that his is the case, one can use the fact that \v{C}ech homology commutes with totally ordered limits for compact Hausdorff spaces \cite[Theorems VIII.3.6 and X.3.1]{Eilenberg.1952} as follows.
@@
 %	In order to verify that the sublevel set filtration of $f$ is weakly $\LC$, we
-%	consider $x \in \HE$, $V$ a neighborhood of $x$ in $\HE$ and $t > f(x)$.
-We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+%	consider $x \in \HE$, any neighborhood $V$ of $x$ in $\HE$ and $t > f(x)$.
+%We need to find a neighborhood $U \subseteq V$ of $x$ and $s \in (f(x), t)$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to a constant map.
 %
 %	If $x$ is the origin, we have $f(x) = 0$ and choose $s \in (0, \min\{t, 1\})$.
-%	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\LC$ condition is trivially satisfied.
+%	Then $f_{\leq s} = \{x\}$, so with $U = V$ the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is the inclusion of $\{x\}$ into $f_{\leq t} \cap V$, which is a constant map, so the weak $\LC$ condition is trivially satisfied.
 %
@@
 %	Clearly, we may choose $\delta > 0$ so small that $B_{\delta}(x) = \{y \in \R^{d+1} \mid \Vert x - y \Vert < \delta\} \cap \HE$ is a topological ball contained in this sphere and contained in $V$.
-%	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
+%	The ball $B_\delta(x)$ can be contracted to $\{x\}$ in $V$, so choosing $U = B_{\delta}(x)$, we obtain that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to the constant map with value $x$.
 %
@@
 %\end{proof}
-Moreover, the singular homology of the $d$-dimensional Hawaiian earring is also infinite dimensional, as proven in \cite{Barratt.1962}. In summary, we have the following.
+%Moreover, the singular homology of $\HE$ is also infinite dimensional, as proven in \cite{Barratt.1962}.
+%In summary, we have the following.
 
 \begin{cor} \label{c:counterexample}
-	The function $f \colon \HE \to \R$ with value~$0$ at the origin and $1$ elsewhere defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to singular and \v{C}ech homology.
+	The function $f \colon \HE \to \R$ with value~$0$ at the origin and $1$ elsewhere defines a weakly $\LC$ compact sublevel set filtration that is not q-tame with respect to either singular or \v{C}ech homology.
 \end{cor}
 
-The gap we have thus highlighted in the argument of Morse and Tompkins, that the sublevel set filtration of $A_g$ is not necessarily q-tame, can be fixed by applying \cref{t:local connectedness implies q-tameness}.
-This is because the proof given in \cite[p.464]{Morse.1939} for the local connectivity of the sublevel set filtration induced by $A_g$ can actually be seen to establish a stronger property described next.
+This counterexample reveals a gap in the argument of Morse and Tompkins, as the sublevel set filtration of $A_g$ is not actually shown to be q-tame.
+Fortunately, this gap can be readily fixed by applying \cref{t:local connectedness implies q-tameness}.
+This is because the proof given in \cite[Theorem 7.2, p.464]{Morse.1939} for the local connectivity of the sublevel set filtration induced by $A_g$ can actually be seen to establish a stronger property, described next.
 
 \begin{defi}
-	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally connected} $\LC$ if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the map $f_{\leq s} \cap U \to f_{\leq t} \cap V$ is homotopic to a constant map.
+	The sublevel set filtration of a function $f \colon X \to \R$ is said to be \emph{locally contractible} or \emph{$\LC$} if for any $x \in X$, any neighborhood $V$ of $x$ and any pair of indices $f(x) < s < t$ there is a neighborhood $U \subseteq V$ of $x$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is homotopic to a constant map.
 \end{defi}
 
-Clearly, the filtration being $\LC$ implies that the filtration is also $\HLC$ for \v{C}ech homology with field coefficients, which is the homology theory Morse and Tompkins use.
-Therefore, from \cref{t:local connectedness implies q-tameness} we can conclude that the sublevel set filtration of $A_g$ is indeed \mbox{q-tame} as needed.
-This implies that the generalized Morse inequalities hold, and hence so does the Unstable Minimal Surfaces Theorem.
+\begin{prop}[{\cite[p.464]{Morse.1939}}]
+\label{prop:douglas_hlc}
+    The sublevel set filtration of the Douglas functional $A_g \colon \Omega_g \to \R$ is $\LC$, and in particular $\HLC$ for \v{C}ech homology.
+\end{prop}
+%
+%Using the fact that $\LC$ implies $\HLC$, an application of \cref{t:local connectedness implies q-tameness} yields:
+%\begin{cor}
+%\label{c:douglas_qtame}
+%	The Douglas functional $A_g$ has q-tame persistent \v{C}ech homology.
+%\end{cor}
 
-We have also mentioned that Morse introduced another condition that he also called local $F$-connectivity three years earlier.
+We can now finally prove the Unstable Minimal Surface Theorem.
+
+\begin{proof}[Proof of \cref{thm:unstable_minimial_surface}]
+    The Douglas functional $A_g$ is weakly upper-reducible by \cite[Theorem 5.1]{Morse.1939}, its sublevel set filtration is compact according to \cite[p.~448]{Morse.1939}, and as previously mentioned $\Omega_g$ is non-empty by \cite[p.~267-268]{Douglas.1931} because $g$ is rectifiable.
+    Moreover, $\Omega_g$ is contractible and hence connected by \cite[Theorem 4.3]{Morse.1939}.
+    The sublevel set filtration of $A_g$ is also $\HLC$ for \v{C}ech homology according to \cref{prop:douglas_hlc}.
+    Finally, we have $\colim \CH_0((A_g)_{\bullet}) \to \CH_0(\Omega_g)$ is an isomorphism according to \cite[p.~444]{Morse.1939} because $A_g$ satisfies the \emph{regularity at infinity} condition by \cite[Theorem 4.3]{Morse.1939}.
+    In total, \cref{thm:mountain_pass} applies to $A_g$.
+    Since any homotopically critical point of $A_g$ corresponds to a minimal surface spanned by $g$ \cite[Theorem 6.2]{Morse.1939}, this implies the claim. 
+\end{proof}
+
+\begin{rem}
+Morse introduced another condition three years earlier, which he also called local $F$-connectivity.
 It roughly corresponds to being $\piLC$ with a certain added uniformity property.
@@
 We expect the quoted claim to be true, but do not investigate it further.
+\end{rem}

### 2022-07-13 sec/vietoris.tex
Enforce basic code conventions
after second ref

@@
 
-\section{Vietoris and \texorpdfstring{\v{C}}{}ech homology} \label{s:vietoris}
+\section{Vietoris and \texorpdfstring{\v{C}}{}ech homology for compact metric spaces} \label{s:vietoris}
 
-For greater generality, in this paper we considered \v{C}ech homology instead of the homology construction used by Morse in functional topology: metric Vietoris homology.
-We now justify this choice by reminding the reader that these two constructions agree on compact metric spaces following \cite{Dowker.1952}.
-For an earlier approach, the reader may also wish to consult \cite[Section VII.6]{Lefschetz.1942}.
+For greater generality, in this paper we consider \v{C}ech homology instead of the homology construction used by Morse in functional topology: metric Vietoris homology.
+We now justify this choice by reminding the reader that these two constructions agree on \emph{compact} metric spaces.
+We follow \cite{Dowker.1952} in our discussion; for an earlier approach, the reader may also consult \cite[Section VII.6]{Lefschetz.1942}.
 
@@
 \Nrv(\alpha) =
-\big\{ \beta \subseteq \alpha \mid \beta \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}.
+\big\{ \beta \subseteq \alpha \mid \beta \neq \emptyset \text{ is finite and } \textstyle{\bigcap_{U \in \beta}} \, U \neq \emptyset \big\}.
 \end{equation*}
@@
 \begin{equation*}
-\Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \text{ is finite and } \sigma \in U \text{ for some } U \in \alpha \right\}.
+\Vietoris (\alpha) = \left\{ \sigma \subseteq X \mid \sigma \neq \emptyset \text{ is finite and } \sigma \subseteq U \text{ for some } U \in \alpha \right\}.
 \end{equation*}
@@
 \end{equation*}
-In other words, for compact metric spaces the metric Vietoris homology theory employed in Morse's setting is isomorphic to the \v{C}ech homology we consider in this paper.
+In other words, for compact metric spaces the metric Vietoris homology theory employed in Morse's setting is isomorphic to the \v{C}ech homology considered in this paper.
 Note that the relevant isomorphisms above can all be seen to be natural with respect to continuous maps (see in particular \cite[Lemma 7a]{Dowker.1952}), so that in particular both homology constructions yield the same persistence modules when applied to sublevel set filtrations.
+In the setting of compact metric spaces, the well-known defect of \v{C}ech homology not having long exact sequences for pairs of spaces also disappears if one uses field coefficients, which is necessary anyway to get persistence diagrams.

### 2022-10-12 sec/caps.tex
Remove double blank spaces
before referee 3

@@
 First, in \cite[Theorem 8.1]{Morse.1938} it is assumed that $F$ is not only weakly upper-reducible but upper-reducible.
-Second, $t$ is not required to satisfy $c(t) > 0$, but required to be a \emph{cap limit}, meaning that $\colim_{s: s < t} \CH_*(F_{\leq t}, F_{\leq s}) \neq 0$ \cite[p.~12]{Morse.1938}.
+Second, $t$ is not required to satisfy $c(t) > 0$, but required to be a \emph{cap limit}, meaning that $\colim_{s: s < t} \CH(F_{\leq t}, F_{\leq s}) \neq 0$ \cite[p.~12]{Morse.1938}.
 Regarding the second point, it turns out that the two requirements are equivalent.
@@
 \begin{prop}\label{prop:cap_limits}
-	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration.
+	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration and fix $t \in \R$.
 	Assume that $\H$ has long exact sequences for pairs of compact spaces, and that $\H_*(F_{\leq \bullet})$ is q-tame and continuous from above.
@@
 	\end{align*}
-    where we have in both cases used the fact that taking filtered colimits of vector spaces is exact, and where the first equalities hold in case both sides of the equation are finite because of \cref{lem:birth_death_formulas} and the fact that $\H_*(F_{\leq \bullet})$ is continuous from above.
+	where we have in both cases used the fact that taking filtered colimits of vector spaces is exact, and where the first equalities hold in case both sides of the equation are finite because of \cref{lem:birth_death_formulas} and the fact that $\H(F_{\leq \bullet})$ is continuous from above.
 	Since $c_d(t) = \alpha_d(t) + \omega_{d-1}(t)$, this finishes the proof.
@@
 \begin{rem}
-	\cref{prop:cap_limits} only references cap limits, i.e., levels $t$ for which the \emph{cap space} $\colim_{s: s < t} \H_*(F_{\leq t}, F_{\leq s})$ is non-zero.
+	\cref{prop:cap_limits} only references cap limits, i.e., levels $t$ for which the \emph{cap space} $\colim_{s: s < t} \H_{d}(F_{\leq t}, F_{\leq s})$ is non-zero.
 	However, Morse not only considers these cap spaces on their own, but he also defines the \emph{span} of a cap, and considers the space of caps with span greater than some $\epsilon > 0$, see for example \cite[Section 11]{Morse.1940}.
-	Using slight generalizations of the arguments proving \cref{prop:cap_limits,lem:birth_death_formulas}, one can show that the dimensions of these spaces agree with $c^{\epsilon}(t)$.
+	Using slight generalizations of the arguments proving \cref{prop:cap_limits,lem:birth_death_formulas}, one can show that the dimensions of these spaces agree with $c_{d}^{\epsilon}(t)$.
 	We already mentioned this when talking about Morse inequalities, which Morse originally formulated for dimensions of such cap spaces.
@@
 Note that the assumptions of \cref{prop:cap_limits} are in particular satisfied for \v{C}ech homology with field coefficients and a function $F$ whose sublevel set filtration is $\HLC$ with respect to this homology theory.
-Regarding the first difference we mentioned between our approach and the one from \cite[Theorem 8.1]{Morse.1938} with respect to upper-reducibility, we will now sketch that this is not an issue.
+Regarding the first difference we mentioned between our approach and the one from \cite[Theorem 8.1]{Morse.1938} with respect to upper-reducibility, we will now show that this is not an issue.
 That is, we will give an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
@@
 		\item $\varphi_{p}(\cdot,0) = \operatorname{id}$,
-		\item for all $V \subseteq B_{\delta_{p}}(p)$ compact there exists $\epsilon(p,V) > 0$ with 
+		\item for all compact $V \subseteq B_{\delta_{p}}(p)$ there exists $\epsilon(p,V) > 0$ with
 		\begin{enumerate}
@@
 	\end{enumerate}
-	For $p$ with $F(p) = t$ the existence of such $\delta_{p}$ and $\varphi_{p}$ is guaranteed by the assumption that $t$ is a regular value and hence $p$ is homotopically regular,
-	and for $p$ with $F(p) < t$ it is guaranteed by the assumption that $F$ is weakly upper-reducible.
+	For $p$ with $F(p) < t$ the existence of such $\delta_{p}$ and $\varphi_{p}$ is guaranteed by the assumption that $F$ is weakly upper-reducible.
+	For $p$ with $F(p) = t$ it follows from the assumption that $t$ is a regular value and hence $p$ is homotopically regular, by the following argument.
+
+	If $p$ is homotopically regular, there exists a neighborhood $U$ of $p$ in $F_{\leq t}$ and a continuous map $\varphi \colon U \times [0,1] \to M$ such that $\varphi(\cdot,0) = \operatorname{id}_{U}$, $\varphi(p,1) \neq p$, and such that on every compact set $V \subseteq U$ there exists a displacement function for $\varphi$ and~$F$.
+	It is clear that $\varphi(V \cap F_{\leq s} \times [0,1]) \subseteq F_{\leq s}$ for all $s \leq t$ and $V \subseteq U$ compact since there exists a displacement function and hence the values of $F$ can not increase along trajectories of $\varphi$.
+	It remains to be checked that we can shrink $U$ enough such that for all compact $V \subseteq U$ there is $\epsilon(p,V)$ with $\varphi(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$.
+	Assume for a contradiction that for all neighborhoods $W \subseteq U$ there exists a compact $V \subseteq W$ such that for all $\epsilon > 0$ there is some $q \in V$ with $t \geq F(q) \geq F(\varphi(q,1)) > t - \epsilon$, where we note that $F(q) \geq F(\varphi(q,1))$ is a consequence of the existence of a displacement function on~$V$.
+	It follows that there exists a sequence $(q_{n})_{n}$ in $F_{\leq t}$ with $F(q_{n}) \to t$ and $q_{n} \to p$ for $n \to \infty$.
+	Since $\varphi$ is continuous we have that $\varphi(q_{n},1)$ converges to $\varphi(p,1)$, which is different from $p$ by the choice of $\varphi$, so there can be no infinite subsequence of $(q_{n})_{n}$ consisting of fixed points for $\varphi(\cdot,1)$.
+	Without loss of generality, we can thus assume that $\varphi(q_{n},1) \neq q_{n}$ for all $n$.
+	Now consider the compact set $K = \{q_{n} \mid n \in \N \} \cup \{p\}$.
+	By assumption, we can choose a continuous displacement function $\delta$ on $K$.
+	Since $K$ is compact, $\varphi$ is continuous, $\delta$ is continuous, and $\varphi(\cdot,1)$ has no fixed points in $K$, the function $x \mapsto \delta(d(x,\varphi(x,1)))$ attains a minimum $\epsilon > 0$ on $K$.
+	We get $F(x) - t \geq F(x) - F(\varphi(x,1)) \geq \epsilon > 0$ for all $x \in K$, which contradicts the fact that $F(q_{n}) \to t$ for $n \to \infty$.
+	This proves the claim.
+
 	Because $F_{\leq t}$ is compact, we can now choose finitely many points $p_{1}, \dots, p_{n}$ such that $F_{\leq t}$ is covered by $( B_{\frac{\delta_{p_{i}}}{3}}(p_{i}))_{i}$, and we set
@@
 	\end{enumerate}
-	This shows that, indeed, the inclusions $F_{\leq s} \hookrightarrow F_{\leq t}$ are homotopy equivalences for $s \in (t - \epsilon, t]$, with homotopy inverses given by $\varphi$.
+	This shows that, indeed, for $s \in (t - \epsilon, t]$ the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence, with homotopy inverse given by $\varphi$.
 \end{proof}

### 2022-10-12 sec/connectivity.tex
Remove double blank spaces
before referee 3

@@
 
-\begin{defi}
+\begin{defi}\label{defi:LHS}
 	The sublevel set filtration of a function $f \colon X \to \R$ is called \emph{locally homologically small} or \emph{$\HLC$} if for any $x \in X$, any neighborhood $V$ of $x$, and any pair of indices $s,t$ with $f(x) < s < t$ there is a neighborhood $U$ of $x$ with $U \subseteq V$ such that the inclusion $f_{\leq s} \cap U \hookrightarrow f_{\leq t} \cap V$ is $\HS$.
@@
 
-	Next, we will show using the $\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
+	First, we will show using the $\HLC$ property that $\Sigma_{s, t}$ has the first required property, i.e., that any point $x \in L \cap f_{\leq s}$ has a neighborhood in $\Sigma_{s, t}$.
 	Choose an arbitrary $s' \in (s,\, t)$.
@@
 
-	Finally, using the Mayer--Vietoris property and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
+	Next, using the Mayer--Vietoris property and the induction hypothesis we will show that $\Sigma_{s,t}$ has the second required property, i.e., that it is closed under finite unions.
 	So for $i \in \{1, 2\}$ let $V_i \in \Sigma_{s,t}$ with $U_i$ and $s'_i \in (s,\, t)$ such that

### 2022-10-12 sec/introduction.tex
before referee 3

@@
 The persistence module associated to a filtration depends on the homology construction used, which, even when agreeing on cellular spaces, need not coincide for general topological spaces.
-We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open or closed sets, the primary examples being singular homology or \v{C}ech homology, respectively.
+We restrict attention to homotopy invariant functors to the category of graded vector spaces satisfying the Mayer--Vietoris property for either open or closed sets, the primary examples being singular homology and \v{C}ech homology, respectively.
 

### 2022-10-12 sec/surfaces.tex
Remove double blank spaces
before referee 3

@@
 Having established topological conditions for the existence of persistence diagrams associated to filtrations and corresponding generalized Morse inequalities, we now describe how these results relate to Morse's general theory of functional topology \cite{Morse.1937, Morse.1938, Morse.1940}, and to its application in Morse and Tompkins' work on unstable minimal surfaces from \cite{Morse.1939}.
-We will focus on the homological aspects of this approach, referring to \cite[Sections 4.3--5]{Bott.1980} for a general exposition.
-For a more thorough presentation of the unstable minimal surface problem, including the analytical details see \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
+We focus on the connection of homological and homotopical aspects of this approach, referring to \cite[Sections 4.3--5]{Bott.1980} for a general exposition.
+For a more thorough presentation of the unstable minimal surface problem, including the analytical details, see \cite[Section II.6]{Struwe.1988}, and for a historical account and an overview of subsequent results see \cite[Section 6]{Dierkes.2010} and \cite[Section 6.8.1]{Dierkes.2010b}.
 
@@
 	Consider a real-valued function $F$ on a metric space $(M,d)$.
-	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(p,1) \neq p$, such that for every compact subset $V \subseteq U$ there exists a \emph{displacement function} $\delta \colon \R_{\geq 0} \to \R_{\geq 0}$ with
+	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(p,1) \neq p$, such that for every compact subset $V \subseteq U$ there exists a continuous \emph{displacement function} $\delta \colon \R_{\geq 0} \to \R_{\geq 0}$ with
 	$\delta(e) = 0$ if and only if $e = 0$, and
@@
 In \cite[p.~36]{Morse.1938}, the stronger notion of \emph{upper-reducibility}, without the prefix \emph{weakly}, is defined analogously to \cref{def:upper_reducible} with the slight difference that the existence of a displacement function is not only demanded for compact $V \subseteq U \cap F_{\geq c - \eta}$, but for all compact $V \subseteq U$.
+
 Morse and Tompkins state the following Mountain Pass Theorem under slightly different assumptions, and with a slightly different conclusion.
@@
 \begin{rem}\label{rem:critical_set}
-	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
+    Our \cref{def:critical_set} of homotopically regular point differs slightly from that of \citet[p.~30]{Morse.1938} and \citet[p.~444--445]{Morse.1939} as their displacement functions are not explicitly assumed to be continuous.
+    As used in the proof of \cref{lem:sublevel_set_homotopy}, we require this property to establish that a homotopically regular point with value $t$ admits a neighborhood $U$ and a homotopy $\varphi$ as in \cref{def:critical_set} such that for any compact $V \subseteq U$ there is $\epsilon > 0$ with $\varphi(V, 1) \subseteq F_{\leq t - \epsilon}$.
+    That such neighborhoods exist is claimed by Morse in the proof of \cite[Lemma~8.1]{Morse.1938}, where continuity of the displacement functions is not mentioned explicitly.
+    It is not clear to us whether the claim actually holds without continuity, or whether the assumption of continuity was made implicitly.
+    Regardless, all displacement functions considered by \citet{Morse.1939} and used for the purposes of this work are indeed continuous.
+
+	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} also differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
 	Without this additional assumption, however, \cref{thm:mountain_pass} does not hold, as shown by the example $F \colon [0,1] \to \R$ with $F(0) = F(1) = 0$ and $F(t) = 1$ for $0 < t < 1$:
@@
 	Regularity at infinity roughly corresponds to our assumption that $M$ is connected and the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism (see \cite[p.~444]{Morse.1939} and our proof of \cref{thm:unstable_minimial_surface}).
-    This assumption may also replaced by the assumption that $\cp_0 = 1$, which we deduce from our assumptions in \cref{lem:essential_cech_dim}.
+	This assumption may also be replaced by the assumption that $\cp_0 = 1$, which we deduce from our assumptions in \cref{lem:essential_cech_dim}.
 \end{rem}
@@
 	There is a single critical set $C = S^1 \times \{(0,0)\}$, which is of minimum type, but we still have $c_{1}^{\epsilon}(0) > 0$ for any $\epsilon > 0$ if $H$ is a homology theory such that $H_1(C) \neq 0$, e.g.\ singular or \v{C}ech homology.
-    To establish the existence of a critical set not of minimum type in the proof of \cref{thm:mountain_pass}, we will show that not only $c_{1}^{\epsilon}(t) > 0$, but that we indeed have $\omega_1^{\epsilon}(t) > 0$, i.e., that the positive cap number is created by the death of a feature.
+	To establish the existence of a critical set not of minimum type in the proof of \cref{thm:mountain_pass}, we will show that not only $c_{1}^{\epsilon}(t) > 0$, but that we indeed have $\omega_0^{\epsilon}(t) > 0$, i.e., that the positive cap number is created by the death of a feature.
 \end{rem}
@@
 	We mention that more general homology theories can be considered in \cref{thm:mountain_pass}.
-	The precise hypotheses on the homology theory $\H$ are that it is additive, taking non-zero values on non-empty sets in dimension $0$, and such that $\H(F_{\leq \bullet})$ is continuous from above, i.e., $\H(F_{\leq s}) \to \lim_{s < t} \H(F_{\leq t})$ is an isomorphism for all~$s \in \R$.
+	The precise hypotheses on the homology theory $\H$ are that it is additive, taking non-zero values on non-empty sets in dimension $0$, and such that $\H(F_{\leq \bullet})$ is continuous from above, i.e., $\H(F_{\leq t}) \to \lim_{u > t} \H(F_{\leq u})$ is an isomorphism for all~$t \in \R$.
 	One may also replace the topological conditions of $M$ being connected, the natural map $\colim \H_0(F_{\leq \bullet}) \to \H_0(M)$ being an isomorphism, and $F$ being $\HLC$ by the algebraic conditions that $p_0 = 1$ and $\H(F_{\leq \bullet})$ be q-tame.
@@
 
-While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable
+While more efficient and more general proofs for the existence of an unstable minimal surface (with respect to more natural topologies on $\Omega_{g}$ than $C^0$) have subsequently been established \cite{Struwe.1988,Dierkes.2010}, including less restrictive assumptions on the boundary curve, the original approach of Morse and Tompkins is notable
 % for its close connection to persistent homology.
@@
 This corresponds to \cite[Theorem 8.1]{Morse.1938}.
-Note that the definition of cap numbers used by Morse is phrased in terms of relative homology, differing from our definition in terms of absolute homology.
+Note that the definitions of cap numbers used by Morse is phrased in terms of relative homology, differing from our definition in terms of absolute homology.
 The equivalence of both definition is shown in \cref{prop:cap_limits}.
@@
 	Assume that $\H(F_{\leq \bullet})$ is q-tame and continuous from above, and consider $t \in \R$ and its birth and death numbers $\alpha_d(t)$ and $\omega_{d-1}(t)$.
-	If $\alpha_d(t) > 0$ or $\omega_{d-1}(t) > 0$, then $t$ is a critical value of $F$.
+	If $\alpha_d(t) > 0$ or $\omega_{d-1}(t) > 0$ for some degree $d$, then $t$ is a critical value of $F$.
 \end{lem}
@@
 	However, we assume $\H(F_{\leq \bullet})$ to be also continuous from above at every value, and in particular at regular values.
-	Hence, \cref{cor:regular_value_no_endpoint} implies that $\alpha_d(t) = \omega_{d-1}(t) = 0$ whenever $t$ is regular, which proves the claim.
+	Hence, \cref{cor:regular_value_no_endpoint} implies that $\alpha_d(t) = \omega_{d-1}(t) = 0$ for all $d$ whenever $t$ is regular, which proves the claim.
 \end{proof}
@@
 	\begin{enumerate}
-		\item The number of births at $t$ satisfies $\alpha_d(t) \geq \dim \H_d(S)$.
+		\item The number of births at $t$ satisfies $\alpha_d(t) \geq \dim \H_d(S)$ for all $d$.
 		\item If there are no homotopically critical points with value $t$ outside $S$, then the number of deaths at $t$ satisfies $\omega_d(t) = 0$ for all $d$.
@@
 	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
-	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so $\dim \CH_0(M) = 1$.
+	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ is epi.
+	Taking direct limits of vector spaces is exact, so the natural map $\colim H_{0}(F_{\leq \bullet}) \to \colim \CH_{0}(F_{\leq \bullet})$ is still epi. 
+	We assume $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ to be an isomorphism, so the composition $\colim H_0(F_{\leq \bullet}) \to \CH_0(M)$ is still epi.
+	But this map factors through $H_{0}(M)$, which has dimension 1, so we get $\dim \CH_0(M) = 1$.
 	Together with our assumption on the colimit, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
@@
 	Now, from \cref{lem:essential_cech_dim} we obtain that $\cp_{0} = 1$, which yields $\comega_{0}^{\epsilon} = \cc_{0}^{\epsilon} - \cp_{0} \geq 2 - 1 = 1$.
-	Thus, there must be some $t \in \R$ with $\comega_{0}(t) > 0$, so that we may apply \cref{lem:endpoint_implies_crit_pt} to obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
+	Thus, there must be some $t \in \R$ with $\comega_{0}(t) \geq \comega^{\epsilon}_{0})(t) > 0$, so that we may apply \cref{lem:endpoint_implies_crit_pt} to obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
 	If $S$ were of minimum type, then we would have $\comega_{0}(t) = 0$ by the second assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death}, contradicting the choice of $t$.
@@
 
-Throughout his work on functional topology, Morse assumed slightly varying forms of local connectivity on the resulting sublevel set filtrations in order to obtain \mbox{q-tameness}.
+Throughout his work on functional topology, Morse assumed slightly varying forms of local connectivity on the sublevel set filtrations of the functions he considered in order to obtain \mbox{q-tameness}.
 In particular, Morse and Tompkins used the following condition from \cite{Morse.1938,Morse.1940} in their application to minimal surface theory:
@@
 See also \cite[p.~ 25]{Morse.1938} and \cite[p.~464]{Morse.1939}, but note that the definitions given there contain evident typographical errors.
-Expressed in similar language as \cref{s:connectivity}, the property of local $F$-connectedness of all orders is equivalent to the following notion, applicable to general topological spaces.
+Expressed in similar language as \cref{defi:LHS}, the property of local $F$-connectedness of all orders is equivalent to the following notion, applicable to general topological spaces.
 
@@
     The sublevel set filtration of $A_g$ is also $\HLC$ for \v{C}ech homology according to \cref{prop:douglas_hlc}.
-    Finally, we have $\colim \CH_0((A_g)_{\bullet}) \to \CH_0(\Omega_g)$ is an isomorphism according to \cite[p.~444]{Morse.1939} because $A_g$ satisfies the \emph{regularity at infinity} condition by \cite[Theorem 4.3]{Morse.1939}.
+    Finally, we have that $\colim \CH_0((A_g)_{\bullet}) \to \CH_0(\Omega_g)$ is an isomorphism according to \cite[p.~444]{Morse.1939} because $A_g$ satisfies the \emph{regularity at infinity} condition by \cite[Theorem 4.3]{Morse.1939}.
     In total, \cref{thm:mountain_pass} applies to $A_g$.

### 2022-10-12 ref_reply3.tex
Add ref reply 3

--- 2022-07-13 ref_reply2.tex
@@
 
-\title{Author's second reply to the referee report of \\ \textsc{
-    ``PERSISTENCE IN FUNCTIONAL TOPOLOGY: EXISTENCE OF PERSISTENCE DIAGRAMS AND MORSE INEQUALITIES''
+\newcommand{\cc}{\check{c}}
+
+\title{Author's third reply to the referee report of \\ \textsc{
+		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
 	}
@@
 	\section{First point.}
-	After revisiting Struwe's argument for the homotopy equivalence of the sublevel sets more carefully, we were also unable to determine why Struwe supposes the level set to be compact, and we could also not establish a different argument for the necessary homotopy equivalence without returning to Morse's concept of weak upper-reducibility (WUR).
-	Hence, we have added this assumption to the Mountain Pass Theorem and we have added a lemma stating that the needed homotopy equivalence holds given that the function is WUR.
-	This lemma can be proven by a very similar argument to the (imprecise) one by Struwe, and very similar arguments also appear in Morse's monograph on functional topology, where he, however, uses a slightly stronger version of upper-reducibility, making these results not directly citable for us.
-	As a compromise between readability and precision, we have decided to just state the lemma at first without proof and with references to these similar arguments, and then to sketch a proof in a new section in the appendix.
-	There, we now also comment on the differences between Morse's notion of cap numbers and our corresponding notion.
-	The preparatory lemmas now also include the WUR assumption where necessary.
-
+	TBW
 	\section{Second point.}
-	The referee is correct in that the proposition cited from Hatcher does not actually apply in the setting as stated; in fact our lemma is not true as it was stated.
-	We have consequently added the assumption that $\colim \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
-	We also include an example in a remark after the Mountain Pass Theorem showing that if this assumption is removed it may happen that $\check{p}_0 > 1$.
-	Moreover, we added a reference in the proof of the Unstable Minimal Surface Theorem for the fact that this new assumption is satisfied for the Douglas functional, which is due to Morse's "regularity at infinity" condition.
-
+	TBW
+	\section{third point.}
+	TBW
 	\section{List of typos, minor remarks and suggestions.}
 	\begin{enumerate}
-		\item Removed as suggested (A.S.).
-		\item Changed A.S.
-		\item Removed A.S.
-		\item Changed A.S.
-		\item We have added a reference to the original paper by Douglas, where it is explained that his functional takes finite values for rectifiable curves, and we have added a very brief explanation why this applies in our setting.
-		\item Changed A.S.
-		\item Changed A.S.
-		\item We now address this point in a remark after the Mountain Pass Theorem.
-		\item We have replaced ``the following result [...] can be deduced from the Mountain Pass Theorem'' right above the Unstable Minimal Surface Theorem with ``the following result [...] can be deduced from the Mountain Pass Theorem as further explained in \S 5.2.''
-		\item We have included a reference for the fact that $M$ may be replaced by its radical and have added the explicit calculations showing that the lemma holds for the radical.
-		\item Removed A.S.
-		\item Changed A.S.
-		\item Replaced A.S.
+		\item TBW
+		\item Changed as suggested (A.S.).
+		\item Changed as suggested (A.S.).
+		\item TBW
+		\item TBW
+		\item Changed as suggested (A.S.).
+		\item TBW
+		\item TBW
+		\item TBW
+		\item TBW
+		\item TBW
+		\item TBW
+		\item TBW
 	\end{enumerate}
@@
 	\section{Other changes}
-	We fixed a typo in the proof of the Mountain Pass Theorem: It needs to be "...
-, so that in particular $\cc_{1}^{\epsilon}(t) > 0$" instead of "...
-, so that in particular $\cc_{0}^{\epsilon}(t) > 0$".
-
-	We also slightly streamlined the proof of Lemma 4.9: The third requirement on $\Sigma_{s,t}$ was unnecessary and has been removed.
-
-	We also fixed a typo in the definition of the Vietoris complex in the appendix: It should say "$\sigma \subseteq U$" instead of "$\sigma \in U$".
+	TBW
 \end{document}

### 2022-10-12 sec/surfaces.tex
Add ref reply 3

@@
 \begin{lem}\label{lem:sublevel_set_homotopy}
-	Let $F \colon M \to \R$ be a weakly upper-reducible function a metric space with compact sublevel set filtration.
+	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration.
 	If $t \in \R$ is a regular value of $F$, then there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
@@
 	Moreover, any homotopically critical point of $G$ is a homotopically critical point of $F$, so our assumption that $S$ is the set of all homotopically critical points with value $t$ of $F$ implies that $t$ is a regular value for $G$.
-	By \cref{lem:sublevel_set_homotopy},  this implies that there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} = G_{\leq s} \hookrightarrow G_{\leq t} = (F_{\leq t} \setminus S)$ is a homotopy equivalence for for all $s \in (t - \epsilon, t]$
+	By \cref{lem:sublevel_set_homotopy},  this implies that there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} = G_{\leq s} \hookrightarrow G_{\leq t} = (F_{\leq t} \setminus S)$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$
 	Hence, again using additivity of $\H$, continuity from above, and \cref{lem:birth_death_formulas}, we obtain that

### 2023-05-16 ref_reply2.tex
Sent to referee version 3

@@
 \usepackage{csquotes}
-\usepackage{hyperref}
+\usepackage{hyperref,amsmath}
 \usepackage[margin=1in]{geometry}
@@
 	The referee is correct in that the proposition cited from Hatcher does not actually apply in the setting as stated; in fact our lemma is not true as it was stated.
-	We have consequently added the assumption that $\colim \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
+	We have consequently added the assumption that $\operatorname{colim} \check{H}_0(F_{\leq \bullet}) \to \check{H}_0(M)$ needs to be an isomorphism for the Mountain Pass Theorem and have changed the lemma on the essential dimension accordingly.
 	We also include an example in a remark after the Mountain Pass Theorem showing that if this assumption is removed it may happen that $\check{p}_0 > 1$.
@@
 	We fixed a typo in the proof of the Mountain Pass Theorem: It needs to be "...
-, so that in particular $\cc_{1}^{\epsilon}(t) > 0$" instead of "...
-, so that in particular $\cc_{0}^{\epsilon}(t) > 0$".
+, so that in particular $\check c_{1}^{\epsilon}(t) > 0$" instead of "...
+, so that in particular $\check c_{0}^{\epsilon}(t) > 0$".
 

### 2023-05-16 ref_reply3.tex
Sent to referee version 3

@@
 	\maketitle
-	We want to thank the referee for his careful reading of our revised article, again providing very helpful commentary and uncovering many of our inaccuracies.
+	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports.
+To express our gratitude, we have included a corresponding sentence in the acknowledgements section of the article.
 
-	\section{First point.}
-	TBW
-	\section{Second point.}
-	TBW
-	\section{third point.}
-	TBW
+	\section{First point}
+	It was simply an oversight on our part to not include this condition.
+We have added it to the definition and also briefly expanded on why the restriction $G$ of $F$ in the proof of Lemma 5.13 is weakly upper-reducible if $F$ is.
+	\section{Second point}
+	The Eda--Kawamura result can indeed not be applied directly to the space $M$ since $M$ need not be compact.
+We have adapted the proof by applying the Eda--Kawamura result to each sublevel set of $F$ before passing to the colimits, which is still sufficient to reach our desired conclusion.
+	\section{Third point}
+	We have extended the proof of Lemma 5.11 (now Theorem 5.11) to fill the gaps left in Morse's work and make his line of reasoning using a ``related homotopy'' explicit.
+We promoted the statement to the status of a theorem, since the proof is quite extensive, and the statement itself is of general interest for Morse theory.
 	\section{List of typos, minor remarks and suggestions.}
 	\begin{enumerate}
-		\item TBW
-		\item Changed as suggested (A.S.).
-		\item Changed as suggested (A.S.).
-		\item TBW
-		\item TBW
-		\item Changed as suggested (A.S.).
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
+		\item Mentioning boundedness from below was indeed superfluous on page 26 because it follows from compactness of sublevel sets, we have removed the mention of the boundedness property.
+		\item Changed as suggested.
+		\item Changed as suggested.
+		\item It should have indeed said ``disjoint'' instead of ``distinct''. We have also corrected this in the statement of Theorems 5.3 and 5.8.
+		\item As suggested, we have distinguished the two cases where either $t_{1} \neq t_{2}$ or $t_{1} = t_{2}$.
+		\item Changed as suggested.
+		\item Weak upper-reducibility was indeed not needed here, we have removed the assumption.
+		\item Changed as suggested.
+		\item The mentioned part of the proof was indeed not quite accurate.
+We have implemented the suggested fix, where $q_{n}$ can be chosen such that $F(\varphi(q_{n},1)) \to t$ because of the assumption $t \geq F(\varphi(q,1)) > t - \epsilon$ that is supposed to lead to a contradiction.
+		\item We changed the bounds of the interval accordingly.
+		\item Changed as suggested.
+		\item The entire argument has been rewritten, so some of the relevant quantities have changed. In particular, the cover by balls of radius $\delta/3$ has been changed to balls of radius $\delta/6$.
+		\item Changed as suggested.
 	\end{enumerate}
@@
 	\section{Other changes}
-	TBW
+	\begin{enumerate}
+		\item We have slightly changed the definition of displacement function in Definition 5.1.
+Before, we were paraphrasing the version by Struwe, but now we are more closely following the version by Morse--Tompkins, which requires a certain monotonicity.
+This actually makes the continuity assumption for displacement functions unnecessary.
+We have thus also removed the continuity assumption and have correspondingly removed the explanation for why we add this assumption from Remark 5.4.
+We have also correspondingly modified the end of the second paragraph of the proof of Lemma 5.11, where continuity of the displacement function has previously been used.
+		\item We have changed the part of the proof of Lemma 5.11 where homotopies are extended from balls to the whole sublevel set insofar that we now describe the extension process before choosing a cover by finitely many balls.
+This removes the additional index $i$ in the description of the extension process, which improves readability.
+	\end{enumerate}
 \end{document}

### 2023-05-16 sec/acknowledgment.tex
After including counterexample into section 4
after second ref
Sent to referee version 3

--- 2021-09-01 aux/acknowledgment.tex
@@
+%!TEX root = ../func_top.tex
+
 \section*{Acknowledgements}
+The authors wish to thank an anonymous referee for his extensive feedback and valuable suggestions, which have greatly improved the present work.
 
-U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics}.
-
+U.B. has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 109 \emph{Discretization in Geometry and Dynamics} -- 195170736.
 A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1} and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.
-
 M.S.
-has been supported by the German Research Foundation (DFG) through	the Cluster of Excellence EXC-2181/1 \emph{STRUCTURES}, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces}.
+has been supported by the German Research Foundation (DFG) through the Collaborative Research Center SFB/TRR 191 \emph{Symplectic Structures in Geometry, Algebra and Dynamics} -- 281071066, the Cluster of Excellence EXC 2181 \emph{STRUCTURES} -- 390900948, and the Research Training Group RTG 2229 \emph{Asymptotic Invariants and Limits of Groups and Spaces} -- 281869850.

### 2023-05-16 sec/caps.tex
Add ref reply 3
Sent to referee version 3

@@
 \begin{prop}\label{prop:cap_limits}
-	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration and fix $t \in \R$.
-	Assume that $\H$ has long exact sequences for pairs of compact spaces, and that $\H_*(F_{\leq \bullet})$ is q-tame and continuous from above.
+	Let $F \colon M \to \R$ be a function on a metric space with compact sublevel set filtration and fix $t \in \R$.
+	Assume that $\H$ has long exact sequences for pairs of compact spaces, and that $\H_d(F_{\leq \bullet})$ is q-tame and continuous from above.
 	Then $\dim \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) = c_d(t)$ or both quantities are infinite.
@@
 	\colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s})
-	&\cong \im \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_*(F_{\leq t}, F_{\leq s}) \right) \\
+	&\cong \im \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right) \\
 	&\oplus \coker \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right).
@@
 		&= \dim \colim_{s: s < t} \im \left( \H_d(F_{\leq t}) \to \H_d(F_{\leq t}, F_{\leq s}) \right) \\
-		&= \dim \im \left( \H_*(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right), \\
+		&= \dim \im \left( \H_d(F_{\leq t}) \to \colim_{s: s < t} \H_d(F_{\leq t}, F_{\leq s}) \right), \\
 	\end{align*}
@@
 \begin{rem}
+	Note that the assumptions of \cref{prop:cap_limits} are in particular satisfied for \v{C}ech homology with field coefficients and a function $F$ whose sublevel set filtration is $\HLC$ with respect to this homology theory.
+
 	\cref{prop:cap_limits} only references cap limits, i.e., levels $t$ for which the \emph{cap space} $\colim_{s: s < t} \H_{d}(F_{\leq t}, F_{\leq s})$ is non-zero.
@@
 
-Note that the assumptions of \cref{prop:cap_limits} are in particular satisfied for \v{C}ech homology with field coefficients and a function $F$ whose sublevel set filtration is $\HLC$ with respect to this homology theory.
-Regarding the first difference we mentioned between our approach and the one from \cite[Theorem 8.1]{Morse.1938} with respect to upper-reducibility, we will now show that this is not an issue.
-That is, we will give an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
-As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988}.
+We now discuss the difference between our approach and the one from \cite[Theorem 8.1]{Morse.1938} concerning the assumption of upper-reducibility.
+We will show that our weakened assumptions are sufficient for the conclusion, giving an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
+As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988} (although the role of weak upper-reducibility is not addressed there). 
 \begin{proof}[Proof of \cref{lem:sublevel_set_homotopy}]
@@
 	For each $p \in F_{\leq t}$ we can find a number $\delta_{p} > 0$ and a continuous map $\varphi_{p} \colon B_{\delta_{p}}(p) \times [0,1] \to M$, where $B_{\delta_{p}}(p)$ is the open metric ball around $p$ in $F_{\leq t}$ with radius $\delta_{p}$, such that
-	\begin{enumerate}
-		\item $\varphi_{p}(\cdot,0) = \operatorname{id}$,
-		\item for all compact $V \subseteq B_{\delta_{p}}(p)$ there exists $\epsilon(p,V) > 0$ with
-		\begin{enumerate}
+	\begin{enumerate}[label={(\arabic*)}]
+		\item \label{item:id} $\varphi_{p}(\cdot,0) = \operatorname{id}$,
+		\item \label{item:epsilon} for all compact $V \subseteq B_{\delta_{p}}(p)$ there exists $\epsilon(p,V) > 0$ with
+		\begin{enumerate}[label={(\alph*)}]
 			%\item $F(\varphi_{p}(x,r))$ is non-increasing in $r$ for all $x \in B_{\delta_{p}}(p)$, and
-			\item $\varphi_{p}(V \cap F_{\leq s}\times [0,1]) \subseteq F_{\leq s}$ for all $s \in (t - \epsilon(p,V), t]$, and
-			\item $\varphi(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$.
+			\item \label{item:s_below_s} $\varphi_{p}(V \cap F_{\leq s}\times [0,1]) \subseteq F_{\leq s}$ for all $s \in [t - \epsilon(p,V), t]$,
+			\item \label{item:contracting} $\varphi_{p}(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$, and
+			\item \label{item:displacement} there exists a displacement function for $\varphi_{p}$ and $F$ on $V \cap F_{\geq t - \epsilon(p,V)}$.
 		\end{enumerate}
@@
 	Assume for a contradiction that for all neighborhoods $W \subseteq U$ there exists a compact $V \subseteq W$ such that for all $\epsilon > 0$ there is some $q \in V$ with $t \geq F(q) \geq F(\varphi(q,1)) > t - \epsilon$, where we note that $F(q) \geq F(\varphi(q,1))$ is a consequence of the existence of a displacement function on~$V$.
-	It follows that there exists a sequence $(q_{n})_{n}$ in $F_{\leq t}$ with $F(q_{n}) \to t$ and $q_{n} \to p$ for $n \to \infty$.
+	It follows that there exists a sequence $(q_{n})_{n}$ in $F_{\leq t}$ with $F(q_{n}) \to t$, $F(\varphi(q_{n},1)) \to t$, and $q_{n} \to p$ for $n \to \infty$.
 	Since $\varphi$ is continuous we have that $\varphi(q_{n},1)$ converges to $\varphi(p,1)$, which is different from $p$ by the choice of $\varphi$, so there can be no infinite subsequence of $(q_{n})_{n}$ consisting of fixed points for $\varphi(\cdot,1)$.
@@
 	By assumption, we can choose a continuous displacement function $\delta$ on $K$.
-	Since $K$ is compact, $\varphi$ is continuous, $\delta$ is continuous, and $\varphi(\cdot,1)$ has no fixed points in $K$, the function $x \mapsto \delta(d(x,\varphi(x,1)))$ attains a minimum $\epsilon > 0$ on $K$.
-	We get $F(x) - t \geq F(x) - F(\varphi(x,1)) \geq \epsilon > 0$ for all $x \in K$, which contradicts the fact that $F(q_{n}) \to t$ for $n \to \infty$.
+	Since $K$ is compact, $\varphi$ is continuous, %$\delta$ is continuous, 
+	and $\varphi(\cdot,1)$ has no fixed points in $K$, the function $x \mapsto %\delta(
+	d(x,\varphi(x,1))
+	%)
+	$ attains a minimum $\epsilon > 0$ on $K$. 
+	We get $t - F(\varphi(x,1)) \geq F(x) - F(\varphi(x,1)) > \delta(\frac{\epsilon}{2}) > 0$ for all $x \in K$, which contradicts the fact that $F(\varphi(q_{n},1)) \to t$ for $n \to \infty$.
 	This proves the claim.
 
-	Because $F_{\leq t}$ is compact, we can now choose finitely many points $p_{1}, \dots, p_{n}$ such that $F_{\leq t}$ is covered by $( B_{\frac{\delta_{p_{i}}}{3}}(p_{i}))_{i}$, and we set
-	\[
-		\epsilon \defeq \max_{i = 1,\dots,n} \epsilon \left( p_{i}, \overline{B}_{\frac{\delta_{p_{i}}}{3}}(p_{i}) \right).
-	\]
-	We extend the corresponding homotopies $\varphi_{p_{i}}$ from $B_{\delta_{p_{i}}}(p_{i})$ to all of $F_{\leq t}$, not changing them on $B_{\frac{\delta_{p_{i}}}{3}}(p_{i})$, and being the identity on $F_{\leq t} \setminus B_{\delta_{p_{i}}}(p_{i})$:
-	Let $\psi \colon [0,1] \to [0,1]$ be the continous map given by
+	Now, for any $p \in F_{\leq t}$, we extend the homotopy $\varphi_{p}$ from $B_{\delta_{p}}(p)$ to all of $F_{\leq t}$, not changing them on $B_{\frac{\delta_{p}}{3}}(p)$, and being the identity on $F_{\leq t} \setminus B_{\delta_{p}}(p)$:
+	Let $\psi \colon [0,1] \to [0,1]$ be the continuous map given by
 	\[
@@
 	\]
-	We define $\tilde{\varphi}_{i} \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ by
+	We define $\tilde{\varphi}_{p} \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ by
 	\[
-		\tilde{\varphi}_{i}(x,r) =
+		\tilde{\varphi}_{p}(x,r) =
 		\begin{cases}
-			\varphi_{p_{i}} \left( x, \psi \left( \frac{d(x,p_{i})}{\delta_{p_{i}}} \right) \cdot r \right)  & \text{if } x \in B_{\delta_{p_{i}}}(p_{i}), \\
-			x & \text{otherwise}.
+			\varphi_{p} \left( x, \psi \left( \frac{d(x,p)}{\delta_{p}} \right) \cdot r \right)  & \text{if } x \in B_{\delta_{p}}(p), \\
+			x & \text{otherwise},
 		\end{cases}
 	\]
-	Finally, we define $\varphi \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ as the concatenation of the maps $\tilde{\varphi}_{i}$, i.e., $\varphi(x,0) = x$ and $\varphi(x,r) = \varphi_{i} \left( x, n \cdot r - i \right)$ for $r \in \left( \frac{i}{n}, \frac{i+1}{n} \right]$.
-	From the properties of the maps $\varphi_{p_{i}}$ chosen in the beginning and the construction of the maps $\tilde{\varphi}_{i}$, we obtain that
-	\begin{enumerate}
+	which is continuous since $\psi(1) = 0$.
+
+	Because $F_{\leq t}$ is compact, we can now choose finitely many points $p_{1}, \dots, p_{n}$ such that $F_{\leq t}$ is covered by $( B_{\nicefrac{\delta_{p_{i}}}{6}}(p_{i}))_{i}$.
+	For these points $p_{i}$, we modify the homotopies $\tilde{\varphi}_{i} \defeq \tilde{\varphi}_{p_{i}}$ to obtain homotopies $\hat{\varphi}_{i} \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ such that
+	\begin{enumerate}[label={(\arabic*')}]
+		\item \label{item:id'} $\hat{\varphi}_{i}(\cdot,0) = \operatorname{id}$,
+		\item \label{item:epsilon'} there exists $\epsilon_{i} > 0$ such that
+		\begin{enumerate}[label={(\alph*)}, ref={(\arabic{enumi}'\alph*)}]
+			\item \label{item:s_below_s'} $\hat{\varphi}_{i}(F_{\leq s} \times [0,1]) \subseteq F_{\leq s}$ for all $s \in [t - \epsilon_{i}, t]$, 
+			\item \label{item:contracting'} $\hat{\varphi}_{i}(B_{\nicefrac{\delta_{p_{i}}}{3}}(p_{i}), 1) \subseteq F_{\leq t - \epsilon_{i}}$, and
+		\end{enumerate}
+		\item \label{item:small_change} $d(\hat{\varphi}_{i}(x, 0), \hat{\varphi}_{i}(x,1)) < \hat{\delta}$,
+			where we define 
+			\[
+				\hat{\delta} \defeq \frac{1}{6n} \min_{i} \delta_{p_{i}}.
+			\]
+	\end{enumerate}
+	Note that $\tilde{\varphi}_{i}$ already has \cref{item:id',item:epsilon'} as a consequence of $\varphi_{p_{i}}$ having \cref{item:id,item:epsilon}, but $\tilde{\varphi}_{i}$ need not have \cref{item:small_change}.
+	To construct $\hat{\varphi}_{i}$, we use the theory of $\mu$-curves from \cite{Morse.1936}: 
+	By \cite{Morse.1936}, for any continuous path $\eta \colon [0,1] \to F_{\leq t}$ there exists $\mu(\eta) > 0$ and a continuous reparametrization of $\eta$, denoted by $q(\eta) = \eta \circ \chi(\eta) \colon [0, \mu(\eta)] \to F_{\leq t}$ for some order-preserving homeomorphism $\chi(\eta) \colon [0, \mu(\eta)] \to [0,1]$, such that the resulting maps $(\eta,s) \mapsto q(\eta)(s)$ and $\eta \mapsto \mu(\eta)$ are continuous with respect to the Fr\'echet distance on the space of paths and $s$ varying in $[0, \mu(\eta)]$.
+	Moreover, for any $\eta$ and any $s \in [0, \mu(\eta)]$, it holds that
+	\begin{equation}\label{eq:mu_param}
+		\frac{1}{2}\diam\{q(\eta)(r) \mid 0 \leq r \leq s\} \leq s \leq \diam\{q(\eta)(r) \mid 0 \leq r \leq s\}.
+	\end{equation}
+	Now, for $p \in F_{\leq t}$, let $\eta_{i}(p)$ be the path given by $\tilde{\varphi}_{i}(p,\cdot)$. 
+	Since $\tilde{\varphi}_{i}$ is continuous and $F_{\leq t}$ is a compact metric space and in particular locally compact Hausdorff, the map $\eta_{i}$ is continuous with respect to the compact open topology on the space of paths, which in this case is equal to the metric topology induced by the supremum distance.
+	The supremum distance is an upper bound for the Fr\'echet distance, so $\eta_{i}$ is also continuous with respect to this distance.
+	In total, this allows us to define a continuous map $\hat{\varphi}_{i} \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ given by 
+	\[
+	\hat{\varphi}_{i}(p,s) = q(\eta_{i}(p))(\overline{\mu}_{i}(p)\cdot s),
+	\] 
+	where 
+	\[
+	\overline{\mu}_{i}(p) \defeq \min \left\{ \mu(\eta_{i}(p)), \frac{\hat{\delta}}{2} \right\}.
+	\]
+	It is clear that $\hat{\varphi}_{i}$ has \cref{item:id',item:s_below_s'} because, by construction, for all $p$ the curve $\hat{\varphi}_{i}(p,\cdot)$ is a reparametrization of the  curve $\tilde{\varphi}_{i}(p,\cdot)$ restricted to some interval $[0,a_p]$ with $a_p >0$.
+
+	To see that $\hat{\varphi}_{i}$ has \cref{item:contracting'}, we start by partitioning $B_{\nicefrac{\delta_{p_{i}}}{3}}(p_{i})$ into two disjoint subsets $B_{i}$ and $B'_{i}$,
+	 where $B_{i}$ consists of those points $p$ for which $\overline{\mu}_{i}(p) = \mu(\eta_{i}(p))$.
+	 This implies that $\hat{\varphi}_{i}(p,1) = \tilde{\varphi}_{i}(p,1)$ for all $p \in B_{i}$.
+	Thus, because $\tilde{\varphi}_{i}$ has \cref{item:contracting'}, this implies 
+	$\hat{\varphi}_{i}(B_{i}, 1) \subseteq F_{\leq t - \epsilon_i}$ for some sufficiently small $\epsilon_i > 0$.
+	It remains to verify that there exists $\epsilon_{i} > 0$ for which $\hat{\varphi}_{i}(B'_{i},1) \subseteq F_{\leq t-\epsilon_{i}}$.
+	%Now, for $p \in B'_{i}$, we have $\overline{\mu}_{i}(p) < \mu(\eta_{i}(p))$.
+%	Assume that 
+%	
+%	If $p \in F_{\leq t-\epsilon_{i}}$.
+%	
+%	
+	If $\epsilon_{i}$ is chosen according to \cref{item:s_below_s'} for $\hat{\varphi}_{i}$, then we get \[\hat{\varphi}_{i}(B'_{i} \cap F_{\leq t-\epsilon_{i}},1) \subseteq F_{\leq t-\epsilon_{i}}.\]
+	Thus, it remains to check that there exists $\epsilon_{i} > 0$ for which \[\hat{\varphi}_{i}(B'_{i} \cap F_{> t-\epsilon_{i}},1) \subseteq F_{\leq t-\epsilon_{i}}.\]
+	The closure $A_{i}$ of $B'_{i} \cap F_{> t-\epsilon_{i}}$ in $F_{\leq t}$ is a compact subset of $B_{\delta_{p_{i}}}(p_{i})$, so by \cref{item:displacement} we get a displacement function $\rho_{i}$ on $A_{i}$ for $F$ and $\varphi_{p_{i}}$.
+	Note that $\rho_{i}$ is also a displacement function for $\tilde{\varphi}_{i}$ on $A_{i} \subset \overline{B}_{\nicefrac{\delta_{p}}{3}}(p_i)$, where $\tilde{\varphi}_{i} = \varphi_{p_{i}}$.
+
+	By definition of $A_i$ and $B'_{i}$, any point $p \in A_i$ satisfies 
+	$\mu(\eta_{i}(p)) \geq \frac{\hat{\delta}}{2}$.
+	Invoking
+	\cref{eq:mu_param} with $s = \frac{\hat{\delta}}{2}$ yields 
+	\[
+	\diam\{q(\eta_{i}(p))(r) \mid 0 \leq r \leq \frac{\hat{\delta}}{2}\} \geq \frac{\hat{\delta}}{2}.
+	\]
+	Unraveling the definitions $q(\eta) = \eta \circ \chi(\eta)$
+	and letting $a_p = \chi(\eta_{i}(p))(\frac{\hat{\delta}}{2})$
+	yields
+	\[
+	\diam\{\eta_{i}(p)(s) \mid 0 \leq s \leq a_p\} \geq \frac{\hat{\delta}}{2}.
+	\]
+%
+%	By compactness, the diameter is attained by two parameters $r_1<r_2$.
+%	Let $s_1= \chi(\eta_{i}(p))(r_1)$, $s_2=\chi(\eta_{i}(p))(r_2)$ denote the corresponding parameters for the curve $\eta_{i}(p)$, so that
+%	$q(\eta_{i}(p))(r_1) = \eta_{i}(p)(s_1)$ and $q(\eta_{i}(p))(r_2) = \eta_{i}(p)(s_2)$.
+%
+	By compactness, the diameter is attained by two parameters $s_1<s_2$.
+%	We thus have
+%	$d(\eta_{i}(p)(s_1), \eta_{i}(p)(s_2)) \geq \frac{\hat{\delta}}{2}$.
+	Unraveling the definition $\eta_{i}(p)=\tilde{\varphi}_{i}(p,\cdot)$,
+	we thus have
+	\[
+	d(\tilde{\varphi}_{i}(p,s_1), \tilde{\varphi}_{i}(p,s_2) \geq \frac{\hat{\delta}}{2}.\]
+	By definition of displacement function, 
+	\[F(\tilde{\varphi}_{i}(p,s_1)) - F(\tilde{\varphi}_{i}(p,s_2)) > \rho_{i}(\nicefrac{\hat{\delta}}{2}).\]
+	Moreover, by \cref{item:s_below_s'} we have
+	\[
+	t \geq F(\tilde{\varphi}_{i}(p,s_1)).  
+	\]
+	Together, this yields
+	\[F(\tilde{\varphi}_{i}(p,s_2)) < t - \rho_{i}(\nicefrac{\hat{\delta}}{2}).\]
+	Choosing $r_2$ such that $\chi(\eta_{i}(p))(r_2)= s_2$,
+	we have
+	\[\tilde{\varphi}_{i}(p,s_2) =
+	\hat{\varphi}_{i}(p,r_2\frac{2}{\hat{\delta}}).
+	\]
+	The existence of the displacement function $\rho_i$ implies that $F \circ \hat{\varphi}_i(p,\cdot) \colon [0,1] \to \R$ is monotonically decreasing for $p \in A_i$, and thus 
+	\[F(\hat{\varphi}_{i}(p,1)) < t - \rho_{i}(\nicefrac{\hat{\delta}}{2}).\]
+	Choosing $\epsilon_i < \rho_{i}(\nicefrac{\hat{\delta}}{2})$ thus ensures that $\hat{\varphi}_{i}(B'_{i} \cap F_{> t-\epsilon_{i}},1) \subseteq F_{\leq t-\epsilon_{i}}$.
+	We conclude that $\hat{\varphi}_{i}$ has \cref{item:contracting'}.
+
+%	Want:
+%	$d(\hat{\varphi}_{i}(x, 0), \hat{\varphi}_{i}(x,1)) < \hat{\delta}$
+%	Have:
+%		\begin{equation}\label{eq:mu_param}
+%		\frac{1}{2}\diam\{q(\eta)(r) \mid 0 \leq r \leq s\} \leq s \leq \diam\{q(\eta)(r) \mid 0 \leq r \leq s\}.
+%	\end{equation}
+
+	To show \cref{item:small_change}, we observe that
+	\begin{align*}
+	d(\hat{\varphi}_{i}(x, 0), \hat{\varphi}_{i}(x,1)) &\leq
+	\diam\{q(\eta_{i}(p))(r) \mid 0 \leq r \leq \overline{\mu}_{i}(p)\} \\
+	&
+	\leq 2 \overline{\mu}_{i}(p)%\\
+	%&
+	\leq\hat{\delta},
+	\end{align*}
+	where the second inequality follows from \cref{eq:mu_param} and the third inequality from the definition of $\overline{\mu}_{i}$.
+
+	%\hat{\varphi}_{i}(p,s) = q(\eta_{i}(p))(\overline{\mu}_{i}(p)\cdot s)
+
+	Finally, we define $\varphi \colon F_{\leq t} \times [0,1] \to F_{\leq t}$ as the concatenation of the maps $\hat{\varphi}_{i}$, i.e., $\varphi(x,0) = x$ and
+	\[\varphi(x,r) = \hat{\varphi}_{i} \left( \hat{\varphi}_{i-1} \left( \dots \hat{\varphi}_{2} \left( \hat{\varphi}_{1} \left( x, 1 \right), 1 \right) \dots, 1 \right), n \cdot r - i + 1\right)\] for $r \in \left( \frac{i-1}{n}, \frac{i}{n} \right]$.
+	From $\hat{\varphi}_{i}$ having \cref{item:id',item:epsilon',item:small_change}, setting $\epsilon = \min_{i} \epsilon_{i}$, we obtain that $\varphi$ satisfies
+	\begin{enumerate}[label={(\arabic*'')}]
 		\item $\varphi(\cdot, 0) = \operatorname{id}$,
@@
 	\end{enumerate}
+	The first two properties are immediate from the corresponding properties of $\hat{\varphi}_{i}$.
+	To show \cref{item:small_change}, 
+	let $p \in F_{\leq t}$ and let $i$ be such that 
+	$p \in B_{\nicefrac{\delta_{p_{i}}}{6}}(p_{i})$.
+
+	We first show that $\varphi(p, \nicefrac i n) \in F_{\leq t - \epsilon}$.
+	We have 
+	\[
+	\varphi(p, \nicefrac i n) = \hat{\varphi}_{i} \left( \hat{\varphi}_{i-1} \left( \dots \hat{\varphi}_{2} \left( \hat{\varphi}_{1} \left( p, 1 \right), 1 \right) \dots, 1 \right), 1\right).\]
+	Since $\hat{\varphi}_{i}$ has \cref{item:contracting'}, it suffices to show that \[x:=\hat{\varphi}_{i-1} \left( \dots \hat{\varphi}_{2} \left( \hat{\varphi}_{1} \left( p, 1 \right), 1 \right) \dots, 1 \right) \in B_{\nicefrac{\delta_{p_{i}}}{3}}(p_{i}).\]
+	To see this, note that $d(p_i, p) < \nicefrac{\delta_{p_{i}}}{6}$ and $d(x,p) < (i-1)\hat{\delta} \leq (i-1) \frac 1 {6n} \delta_{p_{i}} < \nicefrac{\delta_{p_{i}}}{6}$.
+	By the triangle inequality, we now have $d(x, p_i) < \nicefrac{\delta_{p_{i}}}{3}$ as claimed.
+
+	It remains to show that the point $p$ does not leave the sublevel set at the end of the homotopy, $\varphi(p, 1) \in F_{\leq t - \epsilon}$.
+	To see this, note that			
+		\[
+	\varphi(p, 1) = 
+	%
+	\hat{\varphi}_{n} \left( \hat{\varphi}_{n-1} \left( \dots
+	\hat{\varphi}_{i+1} \left(
+	%
+	\varphi(p, \nicefrac i n) , 1 \right)\dots, 1\right), 1 \right).\]
+	Recall that the point $\varphi(p, \nicefrac i n)$ lies in the sublevel set $F_{\leq t - \epsilon}$, and each of the homotopies $\hat{\varphi}_{i+1}, \dots, \hat{\varphi}_n$ preserves the sublevel set according to \cref{item:s_below_s'} and our choice of $\epsilon = \min_{i} \epsilon_{i}$.
 	This shows that, indeed, for $s \in (t - \epsilon, t]$ the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence, with homotopy inverse given by $\varphi$.

### 2023-05-16 sec/connectivity.tex
Sent to referee version 3

@@
 
-If $f_{\leq t}$ is compact for all $t$, then the function $f$ is necessarily lower-semicontinuous and bounded from below (see \cite[p.~444]{Morse.1939} or \cite[Theorem 3.1]{Struwe.1988}).
+If $f_{\leq t}$ is compact for all $t$, then the function $f$ is necessarily lower-semicontinuous and bounded from below (see \cite[p.~444]{Morse.1939} and \cite[Theorem I.3.1]{Struwe.1988}).
 

### 2023-05-16 sec/introduction.tex
Sent to referee version 3

@@
 \end{displaycquote}
-A similar assessment was given by Bott, who writes in \cite[p.~934]{Bott.1980} that the papers \cite{Morse.1937, Morse.1940} ``are not easy reading'' and constitute a ``tour de force'' by Morse.
+A similar assessment was given by Bott, who writes in \cite[p.~934]{Bott.1980} that the papers \cite{Morse.1937, Morse.1940} ``are not easy reading'', constituting a ``tour de force'' by Morse.
 

### 2023-05-16 sec/surfaces.tex
Sent to referee version 3

@@
 	Consider a real-valued function $F$ on a metric space $(M,d)$.
-	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(p,1) \neq p$, such that for every compact subset $V \subseteq U$ there exists a continuous \emph{displacement function} $\delta \colon \R_{\geq 0} \to \R_{\geq 0}$ with
-	$\delta(e) = 0$ if and only if $e = 0$, and
+	A point $p \in M$ is called \emph{homotopically regular} if there exists a neighborhood $U$ of $p$ in $F_{\leq F(p)}$ and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(p,1) \neq p$, such that for every compact subset $V \subseteq U$ there exists a function $\delta \colon \R_{> 0} \to \R_{> 0}$ with
 	\[
-	F(\varphi(x,s)) - F(\varphi(x,t)) \geq \delta(d(\varphi(x,s),\varphi(x,t)))
+	F(\varphi(x,s)) - F(\varphi(x,t)) > \delta(e)
 	\]
-	for all $x \in V$ and $0 \leq s \leq t \leq 1$.
+	for all $x \in V$, $e > 0$, and $0 \leq s \leq t \leq 1$ such that $d(\varphi(x,s),\varphi(x,t)) > e$.
+	Such a function $\delta$ is called a \emph{displacement function} for the functions $F$ and $\varphi$ on the set $V$.
 % 	\begin{itemize}
@@
 	Let $F \colon M \to \R$ be a function on a metric space.
-	We say that $F$ is \emph{weakly upper-reducible} if for all $p \in M$ and all $c > F(p)$ there exists a neighborhood $U$ of $p$ in $F_{\leq c}$, a positive constant $\eta > 0$, and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$ and $\varphi(U,1) \subseteq F_{\leq c-\eta}$, such that on every compact subset $V \subseteq U \cap F_{\geq c - \eta}$ there exists a displacement function for $\varphi$ as in \cref{def:critical_set}.
+	We say that $F$ is \emph{weakly upper-reducible} if for all $p \in M$ and all $c > F(p)$ there exists a neighborhood $U$ of $p$ in $F_{\leq c}$, a positive constant $\eta > 0$, and a continuous map $\varphi \colon U \times [0,1] \to M$, which satisfies $\varphi(\cdot, 0) = \operatorname{id}_U$, $\varphi((U \cap F_{\leq c-\eta}) \times [0,1]) \subseteq F_{\leq c-\eta}$, and $\varphi(U,1) \subseteq F_{\leq c-\eta}$, such that on %every compact subset $V \subseteq
+	$U \cap F_{\geq c - \eta}$ there exists a displacement function for $\varphi$ and $F$ as in \cref{def:critical_set}.
 \end{defi}
 
-In \cite[p.~36]{Morse.1938}, the stronger notion of \emph{upper-reducibility}, without the prefix \emph{weakly}, is defined analogously to \cref{def:upper_reducible} with the slight difference that the existence of a displacement function is not only demanded for compact $V \subseteq U \cap F_{\geq c - \eta}$, but for all compact $V \subseteq U$.
+In \cite[p.~36]{Morse.1938}, the stronger notion of \emph{upper-reducibility}, without the prefix \emph{weakly}, is defined analogously to \cref{def:upper_reducible} with the slight difference that the existence of a displacement function is not only demanded for the neighborhoods $U \cap F_{\geq c - \eta}$, but for all neighborhoods $U \subseteq M$.
 
@@
 	Assume that the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism, and that the sublevel set filtration of $F$ is $\HLC$ with respect to \v Cech homology.
-	If $M$ contains two distinct critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.
+	If $M$ contains two disjoint critical sets of $F$ of minimum type, then it also contains a critical set not of minimum type.
 \end{thm}
@@
 \begin{rem}\label{rem:critical_set}
-    Our \cref{def:critical_set} of homotopically regular point differs slightly from that of \citet[p.~30]{Morse.1938} and \citet[p.~444--445]{Morse.1939} as their displacement functions are not explicitly assumed to be continuous.
-    As used in the proof of \cref{lem:sublevel_set_homotopy}, we require this property to establish that a homotopically regular point with value $t$ admits a neighborhood $U$ and a homotopy $\varphi$ as in \cref{def:critical_set} such that for any compact $V \subseteq U$ there is $\epsilon > 0$ with $\varphi(V, 1) \subseteq F_{\leq t - \epsilon}$.
-    That such neighborhoods exist is claimed by Morse in the proof of \cite[Lemma~8.1]{Morse.1938}, where continuity of the displacement functions is not mentioned explicitly.
-    It is not clear to us whether the claim actually holds without continuity, or whether the assumption of continuity was made implicitly.
-    Regardless, all displacement functions considered by \citet{Morse.1939} and used for the purposes of this work are indeed continuous.
-
+    %Our \cref{def:critical_set} of homotopically regular point differs slightly from that of \citet[p.~30]{Morse.1938} and \citet[p.~444--445]{Morse.1939} as their displacement functions are not explicitly assumed to be continuous.
+    %As used in the proof of \cref{thm:sublevel_set_homotopy}, we require this property to establish that a homotopically regular point with value $t$ admits a neighborhood $U$ and a homotopy $\varphi$ as in \cref{def:critical_set} such that for any compact $V \subseteq U$ there is $\epsilon > 0$ with $\varphi(V, 1) \subseteq F_{\leq t - \epsilon}$.
+    %That such neighborhoods exist is claimed by Morse in the proof of \cite[Lemma~8.1]{Morse.1938}, where continuity of the displacement functions is not mentioned explicitly.
+    %It is not clear to us whether the claim actually holds without continuity, or whether the assumption of continuity was made implicitly.
+    %Regardless, all displacement functions considered by \citet{Morse.1939} and used for the purposes of this work are indeed continuous.
+    %
 	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} also differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
@@
 \label{thm:unstable_minimial_surface}
-	If the space~$\Omega_g$ contains two minimal surfaces contained in distinct critical sets of minimum type of the functional $A_g$, then it also contains an \emph{unstable} minimal surface, i.e., a minimal surface contained in a critical set that is not of minimum type.
+	If the space~$\Omega_g$ contains two minimal surfaces contained in disjoint critical sets of minimum type of the functional $A_g$, then it also contains an \emph{unstable} minimal surface, i.e., a minimal surface contained in a critical set that is not of minimum type.
 \end{thm}
@@
 
-\begin{lem}\label{lem:sublevel_set_homotopy}
+\begin{thm}\label{thm:sublevel_set_homotopy}
 	Let $F \colon M \to \R$ be a weakly upper-reducible function on a metric space with compact sublevel set filtration.
 	If $t \in \R$ is a regular value of $F$, then there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
-\end{lem}
+\end{thm}
 
-%\cref{lem:sublevel_set_homotopy} can be shown analogously to the argument in \cite[Remark II.6.3]{Struwe.1988}, where level sets of $F$ are assumed to be compact, but $F$ is not assumed to be weakly upper-reducible.
-A weaker version of \cref{lem:sublevel_set_homotopy} is stated in \cite[Lemma 8.1]{Morse.1938}, under the slightly stronger assumption of upper-reducibility.
+%\cref{thm:sublevel_set_homotopy} can be shown analogously to the argument in \cite[Remark II.6.3]{Struwe.1988}, where level sets of $F$ are assumed to be compact, but $F$ is not assumed to be weakly upper-reducible.
+A weaker version of \cref{thm:sublevel_set_homotopy} is stated in \cite[Lemma 8.1]{Morse.1938}, under the slightly stronger assumption of upper-reducibility.
 In \cite{Morse.1939}, Morse and Tompkins introduce and use \emph{weak} upper-reducibility, noting that the results and arguments from \cite[Sections 7 and 8]{Morse.1938} still apply.
@@
 	Assume that $\H(F_{\leq \bullet})$ is q-tame and continuous from above, and consider $t \in \R$ and its birth and death numbers $\alpha_d(t)$ and $\omega_{d-1}(t)$.
-	If $\alpha_d(t) > 0$ or $\omega_{d-1}(t) > 0$ for some degree $d$, then $t$ is a critical value of $F$.
+	If $\alpha_d(t) > 0$ or $\omega_{d-1}(t) > 0$ for some degree $d$, then $t$ is a critical value of~$F$.
 \end{lem}
 \begin{proof}
-	Following \cref{lem:sublevel_set_homotopy}, we know that if $t$ is a regular value, there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
+	Following \cref{thm:sublevel_set_homotopy}, we know that if $t$ is a regular value, there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} \hookrightarrow F_{\leq t}$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$.
 	Thus, $\H(F_{\leq \bullet})$ is continuous from below at every regular value.
@@
 	The set $F_{\leq t} \setminus S$ is compact because $F_{\leq t}$ is compact and $S$ is open in $F_{\leq t}$, so the sublevel set filtration of $G$ is compact.
-	$G$ is also weakly upper-reducible because the same is true for $F$.
-	Moreover, any homotopically critical point of $G$ is a homotopically critical point of $F$, so our assumption that $S$ is the set of all homotopically critical points with value $t$ of $F$ implies that $t$ is a regular value for $G$.
-	By \cref{lem:sublevel_set_homotopy},  this implies that there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} = G_{\leq s} \hookrightarrow G_{\leq t} = (F_{\leq t} \setminus S)$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$
+	$G$ is also weakly upper-reducible because the same is true for $F$: 
+	For points $p \in F_{\leq t} \setminus S$ and $c > F(p)$ with $c > t$ one can choose $\eta > 0$ such that $c-\eta > t$, choose $U \subseteq G_{\leq c} = F_{\leq t} \setminus S$ as an arbitrary neighborhood, and take $\varphi$ to be the homotopy on $U$ such that $\varphi(\cdot,s)$ is the identity for all $s \in [0,1]$.
+	For $c \leq t$, one can choose $\eta > 0$, a neighborhood $U \subseteq F_{\leq c}$, and a homotopy $\varphi$ so that they satisfy the weak upper-reducibility conditions for $F$ and then obtain the corresponding data for $G$ by intersecting $U$ with $F_{\leq t} \setminus S$ and restricting $\varphi$ to this neighborhood of $p$ in $G_{\leq c}$.
+	In addition to the weak upper-reducibility, any homotopically critical point of $G$ is a homotopically critical point of $F$, so our assumption that $S$ is the set of all homotopically critical points with value $t$ of $F$ implies that $t$ is a regular value for $G$.
+	By \cref{thm:sublevel_set_homotopy},  this implies that there exists $\epsilon > 0$ such that the inclusion $F_{\leq s} = G_{\leq s} \hookrightarrow G_{\leq t} = (F_{\leq t} \setminus S)$ is a homotopy equivalence for all $s \in (t - \epsilon, t]$
 	Hence, again using additivity of $\H$, continuity from above, and \cref{lem:birth_death_formulas}, we obtain that
@@
 	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
-	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ is epi.
-	Taking direct limits of vector spaces is exact, so the natural map $\colim H_{0}(F_{\leq \bullet}) \to \colim \CH_{0}(F_{\leq \bullet})$ is still epi.
+	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the map $H_{0}(F_{\leq t}) \to \CH(F_{\leq t})$ is surjective for all $t$.
+	Hence, the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ of persistence modules is epi.
+	Taking colimits preserves epis, so the natural map $\colim H_{0}(F_{\leq \bullet}) \to \colim \CH_{0}(F_{\leq \bullet})$ is still epi. 
 	We assume $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ to be an isomorphism, so the composition $\colim H_0(F_{\leq \bullet}) \to \CH_0(M)$ is still epi.
 	But this map factors through $H_{0}(M)$, which has dimension 1, so we get $\dim \CH_0(M) = 1$.
-	Together with our assumption on the colimit, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
+	Together with our assumption that $\colim \CH_{0}(F_{\leq \bullet}) \cong \CH_{0}(M)$, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
 \end{proof}
@@
 %    \todo{should we move the rest of this remark to after \cref{lem:essential_cech_dim}?}
-    Note that $\cp_0 = 1$ does not already follow from just $M$ being connected, i.e., the assumption $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is non-vacuous:
+    Note that $\cp_0 = 1$ does not already follow from just $M$ being connected, i.e., the assumption that $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ be an isomorphism is non-vacuous:
 	For the lower semi-continuous function $F \colon [0,1] \to \R$ defined as $F(0) = 0$ and $F(t) = \frac1t$ for $t > 0$, we have for $t > 0$ that $F_{\leq t} = \{0\} \cup [\frac1t, 1]$.
@@
 
-	Now assume that $F$ has two distinct critical sets $S_{1}$ and $S_{2}$ of minimum type with values $t_{1}$ and $t_{2}$, respectively.
+	Now assume that $F$ has two disjoint critical sets $S_{1}$ and $S_{2}$ of minimum type with values $t_{1}$ and $t_{2}$, respectively.
+	First, consider the case where $t_{1} \neq t_{2}$.
 	Since both critical sets are non-empty, we have $\CH_{0}(S_{i}) \neq 0$, and thus the first assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death} implies $\calpha_{0}(t_{i}) \geq \dim \CH_0(S_{i}) \geq 1$ for $i = 1,2$,
@@
 	$\cc_{0}^{\epsilon} \geq \calpha_{0}^{\epsilon}(t_{1}) + \calpha_{0}^{\epsilon}(t_{2}) \geq 1 + 1 = 2$.
+	In the case where $t_{0} \defeq t_{1} = t_{2}$, the union $S = S_{1} \cup S_{2}$ is still a critical set of minimum type.
+	The first assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death} implies $\calpha_{0}(t_{0}) \geq \dim \CH_0(S) = \dim \CH_{0}(S_{1}) + \dim \CH_{0}(S_{2}) \geq 2$.
+	Similar to before, we may thus choose $\epsilon > 0$ such that $\cc_{0}^{\epsilon} \geq \calpha_{0}^{\epsilon}(t_{0}) \geq 2$.
+	Hence, in both cases we obtain $\cc_{0}^{\epsilon} \geq 2$.
 	Now, from \cref{lem:essential_cech_dim} we obtain that $\cp_{0} = 1$, which yields $\comega_{0}^{\epsilon} = \cc_{0}^{\epsilon} - \cp_{0} \geq 2 - 1 = 1$.
-	Thus, there must be some $t \in \R$ with $\comega_{0}(t) \geq \comega^{\epsilon}_{0})(t) > 0$, so that we may apply \cref{lem:endpoint_implies_crit_pt} to obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
+	Thus, there must be some $t \in \R$ with $\comega_{0}(t) \geq \comega^{\epsilon}_{0}(t) > 0$, so that we may apply \cref{lem:endpoint_implies_crit_pt} to obtain that the set $S$ of homotopically critical points at value $t$ is non-empty.
 	If $S$ were of minimum type, then we would have $\comega_{0}(t) = 0$ by the second assertion of \cref{lem:minimum_type_implies_some_birth_and_no_death}, contradicting the choice of $t$.
@@
 
-Morse then goes on to claim that the persistent \v{C}ech homology of this sublevel set filtration is q-tame, provided that $F$ is bounded from below and satisfies the assumptions of local $F$-connectivity and compactness of sublevel sets.
+Morse then goes on to claim that the persistent \v{C}ech homology of this sublevel set filtration is q-tame, provided that $F$ %is bounded from below and 
+satisfies the assumptions of local $F$-connectivity and compactness of sublevel sets.
 %, and a further condition called $F$-regularity, which is trivially satisfied if the domain of $F$ is compact.

### 2023-05-16 sec/caps.tex
Fix broken references
lem:sublevel_set_homotopy
to
thm:sublevel_set_homotopy.

@@
 We will now discuss the equivalence of our definition of cap numbers and the one used by Morse.
-Futhermore, we provide a proof of \cref{lem:sublevel_set_homotopy} establishing a homotopy equivalence of sublevel sets at a regular value.
-As a starting point, we observe that the basic use of \cref{lem:sublevel_set_homotopy} is to show that if $t$ is an endpoint of a feature in the persistence diagram associated to our function $F$, i.e., if $c(t) > 0$, then there must be a homotopically critical point with value $t$.
+Futhermore, we provide a proof of \cref{thm:sublevel_set_homotopy} establishing a homotopy equivalence of sublevel sets at a regular value.
+As a starting point, we observe that the basic use of \cref{thm:sublevel_set_homotopy} is to show that if $t$ is an endpoint of a feature in the persistence diagram associated to our function $F$, i.e., if $c(t) > 0$, then there must be a homotopically critical point with value $t$.
 To achieve this, we assume that $F$ is weakly upper-reducible and its sublevel set filtration is compact.
@@
 As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988} (although the role of weak upper-reducibility is not addressed there).
-\begin{proof}[Proof of \cref{lem:sublevel_set_homotopy}]
+\begin{proof}[Proof of \cref{thm:sublevel_set_homotopy}]
 	Let $t \in \R$ be a regular value of $F$.

### 2023-10-10 ref_reply4.tex
Before addressing 4th reply

--- 2023-05-16 ref_reply3.tex
@@
 
-\title{Author's third reply to the referee report of \\ \textsc{
+\title{Author's fourth reply to the referee report of \\ \textsc{
 		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
@@
 	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports.
-To express our gratitude, we have included a corresponding sentence in the acknowledgements section of the article.
 

### 2023-10-10 ref_reply4.tex
Fix typos found by referee (round 4)

--- 2022-10-12 ref_reply3.tex
@@
 	\maketitle
-	We want to thank the referee for his careful reading of our revised article, again providing very helpful commentary and uncovering many of our inaccuracies.
 
-	\section{First point.}
-	TBW
-	\section{Second point.}
-	TBW
-	\section{third point.}
-	TBW
-	\section{List of typos, minor remarks and suggestions.}
+	\section*{Corrections}
 	\begin{enumerate}
-		\item TBW
-		\item Changed as suggested (A.S.).
-		\item Changed as suggested (A.S.).
-		\item TBW
-		\item TBW
-		\item Changed as suggested (A.S.).
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
-		\item TBW
+		\item Fixed.
+		\item Fixed.
+		\item ...
+		\item Fixed.
+		\item ...
+		\item ...
+		\item Fixed.
+		\item ...
+		\item ...
+		\item Fixed
 	\end{enumerate}
-
-	\section{Other changes}
-	TBW
 \end{document}

### 2023-10-10 sec/persistence.tex
Fix typos found by referee (round 4)

@@
 The most commonly used existence result for barcode decompositions is due to Crawley-Boevey \cite{Crawley-Boevey.2015}.
-It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all~$t \in \R$.
+It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence module $M$ such that $M_t$ is a finite dimensional vector space for all~$t \in \R$.
 Unfortunately, the $\PFD$ condition is too restrictive for many purposes.

### 2023-10-10 sec/surfaces.tex
Fix typos found by referee (round 4)

@@
     %
-	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} also differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
+	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
 	Without this additional assumption, however, \cref{thm:mountain_pass} does not hold, as shown by the example $F \colon [0,1] \to \R$ with $F(0) = F(1) = 0$ and $F(t) = 1$ for $0 < t < 1$:
@@
 	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
-	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the map $H_{0}(F_{\leq t}) \to \CH(F_{\leq t})$ is surjective for all $t$.
+	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the map $H_{0}(F_{\leq t}) \to \CH_0(F_{\leq t})$ is surjective for all $t$.
 	Hence, the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ of persistence modules is epi.
